### 2018-01-01 tex/test-WW-type-00s-PS.tex
tex

\documentclass[a4paper,11pt]{article}
\pdfoutput=1 % if your are submitting a pdflatex (i.e. if you have
             % images in pdf, png or jpg format)

\usepackage{jheppub} % for details on the use of the package, please
                     % see the JHEP-author-manua

\usepackage{graphicx,epsfig,wrapfig,amssymb,color,amsmath,bm}

\usepackage[T1]{fontenc} % if needed

%============= FORMATING (A4) ======================================
%\setlength{\textwidth}{17cm}
%\setlength{\textheight}{26.2cm}
%\setlength{\topmargin}{-1cm}
%\renewcommand{\baselinestretch}{1.5}

\bibliographystyle{JHEP}

%=================== USE COLOURS =====================================

\usepackage{hyperref} %links in the table of contents
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\newcommand{\green}[1]{{\color{green} #1}}
\newcommand{\blue}[1]{{\color{blue} #1}}
\newcommand{\red}[1]{{\color{red} #1}}

%===================  NEW COMMANDS  ==================================
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\ba}{\begin{eqnarray}}
\newcommand{\ea}{\end{eqnarray}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\di}{ {\rm d} }
\newcommand{\with}[3]{{\Biggl|{\renewcommand*{\arraystretch}{0.8}
	\begin{array}{l} 
	\phantom{X}\\
	\mbox{\scriptsize ${#1}$}\\
	\mbox{\scriptsize ${#2}$}\\
	\mbox{\scriptsize #3}\end{array}}}}
%
%\newcommand{\xbj}{x}                   % Bjorken variable
%\newcommand{z}{z}
%\newcommand{\de}{d}                    % integration measure
%\newcommand{\ii}{i}                    % imaginary unit
%\newcommand{\eps}{\epsilon}
%\newcommand{\Tr}{\rm Tr} % Trace operator
%\newcommand{\half}{ {\textstyle\frac{1}{2}} }
\newcommand{\slim}{\mskip 1.5mu}       % small space in math
%\newcommand{\bm}{\boldsymbol}
%\newcommand{\bm}{\boldmath}
%\newcommand{\lf}{\left}
%\newcommand{\rg}{\right}
%\newcommand{\h}{\hat{\vec{h}}}
\def\T{_{_T}}
\def\C{_{_C}}

%Editing commands
\newcommand{\TD}{{\bf TODO:}}
\newcommand{\AP}[1]{{\bf AP:} {\color{red} #1}}

\definecolor{darkgreen}{rgb}{0,0.65,0}
\newcommand{\darkgreen}[1]{{\color{darkgreen} #1}}
\newcommand{\PS}[1]{\blue{\bf\boldmath #1}}

\newcommand{\SB}[1]{{\bf SB:} {\color{magenta} #1}}
\newcommand{\judge}[1]{{\boldmath \ ({\lowercase\blue{#1}}, PS)}}

\newcommand{\asym}[2]{{A_{#1}^{#2}}}
\newcommand{\asympre}[2]{{A_{#1,\langle y\rangle}^{#2}}}

 % PETER'S DEFINITIONS
%\def\bfkperp{{\bf p}_T} 
%\def\bfpperp{{\bf k}_T} 
%\def\bfhp{{\bf h}_\perp} 
%\def\bfPhperp{{\bf P}_{h\perp}}
%\def\Phperp{P_{h\perp}}

%\def\kperp{p_T}
%\def\pperp{k_T}
%\def\avkperp{\la \kperp^2 \ra}
%\def\avpperp{\la \pperp^2 \ra}

\def\bflperp{{\bm \ell}_\perp}

 % STANDARD DEFINITIONS
 %INT conventions:
\newcommand{\vect}[1]{\ensuremath{{\bm{#1}}}}
\def\bfkperp{{\bm k}_\perp} 
\def\bfpperp{{\bm P}_\perp} 
\def\bfhp{\hat{\bm h}} 
\def\bfPhperp{{\bm P}_{hT}}
\def\Phperp{P_{hT}}

\def\kperp{k_\perp}
\def\pperp{P_\perp}
\def\avkperp{\la \kperp^2 \ra}
\def\avpperp{\la \pperp^2 \ra}

\newcommand*{\FigPath}{./figs}%  
\newcommand*{\BibPath}{.}%

%===================  TITLE, AUTHORS, AFFILIATIONS ===================

\preprint{JLAB-THY-17-XXXX}

\title{	Semi-Inclusive Deep Inelastic Scattering 
	in Wandzura-Wilczek-type approximation}

\author[a]{S.~Bastami}
%\author[b]{M.~D.~Albright}
\author[c]{H.~Avakian}
\author[d]{A.~V.~Efremov} 
\author[e]{A.~Kotzinian} 
\author[f]{B.~U.~Musch} 
\author[e]{B.~Parsamyan} 
\author[b,c]{A.~Prokudin} 
\author[g]{M.~Schlegel} 
\author[a,g]{P.~Schweitzer} 
\author[g]{W.~Vogelsang}

\affiliation[a]{Department of Physics, University of Connecticut, 
	Storrs, CT 06269, U.S.A.}
\affiliation[b]{Division of Science, Penn State Berks, Reading, 
	PA 19610, USA}
\affiliation[c]{Thomas Jefferson National Accelerator Facility, 
	Newport News, VA 23606, U.S.A.}
\affiliation[d]{Joint Institute for Nuclear Research, Dubna, 
	141980 Russia}
\affiliation[e]{Dipartimento di fisica teorica, Universit\`a degli 
   studi di Torino, and Sezione dell'INFN di Torino, Via Pietro Giuria 1, 
   10125 Torino, Italy}
\affiliation[f]{Institut f\"ur Theoretische Physik, Universit\"at 
  	Regensburg, 93040 Regensburg, Germany}
\affiliation[g]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
	% Auf der Morgenstelle 14, 
	D-72076 T\"ubingen, Germany}

% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{saman.bastami@uconn.edu}
%\emailAdd{mda5232@psu.edu} % Mason Dale Albright
\emailAdd{avakian@jlab.org}
\emailAdd{efremov@theor.jinr.ru}
\emailAdd{aram.kotzinian@cern.ch}
\emailAdd{bmusch@b-mu.de}
\emailAdd{bakur@cern.ch}
\emailAdd{prokudin@jlab.org}
\emailAdd{marc.schlegel@uni-tuebingen.de}
\emailAdd{peter.schweitzer@phys.uconn.edu}
\emailAdd{werner.vogelsang@uni-tuebingen.de}

%\date{\today}
%===================  PREPRINT NUMBER, JOURNAL =======================
%\
%===================  ABSTRACT =======================================
%\begin{abstract}
\abstract{ 
We present the complete cross-section for pion production in Semi-Inclusive 
Deep Inelastic Scattering (SIDIS) in the Wandzura-Wilczek-type approximation 
up to power-suppressed ${\cal O}(1/Q^2)$ terms. We compute all % 18 
twist-2 and twist-3 SIDIS structure functions and the corresponding 
asymmetries. We discuss  the applicability of the
Wandzura-Wilczek-type approximations on the basis of available data,
and make predictions which can be tested by data from 
Jefferson Lab, COMPASS, HERMES, and the future EIC. 
The results of this paper can be readily used for phenomenology and 
for event generators for SIDIS, and will help to improve our 
understanding of the TMD theory beyond leading twist.
} 
%\end{abstract}
%\pacs{13.88.+e, % Polarization in interactions and scattering
%      13.85.Ni, % Inclusive production with identified hadrons
%      13.60.-r, % Photon and charged-lepton interactions with hadrons
 %     13.85.Qk} % Hadron-induced inclusive production with identified leptons, 
                % photons, or other nonhadronic particles (energy > 10 GeV)
\keywords{
	Wandzura-Wilczek approximation, 
	semi-inclusive deep inelastic scattering, 
	transverse momentum dependent distribution functions, 
	spin and azimuthal asymmetries, leading and subleading twist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\flushbottom

%======= SECTION 1: INTRODUCTION =====================================
\section{Introduction}
\label{Sec-1:introduction}

A great deal of what is known about the quark-gluon structure of 
nucleon is due to studies of parton distribution functions (PDFs) 
in deeply inelastic reactions. Leading-twist PDFs  tell us  how likely 
it is to find an unpolarized parton 
(described by PDF $f_1^a(x)$, $a=q,\,\bar q,\,g$) 
or a longitudinally polarized parton 
(described by PDF $g_1^a(x)$, $a=q,\,\bar q,\,g$)
in a fast-moving unpolarized or longitudinally polarized nucleon, 
which carries the fraction $x$ of the nucleon momentum.
This information depends on the ``resolution (renormalization) scale'' 
associated with the hard scale $Q$ of the process.
%, which we will not indicate for notational simplicity.
Although the PDFs  $f_1^a(x)$ and $g_1^a(x)$ continue being the 
subject of intense research (small-$x$, large-$x$, helicity sea 
and gluon distributions) they can be considered as rather 
well-known, and the frontier has been extended in the last years 
to go beyond the one-dimensional picture offered by PDFs.

One way to do this consists in a systematic inclusion of transverse 
parton momenta $\kperp$ whose effects manifest themselves in terms of
transverse momenta of the reaction products in the final state.
If these transverse momenta are much smaller than the hard scale $Q$
of the process, the formal description is given in terms of 
transverse momentum dependent distribution functions (TMDs) 
and fragmentation functions (FFs)
which are defined in terms of quark-quark correlators 
\cite{Mulders:1995dh,Boer:1997nt,Goeke:2005hb,Bacchetta:2006tn},
and depend on two independent variables: the fraction $x$ of 
nucleon momentum carried by parton, and intrinsic transverse 
momentum $\kperp$ of the parton.
Being a vector in the plane transverse with respect to the
light-cone direction singled out by the hard momentum flow in the process,
$\kperp$ allows us to access novel information on the nucleon spin structure 
through correlations of $\kperp$ with nucleon and/or parton spin. The 
latter is a well-defined concept for twist-2 TMDs interpreted in 
the infinite momentum frame or in lightcone quantization formalism.

One powerful tool to study TMDs are measurements of the SIDIS process.
By exploring various possibilities for electron/muon beam and target 
polarizations unambiguous information can be accessed on the 8 leading-twist 
TMDs \cite{Boer:1997nt} and, if one assumes factorization, on certain
linear combinations of the 16 subleading-twist TMDs 
\cite{Goeke:2005hb,Bacchetta:2006tn}.
Complementary information can be obtained 
from the Drell-Yan process \cite{Arnold:2008kf}, 
and $e^+e^-$ annihilation \cite{Metz:2016swz}.

In QCD the TMDs are independent functions. Each TMD contains unique
information on a different aspect of the nucleon structure. 
Twist-2 TMDs have partonic interpretations. Twist-3 TMDs 
give insights on quark-gluon correlations in the nucleon
\cite{Miller:2007ae,Burkardt:2007rv,Burkardt:2009rf}. 
Besides positivity constraints \cite{Bacchetta:1999kz} 
there is little model-independent information on TMDs. 
An important question with practical applications is:
do useful {\sl approximations} for TMDs exist? 
Experience from collinear PDFs encourages to explore this possibility: 
the twist-3 $g_T^a(x)$ and $h_L^a(x)$ can be expressed in terms of 
contributions from twist-2 $g_1^a(x)$ and $h_1^a(x)$, and additional 
quark-gluon-quark ($\bar{q}gq$) correlations or current quark mass 
terms \cite{Wandzura:1977qf,Jaffe:1991ra}. 
We shall refer to the latter generically as $\bar qgq$-terms, keeping in 
mind one deals in each case with matrix elements of different operators.
The $\bar qgq$-correlations contain new insights on hadron structure 
which are worthwhile exploring for their own sake, 
see \cite{Jaffe:1989xx} on $g_T^a(x)$.

The striking observation is that the $\bar qgq$-terms in $g_T^a(x)$ 
and $h_L^a(x)$ are small: theoretical mechanisms predict this 
\cite{Balla:1997hf,Dressler:1999hc,Gockeler:2000ja,Gockeler:2005vw}, 
and in the case of $g_T^a(x)$ data confirm or are compatible with these 
predictions \cite{Abe:1998wq,Anthony:2002hy}.
This approximation (``neglect of $\bar qgq$-terms'') is commonly 
known as Wandzura-Wilczek (WW) approximation \cite{Wandzura:1977qf}.
The possibility to apply this type of approximation also to TMDs has 
been explored in specific cases in \cite{Kotzinian:1995cz,Kotzinian:1997wt,
Kotzinian:2006dw,Avakian:2007mv,Metz:2008ib,Teckentrup:2009tk}.
In both cases, PDFs and TMDs, one basically assumes that the 
contributions from $\bar{q}gq$-terms can be neglected with respect to 
$\bar{q}q$-terms. But the nature of the omitted matrix elements is 
different, and in the context of TMDs one often prefers to speak 
about WW-type approximations.

In this work, after introducing the SIDIS process and defining TMDs and FFs 
(Sec.~\ref{Sec-2:SIDIS+TMDs+FF}), we shall introduce the approximations,
and review what is presently known about their reliability from experiment 
and theory (Sec.~\ref{Sec-3:WW}).
We will show that under the assumption of the validity of these approximations 
it is possible to describe all leading and subleading SIDIS structure functions
in terms of a basis of 6 TMDs and 2 FFs, and review what is presently known
about these functions (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation}).
Using the latest available extractions of the 8 basis functions  
we will systematically apply the WW and/or WW-type approximations
to SIDIS structure at leading (Sec.~\ref{Sec-6:twist-2-and-WW}) 
and subleading (Sec.~\ref{Sec-7:twist-3-and-WW}) twist.
We will conclude with a critical discussion (Sec.~\ref{Sec-8:conclusions}).

This is the first study of all SIDIS structure functions up to twist-3 
in a unique approach. Our results are of use for experiments prepared 
in the near-term (Jefferson Lab 12) or proposed in the long-term 
(Electron Ion Collider), and provide helpful input for Montecarlo event
generators \cite{Avakian:2015vha}.
Our predictions will either be confirmed within the expected accuracy, 
implying the approximations work and calling for dedicated theoretical 
explanations why. Or they will fail in certain cases, calling for 
theoretical work to explain why in some cases $\bar{q}gq$-terms are sizable.
In any case, our results will deepen our understanding.

\newpage
%======= SECTION 2: SIDIS & TMDs & FFs ===============================
\section{The SIDIS process in terms of TMDs and FFs}
\label{Sec-2:SIDIS+TMDs+FF}

In this section we review the description of the SIDIS process, 
define structure functions, PDFs, TMDs, FFs and recall how they
describe the SIDIS structure functions.

\subsection{The SIDIS process}
\label{Sec-2.1:SIDIS+structure-functions}

%------ BEGIN FIGURE 1: Kinematics of SIDIS ---------------------------
\begin{wrapfigure}[8]{RD}{8cm}
\vspace{-5mm}
\centering
	\includegraphics[width=7.5cm]{\FigPath/Fig02a-kin-SIDIS-UT.eps}
        \caption{\label{fig-kin-SIDIS}
    	Kinematics of SIDIS process $lN\to l^\prime h X$.} 
	% and the definitions of azimuthal angles in the lab frame.}
\vspace{-5mm}
\end{wrapfigure}
%------ END FIGURE 1 -------------------------------------------------

The SIDIS process is sketched in 
Fig.~\ref{fig-kin-SIDIS}. Here $l$ and $P$ are momenta of incoming 
lepton and nucleon, and $l^\prime$ and $P_h$ are the momenta of the outgoing
electron and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
selects a z-axis, and $l^\prime$ points in the direction of the x-axis 
from which azimuthal angles are counted. The relevant kinematic invariants 
are
\ba
   x  = \frac{Q^2}{2\,P\cdot  q}, \;\;
   y = \frac{P \cdot  q}{P \cdot  l}, \;\;
   z = \frac{P \cdot  P_h}{P\cdot  q}, \;\;
%   \gamma = \frac{2 M x}{Q} \; .
   Q^2=-q^2.
\label{eq:xyz}\;\;\;\;\ea
In addition to $x$, $y$, $z$ the cross section is also differential 
in the azimuthal angle $\phi_h$ of the produced hadron, the square 
of its momentum component $\Phperp$ perpendicular with respect to the 
virtual photon momentum, and the azimuthal angle $\psi_l$ characterizing 
the overall orientation of the lepton scattering plane in the lab frame.
Notice that $d \psi_l \simeq d\phi_S$ where $\phi_S$ is the azimuthal angle
of the nucleon spin vector. It is convenient to define the unpolarized
lepton -- quark scattering cross section
\ba\label{Eq:sigma0-FUU}
	\sigma_0 \equiv \frac{d \sigma}{dy} 
	= 
	\frac{4 \pi \alpha_{em}^2}{x\,y\,Q^2}
	\biggl(1-y+\frac12y^2\biggr)\;
\ea

To leading order in $1/Q$ the SIDIS cross-section is given by  
\begin{subequations}\ba\hspace{-1cm}
   &&  \frac{d^6\sigma_{\rm leading}}{dx\,dy\,dz\,d\phi_S\,d\phi_h\,d \Phperp^2}
   =	 \frac{\sigma_0 }{4\pi}\; F_{UU}(x,z,\Phperp^2)
        \Biggl\{\;1 
        + \cos(2\phi_h)\,   p_1\,A_{UU}^{\cos(2\phi_h)} \nonumber\\
   && \hspace{2cm}
  	+ S_L\sin(2\phi_h)\,p_1\,A_{UL}^{\sin(2\phi_h)}    
	+ \lambda\,S_L\,    p_2\,A_{LL}  \phantom{\frac11}\nonumber\\
   && \hspace{2cm}
	+ \lambda\,S_T\cos(\phi_h-\phi_S)\,p_2\,A_{LT}^{\cos( \phi_h-\phi_S)}
       	+ S_T\sin( \phi_h-\phi_S)\, A_{UT}^{\sin( \phi_h-\phi_S)} \phantom{\frac11}
	\nonumber\\ 
   && \hspace{2cm}
	+ S_T\sin( \phi_h+\phi_S)\,p_1\,A_{UT}^{\sin( \phi_h+\phi_S)} 
        + S_T\sin(3\phi_h-\phi_S)\,p_1\,A_{UT}^{\sin(3\phi_h-\phi_S)}\Biggr\}
    \hspace{1cm} \label{Eq:SIDIS-leading}
\ea
where $F_{UU}$ is the structure function due to transverse
polarization of the virtual photon (sometimes denoted as $F_{UU,T}$),
and we systematically neglect $1/Q^2$ corrections in 
kinematic factors and a structure function arising from
longitudinal polarization of the virtual photon 
(sometimes denoted as $F_{UU,L}$). %  poorly known in SIDIS.
The structure functions (and asymmetries $A$) also depend on $Q^2$ via the scale dependence of 
TMDs and FFs, which we do not show in formulas throughout this work.

At subleading order one has
\ba\hspace{-1cm}
   &&   \frac{d^6\sigma_{\rm subleading}}{dx\,dy\,dz\,d\phi_S\,d\phi_h\,d \Phperp^2}
   =	\frac{\sigma_0 }{4\pi} \; F_{UU}(x,z,\Phperp^2)
        \Biggl\{ 
          \cos(\phi_h)\,p_3\,A_{UU}^{\cos(\phi_h)}
  	{}
	\nonumber\\ 
   && \hspace{2cm}
	+ \lambda\sin(\phi_h)\,p_4\,A_{LU}^{\sin(\phi_h)}+ S_L\sin(\phi_h)\,p_3\,A_{UL}^{\sin(\phi_h)}    
	+ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)} \phantom{\frac11}\nonumber\\ 
   && \hspace{2cm}
	+ S_T\sin(2\phi_h-\phi_S)\,p_3\,A_{UT}^{\sin(2\phi_h-\phi_S)}
        + \lambda\,S_L\cos(\phi_h)\,p_4\,A_{LL}^{\cos(\phi_h)}\phantom{\frac11}
	\nonumber\\
   && \hspace{2cm}
  	+ \lambda\,S_T\cos(\phi_S)\,p_4\,A_{LT}^{\cos(\phi_S)}
        + \lambda\,S_T\cos(2\phi_h-\phi_S)\,p_4\,A_{LT}^{\cos(2\phi_h-\phi_S)}
	\Biggr\}
   \hspace{1cm} \label{Eq:SIDIS-subleading}
\ea\end{subequations}
Neglecting $1/Q^2$ corrections, the kinematic prefactors $p_i$ are given by 
% \ba\label{Eq:y-prefactors}
% &&	p_1 = \varepsilon \equiv  
%        \frac{1-y -\frac{1}{4}\slim \gamma^2 y^2}{1-y
%        + \frac{1}{2}\slim y^2 +\frac{1}{4}\slim \gamma^2 y^2} 
%        \approx \frac{1-y}{1-y+\frac12\,y^2} 		\;,\nonumber\\
% &&	p_2 = \sqrt{1-\epsilon^2} \approx
%        \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2} 	\;,\nonumber\\
% &&	p_3 =  \sqrt{2\varepsilon(1+\varepsilon)}
%        \approx \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2}\;,\nonumber\\
% &&	p_4 =  \sqrt{2\varepsilon(1-\varepsilon)}
%        \approx \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2} 	\;,\;\;\;
% \ea
\be\label{Eq:y-prefactors}
	p_1 = \frac{1-y}{1-y+\frac12\,y^2} 		\, , \;\;\;
	p_2 = \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2}	\, , \;\;\;
	p_3 = \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2} 	\, , \;\;\;
	p_4 = \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2}     	\, .
\ee
and the asymmetries are defined as 
\be
	A_{XY}^{\rm weight}\equiv A_{XY}^{\rm weight}(x,z,\Phperp)=
	\frac{F_{XY}^{\rm weight}(x,z,\Phperp)}{F_{UU}(x,z,\Phperp)}.
\ee
Hereby the first index $X=U(L)$ denotes the unpolarized beam
(longitudinally polarized beam with helicity $\lambda$).
The second index $Y=U(L,T)$ refers to the target which can be unpolarized
(or longitudinally, transversely polarized with respect to virtual photon).
The superscript ``weight'' indicates the azimuthal dependence with no index 
indicating an isotropic angular distribution of the produced hadrons.

Experimental collaborations often define asymmetries in terms of counts 
$N(\phi_h)$. This means the kinematic prefactors $p_i$ and $1/(x\,y\,Q^2)$ 
are included in the numerators or denominators of the asymmetries which
are averaged over $y$ within experimental kinematics. We will call the 
corresponding asymmetries $\asympre{XY}{\rm weight}$.
For instance, in unpolarized case one has 
\be
	N(\phi) = \frac{N_0}{2\pi} \biggl(1
		+ \cos\phi\;\asympre{UU}{\cos\phi_h}+
		+ \cos2\phi\;\asympre{UU}{\cos2\phi_h}\Biggr)
\ee
where $N_0$ denotes the total $\phi_h$-averaged)\
number of counts in the kinematic bin of interest.
It would be preferable if asymmetries were analyzed with known kinematic 
prefactors divided out on event-by-event basis. One could then directly 
compare asymmetries $\asym{XY}{\rm weight}$ measured in different 
experiments and kinematics, and focus on effects of evolution 
or power suppression for twist-3. In practice, data analysis is easier
with kinematic factors included. Data for such asymmetries 
$\asympre{XY}{\rm weight}$ are more easily available. We will 
define and comment on the explicit expressions as needed.

For completeness we remark that after integrating the cross section
over transverse hadron momenta one obtains 
\begin{subequations}\ba
     	\frac{d^4\sigma_{\rm leading}}{dx\,dy\,dz\,d\phi_S}
   &=&	 \frac{\sigma_0 }{2\pi}\; F_{UU}(x,z) 
        \Biggl\{\;1 + \lambda\,S_L\,    p_2\,A_{LL} \Biggr\}
    	\label{Eq:SIDIS-leading-integrated} \\
	\frac{d^4\sigma_{\rm subleading}}{dx\,dy\,dz\,d\phi_S}
   &=&	 \frac{\sigma_0 }{2\pi}\; F_{UU}(x,z) 
        \Biggl\{ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)} 
  	+ \lambda\,S_T\cos(\phi_S)\,p_4\,A_{LT}^{\cos(\phi_S)}
          \Biggr\}
     \hspace{1cm} \label{Eq:SIDIS-subleading-integrated}
\ea\end{subequations}
where (and analog for the other structure functions)
\be\label{Eq:FUU-integrated}
	F_{UU}(x,z) = \int d^2\Phperp\;F_{UU}(x,z,\Phperp)
\ee
and the asymmetries are defined as
\be
	A_{XY}^{\rm weight}(x,z) = \frac{F_{XY}^{\rm weight}(x,z)}{F_{UU}(x,z)}\,.
\ee

The connection of ``collinear'' SIDIS structure functions
in (\ref{Eq:SIDIS-leading-integrated},~\ref{Eq:SIDIS-subleading-integrated})
to those known from inclusive DIS is established by integrating over $z$
and summing over hadrons as 
\begin{subequations}\begin{alignat}{4}
	&\sum\limits_h\int d z\;z\;F_{UU}(x,z) 
	&\equiv	&&	& 2\,x\,F_1(x) \;, 
	\label{Eq:DIS-F1}\\ % x\sum_q e_q^2\,f_1^q(x) 
	&\sum\limits_h\int d z\;z\;F_{LL}(x,z) 
	&\equiv && 	& 2\,x\,g_1(x) \;, 
	\label{Eq:DIS-g1}\\ % x\sum_q e_q^2\,g_1^q(x) 
	&\sum\limits_h\int d z\;z\;F_{LT}^{\cos\phi_S}(x,z) \;\;
	&\equiv && \;\; -\,\gamma\; & 2\,x\biggl(g_1(x)+g_2(x)\biggr) \;, 
	\label{Eq:DIS-gT}\\ % -\,\frac{2M_Nx^2}{Q} \sum_q e_q^2\,g_T^q(x) 
	&\sum\limits_h\int d z\;z\;F_{UT}^{\sin\phi_S}(x,z) 
	&=      && 	    & \;\; 0 \, ,
	\label{Eq:DIS-zero}
\end{alignat}\end{subequations}
where $\gamma=2M_Nx/Q$ signals the twist-3 character of $F_{LT}^{\cos\phi_S}(x,z)$.
We consequently neglect $1/Q^2$ effects, including the twist-4 DIS structure 
function $F_2(x)$. $F_{UT}^{\sin\phi_S}(x,z)$ has no DIS counterpart due to 
time reversal symmetry of strong interactions.

\subsection{TMDs, FFs and structure functions}
\label{Sec-2.2:def-TMD-FF}

TMDs are defined in terms of light-front correlators
\be\label{Eq:correlator}
    	\Phi(x,\bfkperp)_{ij} = \int\frac{ d \xi^- d^2{\bm \xi}_\perp}{(2\pi)^3}
	\;e^{ik\xi}\;\la N(P,S)|\bar\psi_j(0)\,{\cal W}_{(0,\,\infty)}
	{\cal W}_{(\infty,\xi)}\,\psi_i(\xi)|N(P,S)\ra
    	\with{ }{\xi^+\!=\!0}{$k^+ = xP^+$}
	\ee
where the symbolic Wilson-lines refer to the SIDIS process 
\cite{Collins:2002kn}. For a generic four-vector $a^\mu$ we define
the light-cone coordinates $a^\mu=(a^+,a^-,a_\perp)$ with 
$a^\pm=(a^0\pm a^3)/\sqrt{2}$. 
The light-cone direction is singled out by the virtual photon momentum 
and transverse vectors like $\bfkperp$ are perpendicular to it. In the
virtual-photon--nucleon center-of-mass frame, nucleon and the partons 
inside it move in the $(+)$-lightcone direction, while the struck 
quark and the produced hadron move in $(-)$-light-cone direction.
In the nucleon rest frame the polarization vector is given by 
$S=(0,{\bm S}_T,S_L)$ with ${\bm S}_T^2+S_L^2=1$.

\newpage

The 8 leading-twist TMDs \cite{Boer:1997nt} are projected out from the
correlator (\ref{Eq:correlator}) as follows
(\blue{blue (online only): T-even}, \red{red  (online only): T-odd}; we suppress flavor
and renormalization scale dependence)
\begin{subequations}\ba
    \frac12\;{\rm Tr}\biggl[\gamma^+ \;\Phi(x,\bfkperp)\biggr]
    &=& \hspace{5mm}
    \blue{f_1}-\frac{\varepsilon^{jk}\kperp^j S_T^k}{M_N}\,\red{f_{1T}^\perp}\;, 
    \label{Eq:TMD-pdfs-I}\\
    \frac12\;{\rm Tr}\biggl[\gamma^+\gamma_5 \;\Phi(x,\bfkperp)\biggr] &=&
    S_L\,\blue{g_1} + \frac{\bfkperp \cdot{\bm S}_T}{M_N}\,\blue{g_{1T}^\perp}\;, 
    \label{Eq:TMD-pdfs-II}\\
    \frac12\;{\rm Tr}\biggl[i\sigma^{j+}\gamma_5 \;\Phi(x,\bfkperp)\biggr] &=&
    S_T^j\,\blue{h_1}  + S_L\,\frac{\kperp^j}{M_N}\,\blue{h_{1L}^\perp} +
    \frac{\kappa^{jk}S_T^k}{M_N^2}\,
    \blue{h_{1T}^\perp} + \frac{\varepsilon^{jk}\kperp^k}{M_N}\,\red{h_1^\perp}\;, 
    \label{Eq:TMD-pdfs-III} \hspace{15mm}
\ea
and the 16 subleading twist TMDs \cite{Mulders:1995dh,Bacchetta:2006tn}
are given by
\ba
\hspace{-5mm}    
	\frac12{\rm Tr}\biggl[\,1\;\Phi(x,\bfkperp)\biggr]         &=&
    	\frac{M_N}{P^+}\biggl[
	\hspace{5mm}\blue{e}
	-\frac{\varepsilon^{jk}\kperp^j S_T^k}{M_N}\,\red{e_T^\perp}
    	\biggr], \label{Eq:sub-TMD-pdfs-I}\\
\hspace{-5mm}    
	\frac12{\rm Tr}\biggl[i\gamma_5\Phi(x,\bfkperp)\biggr]        &=&
        \frac{M_N}{P^+}\biggl[
    	S_L\red{e_L} +\frac{\bfkperp \cdot {\bm S}_T}{M_N}\,\red{e_T}
    	\biggr], \label{Eq:sub-TMD-pdfs-II}\\
\hspace{-5mm}    
	\frac12{\rm Tr}\biggl[\,\gamma^j\,\Phi(x,\bfkperp)\biggr]        &=&
        \frac{M_N}{P^+}\biggl[
    	\frac{\kperp^j}{M_N}\blue{f^\perp}\!+\varepsilon^{jk}S_T^k\red{f_T}
	\!+\!S_L\frac{\varepsilon^{jk}\kperp^k}{M_N}\red{f_L^\perp}
	\!-\!\frac{\kappa^{jk}\varepsilon^{kl}S_T^l}{M_N^2}\red{f_T^\perp}\!
	\biggr], \label{Eq:sub-TMD-pdfs-III}\\
\hspace{-5mm}    
	\frac12{\rm Tr}\biggl[\,\gamma^j\gamma_5\Phi(x,\bfkperp)\biggr] &=&
    	\frac{M_N}{P^+}\biggl[
    	S_T^j\,\blue{g_T} 
	+ S_L\,\frac{\kperp^j}{M_N}\blue{g_L^\perp} +
	\frac{\kappa^{jk}S_T^k}{M_N^2}
    	\,\blue{g_T^\perp} 
	+\frac{\varepsilon^{jk}\kperp^k}{M_N}\,\red{g^\perp} 
	\biggr], \label{Eq:sub-TMD-pdfs-IV}\\
\hspace{-5mm}    
	\frac12{\rm Tr}\biggl[i\,\sigma^{jk}\gamma_5\Phi(x,\bfkperp)\biggr] &=&
    	\frac{M_N}{P^+}\biggl[
    	\frac{S_T^j \kperp^k-S_T^k \kperp^j}{M_N}\,\blue{h_T^\perp}
    	-\varepsilon^{jk}\,\red{h} 
	\biggr], \label{Eq:TMD-pdfs-V} \\
\hspace{-5mm}    
	\frac12{\rm Tr}\biggl[i\,\sigma^{+-}\,\gamma_5\,\Phi(x,\bfkperp)\biggr] 
	&=& \frac{M_N}{P^+}\biggl[
    	S_L\,\blue{h_L} + \frac{\bfkperp\cdot{\bm S}_T}{M_N}\,\blue{h_T}
    	\biggr]. \label{Eq:TMD-pdfs-VI}
\ea\end{subequations}
where $\kappa^{jk}\equiv (\kperp^j \kperp^k-\frac12\,\bfkperp^{\:2}\delta^{jk})$.
The indices $j,k,l$ refer to the plane transverse with respect to the
light-cone, $\epsilon^{ij}\equiv\epsilon^{-+ij}$ and $\epsilon^{0123}=+1$.
Dirac-structures not listed in (\ref{Eq:TMD-pdfs-I}--\ref{Eq:TMD-pdfs-VI}) 
are twist-4 \cite{Goeke:2005hb}.
Integrating out transverse momenta in the correlator (\ref{Eq:correlator})
leads to the `usual' PDFs known from collinear kinematics
\cite{Ralston:1979ys,Jaffe:1991ra}, namely at twist-2 level
\begin{subequations}\ba
    \frac12\;{\rm Tr}\biggl[\gamma^+ \;\Phi(x)\biggr]
    &=& \hspace{5mm}
    \blue{f_1}\;, 	\label{Eq:pdf-I}\\
    \frac12\;{\rm Tr}\biggl[\gamma^+\gamma_5 \;\Phi(x)\biggr] &=&
    S_L\,\blue{g_1}\;, 	\label{Eq:pdf-II}\\
    \frac12\;{\rm Tr}\biggl[i\sigma^{j+}\gamma_5 \;\Phi(x)\biggr] &=&
    S_T^j\,\blue{h_1}\;, \label{Eq:pdf-III} \hspace{75mm}
\ea
and at twist-3 level
\ba
    \frac12\;{\rm Tr}\biggl[\,1\;\Phi(x)\biggr] &=&
    \frac{M_N}{P^+}\;\blue{e}\;,  \label{Eq:sub-pdf-I}\\
    \frac12\;{\rm Tr}\biggl[\gamma^j\gamma_5 \;\Phi(x)\biggr] &=&
    \frac{M_N}{P^+}\;S_T^j\,\blue{g_T} \;, \label{Eq:sub-pdf-II}\\ \hspace{6mm}
    \frac12\;{\rm Tr}\biggl[\,i\,\sigma^{+-}\gamma_5 \;\Phi(x)\biggr] 
    &=& \frac{M_N}{P^+}\;S_L\,\blue{h_L}\,. \label{Eq:sub-pdf-III}\hspace{75mm}
\ea\end{subequations}
Other structures drop out either due to explicit $\kperp$-dependence,
or due to the sum rules \cite{Bacchetta:2006tn}
\be\label{Eq:sum-rules-T-odd}
	\int d^2\bfkperp\;f_T^a(x,\kperp^2)=
	\int d^2\bfkperp\;e_L^a(x,\kperp^2)=
	\int d^2\bfkperp\;h^a(x,\kperp^2)=0
\ee
imposed by time reversal constraints.

The fragmentation functions are similarly defined in terms of the correlator
\be\label{Eq:correlator-FF}
    \Delta(z,\bfpperp)_{ij} 
    = \sum\limits_X\!\int\!
    \frac{ d \xi^+ d^2 {\bm \xi}_\perp}{2z(2\pi)^3}\,e^{ip\xi}
    \, \la 0  |{\cal W}_{(\infty,\xi)}\psi_i(\xi)\,|h,X\ra\,
    \la h,X|\bar{\psi}_j(0){\cal W}_{(0,\infty)}|0\ra
    \with{\xi^-\!=\!0}
	 {p^- \!=\! P_h^-/z}
	 {${\bm p}_\perp \!=\! -\bfpperp/z$.}
    \ee
In this work we will consider only unpolarized final state hadrons.
If the produced hadron moves fast in the $(-)$ light cone direction, 
the twist-2 FFs are projected out as 
\begin{subequations}\ba
	\frac{1}{2}{\rm Tr}\big[\gamma^-\Delta(z,\bfpperp)\big]
	&=& \blue{D_1}\, , \label{eq:DeltaTr-twist-2a}\\
	\frac{1}{2}{\rm Tr}\big[i\sigma^{j-}\gamma_5\Delta(z,\bfpperp)\big]
	&=& \epsilon^{jk}\,\frac{\pperp^k}{zm_h}\red{H_1^\perp}\;, 
	\label{eq:DeltaTr-twist-2b}
\ea
and at twist-3 level
\ba
    \frac12\;{\rm Tr}\biggl[\,1\;\Delta(z,\bfpperp)\biggr]         &=&
    \phantom{-}\frac{M_h}{P^-_h}\;\blue{E}\;,  \label{eq:DeltaTr-twist-3a}\\
    \frac12\;{\rm Tr}\biggl[\;\,\gamma^j\;\Delta(z,\bfpperp)\biggr]  &=&
    -\frac{\pperp^j}{zP_h^-}\;\blue{D^\perp}\;, \label{eq:DeltaTr-twist-3b}\\
    \frac12\;{\rm Tr}\biggl[\gamma^j\gamma_5 \,\Delta(z,\bfpperp)\biggr] &=&
    \varepsilon^{jk}\,\frac{\pperp^k}{zP_h^-}\,\red{G^\perp}\;,  
	\label{eq:DeltaTr-twist-3c}\\
    \frac12\;{\rm Tr}\biggl[i\,\sigma^{jk}\gamma_5\,\Delta(z,\bfpperp)
	\biggr] &=&
    -\varepsilon^{jk}\,\frac{M_h}{P_h^-}\;\red{H}\;.  \label{eq:DeltaTr-twist-3d}
\ea\end{subequations}
Here besides scale and flavor dependence we also do not indicate
the type of hadron $h$. Integration over transverse hadron momenta leaves
us with $D_1(z)$, $E(z)$, $H(z)$ while the other structures drop out due to 
their $\pperp$ dependence.

%\subsection{Structure functions}

The structure functions in 
Eqs.~(\ref{Eq:SIDIS-leading},~\ref{Eq:SIDIS-subleading}) are described 
in Bjorken limit at tree level in terms of convolutions of TMDs 
and FFs. We define the unit vector $\bfhp   = \bfPhperp/\Phperp$ 
and use the following convolution integrals 
(see Appendix \ref{ApendixB1} for details) 
\be
 \label{Eq:def-convolution-integral}
 {\cal C}\biggl[\omega\;f\;D\biggr]
	= x \sum_a e_a^2\int d^2\bfkperp^{ } d^2\bfpperp
 	\; \delta^{(2)}(z \bfkperp^{ }+ \bfpperp^{ }-\bfPhperp^{ })\;\omega
	%\left(\bfkperp,-\frac{\bfpperp}{z}\right)
  	\; f^a(x,\bfkperp^2)\ D^a(z,\bfpperp^2)\;,
\ee
where $\omega$ is a weight function which in general depends on 
$\bfkperp$ and $\bfpperp$.
The 8 leading-twist structure functions are 
\begin{subequations}
\label{Eqs:structure-functions-twist-2}
\ba
 F_{UU}	&=&{\cal C}\biggl[\;\omega^{\{0\}}\,f_1 D_1 \;\biggr] \label{FUU}\\
 F_{LL}	&=&{\cal C}\biggl[\;\omega^{\{0\}}\,g_1 D_1 \;\biggr] \label{FLL}\\
 F_{UT}^{\sin\left(\phi_h +\phi_S\right)} 
	&=& {\cal C}\biggl[\;\omega^{\{1\}}_{\rm A} \,h_{1} H_1^{\perp}\;\biggr]
	\label{Eq:FUTCol}\\
 F_{UT}^{\sin\left(\phi_h -\phi_S\right)} 
	&=& {\cal C}\biggl[-\,\omega^{\{1\}}_{\rm B} \,f_{1T}^{\perp } D_1\,\biggr]
	\label{Eq:FUTSiv}\\
 F_{LT}^{\cos(\phi_h -\phi_S)} 
	&=& {\cal C}\biggl[\,\omega^{\{1\}}_{\rm B} \,g_{1T}^\perp D_1\biggr] 
	\label{Eq:FLT-twist-2}\\
 F_{UU}^{\cos 2\phi_h} 	
	&=& {\cal C}\biggl[\;\omega^{\{2\}}_{\rm AB}\,h_{1}^{\perp }\,H_{1}^{\perp }\;
	\biggr] \label{F_UUcos2phi}\\
 F_{UL}^{\sin 2\phi_h} 	
	&=& {\cal C}\biggl[\;\omega^{\{2\}}_{\rm AB}\,h_{1L}^{\perp } H_{1}^{\perp }\; 
	\biggr] \label{F_UUsin2phi}\\
 F_{UT}^{\sin\left(3\phi_h -\phi_S\right)} 
	&=& {\cal C}\biggl[\;\omega^{\{3\}}_{\rm { }}\,h_{1T}^{\perp } H_1^{\perp }\; 
	\biggr] \, . \hspace{75mm} \label{Eq:FUTpretzel}
\ea\end{subequations}
At subleading-twist we have the structure functions
\begin{subequations}
\label{Eqs:structure-functions-twist-3}
\ba
	F_{UU}^{\cos\phi_h}  
	&=& 
	\frac{2M}{Q}\,{\cal C}\biggl[\phantom{-}
   	\omega^{\{1\}}_{\rm A} 
	\biggl( x h\,H_{1}^{\perp } 
   	+ r_h^{ }\,\,f_1 \frac{\tilde{D}^{\perp }}{z}\biggr)
	- \omega^{\{1\}}_{\rm B} \biggl( x  f^{\perp } D_1
   	+ r_h^{ }\,\,h_{1}^{\perp } \frac{\tilde{H}}{z}\biggr)\biggr]\;
	\label{Eq:FUUcosphi}\\
	F_{LU}^{\sin\phi_h}  
	&=& 
	\frac{2M}{Q}\,{\cal C}\biggl[ \phantom{-}
	\omega^{\{1\}}_{\rm A}
   	\biggl( x \, e \, H_1^{\perp } 
   	+ r_h^{ }\,\,f_1\frac{\tilde{G}^{\perp }}{z}\,\biggr)
   	+\omega^{\{1\}}_{\rm B}
   	\biggl( x   g^{\perp }  D_1 
   	+ r_h^{ }\,\, h_1^{\perp } \,\frac{\tilde{E}}{z} \biggr)\biggr]\;
	\label{FLUsinphi}\\
	F_{UL}^{\sin\phi_h} 
 	&=& 
	\frac{2M}{Q}\,{\cal C}\biggl[\phantom{-}
   	\omega^{\{1\}}_{\rm A}
    	\biggl( x   h_L  H_1^{\perp } \! 
   	+ r_h^{ }\,\,g_{1}\frac{\tilde{G}^{\perp } }{z}\biggr)
   	+\omega^{\{1\}}_{\rm B}
    	\biggl( x  f_{L}^{\perp }  D_1 \!
   	- r_h^{ }\,\, h_{1L}^{\perp }  \frac{\tilde{H}}{z}\biggr)\biggr]\;
	\label{FULsinphi}\\
	F_{LL}^{\cos \phi_h} 
 	&=& 
	\frac{2M}{Q}\,{\cal C}\biggl[ 
	-\omega^{\{1\}}_{\rm A}
   	\biggl( x  e_L  H_1^{\perp }
   	- r_h^{ }\,\,g_{1}   \frac{\tilde{D}^{\perp }}{z}\biggr)
   	-\omega^{\{1\}}_{\rm B}
   	\biggl( x   g_L^{\perp }   D_1
   	+  r_h^{ }\,\,h_{1L}^{\perp } \frac{\tilde{E}}{z}\biggr)\biggr]
	\label{FLLcosphi}\;\;\;\;\\
	F_{UT}^{\sin \phi_S } 
	&=&  
	\frac{2M}{Q}\,{\cal C}\biggl[ \phantom{-}
	\omega^{\{0\}}\,\biggl(x   f_T   D_1 \;
   	- r_h^{ }\, \; h_{1} \, \frac{\tilde{H}}{z} \biggr)\nonumber\\
   	&&\hspace{1.2cm}
   	-\frac{\omega^{\{2\}}_{\rm B}}{2}
	\biggl( x   h_{T}  H_{1}^{\perp } 
   	+ r_h^{ }\, g_{1T}^\perp \,\frac{\tilde{G}^{\perp }}{z}
   	- x   h_{T}^{\perp }  H_{1}^{\perp } 
	+ r_h^{ }\, f_{1T}^{\perp } \,\frac{\tilde{D}^{\perp }}{z}
   	\biggr) \biggr]\; \label{FUTsinphiS}\\ 
	F_{LT}^{\cos \phi_S} 
	&=& 
	\frac{2M}{Q}\,{\cal C}\biggl[
   	- \omega^{\{0\}}\,\biggl(x   g_T   D_1
   	+ r_h^{ }\, \, h_{1}  \frac{\tilde{E}}{z} \biggr)\nonumber\\
   	&&\hspace{1.2cm}
	+\frac{\omega^{\{2\}}_{\rm B}}{2}
   	\biggl( x   e_{T}  H_{1}^{\perp } 
   	- r_h^{ }\, g_{1T}^\perp \,\frac{\tilde{D}^{\perp }}{z}
   	+  x   e_{T}^{\perp }  H_{1}^{\perp } 
   	+ r_h^{ }\,f_{1T}^{\perp }\,\frac{\tilde{G}^{\perp }}{z}\biggr)\biggr]
	\; \label{FLTcosphiS} \\ \hspace{-5mm}
	F_{UT}^{\sin(2\phi_h -\phi_S)} 
	&=& 
	\frac{2M}{Q}\,{\cal C}\biggl[\phantom{-}
   	\frac{\omega^{\{2\}}_{\rm AB}}{2}\,
   	\biggl( x   h_{T}  H_{1}^{\perp } 
   	+ r_h^{ }\, g_{1T}^\perp \,\frac{\tilde{G}^{\perp }}{z}
        + x   h_{T}^{\perp }  H_{1}^{\perp } 
   	- r_h^{ }\, f_{1T}^{\perp } \,\frac{\tilde{D}^{\perp }}{z}
	\biggr)\nonumber\\
	&&\hspace{1.3cm}
	+
   	\omega^{\{2\}}_{\rm C}
   	\biggl( x   f_T^{\perp } D_1
   	- r_h^{ }\, \, h_{1T}^{\perp }  \frac{\tilde{H}}{z}\biggr) \biggr]
\ea
\ba
	F_{LT}^{\cos(2\phi_h - \phi_S)} 
	&=& \frac{2M}{Q}\,{\cal C}\biggl[
   	- \frac{\omega^{\{2\}}_{\rm AB}}{2}
   	\biggl( x   e_{T}  H_{1}^{\perp } 
   	- r_h^{ }\, g_{1T}^\perp \,\frac{\tilde{D}^{\perp }}{z}
	- x   e_{T}^{\perp }  H_{1}^{\perp } 
   	- r_h^{ }\, f_{1T}^{\perp } \,\frac{\tilde{G}^{\perp }}{z}\biggr)\nonumber\\
	&&\hspace{1.3cm}
   	- \omega^{\{2\}}_{\rm C}
   	\biggl( x   g_T^{\perp }   D_1
   	+ r_h^{ }\, \, h_{1T}^{\perp }  \frac{\tilde{E}}{z}\biggr)\biggr]\; 
	\label{FLTsin(2phi-phiS)}
\ea\end{subequations}
where $r_h = m_h/M_N$ and 
$F_{XY}^{\rm weight}\equiv F_{XY}^{\rm weight}(x,z,\Phperp)$.
The weight functions are defined as
\ba
&& \omega^{\{0\}}  	= 1 \, , \nonumber\\
&& \omega^{\{1\}}_{\rm A} 	= \frac{\bfhp\cdot\bfpperp^{ }}{z m_h}  \, , \;\;\;
   \omega^{\{1\}}_{\rm B} 	= \frac{\bfhp\cdot\bfkperp^{ }}{M_N}\,,\nonumber\\
&& \omega^{\{2\}}_{\rm A} 	=  \frac{2\, \bigl(\bfhp\cdot\bfpperp^{ }\bigr)\,
			\bigl(\bfhp\cdot\bfkperp^{ }\bigr)}{zM_Nm_h}\,,\;\;\;
   \omega^{\{2\}}_{\rm B}	= -\frac{\bfpperp^{ }\cdot\bfkperp^{ }}{zM_Nm_h}\,,\;\;\;
   \omega^{\{2\}}_{\rm C}	= \frac{2\,(\bfhp\cdot\bfkperp^{ })^2-\bfkperp^2}{2M_N^2}
			\, ,\nonumber\\
&& \omega^{\{3\}}_{\rm{ }}	= \frac{
			 4\,(\bfhp\cdot\bfpperp^{ })\,(\bfhp\cdot\bfkperp^{ })^2
			-2\,\bigl(\bfhp\cdot\bfkperp^{ }\bigr)\, 
        		\bigl(\bfkperp^{ }\cdot\bfpperp^{ }\bigr)
   			-\bigl(\bfhp\cdot\bfpperp^{ }\bigr)\,\bfkperp^2\
   			}{2 z M_N^2 m_h}\,,
			\label{Eq:wi} \ea
and $\omega^{\{2\}}_{\rm AB} = \omega^{\{2\}}_{\rm A} + \omega^{\{2\}}_{\rm B}$.
In $\omega^{\{n\}}_{i}$ the index $n=0,\,1,\,2,\,3$ indicates the (maximal)
power $(\Phperp)^N$ with which the corresponding contribution scales,
and index $i$ (if any) distinguishes different types of contributions
at the given order $N$.
Notice that twist-3 structure functions in 
Eqs.~(\ref{Eq:FUUcosphi}--\ref{FLTsin(2phi-phiS)}) contain an explicit 
factor $M/Q$. We also recall that we neglect two structure functions 
due to longitudinal virtual photon polarization which contribute,
in the TMD factorization framework, at order ${\cal O}(M^2/Q^2)$, 
one being $F_{UU,L}$ and the other contributing to the 
$\sin(\phi_h-\phi_S)$ angular distribution \cite{Bacchetta:2006tn}.

The structures surviving $\Phperp$-integration of the SIDIS cross section in 
(\ref{Eq:SIDIS-leading-integrated},~\ref{Eq:SIDIS-subleading-integrated})
are associated with the trivial weights $\omega^{\{0\}}$ and expressed in 
terms of collinear PDFs and FFs as follows (here the 
sum rules (\ref{Eq:sum-rules-T-odd}) are used)
\begin{subequations}\ba
	F_{UU}(x,z) &=& x\sum\limits_ae_a^2\,f_1^a(x)\,D_1^a(z)
	\label{Eq:FUU-collinear}\\
	F_{LL}(x,z) &=& x\sum\limits_ae_a^2\,g_1^a(x)\,D_1^a(z)
	\label{Eq:FLL-collinear}\\
 	F_{LT}^{\cos\phi_S}(x,z) &=& -\,\frac{2M_N}{Q}\; x\sum_a e_a^2\,
	\biggl(x\,g_T^q(x) + r_h\,h_1^a(x)\frac{\tilde{E}^a(z)}{z}\biggr)
	\label{Eq:FLT-collinear}\\
	 F_{UT}^{\sin\phi_S}(x,z) &=& -\,\frac{2\,m_h}{Q}\; x\sum_a e_a^2\,
	h_1^a(x)\frac{\tilde{H}^a(z)}{z}
	\label{Eq:FUT-collinear}
\ea\end{subequations}
Finally, using the sum rules for the T-odd FFs 
$\sum_h\int d z\;\tilde{E}^a(z)=0$ and
$\sum_h\int d z\;\tilde{H}^a(z)=0$ we recover
Eqs.~(\ref{Eq:DIS-F1}--\ref{Eq:DIS-zero}) and obtain for the DIS structure 
functions
\begin{subequations}\ba
    F_1(x) & = & \frac{1}{2}\sum_a e_a^2\,f_1^a(x) \label{Eq:DIS-F1-II}\\
    g_1(x) & = & \frac{1}{2}\sum_a e_a^2\,g_1^a(x) \label{Eq:DIS-g1-II}\\
    g_2(x) & = & \frac{1}{2}\sum_a e_a^2\,g_T^a(x)\;-\;g_1(x) \label{Eq:DIS-g2}
	\hspace{25mm}
\ea\end{subequations}
Having established the notation we now define and discuss the
approximations.

%======= SECTION 3: WW APPROXIMATIONS ================================
\section{WW and WW-type approximations}
\label{Sec-3:WW}

In this section we will define the approximations and review what is
known about them.
The basic idea of the approximations is simple. One assumes that the 
contributions from $\bar{q}gq$-terms can be neglected with respect to 
$\bar{q}q$-terms with a useful accuracy,
\be\label{Eq:WW-generic}
	\biggl|\frac{\la\bar{q}gq\ra}{\la\bar{q}q\ra}\biggr| \ll 1\,.
\ee

\subsection{WW approximation for PDF\lowercase{s}}
\label{Sec-3.1:WW-classic}

The WW approximation applies in principle to all twist-3 PDFs,
Eqs.~(\ref{Eq:sub-pdf-I},~\ref{Eq:sub-pdf-II},~\ref{Eq:sub-pdf-III}).
It was established first for $g_T^a(x)$ \cite{Wandzura:1977qf}, and 
later for $h_L^a(x)$ \cite{Jaffe:1991ra}. The situation of $e^a(x)$ 
is somewhat special, see below and the review \cite{Efremov:2002qh}.

The origin of the approximations is as follows.
The operators defining $g_T^a(x)$ and~$h_L^a(x)$ can be decomposed by means 
of QCD equations of motion in twist-2 parts, and pure twist-3 
(interaction dependent) $\bar qgq$-terms and current quark mass
terms. We denote $\bar qgq$-terms and mass-terms collectively 
and symbolically by functions with a tilde.
Such decompositions are possible because $g_T^a(x)$ and $h_L^a(x)$ are 
``twist-3'' not according to the ``strict QCD definition''
(twist $=$ mass dimension of associated local operator minus its spin).
Rather they are classified according to the ``working definition'' 
\cite{Jaffe:1996zw}  
(a function is ``twist $t$'' if it contributes to cross sections
suppressed by $(M/Q)^{t-2}$ with $M$ a generic hadronic and $Q$ the 
hard scale).
The two definitions coincide for twist-2 quantities, but higher twist
observables in general contain ``contaminations'' by leading twist.

In this way one obtains the decompositions and, if they apply, WW 
approximations \cite{Wandzura:1977qf,Jaffe:1991ra} (keep in mind 
here tilde terms contain pure twist-3 and current quark mass terms)
\begin{subequations}\begin{alignat}{3}
   	g_T^a(x) &=& 
        \phantom{2x}\;\int_x^1\frac{ d y}{y}\,g_1^a(y) + &\tilde{g}_T^a(x)
        \stackrel{\rm WW}{\approx} 
        \phantom{2x}\;\int_x^1\frac{ d y}{y}\,g_1^a(y) \;, 
	\label{Eq:WW-original1} \\
   	h_L^a(x) &=& 2x\int_x^1\frac{ d y}{y^2}\,h_1^a(y) + &\tilde{h}_L^a(x)
        \stackrel{\rm WW}{\approx} 2x\int_x^1\frac{ d y}{y^2}\,h_1^a(y)\;,
	\label{Eq:WW-original2}\\
   	x\,e^a(x) &=& x\,&\tilde{e}^a(x) \;\stackrel{\rm WW}{\approx} 
	\;\;\;\; 0
\end{alignat}\end{subequations}
where we included $e^a(x)$ which ia a special case in the sense that it 
receives no twist-2 contribution. Notice that a prefactor of $x$ is
provided to cancel a $\delta(x)$-type singularity \cite{Efremov:2002qh}.
After introducing the WW-type approximations for TMDs and FFs,
we will come back to (\ref{Eq:WW-original1},~\ref{Eq:WW-original2}) and 
review the theoretical predictions and experimental data supporting them.

\subsection{WW-type approximations for TMDs and FFs}
\label{Sec-3.2:WW-type-TMD-FF}

Analog to WW approximations for PDFs discussed in 
Sec.~\ref{Sec-3.1:WW-classic}, also certain TMDs and FFs
can be decomposed in twist-2 contributions and tilde-terms.
The latter may be assumed, in the spirit of (\ref{Eq:WW-generic}),
to be small. Hereby it is important to keep in mind that one deals 
with different types of (``unintegrated'') $\bar qgq$-correlations,
and we prefer to refer to them as WW-type approximations.

In the T-even case one obtains the following approximations,
where the terms on the left-hand-side are twist-3, those on the 
right-hand-side (if any) are twist-2,
\begin{subequations}\ba
xe^q(x,\kperp^2)	&\stackrel{\rm WW-type}{\approx}& 
			0, 
			\label{Eq:WW-type-1}\\
xf^{\perp q}(x,\kperp^2)  &\stackrel{\rm WW-type}{\approx}& 
			f_{1}^q(x,\kperp^2),
			\label{Eq:WW-type-Cahn}\phantom{\frac11}\\
xg_L^{\perp q}(x,\kperp^2)&\stackrel{\rm WW-type}{\approx}& 
			g_{1}^q(x,\kperp^2),
			\label{Eq:WW-type-gLperp}\phantom{\frac11}\\
xg_T^{\perp q}(x,\kperp^2)&\stackrel{\rm WW-type}{\approx}& 
			g_{1T}^{\perp q}(x,\kperp^2),\phantom{\frac11}
			\label{Eq:WW-type-gTperp}\\
xg_T^q(x,\kperp^2)   	&\stackrel{\rm WW-type}{\approx}& 
             		g_{1T}^{\perp(1)q}(x,\kperp^2), 
			\label{Eq:WW-type-5}\\
xh_L^q(x,\kperp^2)	&\stackrel{\rm WW-type}{\approx}& -2 \,
                       	h_{1L}^{\perp(1)q}(x,\kperp^2),\phantom{\frac11}
                       	\label{Eq:WW-type-6}\\
xh_T^q(x,\kperp^2)      &\stackrel{\rm WW-type}{\approx}& 
                       	- h_1^q(x,\kperp^2) - h_{1T}^{\perp(1)}(x,\kperp^2),
                       	\label{Eq:WW-type-7}\\
xh_T^{\perp q}(x,\kperp^2)&\stackrel{\rm WW-type}{\approx}& 
                       	\phantom{-}h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2).
                       	\phantom{\frac11} \label{Eq:WW-type-8}
\ea\end{subequations}
In the T-odd case one obtains the approximations
\begin{subequations}\ba
xe_L^q(x,\kperp^2)         	&\stackrel{\rm WW-type}{\approx}& 0, \\
xe_T^q(x,\kperp^2)         	&\stackrel{\rm WW-type}{\approx}& 0, \\
xe_T^{\perp q}(x,\kperp^2) 	&\stackrel{\rm WW-type}{\approx}& 0, \\
xg^{\perp q}(x,\kperp^2)   	&\stackrel{\rm WW-type}{\approx}& 0, 
                       	\label{Eq:WW-type-gperp}\\
xf_L^{\perp q}(x,\kperp^2) 	&\stackrel{\rm WW-type}{\approx}& 0, 
			\phantom{\frac11}\\
xf_T^{\perp q}(x,\kperp^2) 	&\stackrel{\rm WW-type}{\approx}& 
                       	\phantom{-}\,f_{1T}^{\perp q}(x,\kperp^2),
			\phantom{\frac11}
                       	\label{Eq:WW-type-fTperp}\\
xf_T^{q}(x,\kperp^2)       	&\stackrel{\rm WW-type}{\approx}& 
                       	-\,f_{1T}^{\perp(1)q}(x,\kperp^2), \label{Eq:WW-type-fT}\\
xh^q(x,\kperp^2)           	&\stackrel{\rm WW-type}{\approx}& 
                       	- 2\,{h_1^{\perp(1)}(x,\kperp^2)},\phantom{\frac11 XXXXx} 
                       	\label{Eq:WW-type-last} 
\ea\end{subequations}
where the superscript ``(1)'' denotes transverse 
moments of TMDs defined generically as  
\ba
f^{(1)}(x,\kperp^2) = \frac{\kperp^2}{2M^2}\,f(x, \kperp^2)\; , \;\;\;
f^{(1)}(x ) = \int d^2 \bfkperp f^{(1)}(x,\kperp^2) \; . 
\ea

Two very useful WW-type approximations follow from combining the
WW approximations (\ref{Eq:WW-original1},~\ref{Eq:WW-original2}) with the
WW-type approximations (\ref{Eq:WW-type-5},~\ref{Eq:WW-type-6}).
This yields \cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv}
\begin{subequations}\ba
   	g_{1T}^{\perp(1)a}(x)&\stackrel{\rm WW-type}{\approx}& 
        \phantom{-} x\,\int_x^1\frac{d y}{y\;}\,g_1^a(y) \;,
	\label{Eq:WW-approx-g1T}\\
    	h_{1L}^{\perp(1)a}(x)&\stackrel{\rm WW-type}{\approx}& -
	x^2\!\int_x^1\frac{d y}{y^2\;}\,h_1^a(y)\;.
	\label{Eq:WW-approx-h1L}
\ea\end{subequations}
Aspects and phenomenological applications of some of the above
WW-type approximations were discussed in 
\cite{Tangerman:1994bb,Kotzinian:1995cz,Mulders:1995dh,Kotzinian:1997wt,
Kotzinian:2006dw,Avakian:2007mv,Metz:2008ib,Teckentrup:2009tk}.

WW-relations for FFs are actually not needed: in Eqs.~%
(\ref{Eqs:structure-functions-twist-2},~\ref{Eqs:structure-functions-twist-2})
either twist-2 FFs $D_1^a$, $H_1^{\perp a}$ enter or tilde FFs, as a consequence 
of how the azimuthal angles are defined \cite{Bacchetta:2006tn}. 
For completeness we quote the WW-type approximations for FFs
\cite{Bacchetta:2006tn}
\begin{subequations}\ba
	E(z,\pperp^2)      &\stackrel{\rm WW-type}{\approx}& 0 \, ,
	\label{Eq:WW-type-FF-1}\\
	G^\perp(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}& 0 \, ,
	\label{Eq:WW-type-FF-2}\\
	D^\perp(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}
	& \hspace{11mm}z\,D_1(z,\pperp)\,, \label{Eq:WW-type-FF-3}\\
	H(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}& 
	-\frac{\pperp^2}{zM_h^2}\;H_1^\perp(z,\pperp)\,. \label{Eq:WW-type-FF-4}
\ea\end{subequations}
Having introduced the WW- and WW-type approximations, we will review
in the following what is currently known from theory and experiment 
about our approximations.

\subsection{Predictions from instanton vacuum model}
\label{Sec-3.3:WW-classic-instanton}

Insights on the relatve size of hadronic matrix elements, such as 
Eq.~(\ref{Eq:WW-generic}), require a non-perturbative approach. It is 
by no means obvious which small parameter in the strong interaction 
regime would allow to explain such results.

A powerful non-perturbative approach is provided by the instanton model 
of the QCD vacuum \cite{Shuryak:1981ff,Diakonov:1983hh,Diakonov:1995qy}.
This semi-classical approach assumes that properties of the QCD vacuum 
are dominated by instantons and anti-instantons, topological non-perturbative 
gluon field configurations, which form a strongly interacting medium.
The approach provides a natural mechanism for dynamical chiral symmetry 
breaking, the dominant feature of strong interactions in the nonperturbative
regime. It was shown with variational and numerical methods that the strongly
interacting instanton medium is dilute. The ratio of average instanton size 
$\rho_{\rm av}$ and average instanton separation $R_{\rm av}$ is a non-trivial
small parameter, numerically $\rho_{\rm av}/R_{\rm av}\sim1/3$ 
\cite{Shuryak:1981ff,Diakonov:1983hh,Diakonov:1995qy}, 
which can be explored.

Applying the instanton vacuum model to studies of $g_T^a(x)$ and $h_L^a(x)$
it was predicted that matrix elements of the $\bar qgq$ operators defining 
$\tilde{g}_T^a(x)$ \cite{Balla:1997hf} and $\tilde{h}_L^a(x)$ 
\cite{Dressler:1999hc} are strongly suppressed by powers of the small
parameter $\rho_{\rm av}/R_{\rm av}$ with respect to contributions from the 
respective twist-2 parts which are of the order $(\rho_{\rm av}/R_{\rm av})^0$. 
Numerically it was found 
\be\label{Eq:WW-instanoton}
	\biggl|\frac{\la\bar{q}gq\ra}{\la\bar{q}q\ra}\biggr| \sim 
	\biggl(\frac{\rho}{R}\biggr)^{\!4} \log\biggl(\frac{\rho}{R}\biggr)
	\sim 10^{-2}
\ee
in these 2 cases. This result strongly supports the generic approximation
in Eq.~(\ref{Eq:WW-generic}) with the instanton packing fraction providing 
the non-trivial small parameter justifying the neglect of tilde-terms. 
The instanton calculus has not yet been applied to $\tilde{e}^a(x)$.

Noteworthy, the instanton vacuum predictions for $\tilde{g}_T^a(x)$
were made before the advent of the first precise data on $g_2(x)$
which we discuss in the next section.

\newpage
\subsection{Tests of WW approximation in DIS experiments}
\label{Sec-3.4:WW-classic-experiment}

The presently available phenomenological information on $g_T^a(x)$ is due 
to measurements of the structure function $g_2(x)$, Eq.~(\ref{Eq:DIS-g2}),
in DIS off various transversely polarized targets. In the WW-approximation 
(\ref{Eq:WW-original1}) one can write $g_2(x)$ as a total derivative
expressed in terms of the experimentally well known twist-2
structure function $g_1(x)$ as follows
\be
    	g_2(x) \stackrel{\rm WW}{\approx} g_2(x)_{\rm WW} \equiv
	\frac{ d\;}{ d x}\;\Biggl[\frac{x}{2}\int_x^1\frac{ d y}{y}
	\;g_1(y)\Biggr]\,.\label{Eq:g2-in-WW-approximation}
\ee
Data support (\ref{Eq:g2-in-WW-approximation}) to a good accuracy
\cite{Anthony:2002hy,Abe:1998wq}, although especially at smaller 
$x$ more stringent tests are not yet possible. Overall it has been
estimated that the WW approximation for $g_2(x)$ and $g_T^a(x)$ works 
with an accuracy of about $40\,\%$ or better \cite{Accardi:2009au}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t!]
\centering
\includegraphics[width=0.6\textwidth]{\FigPath/g2.pdf} 
\caption{\label{Fig:g2} 
$g_{2}$ structure function in  WW-approximation, 
Eq.~(\ref{Eq:g2-in-WW-approximation}), for proton (P) and neutron (N)
targets. The data are from \cite{Anthony:2002hy,Abe:1998wq}.
The error band procedure is described in the text.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We present calculations of $g_2(x)_{WW}$ in Fig.~\ref{Fig:g2}.
How well does the WW approximation describe data if we allow for a
theoretical ``error band'' of about $40\,\%$ as deduced in 
\cite{Accardi:2009au}? In order to investigate this question, 
we split this uncertainty in two parts, $\varepsilon_1=\pm 20\,\%$ and 
$\varepsilon_2(x)=\pm 20\,\%(1-x)^\epsilon$ with a small $\epsilon>0$,
and estimate the impact of this uncertainty as 
\be\label{Eq:g2-in-WW-model-violation}
    g_2(x)_{\rm WW} = (1\pm\varepsilon_1)\frac{ d\;}{ d x}\;\Biggl[
    x\int_x^1\frac{ d y}{y} \,\biggl(
    \frac12\sum_ae_a^2\,g_1^a(y(1\pm\varepsilon_2))\biggr)\Biggr]\,.
\ee
The effect of $\varepsilon_1$ is to change the magnitude
of $g_2(x)_{\rm WW}$, $\varepsilon_2$ varies the position of its zero.
The $x$-dependence of $\varepsilon_2$ preserves $\lim_{x\to1}g_2(x)= 0$; 
we use $\epsilon=0.05$ which yields $\varepsilon_2\approx 20\,\%$ up to 
the highest measured $x$-bin.
The good agreement of $g_2(x)_{\rm WW}$ with data is encouraging,
and in line with theory predictions \cite{Balla:1997hf}.
Our estimate with the splitted uncertainties 
$\varepsilon_{1,2}$ may overestimate in certain $x$-bins the 
$40\,\%$-``error band'' estimated in \cite{Accardi:2009au}. This however 
helps us to display a conservative estimate of possible uncertainties.

Presently $h_L^a(x)$ is unknown.
With phenomenological information on $h_1^a(x)$
\cite{Efremov:2006qm,Anselmino:2007fs,Anselmino:2008jk}, 
the WW approximation (\ref{Eq:WW-original2}) for $h_L^a(x)$ could 
be tested experimentally in Drell-Yan \cite{Koike:2008du}.

\subsection{Tests in lattice QCD}
\label{Sec-3.5:WW-lattice}

\blue{The lowest Mellin moments of the PDF $g_T^q(x)$ were studied in
lattice QCD in the quenched approximation \cite{Gockeler:2000ja} 
and with $N_f = 2$ flavors of light dynamical quarks \cite{Gockeler:2005vw}.
The obtained results were compatible with a small $\tilde{g}_T^q(x)$. 
We are not aware of lattice QCD studies related to the PDF $h_L^a(x)$,
and turn now our attention to TMD studies in lattice QCD.

After first exploratory investigations of TMDs on the lattice
\cite{Hagler:2009mb,Musch:2010ka}, recent years have witnessed considerable
progress and} improvements with regard to rigor, realism and methodology
\cite{Yoon:2016dyh,%Proceedings of Science LATTICE 2015 (2016) 116, 
Engelhardt:2015xja,%Phys.Rev. D93 (2016) no.5, 054501, 
Ji:2014hxa,%Phys.Rev. D91 (2015) 074009, 
Musch:2011er%Phys.Rev. D85 (2012) 094510
}.
However, numerical results from recent calculations are only available 
for a subset of observables, and the quantities calculated are not in a 
form that lends itself to straighforward tests of the WW-type relations 
as presented in this paper. Details about recent works and future 
perspectives are discussed at the end of this section.

For the time being, we content ourselves with rather crude comparisons 
based on the data published in Refs.~\cite{Hagler:2009mb,Musch:2010ka}. 
These early works explored all nucleon and quark polarizations, but 
they used a gauge link that does not incorporate the final or initial 
state interactions present in SIDIS or Drell-Yan experiments. In other 
words, the transverse momentum dependent quantities computed in
\cite{Hagler:2009mb,Musch:2010ka} are not precisely the TMDs measurable 
in experiment. More caveats will be discussed along the way.

Let us now translate the approximations
(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}) into expressions
for which we have a chance to compare them with available lattice data.
For that we multiply the
Eqs.~(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}) by $x^N$
with $N=0,\,1,\,2,\,\dots$ and integrate over $x\in[-1,1]$ which yields
\ba
        \int_{-1}^1 d x\;x^N
       g_{1T}^{\perp(1)q}(x)&\stackrel{\rm WW-type}{\approx}&
        \phantom{-} \,\frac{1}{N+2} \int_{-1}^1 d x \;x^{N+1}g_1^q(x)
        \;,
    \label{Eq:WW-approx-g1T-d}\\
        \int_{-1}^1 d x\;x^N
        h_{1L}^{\perp(1)q}(x)&\stackrel{\rm WW-type}{\approx}&
        -\,\frac{1}{N+3} \int_{-1}^1 d x\: x^{N+1}\,h_1^q(x)
        \;.
    \label{Eq:WW-approx-h1L-d}
\ea
with the understanding that
negative $x$ refer to antiquark distributions
$g_1^{\bar q}(x) = +\,g_1^{q}(-x)$,
$h_1^{\bar q}(x) = -\,h_1^{q}(-x)$,
$g_{1T}^{\perp(1)\bar q}(x) =- g_{1T}^{\perp(1)q}(-x)$,
$h_{1L}^{\perp(1)\bar q}(x) = +\,h_{1L}^{\perp(1)q}(-x)$
depending on $C$-parity of the involved operators \cite{Mulders:1995dh}.
The right hand sides of 
Eqs.~(\ref{Eq:WW-approx-g1T-d},~\ref{Eq:WW-approx-h1L-d}) are $x$-moments 
of parton distributions, and those can be obtained from lattice QCD using 
well-established methods based on operator product expansion. 
The left hand sides are moments of TMDs in $x$ and $\bfkperp$. We have to 
keep in mind that TMDs diverge for large $\bfkperp$. Therefore, without 
regularizing these divergences in a scheme suitable for the comparison of 
left and right hand side, a test of the above relations is meaningless, 
even before we get to address the issues of lattice calculations. Let us 
not give up at this point and take a look at the lattice observables of 
Ref.~\cite{Musch:2010ka}. Here, the TMDs are obtained from amplitudes 
$\tilde A_i(l^2,\ldots)$ in Fourier space, where $\bfkperp$ is encoded 
in the Fourier conjugate variable $\bflperp$, which is the transverse 
displacement of quark operators in the correlator evaluated on the lattice. 
In Fourier-space, the aforementioned divergent behavior for large $\bfkperp$ 
translates into strong lattice scale and scheme dependences at short distances
$\bflperp$ between the quark operators. The $\bfkperp$ integrals needed for 
the left hand sides of Eqs.~(\ref{Eq:WW-approx-g1T-d},~\ref{Eq:WW-approx-h1L-d})
correspond to the amplitudes at $\bflperp = 0$, where scheme and 
scale-dependence is greatest.  In Ref.~\cite{Musch:2010ka} Gaussian fits 
have been performed to the amplitudes \emph{excluding} data at short quark 
separations $\bflperp$. The Gaussians describe the long range data quite well 
and bridge the gap at short distances $\bflperp$. 
Taking the Gaussian fit at $\bflperp = 0$, we get a value which is 
(presumably) largely lattice scheme and scale independent. We have thus 
swept the problem of divergences under the rug. The Gaussian fit acts as 
a crude regularization of the divergences that appear in TMDs at large 
$\bfkperp$ and manifest themselves as short range artefacts on the lattice. 
Casting this line of thought into Mathematics, we get
\ba
    	\int_{-1}^1 d x\; g_{1T}^{\perp(1)q}(x) 
	= & \int_{-1}^1 d x\; \int  d^2 \bfkperp 
	\frac{\kperp^2}{2M^2} g_{1T}^{\perp q}(x,\kperp) 
	= -2 \tilde{A}_{7,q}( \ell = 0 ) 
	\stackrel{\text{Gaussian}}{=} -c_{7,q}\\
    	\int_{-1}^1 d x\; h_{1L}^{\perp(1)q}(x) 
	= & \int_{-1}^1 d x\; \int  d^2 \bfkperp 
	\frac{\kperp^2}{2M^2} h_{1T}^{\perp q}(x,\kperp) 
	= -2 \tilde{A}_{10,q}( \ell = 0 ) 
	\stackrel{\text{Gaussian}}{=} -c_{10,q}
\ea
We have thus expressed the left hand side of 
Eqs.~(\ref{Eq:WW-approx-g1T-d},~\ref{Eq:WW-approx-h1L-d}) in terms of 
amplitudes $c_{7,q}$ and $c_{10,q}$ of the Gaussian fits on the lattice.
Before quoting numbers, a few more comments are in order. The overall 
multiplicative renormalization had been fixed by setting the Gaussian 
integral $c_{2,u-d}$ of the unpolarized TMD $f_1$ in the isovector channel 
(u-d) to the nucleon quark content, namely, to 1. The validity the 
assumption that renormalization is mutliplicative and flavor-independent 
for the non-local lattice operators is under investigation 
\cite{Micheal-new}.
% [cite Michael Engelhardts upcoming paper, to be published]. 
The gauge link that goes into the evaluation of the quark-quark correlator 
introduces a power divergence that has to be subtracted. The subtraction 
scheme that was chosen on the lattice is not known to have a clear relation 
to a ``real world'' subtraction scheme designed for experimental TMDs and 
the corresponding gauge link geometry. The gauge link renormalization mainly 
influences the width of the Gaussian fits; the amplitudes are only slightly 
affected, so it may not play a big role for our discussion. Altogether, the 
significance of our numerical ``tests'' of WW-relations should be taken 
with a grain of salt.

For the test of Eq.~(\ref{Eq:WW-approx-g1T-d}), we use the numbers 
$\int d x\;g_{1T}^{\perp(1)u}(x)\stackrel{\text{Gaussian}}{=}-c_{7,u}= 0.1041(85)$ 
and
$\int d x\;g_{1T}^{\perp(1)d}(x)\stackrel{\text{Gaussian}}{=}-c_{10,d}=-0.0232(42)$
from \cite{Musch:2010ka}. %[Phys.Rev. D83 (2011) 094507]:
Lattice data for
$\int d x \,x^{N}g_1^q(x)$
\cite{Hagler:2003is,Hagler:2007xi} and
$\int d x \,x^{N}h_1^q(x)$
\cite{Gockeler:2005cj} are available for $N=0,\,1,\,2,\,3$ .
These values have been computed using (quasi-) local operators which 
have been renormalized to the $\overline{MS}$ scheme at the scale 
$\mu^2 = 4\,\text{GeV}^2$.
According to \cite{Hagler:2007xi} (data set 4:
% lattice spacing $a$ and current quark masses $m_{u,d}$ such that
with $am_{u,d} = 0.020$ with $m_\pi\approx 500\,{\rm MeV}$)
one has $\int d x \;x\,g_1^{u-d}(x)= 0.257(10)$ and
$\int d x \;x\,g_1^{u+d}(x)= 0.159(14)$.
Decomposing the results from  \cite{Hagler:2007xi} into
individual flavors, and inserting them into
Eq.~(\ref{Eq:WW-approx-g1T-d}) we obtain
\ba
        \underbrace{\int d x\;g_{1T}^{\perp(1)u}(x)}
        _{= 0.1041(85) \;\mbox{\footnotesize Ref.~\cite{Musch:2010ka}}}
        &\stackrel{!}{\approx}
        \underbrace{\frac{1}{2}\int d x\;x\,g_1^u(x)}
        _{= 0.104(9) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
        \hspace{3mm} , \nonumber \\
        \underbrace{\int d x\;g_{1T}^{\perp(1)d}(x)}
        _{= -0.0232(42) \;\mbox{\footnotesize Ref.~\cite{Musch:2010ka}}}
        &\stackrel{!}{\approx}
        \underbrace{\frac{1}{2}\int d x\;x\,g_1^u(x)}
        _{= -0.025(9) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
        \hspace{3mm}, 
        \label{Eq:test-WW-type-lattice-g1T}
\ea
which confirms the approximation (\ref{Eq:WW-approx-g1T-d}) for $N=0$
within the statistical uncertainties of the lattice calculations.
%
In order to test (\ref{Eq:WW-approx-h1L-d}) we use
$\int d x\;h_{1L}^{\perp(1)u}(x) = -0.0931(73)$ and
$\int d x\;h_{1L}^{\perp(1)d}(x) = 0.0130(40)$ from \cite{Hagler:2009mb}
and the lattice data 
$\int d x \;x\,h_1^u(x)= 0.28(1)$ and
$\int d x \;x\,h_1^d(x)= -0.054(4)$
from QCDSF \cite{Gockeler:2005cj}.\footnote{
  These numbers are read off from a figure in \cite{Gockeler:2005cj},
  and were computed on a different lattice. We interpolate them to a
  common value of the pion mass $m_\pi\approx500\,{\rm MeV}$, and
  estimate the error conservatively in order to take systematic effects
  into account due to the use of a different lattice.}
Inserting these numbers into  (\ref{Eq:WW-approx-h1L-d}) for the case
$N=0$ we obtain
\ba
        \underbrace{\int d x\;h_{1L}^{\perp(1)u}(x)}
        _{= -0.0931(73)\;\mbox{\footnotesize Ref.~\cite{Hagler:2009mb}}}
        \stackrel{!}{\approx}
        \underbrace{-\,\frac{1}{3}\int d x\;x\,g_1^u(x)}
        _{= -0.093(3) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
        \hspace{3mm} , \hspace{7mm} \nonumber \\
        \underbrace{\int d x\;h_{1L}^{\perp(1)d}(x)}
        _{= 0.0130(40) \;\mbox{\footnotesize Ref.~\cite{Hagler:2009mb}}}
        \stackrel{!}{\approx}
        \underbrace{-\,\frac{1}{3}\int d x\;x\,h_1^u(x)}
        _{= 0.018(1) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
        \hspace{3mm}. 
        \label{Eq:test-WW-type-lattice-h1L}
\ea
which again confirms the WW-type approximation within the statistical
uncertainties of the lattice calculations.

Several more comments are in order concerning the, at first glance, remarkably
good confirmation of the  WW-type approximations by lattice data in
Eqs.~(\ref{Eq:test-WW-type-lattice-g1T},~\ref{Eq:test-WW-type-lattice-h1L}).

First, the relations refer to lattice parameters corresponding
to pion masses of $500\,{\rm MeV}$. We do not
need to worry about that too much. The lattice results do provide
a valid test of the approximations in a ``hadronic world'' with
somewhat heavier pions and nucleons. All that matters in our
context is that the relative size of $\bar qgq$-matrix elements
is small with respect to $\bar qq$-matrix elements.
% (Other lattice artifacts, such as finite lattice spacing and
% finite volume effects could potentially play a role, but in the
% context of TMDs such effects are presently beyond systematic control,
% and we assume the associated uncertainties to be not larger than
% the statistical error bars of the lattice data.)

Second, we have to revisit carefully which approximations the above
lattice calculations actually test. As mentioned above, in
the lattice study \cite{Hagler:2007xi} a specific choice for
the path of the gauge link was chosen, which is actually different
from the paths required in SIDIS or DY. With the path choice of
\cite{Hagler:2007xi} there are effectively only (T-even)
$A_i$ amplitudes, the $B_i$ amplitudes are absent.
Therefore, see \cite{Metz:2008ib,Teckentrup:2009tk} and
Sec.~\ref{Sec-3.6:models},
the test (\ref{Eq:test-WW-type-lattice-g1T}) of the WW-type
approximation (\ref{Eq:WW-approx-g1T-d}) actually constitutes a test
of the WW-approximation (\ref{Eq:WW-original1}) and confirms
earlier lattice work \cite{Gockeler:2000ja,Gockeler:2005vw}.
Similarly, the test (\ref{Eq:test-WW-type-lattice-h1L}) of the
WW-type approximation (\ref{Eq:WW-approx-h1L-d}) actually constitutes
a test of the WW-approximation (\ref{Eq:WW-original2}). The latter
however has not been reported previously in literature, and is a
new result.

Third, to be precise:
(\ref{Eq:test-WW-type-lattice-g1T},~\ref{Eq:test-WW-type-lattice-h1L})
test the first Mellin moments of the WW approximations
(\ref{Eq:WW-original1},~\ref{Eq:WW-original2}), which corresponds to the
Burkardt-Cottingham sum rule for $g_T^a(x)$ and an analog sum rule for
$h_L^a(x)$, see \cite{Jaffe:1996zw} and references there in.
In view of the long debate on the validity of those sum rules
\cite{Burkardt:2001iy,Bass:2003vp,Efremov:2002qh}, this is in
an interesting result in itself.

It is important to stress that in view of the pioneering and
exploratory status of the TMD lattice calculations
\cite{Hagler:2007xi}, this is already a remarkable and very
interesting result. Thus, apart from the instanton calculus
\cite{Dressler:1999hc} also lattice data provide support for
the validity of the WW approximation (\ref{Eq:WW-original2}).
At the same time, however, we also have to admit that we do
not really reach our goal of testing the WW-type approximations
on the lattice. With the presently available lattice data
this is not yet possible. Future lattice data on higher
Mellin moments will provide further insights.
Meanwhile we may try to gain insights into the quality of
WW-type approximations from experiment.

\subsection{Tests in models}
\label{Sec-3.6:models}

Effective approaches and models such as bag 
\cite{Jaffe:1991ra,Stratmann:1993aw,Signal:1996ct,Avakian:2010br},
spectator \cite{Jakob:1997wg}, chiral quark-soliton 
\cite{Wakamatsu:2000ex}, or light-cone 
constituent \cite{Pasquini:2008ax,Lorce:2011dv} models
support the approximations (\ref{Eq:WW-original1},~\ref{Eq:WW-original2}) 
for PDFs within an accuracy of $(10-30)\,\%$ at low hadronic scale 
below $1\,{\rm GeV}$.

Turning to TMDs, we recall that in models without gluon 
degrees of freedom certain relations among TMDs hold, the 
so-called quark model Lorentz-invariance relations (qLIRs).
%\cite{Metz:2008ib,Teckentrup:2009tk}. 
Initially thought to be exact \cite{Tangerman:1994bb,Mulders:1995dh}
qLIRs were shown in models with gluons \cite{Kundu:2001pk,Schlegel:2004rg} 
and in QCD \cite{Goeke:2003az} to be invalid.
They originate from decomposing the (completely unintegrated)
quark correlator in terms of Lorentz-invariant amplitudes, and 
TMDs are certain integrals over those amplitudes.
When gluons are absent, the correlator consists
of 12 amplitudes \cite{Tangerman:1994bb,Mulders:1995dh}, i.e.\ fewer 
amplitudes than TMDs which implies relations, qLIRs. 
In QCD the correct Lorentz decomposition requires the consideration of 
gauge links. This generates further amplitudes. As a result one has 
as many amplitudes as TMDs and no relations exist \cite{Goeke:2003az}. 
However, qLIRs ``hold'' in QCD in the WW-type approximation 
\cite{Metz:2008ib}. In models without gluon degrees of freedom 
they are exact
\cite{Metz:2008ib,Teckentrup:2009tk,Avakian:2010br,Jakob:1997wg}.

The bag, spectator and light-cone constituent quark models support 
the approximations (\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}) 
within an accuracy of $(10-30)\,\%$ 
\cite{Avakian:2010br,Jakob:1997wg,Lorce:2011dv,Pasquini:2008ax}.
The spectator and bag model support WW-type approximations 
within $(10-30)\,\%$ \cite{Avakian:2010br}. 
As they are defined in terms of quark bilinear expressions 
(\ref{Eq:correlator}) it is possible to evaluate twist-3 functions
in quark models \cite{Jaffe:1991ra}. The tilde-terms arise due to
the different model interactions, and it is important to discuss
critically how realistically they describe the $\bar{q}gq$-terms
of QCD \cite{Lorce:2014hxa,Lorce:2016ugb}.

In the covariant parton model with intrinsic 3D-symmetric parton 
orbital motion \cite{Zavada:1996kp}  quarks are free, $\bar qgq$ 
correlations absent, and all WW and WW-type relations exact
\cite{Efremov:2010mt,Efremov:2009ze}.
The phenomenological success of this approach \cite{Zavada:1996kp} may 
hint at a general smallness of $\bar qgq$ terms, although many of the 
predictions from this model have yet to be tested \cite{Efremov:2010mt}.

Let us finally discuss quark-target models, 
where gluon degrees of freedom are included and WW(-type)
approximations badly violated
\cite{Kundu:2001pk,Schlegel:2004rg,Meissner:2007rx,Mukherjee:2009uy}.
This is natural in this class of models for two
reasons. First, quark-mass terms are of ${\cal O}(m_q/M_N)$ 
and negligible in the nucleon case, but of ${\cal O}(100\,\%)$
in a quark target where $m_q$ plays also the role of $M_N$. 
Second, even if one refrains from mass terms the approximations are 
spoiled by gluon radiation, see for instance \cite{Harindranath:1997qn} 
in the context of (\ref{Eq:WW-original1}).
This means that perturbative QCD does not support the WW-approximation:
they are certainly not preserved by evolution. However, scaling violations
{\it per se} do not need to be large. What is crucial in this context are 
dynamical reasons for the smallness of the {\sl matrix elements} of
$\bar qgq$-operators. This requires the consideration of chiral symmetry 
breaking effects reflected in the hadronic spectrum, as considered in the
instanton vacuum model \cite{Balla:1997hf,Dressler:1999hc} but 
out of scope in quark-target models.

We are not aware of systematic tests of WW-type approximations for FFs. One 
information worth mentioning in this context is that in spectator models 
\cite{Jakob:1997wg} tilde-contributions to FFs are proportional to the 
offshellness of partons % in complete analogy to the case of TMDs 
\cite{Lorce:2014hxa,Lorce:2016ugb}. This
natural feature may indicate that in the region dominated by effects of
small $P_T$ tilde-terms might be small. On the other hand, quarks have 
sizable constituent masses of the order of few hundred MeV in spectator models 
and the mass-terms are not small. 
The applicability of WW-type approximations to FFs 
remains the least tested point in our approach.

\subsection{Basis functions \& limitations of WW-type approximations}
\label{Sec-3.7:basis+limitations}

The leading-twist 6 TMDs 
$f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a}$
and 2 FFs $D_1^a, \; H_1^{\perp a}$ provide a basis.
Below we shall see that, under the assumption of the validity of WW-type 
approximations, it is possible to express all SIDIS structure
in terms of the basis functions. 
Notice that SIDIS alone is of course not sufficient to determine the basis
functions uniquely: the 8 basis functions appear in 6 SIDIS structure functions.
It is crucial to take advantage of other processes: Drell-Yan for PDFs and TMDs
and hadron production in $e^+e^-$ annihilation for FFs, though other processes 
play also important roles.

The basis functions allow us to describe in WW-type approximation all other 
TMDs, and experiments will decide how well the approximations work.
In two instances, however, we know in advance of limitations, namely in the
description of T-odd TMDs which appear in the decomposition of the 
correlator (\ref{Eq:correlator}) with no prefactor of $\kperp$.
There are three cases: $f_T^a(x,k_\perp)$, $h^a(x,\kperp)$, $e_L^a(x,\kperp)$.
Such TMDs in principle survive integration of the correlator over $\kperp$
and would have PDF counterparts if there were not the sum rules in 
Eq.~(\ref{Eq:sum-rules-T-odd}). These sum rules arise because hypothetical
PDF versions of T-odd TMDs vanish: they have a simple straight gauge link
along the lightcone, and such objects vanish due to parity and time-reversal 
symmetry of strong interactions. This argument does not apply to other T-odd 
TMDs because they drop out from the $\kperp$-integrate correlator due to 
explicit factors of e.g.\ $\kperp^j$ in the case of the Sivers function.

Let us first discuss the case of $f_T^a(x,k_\perp)$. Taking the  
WW-type approximation (\ref{Eq:WW-type-fT}) literally, implies
$x\int d^2 k_\perp\,f_T^a(x,k_\perp)=-f_{1T}^{\perp(1)a}(x) \neq 0$ 
at variance with the sum rule (\ref{Eq:sum-rules-T-odd}). We 
have $xf_T^a(x,k_\perp)=x\tilde{f}_T^a(x,k_\perp)-f_{1T}^{\perp(1)a}(x,k_\perp)$ 
from QCD equations of motion \cite{Bacchetta:2006tn} which yields
(\ref{Eq:WW-type-fT}). The point is of course 
that in this case it is essential to keep the tilde-function. 
The situation for the chirally and T-odd twist-3 
TMD $h^a(x,k_\perp)$ is completely analog. The third function in
(\ref{Eq:sum-rules-T-odd}) is $e_L^a(x,k_\perp)$ and causes no issues
since $e_L^a(x,k_\perp)=\tilde{e}_L^a(x,k_\perp)\approx0$ in WW-type approximation.

Does this mean WW-type approximations fail for $f_T^a(x,k_\perp)$ 
and $h^a(x,k_\perp)$? Not necessarily. One has to keep in mind
the formal character of the sum rules (\ref{Eq:sum-rules-T-odd})
which include integration in the large-$k_\perp$ region where the TMD 
description does not apply. Thus, issues with the sum rules 
(\ref{Eq:sum-rules-T-odd}) do not need to exclude the
possibility that the WW-type approximations for $f_T^a(x,k_\perp)$ and
$h^a(x,k_\perp)$ in (\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-last}) 
may work at small $k_\perp$ where we use them in our TMD approach.
This would mean the UV region is essential to realize the sum rules 
(\ref{Eq:sum-rules-T-odd}). Alternatively, one could also envision 
the sum rules (\ref{Eq:sum-rules-T-odd}) to be sensitive to the
IR region through gluonic or fermionic pole contributions manifest
in tilde-terms.

At the present stage too little is known in the theory of subleading
twist TMDs. Below in Sec.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi} 
we will discuss how one could deal with the TMDs $f_T^a(x,k_\perp)$ and 
$h^a(x,k_\perp)$ phenomenologically. For now let us keep in mind that 
one has to keep a vigilant eye on all WW-type approximations, and 
especially on those for $f_T^a(x,k_\perp)$ and $h^a(x,k_\perp)$.

\newpage
%======= SECTION 4: SIDIS IN WW APPROXIMATION ========================
\section{SIDIS in WW-type approximation}
\label{Sec-4:SIDIS-in-WW-approximation}

In this section we consequently apply the WW- and WW-type approximation
to SIDIS.

\subsection{Leading structure functions amenable to WW-type approximations}
\label{Sec-4.1:WW-twist-2}

The WW- and WW-type approximations are useful for the following
two leading-twist structure functions 
\begin{subequations}\ba
 F_{LT}^{\cos(\phi_h -\phi_S)}
	&\stackrel{\rm WW}{=}& 
	{\cal C}\biggl[\omega^{\{1\}}_{\rm B}\, {g_{1T}^\perp}D_1 \biggr]
        \with{ }{g_{1T}^{\perp a}\to g_1^a}{Eq.~(\ref{Eq:WW-approx-g1T})}
        \label{F_LTcos(phi-phiS)-WW} \\
 F_{UL}^{\sin 2\phi_h} 	
        &\stackrel{\rm WW}{=}& 
	{\cal C}\biggl[\omega^{\{2\}}_{\rm AB}\,
    	{h_{1L}^{\perp }} H_{1}^{\perp }\biggr]  
        \with{ }{h_{1L}^{\perp a}\to h_1^a}{Eq.~(\ref{Eq:WW-approx-h1L})} 
        \label{F_UUsin2phi-WW}
\ea\end{subequations}

\subsection{Subleading structure functions in WW-type approximations}
\label{Sec-4.2:WW-twist-3}

In the case of the subleading twist structure functions the WW-type 
approximations in Eqs.~(\ref{Eq:WW-type-1}--\ref{Eq:WW-type-last})
lead to considerable simplifications. We obtain the approximations
\begin{subequations}\ba
F_{LU}^{\sin\phi_h} &\stackrel{\rm WW}{=}& 0\,, \phantom{\frac11}
	\label{Eq:WW-type-FLUsinphi}\\
F_{LT}^{\cos \phi_S}&\stackrel{\rm WW}{=}& \frac{2M}{Q}\,
	{\cal C}\biggl[-  \omega^{\{0\}}\, x\,g_T D_1 \biggr]
        \with{ }
	{g_T^a\to g_1^a}
	{Eq.~(\ref{Eq:WW-original1}),}\\
F_{LL}^{\cos \phi_h} &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,{\cal C}\biggl[ 
   	-\omega^{\{1\}}_{\rm B}\,
   	xg_L^{\perp} D_1 \biggr]
        \with{ }
	{g_L^{\perp a}\to g_1^a}
	{Eq.~(\ref{Eq:WW-type-gLperp}),}\\
F_{LT}^{\cos(2\phi_h - \phi_S)} &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,{\cal C}\biggl[
   	- \omega^{\{2\}}_{\rm C}\,
   	x g_T^{\perp } D_1 \biggr]
        \with{ }
	{g_T^{\perp a}\to g_1^a}
	{Eqs.~(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T}),}\\
F_{UL}^{\sin\phi_h} &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,{\cal C}\biggl[
   	\phantom{-}\omega^{\{1\}}_{\rm A}\,
    	x\,h_L  H_1^{\perp } \biggr]
        \with{ }
	{h_L^a\to h_{1L}^{\perp a}}
	{with Eq.~(\ref{Eq:WW-type-6}),}
	\label{Eq:WW-type-FULsinphi}\\
F_{UU}^{\cos\phi_h} &\stackrel{\rm WW}{=}&\frac{2M}{Q}\,{\cal C}\biggl[\phantom{-}
	 \omega^{\{1\}}_{\rm A}\,x\,h\,H_{1}^{\perp } 
   	-\omega^{\{1\}}_{\rm B}\,x\,f^\perp D_1\biggr]
        \with{ }
	{f^{\perp a}\to f_1^a, \; h^a\to h_1^{\perp a}}
	{with Eqs.~(\ref{Eq:WW-type-Cahn},~\ref{Eq:WW-type-last}),}
	\label{Eq:WW-type-FUUcosphi}\\
F_{UT}^{\sin \phi_S } &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,
	{\cal C}\biggl[ \phantom{-}\omega^{\{0\}} \, x\,f_TD_1
	-\frac{\omega^{\{2\}}_{\rm B}}{2}\,(xh_T-xh_T^\perp)\,H_{1}^{\perp } \biggr]
        \with
	{f_T^a \to f_{1T}^{\perp a},}
	{h_T^a-h_T^{\perp a}\to h_1^a}
	{(\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}),}\\
F_{UT}^{\sin(2\phi_h -\phi_S)} &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,{\cal C}\biggl[
   	\;\omega^{\{2\}}_{\rm C}\,
   	{  x\,f_T^\perp}D_1
        + \frac{\omega^{\{2\}}_{\rm AB}}{2} 
	{x(h_T+h_T^\perp)}H_1^\perp \biggr]
        \with
	{f_T^{\perp a}\to f_{1T}^{\perp a},}
	{(h_T^a+h_T^{\perp a})\to h_{1T}^{\perp a}}{with 
	(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}).}
	\;\;\;\;
\ea\end{subequations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.4\textwidth]{\FigPath/f1} 
\includegraphics[width=0.4\textwidth]{\FigPath/f1Tperp}

\includegraphics[width=0.4\textwidth]{\FigPath/g1}  
\includegraphics[width=0.4\textwidth]{\FigPath/h1perpBM}

\includegraphics[width=0.4\textwidth]{\FigPath/h1}  
\includegraphics[width=0.4\textwidth]{\FigPath/h1Tperp}

\includegraphics[width=0.4\textwidth]{\FigPath/D1} 
\includegraphics[width=0.4\textwidth]{\FigPath/H1perp} 
\caption{\label{basis} 
	The basis functions $f_1^a, \; g_1^a, \; h_1^a, 
	f_{1T}^{\perp a}, \;h_1^{\perp a},\; h_{1T}^{\perp a}; \; 
	D_1^a, \; H_1^{\perp a} \,$. For details see App.~\ref{App:basis}.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Phenomenological information on basis functions}
\label{Sec-4.3:plot-basis-functions}

We have seen that the following 6 TMDs and 2 FFs provide a basis 
(Sec.~\ref{Sec-3:WW}) and allow us to express all SIDIS structure 
functions (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation})  
in WW-type approximation: 
\be\label{Eq:basis}
   \mbox{basis: \ \ } 
   f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a};
   \; D_1^a, \; H_1^{\perp a} \, .
\ee
Phenomenological information is available for all basis functions at 
least to some extent. 
In Fig.~\ref{basis} we present plots of the basis functions, and refer
to App.~\ref{App:basis} for details.
The four functions $f_1^a, \; g_1^a, \; h_1^a,\; D_1^a$  
are related to twist-2 collinear functions. All collinear functions are calculated at $Q^2 = 2.4$ (GeV$^2$). Collinear $f_1(x)$ are from Ref.~\cite{Martin:2009iq},  $g_1(x)$ are from Ref.~\cite{Gluck:1998xa}, and $D_1(z)$ are from Ref. ~\cite{deFlorian:2007aj}.The other four 
$f_{1T}^{\perp a},  \;h_1^{\perp a},\; H_1^{\perp a} \,$  
have no collinear counterparts, and we consider their (1)-moments, while 
for $ h_{1T}^{\perp a}$  we consider the (2)-moment, see App.~\ref{App:basis} for details.

%======= SECTION 5: TWIST-2 AND BASIS FUNCTIONS ======================
\section{Leading twist asymmetries and basis functions}
\label{Sec-5:twist-2+basis}
In this section we review how the basis functions describe available
SIDIS data. This is of importance to asses the reliability of the
predictions presented in the next sections.

\subsection{\boldmath Gauss Ansatz and $F_{UU}$ structure function}
\label{Sec-5.1:FUU-basis}

Throughout this work we use the so-called Gauss Ansatz for the
transverse momentum dependent distribution and fragmentation functions. 
This Ansatz is popular not only because it considerably simplifies the
calculations. In fact, all convolution integrals of the type 
(\ref{Eq:def-convolution-integral}) can be solved analytically with 
this Ansatz.
Far more important is the fact that it works phenomenologically
with a good accuracy in many practical applications
\cite{Anselmino:2005nn,Collins:2005ie,D'Alesio:2007jt,Schweitzer:2010tt,
Signori:2013mda,Anselmino:2013lza}.
It should be kept in mind that the Gauss Ansatz can, of course, 
be only a rough approximation. For instance, it is not 
consistent with general matching expectations when $\kperp$ 
becomes large \cite{Bacchetta:2008xw}. Nevertheless, if
one limits oneself to work in a region where the transverse
momenta (of hadrons produced in SIDIS,  dileptons produced
in the Drell-Yan process, etc) are small with respect to the hard
scale in the process, then the Ansatz works quantitatively
very well. The most recent and detailed tests were reported in 
\cite{Schweitzer:2010tt}, where the Gauss Ansatz was shown to
describe the most recent SIDIS data. No deviations could
be observed within the error bars of the data provided one
takes into account the broadening of the Gaussian widths
with increasing energy \cite{Schweitzer:2010tt} according
with expectations from QCD \cite{Aybat:2011zv}.
Remarkably, the Gauss Ansatz is approximately compatible with 
the $\kperp$-shapes obtained from evolution \cite{Aybat:2011zv}
or fits to high-energy Tevatron data on weak-boson production
\cite{Landry:2002ix}. On the other end, effective models at 
low \cite{Pasquini:2008ax,Avakian:2010br} and intermediate 
\cite{Efremov:2009ze} energies also support it approximately.

The Gaussian Ansatz for the unpolarized TMD and unpolarized FF 
is given by
\be\label{Eq:Gauss-f1-D1}
    f^a_1(x,\kperp^2) = f^a_1(x)\;
    \frac{e^{-\kperp^2/\avkperp_{f_1}}}{\pi\avkperp_{f_1}} \;,\;\;\;
    D^a_1(z,\pperp^2) = D_1^a(z)\,
    \frac{e^{-\pperp^2/\avpperp_{D_1}}}{\pi\avpperp_{D_1}}\;.
\ee
The parameters $\avkperp_{f_1}$ and $\avpperp_{D_1}$ can
be assumed to be flavor- and $x$- or $z$-dependent, as present
data do not allow us to constrain too many parameters, see
App.~\ref{App:basis-f1-D1} for a review. This assumption can be
relaxed, e.g. theoretical studies in chiral effective field theories 
predict a strong flavor-dependence in the $\kperp$-behavior
of sea and valence quark TMDs \cite{Schweitzer:2012hh}.

The structure function $F_{UU}$ needed for our analysis reads
\begin{subequations}\ba
	F_{UU}(x,z,\Phperp) 
	&=& x \sum_q e_q^2\,f^q_1(x)\,D_1^q(z)\,{\cal G}(\Phperp)\,, 
	\label{Eq:FUU-Phperp}\\
	F_{UU}(x,z) \equiv \int d^2 \Phperp \, F_{UU}(x,z,\Phperp) 
	&=& x \sum_q e_q^2\,f^q_1(x)\,D_1^q(z)  \, ,
	\label{Eq:FUU}
\ea\end{subequations}
where we introduce the notation ${\cal G}(\Phperp)$, which is defined as
\be\label{Eq:def-Gaussian-lambda}
	{\cal G}(\Phperp) = \frac{\exp(-\Phperp^2/\lambda)}{\pi\,\lambda}
	\, , \;\;\; 
	\lambda = z^2\,\la\kperp^2\ra_{f_1} + \la\pperp^2\ra_{D_1} \,,
\ee
with the understanding that the convenient abbreviation $\lambda$ is expressed 
in terms of the Gaussian widths of the {\it preceding} TMD and FF. Notice 
that ${\cal G}(\Phperp)\equiv {\cal G}(x,z,\Phperp)$ and that in general
${\cal G}(\Phperp)$ appears under the flavor sum due to a possible 
flavor-dependence of the involved Gaussian widths.
The normalization $\int d^2\Phperp \,{\cal G}(\Phperp)=1$ 
correctly connects the structure function $F_{UU}(x,z,\Phperp)$ 
in (\ref{Eq:FUU-Phperp}) with its $\Phperp$-integrated counterpart
(\ref{Eq:FUU}). In our effective description this is step is trivial. In 
QCD the connection of TMDs to PDFs is far more subtle \cite{Collins:2016hqq}.
Fig.~\ref{FUU-show-pT-dependence} illustrates how the Gauss Ansatz
describes selected SIDIS data. In Fig.~\ref{FUU-show-pT-dependence} (b) we plot HERMES multiplicity \cite{Airapetian:2012ki}
\be
M_n^h(x,z,\Phperp)  \equiv 2 \pi \Phperp \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
\ee
at $\la Q^2\ra=2.87\,{\rm GeV}^2$,
$\la x\ra  =0.15$, $\la z\ra  =0.22$ for $\pi^+$ production on the proton target.

To streamline the presentation we refer to the comprehensive Appendix 
on the used parametrizations (App.~\ref{App:basis}), and for 
technical details on the Gauss Ansatz (App.~\ref{App:factor}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t!]
\centering
\includegraphics[width=0.3\textwidth]{\FigPath/Fig02a-JLab-ratio-pT-v5.pdf}  (a)
\includegraphics[width=0.37\textwidth]{\FigPath/hermes_pip.pdf} (b)
\caption{\label{FUU-show-pT-dependence}
Examples of the description of transverse momenta of hadrons in 
unpolarized SIDIS. 
(a) Differential cross section at $\la Q^2\ra=2.37\,{\rm GeV}^2$,
$\la x\ra  =0.24$, $\la z\ra  =0.30$ measured at JLab with a 5.75 GeV 
beam \cite{Osipenko:2008aa}. Theoretical curve from Gauss model 
following Ref.~\cite{Schweitzer:2010tt}.
(b) Example for HERMES multiplicities at $\la Q^2\ra=2.87\,{\rm GeV}^2$,
$\la x\ra  =0.15$, $\la z\ra  =0.22$.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newpage
%========= SECTION 6: TESTING APPROACH WITH A_LL =====================
\subsection{\boldmath Leading twist $A_{LL}$: 
           first test of intrinsic $\kperp$ beyond unpolarized case}
\label{Sec-5.2:FLL-basis}

In this Section we discuss the leading twist double spin asymmetry 
$A_{LL} \propto g_{1}^a D_1^a$ which does not require a WW-type approximation
but is important for two reasons. First, we review one of our 
``basis functions'' $g_1^a(x)$, and similarly we will review below 
also other ``basis functions.'' Second, throughout this work we use the 
Gaussian Ansatz demonstrated to provide good services in unpolarized case 
\cite{Anselmino:2005nn,Collins:2005ie,D'Alesio:2007jt,Schweitzer:2010tt,
Signori:2013mda,Anselmino:2013lza}. However, nothing is known about
the applicability of the Gaussian Ansatz in polarized case.
The JLab data \cite{Avakian:2010ae} on $A_{LL}(\Phperp)$ put us 
in the position to conduct a first ``test'' of our understanding of 
the $\kperp$-behavior of polarized partons. To have an ``informed idea''
about the Gaussian width of $g_{1}(x,\kperp)$ we will explore information
from the exploratory lattice QCD study of TMDs \cite{Hagler:2009mb}.

We assume Gaussian form for $g_{1}^{a}(x,\kperp^2)$
\ba\label{eq:g1}
	g_{1}^{a}(x,\kperp^2) = g_{1}^{a}(x)\,
	\frac{e^{-\kperp^2/{\avkperp_{g_{1}}}}}{\pi \avkperp_{g_{1}}}\,\; ,
\ea
and resort to the lattice QCD results \cite{Hagler:2009mb} to gain 
an estimate on width $\avkperp_{g_{1}}$, see App.~\ref{App:basis-g1}.

With $\lambda=z^2\la\kperp^2\ra_{g_1}+\la\pperp^2\ra_{D_1}$ implicit in 
${\cal G}(\Phperp)$, the structure function $F_{LL}$  reads
\begin{subequations}\ba
	F_{LL}(x,z,\Phperp) 
	&=& x \sum_q e_q^2\,g^q_1(x)\,D_1^q(z)\,{\cal G}(\Phperp)\,, 
	\label{Eq:FLL-Phperp}\\
	F_{LL}(x,z)  
	&=& x \sum_q e_q^2\,g^q_1(x)\,D_1^q(z)  \, ,
	\label{Eq:FLL}
\ea\end{subequations}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering 
\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pip}  
\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pi0}  
\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pim}  
\caption{\label{jlab_ALL} 
	$p_2 A_{LL}$ asymmetry compared with Jefferson Lab experimental 
	results Ref.~\cite{Avakian:2010ae} for $\pi^+$ (left panel) and 
	$\pi^-$ (right panel). Solid lines are computations with mean 
	values of kinematic variables  $\langle x \rangle = 0.25$, 
	$\langle z \rangle = 0.5$, $\langle Q^2 \rangle = 1.7$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The first experimental results on the 
$\Phperp$-dependence of $A_{LL} = F_{LL}/F_{UU}$ were presented by
Jefferson Lab \cite{Avakian:2010ae}. The definition of the asymmetry 
in  \cite{Avakian:2010ae} was
\be\label{Eq:ALLy}
	A_{LL,\la y\ra}(x,z,\Phperp) 
	= \la p_2 \,A_{LL}(x,z,\Phperp) \ra \, 
	= \frac{\la y (2-y) \; F_{LL}(x,z,\Phperp)\ra}
	{\la(1+(1-y)^2) \; F_{UU}(x,z,\Phperp)\ra} 
\ee 
where $p_2 = y (2-y)/(1+(1-y)^2)$ and averaging (separately in numerator 
and denominator) over the kinematics of \cite{Avakian:2010ae} is implied. 
We  compare our results for $A_{LL,\la y\ra}(\Phperp)$ to Jefferson Lab data 
\cite{Avakian:2010ae} in Fig.~\ref{jlab_ALL}.

In our approach we use lattice results from \cite{Hagler:2009mb} to
constrain the Gaussian width $\la\kperp^2\ra_{g_1}$, see App.~\ref{App:basis-g1}.
All other ingredients in (\ref{Eq:ALLy}) are known and 
tested through other observables, see Sec.~\ref{Sec-5.1:FUU-basis}.
Therefore Fig.~\ref{jlab_ALL} provides several important tests.
First, the Jefferson Lab data \cite{Avakian:2010ae} is compatible
with the Gauss Ansatz within error bars. Second, the lattice QCD results 
in the way we use them in App.~\ref{App:basis-g1} give an appropriate 
description of these data.\footnote{
	Another important test was already presented in 
	\cite{Avakian:2010ae}: the $\Phperp$-integrated (``collinear'')
	asymmetry (\ref{Eq:FLL}) is compatible with data
	from other experiments and with theoretical results obtained from
	parametrizations of $f_1^a(x)$, $g_1^a(x)$, $D_1^a(z)$. This 
	shows that even at the moderate beam energies of the pre-12GeV era 
	one was indeed already probing DIS at Jefferson Lab,
	at least to a very good approximation \cite{Avakian:2010ae}.}

Encouraged by these findings we will use lattice predictions from 
Ref.~\cite{Hagler:2009mb} below also for the Gaussian widths of 
$g_{1T}^{\perp(1)a}$ and $h_{1L}^{\perp(1)a}$.
Of course, at this point one could argue that the WW- and WW-type 
approximations (\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-g1T}) also
dictate that $g_{1T}^\perp$ and $h_{1L}^\perp$ have the same Gaussian
widths as $g_1$ and $h_1$. In fact, the lattice results for the 
respective widths are numerically similar, which can be interpreted as 
yet another argument in favor of the usefulness of the approximations. 
The practical predictions depend only weakly on the choice of parameters.

\newpage
\subsection{\boldmath Leading twist $A_{UT}^{\sin(\phi_h-\phi_S)}$ Sivers asymmetry}
\label{Sec-5.3:Sivers-basis}

The structure function $F_{UT}^{\sin(\phi_h-\phi_S)}$ reads
\begin{subequations}\ba
	F_{UT}^{\sin(\phi_h-\phi_S)}(x,z,\Phperp) 
	&=& - x\sum_q e_q^2\,f_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \, , \label{FUTsiv-Gauss-Phperp}\\ 
	F_{UT}^{\sin(\phi_h-\phi_S)}(x,z,\la\Phperp\ra) 
	&=& - x\sum_q e_q^2\,f_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\;
	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,,\label{FUTsiv-Gauss}
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{f_{1T}^\perp} + \avpperp_{D_1}$ and
$b^{(1)}_{\rm B}=2M_N$ and $c^{(1)}_{\rm B} = \sqrt{\pi}\,M_N$, 
see App.~\ref{App:convol-details} for details.

Notice that integrating structure functions over $\Phperp$
is different from integrating the cross section over $\Phperp$
where azimuthal hadron modulations drop out. 
Only if the relevant weight is $\omega^{\{0\}}$ we obtain
``collinear structure functions:''  $F_{UU}(x,z)$, $F_{LL}(x,z)$ 
in Secs.~\ref{Sec-5.1:FUU-basis}, \ref{Sec-5.2:FLL-basis}
and below in Secs.~\ref{Sec-7.2:FLTcosphiS}, \ref{Sec-7.6:FUTsinphiS}.
In all other cases, despite integration over $\Phperp$, we end up 
always with true convoluted TMDs (here within Gauss model).
We stress this important point by displaying the dependence of 
the structure functions on the mean hadron momenta, for instance
$F_{UT}^{\sin(\phi_h-\phi_S)}(x,z,\la\Phperp\ra) = 
\int d^2\Phperp F_{UT}^{\sin(\phi_h-\phi_S)}(x,z,\Phperp)$
in (\ref{FUTsiv-Gauss}).

The asymmetries $A_{UT}^{\sin(\phi_h-\phi_S)}= F_{UT}^{\sin(\phi_h-\phi_S)}/F_{UU}$  
for Jefferson Lab 12 GeV are plotted in Fig.~\ref{aut_f1t_jlab}.

\PS{\bf (We should plot here HERMES and/or COMPASS data, two samples
just for illustrative purposes. We can add a comment that Jefferson Lab 12
data will significantly improve the experimental constraints.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_x.pdf}  
\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_PT.pdf}
\caption{\label{aut_f1t_jlab} $A_{UT}^{\sin(\phi_h-\phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage

\subsection{\boldmath Leading twist $A_{UT}^{\sin(\phi_h+\phi_S)}$ Collins asymmetry}
\label{Sec-5.4:Collins-basis}

The structure function $F_{UT}^{\sin(\phi_h+\phi_S)}$ reads
\begin{subequations}\ba
	F_{UT}^{\sin(\phi_h+\phi_S)}(x,z,\Phperp) 
	&=& x\sum_q e_q^2\,h_{1}^{q}(x)\,H_1^{\perp(1)q}(z)\; 
	b^{(1)}_{\rm A}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \, , \\
	F_{UT}^{\sin(\phi_h+\phi_S)}(x,z,\la\Phperp\ra) 
	&=& x\sum_q e_q^2\,h_{1}^{q}(x)\,H_1^{\perp(1)q}(z)\;  
	c^{(1)}_{\rm A}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,,
	\label{eq:asymmetry_aut_h1}
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{h_1} + \avpperp_{H_1^\perp}$ and
$b^{(1)}_{\rm A}=2m_h$ and $c^{(1)}_{\rm A} = \sqrt{\pi}\,m_h$,
see App.~\ref{App:convol-details} for details.

Asymmetries $A_{UT}^{\sin(\phi_h+\phi_S)}=F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$
for Jefferson Lab 12 GeV are plotted in Fig.~\ref{aut_h1_jlab}.

\PS{\bf (We should plot here HERMES and/or COMPASS data, two samples
just for illustrative purposes. We can add a comment that Jefferson Lab 12
data will significantly improve the experimental constraints.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_x.pdf}  
\includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_PT.pdf}
\caption{\label{aut_h1_jlab} $A_{UT}^{\sin(\phi_h+\phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\subsection{\boldmath Leading twist $A_{UU}^{\cos(2\phi_h)}$ Boer-Mulders asymmetry}
\label{Sec-5.5:BM-basis}

The structure function $F_{UU}^{\cos(2\phi_h)}$ reads
\begin{subequations}\ba
	F_{UU}^{\cos(2\phi_h)}(x,z,\Phperp) 
	&=& x \sum_q e_q^2\,h_{1}^{\perp (1) q}(x)\,H_1^{\perp(1) q}(z)\; 
	b^{(2)}_{\rm AB}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\,
	{ \cal G}(\Phperp)\, , \\
	F_{UU}^{\cos2\phi_h}(x,z,\la\Phperp\ra) 
	&=& x\sum_q e_q^2\,h_{1}^{\perp(1) q}(x)\,H_1^{\perp(1)q}(z)\;  
	c^{(2)}_{\rm AB}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!2}\,,
	\label{eq:asymmetry_auu_cos2phi}
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{h_1^\perp} + \avpperp_{H_1^\perp}$ and
$b^{(2)}_{\rm AB}=\red{4}M_Nm_h$ and $c^{(2)}_{\rm AB} = 4M_Nm_h$,
see App.~\ref{App:convol-details}.

Asymmetries $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$  for  
Jefferson Lab 12 GeV are plotted in Fig.~\ref{auu_cos2phi_jlab}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_PT.pdf}
\caption{\label{auu_cos2phi_jlab} $A_{UU}^{\cos(2\phi_h)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PS{\bf (We should plot here HERMES and/or COMPASS data, two samples
just for illustrative purposes. We can add a comment that Jefferson Lab 12
data will significantly improve the experimental constraints. I would also
skip the Cahn effect for simplicity, and add a comment of the following
kind:)}

In the (to be updated) Fig.~\ref{auu_cos2phi_jlab} we plot only the
Boer-Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$ which does not describe
the data accurately. In fact, it is suspected that this observable receives 
a significant contribution from the Cahn effect \cite{Cahn:1978se}, a 
term of higher twist character of the type $\la\Phperp^2\ra/Q^2$ which 
is not negligible in fixed target experiments \cite{Schweitzer:2010tt}. 
This contribution was estimated and corrected for in the phenomenological 
works \cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} which was of
importance to obtain a picture of the Boer-Mulders function undistorted 
from Cahn effect. The point is that this substantial twist-4 contamination 
can be estimated phenomenologically, even though there is no rigorous 
theoretical basis for the description of such power-suppressed terms. 
In this work we consistently neglect power-suppressed contributions of 
order $1/Q^2$, and do so also in Fig.~\ref{auu_cos2phi_jlab}. 
Nevertheless we of course use the parametrizations of 
\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} offering
the best currently available parametrizations for $h_1^{\perp}$
which were corrected for Cahn effect as good as it is possible at
the current stage of art. It is unknown whether other asymmetries
could be similarly effected by such type of power-corrections.
This is an important point to be kept in mind as the lesson 
from Fig.~\ref{auu_cos2phi_jlab} shows.

\newpage
\subsection{\boldmath Leading twist $A_{UT}^{\sin(3\phi_h-\phi_S)}$  asymmetry}
\label{Sec-5.6:pretzel-basis}

The structure function $F_{UT}^{\sin(3\phi_h-\phi_S)}$ reads
\begin{subequations}\ba
	F_{UT}^{\sin(3\phi_h-\phi_S)}(x,z,\Phperp)
	&=& x \sum_q e_q^2\,h_{1T}^{\perp (2) q}(x)\,H_1^{\perp(1) q}(z)\; 
	b^{(3)}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!3}\,
	{ \cal G}(\Phperp) \, , \;\;\;\;
	\label{eq:asymmetry_aut_h1tp} \\
	F_{UT}^{\sin(3\phi_h-\phi_S)}(x,z,\la\Phperp\ra) 
	&=& x\sum_q e_q^2\,h_{1T}^{\perp (2) q}(x)\,H_1^{\perp(1)q}(z)\;  
	c^{(3)}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!\red{3}}\,,
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{h_{1T}^\perp} + \avpperp_{H_1^\perp}$ and
$b^{(3)}=2M_N^2m_h$ and $c^{(3)}_{\rm  } = 3\sqrt{\pi} \,M_N^2m_h$,
see App.~\ref{App:convol-details}.

Asymmetries $A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{aut_h1tp_jlab}.

\

\PS{\bf (We should plot here COMPASS data for illustrative purposes. 
I would propose to add a comment of the type:)}

\

Clearly, the pretzelosity TMD is the least known of the basis TMDs.
Nevertheless it is of fundamental importance, as it provides one of the
basis functions in our approach. It is so difficult to access it 
experimentally, because its contribution to the SIDIS cross section
is proportional to $\Phperp^3$, the TMD approach requires us to
necessarily operate at $\Phperp\ll Q$, and so far only moderate
values of $Q$ could be achieved in the fixed target experiments.
A notable exception is COMPASS where the largest $x$-bins 
(where $Q^2$ is largest) bear the best hints on this TMD,
see Fig.~\ref{aut_h1tp_jlab}.
Future high luminosity data from Jefferson Lab 12 are expected 
to significantly improve our knowledge of this TMD.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_x.pdf}  
\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_PT.pdf}
\caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
%======= SECTION 6: TWIST-2 AND WW-APROXIMATION ======================
\section{Leading twist asymmetries in WW-type approximation}
\label{Sec-6:twist-2-and-WW}

Two out of the 8 leading-twist structure functions can be 
described in the WW-type approximation thanks to the relations 
(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}) which allow us
to express $g_{1T}^{\perp (1) q}(x)$ and $h_{1L}^{\perp (1) q}(x)$ on 
the basis of available information on $g_1^q(x)$ and $h_1^a(x)$,
see Fig.~\ref{g1t_h1l_functions}.
In this section we discuss the associated asymmetries.

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/g1t.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/h1lperp.pdf}
	\caption{\label{g1t_h1l_functions} 
	$g^{\perp (1) q}_{1T}(x)$ (left panel) and
	$h^{\perp (1) q}_{1L}(x)$ distributions (right panel) for 
	$u$- and $d$-flavor. 
	\PS{\bf (Please, remove sea quarks in left panel).}}
\end{figure}

\subsection{\boldmath Leading twist $A_{LT}^{\cos(\phi_h-\phi_S)}$}
\label{Sec-6.1:FLTcosphi-phiS}

We assume for $g^{\perp}_{1T}$ the Gaussian Ansatz as follows 
\cite{Kotzinian:2006dw} 
\be
	g^{\perp q}_{1T}(x,\kperp^2) = 
	g^{\perp (1) q}_{1T}(x)\,\frac{2 M^2}{\pi \avkperp_{g_{1T}^\perp}^2}\,
	e^{-\kperp^2/{\avkperp_{g_{1T}^\perp}}}\;,
	\label{eq:g1t}
\ee
and evaluate $g^{\perp (1) q}_{1T}(x)$ using Eq.~(\ref{Eq:WW-approx-g1T})
which yields the result shown in Fig.~\ref{g1t_h1l_functions}.
For our numerical estimates we use $\avkperp_{g_{1T}^\perp} = \avkperp_{g_{1}}$ 
which is supported by lattice results \cite{Hagler:2009mb}.

In the Gauss Ansatz the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$ 
has the form
\begin{subequations}\ba
	F_{LT}^{\cos(\phi_h -\phi_S)}(x,z,\Phperp) 
	&=& x\sum_q e_q^2\,g_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \\
	F_{LT}^{\cos(\phi_h-\phi_S)}(x,z,\la\Phperp\ra) 
	&=&  x\sum_q e_q^2\,g_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\;
	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,
	\label{eq:asymmetry_g1t_pt-II}
\ea\end{subequations}
where 
$\lambda  = z^2 \avkperp_{g_{1T}^\perp} + \avpperp_{D_1}$,
$b^{(1)}_{\rm B} = 2M_N$,
$c^{(1)}_{\rm B} = \sqrt{\pi}\,M_N$,
see App.~\ref{App:convol-details} for details.
We remind that $g^{\perp q}_{1T}$ and the Sivers function are both 
constrained by the positivity bound \cite{Bacchetta:1999kz} 
\be
	\frac{\kperp^2}{M^2}\left( (g^{\perp q}_{1T}(x,\kperp^2))^2 
	+ (f_{1T}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 
\ee
which the parametrizations for $f^{\perp q}_{1T}$ and $g^{\perp q}_{1T}$
used in this work of course satisfy \PS{\bf (do they??)}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/ALT_x.pdf}  
\includegraphics[width=0.45\textwidth]{\FigPath/ALT_PT.pdf}
	\caption{\label{g1t_jlab} 
	$A_{LT}^{\cos(\phi_h -\phi_S)}$  as a function of $ x $ (left panel), 
	and as a function of $P_{hT}$ (right panel) at typical kinematics 
	of Jefferson Lab 12 GeV, 
	$\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
	\newline\PS{Can we compare here to COMPASS data from 
	\cite{Kotzinian:2007uv}?}}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The asymmetry  $A_{LT}^{\cos(\phi_h -\phi_S)}$ as a function of $x$ and $P_{hT}$ 
for Jefferson Lab 12 GeV is plotted in Fig.~\ref{g1t_jlab}.

\newpage
\subsection{\boldmath 
	Leading twist $A_{UL}^{\sin2\phi_h}$ Kotzinian-Mulders  asymmetry}
\label{Sec-6.2:FULsin2phi}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_PT.pdf}
	\caption{\label{aul_jlab} 
	$A_{UL}^{\sin(2\phi_h)}$  as a function of $ x $ (left panel), and   
	as a function of $P_{hT}$ (right panel) at typical kinematics of 
	Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, 
	$\la Q^2\ra = 2.4$ GeV$^2$.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We assume Gaussian form for Kotzinian-Mulders function $h_{1L}^{\perp a}$:
\be
	h_{1L}^{\perp a}(x,\kperp^2) = h_{1L}^{\perp (1) a}(x)\,
	\frac{2 M^2}{\pi{\avkperp_{h_{1L}^\perp}^2}}\,e^{-\kperp^2/{\avkperp_{h_{1L}^\perp}^2}}
	\;,\label{eq:h1l_final}
\ee
We will use WW-type approximation from Eq.~(\ref{Eq:WW-approx-h1L}) 
for calculation of $h_{1L}^{\perp (1) a}(x)$ and for the estimates of the 
asymmetry $\avkperp_{h_{1L}^\perp} = \avkperp_{h_{1}} = 0.25$ (GeV$^2$).
Notice that the Boer-Mulders function and $h^{\perp q}_{1L}$ obey the
positivity bound \cite{Bacchetta:1999kz}
\be
	\frac{\kperp^2}{M^2}\left( (h^{\perp q}_{1L}(x,\kperp^2))^2 + 
	(h_{1}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 \, .
\ee

The structure function $F_{UL}^{\sin(2\phi_h)}$ reads
\begin{subequations}\ba
	F_{UL}^{\sin(2\phi_h)}(x,z,\Phperp) 
	&=& 
	x \sum_q e_q^2\,h_{1L}^{\perp (1) q}(x)\,H_1^{\perp(1) q/h}(z)  
	\biggl(\frac{z\Phperp}{\lambda}\biggr)^{\!\!2} \;
	b^{(2)}_{\rm AB}\;{ \cal G}(\Phperp )\, , \\
	F_{UL}^{\sin(2\phi_h)}(x,z,\la\Phperp\ra) 
	&=& 
	x \sum_q e_q^2\,h_{1L}^{\perp (1) q}(x)\,H_1^{\perp(1) q/h}(z)  
	\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2} \;
	c^{(2)}_{\rm AB}\,,
\ea\end{subequations}
where $\lambda= z^2 \avkperp_{h_{1L}^\perp} + \avpperp_{H_1^\perp}$ and
$b^{(2)}_{\rm AB}=c^{(2)}_{\rm AB}=4M_Nm_h$,
see App.~\ref{App:convol-details} for details.

Resulting distributions $h^{\perp(1)q}_{1L}(x)$ are plotted in 
Fig.~\ref{g1t_h1l_functions}. 
The asymmetries $A_{UL}^{\sin(2\phi_h)}=F_{UL}^{\sin(2\phi_h)}/F_{UU}$  for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{aul_jlab}.

\newpage
%========= SECTION 8: TWIST-3 IN WW-TYPE APPROXIMATION ===============
\section{Subleading twist asymmetries in WW-type approximation}
\label{Sec-7:twist-3-and-WW}

The WW-type approximations are useful for all 8 subleading-twist observables,
as shown in Sec.~\ref{Sec-4.2:WW-twist-3}. In view of the complex 
structure of subleading-twist structure functions, WW-type approximations
might be particularly useful for the interpretation of twist-3 
observables.

\subsection{\boldmath Subleading twist  $A_{LU}^{\sin\phi_h}$}
\label{Sec-7.1:FLU}

We start our discussion with the structure function $F_{LU}^{\sin\phi_h}$,
Eq.~(\ref{FLUsinphi}), containing 4 terms: 
2 are proportional to pure twist-3 fragmentation functions 
$\tilde{G}^{\perp a}$ and $\tilde{E}^a$ and neglected; the other 2
terms are proportional to the twist-3 TMDs $e^a$ and $g^{\perp a}$ which
also turn out to be given in terms of pure twist-3 terms upon the 
inspection of Eqs.~(\ref{Eq:WW-type-1},~\ref{Eq:WW-type-gperp}).
Hence, after consequently applying the WW-type approximation we are left 
with no term. Our approximation predicts this structure function to be zero.

Instead, data from Jefferson Lab and HERMES show a small but 
clearly non-zero effect of the order of (2-3)\,$\%$ 
\cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,Aghasyan:2011ha,
Adolph:2014pwc,Gohn:2014zbz}.
What may seem at first glance to be a failure of the approach is in 
fact in line with it.
The important point is that in this case, the entire effect is due 
to $\bar qgq$-terms only. More precisely, the numerator of the 
asymmetry is proportional to $\bar q g q$-correlators, while the 
denominator is of course give by $f_1^aD_1^a$, i.e.\ in terms of
$q q$-correlators. Therefore we may formulate this approximation 
as follows
\be\label{Eq:ALU-small}
    A_{LU}^{\sin\phi_h}  
	\;\; \propto \;\;\frac{\la\bar qgq\ra}{\la\bar qq\ra}
    	\;\;\stackrel{\rm exp}{=} \;\; 
	{\cal O}\biggl( (2-3)\,\%\biggr)
    	\;.
\ee
We should keep in mind several reservations. First,
the experimental result quoted in (\ref{Eq:ALU-small})
contains also kinematic prefactors which help to reduce the value. 
Second, the denominator contains $f_1^a$ and $D_1^a$ which are the
largest TMD and FF because of positivity constraints. Third, the 
numerator is a sum of 4 terms, so its overall smallness could also 
result from cancellation of different terms, rather than indicating
that all 4 terms are small.
Keeping these reservations cautiously in mind, we may nevertheless 
consider the experimental observation of a (2-3)\,$\%$ asymmetry 
$A_{LU}^{\sin\phi_h}$ 
\cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,Aghasyan:2011ha,
Adolph:2014pwc,Gohn:2014zbz}
as an encouraging indication that $\bar qgq$-terms are smaller than 
$\bar qq$ terms, in line with the generic expectation (\ref{Eq:WW-generic}).

To conclude, the WW-type approximation does not fail in the case of 
$F_{LU}^{\sin\phi}$. This is a unique observable, the only twist-3 SIDIS 
structure not ``contaminated'' by leading twist terms. 
Our WW-type approximation qualitatively predicts the asymmetry 
$A_{LU}^{\sin\phi}$ to be small which is in agreement with experiment.
It is beyond our approach to make in this case a quantitative prediction. 
We notice that one obtains a zero result for this asymmetry also in
the parton model motivated approach limited to leading twist TMDs 
\cite{Anselmino:2011ch}.

\ \\
\blue{\bf
  COMPASS: https://arxiv.org/pdf/1401.6284.pdf \\
  data: https://hepdata.net/record/ins1278730}

\newpage
\subsection{\boldmath Subleading twist  $A_{LT}^{\cos\phi_S}$}
\label{Sec-7.2:FLTcosphiS}

In the WW-type approximation the structure function
$F_{LT}^{\cos\phi_S}$ is due to $g_T^a(x,\kperp)$ and $D_1^a(z,\pperp)$ 
whose collinear counterparts are more or less well known, see
Secs.~\ref{Sec-3.4:WW-classic-experiment} and \ref{Sec-5.1:FUU-basis}.
Assuming the Gaussian Ansatz for $g_T^a(x,\kperp)$ yields for the
structure function 
\begin{subequations}\ba
	F_{LT}^{\cos\phi_S}(x,z,\Phperp) 
	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\,g_T^q(x)\,D_1^q(z)\;   
	{ \cal G}(\Phperp)\, , \label{Eq:FLTcosphiS-Gauss}\\
	F_{LT}^{\cos\phi_S}(x,z)
	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\, g_T^q(x)\,D_1^q(z)\, ,
\ea\end{subequations}
with the width $\lambda= z^2 \avkperp_{g_T} + \avpperp_{D_1}$
in the Gaussian ${\cal G}(\Phperp)$. We estimate $g_T^a(x)$ in terms 
of $g_1^a(x)$ according to Eq.~(\ref{Eq:WW-original1}) assuming for 
the Gaussian width $\avkperp_{g_T}=\avkperp_{g_1}$.\footnote{
	Notice that one could also proceed in a different way: 
	explore first the WW-type-relation (\ref{Eq:WW-type-5}), and
	assume then the Gauss Ansatz for $g_{1T}^{\perp}(x,\kperp)$ 
	according to (\ref{eq:g1t}). Solving then the convolution integral 
	yields a result different from (\ref{Eq:FLTcosphiS-Gauss})
	which depends much more strongly on Gaussian model parameters.
	The operations of applying the WW-type approximations and 
	employing the Gauss Ansatz do not commute in general.
	The solution presented in (\ref{Eq:FLTcosphiS-Gauss}) is 
	preferable as it helps to minimize model dependence.}

Asymmetries $A_{LT}^{\cos\phi_S} = F_{LT}^{\cos\phi_S}/F_{UU}$ for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{altcosphi_jlab}.
Notice that the asymmetry scales at small transverse hadron
momenta as $A_{LT}^{\cos\phi_S} \propto (\Phperp)^0$ which makes
it easier to measure if longitudinally polarized lepton beams
and transversely polarized targets are available.

\ \\
\PS{We should include a comparison to 
COMPASS data \cite{Kotzinian:2007uv,Parsamyan:2010se}.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/ALTcosPhi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/ALTcosPhi_PT.pdf}
\caption{\label{altcosphi_jlab} $A_{LT}^{\cos\phi_S}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\subsection{\boldmath   Subleading twist  $A_{LL}^{\cos\phi_h}$}
\label{Sec-7.3:FLLcosphi}

The structure function $F_{UL}^{\cos\phi_h}$ reads
\begin{subequations}\ba
	F_{LL}^{\cos \phi_h}(x,z,\Phperp)
	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \, , \\ 
	F_{LL}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\;
	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\, , 
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{g_{L}^\perp} + \avpperp_{D_1}$, 
$b^{(1)}_{\rm B}=2M_N$,
$c^{(1)}_{\rm B} = \sqrt{\pi}\,M_N$, see App.~\ref{App:convol-details}.
We approximate the Gaussian width $\avkperp_{g_{L}^\perp}=\avkperp_{g_1}$ and 
estimate $g_L^{\perp(1) a}(x)$ according to Eq.~(\ref{Eq:WW-type-gLperp}) as
\be
	x\,g_L^{\perp(1) a}(x) = \frac{\la \kperp^2\ra_{g_1}}{2\,M_N^2}\,
	g_1^a(x) \,.
\ee
The asymmetries $A_{LL}^{\cos\phi_S}=F_{LL}^{\cos\phi_S}/F_{UU}$  for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{allcosphi_jlab}.

\ \\
\PS{We should include a comparison to 
COMPASS data \cite{Kotzinian:2007uv,Parsamyan:2010se}.}

\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[b!]
\centering
\includegraphics[width=0.4\textwidth]{figs/ALLcosphi_x.pdf} 
\includegraphics[width=0.4\textwidth]{figs/ALLcosphi_PT.pdf}
\caption{\label{allcosphi_jlab} $A_{LL}^{\cos\phi_h}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\subsection{\boldmath Subleading twist $A_{UL}^{\sin\phi_h}$ }
\label{Sec-7.4:FULsinphi}

This twist-3 asymmetry has played a special role, as it was historically 
the first single spin asymmetry ever measured in SIDIS 
\cite{Airapetian:1999tv,Airapetian:2001eg,Airapetian:2002mf,Airapetian:2005jc}.
See also the recent COMPASS data \cite{Alekseev:2010dm}.
This asymmetry is sizable despite being twist-3. Although it was subject to 
numerous phenomenological studies, this asymmetry still remains unexplained.

Retaining the only non-zero term in the WW-type approximation, and
assuming for $h_L^q(x,\kperp)$ a Gaussian Ansatz, we obtain
for the structure function 
\begin{subequations}\ba
	F_{UL}^{\sin\phi_h}(x,z,\Phperp) 
	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\; 
	b^{(1)}_{\rm A}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \, , \\
	F_{UL}^{\sin\phi_h}(x,z,\la\Phperp\ra) 
	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\;  
	c^{(1)}_{\rm A}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{h_L} + \avpperp_{H_1^\perp}$ and
$b^{(1)}_{\rm A}=2m_h$ and $c^{(1)}_{\rm A} = \sqrt{\pi}\,m_h$,
see App.~\ref{App:convol-details} for details. We now approximate 
$\avkperp_{h_L}=\avkperp_{h_1}$ and explore (\ref{Eq:WW-type-6}) to estimate
\be
	xh_L^q(x) = h_{1L}^{\perp(1)q}(x)
\ee
and finally express $h_{1L}^{\perp(1)q}(x)$ in terms of $h_1^a(x)$
using (\ref{Eq:WW-approx-h1L}).

The asymmetries $A_{UL}^{\sin\phi_h}=F_{UL}^{\sin\phi_h}/F_{UU}$  for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{aulsinphi_jlab}.

\ \\
\PS{See especially \cite{Airapetian:2005jc} where contaminations
from transverse target polarization have been tediously removed!
Have to compare to those VERY CLEAN data!}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_PT.pdf}
\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\subsection{\boldmath Subleading twist  $A_{LT}^{\cos(2\phi_h - \phi_S)}$}
\label{Sec-7.5:FLTcos2phi-phiS}

Retaining the only non-zero term in the WW-type approximation, and
assuming for $g_T^{\perp a}(x,\kperp)$ a Gaussian Ansatz, we obtain
for the structure function 
\begin{subequations}\ba
	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\Phperp) 
	&=& \red{-}x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\; 
	b^{(2)}_{C}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\,
	{ \cal G}(\Phperp)\, , \\
	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\la\Phperp\ra) 
	&=& \red{-}x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\;  
	c^{(2)}_{C}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!2}\,
	\label{eq:asymmetry_auu_cos2phi}
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{g_{T}^\perp} + \avpperp_{D_1}$ and 
$b^{(2)}_{\rm C}=c^{(2)}_{\rm C} = M_N^2$, 
see App.~\ref{App:convol-details} for details. 
We estimate $\avkperp_{g_{T}^\perp}=\avkperp_{g_1}$ and explore
the WW-type approximation (\ref{Eq:WW-type-gTperp}), 
\be
	xg_T^{\perp(2)q}(x) = \frac{\la\kperp^2\ra_{g_{1T}^\perp}}{M_N^2}\;
	g_{1T}^{\perp (1)q}(x)\,,
\ee
where we finally express $g_{1T}^{\perp (1)q}(x)$ in terms of $g_1^q(x)$ 
according to Eq.~(\ref{Eq:WW-approx-g1T}).

The asymmetry  $A_{LT}^{\cos(\phi_h -\phi_S)}=F_{LT}^{\cos(\phi_h -\phi_S)}/F_{UU}$ 
as a function of $x$ and $P_{hT}$ for Jefferson Lab 12 GeV is plotted in 
Fig.~\ref{altcos2phi_jlab}.

\ \\
\PS{We should include a comparison to 
COMPASS data \cite{Kotzinian:2007uv,Parsamyan:2010se}.}

\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/ALTcos2phi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/ALTcos2phi_PT.pdf}
\caption{\label{altcos2phi_jlab} $A_{LT}^{\cos(2\phi_h - \phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\subsection{\boldmath Subleading twist  $A_{UT}^{\sin\phi_S}$}
\label{Sec-7.6:FUTsinphiS}

In the structure function $F_{UT}^{\sin\phi_S}$ we encounter 3 interesting 
new features. This is the first case with more than 1 contribution after 
applying the WW-type approximation. Assuming Gauss Ans\"atze for the TMDs
$f_T^q(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
we obtain 
\begin{subequations}\begin{alignat}{1}
	F_{UT}^{\sin\phi_S}(x,z,\Phperp) 
	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	  x\,f_T^q(x)
	\, D_1(z) \, { \cal G}(\Phperp)  \label{Eq:FUTsinphiS-Gauss-I-PhT}\\
	&- {\textstyle\frac12}\,x\,\left(h_T^{(1)q}(x)-h_T^{\perp(1)q}(x)\right)
	\,H_1^{\perp(1)q}(z)\; \frac{4z^2 m_h\,M_N}{\lambda} 
	\left(1-\frac{\Phperp^2}{\lambda}\right) {\cal G}(\Phperp) \Biggr] 
  	\nonumber\\
	F_{UT}^{\sin\phi_S}(x,z) 
	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\, x\,f_T^q(x)\, D_1(z) 
	\label{Eq:FUTsinphiS-I-naive}\
\end{alignat}\end{subequations}
with  respectively
$\lambda=z^2\la\kperp^2\ra_{f_T}+\la\pperp^2\ra_{D_1}$ in the first, and  
$\lambda=z^2\la\kperp^2\ra_{h_T^\perp}+\la\pperp^2\ra_{H_1^\perp}$ in the 
second term of Eq.~(\ref{Eq:FUTsinphiS-Gauss-I-PhT}) where we 
assumed $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}$.

The second interesting feature not encountered before is that a contribution
drops out upon integrating the structure function over $\Phperp$, cf.\ 
Eq.~(\ref{Eq:FUTsinphiS-Gauss-I-PhT}) vs.\ (\ref{Eq:FUTsinphiS-I-naive}).
This is a property of the weight $\omega^{\{2\}}_{\rm B}$,
see Eq.~(\ref{Eq:wi}) and App.~\ref{App:factor}, which appears
also in $F_{LT}^{\cos\phi_S}$, Eq.~(\ref{FLTcosphiS}), where it however drops
out in WW-type approximation. In principle, this property could  help to 
discriminate experimentally the terms associated with this weight.

Exploring the WW-type approximations (\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}) 
the chiral odd twist-3 TMDs can be unambiguously related to transversity
\begin{subequations}\be
   	-\,{\textstyle\frac12}\,x \left(h_T^{(1)q}(x) - h_T^{\perp(1)q}(x)\right)
	= h_1^{(1)q}(x) = \frac{\la\kperp^2\ra_{h_1}}{2M_N^2}\,h_1^q(x)\, .
\ee
Now we encounter the third interesting feature, namely the treatment 
of $f_T^q(x)$ is not unambiguous. We could explore the sum rule 
(\ref{Eq:sum-rules-T-odd}) or employ the WW-type approximation 
(\ref{Eq:WW-type-fT}) to obtain 
\be
   	x \, f_T^q(x) 
	\stackrel{!?}{=} \begin{cases} 
	\phantom{-}\, 0 	
	& \mbox{due to sum rule (\ref{Eq:sum-rules-T-odd}),} \cr
	- \, f_{1T}^{\perp (1)q}(x) 
		& \mbox{due to WW-type (\ref{Eq:WW-type-fT}),} 
		\end{cases}\label{WW-type-fTperp-discuss-II}
		\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
\ee\end{subequations}
We recall that the twist-3 TMD $f_T^q(x,\kperp) \neq 0$ in general, 
but the collinear T-odd PDF $f_T^q(x) = 0$ due to time reversal, 
Eq.~(\ref{Eq:sum-rules-T-odd}). This was discussed in 
Sec.~\ref{Sec-3.7:basis+limitations}.

Notice that in Eq.~(\ref{Eq:FUTsinphiS-Gauss-I-PhT}) we really have a 
choice, because we strictly speaking deal with the convoluted non-zero 
TMD $f_T^q(x,\kperp)$, and the Gauss model only {\it artificially} 
introduces the collinear function $f_T^q(x)$ expected to be zero.
However, in Eq.~(\ref{Eq:FUTsinphiS-I-naive}) we have no choice.
Here we really deal with the collinear function $f_T^q(x)$ which
must vanish due to the sum rule (\ref{Eq:sum-rules-T-odd}).
How should one proceed?

If we wish to respect the sum rule (\ref{Eq:sum-rules-T-odd}), 
we have to describe $f_T^q(x,\kperp)$ by a function with a node 
in $\kperp$. A simple Gaussian is not adequate for that. But from
phenomenological point of view, one of course could work with a 
superposition of Gaussians\footnote{
	The possibility of TMDs with nodes is not unrealistic.
	For instance in the covariant parton model the helicity TMDs 
	exhibit nodes for the $u$ and $d$- flavor \cite{Efremov:2010mt}.
	We will have to revise our description of $g_1^q(x,\kperp)$ 
	in Eq.~(\ref{eq:g1}) and App.~\ref{App:basis-g1} to something 
	of the type (\ref{Eq:multiple-Gauss}), if this prediction is 
	confirmed experimentally. }
with different widths, 
\begin{alignat}{1}
	x \, f_T^q(x,\kperp) =  - \, f_{1T}^{\perp (1)q}(x)\;
	&\sum\limits_{i=1}^{n} a_i\;
	\frac{\exp(-\kperp^2/\la\kperp^2\ra_i^{ }}{\pi\la\kperp^2\ra_i^{ }}\,,
	\nonumber\\
	&\sum\limits_{i=1}^n a_i = 0\,, \;\;
	\la\kperp^2\ra_i^{ }\neq\la\kperp^2\ra_j^{ }\;\;\forall\;i\neq j,
	\; 1\le i,\,j\le n,\;n\ge 2.\label{Eq:multiple-Gauss}
\end{alignat}
The minimal choice would be $n=2$ with $a_1=-a_2=1$ and
$\la\kperp^2\ra_1^{ } = \la\kperp^2\ra_{f_1^\perp}$ to make maximal use 
of the theoretical guidance provided by the WW-type approximation 
(\ref{Eq:WW-type-fT}). 
The second Gaussian width $\la\kperp^2\ra_2^{ }$ could then be chosen
very small $\la\kperp^2\ra_2^{ } \ll \la\kperp^2\ra_{f_1^\perp}$.
Within such a Gaussian description we would have a transverse momentum 
dependence of $f_T^{q}(x,\kperp^2)$ similar to that of 
$f_{1T}^{\perp(1)q}(x,\kperp^2)$ at not too small $\kperp$. 
A very small parameter $\la\kperp^2\ra_2^{ }$ could be thought of as 
a relict, e.g.\ of gluonic pole contributions in the $\bar qgq$-term 
$\tilde{f}_T^q(x,\kperp)$. It will be very interesting to follow up
on this in future studies.

At this point, however, we have no guidance from phenomenology or theory 
to fix additional parameters and choose a pragmatic and simple solution, 
namely to implement the sum rule (\ref{Eq:sum-rules-T-odd}) also in 
Eq.~(\ref{Eq:FUTsinphiS-Gauss-I-PhT}). This is
a model-dependent choice and this step could be revised along the
lines of the above discussion. Our final result is therefore
\begin{alignat}{1}
	F_{UT}^{\sin\phi_S}(x,z,\Phperp) 
	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\,
	h_1^{(1)q}(x)\,H_1^{\perp(1)q}(z)\; \frac{4z^2 m_h\,M_N}{\lambda} 
	\left(1-\frac{\Phperp^2}{\lambda}\right) {\cal G}(\Phperp) 
	\nonumber\\
  	F_{UT}^{\sin\phi_S}(x,z) 
	&= 0 \, .	\label{Eq:FUTsinphiS-final}
\end{alignat}
In (\ref{Eq:FUTsinphiS-final}) we recover the consistent result for 
the ``collinear'' (i.e.\ related to the weight $\omega^{\{0\}}$) SIDIS 
structure function $F_{UT}^{\sin\phi_S}(x,z)$ in WW-type approximation, 
see Eq.~(\ref{Eq:FUT-collinear}).

The asymmetries $A_{UT}^{\sin\phi_S}=F_{UT}^{\sin\phi_S}/F_{UU}$  for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{autsinphi_jlab}.
\PS{Compare to HERMES data \cite{Schnell:2010zza}?
Is there by now final data? Will be interesting!}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphi_PT.pdf}
\caption{\label{autsinphi_jlab} $A_{UT}^{\sin\phi_S}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\subsection{\boldmath Subleading twist  $A_{UU}^{\cos\phi_h}$ }
\label{Sec-7.7:FUUcosphi}

Historically this was the first predicted \cite{Cahn:1978se} and measured
\cite{Aubert:1983cz} azimuthal asymmetry in (unpolarized) SIDIS, and
later explored in \cite{Anselmino:2005nn} to extract information on the 
Gaussian widths of $f_1^q(x,\kperp)$ and $D_1^q(x,\pperp)$ (under the 
implicit assumption of WW-type approximations).

The structure function $F_{UU}^{\cos\phi_h}$, Eq.~(\ref{Eq:FUUcosphi}),
contains after the WW-type approximation two contributions. Assuming
Gaussian Ans\"atze for $h^{q}(x,\kperp)$ and $f^\perp(x,\pperp)$ we obtain
\begin{subequations}\begin{alignat}{1}
	F_{UU}^{\cos\phi_h}(x,z,\Phperp) 
	= \red{+}\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;b^{(1)}_{\rm A}\,
	  \biggl(\frac{z \Phperp} {\lambda}\biggr)\, & { \cal G}(\Phperp)
	  \nonumber\\
	\red{-} x\,f^{\perp(1)q}(x)\,D_1^q(z)\;b^{(1)}_{\rm B}\,
	  \biggl(\frac{z \Phperp} {\lambda}\biggr)\, & { \cal G}(\Phperp ) 
	\Biggr] \label{Eq:XXXa}\\
	F_{UU}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
	= \red{+}\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;c^{(1)}_{\rm A}\;
	  \biggl(\frac{z}{\lambda^{1/2}}\biggr)&
	  \nonumber\\
	\red{-}x\,f^{\perp(1)q}(x)\,D_1^q(z)\;c^{(1)}_{\rm B}\;
	  \biggl(\frac{z}{\lambda^{1/2}}\biggr)&
	\Biggr] \label{Eq:XXXb}
\end{alignat}\end{subequations}
with $\lambda=z^2\la\kperp^2\ra_{h}+\la\pperp^2\ra_{H_1^\perp}$ in the first, 
and  $\lambda=z^2\la\kperp^2\ra_{f^\perp}+\la\pperp^2\ra_{D_1}$ in the second 
term respectively in (\ref{Eq:XXXa}) and (\ref{Eq:XXXb}). The coefficients 
$b^{(1)}_i$ and $c^{(1)}_i$ are defined in App.~\ref{App:convol-details}.

The application of the WW-type approximation (\ref{Eq:WW-type-last}) 
for $h^q(x)$ is subtle. Applying it literally would imply 
$x\,h^q(x) = - 2\,h_1^{\perp(1)}(x)$ at variance with the sum rule
(\ref{Eq:sum-rules-T-odd}) for the collinear T-odd twist-3 TMD $h^q(x)$.
The situation is analog to the case of $f_T^q(x,\kperp)$
discussed in Sec.~\ref{Sec-7.6:FUTsinphiS}. Also here one could introduce
an additional Gauss parameter and use a double Gaussian to describe 
$h^q(x,\kperp)$. One should keep this in mind as an interesting possibility
to be explored in future studies. However, at this point we have no guidance
from theory or phenomenology to fix additional parameters. We therefore
proceed analogously to Sec.~\ref{Sec-7.7:FUUcosphi}, and impose 
(in a model-dependent step) the sum rule (\ref{Eq:sum-rules-T-odd}) 
by setting 
\begin{subequations}\be
	x\,h_1^q(x) = 0\,.
\ee

For $f^{\perp(1)}(x)$ we explore Eq.~(\ref{Eq:WW-type-Cahn}) as
\be
	x\,f^{\perp(1)}(x) = \frac{\la\kperp^2\ra_{f_1}}{2M_N^2}\,f_{1}^q(x)
	\, , 
\ee\end{subequations}
and estimate its Gaussian width as $\la\kperp^2\ra_{f^\perp}=\la\kperp^2\ra_{f_1}$.
The latter means the Gaussian factors of 
$F_{UU}^{\cos\phi_h}$ and $F_{UU}$ cancel out, i.e.\ at some point 
for $\Phperp\gtrsim1\,$GeV we would obtain from (\ref{Eq:XXXa}) 
an asymmetry $A_{UU}^{\cos\phi_h}=F_{UU}^{\cos\phi_h}/F_{UU}$ exceeding
100$\,\%$ and violating unitarity. This is of course an artifact of our 
approximations, and reminds us that the WW-type approximations as well
as the entire TMD formalism must be applied to small $\Phperp\ll Q$,
and in the case of $A_{UU}^{\cos\phi_h}$ preferably for $\Phperp < 1\,$GeV,
as shown in Fig.~\ref{auucosphi_jlab}. \\
\PS{(Alexei: did you notice it \cite{Anselmino:2005nn}? How did you treat it?)}

The asymmetries $A_{UU}^{\cos\phi_h}$  for 
Jefferson Lab 12 GeV are plotted in Fig.~\ref{auucosphi_jlab}.
\PS{We should compare to EMC, or 
	JLab \cite{Osipenko:2008aa,Mkrtchyan:2007sr}, 
	HERMES and COMPASS \cite{Giordano:2009hi,Joosten:2009zz}.
	There is probably also newer data!}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_PT.pdf}
\caption{\label{auucosphi_jlab} $A_{UU}^{\cos\phi_h}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\

\ \\
\PS{We may potentially run into positivity issues also for other observables. 
However, I would suggest not to worry too much. We see in the pictures that 
the respective asymmetries are smaller than 100$\,\%$ for reasonably small 
$\Phperp$ and can be happy with that! But perhaps we should include a 
comment somewhere?}

%------ BEGIN FIGURE 4: Phperp(z) AND Phperp^2(z) at HERMES ----------
        \begin{figure}[b!]
        \vspace{-0.6cm}
        \includegraphics[height=8cm]{\FigPath/Fig06-EMC-cosphi-z.pdf}
        \vspace{-0.5cm}
        \caption{\label{Fig-02:EMC}
        Azimuthal asymmetry $A_{UU}^{\cos\phi}$ in charged hadron 
        production in SIDIS of $280\,{\rm GeV}$ muons off protons
        as function of $z$. The data from EMC \cite{Aubert:1983cz}
        refer to $\la Q\ra=4.8\,{\rm GeV}$. The theoretical
        curve is the ``WW-type and Cahn-effect-only'' approximation 
        for this observable in the Gauss model with parameters 
        fixed from HERMES data and neglecting evolution effects. 
	From Ref.~\cite{Schweitzer:2010tt}.}
        \end{figure}
%------ END FIGURE 4 -------------------------------------------------

\newpage
\subsection{\boldmath Subleading twist  $A_{UT}^{\sin(2\phi_h-\phi_S)}$ }
\label{Sec-7.8:FUTsin2phi-phiS}

In this last asymmetry we encounter the first case with more than 
1 contribution in our treatment. Assuming Gauss Ans\"atze for 
$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ we find
\begin{subequations}\begin{alignat}{1}
	F_{UT}^{\sin(2\phi_h -\phi_S)}(x,z,\Phperp) \; \; 
	= \; \; \; \;
	\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	x \; f_T^{\perp(2)q}(x) \; D_1(z) \;b^{(2)}_{\rm C}\;
	&\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\;{ \cal G}(\Phperp) 
	\nonumber\\
	+ \;
	x\left(h_T^{(1)q}(x)+h_T^{\perp(1)q}(x)\right)H_1^{\perp(1)q}(z)\,
	\frac{b^{(2)}_{\rm AB}}{2}
	&\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\;{\cal G}(\Phperp)\Biggr] 
	\label{Eq:FUTsin2phi-phiS-Gauss-PhT}\\
{ }
	F_{UT}^{\sin(2\phi_h -\phi_S)}(x,z,\Phperp) \; \; 
	= \; \; \; \;
	\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
	x \; f_T^{\perp(2)q}(x) \; D_1(z) \; c^{(2)}_{\rm C} \;
	&\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2}
	\nonumber\\
	+ \;
	x\left(h_T^{(1)q}(x)+h_T^{\perp(1)q}(x)\right)H_1^{\perp(1)q}(z)\,
	\frac{c^{(2)}_{\rm AB}}{2}
	&\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2}\Biggr] 
	\label{Eq:FUTsin2phi-phiS-Gauss}
\end{alignat}\end{subequations}
with respectively 
$\lambda=z^2\la\kperp^2\ra_{f_T^\perp}+\la\pperp^2\ra_{D_1}$ in the first, and  
$\lambda=z^2\la\kperp^2\ra_{h_T^\perp}+\la\pperp^2\ra_{H_1^\perp}$ in the second 
terms in 
Eqs.~(\ref{Eq:FUTsin2phi-phiS-Gauss-PhT},~\ref{Eq:FUTsin2phi-phiS-Gauss}).
We use $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T}$. The coefficients 
$b^{(2)}_i$ and $c^{(2)}_i$ are defined in App.~\ref{App:convol-details}.
We now explore the WW-type approximations in
Eqs.~(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}) to 
express the twist-3 TMDs in terms of the Sivers function and pretzelosity
as follows
\begin{subequations}\ba
   	x \, f_T^{\perp(2)q}(x) 
	&=& f_{1T}^{\perp (2)q}(x) 
	\equiv \frac{\la\kperp^2\ra_{f_{1T}^\perp}}{M_N^2}\,f_{1T}^{\perp (1)q}(x)\,,\\
   	-\,{\textstyle\frac12}\,x \left(h_T^{(1)q}(x) + h_T^{\perp(1)q}(x)\right)
	&=& h_{1T}^{\perp(2)q}(x) \, .
%	\equiv\frac{\la\kperp^2\ra_{f_{1T}^\perp}}{M_N^2}\,f_{1T}^{\perp(1)q}(x)
\ea\end{subequations}
%
%
% $xh_T^q(x,\kperp^2)        =-h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2)$
% $xh_T^{\perp q}(x,\kperp^2)= h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2)$
%
% $xf_T^{\perp q}(x,\kperp^2) = f_{1T}^{\perp   q}(x,\kperp^2)$
% $xf_T^{q}      (x,\kperp^2) =-f_{1T}^{\perp(1)q}(x,\kperp^2)$
%
% In our approach this is the only asymmetry which receives 2 contributions.
The asymmetries $A_{UT}^{\sin (2 \phi_h-\phi_S)}=F_{UT}^{\sin (2 \phi_h-\phi_S)}/F_{UU}$  
for Jefferson Lab 12 GeV are plotted in Fig.~\ref{autsin2phi_jlab}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2phi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2phi_PT.pdf}
\caption{\label{autsin2phi_jlab} $A_{UT}^{\sin(2\phi_h- \phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{}

%======= SECTION 9: CONCLUSIONS ======================================
\newpage
\section{Conclusions  \judge{0$\,\%$ okay}}
\label{Sec-8:conclusions}

\red{\bf The following is just a collections of text fragments cut out
from the main text and pasted here in the hope it might be useful.}

\

% , and show that in this approximation all leading- and
% subleading-twist structure functions are expressed in terms of
% a ``basis'' consisting of 6 twist-2 TMDs and 2 twist-2 fragmentation 
% functions. 
It is important to remark that the generalized parton model 
approach of Ref.~\cite{Anselmino:2011ch} provides a description,
which is largely equivalent to ours.

\

The results presented in this work are of importance for several reasons.
First, to the best of our knowledge it is the first complete study 
of all SIDIS structure functions up to twist-3 in a unique approach. 
Second, the results are of use for experiments prepared in the near-term 
(Jefferson Lab 12) or proposed in the long-term (Electron Ion Collider),
and provide helpful input for Montecarlo event generators 
\cite{Avakian:2015vha}.
Third, our predictions will help to interpret data.
The quality of the approximations can only be determined experimentally. 
It is of importance to establish clear predictions, what we can expect 
to see in experiments on the basis of the WW approximation.
If our predictions will be confirmed, it will mean the WW-type approximations
for TMDs work well and call for theoretical explanations why.
If our predictions fail, it will mean that certain $\bar{q}gq$-terms are
sizable and call for theoretical studies to explain why.
In any case, we are going to learn important lessons

\

In the dedicated study \cite{Accardi:2009au} it was shown that the
error bars of the present data are compatible with a violation of the 
WW-approximation for $g_T^a(x)$ up to $40\,\%$ in certain regions of $x$. 
Rephrased in a more optimistic way, one may interpret the findings of
\cite{Accardi:2009au} as ``the WW approximation works to an accuracy of
 $40\,\%$ or better,'' and having an approximation with such a quality
for TMDs would be very valuable. It would help to interpret first
data, and allow us to make predictions for new experiments 
(JLab 12, EIC) where unknown TMDs contribute.

The aim of the presented study was to review what can be said about
the quality of  WW-(type-)approximations on the basis of results
from theory, models, and phenomenology. In particular, we have
presented a complete treatment of SIDIS observables in the
WW-type-approximation. This is what we found out.

Bla, bla, bla.

\section{Acknowledgments}
This work was partially supported by the U.S.\
Department of Energy under Contract No.~DE-AC05-06OR23177 (A.P.) and by the National Science Foundation
under Contract No. PHY-1623454 (A.P.).

\newpage
\appendix

\section{\boldmath The ``minimal basis" of TMDs and FFs}
\label{App:basis}

This Appendix describes the technical details of the parametrizations
used in this work.

\subsection{\boldmath Unpolarised functions $f_1^a(x,k_\perp)$ 
			and $D_1(z,P_\perp)$}
\label{App:basis-f1-D1}

In this work we use the leading-order parametrizations 
from \cite{Martin:2009iq} for the unpolarized PDF $f_1^a(x)$ and 
from \cite{deFlorian:2007aj} for the unpolarized FF $D_1^a(z)$.
If not otherwise stated the parametrizations are taken at the scale 
$Q^2=2.4\,{\rm GeV}^2$ typical for many currently available SIDIS data.
These parameterizations were used in \cite{Anselmino:2005nn} and other 
works whose extractions we adopt.

To describe the transverse momentum dependence of $f_1^a(x,k_\perp)$ 
and $D_1(z,P_\perp)$ we use the Gaussian Ansatz in 
Eqs.~(\ref{Eq:Gauss-f1-D1}). All early 
\cite{Anselmino:2005nn,Collins:2005ie,D'Alesio:2007jt,Schweitzer:2010tt}
and some recent \cite{Signori:2013mda} analyses employed flavor and 
$x$- or $z$-independent widths $\avkperp$ and $\avpperp$.
In the the analysis \cite{Anselmino:2013lza} 
of HERMES multiplicities flavor-independence of the widths was 
assumed. On long run one may anticipate that new precision data will 
require to relax these assumptions. However, one may also expect that the 
Gaussian Ansatz will remain a useful {\it approximation} as long as one is 
interested in describing data on transverse hadron momenta $\Phperp \ll Q $.

The parameters resulting from calculations or extractions are presented in
Table~\ref{Table:Gauss-paramaters}. 
As most extractions of TMDs that we will use are done with the choice of 
$\avkperp_{f_1} = 0.25$ GeV$^2$, $\avpperp_{D_1}= 0.2$ GeV$^2$, for our numerical estimates in this work  we will use these fixed widths.

Some comments are in order.
In \cite{Anselmino:2005nn} no attempt was made to assign an uncertainty of the 
best fit result. The uncertainty of the numbers from \cite{Schweitzer:2010tt}
includes only the statistical error, but no systematic uncertainty.
For comparison lattice results from \cite{Hagler:2009mb} are included
whose range indicates flavor-dependence 
(first number $u$-flavor,
second number $d$-flavor). 
Notice that this is the contribution of the flavor averaged
over contributions from the respective quarks and antiquarks.
Chiral theories predict significant differences in the $\kperp$-behavior
of sea and valence quarks \cite{Schweitzer:2012hh}.
We will comment more on the lattice results in the next section.
In view of the large (and partly underestimated) uncertainties and the 
fact that those parameters are anti-correlated the numbers from the 
different approaches quoted in Table~\ref{Table:Gauss-paramaters} 
can be considered to be in good agreement.

\begin{table}[h!]
\centering
\begin{tabular}{|r|l|c|c|c|}
\hline
  & & & & \cr
  study \ \ \ \ 
	& $\;\;\la Q^2\ra$, $\la x\ra$, $\la z\ra$ 
	& $\avkperp_{f_1}$ 
  	& $\avpperp_{D_1}$ 
	& $\avkperp_{g_1}$ \cr
  	& {\footnotesize $[{\rm GeV}^2]$} 
  	& {\footnotesize $[{\rm GeV}^2]$} 
  	& {\footnotesize $[{\rm GeV}^2]$} 
  	& {\footnotesize $[{\rm GeV}^2]$} \cr
  & & & & \cr
\hline
  & & & & \cr
\ fit of \cite{Anselmino:2005nn} & 5, 0.1, 0.3
	& $\sim 0.25$ 
	& $\sim 0.2$ 
	& -- \cr
\ fit of \cite{Schweitzer:2010tt} & 2.5, 0.1, 0.4 
	& $0.38\pm0.06$ 
	& $0.16\pm0.01$ 
	& -- \cr
\ fit of \cite{Anselmino:2013lza} & 2.4, 0.1, 0.3 
	& $0.57\pm0.08$ 
	& $0.12\pm0.01$ 
	& -- \cr
\ fit of \cite{Signori:2013mda} & 2.4, 0.1, 0.5 
	& $\sim0.3$
	& $\sim0.18$ 
	& -- \cr
\ lattice \cite{Hagler:2009mb}  & 4, -- , --
	& 0.14--0.15   
	& -- 
	& 0.11-0.15 \cr
  & & & & \cr 
\hline
\end{tabular}
\caption{\label{Table:Gauss-paramaters}
  	Gauss model parameters for $f_1^a(x,k_\perp)$, $D_1^a(z,P_\perp)$, 
 	$g_{1}^a(x,k_\perp)$ from phenomenological and lattice QCD studies.
  	The kinematics to which the phenomenological results and the
	renormalization scale of the lattice results are indicated.
	The range of lattice values indicates flavor dependence
        (first number refers to $u$-flavor, second number to $d$-flavor).}
\end{table}

\subsection{\boldmath Helicity distribution $g_1^a(x,k_\perp)$}
\label{App:basis-g1}

For the helicity PDF $g_1^a(x)=\int d^2k_\perp\,g_1^a(x,k_\perp)\equiv 
\int d^2k_\perp\,g_{1L}^a(x,k_\perp)$ we use in this work the leading-order 
parameterizations from \cite{Gluck:1998xa}.
If not otherwise stated the parametrizations are taken at the scale 
$Q^2=2.5\,{\rm GeV}^2$.

In lack of phenomenological information on the $k_\perp$-dependence of
$g_1^a(x,k_\perp)$ we explore lattice QCD results from \cite{Hagler:2009mb}
to constrain the Gaussian width in Eq.~(\ref{eq:g1}). 
On a lattice with pion and nucleon masses 
$m_\pi\approx 500\,{\rm MeV}$ and $M_N=1.291(23)\,{\rm GeV}$ 
and with an axial coupling constant $g_A^{(3)}= 1.209(36)$ reasonably
close to its physical value $1.2695(29)$ the following results were
obtained for the mean square transverse parton momenta \cite{Hagler:2009mb}.
For the unpolarized TMDs it was found
$\langle \kperp^2 \rangle_{f_1^u} = (0.3741\,{\rm GeV})^2$ and
$\langle \kperp^2 \rangle_{f_1^d} = (0.3839\,{\rm GeV})^2$.
For the helicity TMDs it was found
$\avkperp_{g_1^u} = (0.327\,{\rm GeV})^2$ and
$\avkperp_{g_1^d} = (0.385\,{\rm GeV})^2$. 
These values are quoted in Table~\ref{Table:Gauss-paramaters}.

The lattice values for $\langle \kperp^2 \rangle_{f_1}$ consistently 
underestimate the phenomenological numbers, see 
Table~\ref{Table:Gauss-paramaters}.
The exact reasons for that are unknown, but it is natural to think it
might be related to the fact that the lattice predictions \cite{Hagler:2009mb}
do not refer to TMDs entering in SIDIS (or Drell-Yan or other process) 
because a different gauge link was chosen, see Sec.~\ref{Sec-3.5:WW-lattice}. 
Still one may expect these results to bear considerable information 
on QCD dynamics.\footnote{
	The results \cite{Hagler:2009mb} refer also to pion masses above the 
	physical value. This is caveat is presumably less critical and
	will be overcome as lattice QCD simulations are becoming feasible 
	at physical pion masses.}
To make use of this information we shall assume that the lattice results
\cite{Hagler:2009mb} provide robust predictions for the {\it ratios}
$\langle \kperp^2 \rangle_{g_1^u}/\langle \kperp^2 \rangle_{f_1^u}\approx 0.76$.
With the phenomenological value $\langle \kperp^2 \rangle_{f_1} = 0.25$ GeV$^2$ 
we then obtain the estimate for the width of the helicity TMD
$\langle \kperp^2 \rangle_{g_1} = 0.19$ GeV$^2$.
In our phenomenological study we use this value for $u$-quarks and for 
simplicity also for $d$-quarks. Even though the lattice values indicate 
an interesting flavor dependence, see Table~\ref{Table:Gauss-paramaters},
for a proton target this is a very good approximation due to $u$-quark 
dominance. When precision data for deuterium and especially for $^3$He
from Jefferson Lab become available, it will be interesting to 
re-investigate this point in detail.

\subsection{\boldmath Sivers function $f_{1T}^{\perp q}(x,k_\perp)$}
\label{App:basis-f1Tperp}

Sivers distribution function was studied in Refs.~\cite{Efremov:2004tp,Anselmino:2008sga,Anselmino:2011gs,Anselmino:2011ch, Aybat:2011ge,Gamberg:2013kla,Bacchetta:2011gx,Anselmino:2012aa,Sun:2013dya,Echevarria:2014xaa}. 
We will use parametrizations from  Refs.~\cite{Anselmino:2008sga,Anselmino:2011gs,Anselmino:2011ch}:
\ba
 \avkperp_{f_{1T}^\perp} &\equiv& \frac{\avkperp M_1^2}{\avkperp + M_1^2} \\
f_{1T}^{\perp}(x, \kperp^2)& =& - \frac {M}{M_1} \sqrt{2e} \;
{\cal N}_q(x) \, f_{q/p} (x,Q) \, \frac{e^{-\kperp^2/{\avkperp_{f_{1T}^\perp}}}}{\pi \avkperp} ,
\label{fiTp}
\ea
%
where $M_1$ is a mass parameter, $M$ the proton mass and
%
\ba
{\cal N}_q(x)= N_q \, x^{\alpha} (1-x)^{\beta} \,
\frac{(\alpha + \beta)^{(\alpha +\beta)}}
{\alpha^{\alpha} \beta^{\beta}}
 \ea
The first moment of Sivers function is:
\ba
f_{1T}^{\perp (1) q}(x)  = -\frac{\sqrt{\frac{e}{2}} \ \avkperp M_1^3}{M (\avkperp + M_1^2)^2}  \ {\cal N}_q(x)  f_q(x, Q) = -\sqrt{\frac{e}{2}} \frac{1}{M M_1}  \frac{\avkperp_{f_{1T}^\perp}^2}{\avkperp}    \ {\cal N}_q(x)  f_q(x, Q)
\label{siversm} \ .
\ea

We can rewrite parameterizations of Sivers functions as

\ba
f_{1T}^{\perp q}(x,\kperp) =  f_{1T}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{f_{1T}^\perp}^2} e^{-\kperp^2/{\avkperp_{f_{1T}^\perp}}}
\label{sivers_new} \ .
\ea

The fit the HERMES proton and COMPASS deuteron data from 
including only Sivers functions for $u$ and $d$ quarks was done in Ref.~\cite{Anselmino:2011gs},
corresponding to seven free parameters, and parameters are shown in Table~\ref{tab:a}.

\begin{table}
\centering
\begin{tabular}{ccc}
\hline
$N_u=0.40$ & $\alpha_u=0.35$ & $\beta_u=2.6$ \\
$N_d=-0.97$ & $\alpha_d=0.44$ & $\beta_d=0.90$\\
& $M_1^2=0.19\textrm{(GeV}^2$) &   \\
\hline
\end{tabular}
\caption{Best values of the fit of the Sivers functions. Table from Ref.~\cite{Anselmino:2011gs}}
\label{tab:a}
\end{table}

\subsection{\boldmath Transversity $h_{1}^{q}(x,k_\perp)$ and 
Collins function $H_{1}^{\perp q}(x,P_\perp)$}
\label{App:basis-h1-H1perp}

These functions were studied in  
Refs.~\cite{Anselmino:2007fs,Anselmino:2008jk,Anselmino:2013vqa,
Kang:2014zza,Kang:2015msa,Anselmino:2015sxa}.
The following shape was assumed for parametrizations 
Refs.~\cite{Anselmino:2007fs,Anselmino:2008jk,Anselmino:2013vqa}:
 \ba
h_{1}^{q} (x, \kperp^2) &=&h_{1}^{q} (x)  \frac{e^{-{\kperp^2}/{\avkperp_{h_1} }}}{\pi \avkperp_{h_1}} \; ,\label{tr-funct}\\
h_{1}^{q} (x) &=&\frac{1}{2} {\cal N}^{\T}_q(x)\,
[f_{1}(x)+g_1(x)]\; ,\\
H_{1 h/q}^{\perp}(z, \pperp^2) = \frac{z m_h}{2 \pperp} \Delta^N \! D_{h/q^\uparrow}(z,\pperp^2) &=&  \frac{z m_h}{M_C} e^{-p_{\perp}^2/M_C^2} \sqrt{2 e} H_{1 h/q}^{\perp}(z) \,\frac{e^{-\pperp^2/{\avpperp}}}{\pi \avpperp}\,,
\label{coll-funct}
 \ea
 with $m_h$ produced hadron mass and
 \ba
 {\cal N}^{\T}_q(x)= N^{\T}_q
\,x^{\alpha} (1-x)^{\beta} \, \frac{(\alpha + \beta)^{(\alpha
+\beta)}} {\alpha^{\alpha} \beta^{\beta}}\; ,
\\
H_{1 h/q}^{\perp}(z) =  {\cal N}^{\C}_q(z) D_{h/q}(z)\, , \\
{\cal N}^{\C}_q(z)= N^{\C}_q \, z^{\gamma} (1-z)^{\delta} \,
\frac{(\gamma + \delta)^{(\gamma +\delta)}}
{\gamma^{\gamma} \delta^{\delta}}\, ,
 \ea
and $-1\le N^{\T}_q\le 1$, $-1 \le N^{\C}_q \le 1$. The helicity distributions $g_1(x)$ are taken
from Ref.~\cite{Gluck:2000dy}, parton distribution and fragmentation functions are the GRV98LO PDF set~\cite{Gluck:1998xa} and the
DSS fragmentation function set~\cite{deFlorian:2007aj}. Notice that with these choices both
the transversity and the Collins function automatically obey their
proper positivity bounds. Note that as in Ref.~\cite{Anselmino:2013vqa} we use two 
Collins fragmentation functions, {\it favored} and {\it disfavored} ones, see Ref.~\cite{Anselmino:2013vqa} for details on implementation, and corresponding parameters ${N}^{\C}_a$ are then  ${N}^{\C}_{fav}$ and ${N}^{\C}_{dis}$. For numerical estimates we use parameters extracted in Ref.~\cite{Anselmino:2013vqa}, see Table~\ref{fitpar}.

\begin{table}[h]
\centering
\renewcommand{\tabcolsep}{0.4pc} % enlarge column spacing
\renewcommand{\arraystretch}{1.2} % enlarge line spacing
\begin{tabular}{@{ }ll}
 \hline
 $N_{u}^{\T}$ = $0.46^{+0.20}_{-0.14}$ & $N_{d}^{\T}$ = $ -1.00^{+1.17}_{-0.00}$ \\
 $\alpha$ =  $1.11^{+0.89}_{-0.66}$ & $\beta$  = $3.64^{+5.80}_{-3.37}$ \\
 $\avkperp_{h_1} = 0.25$ (GeV$^2$) & \\
 \hline
 $N_{\rm fav}^{\C}$  = $0.49^{+0.20}_{-0.18}$ & $N_{\rm dis}^{\C}$  = 
 $-1.00^{+0.38}_{-0.00}$ \\
 $\gamma$  = $1.06^{+0.45}_{-0.32}$  & $\delta$   = $0.07^{+0.42}_{-0.07}$    \\
 $M^2_C = 1.50^{+2.00}_{-1.12}$ (GeV$^2$) & \\
 \hline
\end{tabular}
\caption{
Best values of the 9 free parameters fixing the $u$ and $d$ quark
transversity distribution functions and the favored and
disfavored Collins fragmentation functions. The table is from Ref.~\cite{Anselmino:2013vqa}.
\label{fitpar}}
\end{table}

According to Eq.~(\ref{eq:moments}) we obtain the following expression for the first moment of 
Collins fragmentation function: 
\ba
H_{1 h/q}^{\perp (1)}(z) = \frac{H_{1 h/q}^{\perp}(z) \sqrt{e/2}  \avpperp M_C^3}{z m_h  (M_C^2+\avpperp)^2}\; .
\ea 
We also define the following variable:
\ba
\avpperp_{H_1^\perp} = \frac{\avpperp M_C^2 }{\avpperp + M_C^2} .  
\ea

We can rewrite the parameterizations of Collins FF as

\ba
H_{1}^{\perp}(z,\pperp) =  H_{1}^{\perp (1)}(z)   \frac{2 z^2 m_h^2}{\pi \avpperp_{H_{1}^\perp}^2} e^{-\pperp^2/{\avpperp_{H_{1}^\perp}}}
\label{coll-funct_new} \, .
\ea

\subsection{\boldmath Boer-Mulders function $h_{1}^{\perp}(x,k_\perp)$} 
\label{App:basis-h1perp}

The Boer-Mulders function $h_{1}^{\perp}$~\cite{Boer:1997nt} measures 
the transverse polarization asymmetry of quarks inside an unpolarized 
nucleon. The Boer-Mulders functions were studied phenomenologically in 
Refs.~\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa}

The following parameterization was used in Refs.~\cite{Barone:2015ksa}:
\ba
\avkperp_{h_1^\perp} &=& \frac{\avkperp \, M^2_{BM}}{\avkperp + M^2_{BM}} \, , \\
h_{1}^{\perp}(x, \kperp^2) &= &
- \,\frac{M}{M_{BM}}  
\sqrt{2e}\; N_q 
\, f_{q/p} (x, Q)\frac{e^{-\kperp^2/\avkperp_{h_{1}^{\perp}}}}{\pi\avkperp},  
\label{BM-dist}
\ea

The first moment of Boer-Mulders function is:
\ba
h_{1}^{\perp (1) q}(x)  = -\frac{\sqrt{\frac{e}{2}} \ \avkperp M_{BM}^3}{M (\avkperp + M_{BM}^2)^2}  \ {N}_q f_q(x, Q) = -\sqrt{\frac{e}{2}} \frac{1}{M M_{BM}}  \frac{\avkperp_{h_1^\perp}^2}{\avkperp}    \ {N}_q  f_q(x, Q)
\label{bm} \ .
\ea

We can rewrite parameterization of Boer-Mulders functions as

\ba
h_{1}^{\perp q}(x,\kperp) =  h_{1}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{h_{1}^\perp}^2} e^{-\kperp^2/{\avkperp_{h_{1}^\perp}}}\label{bm_new} \ .
\ea

%
\begin{table}[htb]
\centering
\begin{tabular}{l c l l c l}
\hline
 $N_{u}$ &=& $-0.49 \pm 0.15$ & $N_{d}$ &=& $-1 \pm 0.2$\\
 $M_{BM}^2$ &=& $0.1 \pm  0.2$&\multicolumn{3}{l}{(GeV$^2$)}\\ 
\hline
\end{tabular}
\caption{Fitted parameters of Boer-Mulders quark distributions. Values are from Ref.~\cite{Barone:2015ksa}}
\label{fitparbm}
\end{table}

\subsection{\boldmath Pretzelosity distribution $h_{1T}^{\perp}(x,k_\perp)$}
\label{App:basis-h1Tperp}

Pretzelosity   distribution function   
$h_{1T}^{\perp}$~\cite{Lefky:2014eia} describes transversely polarized quarks 
inside a transversely polarized nucleon.
We use the following form of $h_{1T}^{\perp a}$ ~\cite{Lefky:2014eia}:
\ba
h_{1T}^{\perp a}(x,k_{\perp}^2) = \frac{M^2}{M_{TT}^2} e^{-\kperp^2/M_{TT}^2} h^{\perp a}_{1T}(x) \frac{e^{-{\kperp^2}/{\avkperp}}}{\pi \avkperp}=\frac{M^2}{M_T^2} h^{\perp a}_{1T}(x) \frac{e^{-{\kperp^2}/{\avkperp_{h_{1T}^\perp}}}}{\pi \avkperp}\,\;,
\label{eq:h1Tperp}
\ea
where
\ba
h^{\perp a}_{1T}(x) = e  \ {\cal N}^a(x) (f_{1}^{a}(x, Q) - g_{1}^{a}(x, Q)), \label{eq:hx_par}\\
{\cal N}^a(x) = N^{a} x^{\alpha} (1-x)^{\beta} \frac{(\alpha + \beta)^{\alpha + \beta}}{\alpha^{\alpha} \beta^{\beta}}\, ,  \\
\avkperp_{h_{1T}^\perp}  = \frac{\avkperp M_{TT}^2}{\avkperp + M_{TT}^2}\, ,
\ea
where ${N}^a$, $\alpha$, $\beta$, and $M_T$ are parameters fitted to data that can be found in Table~\ref{fitparI}.

  We use Eq.~(\ref{eq:moments}) to calculate the second moment of $ h_{1T}^{\perp a}(x,\kperp^2)$
of Eq.~(\ref{eq:h1Tperp}) and obtain:
\be
h_{1T}^{\perp (2) a}(x) =  \frac{h^{\perp a}_{1T}(x) \avkperp_{h_{1T}^\perp}^3}{2 M^2 M_{TT}^2 \avkperp} \, .
\ee

We can rewrite parametrization of pretzelosity   functions as

\ba
h_{1T}^{\perp q}(x,\kperp) =  h_{1T}^{\perp (2) q}(x)   \frac{2 M^4}{\pi \avkperp_{h_{1T}^\perp}^3} e^{-\kperp^2/{\avkperp_{h_{1T}^\perp}}}
\label{pretzelosity_new} \ .
\ea

%
\begin{table}[htb]
\centering
\begin{tabular}{l c l l c l}
\hline
$\alpha$ &=& $2.5\pm1.5$ & $\beta$ &=& $2$ fixed \\
 $N_{u}$ &=& $1 \pm 1.4$ & $N_{d}$ &=& $-1 \pm 1.3$\\
 $M_{TT}^2$ &=& $0.18 \pm  0.7$&\multicolumn{3}{l}{(GeV$^2$)}\\ 
\hline
\end{tabular}
\caption{Fitted parameters of the pretzelosity quark distributions. Table from Ref.~\cite{Lefky:2014eia}}
\label{fitparI}
\end{table}
%

\newpage
\section{Convolution integrals and expressions in Gaussian Ansatz}}
\label{App:factor}

In this Appendix we explain the notation for convolution integrals
of TMDs and FFs and give the explicit results obtained assuming the
Gaussian Ansatz.

\subsection{Notation for convolution integrals \label{ApendixB1}}

Structure functions are expressed as convolutions of TMDs and FFs 
in the Bjorken limit at tree level. For reference we quote the 
convolution integrals in ``Amsterdam notation'' \cite{Bacchetta:2006tn}
\be
	{\cal C}\bigl[ w\slim f\slim D \bigr]
	=  x \, \sum_a e_a^2 \int d^2 {\bm p}_T \,  d^2 {\bm k}_T
	\, \delta^{(2)}\bigl({\bm p}_T - {\bm k}_T - {\bm P}_{h \perp}/z \bigr)
	\,w({\bm p}_T,{\bm k}_T)\,
	f^a( x ,p_T^2)\,D^a(z,z^2 k_T^2) , \label{eq:convolution-Amsterdam}
\ee
where all transverse momenta refer to the virtual photon-proton 
center-of-mass frame and $\bfhp  ={\bm P}_{h \perp}/{P}_{h\perp}$. 
Hereby ${\bm p}_T$ is 
the transverse momentum of quark with respect to nucleon, 
${\bm k}_T$ is the transverse momentum of the fragmenting quark 
with respect to produced hadron. The notation is not unique. 
The one chosen in this work, in comparison to other works, is 
\begin{alignat}{3} 
	\mbox{transverse momentum in TMD:}\;\;\;&
    	\left[\bfkperp\right]_{\rm our}
    &=& 	\left[{\bm k}_\perp\right]_{\mbox{\tiny Ref.\cite{Anselmino:2011ch}}} \;
    =  	\;\;\;\;\;\left[{\bm p}_T\right]_{\mbox{\tiny Ref.\cite{Bacchetta:2006tn}}}\,,
	\\
	\mbox{transverse momentum in \ FF:}\;\;\;&
	\left[\bfpperp\right]_{\rm our}
    &=& 	\left[{\bm p}_\perp\right]_{\mbox{\tiny Ref.\cite{Anselmino:2011ch}}} \;
    =  	-z\left[{\bm k}_T\right]_{\mbox{\tiny Ref.\cite{Bacchetta:2006tn}}}\,, 
	\\
	\mbox{transverse hadron momenta:}\;\;\;&
    	\left[\bfPhperp\right]_{\rm our}
    &=&	\left[{\bm P}_T\right]_{\mbox{\tiny Ref.\cite{Anselmino:2011ch}}} \;
    =  	\;\;\;\left[{\bm P}_{h\perp}\right]_{\mbox{\tiny Ref.\cite{Bacchetta:2006tn}}}\,.
\end{alignat}
Notice that 
$\left[\bfpperp\right]_{\rm our}=
-z\left[{\bm k}_T\right]_{\mbox{\tiny Ref.\cite{Bacchetta:2006tn}}}$ 
is the transverse momentum the hadron acquires in the fragmentation process.
The normalization for unpolarized fragmentation functions is 
\be
	D_1^a(z) 
	= \left[\,\int d^2{\bm P}_\perp D_1^a(z,P_\perp^2)\right]_{\rm our}
	= \left[z^2\int d^2{\bm k}_TD_1^a(z, z^2  k_T^2)
	  \right]_{\mbox{\tiny Ref.~\cite{Bacchetta:2006tn}}}
	\label{eq:D1}\;. 
\ee
The ``Amsterdam'' convolution integral (\ref{eq:convolution-Amsterdam})
reads in our notation
\be
	{\cal C}\bigl[ w\slim f\slim D \bigr]
	=  x \,
	\sum_a e_a^2 \int d^2 \bfkperp\,  d^2 \bfpperp^{ }
	\, \delta^{(2)}\bigl(z\bfkperp + \bfpperp - \bfPhperp \bigr)
	\,w\left(\bfkperp,-\frac{\bfpperp^{ }}{z}\right)
	f^a( x ,\kperp^2)\,D^a(z,\pperp^2) . \label{eq:convolution_our}
\ee

\subsection{Gaussian Ansatz}

For a generic TMD and FF the Gaussian Ansatz is given by 
\be
    f^a(x,\kperp^2)=
    f^a(x)\,\frac{\exp(-\kperp^2/\la\kperp^2\ra)}{\pi\la\kperp^2\ra}\,,\;\;\;
    D^a(z,\pperp^2)=
    D^a(z)\,\frac{\exp(-\pperp^2/\la\pperp^2\ra)}{\pi\la\pperp^2\ra}
\ee
where 
$\la\kperp^2\ra$ could be $x$-dependent,  
and $\la\pperp^2\ra$ $z$-dependent. 
Both could be flavor-dependent.
The variable $\pperp$ is convenient because phenomenological experience 
shows that $\pperp$ in $D_1^{q/h}(z,\pperp^2)$ exhibits a Gaussian distribution 
with weakly $z$-dependent Gaussian width. The distribution of transverse 
momenta in $\left[D^a(z,z^2 k_T^2)\right]_{\mbox{\tiny Ref.\cite{Bacchetta:2006tn}}}$ 
would require a strongly $z$-dependent Gaussian width. It is of course 
a matter of taste which one prefers to use.

It is convenient to work with transverse moments of TMDs and FFs
which are defined, and in the Gaussian model given by
\begin{alignat}{6}
	f^{(n)}(x) &=& \int d^2\bfkperp
	\left(\frac{\kperp^2}{2M^2}\right)^{\!\!n}\; f(x, \kperp^2)
	\;&\stackrel{\rm Gauss}{=}&\;
	\frac{n!\,\la \kperp^2\ra^n}{ 2^n\,M_N^{2n}}\, f(x),\;\;\;\nonumber\\
	D^{(n)}(z) &=& \int d^2\bfpperp
	\left(\frac{\pperp^2}{2 z^2 m_h^2}\right)^{\!\!n}\; D(z, \pperp^2)
	\;&\stackrel{\rm Gauss}{=}&\;
	\frac{n!\,\la \pperp^2\ra^n}{ 2^n_{ }z^{2n}_{ }\,m_{h}^{2n}} D(z)\,. \;\;\;
	\label{eq:moments}
\end{alignat}
It is important to keep in mind that these objects are well-defined
in the Gaussian model. However, in QCD and even in simple models
\cite{Avakian:2010br,Schweitzer:2012hh} one faces issues with UV 
divergences and has to carefully define how to deal with them. Results of Eqs.~(\ref{eq:moments}) assume that Gaussian dependence is factorized from $x$ or $z$ dependence and parametrizations are made with respect to either $f(x)$ or $D(z)$. As we saw in Appendix \ref{App:basis} some TMD functions are parametrized with higher moments directly as operator product expansion of TMDs may start from higher twist matrix element instead of the usual twist-2 one. In those cases equivalent formulas to Eqs.~(\ref{eq:moments}) can be easily derived.

\subsection{Convolution integrals in Gauss Ansatz}
\label{App:convol-details}

Solving the convolution integrals relevant for SIDIS in the 
Gaussian Ansatz yields 
\begin{subequations}\label{Eq:Gaussian-integrals-RAW}\ba
  {\cal C}\bigl[\;\omega^{\{0\}}\, f \, D \bigr]
    &=&	\phantom{-}\,u \;{\cal G}(\Phperp)\\
  {\cal C}\bigl[ \omega^{\{1\}}_{\rm A} \, f \, D \bigr]
    &=&	\phantom{-}\,u \;{\cal G}(\Phperp)\;
	\biggl(\frac{z\Phperp}{m_h}\biggr)\;\frac{\la\pperp^2\ra}{z^2\lambda}\\
  {\cal C}\bigl[\omega^{\{1\}}_{\rm B} \, f \, D \bigr]
    &=&	- \,u \;{\cal G}(\Phperp) \; 
	\biggl(\frac{z\Phperp}{M_N}\biggr)\;\frac{\la\kperp^2\ra}{\lambda}\\
  {\cal C}\bigl[ \omega^{\{2\}}_{\rm A} \, f \, D \bigr]
    &=&	\phantom{-}\,u \; {\cal G}(\Phperp)\;
	\frac{\la\kperp^2\ra\la\pperp^2\ra}{\lambda M_N m_h}
	\left(-1+\frac{2\Phperp^2}{\lambda}\right)\\
  {\cal C}\bigl[ \omega^{\{2\}}_{\rm B} \, f \, D \bigr]
    &=&	\phantom{-}\,u \; {\cal G}(\Phperp)\;
	\frac{\la\kperp^2\ra\la\pperp^2\ra}{\lambda M_N m_h}
	\left(1-\frac{\Phperp^2}{\lambda}\right)\\
  {\cal C}\bigl[ \, \omega^{\{2\}}_{\rm AB} \: f \, D \bigr]
    &=&	\phantom{-}\,u \; {\cal G}(\Phperp)\;
	\biggl(\frac{z\Phperp}{M_N}\biggr)
	\biggl(\frac{z\Phperp}{M_h}\biggr)
	\;\frac{\la\kperp^2\ra}{\lambda}
	\;\frac{\la\pperp^2\ra}{z^2\lambda}\\
  {\cal C}\bigl[ \, \omega^{\{2\}}_{\rm C} \: f \, D \bigr]
    &=&	\phantom{-}\,\frac{u}{2} \; {\cal G}(\Phperp)\;
	\biggl(\frac{z\Phperp}{M_N}\biggr)
	\biggl(\frac{z\Phperp}{M_N}\biggr)
	\;\frac{\la\kperp^2\ra}{\lambda}
	\;\frac{\la\kperp^2\ra}{\lambda}\\
  {\cal C}\bigl[ \, \omega^{\{3\}}_{\rm { }} \: f \, D \bigr]
    &=&	\phantom{-}\,\frac{u}{2} \; {\cal G}(\Phperp)\;
	\biggl(\frac{z\Phperp}{M_N}\biggr)
	\biggl(\frac{z\Phperp}{M_N}\biggr)
	\biggl(\frac{z\Phperp}{m_h}\biggr)
	\;\frac{\la\kperp^2\ra}{\lambda}
	\;\frac{\la\kperp^2\ra}{\lambda}
	\;\frac{\la\pperp^2\ra}{z^2\lambda} 
\ea\end{subequations}
with the $\omega^{\{n\}}_i$ as defined in Eq.~(\ref{Eq:wi}), 
and we introduced the abbreviations
\be
	u=x\,\sum_a e_a^2 f^a(x)D^a(z) \,, \;\;\;
	{\cal G}(\Phperp)=\frac{\exp(-\Phperp^2/\lambda)}{\pi\lambda}\,,\;\;\;
	\lambda = z^2\la\kperp^2\ra+\la\pperp^2\ra\,,
\ee
with the normalization $\int d^2\Phperp\,{\cal G}(\Phperp) = 1$.
It is important to keep in mind that strictly speaking 
${\cal G}(\Phperp) = {\cal G}(\Phperp,x,z)$ {\it also} depends
on $x$ and $z$.
The ``non-compact'' notation in Eqs.~(\ref{Eq:Gaussian-integrals-RAW}) 
was chosen to display the pattern. The masses $M_N$ or $m_h$ in the 
denominators of the $\Phperp$ indicate the ``origins'' of the
contributions: due to intrinsic $\kperp$ from target, due to 
transverse momenta $\pperp$ acquired during fragmentation, or both.
The weight $\omega^{\{2\}}_{\rm B}$ is the only which enters
cross sections and does not have a homogeneous scaling in $\Phperp$.

For practical application it is convenient to absorb as many 
(Gauss model) parameters as possible into expressions that can
be more easily fitted to data. One way to achieve this is to make 
use of the transverse moments (\ref{eq:moments}). 
We introduce the following abbreviations
\begin{alignat}{6}
u^{\{1\}}_{\rm A} 	&=& \;x\,\sum_a e_a^2 f^{   a}(x)D^{(1)a}(z) \,, &\hspace{1cm}&
u^{\{1\}}_{\rm B} 	&=& \;x\,\sum_a e_a^2 f^{(1)a}(x)D^{   a}(z) \,, \\
u^{\{2\}}_{\rm AB}	&=& \;x\,\sum_a e_a^2 f^{(1)a}(x)D^{(1)a}(z) \,, &\hspace{1cm}&
u^{\{2\}}_{\rm C}	&=& \;x\,\sum_a e_a^2 f^{(2)a}(x)D^{   a}(z) \,, \\
u^{\{3\}}_{\rm C}	&=& \;x\,\sum_a e_a^2 f^{(2)a}(x)D^{(1)a}(z) \,. &\hspace{1cm}& &&
\end{alignat}
In this notation the results in Eqs.~(\ref{Eq:Gaussian-integrals-RAW}) 
read 
\begin{subequations}\label{Eq:Gaussian-integrals-working}\ba
  {\cal C}\bigl[ \omega^{\{1\}}_{\rm A} \, f \, D \bigr]
    &=&	\phantom{-}\,u^{(1)}_{\rm A} \;{\cal G}(\Phperp)\;
	\biggl(\frac{z\Phperp}{m_h}\biggr)\;\frac{2m_h^2}{\lambda}\\
  {\cal C}\bigl[ \omega^{\{1\}}_{\rm B} \, f \, D \bigr]
    &=&	- \,u^{(1)}_{\rm B} \;{\cal G}(\Phperp) \; 
	\biggl(\frac{z\Phperp}{M_N}\biggr)\;\frac{2M_N^2}{\lambda}\\
  {\cal C}\bigl[ \omega^{\{2\}}_{\rm B} \, f \, D \bigr]
    &=&	\phantom{-}\, u^{(2)}_{\rm B}\; {\cal G}(\Phperp)\;
	\frac{4z^2 m_h\,M_N}{\lambda}
	\left(1-\frac{\Phperp^2}{\lambda}\right)\\
  {\cal C}\bigl[ \, \omega^{\{2\}}_{\rm AB} \: f \, D \bigr]
    &=&	\phantom{-}\,u^{(2)}_{\rm AB} \; {\cal G}(\Phperp)\;
	\biggl(\frac{z\Phperp}{M_N}\biggr)
	\biggl(\frac{z\Phperp}{M_h}\biggr)
	\;\frac{2M_N^2}{\lambda}
	\;\frac{2m_h^2}{\lambda}\\
  {\cal C}\bigl[ \, \omega^{\{2\}}_{\rm C} \: f \, D \bigr]
    &=&	\phantom{-}\,\frac{u^{(2)}_{\rm C}}{2} \; {\cal G}(\Phperp)\;
	\biggl(\frac{z\Phperp}{M_N}\biggr)
	\biggl(\frac{z\Phperp}{M_N}\biggr)
	\;\frac{2M_N^2}{\lambda}
	\;\frac{2M_N^2}{\lambda}\\
  {\cal C}\bigl[ \, \omega^{\{3\}}_{\rm { }} \: f \, D \bigr]
    &=&	\phantom{-}\,\frac{u^{(3)}_{\rm  }}{2} \; {\cal G}(\Phperp)\;
	\biggl(\frac{z\Phperp}{M_N}\biggr)
	\biggl(\frac{z\Phperp}{M_N}\biggr)
	\biggl(\frac{z\Phperp}{m_h}\biggr)
	\;\frac{2M_N^2}{\lambda}
	\;\frac{2M_N^2}{\lambda}
	\;\frac{2m_h^2}{\lambda} 
\ea\end{subequations}
In this notation the results in Eqs.~(\ref{Eq:Gaussian-integrals-RAW}) 
read 
\be
	{\cal C}\bigl[ \omega^{\{n\}}_{i} \, f \, D \bigr]
	= u^{(n)}_{i} \;{\cal G}(\Phperp)\;\times
	\left[
	\delta_{n2}\,\delta_{i\rm B}\;a^{(2)}_{B} + b^{(n)}_{i} 
	\left(\frac{z\Phperp}{\lambda}\right)^{\!\!n}\;\right]
\ee
with
\begin{alignat}{7}
	b^{(0)}_{\rm  } 	&= 1 \, , \\
	b^{(1)}_{\rm A} 	&= 2m_h	\, , &
	b^{(1)}_{\rm B} 	&= 2M_N	\, , \\
	a^{(2)}_{\rm B}	&= 4M_Nm_h\lambda^{-1}\,z^2  \, , \;\;\;\;\;\; & 
	b^{(2)}_{\rm AB} 	&= -\,b^{(2)}_{\rm B}
			 = 4M_Nm_h 	\, , \;\;\;\;\;\; & 
	b^{(2)}_{\rm C} 	&= M_N^2  \, ,\\
	b^{(3)}_{\rm  } 	&= 2M_N^2m_h \, .
	\label{Eq:Gaussian-integrals-working-III}
\end{alignat}
Finally, integrating out transverse hadron momenta yields
\be
	\int d^2\Phperp\;
	{\cal C}\bigl[\,\omega^{\{n\}}_{i} \, f \, D \bigr] 
	= u^{(n)}_{i} \;c^{(n)}_{i}\;\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!n}
\ee
with
\begin{alignat}{7}
	c^{(0)}_{\rm  } 	&= 1 \, , \\
	c^{(1)}_{\rm A} 	&= \sqrt{\pi}\,m_h	\, , &
	c^{(1)}_{\rm A} 	&= \sqrt{\pi}\,M_N	\, , \\
	c^{(2)}_{\rm AB} 	&= 4M_Nm_h		\, , \;\;\;\;\;\; & 
	c^{(2)}_{\rm C} 	&= M_N^2 		\, , \;\;\;\;\;\;\;\;\;\; & 
	c^{(2)}_{\rm B}	&= 0 			\, ,\\
	c^{(3)}_{\rm  } 	&= {\textstyle\frac32}\sqrt{\pi} \,M_N^2m_h 
	\, . \;\;\;     &
			&
	\label{Eq:Gaussian-integrals-working-III}
\end{alignat}

 \bibliography{\BibPath/biblio_ww}

\newpage
\section*{Remarks  \& Corrections in version 00r (PS) {}}

\begin{itemize}

\item	I reshuffled some subsections with good intentions.
	Please, see whether you like it.

\item	Introduced a new procedure: first assume Gauss Ansatz,
	then evaluate convolution integrals, finally use WW.
	This gives \blue{\bf different} results from Saman \& Alexei.\\
	Advantages: \\
	1. The results can be written in a compact way.\\
	2. There is less model dependence due to the simpler expressions.\\
	3. In the new expressions it is more natural to incorporate the 
	sum rules (\ref{Eq:sum-rules-T-odd}) for T-odd twist-3 functions.

\item   The numerical results are obtained with 
	DSS'07 and GRV'00 and GRSV'98.
	DSS is 10 years old. GRSV is from last millennium.
	I agree that DSS is acceptable (if we do not touch kaons). 
	However, we should use a more modern input for $f_1^q(x)$ and 
	$g_1^q(x)$ (even though I know and understand that it does not matter).

\item 	I introduced 
	{\textbackslash}begin\{subequations\} $\dots$
	{\textbackslash}end\{subequations\}. Notice that it comes
	before equations arrays start and after they end, and it can
	contain text in-between.

\item	notation: in all(?) formulas 
	{\{{\textbackslash}bf $\dots$\}} changed to
	{\{{\textbackslash}bm $\dots$\}} \\
	${\bm \xi}_T$ changed to ${\bm \xi}_\perp$ in 
	Eqs.~(\ref{Eq:correlator},~\ref{Eq:correlator-FF})
	(Fourier variables of ${\bm k}_\perp$, ${\bm p}_\perp$)\\
	In Eq.~(\ref{Eq:correlator-FF}) the integration is over
	$\xi^+$ (not $\xi^-$), and $(-\infty)\to(+\infty)$.

\item	more serious: in Eq.~(\ref{Eq:correlator-FF}) replacement 
	${\bm p}_\perp = \bfpperp$ was wrong. Correct:
	${\bm p}_\perp = -\bfpperp/z$.
	Because of that we have corrections
	$\pperp^k\to - \pperp^k/z$ in 
	(\ref{eq:DeltaTr-twist-2b},
	 \ref{eq:DeltaTr-twist-3b},
	 \ref{eq:DeltaTr-twist-3c},
	 \ref{Eq:WW-type-FF-4}). \\
	Luckily no influence on numerical results. \red{Please, double check 
	(\ref{eq:DeltaTr-twist-2a}-\ref{eq:DeltaTr-twist-3c})!}

\item	in several places correction $D_q^h(z)\to D_1^q(z)$, \\
	correction $H^\perp(z,\pperp^2) \to H(z,\pperp^2)$
	in (\ref{Eq:WW-type-FF-4})

\item	after Eq.~(\ref{Eq:TMD-pdfs-VI}) changed
	$\epsilon_T^{ij}\equiv\epsilon^{-+ij}$ to
	$\epsilon^{ij}\equiv\epsilon^{-+ij}$
	(we use throughout $\epsilon^{ij}$)

\item 	corrected sign of term with $f_T^\perp$ in (\ref{Eq:sub-TMD-pdfs-III}). 
	Should be negative. Compare to \cite{Bacchetta:2006tn}.

\item	corrected sign typos in 
	Eq.~(\ref{FUTsinphiS}) (term with $\tilde{D}^\perp$) and 
	Eq.~(\ref{FLTsin(2phi-phiS)}) (term with $\tilde{G}^\perp$)\\
	Both drop out in WW, so no consequence.

\item 	the figure names \\ {\tt
	ALLcosPhi\_x.pdf, ALLcosPhi\_PT.pdf,  \\
  	ALTcos2Phi\_x.pdf, ALTcos2Phi\_PT.pdf, \\
  	AULsinPhi\_x.pdf, AULsinPhi\_PT.pdf} \\
	were spelled incorrectly (in latex source: {\tt Phi}. Name of file
	{\tt phi}).\\
	Fixed in latex file, names of figures are unchanged.

\item	We should not show predictions for JLab 12,
	but compare to available data. Often we will have huge error bars.
	Then we can say that JLab 12 will resolve the situation.

\item	Often we write $M$ or $M_N$ and mean the nucleon mass.
	I would prefer $M_N$ but writing $M$ everywhere would be less work.
	We write sometimes $H^\perp(z,\pperp^2)$ and sometimes
	$H^\perp(z,\pperp)$, etc. We have to agree on a common notation. 
	I propose without square.

{}
\end{itemize}

\end{document}

\subsubsection*{Old review-type text from $A_{UU}^{\cos\phi}$, 
to be saved partially?}

The asymmetry $A_{UU}^{\cos\phi}$ was measured in several experiments,
such as EMC \cite{Aubert:1983cz}, and more recently also at JLab 
\cite{Osipenko:2008aa,Mkrtchyan:2007sr}, HERMES \cite{Giordano:2009hi} 
and COMPASS \cite{Joosten:2009zz}.
The asymmetry was also subject to several theoretical studies.
In our context it is of interest to review two of them in some more 
detail, namely Refs.~\cite{Anselmino:2005nn} and \cite{Schweitzer:2010tt}.

In Ref.~\cite{Anselmino:2005nn} it was assumed that the EMC data on 
$A_{UU}^{\cos\phi}$ is due to the Cahn effect only, and on the basis 
of this assumption, the Gaussian widths of $f_1^a(x,\kperp)$ and 
$D_1^a(z,\pperp)$ were extracted from the EMC data \cite{Aubert:1983cz}.
In the WW-type approximation, the EMC data contain also contributions 
from the Boer-Mulders effect, see Eq.~(\ref{Eq:WW-type-FUUcosphi}). 
There are two reasons, why one may neglect this contribution with
a presumably good approximation \cite{Schweitzer:2010tt}.
First, one may expect it to be less dominant than the Cahn effect
contribution because the Boer-Mulders and Collins functions
are required by positivity inequalities to be smaller than
$f_1^a$ and $D_1^a$, and phenomenologically $h_1^{\perp a}$ 
and $H_1^{\perp a}$ are both observed to be clearly smaller than
the respectively allowed upper bounds.
Moreover, EMC has not detected specific final state hadrons, 
but summed over all charged hadrons. In such sums the Collins 
effect for positive and negative pions tends to cancel out largely.
Charged pions yield the main part of charged hadrons, and the 
Collins effect of for instance kaons is observed to be small.
Therefore, the analysis of the EMC data of \cite{Anselmino:2005nn}
gives insights mainly on the transverse momentum dependencies of 
$f_1^a$ and $D_1^a$, {\sl provided} the WW-type approximation holds.

In contrast to this in \cite{Schweitzer:2010tt} recent data
on cross sections and mean transverse hadron momenta 
from Jefferson Lab \cite{Osipenko:2008aa,Mkrtchyan:2007sr} and HERMES 
\cite{Airapetian:2009jy} were studied. The results from 
\cite{Schweitzer:2010tt} were also shown to be compatible
with COMPASS data, see \cite{Rajotte:2010ir}. The important
point is that the analysis of \cite{Schweitzer:2010tt} was free
of any WW-type-approximations. Nevertheless, the phenomenological
numbers from the studies \cite{Anselmino:2005nn} and
\cite{Schweitzer:2010tt} are in good agreement
(and both results are also supported by lattice QCD),
see Sec.~\ref{Sec-5.1:FUU-basis}.
The agreement of \cite{Anselmino:2005nn} and \cite{Schweitzer:2010tt}
indicates that the neglect of $\bar qgq$-terms in $A_{UU}^{\cos\phi}$ 
is, at least in the kinematics of the EMC experiment and within the
accuracy of that data \cite{Aubert:1983cz}, 
a useful assumption.

It is necessary to make one cautious comment though. In the EMC experiment
the data were taken with a $280\,{\rm GeV}$ muon beam, and one expects
$\kperp$-broadening effects \cite{Schweitzer:2010tt,Aybat:2011zv} as compared 
to HERMES or JLab energies. Without considering evolution effects,
one obtains a good agreement of the descriptions of HERMES and EMC data
with the same parameter set, see Fig.~\ref{Fig-02:EMC}.
If one takes these effects phenomenologically \cite{Schweitzer:2010tt}
or rigorously \cite{Aybat:2011zv} into account, one would expect
the theoretical curve in Fig.~\ref{Fig-02:EMC} to
overshoot the data by about $30\,\%$. This would indicate that the
$\bar qgq$-terms in this observable could about about $30\,\%$.
We stress that we would not expect WW-type approximations to
work better then that.
\PS{We probably can considerably shorten this lengthy review section
to 2--3 sentences. Any objections?}

{}

\newpage
\section{Convolution integrals and expressions in Gaussian Ansatz (OLD)}
\label{App:factor-old}

In this Appendix we explain the notation for convolution integrals
of TMDs and FFs and give the explicit results obtained assuming the
Gaussian Ansatz.

\subsection{Notation for convolution integrals \label{old-ApendixB1}}

Parton interpretation of structure functions can be obtained as convolution of distribution and fragmentation functions \cite{Mulders:1995dh,Bacchetta:2006tn,Anselmino:2011ch}
\be
{\cal C}\bigl[ w\slim f\slim D \bigr]
=  x \,
\sum_a e_a^2 \int d^2 {\bm p}_T \,  d^2 {\bm k}_T
\, \delta^{(2)}\bigl({\bm p}_T - {\bm k}_T - {\bm P}_{h \perp}/z \bigr)
\,w({\bm p}_T,{\bm k}_T)\,
f^a( x ,p_T^2)\,D^a(z,z^2 k_T^2) ,
\label{old-eq:convolution}
\ee
and the unit vector is defined as $\bfhp  ={\bm P}_{h \perp}/{P}_{h
  \perp}$, here ${\bm p}_T$ is the transverse momentum of quark with respect to the proton, ${\bm k}_T$ is the transverse momentum of fragmenting quark with respect to the produced hadron, and  $- {\bm P}_{h \perp}/z \simeq {\bm q}_T$ the transverse momentum of the virtual photon; these momenta are defined in ``target - produced hadron" cm frame.

Fragmentation function have probabilistic interpretation with respect to transverse momentum of produced hadron with respect to the fragmenting quark 
\be
{\bm P}_\perp\simeq -{z}\; {\bm k}_T\;,
\ee
so that for unpolarized fragmentation function one has
\be
D_{1 q/h}(z) \equiv  \int d^2 {\bm P}_\perp D_{1 q/h}(z, P_\perp^2) = z^2 \int d^2 {\bm k}_T D_{1 q/h}(z, z^2  k_T^2) \label{old-eq:D1}\;.
\ee
Experimental measurements are usually given in the photon-proton cm frame in which we can rewrite Eq.(\ref{old-eq:convolution}) using ``physical'' vector $ {\bm P}_\perp$
\be
{\cal C}\bigl[ w\slim f\slim D \bigr]
=  x \,
\sum_a e_a^2 \int d^2 \bfkperp\,  d^2 \bfpperp^{ }
\, \delta^{(2)}\bigl(z\bfkperp + \bfpperp - \bfPhperp \bigr)
\,w\left(\bfkperp,-\frac{\bfpperp^{ }}{z}\right)\,
f^a( x ,\kperp^2)\,D^a(z,\pperp^2) ,
\label{old-eq:convolution_our}
\ee
integrating $\delta$ function we obtain
\be
{\cal C}\bigl[ w\slim f\slim D \bigr]
=  x \,
\sum_a e_a^2 \int d^2 \bfkperp\, 
\, 
\,w\left(\bfkperp,-\frac{\left({\bm P}_{h \perp} - z\bfkperp\right)}{z}\right)\,
f^a( x ,\kperp^2)\,D^a\left(z,({\bm P}_{h \perp} - z\bfkperp)^2\right) .
\label{old-eq:convolution_our_main}
\ee

The notations of our paper can be readily compared to notations of other papers, such as Ref.~\cite{Anselmino:2011ch}, for instance, where $\bfpperp |_{our} \equiv {\bm p}_\perp |${\cite{Anselmino:2011ch}} and $\bfkperp |_{our} \equiv {\bm k}_\perp${\cite{Anselmino:2011ch}}.

We are using the following definitions of moments of TMDs
\ba
f^{(n)}(x) &=& \int d^2 \bfkperp \left(\frac{\kperp^2}{2M^2}\right)^n f(x, \kperp^2)\;, \\
D^{(n)}(z) &=& \int d^2 \bfpperp \left(\frac{\pperp^2}{2 z^2 m_h^2}\right)^n D(z, \pperp^2)\; .
\label{old-eq:moments}
\ea

\subsection{Gaussian factors}

The gaussian factor for $F_{UU}$:

\be
{ \cal G}_{UU}(x,z,\Phperp ) = \frac{1}{\pi \la \Phperp^2 \ra}e^{-\Phperp^2/\la \Phperp^2 \ra}, \; \la \Phperp^2 \ra =  z^2 \avkperp + \avpperp .
\label{old-eq:factor_fuu}
\ee

The gaussian factor for $F_{LL}$:

\be
{ \cal G}_{LL}(x,z,\Phperp ) = \frac{1}{\pi \la \Phperp^2 \ra_{g_1}}e^{-\Phperp^2/\la \Phperp^2 \ra_{g_1}}, \; \la \Phperp^2 \ra_{g_1} =  z^2 \avkperp_{g_1} + \avpperp .
\label{old-eq:factor_fll}
\ee

The gaussian factors for $F_{LT}^{\cos(\phi_h-\phi_S)}$:

\be
{ \cal G}_{LT}(x,z,\Phperp ) = \frac{M^2}{\pi \la \Phperp^2 \ra_{g_{1T}^\perp}^2}e^{-\Phperp^2/\la \Phperp^2 \ra_{g_{1T}^\perp}}, \; \la \Phperp^2 \ra_{g_{1T}^\perp} =  z^2 \avkperp_{g_{1T}^\perp} + \avpperp .
\label{old-eq:factor_flt}
\ee

\be
{\cal A}_{LT}^{\cos(\phi_h -\phi_S)} = \frac{M
z \sqrt{\pi}}{\sqrt{\la \Phperp^2 \ra_{g_{1T}^\perp}}} .
\label{old-eq:factor_aflt}
\ee

The gaussian factors for $F_{UL}^{\sin(2\phi_h)}$:
\be
{ \cal G}_{UL}^{\sin(2\phi_h)}(x,z,\Phperp ) = \frac{M^4}{\pi \la \Phperp^2 \ra_{h_{1L}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1L}^\perp}}, \; \la \Phperp^2 \ra_{h_{1L}^\perp} =  z^2 \avkperp_{h_{1L}^\perp} + \avpperp_{H_1^\perp} .
\label{old-eq:factor_hlt}
\ee

\be
{\cal A}_{UL}^{\sin(2\phi_h)} = \frac{4 m_h M 
z^2}{ \la \Phperp^2 \ra_{h_{1L}^\perp}} .
\label{old-eq:factor_ahlt}
\ee

The gaussian factors for $F_{UT}^{\sin(\phi_h+\phi_S)}$:
\be
{ \cal G}_{UT}^{\sin(\phi_h+\phi_S)}(x,z,\Phperp ) = \frac{M^2}{\pi \la \Phperp^2 \ra_{h_{1}}^2}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1}}}, \; \la \Phperp^2 \ra_{h_{1}} =  z^2 \avkperp_{h_{1}} + \avpperp_{H_1^\perp} .
\label{old-eq:factor_h1}
\ee

\be
{\cal A}_{UT}^{\sin(\phi_h+\phi_S)} = \frac{m_h 
z \sqrt{\pi}}{ \sqrt{\la \Phperp^2 \ra_{h_{1}}}} .
\label{old-eq:factor_ah1}
\ee

The gaussian factors for $F_{UT}^{\sin(\phi_h-\phi_S)}$:
\be
{ \cal G}_{UT}^{\sin(\phi_h-\phi_S)}(x,z,\Phperp ) = \frac{M^2}{\pi \la \Phperp^2 \ra_{f_{1T}^\perp}^2}e^{-\Phperp^2/\la \Phperp^2 \ra_{f_{1T}^\perp}}, \; \la \Phperp^2 \ra_{f_{1T}^\perp} =  z^2 \avkperp_{f_{1T}^\perp} + \avpperp .
\label{old-eq:factor_f1t}
\ee

\be
{\cal A}_{UT}^{\sin(\phi_h-\phi_S)} = \frac{M 
z \sqrt{\pi}}{ \sqrt{\la \Phperp^2 \ra_{f_{1T}^\perp}}} .
\label{old-eq:factor_af1t}
\ee

The gaussian factors for $F_{UT}^{\sin(3 \phi_h-\phi_S)}$:
\be
{ \cal G}_{UT}^{\sin(3 \phi_h-\phi_S)}(x,z,\Phperp ) = \frac{M^4 \avkperp_{h_{1T}^\perp}}{\pi \la \Phperp^2 \ra_{h_{1T}^\perp}^4}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1T}^\perp}}, \; \la \Phperp^2 \ra_{h_{1T}^\perp} =  z^2 \avkperp_{h_{1T}^\perp} + \avpperp_{H_1^\perp} .
\label{old-eq:factor_h1tp}
\ee

\be
{\cal A}_{UT}^{\sin(3 \phi_h-\phi_S)} = \frac{3 m_h \avkperp_{h_{1T}^\perp}
z^3  \sqrt{\pi}}{ 2 \sqrt{\la \Phperp^2 \ra_{f_{1T}^\perp}^3}} .
\label{old-eq:factor_ah1tp}
\ee

The gaussian factors for $F_{UU}^{\cos(2\phi_h)}$:
\be
{ \cal G}_{UU}^{\cos(2\phi_h)}(x,z,\Phperp ) = \frac{M^4}{\pi \la \Phperp^2 \ra_{h_{1}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1}^\perp}}, \; \la \Phperp^2 \ra_{h_{1}^\perp} =  z^2 \avkperp_{h_{1}^\perp} + \avpperp_{H_1^\perp} .
\label{old-eq:factor_h1perp}
\ee

\be
{\cal A}_{UU}^{\cos(2\phi_h)} = \frac{4 m_h M 
z^2}{ \la \Phperp^2 \ra_{h_{1}^\perp}} .
\label{old-eq:factor_ah1perp}
\ee

The gaussian factor for $F_{LT}^{\cos\phi_S}$:
\be
{ \cal G}_{LT}^{\cos\phi_S}(x,z,\Phperp ) = \frac{z^2\avkperp_{g_{1T}^\perp} (\Phperp^2+\avpperp) + \avpperp^2}{\pi \la \Phperp^2 \ra_{g_{1T}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{g_{1T}^\perp}}, \; \la \Phperp^2 \ra_{g_{1T}^\perp} =  z^2 \avkperp_{g_{1T}^\perp} + \avpperp .
\label{old-eq:factor_gltcosphi}
\ee

The gaussian factors for $F_{UL}^{\sin \phi_h}$:
\ba
{ \cal G}_{UL}^{\sin \phi_h}(x,z,\Phperp ) &=& \frac{4 M^2 \left(z^2\avkperp_{h_{1L}^\perp} (\Phperp^2-z^2\avkperp_{h_{1L}^\perp}) + \avpperp^2_{H_1^\perp}\right)}{\pi \la \Phperp^2 \ra_{h_{1L}^\perp}^4}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1L}^\perp}}, \nonumber \\
\la \Phperp^2 \ra_{h_{1L}^\perp} &= & z^2 \avkperp_{h_{1L}^\perp} + \avpperp_{H_1^\perp}  .
\label{old-eq:factor_gulsinphi}
\ea

\be
{\cal A}_{UL}^{\sin \phi_h} = \frac{m_h  
z \sqrt{\pi} \left(2 \avpperp_{H_1^\perp} + z^2 \avkperp_{h_{1L}^\perp}\right)} { \sqrt{\la \Phperp^2 \ra_{h_{1L}^\perp}^3 }} \; .
\label{old-eq:factor_aulsinphi}
\ee

The gaussian factors for $F_{LL}^{\cos\phi_h}$:
\be
{ \cal G}_{LL}^{\cos\phi_h}(x,z,\Phperp ) =\frac{\avkperp_{g_{1}}}{\pi \la \Phperp^2 \ra_{g_{1}}^2}e^{-\Phperp^2/\la \Phperp^2 \ra_{g_{1}}}, 
\la \Phperp^2 \ra_{g_{1}} =  z^2 \avkperp_{g_{1}} + \avpperp .
\label{old-eq:factor_gllcosphi}
\ee

\be
{\cal A}_{LL}^{\cos\phi_h} = \frac{
z \sqrt{\pi} \avkperp_{g_{1}}}{ 2 M \sqrt{\la \Phperp^2 \ra_{g_{1}}}} .
\label{old-eq:factor_allcosphi}
\ee

  The gaussian factors for $F_{LT}^{\cos(2\phi_h-\phi_S)}$:

\be
{ \cal G}_{LT}^{\cos(2\phi_h-\phi_S)}(x,z,\Phperp ) = \frac{M^2 \avkperp_{g_{1T}^\perp}}{\pi \la \Phperp^2 \ra_{g_{1T}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{g_{1T}^\perp}}, \; \la \Phperp^2 \ra_{g_{1T}^\perp} =  z^2 \avkperp_{g_{1T}^\perp} + \avpperp .
\label{old-eq:factor_gltcos2phi}
\ee

\be
{\cal A}_{LT}^{\cos(2\phi_h -\phi_S)} = \frac{M^2 \avkperp_{g_{1T}^\perp}
z^2 }{ \la \Phperp^2 \ra_{g_{1T}^\perp}} .
\label{old-eq:factor_altcos2phi}
\ee

The gaussian factors for $F_{UU}^{\cos \phi_h}$:

\ba
{ \cal G}_{UU1}^{\cos \phi_h}(x,z,\Phperp ) = \frac{ 4 M^2 (\avpperp_{H_{1}^\perp}+z^2 \avkperp_{h_{1}^\perp} (  \Phperp^2  -z^2\avkperp_{h_{1}^\perp} ) }{\pi \la \Phperp^2 \ra_{h_{1}^\perp}^4}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1}^\perp}}, \nonumber \\
\; \la \Phperp^2 \ra_{h_{1}^\perp} =  z^2 \avkperp_{h_{1}^\perp} + \avpperp_{H_{1}^\perp} .
\label{old-eq:factor_guucosphi1}
\ea

\be
{\cal A}_{UU1}^{\cos \phi_h} = \frac{m_h  
z \sqrt{\pi} \left(2 \avpperp_{H_1^\perp} + z^2 \avkperp_{h_{1}^\perp}\right)} { \sqrt{\la \Phperp^2 \ra_{h_{1}^\perp}^3 }} \; .
\label{old-eq:factor_auucosphi1}
\ee

\be
{ \cal G}_{UU2}^{\cos\phi_h}(x,z,\Phperp ) =\frac{\avkperp}{\pi \la \Phperp^2 \ra^2}e^{-\Phperp^2/\la \Phperp^2 \ra}, \la \Phperp^2 \ra =  z^2 \avkperp + \avpperp .
\label{old-eq:factor_guucosphi2}
\ee

\be
{\cal A}_{UU2}^{\cos\phi_h} = \frac{
z \sqrt{\pi} \avkperp}{ 2 M \sqrt{\la \Phperp^2 \ra}} .
\label{old-eq:factor_auucosphi2}
\ee

The gaussian factors for $F_{UT}^{\sin\phi_S}$:
\ba
{ \cal G}_{UT1}^{\sin\phi_S}(x,z,\Phperp ) = \frac{z^2\avkperp_{f_{1T}^\perp} \left(\Phperp^2+\avpperp\right) + \avpperp^2}{\pi \la \Phperp^2 \ra_{f_{1T}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{f_{1T}^\perp}}, \nonumber \\
\; \la \Phperp^2 \ra_{f_{1T}^\perp} =  z^2 \avkperp_{f_{1T}^\perp} + \avpperp .
\label{old-eq:factor_gutsinphi1}
\ea

\be
{ \cal G}_{UT2}^{\sin\phi_S}(x,z,\Phperp ) = \frac{\avkperp_{h_{1}} \left(-\Phperp^2+\la \Phperp^2 \ra_{h_{1}}\right)}{\pi \la \Phperp^2 \ra_{h_{1}}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1}}}, \; \la \Phperp^2 \ra_{h_{1}} =  z^2 \avkperp_{h_{1}} + \avpperp_{H_{1}^\perp} .
\label{old-eq:factor_gutsinphi2}
\ee

The gaussian factors for $F_{UT}^{\sin( 2\phi_h -\phi_S)}$:

\ba
{ \cal G}_{UT1}^{\sin( 2\phi_h -\phi_S)}(x,z,\Phperp ) = \frac{M^2 \avkperp_{f_{1T}^\perp}  }{\pi \la \Phperp^2 \ra_{f_{1T}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{f_{1T}^\perp}}, \; \nonumber \\
 \la \Phperp^2 \ra_{f_{1T}^\perp} =  z^2 \avkperp_{f_{1T}^\perp} + \avpperp. \nonumber \\
\label{old-eq:factor_gutsin2phi1}
\ea

\be
{\cal A}_{UT1}^{\sin( 2\phi_h -\phi_S)} = \frac{
z^2 \avkperp_{f_{1T}^\perp}}{  \la \Phperp^2 \ra_{f_{1T}^\perp}} \; .
\label{old-eq:factor_autsin2phi1}
\ee

\ba
{ \cal G}_{UT2}^{\sin( 2\phi_h -\phi_S)}(x,z,\Phperp ) =  \frac{ 2 M^2 m_h \avkperp_{h_{1T}^\perp} \left(2 \avpperp_{H_{1}^\perp}^2+z^2 \avkperp_{h_{1T}^\perp} \left(  \Phperp^2  + \avpperp_{H_{1}^\perp} \right) - z^4 \avkperp_{h_{1T}^\perp}^2 \right) }{\pi \la \Phperp^2 \ra_{h_{1T}^\perp}^5} \times \nonumber \\ e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1T}^\perp}}, \nonumber \\ 
\; \la \Phperp^2 \ra_{h_{1T}^\perp} =  z^2 \avkperp_{h_{1T}^\perp} + \avpperp_{H_{1}^\perp} \nonumber \\ 
\label{old-eq:factor_gutsin2phi2}
\ea

\be
{\cal A}_{UT2}^{\sin( 2\phi_h -\phi_S)} =  \frac{2 m_h  M
z^2 \avkperp_{h_{1T}^\perp} \left(2 \avpperp_{H_1^\perp} + z^2 \avkperp_{h_{1T}^\perp}\right)} { \la \Phperp^2 \ra_{h_{1T}^\perp}^2 }.
\label{old-eq:factor_autsin2phi2}
\ee

{}

\newpage

### 2018-01-04 tex/test-WW-type-00s-PS.tex
alexei

@@
 	D^\perp(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}
-	& \hspace{11mm}z\,D_1(z,\pperp)\,, \label{Eq:WW-type-FF-3}\\
+	& \hspace{11mm}z\,D_1(z,\pperp^2)\,, \label{Eq:WW-type-FF-3}\\
 	H(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}& 
-	-\frac{\pperp^2}{zM_h^2}\;H_1^\perp(z,\pperp)\,. \label{Eq:WW-type-FF-4}
+	-\frac{\pperp^2}{zM_h^2}\;H_1^\perp(z,\pperp^2)\,. \label{Eq:WW-type-FF-4}
 \ea\end{subequations}
@@
 have no collinear counterparts, and we consider their (1)-moments, while 
-for $ h_{1T}^{\perp a}$  we consider the (2)-moment, see App.~\ref{App:basis} for details.
+for $ h_{1T}^{\perp a}$  we consider the (2)-moment,
+such that parametrizations of TMD functions read
+\begin{subequations}\ba
+f^a_1(x,\kperp^2) &=& f^a_1(x)\;
+    \frac{e^{-\kperp^2/\avkperp_{f_1}}}{\pi\avkperp_{f_1}} \, ,\\
+    D^a_1(z,\pperp^2) &=& D_1^a(z)\,
+    \frac{e^{-\pperp^2/\avpperp_{D_1}}}{\pi\avpperp_{D_1}} \, ,\\
+g^a_1(x,\kperp^2) &=& g^a_1(x)\;
+    \frac{e^{-\kperp^2/\avkperp_{g_1}}}{\pi\avkperp_{g_1}} \, ,\\    
+f_{1T}^{\perp q}(x,\kperp^2) &=&  f_{1T}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{f_{1T}^\perp}^2} e^{-\kperp^2/{\avkperp_{f_{1T}^\perp}}} \, ,\\
+h_{1}^{q} (x, \kperp^2) &=&h_{1}^{q} (x)  \frac{e^{-{\kperp^2}/{\avkperp_{h_1} }}}{\pi \avkperp_{h_1}}\, ,\\
+H_{1}^{\perp}(z,\pperp^2) &=&  H_{1}^{\perp (1)}(z)   \frac{2 z^2 m_h^2}{\pi \avpperp_{H_{1}^\perp}^2} e^{-\pperp^2/{\avpperp_{H_{1}^\perp}}}\, ,\\
+h_{1}^{\perp q}(x,\kperp^2) &=&  h_{1}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{h_{1}^\perp}^2} e^{-\kperp^2/{\avkperp_{h_{1}^\perp}}}\, ,\\
+h_{1T}^{\perp q}(x,\kperp^2) &=&  h_{1T}^{\perp (2) q}(x)   \frac{2 M^4}{\pi \avkperp_{h_{1T}^\perp}^3} e^{-\kperp^2/{\avkperp_{h_{1T}^\perp}}} \, ,
+\ea\end{subequations}
+see App.~\ref{App:basis} for details.
 
@@
 $\la x\ra  =0.15$, $\la z\ra  =0.22$ for $\pi^+$ production on the proton target.
+In Fig.~\ref{FUU-show-pT-dependence} (c) we plot COMPASS multiplicity \cite{Aghasyan:2017ctw}
+\be
+n^h(x,z,\Phperp)  \equiv \pi \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
+\ee
+at $\la Q^2\ra=20\,{\rm GeV}^2$,
+$\la x\ra  =0.15$, $\la z\ra  =0.2$ for $h^+$ production on the deuterium target.
 
@@
 \includegraphics[width=0.37\textwidth]{\FigPath/hermes_pip.pdf} (b)
+\includegraphics[width=0.37\textwidth]{\FigPath/compass_hp.pdf} (c)
 \caption{\label{FUU-show-pT-dependence}
@@
 following Ref.~\cite{Schweitzer:2010tt}.
-(b) Example for HERMES multiplicities at $\la Q^2\ra=2.87\,{\rm GeV}^2$,
-$\la x\ra  =0.15$, $\la z\ra  =0.22$.}
+(b) Example for HERMES multiplicities \cite{Airapetian:2012ki} at $\la Q^2\ra=2.87\,{\rm GeV}^2$,
+$\la x\ra  =0.15$, $\la z\ra  =0.22$.
+(b) Example for COMPASS multiplicities \cite{Aghasyan:2017ctw} at $\la Q^2\ra=20\,{\rm GeV}^2$,
+$\la x\ra  =0.15$, $\la z\ra  =0.2$.}
 \end{figure}
@@
 \caption{\label{jlab_ALL} 
-	$p_2 A_{LL}$ asymmetry compared with Jefferson Lab experimental 
+	$A_{LL,\la y\ra}$ asymmetry compared with Jefferson Lab experimental 
 	results Ref.~\cite{Avakian:2010ae} for $\pi^+$ (left panel) and 
@@
 The asymmetries $A_{UT}^{\sin(\phi_h-\phi_S)}= F_{UT}^{\sin(\phi_h-\phi_S)}/F_{UU}$  
-for Jefferson Lab 12 GeV are plotted in Fig.~\ref{aut_f1t_jlab}.
-
-\PS{\bf (We should plot here HERMES and/or COMPASS data, two samples
-just for illustrative purposes. We can add a comment that Jefferson Lab 12
-data will significantly improve the experimental constraints.)}
+and comparison to HERMES data \cite{Airapetian:2009ae} are plotted in Fig.~\ref{aut_f1t_jlab}.
 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_PT.pdf}
-\caption{\label{aut_f1t_jlab} $A_{UT}^{\sin(\phi_h-\phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+\caption{\label{aut_f1t_jlab} Comparison of calculation of $A_{UT}^{\sin(\phi_h-\phi_S)}$  using fit results of Ref.~\cite{Anselmino:2011gs} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ and HERMES data \cite{Airapetian:2009ae}.
 }
@@
 
-Asymmetries $A_{UT}^{\sin(\phi_h+\phi_S)}=F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$
-for Jefferson Lab 12 GeV are plotted in Fig.~\ref{aut_h1_jlab}.
-
-\PS{\bf (We should plot here HERMES and/or COMPASS data, two samples
-just for illustrative purposes. We can add a comment that Jefferson Lab 12
-data will significantly improve the experimental constraints.)}
+The asymmetries $A_{UT}^{\sin(\phi_h+\phi_S)}=F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$
+and comparison to HERMES data \cite{Airapetian:2010ds} are plotted in Fig.~\ref{aut_h1_jlab}.
 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_PT.pdf}
-\caption{\label{aut_h1_jlab} $A_{UT}^{\sin(\phi_h+\phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+\caption{\label{aut_h1_jlab} Comparison of calculation of $A_{UT}^{\sin(\phi_h+\phi_S)}$  using fit results of Ref.~\cite{Anselmino:2013vqa} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ and HERMES data \cite{Airapetian:2009ae}.
 }
@@
 where $\lambda=z^2 \avkperp_{h_1^\perp} + \avpperp_{H_1^\perp}$ and
-$b^{(2)}_{\rm AB}=\red{4}M_Nm_h$ and $c^{(2)}_{\rm AB} = 4M_Nm_h$,
+$b^{(2)}_{\rm AB}=4M_Nm_h$ and $c^{(2)}_{\rm AB} = 4M_Nm_h$,
 see App.~\ref{App:convol-details}.
-
-Asymmetries $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$  for  
-Jefferson Lab 12 GeV are plotted in Fig.~\ref{auu_cos2phi_jlab}.
 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_PT.pdf}
-\caption{\label{auu_cos2phi_jlab} $A_{UU}^{\cos(2\phi_h)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+\caption{\label{auu_cos2phi_jlab} Comparison of calculation of $A_{UU}^{\cos(2\phi_h)}$  using fit results of Ref.~\cite{Barone:2015ksa} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ and HERMES data \cite{Giordano:2009hi}.
 }
@@
 
-\PS{\bf (We should plot here HERMES and/or COMPASS data, two samples
-just for illustrative purposes. We can add a comment that Jefferson Lab 12
-data will significantly improve the experimental constraints. I would also
-skip the Cahn effect for simplicity, and add a comment of the following
-kind:)}
-
-In the (to be updated) Fig.~\ref{auu_cos2phi_jlab} we plot only the
+Asymmetries $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$  for  
+HERMES are plotted in Fig.~\ref{auu_cos2phi_jlab}.
+In the Fig.~\ref{auu_cos2phi_jlab} we plot only the
 Boer-Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$ which does not describe
@@
 	&=& x\sum_q e_q^2\,h_{1T}^{\perp (2) q}(x)\,H_1^{\perp(1)q}(z)\;  
-	c^{(3)}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!\red{3}}\,,
+	c^{(3)}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{3}\,,
 \ea\end{subequations}
 where $\lambda=z^2 \avkperp_{h_{1T}^\perp} + \avpperp_{H_1^\perp}$ and
-$b^{(3)}=2M_N^2m_h$ and $c^{(3)}_{\rm  } = 3\sqrt{\pi} \,M_N^2m_h$,
+$b^{(3)}=2M_N^2m_h$ and $c^{(3)}_{\rm  } = 3/2\sqrt{\pi} \,M_N^2m_h$,
 see App.~\ref{App:convol-details}.
@@
 Asymmetries $A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ for 
-Jefferson Lab 12 GeV are plotted in Fig.~\ref{aut_h1tp_jlab}.
-
-\
-
-\PS{\bf (We should plot here COMPASS data for illustrative purposes. 
-I would propose to add a comment of the type:)}
-
-\
-
+COMPASS data \cite{Parsamyan:2010se} are plotted in Fig.~\ref{aut_h1tp_jlab}.
 Clearly, the pretzelosity TMD is the least known of the basis TMDs.
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_PT.pdf}
-\caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+\caption{\label{aut_h1tp_jlab}  Comparison of calculation of $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  using fit results of Ref.~\cite{Lefky:2014eia} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ and preliminary COMPASS data \cite{Parsamyan:2010se}.
 }
@@
 	$u$- and $d$-flavor. 
-	\PS{\bf (Please, remove sea quarks in left panel).}}
+}
 \end{figure}
@@
 \ee
-which the parametrizations for $f^{\perp q}_{1T}$ and $g^{\perp q}_{1T}$
-used in this work of course satisfy \PS{\bf (do they??)}.
+so that one has
+\be
+\frac{f_{1}^{q}(x)^2}{16\pi M^2} - \frac{f_{1T}^{\perp q}(x)^2}{4\pi \avkperp_{f_{1T}^\perp} } -
+\frac{g_{1T}^{\perp q}(x)^2}{4\pi \avkperp_{g_{1T}^\perp} } \ge 0
+\label{eq:positivity}
+\ee
+see Fig.~\ref{g1t_pos}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/g1t_positivity.pdf}  
+	\caption{\label{g1t_pos} 
+	LHS of Eq.~\eqref{eq:positivity}.
+}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/ALT_x.pdf}  
-\includegraphics[width=0.45\textwidth]{\FigPath/ALT_PT.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/ALT_COMPASS_x.pdf}  
 	\caption{\label{g1t_jlab} 
-	$A_{LT}^{\cos(\phi_h -\phi_S)}$  as a function of $ x $ (left panel), 
-	and as a function of $P_{hT}$ (right panel) at typical kinematics 
-	of Jefferson Lab 12 GeV, 
+	$A_{LT}^{\cos(\phi_h -\phi_S)}$  as a function of $ x $  at typical kinematics 
+	of COMPASS, 
 	$\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
@@
 
-The asymmetry  $A_{LT}^{\cos(\phi_h -\phi_S)}$ as a function of $x$ and $P_{hT}$ 
-for Jefferson Lab 12 GeV is plotted in Fig.~\ref{g1t_jlab}.
+The asymmetry  $A_{LT}^{\cos(\phi_h -\phi_S)}$ as a function of $x$  
+for COMPASS is plotted in Fig.~\ref{g1t_jlab}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_x.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_PT.pdf}
-	\caption{\label{aul_jlab} 
-	$A_{UL}^{\sin(2\phi_h)}$  as a function of $ x $ (left panel), and   
-	as a function of $P_{hT}$ (right panel) at typical kinematics of 
-	Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, 
-	$\la Q^2\ra = 2.4$ GeV$^2$.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 We assume Gaussian form for Kotzinian-Mulders function $h_{1L}^{\perp a}$:
@@
 asymmetry $\avkperp_{h_{1L}^\perp} = \avkperp_{h_{1}} = 0.25$ (GeV$^2$).
-Notice that the Boer-Mulders function and $h^{\perp q}_{1L}$ obey the
+Notice that the Kotzinian-Mulders function and $h^{\perp q}_{1L}$ obey the
 positivity bound \cite{Bacchetta:1999kz}
@@
 \ee
+so that one has
+\be
+\frac{f_{1}^{q}(x)^2}{16\pi M^2} - \frac{h_{1}^{\perp q}(x)^2}{4\pi \avkperp_{h_{1}^\perp} } -
+\frac{h_{1L}^{\perp q}(x)^2}{4\pi \avkperp_{h_{1TL}^\perp} } \ge 0
+\label{eq:positivity1}
+\ee
+which is plottde in Fig.~\ref{h1l_pos}.
+Notice that for $d$-quark the positivity is violated that may be due to the big Boer-Mulders $d$-quark function from Ref.~\cite{Barone:2015ksa}.
+As far as determination of the size of Boer-Mulders functions is far from ideal, we cautiously keep the present result.
+Future determinations of Boer-Mulders functions will help to clarify the issue of positivity constraints.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/h1lperp_positivity.pdf}  
+	\caption{\label{h1l_pos} 
+	LHS of Eq.~\eqref{eq:positivity1}.
+}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_COMPASS_x.pdf}  
+	\caption{\label{aul_jlab} 
+	$A_{UL}^{\sin(2\phi_h)}$  as a function of $ x $  at typical kinematics 
+	of COMPASS, 
+	$\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+	}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%
 \newpage
@@
 \section{Acknowledgments}
-This work was partially supported by the U.S.\
-Department of Energy under Contract No.~DE-AC05-06OR23177 (A.P.) and by the National Science Foundation
-under Contract No. PHY-1623454 (A.P.).
+The authors would like to thank their families for the constant support during work on this project. This work was partially supported by the U.S.\
+Department of Energy under Contract No.~DE-AC05-06OR23177 (A.P.) and by the National Science Foundation under Contract No. PHY-1623454 (A.P.).
 
@@
 \item	I reshuffled some subsections with good intentions.
-	Please, see whether you like it.
+	Please, see whether you like it. {\color{red} AP good for me}
 
@@
 	sum rules (\ref{Eq:sum-rules-T-odd}) for T-odd twist-3 functions.
+	{\color{red} AP good for me, we need to expand a little on differences with the previous version.}
 
@@
 	$g_1^q(x)$ (even though I know and understand that it does not matter).
+	 {\color{red} AP good for me, I implemented MRSTW instead.}
 
@@
 	before equations arrays start and after they end, and it can
-	contain text in-between.
+	contain text in-between.  {\color{red} AP good for me}
 
@@
 	In Eq.~(\ref{Eq:correlator-FF}) the integration is over
-	$\xi^+$ (not $\xi^-$), and $(-\infty)\to(+\infty)$.
+	$\xi^+$ (not $\xi^-$), and $(-\infty)\to(+\infty)$.  {\color{red} AP good for me}
 
@@
 	Luckily no influence on numerical results. \red{Please, double check 
-	(\ref{eq:DeltaTr-twist-2a}-\ref{eq:DeltaTr-twist-3c})!}
+	(\ref{eq:DeltaTr-twist-2a}-\ref{eq:DeltaTr-twist-3c})!}  {\color{red} AP have no time, anybody?}
 
@@
 	correction $H^\perp(z,\pperp^2) \to H(z,\pperp^2)$
-	in (\ref{Eq:WW-type-FF-4})
+	in (\ref{Eq:WW-type-FF-4})  {\color{red} AP good for me}
 
@@
 	$\epsilon^{ij}\equiv\epsilon^{-+ij}$
-	(we use throughout $\epsilon^{ij}$)
+	(we use throughout $\epsilon^{ij}$)  {\color{red} AP good for me}
 
 \item 	corrected sign of term with $f_T^\perp$ in (\ref{Eq:sub-TMD-pdfs-III}). 
-	Should be negative. Compare to \cite{Bacchetta:2006tn}.
+	Should be negative. Compare to \cite{Bacchetta:2006tn}.   {\color{red} AP good for me, thank you}
 
@@
 	Eq.~(\ref{FLTsin(2phi-phiS)}) (term with $\tilde{G}^\perp$)\\
-	Both drop out in WW, so no consequence.
+	Both drop out in WW, so no consequence.  {\color{red} AP good for me}
 
@@
 	{\tt phi}).\\
-	Fixed in latex file, names of figures are unchanged.
+	Fixed in latex file, names of figures are unchanged.  {\color{red} AP good for me}
 
@@
 	but compare to available data. Often we will have huge error bars.
-	Then we can say that JLab 12 will resolve the situation.
+	Then we can say that JLab 12 will resolve the situation.  {\color{red} AP good for me, I change that}
 
@@
 	$H^\perp(z,\pperp)$, etc. We have to agree on a common notation. 
-	I propose without square.
+	I propose without square.  {\color{red} AP good for me, I prefer $H^\perp(z,\pperp^2)$}
 

### 2018-01-05 tex/test-WW-type-00s-PS.tex
alexei

@@
 
+The $F_{UT}^{\sin(\phi_h-\phi_S)}$ modulation of SIDIS cross section is related to  the Sivers function~\cite{Sivers:1989cc}, which describes the number density of unpolarized quarks inside a 
+transversely polarized proton, has so far received the widest attention, 
+from both phenomenological and experimental points of view.
+
+The Sivers function $f_{1T}^\perp$ is related to initial and final state interactions of the struck quark and the rest of the nucleon and could not exist 
+without the contribution of the orbital angular momentum of partons to the spin of the nucleon. 
+As such it encodes the correlation between the partonic intrinsic motion and the transverse spin of the nucleon, and it generates a dipole deformation in momentum space.
+
+Over the years, the Sivers function has been extracted from SIDIS data
+by several groups, with consistent results 
+\cite{Anselmino:2010bs,Anselmino:2005ea,Anselmino:2005an,Collins:2005ie,Vogelsang:2005cs,Anselmino:2008sga,Bacchetta:2011gx,Echevarria:2014xaa}.
+
 The structure function $F_{UT}^{\sin(\phi_h-\phi_S)}$ reads
@@
 \label{Sec-5.4:Collins-basis}
+
+The $F_{UT}^{\sin(\phi_h+\phi_S)}$ modulation of the SIDIS cross section is due to convolution of the transversity distribution $h_1$, which is the only source of information on the tensor charge of the
+nucleon, and the Collins FF $H_1^\perp$, that decodes the fundamental correlation between
+the transverse spin of a fragmenting quark and the transverse momentum
+of the final produced hadron.
+
+There are many extractions of $h_1$ and $H_1^\perp$ from a combined fit of SIDIS and $e^+e^-$ data, for instance those of Refs.~\cite{Anselmino:2013vqa,Kang:2014zza,Anselmino:2015sxa}.
 
@@
 \be
-\frac{f_{1}^{q}(x)^2}{16\pi M^2} - \frac{f_{1T}^{\perp q}(x)^2}{4\pi \avkperp_{f_{1T}^\perp} } -
-\frac{g_{1T}^{\perp q}(x)^2}{4\pi \avkperp_{g_{1T}^\perp} } \ge 0
+\frac{(f_{1}^{q}(x))^2}{16\pi M^2} - \frac{(f_{1T}^{\perp q}(x))^2}{4\pi \avkperp_{f_{1T}^\perp} } -
+\frac{(g_{1T}^{\perp q}(x))^2}{4\pi \avkperp_{g_{1T}^\perp} } \ge 0
 \label{eq:positivity}
@@
 	of COMPASS, 
-	$\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$.
 	\newline\PS{Can we compare here to COMPASS data from 
@@
 \be
-\frac{f_{1}^{q}(x)^2}{16\pi M^2} - \frac{h_{1}^{\perp q}(x)^2}{4\pi \avkperp_{h_{1}^\perp} } -
-\frac{h_{1L}^{\perp q}(x)^2}{4\pi \avkperp_{h_{1TL}^\perp} } \ge 0
+\frac{(f_{1}^{q}(x))^2}{16\pi M^2} - \frac{(h_{1}^{\perp q}(x))^2}{4\pi \avkperp_{h_{1}^\perp} } -
+\frac{(h_{1L}^{\perp q}(x))^2}{4\pi \avkperp_{h_{1TL}^\perp} } \ge 0
 \label{eq:positivity1}
@@
 	of COMPASS, 
-	$\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$.
 	}
@@
 \ea\end{subequations}
+{\color{blue} AP - I disagree with \ref{Eq:FLTcosphiS-Gauss} see my notes}
 with the width $\lambda= z^2 \avkperp_{g_T} + \avpperp_{D_1}$
@@
 The asymmetries $A_{LL}^{\cos\phi_S}=F_{LL}^{\cos\phi_S}/F_{UU}$  for 
-Jefferson Lab 12 GeV are plotted in Fig.~\ref{allcosphi_jlab}.
+COMPASS are plotted in Fig.~\ref{allcosphi_jlab}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
+\begin{figure}[h!]
 \centering
-\includegraphics[width=0.4\textwidth]{figs/ALLcosphi_x.pdf} 
-\includegraphics[width=0.4\textwidth]{figs/ALLcosphi_PT.pdf}
-\caption{\label{allcosphi_jlab} $A_{LL}^{\cos\phi_h}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+\includegraphics[width=0.45\textwidth]{\FigPath/ALLcosphi_COMPASS_x.pdf}  
+	\caption{\label{allcosphi_jlab} 
+	$A_{LL}^{\cos(\phi_h)}$  as a function of $ x $  at typical kinematics 
+	of COMPASS, 
+	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$.
 	}
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%
 

### 2018-01-07 tex/test-WW-type-00s-PS.tex
alexei

@@
 see App.~\ref{App:convol-details} for details.
-We remind that $g^{\perp q}_{1T}$ and the Sivers function are both 
+The $g^{\perp q}_{1T}$ and the Sivers function $f^{\perp q}_{1T}$ are both 
 constrained by the positivity bound \cite{Bacchetta:1999kz} 
@@
 \ee
-so that one has
+so that using our Gaussian parametrizations from Eqs.~(\ref{Eq:Gauss-f1-D1},\ref{eq:g1t},\ref{sivers_new}) one has
 \be
@@
 \ee
-see Fig.~\ref{g1t_pos}.
+see Fig.~\ref{g1t_pos} where RHS of this equation multiplied by $16\pi M^2$ is shown.
 
@@
 \ee
-so that one has
+so that using our Gaussian parametrizations from Eqs.~(\ref{Eq:Gauss-f1-D1},\ref{eq:h1l_final},\ref{bm_new})  one has
 \be
@@
 \ee
-which is plottde in Fig.~\ref{h1l_pos}.
+which, multiplied by $16\pi M^2$,  is plotted in Fig.~\ref{h1l_pos}.
 Notice that for $d$-quark the positivity is violated that may be due to the big Boer-Mulders $d$-quark function from Ref.~\cite{Barone:2015ksa}.
@@
 Secs.~\ref{Sec-3.4:WW-classic-experiment} and \ref{Sec-5.1:FUU-basis}.
-Assuming the Gaussian Ansatz for $g_T^a(x,\kperp)$ yields for the
-structure function 
+
+We assume the Gaussian Ansatz for $g_T^a(x,\kperp)$ 
+\be
+	g^{q}_{T}(x,\kperp^2) = 
+	g^{q}_{T}(x)\,\frac{1}{\pi \avkperp_{g_{T}}}\,
+	e^{-\kperp^2/{\avkperp_{g_{T}}}}\;,
+	\label{eq:gtnew}
+\ee
+where $g^{q}_{T}(x)$ is calculated according to Eq.~\ref{Eq:WW-original1}.
+Notice that we could have used WW-type relation of Eq.~(\ref{Eq:WW-type-6}) to relate $g^{q}_{T}(x,\kperp^2)$
+and $g^{\perp q}_{1T}(x,\kperp^2)$ however we choose not to do it. In fact Eq.~(\ref{Eq:WW-type-6}) suggests kinematical zero 
+$g^{q}_{T}(x, 0) = 0$  which is not supported by the model calculations \cite{Avakian:2010br} and thus  Eq.~(\ref{Eq:WW-type-6}) can be used only in its integrated form. 
+The Eq.~(\ref{Eq:WW-type-6}) is not exact and is not on the same footing as WW-approximation of Eq.~(\ref{Eq:WW-original1}), and we parametrize directly $g^{q}_{T}(x,\kperp^2)$ using the Gaussian shape.
+For illustrative purpose we show ``violation'' of  Eq.~(\ref{Eq:WW-type-6}) in Fig.~\ref{altcosphi_wwtype}.
+
+$F_{LT}^{\cos\phi_S}$
+structure function then reads 
 \begin{subequations}\ba
@@
 \ea\end{subequations}
-{\color{blue} AP - I disagree with \ref{Eq:FLTcosphiS-Gauss} see my notes}
 with the width $\lambda= z^2 \avkperp_{g_T} + \avpperp_{D_1}$
@@
 Asymmetries $A_{LT}^{\cos\phi_S} = F_{LT}^{\cos\phi_S}/F_{UU}$ for 
-Jefferson Lab 12 GeV are plotted in Fig.~\ref{altcosphi_jlab}.
+COMPASS are plotted in Fig.~\ref{altcosphi_jlab}.
 Notice that the asymmetry scales at small transverse hadron
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/ALTcosPhi_x.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/ALTcosPhi_PT.pdf}
-\caption{\label{altcosphi_jlab} $A_{LT}^{\cos\phi_S}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+\includegraphics[width=0.45\textwidth]{\FigPath/ALTcosPhi_COMPASS_x.pdf} 
+\caption{\label{altcosphi_jlab} $A_{LT}^{\cos\phi_S}$  as a function of $ x $.
+}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+ %%%%%%%%%%%%%
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/gT_vs_g1Tperp_wwtype.pdf} 
+\caption{\label{altcosphi_wwtype} RHS and LHS of Eq.~\ref{Eq:WW-type-6}.
 }

### 2018-01-07 tex/test-WW-type-00s-PS.tex
alexei

@@
 and finally express $h_{1L}^{\perp(1)q}(x)$ in terms of $h_1^a(x)$
-using (\ref{Eq:WW-approx-h1L}).
-
-The asymmetries $A_{UL}^{\sin\phi_h}=F_{UL}^{\sin\phi_h}/F_{UU}$  for 
-Jefferson Lab 12 GeV are plotted in Fig.~\ref{aulsinphi_jlab}.
-
-\ \\
-\PS{See especially \cite{Airapetian:2005jc} where contaminations
-from transverse target polarization have been tediously removed!
-Have to compare to those VERY CLEAN data!}
+using (\ref{Eq:WW-approx-h1L}). $h_{1L}^{\perp(1)q}(x)$  is shown in Fig.~\ref{g1t_h1l_functions}.
+
+The asymmetries $A_{UL}^{\sin\phi_h}=F_{UL}^{\sin\phi_h}/F_{UU}$  as a function of $x$  
+for COMPASS is plotted in Fig.~\ref{aulsinphi_jlab} (a). We also compare our calculations to HERMES data \cite{Airapetian:2005jc} in Fig.~\ref{aulsinphi_jlab} (b).
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_x.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_PT.pdf}
-\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf} (a)
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf} (b)
+\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $  for COMPASS (a), and  comparison to HERMES data \cite{Airapetian:2005jc} (b).
 }

### 2018-01-09 tex/test-WW-type-00s-PS.tex
alexei

@@
 Retaining the only non-zero term in the WW-type approximation, and
-assuming for $h_L^q(x,\kperp)$ a Gaussian Ansatz, we obtain
+assuming for $h_L^q(x,\kperp)$ a Gaussian Ansatz 
+\be
+h_L^q(x,\kperp^2) = h_L^q(x) \,\frac{1}{\pi \avkperp_{h_{L}}}\,
+	e^{-\kperp^2/{\avkperp_{h_{L}}}}\;,
+	\label{eq:hLnew}
+\ee
+we obtain
 for the structure function 
@@
 \be
-	xh_L^q(x) = h_{1L}^{\perp(1)q}(x)
+	xh_L^q(x) = -2 h_{1L}^{\perp(1)q}(x)
 \ee
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf} (a)
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf} (b)
-\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $  for COMPASS (a), and  comparison to HERMES data \cite{Airapetian:2005jc} (b).
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf} (a)
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf} (b)
+\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $ , comparison to HERMES data \cite{Airapetian:2005jc} (a), and predictions for COMPASS (b).
 }
@@
 Retaining the only non-zero term in the WW-type approximation, and
-assuming for $g_T^{\perp a}(x,\kperp)$ a Gaussian Ansatz, we obtain
+assuming for $g_T^{\perp a}(x,\kperp)$ a Gaussian Ansatz
+\be
+	g^{\perp q}_{T}(x,\kperp^2) = 
+	g^{\perp (2) q}_{T}(x)\,\frac{2 M^4}{\pi \avkperp^3_{g_{T}^{\perp} }}\,
+	e^{-\kperp^2/{\avkperp_{g_{T}^{\perp} }}}\;,
+	\label{eq:gtperpnew}
+\ee
+We estimate $\avkperp_{g_{T}^\perp}=\avkperp_{g_1}$ and explore
+the WW-type approximation (\ref{Eq:WW-type-gTperp}), 
+\be
+	xg_T^{\perp(2)q}(x) = \frac{\la\kperp^2\ra_{g_{1T}^\perp}}{M_N^2}\;
+	g_{1T}^{\perp (1)q}(x)\,,
+\ee
+where we finally express $g_{1T}^{\perp (1)q}(x)$ in terms of $g_1^q(x)$ 
+according to Eq.~(\ref{Eq:WW-approx-g1T}).
+
+We obtain
 for the structure function 
@@
 	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\Phperp) 
-	&=& \red{-}x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\; 
+	&=& -\frac{2M}{Q} x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\; 
 	b^{(2)}_{C}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\,
@@
 	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\la\Phperp\ra) 
-	&=& \red{-}x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\;  
+	&=& -\frac{2M}{Q} x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\;  
 	c^{(2)}_{C}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!2}\,
@@
 see App.~\ref{App:convol-details} for details.
-We estimate $\avkperp_{g_{T}^\perp}=\avkperp_{g_1}$ and explore
-the WW-type approximation (\ref{Eq:WW-type-gTperp}), 
-\be
-	xg_T^{\perp(2)q}(x) = \frac{\la\kperp^2\ra_{g_{1T}^\perp}}{M_N^2}\;
-	g_{1T}^{\perp (1)q}(x)\,,
-\ee
-where we finally express $g_{1T}^{\perp (1)q}(x)$ in terms of $g_1^q(x)$ 
-according to Eq.~(\ref{Eq:WW-approx-g1T}).
 
 The asymmetry  $A_{LT}^{\cos(\phi_h -\phi_S)}=F_{LT}^{\cos(\phi_h -\phi_S)}/F_{UU}$ 
-as a function of $x$ and $P_{hT}$ for Jefferson Lab 12 GeV is plotted in 
+as a function of $x$ and $P_{hT}$ for COMPASS is plotted in 
 Fig.~\ref{altcos2phi_jlab}.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/ALTcos2phi_x.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/ALTcos2phi_PT.pdf}
-\caption{\label{altcos2phi_jlab} $A_{LT}^{\cos(2\phi_h - \phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+\includegraphics[width=0.45\textwidth]{\FigPath/ALTcos2PhiminusPhiS_COMPASS_x.pdf} 
+\caption{\label{altcos2phi_jlab} $A_{LT}^{\cos(2\phi_h - \phi_S)}$  as a function of $ x $ for COMPASS.
 }

### 2018-01-09 tex/test-WW-type-00s-PS.tex
alexei

@@
 $f_T^q(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
+\begin{subequations}
+\be
+f_T^q(x,\kperp^2) = f_T^q(x) \,\frac{1}{\pi \avkperp_{f_{T}}}\,
+	e^{-\kperp^2/{\avkperp_{f_{T}}}}\;,
+	\label{eq:fTnew}
+\ee
+\be
+h_T^{\perp q}(x,\kperp^2) =h_T^{\perp (1) q}(x) \,\frac{2 M^2}{\pi \avkperp_{h_{T}^\perp}^2}\,
+	e^{-\kperp^2/{\avkperp_{h_{T}^\perp}}}\;,
+	\label{eq:hTperpnew}
+\ee
+\be
+h_T^{q}(x,\kperp^2) =h_T^{(1) q}(x) \,\frac{2 M^2}{\pi \avkperp_{h_{T}}^2}\,
+	e^{-\kperp^2/{\avkperp_{h_{T}}}}\;,
+	\label{eq:hTnew}
+\ee
+\end{subequations}
 we obtain 
@@
 The asymmetries $A_{UT}^{\sin\phi_S}=F_{UT}^{\sin\phi_S}/F_{UU}$  for 
-Jefferson Lab 12 GeV are plotted in Fig.~\ref{autsinphi_jlab}.
+COMPASS are plotted in Fig.~\ref{autsinphi_jlab}.
 \PS{Compare to HERMES data \cite{Schnell:2010zza}?
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphi_x.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphi_PT.pdf}
-\caption{\label{autsinphi_jlab} $A_{UT}^{\sin\phi_S}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphiS_COMPASS_x.pdf} 
+\caption{\label{autsinphi_jlab} $A_{UT}^{\sin\phi_S}$  as a function of $ x $ for COMPASS.
 }
@@
 contains after the WW-type approximation two contributions. Assuming
-Gaussian Ans\"atze for $h^{q}(x,\kperp)$ and $f^\perp(x,\pperp)$ we obtain
+Gaussian Ans\"atze for $h^{q}(x,\kperp)$ and $f^\perp(x,\pperp)$ 
+\begin{subequations}
+\be
+h^q(x,\kperp^2) = h^q(x) \,\frac{1}{\pi \avkperp_{h}}\,
+	e^{-\kperp^2/{\avkperp_{h}}}\;,
+	\label{eq:hnew}
+\ee
+\be
+f^{\perp q}(x,\kperp^2) =f^{\perp (1) q}(x) \,\frac{2 M^2}{\pi \avkperp_{f^\perp}^2}\,
+	e^{-\kperp^2/{\avkperp_{f^\perp}}}\;,
+	\label{eq:fperpnew}
+\ee
+\end{subequations}
+we obtain
 \begin{subequations}\begin{alignat}{1}
 	F_{UU}^{\cos\phi_h}(x,z,\Phperp) 
-	= \red{+}\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
+	= +\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
 	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;b^{(1)}_{\rm A}\,
@@
 	  \nonumber\\
-	\red{-} x\,f^{\perp(1)q}(x)\,D_1^q(z)\;b^{(1)}_{\rm B}\,
+	- x\,f^{\perp(1)q}(x)\,D_1^q(z)\;b^{(1)}_{\rm B}\,
 	  \biggl(\frac{z \Phperp} {\lambda}\biggr)\, & { \cal G}(\Phperp ) 
@@
 	F_{UU}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
-	= \red{+}\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
+	= +\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
 	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;c^{(1)}_{\rm A}\;
@@
 	  \nonumber\\
-	\red{-}x\,f^{\perp(1)q}(x)\,D_1^q(z)\;c^{(1)}_{\rm B}\;
+	-x\,f^{\perp(1)q}(x)\,D_1^q(z)\;c^{(1)}_{\rm B}\;
 	  \biggl(\frac{z}{\lambda^{1/2}}\biggr)&
@@
 as shown in Fig.~\ref{auucosphi_jlab}. \\
-\PS{(Alexei: did you notice it \cite{Anselmino:2005nn}? How did you treat it?)}
+\PS{(Alexei: did you notice it \cite{Anselmino:2005nn}? How did you treat it? AP we did notice and did nothing.)}
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_x.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_PT.pdf}
-\caption{\label{auucosphi_jlab} $A_{UU}^{\cos\phi_h}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
+\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_PT.pdf} 
+\caption{\label{auucosphi_jlab} $A_{UU}^{\cos\phi_h}$  for COMPASS.
 }
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\
-
-\ \\
-\PS{We may potentially run into positivity issues also for other observables. 
-However, I would suggest not to worry too much. We see in the pictures that 
-the respective asymmetries are smaller than 100$\,\%$ for reasonably small 
-$\Phperp$ and can be happy with that! But perhaps we should include a 
-comment somewhere?}
-
 %------ BEGIN FIGURE 4: Phperp(z) AND Phperp^2(z) at HERMES ----------
@@
 
+\
+
+\ \\
+\PS{We may potentially run into positivity issues also for other observables. 
+However, I would suggest not to worry too much. We see in the pictures that 
+the respective asymmetries are smaller than 100$\,\%$ for reasonably small 
+$\Phperp$ and can be happy with that! But perhaps we should include a 
+comment somewhere?}
+
 \newpage
@@
 1 contribution in our treatment. Assuming Gauss Ans\"atze for 
-$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ we find
+$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$ (Eq.~\ref{eq:hTperpnew}), $h_T^q(x,\kperp)$ (Eq.~\ref{eq:hTnew}),
+\be
+	f^{\perp q}_{T}(x,\kperp^2) = 
+	f^{\perp (2) q}_{T}(x)\,\frac{2 M^4}{\pi \avkperp^3_{f_{T}^{\perp} }}\,
+	e^{-\kperp^2/{\avkperp_{f_{T}^{\perp} }}}\;,
+	\label{eq:ftperpnew}
+\ee
+we find
 \begin{subequations}\begin{alignat}{1}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2phi_x.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2phi_PT.pdf}
-\caption{\label{autsin2phi_jlab} $A_{UT}^{\sin(2\phi_h- \phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2PhiminusPhiS_COMPASS_x.pdf} 
+\caption{\label{autsin2phi_jlab} $A_{UT}^{\sin(2\phi_h- \phi_S)}$  for COMPASS.
 }
@@
 
-\subsection{\boldmath Unpolarised functions $f_1^a(x,k_\perp)$ 
-			and $D_1(z,P_\perp)$}
+\subsection{\boldmath Unpolarised functions $f_1^a(x,k_\perp^2)$ 
+			and $D_1(z,P_\perp^2)$}
 \label{App:basis-f1-D1}
@@
 
-To describe the transverse momentum dependence of $f_1^a(x,k_\perp)$ 
-and $D_1(z,P_\perp)$ we use the Gaussian Ansatz in 
+To describe the transverse momentum dependence of $f_1^a(x,k_\perp^2)$ 
+and $D_1(z,P_\perp^2)$ we use the Gaussian Ansatz in 
 Eqs.~(\ref{Eq:Gauss-f1-D1}). All early 
@@
 
-\subsection{\boldmath Helicity distribution $g_1^a(x,k_\perp)$}
+\subsection{\boldmath Helicity distribution $g_1^a(x,k_\perp^2)$}
 \label{App:basis-g1}
 
-For the helicity PDF $g_1^a(x)=\int d^2k_\perp\,g_1^a(x,k_\perp)\equiv 
-\int d^2k_\perp\,g_{1L}^a(x,k_\perp)$ we use in this work the leading-order 
+For the helicity PDF $g_1^a(x)=\int d^2k_\perp\,g_1^a(x,k_\perp^2)\equiv 
+\int d^2k_\perp\,g_{1L}^a(x,k_\perp^2)$ we use in this work the leading-order 
 parameterizations from \cite{Gluck:1998xa}.
@@
 In lack of phenomenological information on the $k_\perp$-dependence of
-$g_1^a(x,k_\perp)$ we explore lattice QCD results from \cite{Hagler:2009mb}
+$g_1^a(x,k_\perp^2)$ we explore lattice QCD results from \cite{Hagler:2009mb}
 to constrain the Gaussian width in Eq.~(\ref{eq:g1}). 
@@
 \ba
-f_{1T}^{\perp q}(x,\kperp) =  f_{1T}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{f_{1T}^\perp}^2} e^{-\kperp^2/{\avkperp_{f_{1T}^\perp}}}
+f_{1T}^{\perp q}(x,\kperp^2) =  f_{1T}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{f_{1T}^\perp}^2} e^{-\kperp^2/{\avkperp_{f_{1T}^\perp}}}
 \label{sivers_new} \ .
@@
 \ba
-H_{1}^{\perp}(z,\pperp) =  H_{1}^{\perp (1)}(z)   \frac{2 z^2 m_h^2}{\pi \avpperp_{H_{1}^\perp}^2} e^{-\pperp^2/{\avpperp_{H_{1}^\perp}}}
+H_{1}^{\perp}(z,\pperp^2) =  H_{1}^{\perp (1)}(z)   \frac{2 z^2 m_h^2}{\pi \avpperp_{H_{1}^\perp}^2} e^{-\pperp^2/{\avpperp_{H_{1}^\perp}}}
 \label{coll-funct_new} \, .
@@
 \ba
-h_{1}^{\perp q}(x,\kperp) =  h_{1}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{h_{1}^\perp}^2} e^{-\kperp^2/{\avkperp_{h_{1}^\perp}}}\label{bm_new} \ .
+h_{1}^{\perp q}(x,\kperp^2) =  h_{1}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{h_{1}^\perp}^2} e^{-\kperp^2/{\avkperp_{h_{1}^\perp}}}\label{bm_new} \ .
 \ea
@@
 \ba
-h_{1T}^{\perp q}(x,\kperp) =  h_{1T}^{\perp (2) q}(x)   \frac{2 M^4}{\pi \avkperp_{h_{1T}^\perp}^3} e^{-\kperp^2/{\avkperp_{h_{1T}^\perp}}}
+h_{1T}^{\perp q}(x,\kperp^2) =  h_{1T}^{\perp (2) q}(x)   \frac{2 M^4}{\pi \avkperp_{h_{1T}^\perp}^3} e^{-\kperp^2/{\avkperp_{h_{1T}^\perp}}}
 \label{pretzelosity_new} \ .
@@
 \newpage
-\section{Convolution integrals and expressions in Gaussian Ansatz}}
+\section{Convolution integrals and expressions in Gaussian Ansatz}
 \label{App:factor}
@@
 	c^{(1)}_{\rm A} 	&= \sqrt{\pi}\,m_h	\, , &
-	c^{(1)}_{\rm A} 	&= \sqrt{\pi}\,M_N	\, , \\
+	c^{(1)}_{\rm B} 	&= \sqrt{\pi}\,M_N	\, , \\
 	c^{(2)}_{\rm AB} 	&= 4M_Nm_h		\, , \;\;\;\;\;\; & 

### 2018-01-15 tex/test-WW-type-00s-PS.tex

@@
 progress and} improvements with regard to rigor, realism and methodology
-\cite{Yoon:2016dyh,%Proceedings of Science LATTICE 2015 (2016) 116, 
+\cite{Yoon:2017qzo, %PhysRevD.96.094508
 Engelhardt:2015xja,%Phys.Rev. D93 (2016) no.5, 054501, 
@@
 for the non-local lattice operators is under investigation 
-\cite{Micheal-new}.
-% [cite Michael Engelhardts upcoming paper, to be published]. 
+\cite{Yoon:2017qzo}. %PhysRevD.96.094508
 The gauge link that goes into the evaluation of the quark-quark correlator 
@@
 and
-$\int d x\;g_{1T}^{\perp(1)d}(x)\stackrel{\text{Gaussian}}{=}-c_{10,d}=-0.0232(42)$
+$\int d x\;g_{1T}^{\perp(1)d}(x)\stackrel{\text{Gaussian}}{=}-c_{7,d}=-0.0232(42)$
 from \cite{Musch:2010ka}. %[Phys.Rev. D83 (2011) 094507]:
@@
 In order to test (\ref{Eq:WW-approx-h1L-d}) we use
-$\int d x\;h_{1L}^{\perp(1)u}(x) = -0.0931(73)$ and
-$\int d x\;h_{1L}^{\perp(1)d}(x) = 0.0130(40)$ from \cite{Hagler:2009mb}
+% old numbers
+% $\int d x\;h_{1L}^{\perp(1)u}(x) = -0.0931(73)$ and
+% $\int d x\;h_{1L}^{\perp(1)d}(x) = 0.0130(40)$ from \cite{Hagler:2009mb}
+$\int d x\;h_{1L}^{\perp(1)u}(x)\stackrel{\text{Gaussian}}{=}-c_{10,u} = -0.0881(72)$ and
+$\int d x\;h_{1L}^{\perp(1)d}(x)\stackrel{\text{Gaussian}}{=}-c_{10,d} = 0.0137(34)$ from  \cite{Musch:2010ka}
+
 and the lattice data 
@@
         \underbrace{\int d x\;h_{1L}^{\perp(1)u}(x)}
-        _{= -0.0931(73)\;\mbox{\footnotesize Ref.~\cite{Hagler:2009mb}}}
+        _{= -0.0881(72)\;\mbox{\footnotesize Ref.~\cite{Musch:2010ka}}}
         \stackrel{!}{\approx}
@@
         \underbrace{\int d x\;h_{1L}^{\perp(1)d}(x)}
-        _{= 0.0130(40) \;\mbox{\footnotesize Ref.~\cite{Hagler:2009mb}}}
+        _{= 0.0137(34) \;\mbox{\footnotesize Ref.~\cite{Musch:2010ka}}}
         \stackrel{!}{\approx}
@@
 	The results \cite{Hagler:2009mb} refer also to pion masses above the 
-	physical value. This is caveat is presumably less critical and
+	physical value. This caveat is presumably less critical and
 	will be overcome as lattice QCD simulations are becoming feasible 

### 2018-01-17 tex/test-WW-type-00s-PS.tex
jlab

@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_COMPASS_x.pdf}  
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_COMPASS_x.pdf}  (a)
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_JLAB_x.pdf}  (b)
 	\caption{\label{aul_jlab} 
@@
 	of COMPASS, 
-	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$.
+	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$ (a) and comparison to JLab (b).
 	}
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf} (b)
-\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $ , comparison to HERMES data \cite{Airapetian:2005jc} (a), and predictions for COMPASS (b).
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} (c)
+\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $ , comparison to HERMES data \cite{Airapetian:2005jc} (a), and predictions for COMPASS (b), and comparison to JLab (c).
 }
@@
 \begin{subequations}\be
-	x\,h_1^q(x) = 0\,.
+	x\,h^q(x) = 0\,.
 \ee

### 2018-02-12 tex/test-WW-type-00s-PS.tex
TEX
alexei

@@
 
-\preprint{JLAB-THY-17-XXXX}
+\preprint{JLAB-THY-18-XXXX}
 
@@
 \author[a]{S.~Bastami}
-%\author[b]{M.~D.~Albright}
 \author[c]{H.~Avakian}
 \author[d]{A.~V.~Efremov} 
-\author[e]{A.~Kotzinian} 
-\author[f]{B.~U.~Musch} 
+\author[e,f]{A.~Kotzinian} 
+\author[g]{B.~U.~Musch} 
 \author[e]{B.~Parsamyan} 
 \author[b,c]{A.~Prokudin} 
-\author[g]{M.~Schlegel} 
-\author[a,g]{P.~Schweitzer} 
-\author[g]{W.~Vogelsang}
+\author[i]{M.~Schlegel} 
+\author[]{G.~Schnell} 
+\author[a,i]{P.~Schweitzer} 
+\author[i]{W.~Vogelsang}
 
@@
 	141980 Russia}
-\affiliation[e]{Dipartimento di fisica teorica, Universit\`a degli 
-   studi di Torino, and Sezione dell'INFN di Torino, Via Pietro Giuria 1, 
-   10125 Torino, Italy}
-\affiliation[f]{Institut f\"ur Theoretische Physik, Universit\"at 
+\affiliation[e]{Yerevan Physics Institute,
+2 Alikhanyan Brothers St.,
+375036 Yerevan, Armenia
+}
+\affiliation[f]{INFN, Sezione di Torino, 10125 Torino, Italy
+}
+
+\affiliation[g]{Institut f\"ur Theoretische Physik, Universit\"at 
   	Regensburg, 93040 Regensburg, Germany}
-\affiliation[g]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
+\affiliation[i]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
 	% Auf der Morgenstelle 14, 
@@
 The asymmetries $A_{UL}^{\sin(2\phi_h)}=F_{UL}^{\sin(2\phi_h)}/F_{UU}$  for 
-Jefferson Lab 12 GeV are plotted in Fig.~\ref{aul_jlab}.
+ Jefferson Lab data from CLAS for neutral pion SIDIS \cite{Jawalkar:2017ube} are plotted in Fig.~\ref{aul_jlab}.
 

### 2018-05-19 tex/old/test-WW-type-00t-PS.tex
last version

--- 2018-01-17 tex/test-WW-type-00s-PS.tex
@@
 \newcommand{\darkgreen}[1]{{\color{darkgreen} #1}}
-\newcommand{\PS}[1]{\blue{\bf\boldmath #1}}
+\newcommand{\ps}[1]{\blue{ #1}}
 
@@
 \author[a]{S.~Bastami}
-%\author[b]{M.~D.~Albright}
-\author[c]{H.~Avakian}
-\author[d]{A.~V.~Efremov} 
-\author[e]{A.~Kotzinian} 
+\author[b]{H.~Avakian}
+\author[c]{A.~V.~Efremov} 
+\author[d,e]{A.~Kotzinian} 
 \author[f]{B.~U.~Musch} 
 \author[e]{B.~Parsamyan} 
-\author[b,c]{A.~Prokudin} 
-\author[g]{M.~Schlegel} 
-\author[a,g]{P.~Schweitzer} 
-\author[g]{W.~Vogelsang}
+\author[g,b]{A.~Prokudin} 
+\author[h]{M.~Schlegel} 
+\author[i]{G.~Schnell} 
+\author[a,j]{P.~Schweitzer} 
+\author[a]{K.~Tezgin}
+\author[j]{W.~Vogelsang}
 
@@
 	Storrs, CT 06269, U.S.A.}
-\affiliation[b]{Division of Science, Penn State Berks, Reading, 
-	PA 19610, USA}
-\affiliation[c]{Thomas Jefferson National Accelerator Facility, 
+\affiliation[b]{Thomas Jefferson National Accelerator Facility, 
 	Newport News, VA 23606, U.S.A.}
-\affiliation[d]{Joint Institute for Nuclear Research, Dubna, 
+\affiliation[c]{Joint Institute for Nuclear Research, Dubna, 
 	141980 Russia}
-\affiliation[e]{Dipartimento di fisica teorica, Universit\`a degli 
-   studi di Torino, and Sezione dell'INFN di Torino, Via Pietro Giuria 1, 
+\affiliation[d]{Yerevan Physics Institute,  Alikhanyan Brothers St.,
+	375036 Yerevan, Armenia}
+\affiliation[e]{INFN, Sezione di Torino, 
 	10125 Torino, Italy}
@@
   	Regensburg, 93040 Regensburg, Germany}
-\affiliation[g]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
-	% Auf der Morgenstelle 14, 
-	D-72076 T\"ubingen, Germany}
+\affiliation[g]{Division of Science, Penn State Berks, Reading, 
+	PA 19610, USA}
+\affiliation[h]{Department of Physics, New Mexico State University, 
+	Las Cruces, NM 88003-001, USA}
+\affiliation[i]{Department of Theoretical Physics, University of the Basque 
+	Country UPV/EHU, 48080 Bilbao, Spain, and
+	IKERBASQUE, Basque Foundation for Science, 48013 Bilbao, Spain}
+\affiliation[j]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
+	D-72076 T\"ubingen, Germany} % Auf der Morgenstelle 14,
 
@@
 \emailAdd{saman.bastami@uconn.edu}
-%\emailAdd{mda5232@psu.edu} % Mason Dale Albright
 \emailAdd{avakian@jlab.org}
@@
 \emailAdd{prokudin@jlab.org}
-\emailAdd{marc.schlegel@uni-tuebingen.de}
+\emailAdd{schlegel@nmsu.edu}
+\emailAdd{gunar.schnell@desy.de}
 \emailAdd{peter.schweitzer@phys.uconn.edu}
+\emailAdd{kemal.tezgin@uconn.edu}
 \emailAdd{werner.vogelsang@uni-tuebingen.de}
@@
 \abstract{ 
-We present the complete cross-section for pion production in Semi-Inclusive 
-Deep Inelastic Scattering (SIDIS) in the Wandzura-Wilczek-type approximation 
-up to power-suppressed ${\cal O}(1/Q^2)$ terms. We compute all % 18 
-twist-2 and twist-3 SIDIS structure functions and the corresponding 
-asymmetries. We discuss  the applicability of the
-Wandzura-Wilczek-type approximations on the basis of available data,
-and make predictions which can be tested by data from 
-Jefferson Lab, COMPASS, HERMES, and the future EIC. 
-The results of this paper can be readily used for phenomenology and 
-for event generators for SIDIS, and will help to improve our 
+We present the complete cross-section for pion production in semi-inclusive 
+deep-inelastic scattering up to power-suppressed ${\cal O}(1/Q^2)$ terms in 
+the Wandzura--Wilczek-type approximation \ps{which consists in a systematic
+neglect of $q\bar q g$-terms with respect to $\bar{q}q$-correlators.}
+We compute all twist-2 and twist-3 structure functions and the corresponding 
+asymmetries, and discuss the applicability of the Wandzura--Wilczek-type 
+approximations on the basis of available data. We make predictions which 
+can be tested by data from Jefferson Lab, COMPASS, HERMES, and the future 
+Electron-Ion Collider. The results of this paper can be readily used for 
+phenomenology and for event generators, and will help to improve our 
 understanding of the TMD theory beyond leading twist.
@@
 \keywords{
-	Wandzura-Wilczek approximation, 
+	Wandzura--Wilczek approximation, 
 	semi-inclusive deep inelastic scattering, 
@@
 nucleon is due to studies of parton distribution functions (PDFs) 
-in deeply inelastic reactions. Leading-twist PDFs  tell us  how likely 
+in deep-inelastic reactions. leading--twist PDFs  tell us  how likely 
 it is to find an unpolarized parton 
@@
 well-known, and the frontier has been extended in the last years 
-to go beyond the one-dimensional picture offered by PDFs.
+to go beyond the one-dimensional picture offered by those PDFs.
 
@@
 of the process, the formal description is given in terms of 
-transverse momentum dependent distribution functions (TMDs) 
+transverse momentum dependent distribution functions TMDs) 
 and fragmentation functions (FFs)
@@
 
-One powerful tool to study TMDs are measurements of the SIDIS process.
+One powerful tool to study TMDs are measurements of the 
+semi-inclusive deep-inelastic scattering (SIDIS) process.
 By exploring various possibilities for electron/muon beam and target 
-polarizations unambiguous information can be accessed on the 8 leading-twist 
+polarizations unambiguous information can be accessed on the 8 leading--twist 
 TMDs \cite{Boer:1997nt} and, if one assumes factorization, on certain
-linear combinations of the 16 subleading-twist TMDs 
+linear combinations of the 16 subleading--twist TMDs 
 \cite{Goeke:2005hb,Bacchetta:2006tn}.
@@
 and in the case of $g_T^a(x)$ data confirm or are compatible with these 
-predictions \cite{Abe:1998wq,Anthony:2002hy}.
+predictions \cite{Abe:1998wq,Anthony:2002hy,Airapetian:2011wu}.
 This approximation (``neglect of $\bar qgq$-terms'') is commonly 
-known as Wandzura-Wilczek (WW) approximation \cite{Wandzura:1977qf}.
+known as Wandzura--Wilczek (WW) approximation \cite{Wandzura:1977qf}.
 The possibility to apply this type of approximation also to TMDs has 
 been explored in specific cases in \cite{Kotzinian:1995cz,Kotzinian:1997wt,
-Kotzinian:2006dw,Avakian:2007mv,Metz:2008ib,Teckentrup:2009tk}.
+Kotzinian:2006dw,Avakian:2007mv,Metz:2008ib,Teckentrup:2009tk,Tangerman:1994bb}.
 In both cases, PDFs and TMDs, one basically assumes that the 
@@
 In this work, after introducing the SIDIS process and defining TMDs and FFs 
-(Sec.~\ref{Sec-2:SIDIS+TMDs+FF}), we shall introduce the approximations,
-and review what is presently known about their reliability from experiment 
-and theory (Sec.~\ref{Sec-3:WW}).
+(Sec.~\ref{Sec-2:SIDIS+TMDs+FF}), we shall introduce the WW(-type) 
+approximations, and review what is presently known about them 
+from experiment and theory (Sec.~\ref{Sec-3:WW}).
 We will show that under the assumption of the validity of these approximations 
-it is possible to describe all leading and subleading SIDIS structure functions
-in terms of a basis of 6 TMDs and 2 FFs, and review what is presently known
-about these functions (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation}).
-Using the latest available extractions of the 8 basis functions  
-we will systematically apply the WW and/or WW-type approximations
+all leading and subleading SIDIS structure functions are described in terms of 
+a basis of 6 TMDs and 2 FFs (Sec.~\ref{Sec-4:SIDIS-in-WW-approximation}),
+and review how these basis functions describe available data 
+(Sec.~\ref{Sec-5:twist-2+basis}).
+We will systematically apply the WW and/or WW-type approximations
 to SIDIS structure at leading (Sec.~\ref{Sec-6:twist-2-and-WW}) 
-and subleading (Sec.~\ref{Sec-7:twist-3-and-WW}) twist.
-We will conclude with a critical discussion (Sec.~\ref{Sec-8:conclusions}).
+and subleading (Sec.~\ref{Sec-7:twist-3-and-WW}) twist, and
+conclude with a critical discussion (Sec.~\ref{Sec-8:conclusions}).
 
 This is the first study of all SIDIS structure functions up to twist-3 
-in a unique approach. Our results are of use for experiments prepared 
-in the near-term (Jefferson Lab 12) or proposed in the long-term 
-(Electron Ion Collider), and provide helpful input for Montecarlo event
+in a unique approach. Our results are of importance for experiments prepared 
+in the near-term (JLab 12, \ps{COMPASS}) or proposed in the long-term 
+(Electron Ion Collider), and provide helpful input for Monte Carlo event
 generators \cite{Avakian:2015vha}.
-Our predictions will either be confirmed within the expected accuracy, 
-implying the approximations work and calling for dedicated theoretical 
-explanations why. Or they will fail in certain cases, calling for 
-theoretical work to explain why in some cases $\bar{q}gq$-terms are sizable.
-In any case, our results will deepen our understanding.
+Our predictions will either be confirmed within the expected accuracy
+\ps{or not be supported by data. The first case will call for dedicated 
+theoretical studies to explain why the pertinent $\bar{q}gq$-terms are 
+so small. The second case will call for explanations why sometimes 
+$\bar{q}gq$-terms are so sizable. In this way our work will help to guide 
+further developments. In either case our results will deepen the
+understanding of the quark-gluon correlations inside hadrons.}
 
@@
 \begin{wrapfigure}[8]{RD}{8cm}
-\vspace{-5mm}
+\vspace{-7mm}
 \centering
-	\includegraphics[width=7.5cm]{\FigPath/Fig02a-kin-SIDIS-UT.eps}
+	\includegraphics[width=7.2cm]{\FigPath/Fig02a-kin-SIDIS-UT.eps}
         \caption{\label{fig-kin-SIDIS}
-    	Kinematics of SIDIS process $lN\to l^\prime h X$.} 
-	% and the definitions of azimuthal angles in the lab frame.}
+    	Kinematics of SIDIS process $lN\to l^\prime h X$
+	in 1-photon exchange approximation.}
 \vspace{-5mm}
@@
 of its momentum component $\Phperp$ perpendicular with respect to the 
-virtual photon momentum, and the azimuthal angle $\psi_l$ characterizing 
-the overall orientation of the lepton scattering plane in the lab frame.
-Notice that $d \psi_l \simeq d\phi_S$ where $\phi_S$ is the azimuthal angle
-of the nucleon spin vector. It is convenient to define the unpolarized
-lepton -- quark scattering cross section
+virtual photon momentum. 
+\ps{In principle the cross section is also differential with respect to the} 
+azimuthal angle $\psi_l$ characterizing the overall orientation of the 
+lepton scattering plane in \ps{a fixed} lab frame.
+%
+% Notice that $d \psi_l \simeq d\phi_S$ where $\phi_S$ is the azimuthal angle
+% of the nucleon spin vector. 
+%
+\ps{By analyzing the data in the reference frame in Fig.~\ref{fig-kin-SIDIS}
+all events are by definition in the ``bin'' $\psi_l=0$ (within detector
+resolution) and the variable $\psi_l$ is practically integrated out leaving 
+us with a 5-dimensional cross section. Below we keep the cross section 
+``differential'' in $\psi_l$ for symbolic reasons.}
+%
+It is convenient to define the unpolarized
+lepton--quark scattering \ps{subprocess} cross section
 \ba\label{Eq:sigma0-FUU}
-	\sigma_0 \equiv \frac{d \sigma}{dy} 
+	% \sigma_0 \equiv 
+	\frac{d \hat{\sigma}}{dy} 
 	= 
@@
 \begin{subequations}\ba\hspace{-1cm}
-   &&  \frac{d^6\sigma_{\rm leading}}{dx\,dy\,dz\,d\phi_S\,d\phi_h\,d \Phperp^2}
-   =	 \frac{\sigma_0 }{4\pi}\; F_{UU}(x,z,\Phperp^2)
+   &&  \frac{d^6\sigma_{\rm leading}}{dx\,dy\,dz\,d\psi_l\,d\phi_h\,d \Phperp^2}
+   =	 \frac{1}{4\pi}\;\frac{d \hat{\sigma}}{dy}\;F_{UU}(x,z,\Phperp^2)
         \Biggl\{\;1 
@@
 polarization of the virtual photon (sometimes denoted as $F_{UU,T}$),
-and we systematically neglect $1/Q^2$ corrections in 
-kinematic factors and a structure function arising from
-longitudinal polarization of the virtual photon 
-(sometimes denoted as $F_{UU,L}$). %  poorly known in SIDIS.
-The structure functions (and asymmetries $A$) also depend on $Q^2$ via the scale dependence of 
+and we systematically neglect $1/Q^2$ corrections in kinematic factors 
+and a structure function (sometimes denoted as $F_{UU,L}$) arising from
+longitudinal polarization of the virtual photon (and analog for the 
+structure function $\propto S_T\,\sin( \phi_h-\phi_S)$, see below).
+The structure functions 
+(and asymmetries) also depend on $Q^2$ via the scale dependence of 
 TMDs and FFs, which we do not show in formulas throughout this work.
 
-At subleading order one has
+At subleading order \ps{in the $1/Q$ expansion} one has
 \ba\hspace{-1cm}
-   &&   \frac{d^6\sigma_{\rm subleading}}{dx\,dy\,dz\,d\phi_S\,d\phi_h\,d \Phperp^2}
-   =	\frac{\sigma_0 }{4\pi} \; F_{UU}(x,z,\Phperp^2)
+   &&   \frac{d^6\sigma_{\rm subleading}}{dx\,dy\,dz\,d\psi_l\,d\phi_h\,d \Phperp^2}
+   =	\frac{1}{4\pi} \; \frac{d \hat{\sigma}}{dy} \; F_{UU}(x,z,\Phperp^2)
         \Biggl\{ 
           \cos(\phi_h)\,p_3\,A_{UU}^{\cos(\phi_h)}
-  	{}
 	\nonumber\\ 
@@
 
+\ps{In the partonic description the structure functions in 
+(\ref{Eq:SIDIS-leading})    are ``twist-2.'' Those in
+(\ref{Eq:SIDIS-subleading}) are ``twist-3'' and contain a
+factor $M/Q$ in their definitions, see below. In our treatment to $1/Q^2$ 
+accuracy we neglect two structure functions due to longitudinal virtual 
+photon polarization which contribute at order ${\cal O}(M^2/Q^2)$ in the 
+partonic description of the process, one being $F_{UU,L}$ and the other 
+contributing to the $\sin(\phi_h-\phi_S)$ angular distribution 
+\cite{Bacchetta:2006tn}.}
+
 Experimental collaborations often define asymmetries in terms of counts 
@@
 \be
-	N(\phi) = \frac{N_0}{2\pi} \biggl(1
-		+ \cos\phi\;\asympre{UU}{\cos\phi_h}+
-		+ \cos2\phi\;\asympre{UU}{\cos2\phi_h}\Biggr)
-\ee
-where $N_0$ denotes the total $\phi_h$-averaged)\
-number of counts in the kinematic bin of interest.
+	N(x,\dots,\phi) = \frac{N_0(x,\dots)}{2\pi} \biggl(1
+		+ \cos\phi\;\asympre{UU}{\cos\phi_h}(x,\dots)
+		+ \cos2\phi\;\asympre{UU}{\cos2\phi_h}(x,\dots)\Biggr)
+\ee
+where $N_0$ denotes the total ($\phi_h$-averaged) number of counts 
+and the dots indicate further kinematic variables in the kinematic 
+bin of interest (which may also be averaged over).
 It would be preferable if asymmetries were analyzed with known kinematic 
@@
 experiments and kinematics, and focus on effects of evolution 
-or power suppression for twist-3. In practice, data analysis is easier
-with kinematic factors included. Data for such asymmetries 
-$\asympre{XY}{\rm weight}$ are more easily available. We will 
-define and comment on the explicit expressions as needed.
+or power suppression for twist-3. In practice, often the kinematic 
+factors were included. We will define and comment on the explicit 
+expressions as needed.
 
@@
 \begin{subequations}\ba
-     	\frac{d^4\sigma_{\rm leading}}{dx\,dy\,dz\,d\phi_S}
-   &=&	 \frac{\sigma_0 }{2\pi}\; F_{UU}(x,z) 
+     	\frac{d^4\sigma_{\rm leading}}{dx\,dy\,dz\,d\psi_l}
+   &=&	 \frac{1}{2\pi}\;\frac{d \hat{\sigma}}{dy} \; F_{UU}(x,z) 
         \Biggl\{\;1 + \lambda\,S_L\,    p_2\,A_{LL} \Biggr\}
     	\label{Eq:SIDIS-leading-integrated} \\
-	\frac{d^4\sigma_{\rm subleading}}{dx\,dy\,dz\,d\phi_S}
-   &=&	 \frac{\sigma_0 }{2\pi}\; F_{UU}(x,z) 
+	\frac{d^4\sigma_{\rm subleading}}{dx\,dy\,dz\,d\psi_l}
+   &=&	 \frac{1}{2\pi}\;\frac{d \hat{\sigma}}{dy} \; F_{UU}(x,z) 
         \Biggl\{ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)} 
@@
 where $\gamma=2M_Nx/Q$ signals the twist-3 character of $F_{LT}^{\cos\phi_S}(x,z)$.
-We consequently neglect $1/Q^2$ effects, including the twist-4 DIS structure 
-function $F_2(x)$. $F_{UT}^{\sin\phi_S}(x,z)$ has no DIS counterpart due to 
-time reversal symmetry of strong interactions.
+\ps{As we consequently neglect $1/Q^2$ effects, the twist-4 DIS structure 
+function $F_2(x)$ does not appear in (\ref{Eq:DIS-F1}).}
+$F_{UT}^{\sin\phi_S}(x,z)$ has no DIS 
+counterpart due to time reversal symmetry of strong interactions.
 
@@
 	\ee
-where the symbolic Wilson-lines refer to the SIDIS process 
+where the % symbolic 
+Wilson-lines refer to the SIDIS process 
 \cite{Collins:2002kn}. For a generic four-vector $a^\mu$ we define
@@
 
-\newpage
-
-The 8 leading-twist TMDs \cite{Boer:1997nt} are projected out from the
-correlator (\ref{Eq:correlator}) as follows
-(\blue{blue (online only): T-even}, \red{red  (online only): T-odd}; we suppress flavor
-and renormalization scale dependence)
+The 8 leading--twist TMDs \cite{Boer:1997nt} are 
+projected out from the correlator (\ref{Eq:correlator}) as follows
+(\blue{blue: 
+%(online only): 
+T-even}, \red{red:  
+%(online only): 
+T-odd};
+ we suppress flavor and renormalization scale dependence)
 \begin{subequations}\ba
@@
 Integrating out transverse momenta in the correlator (\ref{Eq:correlator})
-leads to the `usual' PDFs known from collinear kinematics
+leads to the ``usual'' PDFs known from collinear kinematics
 \cite{Ralston:1979ys,Jaffe:1991ra}, namely at twist-2 level
@@
 $\bfkperp$ and $\bfpperp$.
-The 8 leading-twist structure functions are 
+The 8 leading--twist structure functions are 
 \begin{subequations}
@@
 \ea\end{subequations}
-At subleading-twist we have the structure functions
+At subleading--twist we have the structure functions
 \begin{subequations}
@@
 In $\omega^{\{n\}}_{i}$ the index $n=0,\,1,\,2,\,3$ indicates the (maximal)
-power $(\Phperp)^N$ with which the corresponding contribution scales,
+power $(\Phperp)^n$ with which the corresponding contribution scales,
 and index $i$ (if any) distinguishes different types of contributions
@@
 Eqs.~(\ref{Eq:FUUcosphi}--\ref{FLTsin(2phi-phiS)}) contain an explicit 
-factor $M/Q$. We also recall that we neglect two structure functions 
-due to longitudinal virtual photon polarization which contribute,
-in the TMD factorization framework, at order ${\cal O}(M^2/Q^2)$, 
-one being $F_{UU,L}$ and the other contributing to the 
-$\sin(\phi_h-\phi_S)$ angular distribution \cite{Bacchetta:2006tn}.
+factor $M/Q$. \ps{We also recall that we neglect two structure 
+functions, $F_{UU,L}$ and $F_{UT,L}^{\sin( \phi_h-\phi_S)}$ in the
+notation of \cite{Bacchetta:2006tn}, due to longitudinal virtual photon 
+polarization which are of order ${\cal O}(M^2/Q^2)$ in the TMD 
+factorization approach.}
 
@@
 \ea\end{subequations}
-Finally, using the sum rules for the T-odd FFs 
+Finally, \ps{integrating over $z$, summing over hadrons, and} 
+using the sum rules for the T-odd FFs 
 $\sum_h\int d z\;\tilde{E}^a(z)=0$ and
@@
 known about them.
-The basic idea of the approximations is simple. One assumes that the 
-contributions from $\bar{q}gq$-terms can be neglected with respect to 
-$\bar{q}q$-terms with a useful accuracy,
+The basic idea of the approximations is simple. One \ps{uses QCD
+equations of motion to separate contributions from $\bar{q}q$-terms 
+and $\bar{q}gq$-terms and assumes that the latter} can be neglected 
+with respect to \ps{the leading} $\bar{q}q$-terms with a useful accuracy,
 \be\label{Eq:WW-generic}
@@
    	x\,e^a(x) &=& x\,&\tilde{e}^a(x) \;\stackrel{\rm WW}{\approx} 
-	\;\;\;\; 0
+	\;\;\;\; 0 \label{Eq:WW-original-e}
 \end{alignat}\end{subequations}
-where we included $e^a(x)$ which ia a special case in the sense that it 
-receives no twist-2 contribution. Notice that a prefactor of $x$ is
-provided to cancel a $\delta(x)$-type singularity \cite{Efremov:2002qh}.
+where we included $e^a(x)$ which is a special case in the sense that it 
+receives no twist-2 contribution. 
+\ps{A prefactor of $x$ is provided in (\ref{Eq:WW-original-e})}
+to cancel a $\delta(x)$-type singularity \cite{Efremov:2002qh}.
 After introducing the WW-type approximations for TMDs and FFs,
@@
 \begin{subequations}\ba
-xe_L^q(x,\kperp^2)         	&\stackrel{\rm WW-type}{\approx}& 0, \\
+xe_L^q(x,\kperp^2)         	&\stackrel{\rm WW-type}{\approx}& 0, 
+			\label{Eq:WW-type-eLperp}\\\\
 xe_T^q(x,\kperp^2)         	&\stackrel{\rm WW-type}{\approx}& 0, \\
@@
 xf_L^{\perp q}(x,\kperp^2) 	&\stackrel{\rm WW-type}{\approx}& 0, 
-			\phantom{\frac11}\\
+			\label{Eq:WW-type-fLperp}\phantom{\frac11}\\
 xf_T^{\perp q}(x,\kperp^2) 	&\stackrel{\rm WW-type}{\approx}& 
@@
 
-Insights on the relatve size of hadronic matrix elements, such as 
+Insights on the relative size of hadronic matrix elements, such as 
 Eq.~(\ref{Eq:WW-generic}), require a non-perturbative approach. It is 
 by no means obvious which small parameter in the strong interaction 
-regime would allow to explain such results.
+regime would allow one to explain such results 	.
 
@@
 Noteworthy, the instanton vacuum predictions for $\tilde{g}_T^a(x)$
+\cite{Balla:1997hf}
 were made before the advent of the first precise data on $g_2(x)$
@@
 Data support (\ref{Eq:g2-in-WW-approximation}) to a good accuracy
-\cite{Anthony:2002hy,Abe:1998wq}, although especially at smaller 
-$x$ more stringent tests are not yet possible. Overall it has been
-estimated that the WW approximation for $g_2(x)$ and $g_T^a(x)$ works 
+\cite{Anthony:2002hy,Abe:1998wq,Airapetian:2011wu}, although especially 
+at smaller $x$ more stringent tests are not yet possible. Overall it has 
+been estimated that the WW approximation for $g_2(x)$ and $g_T^a(x)$ works 
 with an accuracy of about $40\,\%$ or better \cite{Accardi:2009au}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t!]
+\begin{figure}[b!]
 \centering
@@
 \caption{\label{Fig:g2} 
-$g_{2}$ structure function in  WW-approximation, 
-Eq.~(\ref{Eq:g2-in-WW-approximation}), for proton (P) and neutron (N)
-targets. The data are from \cite{Anthony:2002hy,Abe:1998wq}.
-The error band procedure is described in the text.}
+The structure function $xg_2(x)$ in WW-approximation at $Q^2=7.1\,{\rm GeV}^2$,
+Eq.~(\ref{Eq:g2-in-WW-approximation}), for proton (P) and neutron (N) targets. 
+The data are from \cite{Anthony:2002hy,Abe:1998wq}. The \ps{estimate of the 
+theoretical uncertainty} is described in the text.
+\red{Gunar: good idea to include HERMES data \cite{Airapetian:2011wu}!
+Please send us the table with the data points.}}
 \end{figure}
@@
 How well does the WW approximation describe data if we allow for a
-theoretical ``error band'' of about $40\,\%$ as deduced in 
+theoretical ``uncertainty band'' of about $40\,\%$ as deduced in 
 \cite{Accardi:2009au}? In order to investigate this question, 
@@
 $\varepsilon_{1,2}$ may overestimate in certain $x$-bins the 
-$40\,\%$-``error band'' estimated in \cite{Accardi:2009au}. This however 
+$40\,\%$-``uncertainty band'' estimated in \cite{Accardi:2009au}. This however 
 helps us to display a conservative estimate of possible uncertainties.
@@
 
-\blue{The lowest Mellin moments of the PDF $g_T^q(x)$ were studied in
+The lowest Mellin moments of the PDF $g_T^q(x)$ were studied in
 lattice QCD in the quenched approximation \cite{Gockeler:2000ja} 
@@
 \cite{Hagler:2009mb,Musch:2010ka}, recent years have witnessed considerable
-progress and} improvements with regard to rigor, realism and methodology
+progress and improvements with regard to rigor, realism and methodology
 \cite{Yoon:2017qzo, %PhysRevD.96.094508
@@
 $\bfkperp$ and manifest themselves as short range artefacts on the lattice. 
-Casting this line of thought into Mathematics, we get
+Casting this line of thought into mathematics, we get
 \ba
@@
 % lattice spacing $a$ and current quark masses $m_{u,d}$ such that
-with $am_{u,d} = 0.020$ with $m_\pi\approx 500\,{\rm MeV}$)
+with $a\,m_{u,d} = 0.020$ with $m_\pi\approx 500\,{\rm MeV}$)
 one has $\int d x \;x\,g_1^{u-d}(x)= 0.257(10)$ and
@@
 % $\int d x\;h_{1L}^{\perp(1)d}(x) = 0.0130(40)$ from \cite{Hagler:2009mb}
-$\int d x\;h_{1L}^{\perp(1)u}(x)\stackrel{\text{Gaussian}}{=}-c_{10,u} = -0.0881(72)$ and
-$\int d x\;h_{1L}^{\perp(1)d}(x)\stackrel{\text{Gaussian}}{=}-c_{10,d} = 0.0137(34)$ from  \cite{Musch:2010ka}
-
-and the lattice data 
+$\int dx\;h_{1L}^{\perp(1)u}(x)\stackrel{\text{Gaussian}}{=}-c_{10,u}=-0.0881(72)$ 
+and
+$\int dx\;h_{1L}^{\perp(1)d}(x)\stackrel{\text{Gaussian}}{=}-c_{10,d}=0.0137(34)$
+from \cite{Musch:2010ka} and the lattice data 
 $\int d x \;x\,h_1^u(x)= 0.28(1)$ and
@@
   common value of the pion mass $m_\pi\approx500\,{\rm MeV}$, and
-  estimate the error conservatively in order to take systematic effects
+  estimate the uncertainty conservatively in order to take systematic effects
   into account due to the use of a different lattice.}
@@
         _{= -0.0881(72)\;\mbox{\footnotesize Ref.~\cite{Musch:2010ka}}}
-        \stackrel{!}{\approx}
+        &\stackrel{!}{\approx}&
         \underbrace{-\,\frac{1}{3}\int d x\;x\,g_1^u(x)}
@@
         _{= 0.0137(34) \;\mbox{\footnotesize Ref.~\cite{Musch:2010ka}}}
-        \stackrel{!}{\approx}
+        &\stackrel{!}{\approx}&
         \underbrace{-\,\frac{1}{3}\int d x\;x\,h_1^u(x)}
@@
 the path of the gauge link was chosen, which is actually different
-from the paths required in SIDIS or DY. With the path choice of
+from the paths required in SIDIS or Drell-Yan. With the path choice of
 \cite{Hagler:2007xi} there are effectively only (T-even)
 $A_i$ amplitudes, the $B_i$ amplitudes are absent.
-Therefore, see \cite{Metz:2008ib,Teckentrup:2009tk} and
-Sec.~\ref{Sec-3.6:models},
-the test (\ref{Eq:test-WW-type-lattice-g1T}) of the WW-type
+Therefore the test (\ref{Eq:test-WW-type-lattice-g1T}) of the WW-type
 approximation (\ref{Eq:WW-approx-g1T-d}) actually constitutes a test
 of the WW-approximation (\ref{Eq:WW-original1}) and confirms
-earlier lattice work \cite{Gockeler:2000ja,Gockeler:2005vw}.
+earlier lattice work \cite{Gockeler:2000ja,Gockeler:2005vw},
+cf.\ Refs.~\cite{Metz:2008ib,Teckentrup:2009tk} and
+Sec.~\ref{Sec-3.6:models}.
 Similarly, the test (\ref{Eq:test-WW-type-lattice-h1L}) of the
@@
 Third, to be precise:
-(\ref{Eq:test-WW-type-lattice-g1T},~\ref{Eq:test-WW-type-lattice-h1L})
+Eqs.~(\ref{Eq:test-WW-type-lattice-g1T},~\ref{Eq:test-WW-type-lattice-h1L})
 test the first Mellin moments of the WW approximations
@@
 Meanwhile we may try to gain insights into the quality of
-WW-type approximations from experiment.
+WW-type approximations from \ps{models}.
 
@@
 of 12 amplitudes \cite{Tangerman:1994bb,Mulders:1995dh}, i.e.\ fewer 
-amplitudes than TMDs which implies relations, qLIRs. 
+amplitudes than TMDs which implies relations: the qLIRs. 
 In QCD the correct Lorentz decomposition requires the consideration of 
-gauge links. This generates further amplitudes. As a result one has 
+gauge links which introduces further amplitudes. As a result one has 
 as many amplitudes as TMDs and no relations exist \cite{Goeke:2003az}. 
@@
 within an accuracy of $(10-30)\,\%$ 
-\cite{Avakian:2010br,Jakob:1997wg,Lorce:2011dv,Pasquini:2008ax}.
+\cite{Jakob:1997wg,Pasquini:2008ax,Avakian:2010br,Lorce:2011dv}.
 The spectator and bag model support WW-type approximations 
@@
 predictions from this model have yet to be tested \cite{Efremov:2010mt}.
+
+\ps{Noteworthy is the result from the chiral quark soliton
+model where the WW-type approximation (\ref{Eq:WW-type-Cahn})
+happens to be exact: $xf^{\perp q}(x,\kperp^2)=f_{1}^q(x,\kperp^2)$
+for quarks and antiquarks \cite{Lorce:2014hxa}. The degrees of freedom
+in this model are quarks, antiqarks and Goldstone bosons which are 
+strongly coupled (the coupling constant is $\sim 4$) and has to be
+solved using nonperturbative techniques (expansion in $1/N_c$ where
+$N_c$ is the number of colors) with the nucleon described as a 
+chiral soliton. In general the model predicts non-zero tilde-terms, for 
+instance $\tilde{e}^a(x)\neq 0$ 
+\cite{Schweitzer:2003uy,Ohnishi:2003mf,Cebulla:2007ej}.
+However, despite strong interactions in this effective theory, the tilde 
+term $\tilde{f}^{\perp q}(x,\kperp^2)$ vanishes exactly in this model 
+\cite{Lorce:2014hxa} and the WW-type approximation (\ref{Eq:WW-type-Cahn})
+becomes exact at the low initial scale of this model of 
+$\mu_0\sim 0.6\,{\rm GeV}$.}
 
@@
 in the context of (\ref{Eq:WW-original1}).
-This means that perturbative QCD does not support the WW-approximation:
-they are certainly not preserved by evolution. However, scaling violations
+This means that perturbative QCD does not support the WW-approximations:
+they certainly are not preserved by evolution. However, scaling violations
 {\it per se} do not need to be large. What is crucial in this context are 
@@
 
-\subsection{Basis functions \& limitations of WW-type approximations}
-\label{Sec-3.7:basis+limitations}
-
-The leading-twist 6 TMDs 
+\subsection{Basis functions for the WW-type approximations}
+\label{Sec-3.7:basis}
+
+The leading--twist 6 TMDs 
 $f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a}$
@@
 It is crucial to take advantage of other processes: Drell-Yan for PDFs and TMDs
-and hadron production in $e^+e^-$ annihilation for FFs, though other processes 
+and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
 play also important roles.
 
-The basis functions allow us to describe in WW-type approximation all other 
+These basis functions allow us to describe in WW-type approximation all other 
 TMDs, and experiments will decide how well the approximations work.
-In two instances, however, we know in advance of limitations, namely in the
-description of T-odd TMDs which appear in the decomposition of the 
+\ps{In some cases, however, we know in advance that the WW-type approximations 
+have limitations, which we discuss in the next section.}
+
+\subsection{Limitation of WW-type approximation for certain T-odd TMDs}
+\label{Sec-3.8:limitations}
+
+\ps{The WW-type approximations have limitations} in the description of 
+those twist-3 T-odd TMDs which appear in the decomposition of the 
 correlator (\ref{Eq:correlator}) with no prefactor of $\kperp$.
@@
 symmetry of strong interactions. This argument does not apply to other T-odd 
-TMDs because they drop out from the $\kperp$-integrate correlator due to 
+TMDs because they drop out from the $\kperp$-integrated correlator due to 
 explicit factors of e.g.\ $\kperp^j$ in the case of the Sivers function.
@@
 Let us first discuss the case of $f_T^a(x,k_\perp)$. Taking the  
-WW-type approximation (\ref{Eq:WW-type-fT}) literally, implies
-$x\int d^2 k_\perp\,f_T^a(x,k_\perp)=-f_{1T}^{\perp(1)a}(x) \neq 0$ 
+WW-type approximation (\ref{Eq:WW-type-fT}) literally \ps{means}
+$x\int d^2 k_\perp\,f_T^a(x,k_\perp)\,\ps{\stackrel{!?}{=}}
+-f_{1T}^{\perp(1)a}(x)\neq0$ 
 at variance with the sum rule (\ref{Eq:sum-rules-T-odd}). We 
@@
 
-\newpage
+%\newpage
 %======= SECTION 4: SIDIS IN WW APPROXIMATION ========================
-\section{SIDIS in WW-type approximation}
+\section{SIDIS in WW-type approximation \ps{and Gaussian model}}
 \label{Sec-4:SIDIS-in-WW-approximation}
@@
 In this section we consequently apply the WW- and WW-type approximation
-to SIDIS.
+to SIDIS, \ps{and describe our procedure to evaluate the structure 
+functions in this approximation and the Gaussian Ansatz which we use
+to model the $k_\perp$ dependence of TMDs.}
 
@@
 The WW- and WW-type approximations are useful for the following
-two leading-twist structure functions 
+two leading--twist structure functions 
 \begin{subequations}\ba
@@
 	{g_T^{\perp a}\to g_1^a}
-	{Eqs.~(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T}),}\\
+	{Eqs.~(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T}),}
+\ea
+\ba
 F_{UL}^{\sin\phi_h} &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,{\cal C}\biggl[
@@
 
+\ps{
+
+\subsection{Gaussian Ansatz for TMDs}
+\label{Sec-4.3:evaluation}
+
+In this work we will use the so-called Gaussian Ansatz for the TMDs and FFs.
+This Ansatz, which for a generic TMD or FF is given by
+\be\label{Eq:Gauss-generic}
+    f(x,\kperp^2) = f(x)\;
+    \frac{e^{-\kperp^2/\avkperp}}{\pi\avkperp} \;,\;\;\;
+    D(z,\pperp^2) = D(z)\,
+    \frac{e^{-\pperp^2/\avpperp}}{\pi\avpperp}\;,
+\ee
+is popular not only because it considerably simplifies the
+calculations. In fact, all convolution integrals of the type 
+(\ref{Eq:def-convolution-integral}) can be solved analytically 
+with this Ansatz. Far more important is the fact that it works 
+phenomenologically with a good accuracy in many practical applications
+\cite{Anselmino:2005nn,Collins:2005ie,D'Alesio:2007jt,Schweitzer:2010tt,
+Signori:2013mda,Anselmino:2013lza}.
+Of course this Ansatz is only a rough approximation. For instance, 
+it is not consistent with general matching expectations when $\kperp$ 
+becomes large \cite{Bacchetta:2008xw}.
+
+Nevertheless, if one limits oneself to work in a regime where the 
+transverse momenta (of hadrons produced in SIDIS, dileptons produced
+in the Drell-Yan process, etc) are small compared to the hard
+scale in the process, then the Ansatz works quantitatively
+very well. The most recent and detailed tests were reported in 
+\cite{Schweitzer:2010tt}, where the Gaussian Ansatz was shown to
+describe the most recent SIDIS data: no deviations were observed 
+within the error bars of the data provided one takes into account 
+the broadening of the Gaussian widths with increasing energy 
+\cite{Schweitzer:2010tt} according
+with expectations from QCD \cite{Aybat:2011zv}.
+The Gaussian Ansatz is approximately compatible with 
+the $\kperp$-shapes obtained from evolution \cite{Aybat:2011zv}
+or fits to high-energy Tevatron data on weak-boson production
+\cite{Landry:2002ix}. Effective models at 
+low \cite{Pasquini:2008ax,Avakian:2010br,Lorce:2011dv} and 
+high \cite{Efremov:2009ze} renormalization scales support this
+Ansatz as a good approximation.
+
+\subsection{Evaluation of structure functions in WW-type \&
+ Gaussian approximation}
+\label{Sec-4.4:evaluation}
+
+The Gaussian Ansatz is compatible with many WW-type type approximations
+but not all. The trivial approximations (\ref{Eq:WW-type-1}) and
+(\ref{Eq:WW-type-eLperp}--\ref{Eq:WW-type-fLperp}) of course 
+cause no issue. 
+The Gaussian Ansatz can also be applied to the nontrivial approximations 
+in Eqs.~(\ref{Eq:WW-type-Cahn}--\ref{Eq:WW-type-gTperp})
+and (\ref{Eq:WW-type-fTperp}), provided the corresponding Gaussian 
+widths are defined to be equal to each other: for example, in the 
+WW-type approximation (\ref{Eq:WW-type-Cahn}),
+$xf^{\perp q}(x,\kperp^2)\approx f_1^q(x,\kperp^2)$, one may 
+assume Gaussian $\kperp$-dependence for $f^{\perp q}(x,\kperp^2)$ 
+and for $f_1^q(x,\kperp^2)$ as long as the Gaussian widths
+of these two TMDs are assumed to be equal.
+
+In the case of the approximations 
+(\ref{Eq:WW-type-5}--\ref{Eq:WW-type-8})
+the situation is different. In these approximations a twist-3 TMD
+is related to a transverse moment of twist-2 TMD. In such cases the 
+Gaussian Ansatz is not compatible with the WW-type approximations:
+for instance, the approximation (\ref{Eq:WW-type-5}) relates
+$xg_T^q(x,\kperp^2)\approx\frac{k_\perp^2}{2M_N^2}\,g_{1T}^{q}(x,\kperp^2)$,
+i.e.\ if $g_{1T}^q(x,\kperp^2)$ was exactly Gaussian then 
+$g_T^q(x,\kperp^2)$ certainly could not be Gaussian. If one would take
+the Gaussian Ansatz and WW-type approximations literally, one clearly
+would deal with an incompatibility. However, we of course must keep 
+in mind that both are approximations.
+
+Some comments are in order to understand how the usage of the Gaussian 
+Ansatz and the WW-type approximations can be reconciled.
+First, let us remark that the individual TMDs, say 
+$g_T^q(x,\kperp^2)$ and $g_{1T}^{q}(x,\kperp^2)$ in our example,
+may each by itself be assumed to be approximately Gaussian in $k_\perp$
+which is supported by quark model calculations \cite{Avakian:2010br}.
+Second, we actually do not need the unintegrated WW-type approximations. 
+For phenomenological applications we can use the WW-type approximations 
+in ``integrated form.''
+
+Let us stress that if one took an unintegrated WW-type approximation of the 
+type $xg_T^q(x,\kperp^2)\approx\frac{k_\perp^2}{2M_N^2}\,g_{1T}^{q}(x,\kperp^2)$
+literally and assumed both TMDs to be exactly Gaussian, one would find
+``incompatibilities:'' perhaps most strikingly in the limit $k_\perp\to 0$
+where the left-hand side is finite while the right-hand side vanishes.
+However, such incompatibilities are washed out and not apparent after
+the convolution integrals defining the structure functions are solved.
+Notice that the failure of the WW-type approximations
+(\ref{Eq:WW-type-5}--\ref{Eq:WW-type-8}) in the limit $k_\perp\to 0$ is 
+not specific to the Gaussian model,
+but a general feature caused by neglecting tilde-terms. This indicates 
+a practical scheme how to use responsibly the WW-type approximations in 
+Eqs.~(\ref{Eq:WW-type-5}--\ref{Eq:WW-type-8}).
+
+Our procedure is as follows. In a first step we assume that all TMDs and 
+FFs are (approximately) Gaussian, and solve the convolution integrals.
+In the second step we use the integrated WW-type approximations to
+simplify the results for the structure functions.
+
+Notice that in principle one could choose a different order
+of the steps: first use WW-type approximations and then
+solve the convolution integrals assuming  Gaussian Ansatz.
+This would constitutes ``alternative scheme'' with 
+in general different (and bulkier) analytical expressions.
+Given the modest understanding of factorization for twist-3 
+TMDs it is not possible to discriminate which scheme might be a
+better approximation. But we convinced ourselves that the two 
+schemes yield similar results for the structure functions, and the 
+differences are numerically within the accuracy expected for
+this approach.
+
+When following the above-described scheme (solving first the 
+convolutions integrals and using then WW-type approximations) 
+we will see that the results for the structure functions can 
+be conveniently expressed in terms of the basis TMDs or their
+adequate transverse moments. We will come back to this point.
+
+Finally, let us recall that the WW-type approximations 
+(\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-last}) for those
+twist-3 T-odd TMDs which are subject to the sum rules
+in Eq.~(\ref{Eq:sum-rules-T-odd}) require special care,
+see the discussion in Sec.~\ref{Sec-3.8:limitations}.
+
+}
+
+\newpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 to App.~\ref{App:basis} for details.
-The four functions $f_1^a, \; g_1^a, \; h_1^a,\; D_1^a$  
-are related to twist-2 collinear functions.
-All collinear functions are calculated at $Q^2 = 2.4$ (GeV$^2$).
-Collinear $f_1(x)$ are from Ref.~\cite{Martin:2009iq},  $g_1(x)$ are from Ref.~\cite{Gluck:1998xa}, and $D_1(z)$ are from Ref.
-~\cite{deFlorian:2007aj}.The other four
-$f_{1T}^{\perp a},  \;h_1^{\perp a},\; H_1^{\perp a} \,$  
-have no collinear counterparts, and we consider their (1)-moments, while 
-for $ h_{1T}^{\perp a}$  we consider the (2)-moment,
-such that parametrizations of TMD functions read
+The four functions $f_1^a, \; g_1^a, \; h_1^a,\; D_1^a$  are related to 
+twist-2 collinear functions. All collinear functions are calculated at 
+$Q^2 = 2.4$ GeV$^2$. Collinear $f_1^a(x)$ are from Ref.~\cite{Martin:2009iq},  
+$g_1^a(x)$ are from Ref.~\cite{Gluck:1998xa}, and $D_1^a)$ are from 
+Ref.~\cite{deFlorian:2007aj}. The other four TMDs 
+\ps{have no collinear counterparts. 
+For $f_{1T}^{\perp a},\;h_1^{\perp a},\;H_1^{\perp a}$ it is convenient to 
+consider their (1)-moments, and for $ h_{1T}^{\perp a}$  the (2)-moment.
+This has two important advantages. First, this step simplifies the
+the Gaussian Ansatz expressions, and the Gaussian width parameters are
+largely absorbed in the definitions of the transverse moments which 
+helps to minimize the model-dependence. Second,
+the $k_\perp$-moments of these TMDs have in principle simple definitions
+in QCD (whereas e.g.\ the function $f_{1T}^{\perp q}(x)$ can be computed in
+models but is very cumbersome to define in QCD).
+Thus the parametrizations for the basis functions read}
 \begin{subequations}\ba
 	f^a_1(x,\kperp^2) &=& f^a_1(x)\;
-    \frac{e^{-\kperp^2/\avkperp_{f_1}}}{\pi\avkperp_{f_1}} \, ,\\
+    	\frac{1}{\,\pi\avkperp_{f_1}}\;e^{-\kperp^2/\avkperp_{f_1}} \, ,
+	\label{Eq:Gauss-f1}\\
     	D^a_1(z,\pperp^2) &=& D_1^a(z)\,
-    \frac{e^{-\pperp^2/\avpperp_{D_1}}}{\pi\avpperp_{D_1}} \, ,\\
+    	\frac{1}{\,\pi\avpperp_{D_1}}\;e^{-\pperp^2/\avpperp_{D_1}} \, ,
+	\label{Eq:Gauss-D1}\\
 	g^a_1(x,\kperp^2) &=& g^a_1(x)\;
-    \frac{e^{-\kperp^2/\avkperp_{g_1}}}{\pi\avkperp_{g_1}} \, ,\\    
-f_{1T}^{\perp q}(x,\kperp^2) &=&  f_{1T}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{f_{1T}^\perp}^2} e^{-\kperp^2/{\avkperp_{f_{1T}^\perp}}} \, ,\\
-h_{1}^{q} (x, \kperp^2) &=&h_{1}^{q} (x)  \frac{e^{-{\kperp^2}/{\avkperp_{h_1} }}}{\pi \avkperp_{h_1}}\, ,\\
-H_{1}^{\perp}(z,\pperp^2) &=&  H_{1}^{\perp (1)}(z)   \frac{2 z^2 m_h^2}{\pi \avpperp_{H_{1}^\perp}^2} e^{-\pperp^2/{\avpperp_{H_{1}^\perp}}}\, ,\\
-h_{1}^{\perp q}(x,\kperp^2) &=&  h_{1}^{\perp (1) q}(x)   \frac{2 M^2}{\pi \avkperp_{h_{1}^\perp}^2} e^{-\kperp^2/{\avkperp_{h_{1}^\perp}}}\, ,\\
-h_{1T}^{\perp q}(x,\kperp^2) &=&  h_{1T}^{\perp (2) q}(x)   \frac{2 M^4}{\pi \avkperp_{h_{1T}^\perp}^3} e^{-\kperp^2/{\avkperp_{h_{1T}^\perp}}} \, ,
+    	\frac{1}{\,\pi\avkperp_{g_1}}\;e^{-\kperp^2/\avkperp_{g_1}} \, ,
+	\label{Eq:Gauss-g1}\\
+	h_{1}^{q} (x, \kperp^2) &=& h_{1}^{q} (x)\;
+  	\frac{1}{\,\pi \avkperp_{h_1}}\;e^{-{\kperp^2}/{\avkperp_{h_1} }} \, ,
+	\label{Eq:Gauss-h1}\\
+	H_{1}^{\perp}(z,\pperp^2) &=&  H_{1}^{\perp (1)}(z) \;  
+	\frac{2 z^2 m_h^2}{\pi \avpperp_{H_{1}^\perp}^2} \;
+	e^{-\pperp^2/{\avpperp_{H_{1}^\perp}}}\, ,\\
+	f_{1T}^{\perp q}(x,\kperp^2) &=&  f_{1T}^{\perp (1) q}(x)   \;
+	\frac{2 M^2}{\pi \avkperp_{f_{1T}^\perp}^2} \;
+	e^{-\kperp^2/{\avkperp_{f_{1T}^\perp}}} 
+	\label{Eq:Gauss-f1Tperp}\, ,\\
+	h_{1}^{\perp q}(x,\kperp^2) &=&  h_{1}^{\perp (1) q}(x)\;
+   	\frac{2 M^2}{\pi \avkperp_{h_{1}^\perp}^2}\;
+ 	e^{-\kperp^2/{\avkperp_{h_{1}^\perp}}}\,
+	\label{Eq:Gauss-h1perp}\, ,\\
+	h_{1T}^{\perp q}(x,\kperp^2) &=&  h_{1T}^{\perp (2) q}(x)\;
+   	\frac{2 M^4}{\pi \avkperp_{h_{1T}^\perp}^3} \;
+	e^{-\kperp^2/{\avkperp_{h_{1T}^\perp}}}
+	\label{Eq:Gauss-h1Tperp}\, .
 \ea\end{subequations}
-see App.~\ref{App:basis} for details.
+The parametrizations of the basis functions and the Gaussian model
+parameters are described in detail in App.~\ref{App:basis}.
 
@@
 
-\subsection{\boldmath Gauss Ansatz and $F_{UU}$ structure function}
+\subsection{\boldmath Leading twist $F_{UU}$ and Gaussian Ansatz}
 \label{Sec-5.1:FUU-basis}
 
-Throughout this work we use the so-called Gauss Ansatz for the
-transverse momentum dependent distribution and fragmentation functions. 
-This Ansatz is popular not only because it considerably simplifies the
-calculations. In fact, all convolution integrals of the type 
-(\ref{Eq:def-convolution-integral}) can be solved analytically with 
-this Ansatz.
-Far more important is the fact that it works phenomenologically
-with a good accuracy in many practical applications
+As explained in Sec.~\ref{Sec-4.3:evaluation} the Gaussian Ansatz is chosen
+not only because it considerably simplifies the calculations, but more 
+importantly because it works phenomenologically with a good accuracy 
+in many processes including SIDIS
 \cite{Anselmino:2005nn,Collins:2005ie,D'Alesio:2007jt,Schweitzer:2010tt,
 Signori:2013mda,Anselmino:2013lza}.
-It should be kept in mind that the Gauss Ansatz can, of course, 
-be only a rough approximation. For instance, it is not 
-consistent with general matching expectations when $\kperp$ 
-becomes large \cite{Bacchetta:2008xw}. Nevertheless, if
-one limits oneself to work in a region where the transverse
-momenta (of hadrons produced in SIDIS,  dileptons produced
-in the Drell-Yan process, etc) are small with respect to the hard
-scale in the process, then the Ansatz works quantitatively
-very well. The most recent and detailed tests were reported in 
-\cite{Schweitzer:2010tt}, where the Gauss Ansatz was shown to
-describe the most recent SIDIS data. No deviations could
-be observed within the error bars of the data provided one
-takes into account the broadening of the Gaussian widths
-with increasing energy \cite{Schweitzer:2010tt} according
-with expectations from QCD \cite{Aybat:2011zv}.
-Remarkably, the Gauss Ansatz is approximately compatible with 
-the $\kperp$-shapes obtained from evolution \cite{Aybat:2011zv}
-or fits to high-energy Tevatron data on weak-boson production
-\cite{Landry:2002ix}. On the other end, effective models at 
-low \cite{Pasquini:2008ax,Avakian:2010br} and intermediate 
-\cite{Efremov:2009ze} energies also support it approximately.
-
-The Gaussian Ansatz for the unpolarized TMD and unpolarized FF 
-is given by
-\be\label{Eq:Gauss-f1-D1}
-    f^a_1(x,\kperp^2) = f^a_1(x)\;
-    \frac{e^{-\kperp^2/\avkperp_{f_1}}}{\pi\avkperp_{f_1}} \;,\;\;\;
-    D^a_1(z,\pperp^2) = D_1^a(z)\,
-    \frac{e^{-\pperp^2/\avpperp_{D_1}}}{\pi\avpperp_{D_1}}\;.
-\ee
+
+The Gaussian Ansatz for the unpolarized TMD and FF 
+is given by Eqs.~(\ref{Eq:Gauss-f1},~\ref{Eq:Gauss-D1}).
 The parameters $\avkperp_{f_1}$ and $\avpperp_{D_1}$ can
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
+\centering
+\includegraphics[height=3cm]{\FigPath/Fig02a-JLab-ratio-pT-v5-NEW.pdf}  \quad
+\includegraphics[height=3cm]{\FigPath/hermes_pip.pdf} \quad
+\includegraphics[height=3cm]{\FigPath/compass_hp.pdf} 
+\caption{\label{FUU-show-pT-dependence}
+Examples of the 
+	description of transverse momenta of hadrons in unpolarized SIDIS. 
+Left panel: 
+	cross section for $\pi^+$ production normalized with 
+	respect to its value at zero transverse momentum at 
+	$\la Q^2\ra=2.37\,{\rm GeV}^2$, $\la x\ra=0.24$, $\la z\ra=0.30$ 
+	at JLab with 5.75 GeV beam \cite{Osipenko:2008aa}, cf.\  
+	\cite{Schweitzer:2010tt}.
+Middle panel: 
+	HERMES multiplicity (\ref{Eq:multiplicity-HERMES}) at 
+	$\la Q^2\ra=2.87\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.22$
+	from \cite{Airapetian:2012ki}.
+Right panel: 
+	COMPASS multiplicity (\ref{Eq:multiplicity-COMPASS}) at 
+	$\la Q^2\ra=20\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.2$
+	from \cite{Aghasyan:2017ctw}.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The structure function $F_{UU}$ needed for our analysis reads
@@
 	\label{Eq:FUU-Phperp}\\
-	F_{UU}(x,z) \equiv \int d^2 \Phperp \, F_{UU}(x,z,\Phperp) 
+	F_{UU}(x,z) %\equiv \int d^2 \Phperp \, F_{UU}(x,z,\Phperp) 
 	&=& x \sum_q e_q^2\,f^q_1(x)\,D_1^q(z)  \, ,
@@
 with the understanding that the convenient abbreviation $\lambda$ is expressed 
-in terms of the Gaussian widths of the {\it preceding} TMD and FF. Notice 
+in terms of the Gaussian widths of the {\it preceeding} TMD and FF. Notice 
 that ${\cal G}(\Phperp)\equiv {\cal G}(x,z,\Phperp)$ and that in general
@@
 (\ref{Eq:FUU}). In our effective description this is step is trivial. In 
-QCD the connection of TMDs to PDFs is far more subtle \cite{Collins:2016hqq}.
-Fig.~\ref{FUU-show-pT-dependence} illustrates how the Gauss Ansatz
-describes selected SIDIS data. In Fig.~\ref{FUU-show-pT-dependence} (b) we plot HERMES multiplicity \cite{Airapetian:2012ki}
-\be
-M_n^h(x,z,\Phperp)  \equiv 2 \pi \Phperp \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
-\ee
-at $\la Q^2\ra=2.87\,{\rm GeV}^2$,
-$\la x\ra  =0.15$, $\la z\ra  =0.22$ for $\pi^+$ production on the proton target.
-In Fig.~\ref{FUU-show-pT-dependence} (c) we plot COMPASS multiplicity \cite{Aghasyan:2017ctw}
-\be
-n^h(x,z,\Phperp)  \equiv \pi \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
-\ee
-at $\la Q^2\ra=20\,{\rm GeV}^2$,
-$\la x\ra  =0.15$, $\la z\ra  =0.2$ for $h^+$ production on the deuterium target.
+QCD the connection of TMDs to PDFs is subtle \cite{Collins:2016hqq}.
+Figure~\ref{FUU-show-pT-dependence} illustrates how the Gaussian Ansatz
+describes selected SIDIS data. 
+In Fig.~\ref{FUU-show-pT-dependence} (a) we show CLAS data 
+\cite{Osipenko:2008aa} on $\pi^+$ production from proton 
+with a 5.75 GeV beam which shows a Gaussian $P_{hT}$-dependence
+over 2 orders of magnitude, see \cite{Schweitzer:2010tt} for details.
+In Fig.~\ref{FUU-show-pT-dependence} (b) we plot 
+the HERMES multiplicity~\cite{Airapetian:2012ki}
+\be\label{Eq:multiplicity-HERMES}
+	M_n^h(x,z,\Phperp)  \equiv 
+	2 \pi \Phperp \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
+\ee
+at $\la Q^2\ra=2.87\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.22$ 
+for $\pi^+$ production on the proton target.
+In Fig.~\ref{FUU-show-pT-dependence} (c) we plot the COMPASS multiplicity 
+\cite{Aghasyan:2017ctw}
+\be\label{Eq:multiplicity-COMPASS}
+	n^h(x,z,\Phperp)  \equiv 
+	\pi \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
+\ee
+at $\la Q^2\ra=20\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.2$ 
+for $h^+$ production on the deuterium target.
 
@@
 on the used parametrizations (App.~\ref{App:basis}), and for 
-technical details on the Gauss Ansatz (App.~\ref{App:factor}).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t!]
-\centering
-\includegraphics[width=0.3\textwidth]{\FigPath/Fig02a-JLab-ratio-pT-v5.pdf}  (a)
-\includegraphics[width=0.37\textwidth]{\FigPath/hermes_pip.pdf} (b)
-\includegraphics[width=0.37\textwidth]{\FigPath/compass_hp.pdf} (c)
-\caption{\label{FUU-show-pT-dependence}
-Examples of the description of transverse momenta of hadrons in 
-unpolarized SIDIS. 
-(a) Differential cross section at $\la Q^2\ra=2.37\,{\rm GeV}^2$,
-$\la x\ra  =0.24$, $\la z\ra  =0.30$ measured at JLab with a 5.75 GeV 
-beam \cite{Osipenko:2008aa}. Theoretical curve from Gauss model 
-following Ref.~\cite{Schweitzer:2010tt}.
-(b) Example for HERMES multiplicities \cite{Airapetian:2012ki} at $\la Q^2\ra=2.87\,{\rm GeV}^2$,
-$\la x\ra  =0.15$, $\la z\ra  =0.22$.
-(b) Example for COMPASS multiplicities \cite{Aghasyan:2017ctw} at $\la Q^2\ra=20\,{\rm GeV}^2$,
-$\la x\ra  =0.15$, $\la z\ra  =0.2$.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+technical details on the Gaussian Ansatz (App.~\ref{App:factor}).
 
@@
 %========= SECTION 6: TESTING APPROACH WITH A_LL =====================
-\subsection{\boldmath Leading twist $A_{LL}$: 
-           first test of intrinsic $\kperp$ beyond unpolarized case}
+\subsection{\boldmath Leading twist $A_{LL}$ and first test of Gaussian Ansatz
+	in polarized scattering}
 \label{Sec-5.2:FLL-basis}
 
-In this Section we discuss the leading twist double spin asymmetry 
-$A_{LL} \propto g_{1}^a D_1^a$ which does not require a WW-type approximation
-but is important for two reasons. First, we review one of our 
-``basis functions'' $g_1^a(x)$, and similarly we will review below 
-also other ``basis functions.'' Second, throughout this work we use the 
-Gaussian Ansatz demonstrated to provide good services in unpolarized case 
+The Gaussian Ansatz is useful in unpolarized case 
 \cite{Anselmino:2005nn,Collins:2005ie,D'Alesio:2007jt,Schweitzer:2010tt,
-Signori:2013mda,Anselmino:2013lza}. However, nothing is known about
-the applicability of the Gaussian Ansatz in polarized case.
-The JLab data \cite{Avakian:2010ae} on $A_{LL}(\Phperp)$ put us 
-in the position to conduct a first ``test'' of our understanding of 
-the $\kperp$-behavior of polarized partons. To have an ``informed idea''
-about the Gaussian width of $g_{1}(x,\kperp)$ we will explore information
-from the exploratory lattice QCD study of TMDs \cite{Hagler:2009mb}.
-
-We assume Gaussian form for $g_{1}^{a}(x,\kperp^2)$
-\ba\label{eq:g1}
-	g_{1}^{a}(x,\kperp^2) = g_{1}^{a}(x)\,
-	\frac{e^{-\kperp^2/{\avkperp_{g_{1}}}}}{\pi \avkperp_{g_{1}}}\,\; ,
-\ea
-and resort to the lattice QCD results \cite{Hagler:2009mb} to gain 
-an estimate on width $\avkperp_{g_{1}}$, see App.~\ref{App:basis-g1}.
-
-With $\lambda=z^2\la\kperp^2\ra_{g_1}+\la\pperp^2\ra_{D_1}$ implicit in 
-${\cal G}(\Phperp)$, the structure function $F_{LL}$  reads
+Signori:2013mda,Anselmino:2013lza}, but nothing is known about its 
+applicability to spin assymetries. The JLab data \cite{Avakian:2010ae} 
+on $A_{LL}(\Phperp)$ put us in the position to conduct a first ``test'' 
+for polarized partons. We assume Gaussian form for $g_{1}^{a}(x,\kperp^2)$, 
+Eq.~(\ref{Eq:Gauss-g1}), and use lattice QCD results \cite{Hagler:2009mb} 
+to estimate the width $\avkperp_{g_{1}}$, see App.~\ref{App:basis-g1}.
+With $\lambda=z^2\la\kperp^2\ra_{g_1}+\la\pperp^2\ra_{D_1}$ implicit 
+in ${\cal G}(\Phperp)$, the structure function $F_{LL}$  reads
 \begin{subequations}\ba
@@
 	F_{LL}(x,z)  
-	&=& x \sum_q e_q^2\,g^q_1(x)\,D_1^q(z)  \, ,
+	&=& x \sum_q e_q^2\,g^q_1(x)\,D_1^q(z)  \, .
 	\label{Eq:FLL}
@@
 \caption{\label{jlab_ALL} 
-	$A_{LL,\la y\ra}$ asymmetry compared with Jefferson Lab experimental 
-	results Ref.~\cite{Avakian:2010ae} for $\pi^+$ (left panel) and 
-	$\pi^-$ (right panel). Solid lines are computations with mean 
-	values of kinematic variables  $\langle x \rangle = 0.25$, 
-	$\langle z \rangle = 0.5$, $\langle Q^2 \rangle = 1.7$ GeV$^2$.
+	$A_{LL,\la y\ra}$ asymmetry compared to JLab data \cite{Avakian:2010ae}
+ 	for $\pi^+$, $\pi^0$, $\pi^-$. The solid lines are 
+	our computations for the mean values of kinematical variable
+	$\langle x \rangle = 0.25$, 
+	$\langle z \rangle = 0.5$, $\langle Q^2 \rangle = 1.67$ GeV$^2$.
 }
@@
 and denominator) over the kinematics of \cite{Avakian:2010ae} is implied. 
-We  compare our results for $A_{LL,\la y\ra}(\Phperp)$ to Jefferson Lab data 
-\cite{Avakian:2010ae} in Fig.~\ref{jlab_ALL}.
-
-In our approach we use lattice results from \cite{Hagler:2009mb} to
-constrain the Gaussian width $\la\kperp^2\ra_{g_1}$, see App.~\ref{App:basis-g1}.
-All other ingredients in (\ref{Eq:ALLy}) are known and 
-tested through other observables, see Sec.~\ref{Sec-5.1:FUU-basis}.
-Therefore Fig.~\ref{jlab_ALL} provides several important tests.
-First, the Jefferson Lab data \cite{Avakian:2010ae} is compatible
-with the Gauss Ansatz within error bars. Second, the lattice QCD results 
-in the way we use them in App.~\ref{App:basis-g1} give an appropriate 
-description of these data.\footnote{
+We use the lattice data \cite{Hagler:2009mb} to
+constrain the Gaussian width $\la\kperp^2\ra_{g_1}$ as described in 
+App.~\ref{App:basis-g1}. All other ingredients in (\ref{Eq:ALLy}) are known 
+and tested through other observables in Sec.~\ref{Sec-5.1:FUU-basis}.
+Therefore the comparison of our results to JLab data \cite{Avakian:2010ae} 
+shown in Fig.~\ref{jlab_ALL} provides several important tests.\footnote{
 	Another important test was already presented in 
@@
 	at least to a very good approximation \cite{Avakian:2010ae}.}
+First, the JLab data \cite{Avakian:2010ae} are compatible
+with the Gaussian Ansatz within error bars. Second, the lattice results
+in the way we use them in App.~\ref{App:basis-g1} give an appropriate 
+description of the data.
 
@@
 Of course, at this point one could argue that the WW- and WW-type 
-approximations (\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-g1T}) also
+approximations (\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}) also
 dictate that $g_{1T}^\perp$ and $h_{1L}^\perp$ have the same Gaussian
@@
 
-The $F_{UT}^{\sin(\phi_h-\phi_S)}$ modulation of SIDIS cross section is related to  the Sivers function~\cite{Sivers:1989cc}, which describes the number density of unpolarized quarks inside a 
-transversely polarized proton, has so far received the widest attention, 
-from both phenomenological and experimental points of view.
-
-The Sivers function $f_{1T}^\perp$ is related to initial and final state interactions of the struck quark and the rest of the nucleon and could not exist 
-without the contribution of the orbital angular momentum of partons to the spin of the nucleon. 
-As such it encodes the correlation between the partonic intrinsic motion and the transverse spin of the nucleon, and it generates a dipole deformation in momentum space.
-
+The $F_{UT}^{\sin(\phi_h-\phi_S)}$ \ps{structure function} is related to the 
+Sivers function~\cite{Sivers:1989cc}, which describes the \ps{distribution}
+of unpolarized quarks inside a transversely polarized proton, has so far 
+received the widest attention, from both phenomenological and experimental 
+points of view.
+
+The Sivers function $f_{1T}^\perp$ is related to initial and final state 
+interactions of the struck quark and the rest of the nucleon and could 
+not exist without the contribution of the orbital angular momentum of 
+partons to the spin of the nucleon. As such it encodes the correlation 
+between the partonic intrinsic motion and the transverse spin of the 
+nucleon, and it generates a dipole deformation in momentum space.
 Over the years, the Sivers function has been extracted from SIDIS data
@@
 	&=& - x\sum_q e_q^2\,f_{1T}^{\perp (1) q}(x)\,D_1^{q}(z)\;
-	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,,\label{FUTsiv-Gauss}
+	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,,
+	\label{FUTsiv-Gauss}
 \ea\end{subequations}
@@
 In all other cases, despite integration over $\Phperp$, we end up 
-always with true convoluted TMDs (here within Gauss model).
+always with true convoluted TMDs (here within Gaussian model).
 We stress this important point by displaying the dependence of 
@@
 The asymmetries $A_{UT}^{\sin(\phi_h-\phi_S)}= F_{UT}^{\sin(\phi_h-\phi_S)}/F_{UU}$  
-and comparison to HERMES data \cite{Airapetian:2009ae} are plotted in Fig.~\ref{aut_f1t_jlab}.
+\ps{are plotted in Fig.~\ref{aut_f1t_jlab} in comparison to HERMES data 
+on charged pion production from a proton target \cite{Airapetian:2009ae}.
+The $x$- and $P_{hT}$-dependencies of the asymmetry are displayed. The 
+latter shows that the Gaussian model works well also in this case.
+COMPASS data are described equally well by the fit \cite{Anselmino:2011gs}. }
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_x.pdf}  
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_PT.pdf}
-\caption{\label{aut_f1t_jlab} Comparison of calculation of $A_{UT}^{\sin(\phi_h-\phi_S)}$  using fit results of Ref.~\cite{Anselmino:2011gs} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ and HERMES data \cite{Airapetian:2009ae}.
-}
+\includegraphics[width=0.43\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
+\includegraphics[width=0.43\textwidth]{\FigPath/AUTSivers_PT.pdf}
+\caption{\label{aut_f1t_jlab} The Sivers asymmetry $A_{UT}^{\sin(\phi_h-\phi_S)}$  
+	as a function of $ x $ (left panel) and $P_{hT}$ (right panel).
+	The data are from the HERMES experiment and refer to the mean values
+	$\la x\ra = 0.1$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ 
+	\cite{Airapetian:2009ae}. The theoretical curves are based on 
+	the fit results of Ref.~\cite{Anselmino:2011gs}.}
 \end{figure}
@@
 
-The $F_{UT}^{\sin(\phi_h+\phi_S)}$ modulation of the SIDIS cross section is due to convolution of the transversity distribution $h_1$, which is the only source of information on the tensor charge of the
-nucleon, and the Collins FF $H_1^\perp$, that decodes the fundamental correlation between
-the transverse spin of a fragmenting quark and the transverse momentum
-of the final produced hadron.
-
-There are many extractions of $h_1$ and $H_1^\perp$ from a combined fit of SIDIS and $e^+e^-$ data, for instance those of Refs.~\cite{Anselmino:2013vqa,Kang:2014zza,Anselmino:2015sxa}.
+The $F_{UT}^{\sin(\phi_h+\phi_S)}$ modulation of the SIDIS cross section is due 
+to the convolution of the transversity distribution $h_1$ \ps{and the Collins 
+FF $H_1^\perp$. Transversity can in principle be accessed also as a PDF in
+Drell-Yan. It describes the distribution of transversely polarized quarks
+in a transversely polarized nucleon, and} is the only source of information 
+on the tensor charge of the nucleon. The Collins FF $H_1^\perp$ decodes the 
+fundamental correlation between the transverse spin of a fragmenting quark 
+and the transverse momentum of the final produced hadron \cite{Collins:1992kk}.
+
+There are many extractions of $h_1$ and $H_1^\perp$ from a 
+combined fit of SIDIS and $e^+e^-$ data, for instance those of 
+Refs.~\cite{Anselmino:2013vqa,Kang:2014zza,Anselmino:2015sxa}.
+In this work we will use the extractions of $h_1$ and $H_1^\perp$ 
+from Ref.~\cite{Anselmino:2013vqa}.
 
@@
 
-The asymmetries $A_{UT}^{\sin(\phi_h+\phi_S)}=F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$
-and comparison to HERMES data \cite{Airapetian:2010ds} are plotted in Fig.~\ref{aut_h1_jlab}.
+The asymmetries $A_{UT}^{\sin(\phi_h+\phi_S)}= F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$  
+\ps{are plotted in Fig.~\ref{aut_h1_jlab} in comparison to HERMES data 
+on charged pion production from a proton target \cite{Airapetian:2009ae}.
+Also in Fig.~\ref{aut_h1_jlab} we show the $x$- and $P_{hT}$-dependencies 
+of this azimuthal spin asymmetry. The right panel of Fig.~\ref{aut_h1_jlab}
+on the $P_{hT}$-dependence shows that the data are compatible with the 
+Gaussian Ansatz. Let us remark that the COMPASS data are described equally 
+well by the fit of Ref.~\cite{Anselmino:2013vqa}.}
 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_PT.pdf}
-\caption{\label{aut_h1_jlab} Comparison of calculation of $A_{UT}^{\sin(\phi_h+\phi_S)}$  using fit results of Ref.~\cite{Anselmino:2013vqa} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ and HERMES data \cite{Airapetian:2009ae}.
-}
+\caption{\label{aut_h1_jlab} The Collins asymmetry $A_{UT}^{\sin(\phi_h+\phi_S)}$  
+	as a function of $ x $ (left panel) and $P_{hT}$ (right panel).
+	The data are from the HERMES experiment and refer to the mean values
+	$\la x\ra = 0.1$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ 
+	\cite{Airapetian:2009ae}. The theoretical curves are based on 
+	the fit results of Ref.~\cite{Anselmino:2013vqa}.\newline
+	\red{Do we cite here the right HERMES paper? Please, double check.}}
 \end{figure}
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_PT.pdf}
-\caption{\label{auu_cos2phi_jlab} Comparison of calculation of $A_{UU}^{\cos(2\phi_h)}$  using fit results of Ref.~\cite{Barone:2015ksa} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ and HERMES data \cite{Giordano:2009hi}.
+\caption{\label{auu_cos2phi_jlab} Comparison of calculation of 
+	$A_{UU}^{\cos(2\phi_h)}$  using fit results of Ref.~\cite{Barone:2015ksa} 
+	as a function of $x$ (left panel), and as a function of $P_{hT}$ 
+	(right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, 
+	$\la Q^2\ra = 2.4$ GeV$^2$ and HERMES data \cite{Airapetian:2012yg}.
 }
@@
 
-Asymmetries $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$  for  
-HERMES are plotted in Fig.~\ref{auu_cos2phi_jlab}.
-In the Fig.~\ref{auu_cos2phi_jlab} we plot only the
+Asymmetries $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$  for HERMES 
+are plotted in Fig.~\ref{auu_cos2phi_jlab} where we only considered the
 Boer-Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$ which does not describe
@@
 which were corrected for Cahn effect as good as it is possible at
-the current stage of art. It is unknown whether other asymmetries
+the current state of art. It is unknown whether other asymmetries
 could be similarly effected by such type of power-corrections.
@@
 
-Asymmetries $A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ for 
-COMPASS data \cite{Parsamyan:2010se} are plotted in Fig.~\ref{aut_h1tp_jlab}.
+The preliminary COMPASS data \cite{Parsamyan:2010se} for 
+$A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ 
+are plotted in Fig.~\ref{aut_h1tp_jlab}.
 Clearly, the pretzelosity TMD is the least known of the basis TMDs.
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_PT.pdf}
-\caption{\label{aut_h1tp_jlab}  Comparison of calculation of $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  using fit results of Ref.~\cite{Lefky:2014eia} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ and preliminary COMPASS data \cite{Parsamyan:2010se}.
+\caption{\label{aut_h1tp_jlab}  Comparison of calculation of $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  using fit results of Ref.~\cite{Lefky:2014eia} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 3.6$ GeV$^2$ and preliminary COMPASS data \cite{Parsamyan:2010se}.
 }
@@
 
-Two out of the 8 leading-twist structure functions can be 
-described in the WW-type approximation thanks to the relations 
-(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}) which allow us
-to express $g_{1T}^{\perp (1) q}(x)$ and $h_{1L}^{\perp (1) q}(x)$ on 
-the basis of available information on $g_1^q(x)$ and $h_1^a(x)$,
-see Fig.~\ref{g1t_h1l_functions}.
+Two out of the 8 leading--twist structure functions can be 
+described in WW-type approximation thanks to 
+Eqs.~(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}) which 
+relate $g_{1T}^{\perp (1) q}(x)$ and $h_{1L}^{\perp (1) q}(x)$ to the
+basis functions $g_1^q(x)$ and $h_1^a(x)$, see Fig.~\ref{g1t_h1l_functions}.
 In this section we discuss the associated asymmetries.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/g1t.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/h1lperp.pdf}
+\includegraphics[width=0.3\textwidth]{\FigPath/g1t.pdf} \quad
+\includegraphics[width=0.3\textwidth]{\FigPath/h1Lperp.pdf}
 	\caption{\label{g1t_h1l_functions} 
 	$g^{\perp (1) q}_{1T}(x)$ (left panel) and
-	$h^{\perp (1) q}_{1L}(x)$ distributions (right panel) for 
-	$u$- and $d$-flavor. 
-}
+	$h^{\perp (1) q}_{1L}(x)$ distributions (right panel) 
+	for $u$- and $d$-flavor 
+	as predicted by the WW-ype approximations in
+	Eqs.~(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}).}
 \end{figure}
 
+\newpage
 \subsection{\boldmath Leading twist $A_{LT}^{\cos(\phi_h-\phi_S)}$}
@@
 
-We assume for $g^{\perp}_{1T}$ the Gaussian Ansatz as follows 
-\cite{Kotzinian:2006dw} 
-\be
-	g^{\perp q}_{1T}(x,\kperp^2) = 
-	g^{\perp (1) q}_{1T}(x)\,\frac{2 M^2}{\pi \avkperp_{g_{1T}^\perp}^2}\,
-	e^{-\kperp^2/{\avkperp_{g_{1T}^\perp}}}\;,
-	\label{eq:g1t}
-\ee
-and evaluate $g^{\perp (1) q}_{1T}(x)$ using Eq.~(\ref{Eq:WW-approx-g1T})
-which yields the result shown in Fig.~\ref{g1t_h1l_functions}.
+We assume for $g^{\perp}_{1T}$ the Gaussian Ansatz as shown 
+in Eq.~(\ref{eq:g1t}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, 
+see also \cite{Kotzinian:2006dw}, and evaluate $g^{\perp (1) q}_{1T}(x)$ 
+using Eq.~(\ref{Eq:WW-approx-g1T}) which yields the result 
+shown in Fig.~\ref{g1t_h1l_functions}.
 For our numerical estimates we use $\avkperp_{g_{1T}^\perp} = \avkperp_{g_{1}}$ 
@@
 
-In the Gauss Ansatz the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$ 
+In the Gaussian Ansatz the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$ 
 has the form
@@
 see App.~\ref{App:convol-details} for details.
-The $g^{\perp q}_{1T}$ and the Sivers function $f^{\perp q}_{1T}$ are both 
-constrained by the positivity bound \cite{Bacchetta:1999kz} 
-\be
-	\frac{\kperp^2}{M^2}\left( (g^{\perp q}_{1T}(x,\kperp^2))^2 
-	+ (f_{1T}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 
-\ee
-so that using our Gaussian parametrizations from Eqs.~(\ref{Eq:Gauss-f1-D1},\ref{eq:g1t},\ref{sivers_new}) one has
-\be
-\frac{(f_{1}^{q}(x))^2}{16\pi M^2} - \frac{(f_{1T}^{\perp q}(x))^2}{4\pi \avkperp_{f_{1T}^\perp} } -
-\frac{(g_{1T}^{\perp q}(x))^2}{4\pi \avkperp_{g_{1T}^\perp} } \ge 0
-\label{eq:positivity}
-\ee
-see Fig.~\ref{g1t_pos} where RHS of this equation multiplied by $16\pi M^2$ is shown.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/g1t_positivity.pdf}  
-	\caption{\label{g1t_pos} 
-	LHS of Eq.~\eqref{eq:positivity}.
-}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/ALT_COMPASS_x.pdf}  
+%\includegraphics[width=0.3\textwidth]{\FigPath/ALT_COMPASS_x.pdf}  
+\includegraphics[width=0.9\textwidth]{Fig-COMPASS-A_LT_Pr10.pdf}
 	\caption{\label{g1t_jlab} 
-	$A_{LT}^{\cos(\phi_h -\phi_S)}$  as a function of $ x $  at typical kinematics 
-	of COMPASS, 
-	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$.
-	\newline\PS{Can we compare here to COMPASS data from 
-	\cite{Kotzinian:2007uv}?}}
+	Asymmetries as functions of $x$ from scattering of 160 GeV
+	longitudinally polarized muons off a transversely polarized 
+	proton target \cite{Parsamyan:2015dfa}.
+	Left panel: 
+	leading-twist asymmetry $A_{LT}^{\cos(\cos\phi_h-\phi_S)}$ 
+	described in Sec.~\ref{Sec-6.1:FLTcosphi-phiS}.
+	Middle panel: 
+	subleading-twist $A_{LT}^{\cos\phi_S}$ 
+	discussed in Sec.~\ref{Sec-7.2:FLTcosphiS}.
+	Right panel: 
+	subleading-twist $A_{LT}^{\cos(2\cos\phi_h-\phi_S)}$
+	on which we comment in Sec.~\ref{Sec-7.5:FLTcos2phi-phiS}.}
 \end{figure}
@@
 
-The asymmetry  $A_{LT}^{\cos(\phi_h -\phi_S)}$ as a function of $x$  
-for COMPASS is plotted in Fig.~\ref{g1t_jlab}.
+The left panel of Fig.~\ref{g1t_jlab} shows the 2010 COMPASS data 
+for $A_{LT}^{\cos(\phi_h -\phi_S)}$ \cite{Parsamyan:2015dfa} measured 
+with 160 GeV longitudinally polarized muons impinging on a 
+transversely polarized proton (NH$_3$) target \cite{Goertz:2002vv}. 
+As at COMPASS about $90\,\%$ of charged hadrons are $\pi^\pm$, in our 
+calculation we approximate charged hadron fragmentation functions by 
+$D_1^a(z)$ of pions, see App.~\ref{App:basis-f1-D1}.
+Clearly, our results describe the data rather well within the 
+experimemental uncertainties. We observe that the WW-type 
+approximation works in this case. For comparison also results from 
+\cite{Kotzinian:2006dw,Kotzinian:2008fe,Boffi:2009sh} are shown.
+The results shown in middle and right panel of Fig.~\ref{g1t_jlab} will be 
+discussed in Secs.~\ref{Sec-7.2:FLTcosphiS},~\ref{Sec-7.5:FLTcos2phi-phiS}.
 
 \newpage
+
 \subsection{\boldmath 
@@
 
-We assume Gaussian form for Kotzinian-Mulders function $h_{1L}^{\perp a}$:
-\be
-	h_{1L}^{\perp a}(x,\kperp^2) = h_{1L}^{\perp (1) a}(x)\,
-	\frac{2 M^2}{\pi{\avkperp_{h_{1L}^\perp}^2}}\,e^{-\kperp^2/{\avkperp_{h_{1L}^\perp}^2}}
-	\;,\label{eq:h1l_final}
-\ee
-We will use WW-type approximation from Eq.~(\ref{Eq:WW-approx-h1L}) 
-for calculation of $h_{1L}^{\perp (1) a}(x)$ and for the estimates of the 
-asymmetry $\avkperp_{h_{1L}^\perp} = \avkperp_{h_{1}} = 0.25$ (GeV$^2$).
-Notice that the Kotzinian-Mulders function and $h^{\perp q}_{1L}$ obey the
-positivity bound \cite{Bacchetta:1999kz}
-\be
-	\frac{\kperp^2}{M^2}\left( (h^{\perp q}_{1L}(x,\kperp^2))^2 + 
-	(h_{1}^{\perp q}(x,\kperp^2))^2\right) \le (f_{1}^{q}(x,\kperp^2))^2 \, .
-\ee
-so that using our Gaussian parametrizations from Eqs.~(\ref{Eq:Gauss-f1-D1},\ref{eq:h1l_final},\ref{bm_new})  one has
-\be
-\frac{(f_{1}^{q}(x))^2}{16\pi M^2} - \frac{(h_{1}^{\perp q}(x))^2}{4\pi \avkperp_{h_{1}^\perp} } -
-\frac{(h_{1L}^{\perp q}(x))^2}{4\pi \avkperp_{h_{1TL}^\perp} } \ge 0
-\label{eq:positivity1}
-\ee
-which, multiplied by $16\pi M^2$,  is plotted in Fig.~\ref{h1l_pos}.
-Notice that for $d$-quark the positivity is violated that may be due to the big Boer-Mulders $d$-quark function from Ref.~\cite{Barone:2015ksa}.
-As far as determination of the size of Boer-Mulders functions is far from ideal, we cautiously keep the present result.
-Future determinations of Boer-Mulders functions will help to clarify the issue of positivity constraints.
+We assume Gaussian form for the Kotzinian-Mulders function 
+$h_{1L}^{\perp a}$, see Eq.~(\ref{eq:h1l_final}) in
+App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}. From 
+Eq.~(\ref{Eq:WW-approx-h1L}) we obtain the WW-type estimate
+for $h_{1L}^{\perp(1) a}(x)$ shown in Fig.~\ref{g1t_h1l_functions}. 
+For the Gaussian width we assume $\avkperp_{h_{1L}^\perp} = \avkperp_{h_{1}}$ 
+supported by lattice data \cite{Hagler:2009mb}.
 
@@
 
-Resulting distributions $h^{\perp(1)q}_{1L}(x)$ are plotted in 
-Fig.~\ref{g1t_h1l_functions}. 
-The asymmetries $A_{UL}^{\sin(2\phi_h)}=F_{UL}^{\sin(2\phi_h)}/F_{UU}$  for 
-Jefferson Lab 12 GeV are plotted in Fig.~\ref{aul_jlab}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
+\centering
+\includegraphics[height=3.4cm]{Fig-COMPASS-A_2_Pr0711_Zgt02.pdf} \quad
+\includegraphics[height=3.4cm]{\FigPath/AULsin2phi_JLAB_x.pdf}  
+	\caption{\label{aul_jlab} 
+	$A_{UL}^{\sin(2\phi_h)}$ as function of $x$ from HERMES
+	\cite{Airapetian:1999tv} and COMPASS \cite{Parsamyan:2015dfa} 
+	experiments (left panel) and at Jefferson Lab 
+	\cite{Jawalkar:2017ube} in comparison to predictions from
+	WW-type approximation.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The asymmetry $A_{UL}^{\sin(2\phi_h)}=F_{UL}^{\sin(2\phi_h)}/F_{UU}$  was 
+studied at HERMES \cite{Airapetian:1999tv,Airapetian:2002mf}, 
+COMPASS \cite{Parsamyan:2015dfa}, and JLab \cite{Jawalkar:2017ube}.
+In the left panel of Fig.~\ref{aul_jlab} the results for proton
+target are shown. At HERMES 27.6 GeV positrons from the HERA polarized 
+positron storage ring at DESY scattering off a nuclear-polarized hydrogen 
+internal gas targets \cite{Stock:1994vv} in the kinematics
+$1\,{\rm GeV}^2 < Q^2 < 15 \,{\rm GeV}^2$, $W > 2\,{\rm Gev}$,
+$0.023 < x < 0.4$ and $y < 0.85$. The data for $\pi^\pm$ from 
+proton are shown in Fig.~\ref{aul_jlab}. The COMPASS data show 
+the asymmetry for charged hadrons, which in practice are mainly
+pions. Since $y$-dependent prefactors were included in the
+analyses (see Sec.~\ref{Sec-2.1:SIDIS+structure-functions}),
+the HERMES data is adequately rescaled (``$D(y)$--rescaled'').
+
+\ \\
+\red{\large\bf Stopping here. Sending to Alexei!
+Continue from here.}
+
+\newpage
+
+\ps{
+
+\subsection{Inequalities and a cross check}
+
+We discussed WW-type approximations for
+$g^{\perp q}_{1T}$ and $h^{\perp q}_{1L}$ and the two
+twist-2 structure functions amenable to this approximation
+in Secs.~\ref{Sec-6.1:FLTcosphi-phiS} and~\ref{Sec-6.2:FULsin2phi}.
+Before focusing on twist-3 let us pause 
+and revisit positivity bounds \cite{Bacchetta:1999kz} 
+which offer unique cross checks.
+
+The Kotzinian-Mulders function $h^{\perp q}_{1L}$ in conjuction with 
+the Boer-Mulders function, and the TMD $g^{\perp q}_{1T}$ in conjuction 
+with the Sivers function obey the positivity bounds 
+\cite{Bacchetta:1999kz}
+\begin{subequations}\ba
+	\frac{\kperp^2}{M^2}\left[ (h^{\perp q}_{1L}(x,\kperp^2))^2 + 
+	(h_{1}^{\perp q}(x,\kperp^2))^2\right] 
+	& \le & (f_{1}^{q}(x,\kperp^2))^2 \, ,\\
+	\frac{\kperp^2}{M^2}\left[ (g^{\perp q}_{1T}(x,\kperp^2))^2 
+	+ (f_{1T}^{\perp q}(x,\kperp^2))^2\right] 
+	& \le & (f_{1}^{q}(x,\kperp^2))^2 \; . 
+\ea\end{subequations}
+From these inequalities and our Gaussian Ans\"atze in 
+Eqs.~(\ref{Eq:Gauss-f1}, \ref{Eq:Gauss-h1}, \ref{Eq:Gauss-f1Tperp}, 
+\ref{Eq:Gauss-h1perp}, \ref{eq:g1t}, \ref{eq:h1l_final}) one obtains 
+(after $k_\perp$-integration and mutliplication by $16\pi M_N^2$) 
+the inequalities
+\begin{subequations}\ba
+	(f_{1}^{q}(x))^2
+	- \frac{4M^2 (f_{1T}^{\perp q}(x))^2}{\avkperp_{f_{1T}^\perp} } 
+	- \frac{4M^2 (g_{1T}^{\perp q}(x))^2}{\avkperp_{g_{1T}^\perp} } &\ge& 0
+	\;, \label{eq:positivity}\\
+	(f_{1}^{q}(x))^2 
+	- \frac{4M^2 (h_{1}^{\perp q}(x))^2}{\avkperp_{h_{1}^\perp} } 
+	- \frac{4M^2 (h_{1L}^{\perp q}(x))^2}{\avkperp_{h_{1TL}^\perp} } &\ge& 0\,.
+	\mbox{\red{\ (introduce (1)-moments!)}}
+\label{eq:positivity1}
+\ea\end{subequations}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
+\begin{figure}[b!]
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/h1lperp_positivity.pdf}  
+\includegraphics[width=0.3\textwidth]{\FigPath/g1t_positivity.pdf}  \quad
+\includegraphics[width=0.3\textwidth]{\FigPath/h1lperp_positivity.pdf}  
 	\caption{\label{h1l_pos} 
 	LHS of Eq.~\eqref{eq:positivity1}.
-}
+	LHS of Eq.~\eqref{eq:positivity}.}
 \end{figure}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_COMPASS_x.pdf}  (a)
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_JLAB_x.pdf}  (b)
-	\caption{\label{aul_jlab} 
-	$A_{UL}^{\sin(2\phi_h)}$  as a function of $ x $  at typical kinematics 
-	of COMPASS, 
-	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$ (a) and comparison to JLab (b).
+The left-hand-sides of these inequalities are plotted in 
+Fig.~\ref{h1l_pos} which shows that positivity is satisfied 
+in 3 out of 4 cases: only (\ref{eq:positivity1}) for $d$-flavor 
+seems violated for $x>0.2$.
+
+At this point some remarks are in order.
+First, the inequalities (\ref{eq:positivity},~\ref{eq:positivity1}) 
+must be strictly satisfied by the {\it exact} leading--order QCD 
+expressions for the TMDs. 
+(For PDFs it is known that positivity can be preserved in some schemes 
+and violated in other schemes. For TMDs not much is known about 
+positivity conditions beyond leading order.)
+However, here we do not deal with exact expressions for the TMDs
+but we invoked two strong model assumptions: WW-type
+approximations for $g^{\perp q}_{1T}$ and $h^{\perp q}_{1L}$, and 
+Gauss Ansatz for all TMDs. This is a lot! Neverthelss we find 
+that (\ref{eq:positivity},~\ref{eq:positivity1}) are respected 
+for $x<0.2$. This is a non-trivial cross check of our aproach. 
+Second, available data constraining the TMDs are mostly at $x<0.2$. 
+There are in fact only few $x$-bins above $x>0.2$. For $x>0.4$ the 
+available parameterizations of TMDs are practically unconstrained.
+Third, the determination of the Boer-Mulders function from 
+Ref.~\cite{Barone:2015ksa} is far from ideal especially for $d$-flavor, 
+and non-factorizing power-corrections (due to Cahn effect) may be at play.
+
+Considering that we deal with approximations (WW-type, Gauss) 
+and considering current state of TMD-extractions, the 
+positivity test in Fig.~\ref{h1l_pos} can be considered satisfactory.
+
 }
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
+
 \newpage
@@
 
-The WW-type approximations are useful for all 8 subleading-twist observables,
+The WW-type approximations are useful for all 8 subleading--twist observables,
 as shown in Sec.~\ref{Sec-4.2:WW-twist-3}. In view of the complex 
-structure of subleading-twist structure functions, WW-type approximations
-might be particularly useful for the interpretation of twist-3 
-observables.
+structure of subleading--twist structure functions, WW-type approximations
+are potentially very useful for the interpretation of twist-3 observables.
 
@@
 
-Instead, data from Jefferson Lab and HERMES show a small but 
-clearly non-zero effect of the order of (2-3)\,$\%$ 
+But data from Jefferson Lab, HERMES \ps{and COMPASS} show a small 
+but clearly non-zero effect of the order of (2-3)\,$\%$ 
 \cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,Aghasyan:2011ha,
-Adolph:2014pwc,Gohn:2014zbz}.
+Adolph:2014pwc,Gohn:2014zbz,Adolph:2014pwc}.
 What may seem at first glance to be a failure of the approach is in 
@@
 
-\newpage
+\begin{figure}[h!]
+\includegraphics[width=0.8\textwidth]{Fig-COMPASS-A_LL_Pr0711_Zgt02.pdf}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=0.8\textwidth]{Fig-COMPASS-A_UL1_Pr0711_Zgt02.pdf}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=0.8\textwidth]{Fig-COMPASS-A_UT_Pr10.pdf}
+\end{figure}
+
 \subsection{\boldmath Subleading twist  $A_{LT}^{\cos\phi_S}$}
@@
 \ee
-where $g^{q}_{T}(x)$ is calculated according to Eq.~\ref{Eq:WW-original1}.
-Notice that we could have used WW-type relation of Eq.~(\ref{Eq:WW-type-6}) to relate $g^{q}_{T}(x,\kperp^2)$
-and $g^{\perp q}_{1T}(x,\kperp^2)$ however we choose not to do it. In fact Eq.~(\ref{Eq:WW-type-6}) suggests kinematical zero 
-$g^{q}_{T}(x, 0) = 0$  which is not supported by the model calculations \cite{Avakian:2010br} and thus  Eq.~(\ref{Eq:WW-type-6}) can be used only in its integrated form. 
-The Eq.~(\ref{Eq:WW-type-6}) is not exact and is not on the same footing as WW-approximation of Eq.~(\ref{Eq:WW-original1}), and we parametrize directly $g^{q}_{T}(x,\kperp^2)$ using the Gaussian shape.
-For illustrative purpose we show ``violation'' of  Eq.~(\ref{Eq:WW-type-6}) in Fig.~\ref{altcosphi_wwtype}.
-
-$F_{LT}^{\cos\phi_S}$
-structure function then reads 
+where $g^{q}_{T}(x)$ is calculated according to Eq.~(\ref{Eq:WW-original1}).
+Notice that we could have used WW-type relation of Eq.~(\ref{Eq:WW-type-6}) 
+to relate $g^{q}_{T}(x,\kperp^2)$ and $g^{\perp q}_{1T}(x,\kperp^2)$ however we 
+choose not to do it. In fact Eq.~(\ref{Eq:WW-type-6}) suggests kinematical 
+zero $g^{q}_{T}(x, 0) = 0$  which is not supported by the model calculations 
+\cite{Avakian:2010br} and thus  Eq.~(\ref{Eq:WW-type-6}) can be used only 
+in its integrated form. 
+The Eq.~(\ref{Eq:WW-type-6}) is not exact and is not on the same footing as 
+WW-approximation of Eq.~(\ref{Eq:WW-original1}), and we parametrize directly 
+$g^{q}_{T}(x,\kperp^2)$ using the Gaussian shape. For illustrative purpose we 
+show ``violation'' of  Eq.~(\ref{Eq:WW-type-6}) in Fig.~\ref{altcosphi_wwtype}.
+
+The $F_{LT}^{\cos\phi_S}$ structure function then reads 
 \begin{subequations}\ba
@@
 	explore first the WW-type-relation (\ref{Eq:WW-type-5}), and
-	assume then the Gauss Ansatz for $g_{1T}^{\perp}(x,\kperp)$ 
+	assume then the Gaussian Ansatz for $g_{1T}^{\perp}(x,\kperp)$ 
 	according to (\ref{eq:g1t}). Solving then the convolution integral 
@@
 	The operations of applying the WW-type approximations and 
-	employing the Gauss Ansatz do not commute in general.
+	employing the Gaussian Ansatz do not commute in general.
 	The solution presented in (\ref{Eq:FLTcosphiS-Gauss}) is 
@@
 \ \\
-\PS{We should include a comparison to 
+\ps{We should include a comparison to 
 COMPASS data \cite{Kotzinian:2007uv,Parsamyan:2010se}.}
@@
 
-The asymmetries $A_{UL}^{\sin\phi_h}=F_{UL}^{\sin\phi_h}/F_{UU}$  as a function of $x$  
-for COMPASS is plotted in Fig.~\ref{aulsinphi_jlab} (a). We also compare our calculations to HERMES data \cite{Airapetian:2005jc} in Fig.~\ref{aulsinphi_jlab} (b).
+We compare our calculations to HERMES data \cite{Airapetian:2005jc} 
+in Fig.~\ref{aulsinphi_jlab} (a) and to CLAS data in 
+Fig.~\ref{aulsinphi_jlab} (c).
+The asymmetries $A_{UL}^{\sin\phi_h}=F_{UL}^{\sin\phi_h}/F_{UU}$  as a function 
+of $x$  for COMPASS is plotted in Fig.~\ref{aulsinphi_jlab} (b).
 
@@
 new features. This is the first case with more than 1 contribution after 
-applying the WW-type approximation. Assuming Gauss Ans\"atze for the TMDs
+applying the WW-type approximation. Assuming Gaussian Ans\"atze for the TMDs
 $f_T^q(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
@@
 Eq.~(\ref{Eq:FUTsinphiS-Gauss-I-PhT}) vs.\ (\ref{Eq:FUTsinphiS-I-naive}).
-This is a property of the weight $\omega^{\{2\}}_{\rm B}$,
+This is a property of the weight $\omega^{\{2\}}_{\rm B}$ 
+in Eq.~(\ref{FUTsinphiS}),
 see Eq.~(\ref{Eq:wi}) and App.~\ref{App:factor}, which appears
@@
 Exploring the WW-type approximations (\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}) 
-the chiral odd twist-3 TMDs can be unambiguously related to transversity
+the chiral--odd twist-3 TMDs can be unambiguously related to transversity
 \begin{subequations}\be
@@
 Eq.~(\ref{Eq:sum-rules-T-odd}). This was discussed in 
-Sec.~\ref{Sec-3.7:basis+limitations}.
+Sec.~\ref{Sec-3.8:limitations}.
 
@@
 choice, because we strictly speaking deal with the convoluted non-zero 
-TMD $f_T^q(x,\kperp)$, and the Gauss model only {\it artificially} 
+TMD $f_T^q(x,\kperp)$, and the Gaussian model only {\it artificially} 
 introduces the collinear function $f_T^q(x)$ expected to be zero.
@@
 	We will have to revise our description of $g_1^q(x,\kperp)$ 
-	in Eq.~(\ref{eq:g1}) and App.~\ref{App:basis-g1} to something 
+	in Eq.~(\ref{Eq:Gauss-g1}) and App.~\ref{App:basis-g1} to something 
 	of the type (\ref{Eq:multiple-Gauss}), if this prediction is 
@@
 COMPASS are plotted in Fig.~\ref{autsinphi_jlab}.
-\PS{Compare to HERMES data \cite{Schnell:2010zza}?
+\ps{Compare to HERMES data \cite{Schnell:2010zza}?
 Is there by now final data? Will be interesting!}
@@
 	F_{UU}^{\cos\phi_h}(x,z,\Phperp) 
-	= +\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
+	= \frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
 	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;b^{(1)}_{\rm A}\,
@@
 	F_{UU}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
-	= +\,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
+	= \frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
 	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;c^{(1)}_{\rm A}\;
@@
 discussed in Sec.~\ref{Sec-7.6:FUTsinphiS}. Also here one could introduce
-an additional Gauss parameter and use a double Gaussian to describe 
+an additional Gaussian parameter and use a double Gaussian to describe 
 $h^q(x,\kperp)$. One should keep this in mind as an interesting possibility
@@
 as shown in Fig.~\ref{auucosphi_jlab}. \\
-\PS{(Alexei: did you notice it \cite{Anselmino:2005nn}? How did you treat it? AP we did notice and did nothing.)}
+\ps{(Alexei: did you notice it \cite{Anselmino:2005nn}? How did you treat it? AP we did notice and did nothing.)}
 
@@
 Jefferson Lab 12 GeV are plotted in Fig.~\ref{auucosphi_jlab}.
-\PS{We should compare to EMC, or 
+\ps{We should compare to EMC, or 
 	JLab \cite{Osipenko:2008aa,Mkrtchyan:2007sr}, 
@@
         curve is the ``WW-type and Cahn-effect-only'' approximation 
-        for this observable in the Gauss model with parameters 
+        for this observable in the Gaussian model with parameters 
         fixed from HERMES data and neglecting evolution effects. 
@@
 \ \\
-\PS{We may potentially run into positivity issues also for other observables. 
+\ps{We may potentially run into positivity issues also for other observables. 
 However, I would suggest not to worry too much. We see in the pictures that 
@@
 
-In this last asymmetry we encounter the first case with more than 
-1 contribution in our treatment. Assuming Gauss Ans\"atze for 
-$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$ (Eq.~\ref{eq:hTperpnew}), $h_T^q(x,\kperp)$ (Eq.~\ref{eq:hTnew}),
+In this last asymmetry we encounter the first case with more than one 
+surviving contribution in our treatment. Assuming Gaussian Ans\"atze for 
+$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$ Eq.~(\ref{eq:hTperpnew}), 
+$h_T^q(x,\kperp)$ Eq.~(\ref{eq:hTnew}),
 \be
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2PhiminusPhiS_COMPASS_x.pdf} 
-\caption{\label{autsin2phi_jlab} $A_{UT}^{\sin(2\phi_h- \phi_S)}$  for COMPASS.
-}
+\caption{\label{autsin2phi_jlab} $A_{UT}^{\sin(2\phi_h- \phi_S)}$  for COMPASS
+	\red{(GUNAR: here it says COMPASS, in text JLab)}}
 \end{figure}
@@
 
+Regarding inequalities:
+This point has to be cautiously kept in mind. Future determinations 
+of not only of the Boer-Mulders functions but also all other TMDs
+from precision JLab data (and on long run from the EIC) will 
+improve the situation, and allow to test the positivity constraints
+more rigorously. In this way, the TMD leading-twist factorization
+approach will also be validated.
+
+\
+
 % , and show that in this approximation all leading- and
-% subleading-twist structure functions are expressed in terms of
+% subleading--twist structure functions are expressed in terms of
 % a ``basis'' consisting of 6 twist-2 TMDs and 2 twist-2 fragmentation 
@@
 (Jefferson Lab 12) or proposed in the long-term (Electron Ion Collider),
-and provide helpful input for Montecarlo event generators 
+and provide helpful input for Monte Carlo event generators 
 \cite{Avakian:2015vha}.
@@
 $Q^2=2.4\,{\rm GeV}^2$ typical for many currently available SIDIS data.
-These parameterizations were used in \cite{Anselmino:2005nn} and other 
+These parametrizations were used in \cite{Anselmino:2005nn} and other 
 works whose extractions we adopt.
@@
 and $D_1(z,P_\perp^2)$ we use the Gaussian Ansatz in 
-Eqs.~(\ref{Eq:Gauss-f1-D1}). All early 
+Eqs.~(\ref{Eq:Gauss-f1},~\ref{Eq:Gauss-D1}). All early 
 \cite{Anselmino:2005nn,Collins:2005ie,D'Alesio:2007jt,Schweitzer:2010tt}
@@
 $x$- or $z$-independent widths $\avkperp$ and $\avpperp$.
-In the the analysis \cite{Anselmino:2013lza} 
+In the analysis \cite{Anselmino:2013lza} 
 of HERMES multiplicities flavor-independence of the widths was 
@@
 best fit result. The uncertainty of the numbers from \cite{Schweitzer:2010tt}
-includes only the statistical error, but no systematic uncertainty.
+includes only the statistical uncertainty, but no systematic uncertainty.
 For comparison lattice results from \cite{Hagler:2009mb} are included
@@
 \caption{\label{Table:Gauss-paramaters}
-  	Gauss model parameters for $f_1^a(x,k_\perp)$, $D_1^a(z,P_\perp)$, 
+  	Gaussian model parameters for $f_1^a(x,k_\perp)$, $D_1^a(z,P_\perp)$, 
  	$g_{1}^a(x,k_\perp)$ from phenomenological and lattice QCD studies.
@@
 \int d^2k_\perp\,g_{1L}^a(x,k_\perp^2)$ we use in this work the leading-order 
-parameterizations from \cite{Gluck:1998xa}.
+parametrizations from \cite{Gluck:1998xa}.
 If not otherwise stated the parametrizations are taken at the scale 
@@
 $g_1^a(x,k_\perp^2)$ we explore lattice QCD results from \cite{Hagler:2009mb}
-to constrain the Gaussian width in Eq.~(\ref{eq:g1}). 
+to constrain the Gaussian width in Eq.~(\ref{Eq:Gauss-g1}). 
 On a lattice with pion and nucleon masses 
@@
 
-We can rewrite parameterizations of Sivers functions as
+We can rewrite parametrizations of Sivers functions as
 
@@
 Kang:2014zza,Kang:2015msa,Anselmino:2015sxa}.
-The following shape was assumed for parametrizations 
+The following shape was assumed for parametrizations in
 Refs.~\cite{Anselmino:2007fs,Anselmino:2008jk,Anselmino:2013vqa}:
@@
  \ea
- with $m_h$ produced hadron mass and
+ with $m_h$ the mass of the produced hadron and
  \ba
@@
 
-We can rewrite the parameterizations of Collins FF as
+We can rewrite the parametrizations of Collins FF as
 
@@
 
-The following parameterization was used in Refs.~\cite{Barone:2015ksa}:
+The following parametrizations was used in Ref.~\cite{Barone:2015ksa}:
 \ba
@@
 
-We can rewrite parameterization of Boer-Mulders functions as
+We can rewrite parametrizations of Boer-Mulders functions as
 
@@
 momenta in $\left[D^a(z,z^2 k_T^2)\right]_{\mbox{\tiny Ref.\cite{Bacchetta:2006tn}}}$ 
-would require a strongly $z$-dependent Gaussian width. It is of course 
-a matter of taste which one prefers to use.
+would require a strongly $z$-dependent Gaussian width. It is a matter of 
+taste which one prefers to use.
 
@@
 divergences and has to carefully define how to deal with them.
-Results of Eqs.~(\ref{eq:moments}) assume that Gaussian dependence is factorized from $x$ or $z$ dependence and parametrizations are made with respect to either $f(x)$ or $D(z)$.
-As we saw in Appendix \ref{App:basis} some TMD functions are parametrized with higher moments directly as operator product expansion of TMDs may start from higher twist matrix element instead of the usual twist-2 one.
-In those cases equivalent formulas to Eqs.~(\ref{eq:moments}) can be easily derived.
-
-\subsection{Convolution integrals in Gauss Ansatz}
+
+In Eqs.~(\ref{eq:moments}) the Gaussian dependence is factorized 
+from $x$ or $z$ dependence and parametrizations are made with 
+respect to either $f(x)$ or $D(z)$. As we saw in Appendix 
+\ref{App:basis} some TMD functions are parametrized with higher 
+moments directly as operator product expansion of TMDs may start 
+from higher twist matrix element instead of the usual twist-2 one. 
+In those cases equivalent formulas to Eqs.~(\ref{eq:moments}) can 
+be easily derived.
+
+\ps{
+
+\subsection{Gaussian Ans\"atze used in this work}
+\label{App-B:Gauss-Ansatz-non-basis-TMDs}
+
+The Gaussian Ans\"atze for the 8 basis functions were shown 
+in Eqs.~(\ref{Eq:Gauss-f1}--\ref{Eq:Gauss-h1Tperp}) in 
+Sec.~\ref{Sec-4.4:evaluation}, and the pertinent parameters
+and parametrizations were reviewed in App.~\ref{App:basis}.
+Besides the basis function we also need Ans\"atze for the 
+following 8 TMDs as listed below:
+\begin{subequations}\begin{align}
+	g^{\perp q}_{1T}(x,\kperp^2) 
+	  & =	g^{\perp (1) q}_{1T}(x)\,
+		\frac{2 M_N^2}{\pi \avkperp_{g_{1T}^\perp}^2}\,
+		e^{-\kperp^2/{\avkperp_{g_{1T}^\perp}}}  \,, 
+	  && 	\mbox{cf.\ Sec.~\ref{Sec-6.1:FLTcosphi-phiS},}
+		\label{eq:g1t}\\
+	h_{1L}^{\perp a}(x,\kperp^2) 
+	  & = 	h_{1L}^{\perp (1) a}(x)\,
+		\frac{2 M_N0^2}{\pi{\avkperp_{h_{1L}^\perp}^2}}\,
+		e^{-\kperp^2/{\avkperp_{h_{1L}^\perp}^2}}
+	  && 	\mbox{cf.\ Sec.~\ref{Sec-6.2:FULsin2phi},}	
+		\label{eq:h1l_final}
+\end{align}\end{subequations}
+
+{}
+
+}
+
+\subsection{Convolution integrals in Gaussian Ansatz}
 \label{App:convol-details}
@@
 For practical application it is convenient to absorb as many 
-(Gauss model) parameters as possible into expressions that can
+(Gaussian model) parameters as possible into expressions that can
 be more easily fitted to data. One way to achieve this is to make 
@@
 
-\newpage
-\section*{Remarks  \& Corrections in version 00r (PS) {}}
-
-\begin{itemize}
-
-\item	I reshuffled some subsections with good intentions.
-	Please, see whether you like it. {\color{red} AP good for me}
-
-\item	Introduced a new procedure: first assume Gauss Ansatz,
-	then evaluate convolution integrals, finally use WW.
-	This gives \blue{\bf different} results from Saman \& Alexei.\\
-	Advantages: \\
-	1. The results can be written in a compact way.\\
-	2. There is less model dependence due to the simpler expressions.\\
-	3. In the new expressions it is more natural to incorporate the 
-	sum rules (\ref{Eq:sum-rules-T-odd}) for T-odd twist-3 functions.
-	{\color{red} AP good for me, we need to expand a little on differences with the previous version.}
-
-\item   The numerical results are obtained with 
-	DSS'07 and GRV'00 and GRSV'98.
-	DSS is 10 years old. GRSV is from last millennium.
-	I agree that DSS is acceptable (if we do not touch kaons). 
-	However, we should use a more modern input for $f_1^q(x)$ and 
-	$g_1^q(x)$ (even though I know and understand that it does not matter).
-	 {\color{red} AP good for me, I implemented MRSTW instead.}
-
-\item 	I introduced 
-	{\textbackslash}begin\{subequations\} $\dots$
-	{\textbackslash}end\{subequations\}. Notice that it comes
-	before equations arrays start and after they end, and it can
-	contain text in-between.  {\color{red} AP good for me}
-
-\item	notation: in all(?) formulas 
-	{\{{\textbackslash}bf $\dots$\}} changed to
-	{\{{\textbackslash}bm $\dots$\}} \\
-	${\bm \xi}_T$ changed to ${\bm \xi}_\perp$ in 
-	Eqs.~(\ref{Eq:correlator},~\ref{Eq:correlator-FF})
-	(Fourier variables of ${\bm k}_\perp$, ${\bm p}_\perp$)\\
-	In Eq.~(\ref{Eq:correlator-FF}) the integration is over
-	$\xi^+$ (not $\xi^-$), and $(-\infty)\to(+\infty)$.  {\color{red} AP good for me}
-
-\item	more serious: in Eq.~(\ref{Eq:correlator-FF}) replacement 
-	${\bm p}_\perp = \bfpperp$ was wrong. Correct:
-	${\bm p}_\perp = -\bfpperp/z$.
-	Because of that we have corrections
-	$\pperp^k\to - \pperp^k/z$ in 
-	(\ref{eq:DeltaTr-twist-2b},
-	 \ref{eq:DeltaTr-twist-3b},
-	 \ref{eq:DeltaTr-twist-3c},
-	 \ref{Eq:WW-type-FF-4}). \\
-	Luckily no influence on numerical results. \red{Please, double check 
-	(\ref{eq:DeltaTr-twist-2a}-\ref{eq:DeltaTr-twist-3c})!}  {\color{red} AP have no time, anybody?}
-
-\item	in several places correction $D_q^h(z)\to D_1^q(z)$, \\
-	correction $H^\perp(z,\pperp^2) \to H(z,\pperp^2)$
-	in (\ref{Eq:WW-type-FF-4})  {\color{red} AP good for me}
-
-\item	after Eq.~(\ref{Eq:TMD-pdfs-VI}) changed
-	$\epsilon_T^{ij}\equiv\epsilon^{-+ij}$ to
-	$\epsilon^{ij}\equiv\epsilon^{-+ij}$
-	(we use throughout $\epsilon^{ij}$)  {\color{red} AP good for me}
-
-\item 	corrected sign of term with $f_T^\perp$ in (\ref{Eq:sub-TMD-pdfs-III}). 
-	Should be negative. Compare to \cite{Bacchetta:2006tn}.   {\color{red} AP good for me, thank you}
-
-\item	corrected sign typos in 
-	Eq.~(\ref{FUTsinphiS}) (term with $\tilde{D}^\perp$) and 
-	Eq.~(\ref{FLTsin(2phi-phiS)}) (term with $\tilde{G}^\perp$)\\
-	Both drop out in WW, so no consequence.  {\color{red} AP good for me}
-
-\item 	the figure names \\ {\tt
-	ALLcosPhi\_x.pdf, ALLcosPhi\_PT.pdf,  \\
-  	ALTcos2Phi\_x.pdf, ALTcos2Phi\_PT.pdf, \\
-  	AULsinPhi\_x.pdf, AULsinPhi\_PT.pdf} \\
-	were spelled incorrectly (in latex source: {\tt Phi}. Name of file
-	{\tt phi}).\\
-	Fixed in latex file, names of figures are unchanged.  {\color{red} AP good for me}
-
-\item	We should not show predictions for JLab 12,
-	but compare to available data. Often we will have huge error bars.
-	Then we can say that JLab 12 will resolve the situation.  {\color{red} AP good for me, I change that}
-
-\item	Often we write $M$ or $M_N$ and mean the nucleon mass.
-	I would prefer $M_N$ but writing $M$ everywhere would be less work.
-	We write sometimes $H^\perp(z,\pperp^2)$ and sometimes
-	$H^\perp(z,\pperp)$, etc. We have to agree on a common notation. 
-	I propose without square.  {\color{red} AP good for me, I prefer $H^\perp(z,\pperp^2)$}
-
-{}
-\end{itemize}
-
 \end{document}
@@
 work better then that.
-\PS{We probably can considerably shorten this lengthy review section
+\ps{We probably can considerably shorten this lengthy review section
 to 2--3 sentences. Any objections?}

### 2018-05-21 tex/test-WW-type-00v-PS.tex
tex

--- 2018-05-19 tex/old/test-WW-type-00t-PS.tex
@@
 \newcommand{\SB}[1]{{\bf SB:} {\color{magenta} #1}}
-\newcommand{\judge}[1]{{\boldmath \ ({\lowercase\blue{#1}}, PS)}}
 
@@
 the Wandzura--Wilczek-type approximation \ps{which consists in a systematic
-neglect of $q\bar q g$-terms with respect to $\bar{q}q$-correlators.}
+neglect of $\bar{q}gq$--terms with respect to $\bar{q}q$--correlators.}
 We compute all twist-2 and twist-3 structure functions and the corresponding 
@@
 associated with the hard scale $Q$ of the process.
-%, which we will not indicate for notational simplicity.
 Although the PDFs  $f_1^a(x)$ and $g_1^a(x)$ continue being the 
@@
 terms \cite{Wandzura:1977qf,Jaffe:1991ra}. 
-We shall refer to the latter generically as $\bar qgq$-terms, keeping in 
+We shall refer to the latter generically as $\bar qgq$--terms, keeping in 
 mind one deals in each case with matrix elements of different operators.
-The $\bar qgq$-correlations contain new insights on hadron structure 
+The $\bar qgq$--correlations contain new insights on hadron structure 
 which are worthwhile exploring for their own sake, 
@@
 
-The striking observation is that the $\bar qgq$-terms in $g_T^a(x)$ 
+The striking observation is that the $\bar qgq$--terms in $g_T^a(x)$ 
 and $h_L^a(x)$ are small: theoretical mechanisms predict this 
@@
 predictions \cite{Abe:1998wq,Anthony:2002hy,Airapetian:2011wu}.
-This approximation (``neglect of $\bar qgq$-terms'') is commonly 
+This approximation (``neglect of $\bar qgq$--terms'') is commonly 
 known as Wandzura--Wilczek (WW) approximation \cite{Wandzura:1977qf}.
@@
 In both cases, PDFs and TMDs, one basically assumes that the 
-contributions from $\bar{q}gq$-terms can be neglected with respect to 
-$\bar{q}q$-terms. But the nature of the omitted matrix elements is 
+contributions from $\bar{q}gq$--terms can be neglected with respect to 
+$\bar{q}q$--terms. But the nature of the omitted matrix elements is 
 different, and in the context of TMDs one often prefers to speak 
@@
 in a unique approach. Our results are of importance for experiments prepared 
-in the near-term (JLab 12, \ps{COMPASS}) or proposed in the long-term 
+in the near-term at \ps{Jefferson Lab (JLab) with 12$\,$GeV beam energy
+upgrade and COMPASS} or proposed in the long-term  
 (Electron Ion Collider), and provide helpful input for Monte Carlo event
 generators \cite{Avakian:2015vha}.
+
 Our predictions will either be confirmed within the expected accuracy
-\ps{or not be supported by data. The first case will call for dedicated 
-theoretical studies to explain why the pertinent $\bar{q}gq$-terms are 
-so small. The second case will call for explanations why sometimes 
-$\bar{q}gq$-terms are so sizable. In this way our work will help to guide 
-further developments. In either case our results will deepen the
-understanding of the quark-gluon correlations inside hadrons.}
+\ps{or not supported by data. This will call for dedicated theoretical 
+studies to explain either why the pertinent $\bar{q}gq$--terms are 
+so small or so sizable. In either case our results will deepen the 
+understanding of  $\bar{q}gq$--correlations and help to guide 
+further developments.}
 
@@
 virtual photon momentum. 
-\ps{In principle the cross section is also differential with respect to the} 
+In principle the cross section is also differential with respect to the
 azimuthal angle $\psi_l$ characterizing the overall orientation of the 
-lepton scattering plane in \ps{a fixed} lab frame.
-%
-% Notice that $d \psi_l \simeq d\phi_S$ where $\phi_S$ is the azimuthal angle
-% of the nucleon spin vector. 
-%
+lepton scattering plane in a fixed lab frame.
 \ps{By analyzing the data in the reference frame in Fig.~\ref{fig-kin-SIDIS}
@@
 ``differential'' in $\psi_l$ for symbolic reasons.} 
-%
 It is convenient to define the unpolarized 
-lepton--quark scattering \ps{subprocess} cross section
+lepton--quark scattering subprocess cross section
 \ba\label{Eq:sigma0-FUU}
@@
 
-At subleading order \ps{in the $1/Q$ expansion} one has
+At subleading order in the $1/Q$ expansion one has
 \ba\hspace{-1cm}
@@
 \ee
-where $N_0$ denotes the total ($\phi_h$-averaged) number of counts 
+where $N_0$ denotes the total ($\phi_h$--averaged) number of counts 
 and the dots indicate further kinematic variables in the kinematic 
@@
 virtual-photon--nucleon center-of-mass frame, nucleon and the partons 
-inside it move in the $(+)$-lightcone direction, while the struck 
-quark and the produced hadron move in $(-)$-light-cone direction.
+inside it move in the $(+)$--lightcone direction, while the struck 
+quark and the produced hadron move in $(-)$--light-cone direction.
 In the nucleon rest frame the polarization vector is given by 
@@
 \ea\end{subequations}
-Other structures drop out either due to explicit $\kperp$-dependence,
+Other structures drop out either due to explicit $\kperp$--dependence,
 or due to the sum rules \cite{Bacchetta:2006tn}
@@
 
-The structures surviving $\Phperp$-integration of the SIDIS cross section in 
+The structures surviving $\Phperp$--integration of the SIDIS cross section in 
 (\ref{Eq:SIDIS-leading-integrated},~\ref{Eq:SIDIS-subleading-integrated})
@@
  	F_{LT}^{\cos\phi_S}(x,z) &=& -\,\frac{2M_N}{Q}\; x\sum_a e_a^2\,
-	\biggl(x\,g_T^q(x) + r_h\,h_1^a(x)\frac{\tilde{E}^a(z)}{z}\biggr)
+	\biggl(x\,g_T^q(x)\,D_1^a(z)+r_h\,h_1^a(x)\frac{\tilde{E}^a(z)}{z}\biggr)
 	\label{Eq:FLT-collinear}\\
@@
 \ea\end{subequations}
-Finally, \ps{integrating over $z$, summing over hadrons, and} 
+Finally, integrating over $z$, summing over hadrons, and 
 using the sum rules for the T-odd FFs 
@@
 known about them.
-The basic idea of the approximations is simple. One \ps{uses QCD
-equations of motion to separate contributions from $\bar{q}q$-terms 
-and $\bar{q}gq$-terms and assumes that the latter} can be neglected 
-with respect to \ps{the leading} $\bar{q}q$-terms with a useful accuracy,
+The basic idea of the approximations is simple. One uses QCD
+equations of motion to separate contributions from $\bar{q}q$--terms 
+and $\bar{q}gq$--terms and assumes that the latter can be neglected 
+with respect to the leading $\bar{q}q$--terms with a useful accuracy,
 \be\label{Eq:WW-generic}
@@
 of QCD equations of motion in twist-2 parts, and pure twist-3 
-(interaction dependent) $\bar qgq$-terms and current quark mass
-terms. We denote $\bar qgq$-terms and mass-terms collectively 
+(interaction dependent) $\bar qgq$--terms and current quark mass
+terms. We denote $\bar qgq$--terms and mass-terms collectively 
 and symbolically by functions with a tilde.
@@
 receives no twist-2 contribution. 
-\ps{A prefactor of $x$ is provided in (\ref{Eq:WW-original-e})}
-to cancel a $\delta(x)$-type singularity \cite{Efremov:2002qh}.
+A prefactor of $x$ is provided in (\ref{Eq:WW-original-e})
+to cancel a $\delta(x)$--type singularity \cite{Efremov:2002qh}.
 After introducing the WW-type approximations for TMDs and FFs,
@@
 to be small. Hereby it is important to keep in mind that one deals 
-with different types of (``unintegrated'') $\bar qgq$-correlations,
+with different types of (``unintegrated'') $\bar qgq$--correlations,
 and we prefer to refer to them as WW-type approximations.
@@
              		g_{1T}^{\perp(1)q}(x,\kperp^2), 
-			\label{Eq:WW-type-5}\\
+			\label{Eq:WW-type-gT}\\
 xh_L^q(x,\kperp^2)	&\stackrel{\rm WW-type}{\approx}& -2 \,
@@
 xe_L^q(x,\kperp^2)         	&\stackrel{\rm WW-type}{\approx}& 0, 
-			\label{Eq:WW-type-eLperp}\\\\
+			\label{Eq:WW-type-eLperp}\\
 xe_T^q(x,\kperp^2)         	&\stackrel{\rm WW-type}{\approx}& 0, \\
@@
 WW approximations (\ref{Eq:WW-original1},~\ref{Eq:WW-original2}) with the
-WW-type approximations (\ref{Eq:WW-type-5},~\ref{Eq:WW-type-6}).
+WW-type approximations (\ref{Eq:WW-type-gT},~\ref{Eq:WW-type-6}).
 This yields \cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv}
@@
 \centering
-\includegraphics[width=0.6\textwidth]{\FigPath/g2.pdf} 
+\includegraphics[width=0.45\textwidth]{\FigPath/g2.pdf} 
+\includegraphics[width=0.45\textwidth]{\FigPath/g2-HERMES.pdf} 
 \caption{\label{Fig:g2} 
@@
 Eq.~(\ref{Eq:g2-in-WW-approximation}), for proton (P) and neutron (N) targets. 
-The data are from \cite{Anthony:2002hy,Abe:1998wq}. The \ps{estimate of the 
-theoretical uncertainty} is described in the text.
-\red{Gunar: good idea to include HERMES data \cite{Airapetian:2011wu}!
-Please send us the table with the data points.}}
+Left panel: data from E144 and E155 experiments at $\la Q^2\ra=7.1\,{\rm GeV}^2$ \cite{Anthony:2002hy,Abe:1998wq}. Right panel: HERMES data 
+at $\la Q^2\ra=2.4\,{\rm GeV}^2$ \cite{Airapetian:2011wu}.
+The estimate of the theoretical uncertainty is described in the text.}
 \end{figure}
@@
 theoretical ``uncertainty band'' of about $40\,\%$ as deduced in 
-\cite{Accardi:2009au}? In order to investigate this question, 
+\cite{Accardi:2009au}? To investigate this question, 
 we split this uncertainty in two parts, $\varepsilon_1=\pm 20\,\%$ and 
@@
 of $g_2(x)_{\rm WW}$, $\varepsilon_2$ varies the position of its zero.
-The $x$-dependence of $\varepsilon_2$ preserves $\lim_{x\to1}g_2(x)= 0$; 
+The $x$--dependence of $\varepsilon_2$ preserves $\lim_{x\to1}g_2(x)= 0$; 
 we use $\epsilon=0.05$ which yields $\varepsilon_2\approx 20\,\%$ up to 
-the highest measured $x$-bin.
+the highest measured $x$--bin.
 The good agreement of $g_2(x)_{\rm WW}$ with data is encouraging,
@@
 Our estimate with the splitted uncertainties 
-$\varepsilon_{1,2}$ may overestimate in certain $x$-bins the 
-$40\,\%$-``uncertainty band'' estimated in \cite{Accardi:2009au}. This however 
-helps us to display a conservative estimate of possible uncertainties.
+$\varepsilon_{1,2}$ may overestimate in certain $x$--bins the 
+$40\,\%$--``uncertainty band'' estimated in \cite{Accardi:2009au}. 
+This however helps us to display a conservative estimate of possible 
+uncertainties. 
+We conclude that the WW--approximation works reasonably well
+possibly except for very small $x$ at HERMES, see Fig.~\ref{Fig:g2}.
 
@@
 $h_{1L}^{\perp(1)\bar q}(x) = +\,h_{1L}^{\perp(1)q}(-x)$
-depending on $C$-parity of the involved operators \cite{Mulders:1995dh}.
+depending on $C$--parity of the involved operators \cite{Mulders:1995dh}.
 The right hand sides of 
-Eqs.~(\ref{Eq:WW-approx-g1T-d},~\ref{Eq:WW-approx-h1L-d}) are $x$-moments 
+Eqs.~(\ref{Eq:WW-approx-g1T-d},~\ref{Eq:WW-approx-h1L-d}) are $x$--moments 
 of parton distributions, and those can be obtained from lattice QCD using 
@@
         &\stackrel{!}{\approx}
-        \underbrace{\frac{1}{2}\int d x\;x\,g_1^u(x)}
+        \underbrace{\frac{1}{2}\int d x\;x\,g_1^d(x)}
         _{= -0.025(9) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
@@
         &\stackrel{!}{\approx}&
-        \underbrace{-\,\frac{1}{3}\int d x\;x\,g_1^u(x)}
+        \underbrace{-\,\frac{1}{3}\int d x\;x\,h_1^u(x)}
         _{= -0.093(3) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
@@
         &\stackrel{!}{\approx}&
-        \underbrace{-\,\frac{1}{3}\int d x\;x\,h_1^u(x)}
+        \underbrace{-\,\frac{1}{3}\int d x\;x\,h_1^d(x)}
         _{= 0.018(1) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
@@
 somewhat heavier pions and nucleons. All that matters in our
-context is that the relative size of $\bar qgq$-matrix elements
-is small with respect to $\bar qq$-matrix elements.
+context is that the relative size of $\bar qgq$--matrix elements
+is small with respect to $\bar qq$--matrix elements.
 % (Other lattice artifacts, such as finite lattice spacing and
@@
 Meanwhile we may try to gain insights into the quality of
-WW-type approximations from \ps{models}.
+WW-type approximations from models.
 
@@
 the different model interactions, and it is important to discuss
-critically how realistically they describe the $\bar{q}gq$-terms
+critically how realistically they describe the $\bar{q}gq$--terms
 of QCD \cite{Lorce:2014hxa,Lorce:2016ugb}.
@@
 for quarks and antiquarks \cite{Lorce:2014hxa}. The degrees of freedom
-in this model are quarks, antiqarks and Goldstone bosons which are 
+in this model are quarks, antiquarks and Goldstone bosons which are 
 strongly coupled (the coupling constant is $\sim 4$) and has to be
@@
 dynamical reasons for the smallness of the {\sl matrix elements} of
-$\bar qgq$-operators. This requires the consideration of chiral symmetry 
+$\bar qgq$--operators. This requires the consideration of chiral symmetry 
 breaking effects reflected in the hadronic spectrum, as considered in the
@@
 natural feature may indicate that in the region dominated by effects of
-small $P_T$ tilde-terms might be small. On the other hand, quarks have 
+small $P_\perp$ tilde-terms might be small. On the other hand, quarks have 
 sizable constituent masses of the order of few hundred MeV in spectator models 
@@
 TMDs, and experiments will decide how well the approximations work.
-\ps{In some cases, however, we know in advance that the WW-type approximations 
-have limitations, which we discuss in the next section.}
+In some cases, however, we know in advance that the WW-type approximations 
+have limitations, see next section.
 
@@
 
-\ps{The WW-type approximations have limitations} in the description of 
+The WW-type approximations have limitations in the description of 
 those twist-3 T-odd TMDs which appear in the decomposition of the 
@@
 symmetry of strong interactions. This argument does not apply to other T-odd 
-TMDs because they drop out from the $\kperp$-integrated correlator due to 
+TMDs because they drop out from the $\kperp$--integrated correlator due to 
 explicit factors of e.g.\ $\kperp^j$ in the case of the Sivers function.
@@
 Let us first discuss the case of $f_T^a(x,k_\perp)$. Taking the  
-WW-type approximation (\ref{Eq:WW-type-fT}) literally \ps{means}
-$x\int d^2 k_\perp\,f_T^a(x,k_\perp)\,\ps{\stackrel{!?}{=}}
+WW-type approximation (\ref{Eq:WW-type-fT}) literally means
+$x\int d^2 k_\perp\,f_T^a(x,k_\perp)\,\stackrel{!?}{=}
 -f_{1T}^{\perp(1)a}(x)\neq0$ 
@@
 from QCD equations of motion \cite{Bacchetta:2006tn} which yields
-(\ref{Eq:WW-type-fT}). The point is of course 
-that in this case it is essential to keep the tilde-function. 
+(\ref{Eq:WW-type-fT}). The point is that in this case it is 
+essential to keep the tilde-function. 
 The situation for the chirally and T-odd twist-3 
-TMD $h^a(x,k_\perp)$ is completely analog. The third function in
-(\ref{Eq:sum-rules-T-odd}) is $e_L^a(x,k_\perp)$ and causes no issues
-since $e_L^a(x,k_\perp)=\tilde{e}_L^a(x,k_\perp)\approx0$ in WW-type approximation.
+TMD $h^a(x,k_\perp)$ is analog. The third 
+function in (\ref{Eq:sum-rules-T-odd}) causes no issues since 
+$e_L^a(x,k_\perp)=\tilde{e}_L^a(x,k_\perp)\approx0$ in WW-type approximation.
 
@@
 
-At the present stage too little is known in the theory of subleading
-twist TMDs. Below in Sec.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi} 
-we will discuss how one could deal with the TMDs $f_T^a(x,k_\perp)$ and 
-$h^a(x,k_\perp)$ phenomenologically. For now let us keep in mind that 
+Presently too little is known in the theory of subleading twist TMDs. 
+Below in Sec.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi} we 
+will present a pragmatic solution how to deal with the TMDs 
+$f_T^a(x,k_\perp)$ and $h^a(x,k_\perp)$ phenomenologically. 
+For now let us keep in mind that 
 one has to keep a vigilant eye on all WW-type approximations, and 
@@
 %======= SECTION 4: SIDIS IN WW APPROXIMATION ========================
-\section{SIDIS in WW-type approximation \ps{and Gaussian model}}
+\section{SIDIS in WW-type approximation and Gaussian model}
 \label{Sec-4:SIDIS-in-WW-approximation}
@@
 In this section we consequently apply the WW- and WW-type approximation
-to SIDIS, \ps{and describe our procedure to evaluate the structure 
+to SIDIS, and describe our procedure to evaluate the structure 
 functions in this approximation and the Gaussian Ansatz which we use
-to model the $k_\perp$ dependence of TMDs.}
+to model the $k_\perp$ dependence of TMDs.
 
@@
 	{h_T^a-h_T^{\perp a}\to h_1^a}
-	{(\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}),}\\
+	{(\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}),}
+	\label{Eq:WW-type-FUTsinphiS}\\
 F_{UT}^{\sin(2\phi_h -\phi_S)} &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,{\cal C}\biggl[
@@
 The Gaussian Ansatz is approximately compatible with 
-the $\kperp$-shapes obtained from evolution \cite{Aybat:2011zv}
+the $\kperp$--shapes obtained from evolution \cite{Aybat:2011zv}
 or fits to high-energy Tevatron data on weak-boson production
@@
 $xf^{\perp q}(x,\kperp^2)\approx f_1^q(x,\kperp^2)$, one may 
-assume Gaussian $\kperp$-dependence for $f^{\perp q}(x,\kperp^2)$ 
+assume Gaussian $\kperp$--dependence for $f^{\perp q}(x,\kperp^2)$ 
 and for $f_1^q(x,\kperp^2)$ as long as the Gaussian widths
@@
 In the case of the approximations 
-(\ref{Eq:WW-type-5}--\ref{Eq:WW-type-8})
-the situation is different. In these approximations a twist-3 TMD
-is related to a transverse moment of twist-2 TMD. In such cases the 
+(\ref{Eq:WW-type-gT}--\ref{Eq:WW-type-8})
+the situation is different because here twist-3 TMDs
+are related to transverse moments of twist-2 TMDs. In such cases the 
 Gaussian Ansatz is not compatible with the WW-type approximations:
-for instance, the approximation (\ref{Eq:WW-type-5}) relates
+for instance, the approximation (\ref{Eq:WW-type-gT}) relates
 $xg_T^q(x,\kperp^2)\approx\frac{k_\perp^2}{2M_N^2}\,g_{1T}^{q}(x,\kperp^2)$,
 i.e.\ if $g_{1T}^q(x,\kperp^2)$ was exactly Gaussian then 
-$g_T^q(x,\kperp^2)$ certainly could not be Gaussian. If one would take
+$g_T^q(x,\kperp^2)$ certainly could not be Gaussian. If one wanted to take
 the Gaussian Ansatz and WW-type approximations literally, one clearly
@@
 Notice that the failure of the WW-type approximations
-(\ref{Eq:WW-type-5}--\ref{Eq:WW-type-8}) in the limit $k_\perp\to 0$ is 
+(\ref{Eq:WW-type-gT}--\ref{Eq:WW-type-8}) in the limit $k_\perp\to 0$ is 
 not specific to the Gaussian model,
@@
 a practical scheme how to use responsibly the WW-type approximations in 
-Eqs.~(\ref{Eq:WW-type-5}--\ref{Eq:WW-type-8}).
+Eqs.~(\ref{Eq:WW-type-gT}--\ref{Eq:WW-type-8}).
 
@@
 
-Notice that in principle one could choose a different order
-of the steps: first use WW-type approximations and then
-solve the convolution integrals assuming  Gaussian Ansatz.
-This would constitutes ``alternative scheme'' with 
-in general different (and bulkier) analytical expressions.
-Given the modest understanding of factorization for twist-3 
-TMDs it is not possible to discriminate which scheme might be a
-better approximation. But we convinced ourselves that the two 
-schemes yield similar results for the structure functions, and the 
-differences are numerically within the accuracy expected for
-this approach.
-
-When following the above-described scheme (solving first the 
-convolutions integrals and using then WW-type approximations) 
-we will see that the results for the structure functions can 
-be conveniently expressed in terms of the basis TMDs or their
-adequate transverse moments. We will come back to this point.
-
-Finally, let us recall that the WW-type approximations 
-(\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-last}) for those
-twist-3 T-odd TMDs which are subject to the sum rules
-in Eq.~(\ref{Eq:sum-rules-T-odd}) require special care,
-see the discussion in Sec.~\ref{Sec-3.8:limitations}.
-
+Notice that in some cases (when T-even TMDs are involved) 
+one could choose a different order of the steps: first apply 
+WW-type approximations and then solve convolution integrals 
+with Gaussian Ansatz.
+In general this would yield different (and bulkier) analytical 
+expressions, but we convinced ourselves that the differences 
+are numerically within the accuracy expected for this approach.
+\red{However, for the structure functions discussed in
+Secs.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi}
+such an ``alternative scheme'' would give results at
+variance with the sum rules in for the twist-3 T-odd TMDs
+in Eq.~(\ref{Eq:sum-rules-T-odd}), as discussed in 
+Sec.~\ref{Sec-3.8:limitations}. 
+The scheme presented here will allow us to implement those sum 
+rules in a convenient and consistent way. We will follow up on 
+this in more detail in 
+Secs.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi}.}
+
+To summarize, our procedure is to solve first the convolution 
+integrals in Gauss Ansatz, and use then WW-type approximations.
+When implementing this procedure we will see that the results 
+for the structure functions can be conveniently expressed in 
+terms of the basis TMDs or their adequate transverse moments. 
 }
@@
 consider their (1)-moments, and for $ h_{1T}^{\perp a}$  the (2)-moment.
-This has two important advantages. First, this step simplifies the
-the Gaussian Ansatz expressions, and the Gaussian width parameters are
+This has two important advantages. First, this step simplifies 
+the Gaussian model expressions, and the Gaussian width parameters are
 largely absorbed in the definitions of the transverse moments which 
 helps to minimize the model-dependence. Second,
-the $k_\perp$-moments of these TMDs have in principle simple definitions
+the $k_\perp$--moments of these TMDs have in principle simple definitions
 in QCD (whereas e.g.\ the function $f_{1T}^{\perp q}(x)$ can be computed in
@@
 The parameters $\avkperp_{f_1}$ and $\avpperp_{D_1}$ can
-be assumed to be flavor- and $x$- or $z$-dependent, as present
+be assumed to be flavor- and $x$-- or $z$--dependent, as present
 data do not allow us to constrain too many parameters, see
@@
 relaxed, e.g. theoretical studies in chiral effective field theories 
-predict a strong flavor-dependence in the $\kperp$-behavior
+predict a strong flavor-dependence in the $\kperp$--behavior
 of sea and valence quark TMDs \cite{Schweitzer:2012hh}.
@@
 Left panel: 
-	cross section for $\pi^+$ production normalized with 
+	$F_{UU}(P_{hT}^2)$ for $\pi^+$ production normalized with 
 	respect to its value at zero transverse momentum at 
@@
 correctly connects the structure function $F_{UU}(x,z,\Phperp)$ 
-in (\ref{Eq:FUU-Phperp}) with its $\Phperp$-integrated counterpart
+in (\ref{Eq:FUU-Phperp}) with its $\Phperp$--integrated counterpart
 (\ref{Eq:FUU}). In our effective description this is step is trivial. In 
@@
 Figure~\ref{FUU-show-pT-dependence} illustrates how the Gaussian Ansatz
-describes selected SIDIS data. 
-In Fig.~\ref{FUU-show-pT-dependence} (a) we show CLAS data 
-\cite{Osipenko:2008aa} on $\pi^+$ production from proton 
-with a 5.75 GeV beam which shows a Gaussian $P_{hT}$-dependence
+describes selected SIDIS data:
+the left panel shows CLAS data \cite{Osipenko:2008aa} on $\pi^+$ production 
+from proton with a 5.75 GeV beam which exhibit Gaussian $P_{hT}$--dependence
 over 2 orders of magnitude, see \cite{Schweitzer:2010tt} for details.
-In Fig.~\ref{FUU-show-pT-dependence} (b) we plot 
-the HERMES multiplicity~\cite{Airapetian:2012ki}
+The middle panel in Fig.~\ref{FUU-show-pT-dependence} displays the 
+HERMES multiplicity~\cite{Airapetian:2012ki}
 \be\label{Eq:multiplicity-HERMES}
@@
 \ee
-at $\la Q^2\ra=2.87\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.22$ 
-for $\pi^+$ production on the proton target.
-In Fig.~\ref{FUU-show-pT-dependence} (c) we plot the COMPASS multiplicity 
+at $\la Q^2\ra=2.87\,{\rm GeV}^2$, $\la x\ra=0.15$, $\la z\ra=0.22$ 
+for $\pi^+$ production on the proton target. The right panel of
+Fig.~\ref{FUU-show-pT-dependence} shows the COMPASS multiplicity 
 \cite{Aghasyan:2017ctw}
@@
 The first experimental results on the 
-$\Phperp$-dependence of $A_{LL} = F_{LL}/F_{UU}$ were presented by
-Jefferson Lab \cite{Avakian:2010ae}. The definition of the asymmetry 
+$\Phperp$--dependence of $A_{LL} = F_{LL}/F_{UU}$ were presented by
+Jefferson Lab (JLab) \cite{Avakian:2010ae}. The definition of the asymmetry 
 in  \cite{Avakian:2010ae} was
@@
 	Another important test was already presented in 
-	\cite{Avakian:2010ae}: the $\Phperp$-integrated (``collinear'')
+	\cite{Avakian:2010ae}: the $\Phperp$--integrated (``collinear'')
 	asymmetry (\ref{Eq:FLL}) is compatible with data
@@
 	parametrizations of $f_1^a(x)$, $g_1^a(x)$, $D_1^a(z)$. This 
-	shows that even at the moderate beam energies of the pre-12GeV era 
-	one was indeed already probing DIS at Jefferson Lab,
+	shows that even at the moderate beam energies of the pre-12GeV 
+	era one was indeed probing DIS at JLab,
 	at least to a very good approximation \cite{Avakian:2010ae}.}
@@
 
-The $F_{UT}^{\sin(\phi_h-\phi_S)}$ \ps{structure function} is related to the 
-Sivers function~\cite{Sivers:1989cc}, which describes the \ps{distribution}
+The $F_{UT}^{\sin(\phi_h-\phi_S)}$ structure function is related to the 
+Sivers function~\cite{Sivers:1989cc}, which describes the distribution
 of unpolarized quarks inside a transversely polarized proton, has so far 
@@
 on charged pion production from a proton target \cite{Airapetian:2009ae}.
-The $x$- and $P_{hT}$-dependencies of the asymmetry are displayed. The 
+The $x$-- and $P_{hT}$--dependencies of the asymmetry are displayed. The 
 latter shows that the Gaussian model works well also in this case.
@@
 \newpage
-
 \subsection{\boldmath Leading twist $A_{UT}^{\sin(\phi_h+\phi_S)}$ Collins asymmetry}
@@
 on charged pion production from a proton target \cite{Airapetian:2009ae}.
-Also in Fig.~\ref{aut_h1_jlab} we show the $x$- and $P_{hT}$-dependencies 
+Also in Fig.~\ref{aut_h1_jlab} we show the $x$-- and $P_{hT}$--dependencies 
 of this azimuthal spin asymmetry. The right panel of Fig.~\ref{aut_h1_jlab}
-on the $P_{hT}$-dependence shows that the data are compatible with the 
+on the $P_{hT}$--dependence shows that the data are compatible with the 
 Gaussian Ansatz. Let us remark that the COMPASS data are described equally 
@@
 values of $Q$ could be achieved in the fixed target experiments.
-A notable exception is COMPASS where the largest $x$-bins 
+A notable exception is COMPASS where the largest $x$--bins 
 (where $Q^2$ is largest) bear the best hints on this TMD,
 see Fig.~\ref{aut_h1tp_jlab}.
-Future high luminosity data from Jefferson Lab 12 are expected 
+Future high luminosity data from JLab 12 are expected 
 to significantly improve our knowledge of this TMD.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
+\begin{figure}[h!]
 \centering
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_PT.pdf}
-\caption{\label{aut_h1tp_jlab}  Comparison of calculation of $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  using fit results of Ref.~\cite{Lefky:2014eia} as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at $\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 3.6$ GeV$^2$ and preliminary COMPASS data \cite{Parsamyan:2010se}.
+\caption{\label{aut_h1tp_jlab}  $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  
+	as a function of $ x $ (left panel) and $P_{hT}$ (right panel) 
+	at $\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 3.6$ GeV$^2$ 
+	on the basis of fits from \cite{Lefky:2014eia} 
+	vs preliminary COMPASS data \cite{Parsamyan:2010se}.
 }
@@
 	$h^{\perp (1) q}_{1L}(x)$ distributions (right panel) 
-	for $u$- and $d$-flavor 
+	for $u$-- and $d$--flavor 
 	as predicted by the WW-ype approximations in
@@
 %\includegraphics[width=0.3\textwidth]{\FigPath/ALT_COMPASS_x.pdf}  
-\includegraphics[width=0.9\textwidth]{Fig-COMPASS-A_LT_Pr10.pdf}
+\includegraphics[width=0.9\textwidth]{\FigPath/Fig-COMPASS-A_LT_Pr10.pdf}
 	\caption{\label{g1t_jlab} 
@@
 	subleading-twist $A_{LT}^{\cos(2\cos\phi_h-\phi_S)}$
-	on which we comment in Sec.~\ref{Sec-7.5:FLTcos2phi-phiS}.}
+	on which we comment in Sec.~\ref{Sec-7.3:FLTcos2phi-phiS}.}
 \end{figure}
@@
 
-The left panel of Fig.~\ref{g1t_jlab} shows the 2010 COMPASS data 
-for $A_{LT}^{\cos(\phi_h -\phi_S)}$ \cite{Parsamyan:2015dfa} measured 
-with 160 GeV longitudinally polarized muons impinging on a 
-transversely polarized proton (NH$_3$) target \cite{Goertz:2002vv}. 
-As at COMPASS about $90\,\%$ of charged hadrons are $\pi^\pm$, in our 
-calculation we approximate charged hadron fragmentation functions by 
-$D_1^a(z)$ of pions, see App.~\ref{App:basis-f1-D1}.
-Clearly, our results describe the data rather well within the 
-experimemental uncertainties. We observe that the WW-type 
-approximation works in this case. For comparison also results from 
+This asymmetry was measured at JLab and COMPASS 
+\cite{Huang:2011bc,Parsamyan:2015dfa}. Left panel of Fig.~\ref{g1t_jlab} 
+shows 2010 COMPASS data \cite{Parsamyan:2015dfa} measured with 160 GeV 
+longitudinally polarized muons impinging on a transversely polarized proton 
+(NH$_3$) target \cite{Goertz:2002vv}. We approximate the charged hadrons
+($90\,\%$ of which are $\pi^\pm$ at COMPASS) by charged pions, see 
+App.~\ref{App:basis-f1-D1}.
+Our results are shown as a shaded area which indicates a rough estimate
+of the uncertainty of the WW-type approximation.
+We observe that the WW-type approximation describes the data within 
+their experimemental uncertainties.
+For comparison results from the theoretical works 
 \cite{Kotzinian:2006dw,Kotzinian:2008fe,Boffi:2009sh} are shown.
-The results shown in middle and right panel of Fig.~\ref{g1t_jlab} will be 
-discussed in Secs.~\ref{Sec-7.2:FLTcosphiS},~\ref{Sec-7.5:FLTcos2phi-phiS}.
+Our results are also compatible with the JLab data which was 
+taken with a neutron ($^3$He) target \cite{Huang:2011bc} and has 
+larger statistical uncertainty than COMPASS data. The middle and right 
+panels of Fig.~\ref{g1t_jlab} will be discussed in 
+Secs.~\ref{Sec-7.2:FLTcosphiS},~\ref{Sec-7.3:FLTcos2phi-phiS}.
 
@@
 
-We assume Gaussian form for the Kotzinian-Mulders function 
-$h_{1L}^{\perp a}$, see Eq.~(\ref{eq:h1l_final}) in
-App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}. From 
-Eq.~(\ref{Eq:WW-approx-h1L}) we obtain the WW-type estimate
+We use the Gaussian form for the Kotzinian-Mulders function 
+$h_{1L}^{\perp a}$, Eq.~(\ref{eq:h1l_final}) in
+App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, with
+$\avkperp_{h_{1L}^\perp} = \avkperp_{h_{1}}$ as
+supported by lattice data \cite{Hagler:2009mb}.
+From (\ref{Eq:WW-approx-h1L}) we obtain the WW-type estimate
 for $h_{1L}^{\perp(1) a}(x)$ shown in Fig.~\ref{g1t_h1l_functions}. 
-For the Gaussian width we assume $\avkperp_{h_{1L}^\perp} = \avkperp_{h_{1}}$ 
-supported by lattice data \cite{Hagler:2009mb}.
-
 The structure function $F_{UL}^{\sin(2\phi_h)}$ reads
@@
 \centering
-\includegraphics[height=3.4cm]{Fig-COMPASS-A_2_Pr0711_Zgt02.pdf} \quad
+\includegraphics[height=3.4cm]{\FigPath/Fig-COMPASS-A_2_Pr0711_Zgt02.pdf} \quad
 \includegraphics[height=3.4cm]{\FigPath/AULsin2phi_JLAB_x.pdf}  
@@
 	\cite{Airapetian:1999tv} and COMPASS \cite{Parsamyan:2015dfa} 
-	experiments (left panel) and at Jefferson Lab 
+	experiments (left panel) and at JLab 
 	\cite{Jawalkar:2017ube} in comparison to predictions from
-	WW-type approximation.}
+	WW-type approximation. Predictions from \cite{Avakian:2007mv}
+	are shown for comparison.}
 \end{figure}
@@
 The asymmetry $A_{UL}^{\sin(2\phi_h)}=F_{UL}^{\sin(2\phi_h)}/F_{UU}$  was 
-studied at HERMES \cite{Airapetian:1999tv,Airapetian:2002mf}, 
-COMPASS \cite{Parsamyan:2015dfa}, and JLab \cite{Jawalkar:2017ube}.
-In the left panel of Fig.~\ref{aul_jlab} the results for proton
-target are shown. At HERMES 27.6 GeV positrons from the HERA polarized 
-positron storage ring at DESY scattering off a nuclear-polarized hydrogen 
-internal gas targets \cite{Stock:1994vv} in the kinematics
-$1\,{\rm GeV}^2 < Q^2 < 15 \,{\rm GeV}^2$, $W > 2\,{\rm Gev}$,
-$0.023 < x < 0.4$ and $y < 0.85$. The data for $\pi^\pm$ from 
-proton are shown in Fig.~\ref{aul_jlab}. The COMPASS data show 
-the asymmetry for charged hadrons, which in practice are mainly
-pions. Since $y$-dependent prefactors were included in the
-analyses (see Sec.~\ref{Sec-2.1:SIDIS+structure-functions}),
-the HERMES data is adequately rescaled (``$D(y)$--rescaled'').
-
-\ \\
-\red{\large\bf Stopping here. Sending to Alexei!
-Continue from here.}
+studied at HERMES \cite{Airapetian:1999tv,Airapetian:2002mf}, COMPASS 
+\cite{Parsamyan:2015dfa}, and JLab \cite{Avakian:2010ae,Jawalkar:2017ube}.
+In Fig.~\ref{aul_jlab} proton data are shown. At HERMES $\pi^\pm$ 
+were produced in scattering of 27.6 GeV positrons from the HERA 
+polarized positron storage ring at DESY off nuclear-polarized 
+hydrogen internal gas target \cite{Stock:1994vv} 
+for $1\,{\rm GeV}^2 < Q^2 < 15 \,{\rm GeV}^2$, $W > 2\,{\rm Gev}$,
+$0.023 < x < 0.4$ and $y < 0.85$. The COMPASS data show the 
+asymmetry for charged hadrons (in practice mainly pions).
+Since $y$--dependent prefactors were included in the analyses 
+(see Sec.~\ref{Sec-2.1:SIDIS+structure-functions}),
+the HERMES data is adequately (``$D(y)$--'')rescaled.
+The CLAS $\pi^0$ data in the right panel were measured using 6$\,$GeV 
+longitudinally polarized electrons scattering off 
+longitudinally polarized protons in a cryogenic $^{14}$NH$_3$ 
+target in the kinematics $1.0\,{\rm GeV}^2 < Q^2 < 3.2\,{\rm GeV}^2$, 
+$0.12 < x < 0.48$ and $0.4 < z < 0.7$ \cite{Jawalkar:2017ube}.
+
+$A_{UL}^{\sin(2\phi_h)}$  can be expected to be smaller than 
+$A_{LT}^{\cos(\phi_h -\phi_S)}$ discussed in previous section,
+even though both are leading twist. This is because 
+$F_{UL}^{\sin(2\phi_h)}$ is quadratic in the hadron transverse 
+momenta $P_{hT}\ll Q$, while $F_{LT}^{\cos(\phi_h -\phi_S)}$ is linear. 
+In addition, the former is proportional to the Collins function 
+which is smaller than $D_1^q(z)$, and the WW-type approximation 
+predicts the magnitude of $h_{1L}^{\perp(1)q}(x)$ to be about half 
+of the size of $g_{1T}^{\perp(1)q}(x)$.
+The data support these expectations. HERMES and JLab data are compatible
+with zero for this asymmetry. So are COMPASS data except for the region
+$x>0.1$ for negative hadrons, where the trend of the data provides a first 
+encouraging confirmation for our results. The current data are compatible
+with the WW-type approximation for $h_{1L}^{\perp(1)q}(x)$.
 
@@
 
-We discussed WW-type approximations for
-$g^{\perp q}_{1T}$ and $h^{\perp q}_{1L}$ and the two
-twist-2 structure functions amenable to this approximation
-in Secs.~\ref{Sec-6.1:FLTcosphi-phiS} and~\ref{Sec-6.2:FULsin2phi}.
-Before focusing on twist-3 let us pause 
-and revisit positivity bounds \cite{Bacchetta:1999kz} 
-which offer unique cross checks.
+We discussed WW-type approximations for the twist-2 TMDs
+$g^{\perp q}_{1T}$ and $h^{\perp q}_{1L}$ 
+in Secs.~\ref{Sec-6.1:FLTcosphi-phiS}, \ref{Sec-6.2:FULsin2phi}.
+Before proceeding with twist-3 let us pause and revisit positivity 
+bounds \cite{Bacchetta:1999kz}. % which offer unique cross checks.
 
@@
 \begin{subequations}\ba
-	\frac{\kperp^2}{M^2}\left[ (h^{\perp q}_{1L}(x,\kperp^2))^2 + 
-	(h_{1}^{\perp q}(x,\kperp^2))^2\right] 
-	& \le & (f_{1}^{q}(x,\kperp^2))^2 \, ,\\
-	\frac{\kperp^2}{M^2}\left[ (g^{\perp q}_{1T}(x,\kperp^2))^2 
-	+ (f_{1T}^{\perp q}(x,\kperp^2))^2\right] 
-	& \le & (f_{1}^{q}(x,\kperp^2))^2 \; . 
+	\frac{\kperp^2}{4M_N^2}\;(f_{1}^{q}(x,\kperp^2))^2 
+	- (h^{\perp(1)q}_{1L}(x,\kperp^2))^2 
+	- (h_{1}^{\perp(1)q}(x,\kperp^2))^2
+	& \ge & 0\,, \label{eq:positivity}\\
+	\frac{\kperp^2}{4M_N^2}\;(f_{1}^{q}(x,\kperp^2))^2 
+	- (f_{1T}^{\perp(1)q}(x,\kperp^2))^2
+	- (g^{\perp(1)q}_{1T}(x,\kperp^2))^2 
+	& \ge & 0\,. \label{eq:positivity1}
 \ea\end{subequations}
-From these inequalities and our Gaussian Ans\"atze in 
-Eqs.~(\ref{Eq:Gauss-f1}, \ref{Eq:Gauss-h1}, \ref{Eq:Gauss-f1Tperp}, 
-\ref{Eq:Gauss-h1perp}, \ref{eq:g1t}, \ref{eq:h1l_final}) one obtains 
-(after $k_\perp$-integration and mutliplication by $16\pi M_N^2$) 
-the inequalities
-\begin{subequations}\ba
-	(f_{1}^{q}(x))^2
-	- \frac{4M^2 (f_{1T}^{\perp q}(x))^2}{\avkperp_{f_{1T}^\perp} } 
-	- \frac{4M^2 (g_{1T}^{\perp q}(x))^2}{\avkperp_{g_{1T}^\perp} } &\ge& 0
-	\;, \label{eq:positivity}\\
-	(f_{1}^{q}(x))^2 
-	- \frac{4M^2 (h_{1}^{\perp q}(x))^2}{\avkperp_{h_{1}^\perp} } 
-	- \frac{4M^2 (h_{1L}^{\perp q}(x))^2}{\avkperp_{h_{1TL}^\perp} } &\ge& 0\,.
-	\mbox{\red{\ (introduce (1)-moments!)}}
-\label{eq:positivity1}
-\ea\end{subequations}
+The inequalities provide a non-trivial test of our approach.
+The inequalities (\ref{eq:positivity},~\ref{eq:positivity1}) 
+must be strictly satisfied by the {\it exact} leading--order QCD 
+expressions for the TMDs.  
+(For PDFs it is known that positivity can be preserved in some 
+schemes but violated in other schemes. For TMDs not much is 
+known about positivity conditions beyond leading order.)
+However, here we do not deal with exact TMDs but (i) we invoked 
+strong model assumptions (WW-type approximations for $g^{\perp q}_{1T}$ 
+and $h^{\perp q}_{1L}$ and Gauss Ansatz for all TMDs), and (ii) we deal 
+with first extractions which have sizable uncertainties including 
+poorly controlled systematic uncertainties.
+Therefore, considering that we deal with approximations 
+(WW-type, Gauss) and considering the current state of TMD-extractions, 
+the inequalities (\ref{eq:positivity},~\ref{eq:positivity1}) constitute
+a challenging test for the approach.
 
@@
 	\caption{\label{h1l_pos} 
-	LHS of Eq.~\eqref{eq:positivity1}.
-	LHS of Eq.~\eqref{eq:positivity}.}
+	The normalized inequalities for $g^{\perp(1)q}_{1T}(x)$ and
+	$h^{\perp(1)q}_{1L}(x)$ vs $x$. The normalized inequalities
+	are defined such that they must be positive (and smaller
+	than one), see text for details. Clearly, our approach
+	respects both positivity conditions.}
 \end{figure}
@@
 
-The left-hand-sides of these inequalities are plotted in 
-Fig.~\ref{h1l_pos} which shows that positivity is satisfied 
-in 3 out of 4 cases: only (\ref{eq:positivity1}) for $d$-flavor 
-seems violated for $x>0.2$.
-
-At this point some remarks are in order.
-First, the inequalities (\ref{eq:positivity},~\ref{eq:positivity1}) 
-must be strictly satisfied by the {\it exact} leading--order QCD 
-expressions for the TMDs. 
-(For PDFs it is known that positivity can be preserved in some schemes 
-and violated in other schemes. For TMDs not much is known about 
-positivity conditions beyond leading order.)
-However, here we do not deal with exact expressions for the TMDs
-but we invoked two strong model assumptions: WW-type
-approximations for $g^{\perp q}_{1T}$ and $h^{\perp q}_{1L}$, and 
-Gauss Ansatz for all TMDs. This is a lot! Neverthelss we find 
-that (\ref{eq:positivity},~\ref{eq:positivity1}) are respected 
-for $x<0.2$. This is a non-trivial cross check of our aproach. 
-Second, available data constraining the TMDs are mostly at $x<0.2$. 
-There are in fact only few $x$-bins above $x>0.2$. For $x>0.4$ the 
-available parameterizations of TMDs are practically unconstrained.
-Third, the determination of the Boer-Mulders function from 
-Ref.~\cite{Barone:2015ksa} is far from ideal especially for $d$-flavor, 
-and non-factorizing power-corrections (due to Cahn effect) may be at play.
-
-Considering that we deal with approximations (WW-type, Gauss) 
-and considering current state of TMD-extractions, the 
-positivity test in Fig.~\ref{h1l_pos} can be considered satisfactory.
+To conduct a test we use the Gaussian Ans\"atze 
+(\ref{Eq:Gauss-f1}, \ref{Eq:Gauss-h1}, \ref{Eq:Gauss-f1Tperp}, 
+\ref{Eq:Gauss-h1perp}, \ref{eq:g1t}, \ref{eq:h1l_final}) for the
+TMDs and integrate over $k_\perp$. The results are shown in 
+Fig.~\ref{h1l_pos} where we plot the ``normalized inequalities'' 
+defined as follows:
+given an inequality $a-b-\dots \ge 0$, the normalized inequality 
+is defined as: $0 \le (a-b-\dots)/(|a|+|b|+\dots) \le 1$.
+
+Fig.~\ref{h1l_pos} shows that the results of our approach for the 
+``normalized inequalities'' for both TMDs lie between between
+zero and one, as it is dictated by positivity constraints.
+This is an important consistency cross-check for our approach.
 
@@
 
-The WW-type approximations are useful for all 8 subleading--twist observables,
+WW-type approximations can be applied to all 8 subleading--twist observables,
 as shown in Sec.~\ref{Sec-4.2:WW-twist-3}. In view of the complex 
-structure of subleading--twist structure functions, WW-type approximations
+structure of SIDIS at subleading--twist, WW-type approximations
 are potentially very useful for the interpretation of twist-3 observables.
@@
 Eq.~(\ref{FLUsinphi}), containing 4 terms: 
-2 are proportional to pure twist-3 fragmentation functions 
+2 term are proportional to pure twist-3 fragmentation functions 
 $\tilde{G}^{\perp a}$ and $\tilde{E}^a$ and neglected; the other 2
@@
 
-But data from Jefferson Lab, HERMES \ps{and COMPASS} show a small 
+Data from JLab, HERMES \ps{and COMPASS} show a small 
 but clearly non-zero effect of the order of (2-3)\,$\%$ 
 \cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,Aghasyan:2011ha,
-Adolph:2014pwc,Gohn:2014zbz,Adolph:2014pwc}.
-What may seem at first glance to be a failure of the approach is in 
-fact in line with it.
-The important point is that in this case, the entire effect is due 
-to $\bar qgq$-terms only. More precisely, the numerator of the 
-asymmetry is proportional to $\bar q g q$-correlators, while the 
-denominator is of course give by $f_1^aD_1^a$, i.e.\ in terms of
-$q q$-correlators. Therefore we may formulate this approximation 
-as follows
+Adolph:2014pwc,Gohn:2014zbz}. At first glance this may seem a failure 
+of our approach. However, the numerator of the asymmetry is proportional 
+to $\bar q g q$--correlators, while the denominator ($f_1^aD_1^a$) is a 
+$q q$--correlator. Therefore we may express this observation as
 \be\label{Eq:ALU-small}
-    A_{LU}^{\sin\phi_h}  
+    	|A_{LU}^{\sin\phi_h}|
 	\;\; \propto \;\;\frac{\la\bar qgq\ra}{\la\bar qq\ra}
-    	\;\;\stackrel{\rm exp}{=} \;\; 
-	{\cal O}\biggl( (2-3)\,\%\biggr)
+    	\;\;\stackrel{\rm exp}{\lesssim} \;\; 
+	{\cal O}(3\,\%)
     	\;.
@@
 Adolph:2014pwc,Gohn:2014zbz}
-as an encouraging indication that $\bar qgq$-terms are smaller than 
+as an encouraging indication that $\bar qgq$--terms are smaller than 
 $\bar qq$ terms, in line with the generic expectation (\ref{Eq:WW-generic}).
 
-To conclude, the WW-type approximation does not fail in the case of 
-$F_{LU}^{\sin\phi}$. This is a unique observable, the only twist-3 SIDIS 
-structure not ``contaminated'' by leading twist terms. 
-Our WW-type approximation qualitatively predicts the asymmetry 
-$A_{LU}^{\sin\phi}$ to be small which is in agreement with experiment.
-It is beyond our approach to make in this case a quantitative prediction. 
-We notice that one obtains a zero result for this asymmetry also in
-the parton model motivated approach limited to leading twist TMDs 
-\cite{Anselmino:2011ch}.
-
-\ \\
-\blue{\bf
-  COMPASS: https://arxiv.org/pdf/1401.6284.pdf \\
-  data: https://hepdata.net/record/ins1278730}
-
-\begin{figure}[h!]
-\includegraphics[width=0.8\textwidth]{Fig-COMPASS-A_LL_Pr0711_Zgt02.pdf}
-\end{figure}
-
-\begin{figure}[h!]
-\includegraphics[width=0.8\textwidth]{Fig-COMPASS-A_UL1_Pr0711_Zgt02.pdf}
-\end{figure}
-
-\begin{figure}[h!]
-\includegraphics[width=0.8\textwidth]{Fig-COMPASS-A_UT_Pr10.pdf}
-\end{figure}
+To conclude, the WW-type approximation predicts $A_{LU}^{\sin\phi}\approx 0$
+which is ``compatible'' with experiment in the sense that the data show a 
+small asymmetry. Notice however that some asymmetries appear in experiment
+even smaller (compatible with zero) despite being non-zero in WW-type
+approximation. Further work is needed before we can draw definite
+conclusions. In any case, $F_{LU}^{\sin\phi}$ is the only twist-3 SIDIS 
+structure not ``contaminated'' by leading twist which provides a
+unique window into higher twist physics.
+
+\newpage
 
@@
 
-In the WW-type approximation the structure function
+In  WW-type approximation the structure function
 $F_{LT}^{\cos\phi_S}$ is due to $g_T^a(x,\kperp)$ and $D_1^a(z,\pperp)$ 
-whose collinear counterparts are more or less well known, see
+whose collinear counterparts are more or less known, see
 Secs.~\ref{Sec-3.4:WW-classic-experiment} and \ref{Sec-5.1:FUU-basis}.
-
-We assume the Gaussian Ansatz for $g_T^a(x,\kperp)$ 
-\be
-	g^{q}_{T}(x,\kperp^2) = 
-	g^{q}_{T}(x)\,\frac{1}{\pi \avkperp_{g_{T}}}\,
-	e^{-\kperp^2/{\avkperp_{g_{T}}}}\;,
-	\label{eq:gtnew}
-\ee
-where $g^{q}_{T}(x)$ is calculated according to Eq.~(\ref{Eq:WW-original1}).
-Notice that we could have used WW-type relation of Eq.~(\ref{Eq:WW-type-6}) 
-to relate $g^{q}_{T}(x,\kperp^2)$ and $g^{\perp q}_{1T}(x,\kperp^2)$ however we 
-choose not to do it. In fact Eq.~(\ref{Eq:WW-type-6}) suggests kinematical 
-zero $g^{q}_{T}(x, 0) = 0$  which is not supported by the model calculations 
-\cite{Avakian:2010br} and thus  Eq.~(\ref{Eq:WW-type-6}) can be used only 
-in its integrated form. 
-The Eq.~(\ref{Eq:WW-type-6}) is not exact and is not on the same footing as 
-WW-approximation of Eq.~(\ref{Eq:WW-original1}), and we parametrize directly 
-$g^{q}_{T}(x,\kperp^2)$ using the Gaussian shape. For illustrative purpose we 
-show ``violation'' of  Eq.~(\ref{Eq:WW-type-6}) in Fig.~\ref{altcosphi_wwtype}.
-
-The $F_{LT}^{\cos\phi_S}$ structure function then reads 
+We assume the Gaussian Ansatz for $g_T^a(x,\kperp)$ shown in
+Eq.~(\ref{eq:gtnew}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} 
+with ${\avkperp_{g_T}}={\avkperp_{g_1}}$. We then determine $g^{q}_{T}(x)$ 
+according to Eq.~(\ref{Eq:WW-original1}) which is a well-tested
+approximation in DIS, see Sec.~\ref{Sec-3.4:WW-classic-experiment}.
+In this way we obtain for $F_{LT}^{\cos\phi_S}$ the result
 \begin{subequations}\ba
@@
 	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\, g_T^q(x)\,D_1^q(z)\, ,
+	\label{Eq:FLTcosphiS-Gauss-b}
 \ea\end{subequations}
 with the width $\lambda= z^2 \avkperp_{g_T} + \avpperp_{D_1}$
-in the Gaussian ${\cal G}(\Phperp)$. We estimate $g_T^a(x)$ in terms 
-of $g_1^a(x)$ according to Eq.~(\ref{Eq:WW-original1}) assuming for 
-the Gaussian width $\avkperp_{g_T}=\avkperp_{g_1}$.\footnote{
-	Notice that one could also proceed in a different way: 
-	explore first the WW-type-relation (\ref{Eq:WW-type-5}), and
-	assume then the Gaussian Ansatz for $g_{1T}^{\perp}(x,\kperp)$ 
-	according to (\ref{eq:g1t}). Solving then the convolution integral 
-	yields a result different from (\ref{Eq:FLTcosphiS-Gauss})
-	which depends much more strongly on Gaussian model parameters.
-	The operations of applying the WW-type approximations and 
-	employing the Gaussian Ansatz do not commute in general.
-	The solution presented in (\ref{Eq:FLTcosphiS-Gauss}) is 
-	preferable as it helps to minimize model dependence.}
-
-Asymmetries $A_{LT}^{\cos\phi_S} = F_{LT}^{\cos\phi_S}/F_{UU}$ for 
-COMPASS are plotted in Fig.~\ref{altcosphi_jlab}.
-Notice that the asymmetry scales at small transverse hadron
-momenta as $A_{LT}^{\cos\phi_S} \propto (\Phperp)^0$ which makes
-it easier to measure if longitudinally polarized lepton beams
-and transversely polarized targets are available.
-
-\ \\
-\ps{We should include a comparison to 
-COMPASS data \cite{Kotzinian:2007uv,Parsamyan:2010se}.}
+in the Gaussian ${\cal G}(\Phperp)$.
+
+Notice that we followed here the scheme explained in 
+Sec.~\ref{Sec-4.4:evaluation}: first assume Gaussian Ansatz, then apply 
+WW-type type approximation. For some structure functions the order of 
+these steps is not relevant, but here it is. It is instructive to 
+discuss what the opposite order of these steps yields. 
+One may first plug in the WW-type approximation (\ref{Eq:WW-type-gT}) 
+in the convolution integral (\ref{Eq:WW-original1}) and then solve the
+convolution integral with Gaussian Ansatz. The result is an
+analytical expression which is bulkier than (\ref{Eq:FLTcosphiS-Gauss})  
+though it yields a numerically similar result. But there are 2 critical
+issues with that. First, the WW-type approximation (\ref{Eq:WW-type-gT}) 
+relates $g^{q}_{T}(x,\kperp^2)$ to $g^{\perp(1)q}_{1T}(x,\kperp^2)$ which
+(due to the weight $\kperp^2/(2M_N^2)$ in the (1)-moment) implies a kinematical 
+zero in $\kperp$ as $g^{q}_{T}(x, 0) = 0$  which is not supported by model 
+calculations \cite{Avakian:2010br}. Second, the more economic (because 
+less bulky) expression in (\ref{Eq:FLTcosphiS-Gauss}) automatically 
+yields (\ref{Eq:FLTcosphiS-Gauss-b}) which is the correct colinear
+result for this SIDIS function in Eq.~(\ref{Eq:FLT-collinear})
+in WW-type approximation. This technical remark confirms that
+consistency of the scheme suggested in Sec.~\ref{Sec-4.4:evaluation}.
+
+In the middle panel of Fig.~\ref{g1t_jlab} our predictions
+for $A_{LT}^{\cos\phi_S}$ are shown in comparison to preliminary
+COMPASS data from Ref.~\cite{Parsamyan:2015dfa}. The predicted
+asymmetry is small and compatible with the COMPASS data within
+error bars. More precise data is necessary to judge the how
+well the WW-type approximation works in this case. Such data
+could come from JLab 12 experiments, see Fig.~\ref{altcosphi_jlab}.
 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/ALTcosPhi_COMPASS_x.pdf} 
-\caption{\label{altcosphi_jlab} $A_{LT}^{\cos\phi_S}$  as a function of $ x $.
+\caption{\label{altcosphi_jlab} Predictions for the double--spin asymmetry
+	$A_{LT}^{\cos\phi_S}$  as a function of $x$ from a proton target
+	at JLab 12.
 }
@@
 
- %%%%%%%%%%%%%
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/gT_vs_g1Tperp_wwtype.pdf} 
-\caption{\label{altcosphi_wwtype} RHS and LHS of Eq.~\ref{Eq:WW-type-6}.
-}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-\subsection{\boldmath   Subleading twist  $A_{LL}^{\cos\phi_h}$}
-\label{Sec-7.3:FLLcosphi}
-
-The structure function $F_{UL}^{\cos\phi_h}$ reads
-\begin{subequations}\ba
-	F_{LL}^{\cos \phi_h}(x,z,\Phperp)
-	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
-	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
-	{ \cal G}(\Phperp ) \, , \\ 
-	F_{LL}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
-	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\;
-	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\, , 
-\ea\end{subequations}
-where $\lambda=z^2 \avkperp_{g_{L}^\perp} + \avpperp_{D_1}$, 
-$b^{(1)}_{\rm B}=2M_N$,
-$c^{(1)}_{\rm B} = \sqrt{\pi}\,M_N$, see App.~\ref{App:convol-details}.
-We approximate the Gaussian width $\avkperp_{g_{L}^\perp}=\avkperp_{g_1}$ and 
-estimate $g_L^{\perp(1) a}(x)$ according to Eq.~(\ref{Eq:WW-type-gLperp}) as
-\be
-	x\,g_L^{\perp(1) a}(x) = \frac{\la \kperp^2\ra_{g_1}}{2\,M_N^2}\,
-	g_1^a(x) \,.
-\ee
-The asymmetries $A_{LL}^{\cos\phi_S}=F_{LL}^{\cos\phi_S}/F_{UU}$  for 
-COMPASS are plotted in Fig.~\ref{allcosphi_jlab}.
-
-\ \\
-\ps{We should include a comparison to 
-COMPASS data \cite{Kotzinian:2007uv,Parsamyan:2010se}.}
-
-\
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/ALLcosphi_COMPASS_x.pdf}  
-	\caption{\label{allcosphi_jlab} 
-	$A_{LL}^{\cos(\phi_h)}$  as a function of $ x $  at typical kinematics 
-	of COMPASS, 
-	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$.
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%
-
-\newpage
-\subsection{\boldmath Subleading twist $A_{UL}^{\sin\phi_h}$ }
-\label{Sec-7.4:FULsinphi}
-
-This twist-3 asymmetry has played a special role, as it was historically 
-the first single spin asymmetry ever measured in SIDIS 
-\cite{Airapetian:1999tv,Airapetian:2001eg,Airapetian:2002mf,Airapetian:2005jc}.
-See also the recent COMPASS data \cite{Alekseev:2010dm}.
-This asymmetry is sizable despite being twist-3. Although it was subject to 
-numerous phenomenological studies, this asymmetry still remains unexplained.
-
-Retaining the only non-zero term in the WW-type approximation, and
-assuming for $h_L^q(x,\kperp)$ a Gaussian Ansatz 
-\be
-h_L^q(x,\kperp^2) = h_L^q(x) \,\frac{1}{\pi \avkperp_{h_{L}}}\,
-	e^{-\kperp^2/{\avkperp_{h_{L}}}}\;,
-	\label{eq:hLnew}
-\ee
-we obtain
-for the structure function 
-\begin{subequations}\ba
-	F_{UL}^{\sin\phi_h}(x,z,\Phperp) 
-	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\; 
-	b^{(1)}_{\rm A}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
-	{ \cal G}(\Phperp ) \, , \\
-	F_{UL}^{\sin\phi_h}(x,z,\la\Phperp\ra) 
-	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\;  
-	c^{(1)}_{\rm A}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,
-\ea\end{subequations}
-where $\lambda=z^2 \avkperp_{h_L} + \avpperp_{H_1^\perp}$ and
-$b^{(1)}_{\rm A}=2m_h$ and $c^{(1)}_{\rm A} = \sqrt{\pi}\,m_h$,
-see App.~\ref{App:convol-details} for details. We now approximate 
-$\avkperp_{h_L}=\avkperp_{h_1}$ and explore (\ref{Eq:WW-type-6}) to estimate
-\be
-	xh_L^q(x) = -2 h_{1L}^{\perp(1)q}(x)
-\ee
-and finally express $h_{1L}^{\perp(1)q}(x)$ in terms of $h_1^a(x)$
-using (\ref{Eq:WW-approx-h1L}). $h_{1L}^{\perp(1)q}(x)$  is shown in Fig.~\ref{g1t_h1l_functions}.
-
-We compare our calculations to HERMES data \cite{Airapetian:2005jc} 
-in Fig.~\ref{aulsinphi_jlab} (a) and to CLAS data in 
-Fig.~\ref{aulsinphi_jlab} (c).
-The asymmetries $A_{UL}^{\sin\phi_h}=F_{UL}^{\sin\phi_h}/F_{UU}$  as a function 
-of $x$  for COMPASS is plotted in Fig.~\ref{aulsinphi_jlab} (b).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf} (a)
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf} (b)
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} (c)
-\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $ , comparison to HERMES data \cite{Airapetian:2005jc} (a), and predictions for COMPASS (b), and comparison to JLab (c).
-}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \newpage
 \subsection{\boldmath Subleading twist  $A_{LT}^{\cos(2\phi_h - \phi_S)}$}
-\label{Sec-7.5:FLTcos2phi-phiS}
-
-Retaining the only non-zero term in the WW-type approximation, and
-assuming for $g_T^{\perp a}(x,\kperp)$ a Gaussian Ansatz
-\be
-	g^{\perp q}_{T}(x,\kperp^2) = 
-	g^{\perp (2) q}_{T}(x)\,\frac{2 M^4}{\pi \avkperp^3_{g_{T}^{\perp} }}\,
-	e^{-\kperp^2/{\avkperp_{g_{T}^{\perp} }}}\;,
-	\label{eq:gtperpnew}
-\ee
-We estimate $\avkperp_{g_{T}^\perp}=\avkperp_{g_1}$ and explore
-the WW-type approximation (\ref{Eq:WW-type-gTperp}), 
+\label{Sec-7.3:FLTcos2phi-phiS}
+
+In the WW-type approximation this asymmetry is expressed in terms of
+$g_T^{\perp a}(x,\kperp)$ for which we assume a Gaussian Ansatz according to 
+Eq.~(\ref{eq:gtperpnew}) in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs},
+and use the WW-type approximation (\ref{Eq:WW-type-gTperp}) as
 \be
@@
 where we finally express $g_{1T}^{\perp (1)q}(x)$ in terms of $g_1^q(x)$ 
-according to Eq.~(\ref{Eq:WW-approx-g1T}).
-
-We obtain
-for the structure function 
+according to Eq.~(\ref{Eq:WW-approx-g1T}). For the Gaussian widths
+we assume $\avkperp_{g_{T}^\perp}=\avkperp_{g_{1T}^\perp}=\avkperp_{g_1}$.
+This yields for the structure function 
 \begin{subequations}\ba
@@
 
-The asymmetry  $A_{LT}^{\cos(\phi_h -\phi_S)}=F_{LT}^{\cos(\phi_h -\phi_S)}/F_{UU}$ 
-as a function of $x$ and $P_{hT}$ for COMPASS is plotted in 
-Fig.~\ref{altcos2phi_jlab}.
-
-\ \\
-\ps{We should include a comparison to 
-COMPASS data \cite{Kotzinian:2007uv,Parsamyan:2010se}.}
+Our predictions for the asymmetry  
+$A_{LT}^{\cos(2\phi_h -\phi_S)}=F_{LT}^{\cos(2\phi_h -\phi_S)}/F_{UU}$ as function 
+of $x$ are displayed in the right panel of Fig.~\ref{g1t_jlab} in
+comparison to preliminary COMPASS data from Ref.~\cite{Parsamyan:2015dfa}. 
+The asymmetry is very small, so we show our predictions on a larger
+scale in Fig.~\ref{altcos2phi_jlab}. At the current stage one may
+conclude that the WW-type approximation for the asymmetry 
+$A_{LT}^{\cos(2\phi_h -\phi_S)}$ is compatible with available data. In view 
+of the smallness of the effect, cf.\  Fig.~\ref{altcos2phi_jlab}, 
+it might be difficult to obtain more quantitative insights
+in near future.
 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/ALTcos2PhiminusPhiS_COMPASS_x.pdf} 
-\caption{\label{altcos2phi_jlab} $A_{LT}^{\cos(2\phi_h - \phi_S)}$  as a function of $ x $ for COMPASS.
-}
+\caption{\label{altcos2phi_jlab} $A_{LT}^{\cos(2\phi_h - \phi_S)}$ 
+	as a function of $ x $ from a proton target for the COMPASS
+	kinematics (enlarged detail of right panel Fig.~\ref{g1t_jlab} 
+	where also the preliminary COMPASS data \cite{Parsamyan:2015dfa}
+	are shown). The smallness
+	of this asymmetry has two natural reasons. First, being twist-3
+	it is $M_N/Q$ suppressed. Second, it is proportional to
+	$P_{hT}^2$ with $P_{hT}\ll Q$ in TMD approach.}
 \end{figure}
@@
 \newpage
+
+\subsection{\boldmath   Subleading twist  $A_{LL}^{\cos\phi_h}$}
+\label{Sec-7.3:FLLcosphi}
+
+In WW-type approximation the only contribution to $F_{LL}^{\cos\phi_h}$
+is due to $g_{L}^{\perp q}(x,k_\perp)$ which we assume to be have a
+Gaussian $k_\perp$--behavior according to Eq.~(\ref{eq:gLperp})
+in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, where assume
+for the Gaussian width $\avkperp_{g_{L}^\perp}=\avkperp_{g_1}$. 
+The structure function $F_{UL}^{\cos\phi_h}$ reads
+\begin{subequations}\ba
+	F_{LL}^{\cos \phi_h}(x,z,\Phperp)
+	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
+	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
+	{ \cal G}(\Phperp ) \, , \\ 
+	F_{LL}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
+	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\;
+	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\, , 
+\ea\end{subequations}
+where $\lambda=z^2 \avkperp_{g_{L}^\perp} + \avpperp_{D_1}$, $b^{(1)}_{\rm B}=2M_N$, 
+$c^{(1)}_{\rm B} = \sqrt{\pi}\,M_N$, see App.~\ref{App:convol-details}. Finally 
+we explore the WW-type approximation (\ref{Eq:WW-type-gLperp}) to relate 
+$x\,g_L^{\perp(1) a}(x) = \frac{\la \kperp^2\ra_{g_1}}{2\,M_N^2}\,g_1^a(x)$.
+
+The asymmetry $A_{LL}^{\cos \phi_h}=F_{LL}^{\cos \phi_h}/F_{UU}$ predicted by the
+WW-type approximation in this case is small and compatible with presently 
+available data, see Fig.~\ref{allcosphi_jlab}.
+
+\
+
+\
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.8\textwidth]{\FigPath/Fig-COMPASS-A_LL_Pr0711_Zgt02.pdf}
+	\caption{\label{allcosphi_jlab} $A_{LL}^{\cos(\phi_h)}$  
+	as a function of $ x $ from a proton target for the COMPASS
+	kinematics. The theoretical curves obtained from the WW-type 
+	approximation are compared to the preliminary COMPASS data 
+	\cite{Parsamyan:2015dfa}. }
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%
+
+\newpage
+\subsection{\boldmath Subleading twist $A_{UL}^{\sin\phi_h}$ }
+\label{Sec-7.4:FULsinphi}
+
+In the WW-type approximation the asymmetry is described by 
+$h_L^q(x,\kperp)$ for which we assume the Gaussian Ansatz 
+(\ref{eq:hLnew}) in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}
+with $\avkperp_{h_L}=\avkperp_{h_1}$. We explore (\ref{Eq:WW-type-6}) 
+to estimate $xh_L^q(x) = -2 h_{1L}^{\perp(1)q}(x)$ and express
+$h_{1L}^{\perp(1)q}(x)$ through $h_1^a(x)$ according to 
+(\ref{Eq:WW-approx-h1L}). 
+This yield for the structure function the result
+\begin{subequations}\ba
+	F_{UL}^{\sin\phi_h}(x,z,\Phperp) 
+	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\; 
+	b^{(1)}_{\rm A}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
+	{ \cal G}(\Phperp ) \, , \\
+	F_{UL}^{\sin\phi_h}(x,z,\la\Phperp\ra) 
+	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\;  
+	c^{(1)}_{\rm A}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,
+\ea\end{subequations}
+where $\lambda=z^2 \avkperp_{h_L} + \avpperp_{H_1^\perp}$ and
+$b^{(1)}_{\rm A}=2m_h$ and $c^{(1)}_{\rm A} = \sqrt{\pi}\,m_h$,
+see App.~\ref{App:convol-details} for details.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b]
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} 
+\includegraphics[width=0.8\textwidth]{\FigPath/Fig-COMPASS-A_UL1_Pr0711_Zgt02.pdf}
+\caption{\label{aulsinphi_jlab} The asymmetry $A_{UL}^{\sin\phi_h}$ 
+	as function of $x$ from WW-type approximation in comparison to: 
+	(upper panel left) HERMES \cite{Airapetian:2005jc},
+	(upper panel right) JLab \cite{Jawalkar:2017ube}, and 
+	(lower panel) preliminary COMPASS \cite{Parsamyan:2015dfa} data.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The asymmetries $A_{UL}^{\sin\phi_h}=F_{UL}^{\sin\phi_h}/F_{UU}$ are compared
+to HERMES, JLab, and preliminary COMPASS data in Fig.~\ref{aulsinphi_jlab}.
+The WW-type approximation reproduces the positive sign of the asymmetry
+seen consistently at HERMES and COMPASS for $\pi^+$ and positive hadrons
+but underestimates its magnitude. The results for negative pions and 
+hadrons at HERMES and COMPASS are compatible. An important test for this
+asymmetry is provided by neutral pions where in WW-type approximation
+the contributions for Collins fragmentation function largely cancel.
+The WW-type approximation is not able to explain the large effect
+observed at JLab for $\pi^0$ in the large--$x$ region $0.2< x < 0.4$
+in Fig.~\ref{aulsinphi_jlab}.
+
+\newpage
+
 \subsection{\boldmath Subleading twist  $A_{UT}^{\sin\phi_S}$}
@@
 
-In the structure function $F_{UT}^{\sin\phi_S}$ we encounter 3 interesting 
-new features. This is the first case with more than 1 contribution after 
-applying the WW-type approximation. Assuming Gaussian Ans\"atze for the TMDs
-$f_T^q(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
-\begin{subequations}
-\be
-f_T^q(x,\kperp^2) = f_T^q(x) \,\frac{1}{\pi \avkperp_{f_{T}}}\,
-	e^{-\kperp^2/{\avkperp_{f_{T}}}}\;,
-	\label{eq:fTnew}
-\ee
-\be
-h_T^{\perp q}(x,\kperp^2) =h_T^{\perp (1) q}(x) \,\frac{2 M^2}{\pi \avkperp_{h_{T}^\perp}^2}\,
-	e^{-\kperp^2/{\avkperp_{h_{T}^\perp}}}\;,
-	\label{eq:hTperpnew}
-\ee
-\be
-h_T^{q}(x,\kperp^2) =h_T^{(1) q}(x) \,\frac{2 M^2}{\pi \avkperp_{h_{T}}^2}\,
-	e^{-\kperp^2/{\avkperp_{h_{T}}}}\;,
-	\label{eq:hTnew}
-\ee
-\end{subequations}
-we obtain 
+In the structure function $F_{UT}^{\sin\phi_S}$ several interesting features
+occur not encontered before. Let us summarize the result and follow up 
+with some comments.
+Assuming Gaussian Ans\"atze (\ref{eq:hTperpnew},~\ref{eq:hTnew}) 
+for the TMDs $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
+in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, we obtain 
 \begin{subequations}\begin{alignat}{1}
 	F_{UT}^{\sin\phi_S}(x,z,\Phperp) 
-	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
-	  x\,f_T^q(x)
-	\, D_1(z) \, { \cal G}(\Phperp)  \label{Eq:FUTsinphiS-Gauss-I-PhT}\\
-	&- {\textstyle\frac12}\,x\,\left(h_T^{(1)q}(x)-h_T^{\perp(1)q}(x)\right)
-	\,H_1^{\perp(1)q}(z)\; \frac{4z^2 m_h\,M_N}{\lambda} 
-	\left(1-\frac{\Phperp^2}{\lambda}\right) {\cal G}(\Phperp) \Biggr] 
-  	\nonumber\\
+	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\,
+	h_1^{(1)q}(x)\,H_1^{\perp(1)q}(z)\; \frac{4z^2 m_h\,M_N}{\lambda} 
+	\left(1-\frac{\Phperp^2}{\lambda}\right) {\cal G}(\Phperp) 
+	\label{Eq:FUTsinphiS-final-PhT}\\
   	F_{UT}^{\sin\phi_S}(x,z) 
-	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\, x\,f_T^q(x)\, D_1(z) 
-	\label{Eq:FUTsinphiS-I-naive}\
+	&= 0 \, .	\label{Eq:FUTsinphiS-final}
 \end{alignat}\end{subequations}
-with  respectively
-$\lambda=z^2\la\kperp^2\ra_{f_T}+\la\pperp^2\ra_{D_1}$ in the first, and  
-$\lambda=z^2\la\kperp^2\ra_{h_T^\perp}+\la\pperp^2\ra_{H_1^\perp}$ in the 
-second term of Eq.~(\ref{Eq:FUTsinphiS-Gauss-I-PhT}) where we 
-assumed $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}$.
-
-The second interesting feature not encountered before is that a contribution
+with $\lambda=z^2\la\kperp^2\ra_{h_T^\perp}+\la\pperp^2\ra_{H_1^\perp}$ and
+$\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_1^{ }}$. 
+We can then use (\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}) to relate 
+in the WW-type approximation 
+$-\,\frac12\,x (h_T^{(1)q}(x) - h_T^{\perp(1)q}(x))
+= h_1^{(1)q}(x) = \frac{\la\kperp^2\ra_{h_1}}{2M_N^2}\,h_1^q(x)$.
+
+Some comments are in order. The first interesting feature 
+is that after applying the WW-type approximation more than 
+a single term is left.  Out of the 6 terms contributing to this 
+structure function in (\ref{FUTsinphiS}) after WW-type approximation 
+initially the 3 terms shown in Eq.~(\ref{Eq:WW-type-FUTsinphiS}) 
+remain one of which is proportional to the TMD $f_T^q(x,\kperp)$.
+
+The second interesting feature not encountered before is 
+associated with $f_T^q(x,\kperp)$. This T-odd TMD must 
+satisfy the sum rule (\ref{Eq:sum-rules-T-odd}), see the
+discussion in Sec.~\ref{Sec-3.8:limitations}. This could be
+implemented in two ways: one could describe it with a superposition 
+of Gaussians, see App.~\ref{App-B:comment-Todd-twist-3}.
+At this point, however, we have no guidance from phenomenology or theory 
+to fix additional parameters. Alternatively one could choose a pragmatic 
+and simple solution, namely to neglect the contribution of the TMD
+$f_T^q(x,\kperp)$.\footnote{\label{Footnote:fT-single-Gauss} Notice 
+	that this would correspond to using a ``single Gaussian'' as 
+	$f_T^q(x,\kperp) = f_T^q(x)\;
+	\frac{\exp(-\kperp^2/\la\kperp^2\ra_{f_T}^{ })}
+	{\pi\la\kperp^2\ra_{f_T}^{ }}$
+	with the ``coeffiecient'' $f_T^q(x)=0$ as dictated 
+	by the sum rule (\ref{Eq:sum-rules-T-odd}).}
+The result shown in Eq.~(\ref{Eq:FUTsinphiS-final-PhT})
+is obtained using this second ``pragmatic'' solution.
+
+Interestingly, for the $x$-- and $z$--dependence of the
+structure function $F_{UT}^{\sin\phi_S}(x,z)$ it plays no role
+(footnote~\ref{Footnote:fT-single-Gauss} 
+vs App.~\ref{App-B:comment-Todd-twist-3}) how we model $f_T^q(x,\kperp)$: 
+the result is Eq.~(\ref{Eq:FUTsinphiS-final}) in either case due to the 
+requirement of the sum rule (\ref{Eq:sum-rules-T-odd}).
+Notice that most of the time we focus on the $x$--dependence of 
+asymmetries since this allows us to more directly test the WW-type 
+approximations for TMDs, as opposed to e.g.\ the $P_{hT}$--dependence 
+where in addition we would test at the same time also the Gaussian Ansatz.
+
+The third interesting feature not seen in
+previous sections is the occurence of a term which
 drops out upon integrating the structure function over $\Phperp$, cf.\ 
-Eq.~(\ref{Eq:FUTsinphiS-Gauss-I-PhT}) vs.\ (\ref{Eq:FUTsinphiS-I-naive}).
+Eq.~(\ref{Eq:FUTsinphiS-final-PhT}) vs.\ (\ref{Eq:FUTsinphiS-final}).
 This is a property of the weight $\omega^{\{2\}}_{\rm B}$ 
@@
 
-Exploring the WW-type approximations (\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}) 
-the chiral--odd twist-3 TMDs can be unambiguously related to transversity
-\begin{subequations}\be
-   	-\,{\textstyle\frac12}\,x \left(h_T^{(1)q}(x) - h_T^{\perp(1)q}(x)\right)
-	= h_1^{(1)q}(x) = \frac{\la\kperp^2\ra_{h_1}}{2M_N^2}\,h_1^q(x)\, .
-\ee
-Now we encounter the third interesting feature, namely the treatment 
-of $f_T^q(x)$ is not unambiguous. We could explore the sum rule 
-(\ref{Eq:sum-rules-T-odd}) or employ the WW-type approximation 
-(\ref{Eq:WW-type-fT}) to obtain 
-\be
-   	x \, f_T^q(x) 
-	\stackrel{!?}{=} \begin{cases} 
-	\phantom{-}\, 0 	
-	& \mbox{due to sum rule (\ref{Eq:sum-rules-T-odd}),} \cr
-	- \, f_{1T}^{\perp (1)q}(x) 
-		& \mbox{due to WW-type (\ref{Eq:WW-type-fT}),} 
-		\end{cases}\label{WW-type-fTperp-discuss-II}
-		\;\;\;\;\;\;\;\;\;\;\;\;\;\;\;
-\ee\end{subequations}
-We recall that the twist-3 TMD $f_T^q(x,\kperp) \neq 0$ in general, 
-but the collinear T-odd PDF $f_T^q(x) = 0$ due to time reversal, 
-Eq.~(\ref{Eq:sum-rules-T-odd}). This was discussed in 
-Sec.~\ref{Sec-3.8:limitations}.
-
-Notice that in Eq.~(\ref{Eq:FUTsinphiS-Gauss-I-PhT}) we really have a 
-choice, because we strictly speaking deal with the convoluted non-zero 
-TMD $f_T^q(x,\kperp)$, and the Gaussian model only {\it artificially} 
-introduces the collinear function $f_T^q(x)$ expected to be zero.
-However, in Eq.~(\ref{Eq:FUTsinphiS-I-naive}) we have no choice.
-Here we really deal with the collinear function $f_T^q(x)$ which
-must vanish due to the sum rule (\ref{Eq:sum-rules-T-odd}).
-How should one proceed?
-
-If we wish to respect the sum rule (\ref{Eq:sum-rules-T-odd}), 
-we have to describe $f_T^q(x,\kperp)$ by a function with a node 
-in $\kperp$. A simple Gaussian is not adequate for that. But from
-phenomenological point of view, one of course could work with a 
-superposition of Gaussians\footnote{
-	The possibility of TMDs with nodes is not unrealistic.
-	For instance in the covariant parton model the helicity TMDs 
-	exhibit nodes for the $u$ and $d$- flavor \cite{Efremov:2010mt}.
-	We will have to revise our description of $g_1^q(x,\kperp)$ 
-	in Eq.~(\ref{Eq:Gauss-g1}) and App.~\ref{App:basis-g1} to something 
-	of the type (\ref{Eq:multiple-Gauss}), if this prediction is 
-	confirmed experimentally. }
-with different widths, 
-\begin{alignat}{1}
-	x \, f_T^q(x,\kperp) =  - \, f_{1T}^{\perp (1)q}(x)\;
-	&\sum\limits_{i=1}^{n} a_i\;
-	\frac{\exp(-\kperp^2/\la\kperp^2\ra_i^{ }}{\pi\la\kperp^2\ra_i^{ }}\,,
-	\nonumber\\
-	&\sum\limits_{i=1}^n a_i = 0\,, \;\;
-	\la\kperp^2\ra_i^{ }\neq\la\kperp^2\ra_j^{ }\;\;\forall\;i\neq j,
-	\; 1\le i,\,j\le n,\;n\ge 2.\label{Eq:multiple-Gauss}
-\end{alignat}
-The minimal choice would be $n=2$ with $a_1=-a_2=1$ and
-$\la\kperp^2\ra_1^{ } = \la\kperp^2\ra_{f_1^\perp}$ to make maximal use 
-of the theoretical guidance provided by the WW-type approximation 
-(\ref{Eq:WW-type-fT}). 
-The second Gaussian width $\la\kperp^2\ra_2^{ }$ could then be chosen
-very small $\la\kperp^2\ra_2^{ } \ll \la\kperp^2\ra_{f_1^\perp}$.
-Within such a Gaussian description we would have a transverse momentum 
-dependence of $f_T^{q}(x,\kperp^2)$ similar to that of 
-$f_{1T}^{\perp(1)q}(x,\kperp^2)$ at not too small $\kperp$. 
-A very small parameter $\la\kperp^2\ra_2^{ }$ could be thought of as 
-a relict, e.g.\ of gluonic pole contributions in the $\bar qgq$-term 
-$\tilde{f}_T^q(x,\kperp)$. It will be very interesting to follow up
-on this in future studies.
-
-At this point, however, we have no guidance from phenomenology or theory 
-to fix additional parameters and choose a pragmatic and simple solution, 
-namely to implement the sum rule (\ref{Eq:sum-rules-T-odd}) also in 
-Eq.~(\ref{Eq:FUTsinphiS-Gauss-I-PhT}). This is
-a model-dependent choice and this step could be revised along the
-lines of the above discussion. Our final result is therefore
-\begin{alignat}{1}
-	F_{UT}^{\sin\phi_S}(x,z,\Phperp) 
-	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\,
-	h_1^{(1)q}(x)\,H_1^{\perp(1)q}(z)\; \frac{4z^2 m_h\,M_N}{\lambda} 
-	\left(1-\frac{\Phperp^2}{\lambda}\right) {\cal G}(\Phperp) 
-	\nonumber\\
-  	F_{UT}^{\sin\phi_S}(x,z) 
-	&= 0 \, .	\label{Eq:FUTsinphiS-final}
-\end{alignat}
-In (\ref{Eq:FUTsinphiS-final}) we recover the consistent result for 
-the ``collinear'' (i.e.\ related to the weight $\omega^{\{0\}}$) SIDIS 
-structure function $F_{UT}^{\sin\phi_S}(x,z)$ in WW-type approximation, 
-see Eq.~(\ref{Eq:FUT-collinear}).
-
-The asymmetries $A_{UT}^{\sin\phi_S}=F_{UT}^{\sin\phi_S}/F_{UU}$  for 
-COMPASS are plotted in Fig.~\ref{autsinphi_jlab}.
-\ps{Compare to HERMES data \cite{Schnell:2010zza}?
-Is there by now final data? Will be interesting!}
+The final result in Eq.~(\ref{Eq:FUTsinphiS-final}) is the
+consistent result for the structure function $F_{UT}^{\sin\phi_S}(x,z)$ in 
+WW-type approximation, see Eq.~(\ref{Eq:FUT-collinear}). Our prediction 
+is therefore $A_{UT}^{\sin\phi_S}(x)=F_{UT}^{\sin\phi_S}(x)/F_{UU}(x)=0$.
+This is compatible with preliminary data from HERMES \cite{Schnell:2010zza}
+and COMPASS \cite{Parsamyan:2015dfa} over a wide range of $x$, see 
+Fig.~\ref{autsinphi_jlab} below. Merely for negative hadrons at 
+large-$x$ there might be a disagreement with our prediction.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[ht]
+\begin{figure}[b]
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphiS_COMPASS_x.pdf} 
-\caption{\label{autsinphi_jlab} $A_{UT}^{\sin\phi_S}$  as a function of $ x $ for COMPASS.
-}
+\includegraphics[width=0.8\textwidth]{\FigPath/Fig-COMPASS-A_UT_Pr10.pdf}
+
+\vspace{-5mm}
+
+\caption{\label{autsinphi_jlab} 
+	Preliminary data for azimuthal transverse target single--spin 
+	asymmetries as functions of $x$ from the COMPASS experiment 
+	\cite{Parsamyan:2015dfa}.
+	Left panel: 
+	leading--twist $A_{UT}^{\sin(3\phi_h-\phi_S)}(x)$ which 
+	determines the pretzelosity TMD, one of our basis functions. 
+	This asymmetry was discussed in Sec.~\ref{Sec-5.6:pretzel-basis} 
+	and is included here for completeness. 
+	Middle panel: 
+	subleading--twist $A_{UT}^{\sin\phi_S}(x)$ which is predicted to vanish
+	in the WW-type approximation, see Sec.~\ref{Sec-7.6:FUTsinphiS}.
+	Right panel: 
+	leading--twist $A_{UT}^{\sin(2\phi_h-\phi_S)}(x)$.}
 \end{figure}
@@
 
-\newpage
-\subsection{\boldmath Subleading twist  $A_{UU}^{\cos\phi_h}$ }
-\label{Sec-7.7:FUUcosphi}
-
-Historically this was the first predicted \cite{Cahn:1978se} and measured
-\cite{Aubert:1983cz} azimuthal asymmetry in (unpolarized) SIDIS, and
-later explored in \cite{Anselmino:2005nn} to extract information on the 
-Gaussian widths of $f_1^q(x,\kperp)$ and $D_1^q(x,\pperp)$ (under the 
-implicit assumption of WW-type approximations).
-
-The structure function $F_{UU}^{\cos\phi_h}$, Eq.~(\ref{Eq:FUUcosphi}),
-contains after the WW-type approximation two contributions. Assuming
-Gaussian Ans\"atze for $h^{q}(x,\kperp)$ and $f^\perp(x,\pperp)$ 
-\begin{subequations}
-\be
-h^q(x,\kperp^2) = h^q(x) \,\frac{1}{\pi \avkperp_{h}}\,
-	e^{-\kperp^2/{\avkperp_{h}}}\;,
-	\label{eq:hnew}
-\ee
-\be
-f^{\perp q}(x,\kperp^2) =f^{\perp (1) q}(x) \,\frac{2 M^2}{\pi \avkperp_{f^\perp}^2}\,
-	e^{-\kperp^2/{\avkperp_{f^\perp}}}\;,
-	\label{eq:fperpnew}
-\ee
-\end{subequations}
-we obtain
-\begin{subequations}\begin{alignat}{1}
-	F_{UU}^{\cos\phi_h}(x,z,\Phperp) 
-	= \frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
-	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;b^{(1)}_{\rm A}\,
-	  \biggl(\frac{z \Phperp} {\lambda}\biggr)\, & { \cal G}(\Phperp)
-	  \nonumber\\
-	- x\,f^{\perp(1)q}(x)\,D_1^q(z)\;b^{(1)}_{\rm B}\,
-	  \biggl(\frac{z \Phperp} {\lambda}\biggr)\, & { \cal G}(\Phperp ) 
-	\Biggr] \label{Eq:XXXa}\\
-	F_{UU}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
-	= \frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
-	  x\,h^{q}(x)\,H_1^{\perp(1)q}(z)\;c^{(1)}_{\rm A}\;
-	  \biggl(\frac{z}{\lambda^{1/2}}\biggr)&
-	  \nonumber\\
-	-x\,f^{\perp(1)q}(x)\,D_1^q(z)\;c^{(1)}_{\rm B}\;
-	  \biggl(\frac{z}{\lambda^{1/2}}\biggr)&
-	\Biggr] \label{Eq:XXXb}
-\end{alignat}\end{subequations}
-with $\lambda=z^2\la\kperp^2\ra_{h}+\la\pperp^2\ra_{H_1^\perp}$ in the first, 
-and  $\lambda=z^2\la\kperp^2\ra_{f^\perp}+\la\pperp^2\ra_{D_1}$ in the second 
-term respectively in (\ref{Eq:XXXa}) and (\ref{Eq:XXXb}). The coefficients 
-$b^{(1)}_i$ and $c^{(1)}_i$ are defined in App.~\ref{App:convol-details}.
-
-The application of the WW-type approximation (\ref{Eq:WW-type-last}) 
-for $h^q(x)$ is subtle. Applying it literally would imply 
-$x\,h^q(x) = - 2\,h_1^{\perp(1)}(x)$ at variance with the sum rule
-(\ref{Eq:sum-rules-T-odd}) for the collinear T-odd twist-3 TMD $h^q(x)$.
-The situation is analog to the case of $f_T^q(x,\kperp)$
-discussed in Sec.~\ref{Sec-7.6:FUTsinphiS}. Also here one could introduce
-an additional Gaussian parameter and use a double Gaussian to describe 
-$h^q(x,\kperp)$. One should keep this in mind as an interesting possibility
-to be explored in future studies. However, at this point we have no guidance
-from theory or phenomenology to fix additional parameters. We therefore
-proceed analogously to Sec.~\ref{Sec-7.7:FUUcosphi}, and impose 
-(in a model-dependent step) the sum rule (\ref{Eq:sum-rules-T-odd}) 
-by setting 
-\begin{subequations}\be
-	x\,h^q(x) = 0\,.
-\ee
-
-For $f^{\perp(1)}(x)$ we explore Eq.~(\ref{Eq:WW-type-Cahn}) as
-\be
-	x\,f^{\perp(1)}(x) = \frac{\la\kperp^2\ra_{f_1}}{2M_N^2}\,f_{1}^q(x)
-	\, , 
-\ee\end{subequations}
-and estimate its Gaussian width as $\la\kperp^2\ra_{f^\perp}=\la\kperp^2\ra_{f_1}$.
-The latter means the Gaussian factors of 
-$F_{UU}^{\cos\phi_h}$ and $F_{UU}$ cancel out, i.e.\ at some point 
-for $\Phperp\gtrsim1\,$GeV we would obtain from (\ref{Eq:XXXa}) 
-an asymmetry $A_{UU}^{\cos\phi_h}=F_{UU}^{\cos\phi_h}/F_{UU}$ exceeding
-100$\,\%$ and violating unitarity. This is of course an artifact of our 
-approximations, and reminds us that the WW-type approximations as well
-as the entire TMD formalism must be applied to small $\Phperp\ll Q$,
-and in the case of $A_{UU}^{\cos\phi_h}$ preferably for $\Phperp < 1\,$GeV,
-as shown in Fig.~\ref{auucosphi_jlab}. \\
-\ps{(Alexei: did you notice it \cite{Anselmino:2005nn}? How did you treat it? AP we did notice and did nothing.)}
-
-The asymmetries $A_{UU}^{\cos\phi_h}$  for 
-Jefferson Lab 12 GeV are plotted in Fig.~\ref{auucosphi_jlab}.
-\ps{We should compare to EMC, or 
-	JLab \cite{Osipenko:2008aa,Mkrtchyan:2007sr}, 
-	HERMES and COMPASS \cite{Giordano:2009hi,Joosten:2009zz}.
-	There is probably also newer data!}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_PT.pdf} 
-\caption{\label{auucosphi_jlab} $A_{UU}^{\cos\phi_h}$  for COMPASS.
-}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%------ BEGIN FIGURE 4: Phperp(z) AND Phperp^2(z) at HERMES ----------
-        \begin{figure}[b!]
-        \vspace{-0.6cm}
-        \includegraphics[height=8cm]{\FigPath/Fig06-EMC-cosphi-z.pdf}
-        \vspace{-0.5cm}
-        \caption{\label{Fig-02:EMC}
-        Azimuthal asymmetry $A_{UU}^{\cos\phi}$ in charged hadron 
-        production in SIDIS of $280\,{\rm GeV}$ muons off protons
-        as function of $z$. The data from EMC \cite{Aubert:1983cz}
-        refer to $\la Q\ra=4.8\,{\rm GeV}$. The theoretical
-        curve is the ``WW-type and Cahn-effect-only'' approximation 
-        for this observable in the Gaussian model with parameters 
-        fixed from HERMES data and neglecting evolution effects. 
-	From Ref.~\cite{Schweitzer:2010tt}.}
-        \end{figure}
-%------ END FIGURE 4 -------------------------------------------------
-
-\
-
-\ \\
-\ps{We may potentially run into positivity issues also for other observables. 
-However, I would suggest not to worry too much. We see in the pictures that 
-the respective asymmetries are smaller than 100$\,\%$ for reasonably small 
-$\Phperp$ and can be happy with that! But perhaps we should include a 
-comment somewhere?}
-
-\newpage
 \subsection{\boldmath Subleading twist  $A_{UT}^{\sin(2\phi_h-\phi_S)}$ }
@@
 
-In this last asymmetry we encounter the first case with more than one 
-surviving contribution in our treatment. Assuming Gaussian Ans\"atze for 
-$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$ Eq.~(\ref{eq:hTperpnew}), 
-$h_T^q(x,\kperp)$ Eq.~(\ref{eq:hTnew}),
-\be
-	f^{\perp q}_{T}(x,\kperp^2) = 
-	f^{\perp (2) q}_{T}(x)\,\frac{2 M^4}{\pi \avkperp^3_{f_{T}^{\perp} }}\,
-	e^{-\kperp^2/{\avkperp_{f_{T}^{\perp} }}}\;,
-	\label{eq:ftperpnew}
-\ee
-we find
+Also in this asymmetry we end up more than one surviving 
+contribution in our treatment. We assume Gaussian Ans\"atze for 
+$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
+according to Eqs.~(\ref{eq:hTperpnew},~\ref{eq:hTnew},~\ref{eq:ftperpnew}) 
+in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} with
+$\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_{1T}^\perp}$
+and $\la\kperp^2\ra_{f_T^\perp}=\la\kperp^2\ra_{f_{1T}^\perp}$ and obtain
 \begin{subequations}\begin{alignat}{1}
-	F_{UT}^{\sin(2\phi_h -\phi_S)}(x,z,\Phperp) \; \; 
-	= \; \; \; \;
+	F_{UT}^{\sin(2\phi_h -\phi_S)}(x,z,\Phperp) \; 
+	=
 	\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
-	x \; f_T^{\perp(2)q}(x) \; D_1(z) \;b^{(2)}_{\rm C}\;
-	&\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\;{ \cal G}(\Phperp) 
+	x \, f_T^{\perp(2)q}(x) \; D_1(z) \;b^{(2)}_{\rm C}\;
+	\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\,{ \cal G}(\Phperp)&
 	\nonumber\\
 	+ \;
-	x\left(h_T^{(1)q}(x)+h_T^{\perp(1)q}(x)\right)H_1^{\perp(1)q}(z)\,
-	\frac{b^{(2)}_{\rm AB}}{2}
-	&\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\;{\cal G}(\Phperp)\Biggr] 
+	\frac{x}{2}\left(h_T^{(1)q}(x)+h_T^{\perp(1)q}(x)\right)H_1^{\perp(1)q}(z)\,
+	b^{(2)}_{\rm AB}
+	\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\,{\cal G}(\Phperp)&\Biggr]
 	\label{Eq:FUTsin2phi-phiS-Gauss-PhT}\\
 { }
-	F_{UT}^{\sin(2\phi_h -\phi_S)}(x,z,\Phperp) \; \; 
-	= \; \; \; \;
+	F_{UT}^{\sin(2\phi_h -\phi_S)}(x,z,\la\Phperp\ra) \; 
+	= \; 
 	\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
 	x \; f_T^{\perp(2)q}(x) \; D_1(z) \; c^{(2)}_{\rm C} \;
-	&\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2}
+	\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2} &
 	\nonumber\\
 	+ \;
-	x\left(h_T^{(1)q}(x)+h_T^{\perp(1)q}(x)\right)H_1^{\perp(1)q}(z)\,
-	\frac{c^{(2)}_{\rm AB}}{2}
-	&\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2}\Biggr] 
+	\frac{x}{2}\left(h_T^{(1)q}(x)+h_T^{\perp(1)q}(x)\right)H_1^{\perp(1)q}(z)\,
+	c^{(2)}_{\rm AB}
+	\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2} & \Biggr] 
 	\label{Eq:FUTsin2phi-phiS-Gauss}
@@
 Eqs.~(\ref{Eq:FUTsin2phi-phiS-Gauss-PhT},~\ref{Eq:FUTsin2phi-phiS-Gauss}).
-We use $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T}$. The coefficients 
+The coefficients 
 $b^{(2)}_i$ and $c^{(2)}_i$ are defined in App.~\ref{App:convol-details}.
-We now explore the WW-type approximations in
-Eqs.~(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}) to 
-express the twist-3 TMDs in terms of the Sivers function and pretzelosity
-as follows
-\begin{subequations}\ba
-   	x \, f_T^{\perp(2)q}(x) 
-	&=& f_{1T}^{\perp (2)q}(x) 
-	\equiv \frac{\la\kperp^2\ra_{f_{1T}^\perp}}{M_N^2}\,f_{1T}^{\perp (1)q}(x)\,,\\
-   	-\,{\textstyle\frac12}\,x \left(h_T^{(1)q}(x) + h_T^{\perp(1)q}(x)\right)
-	&=& h_{1T}^{\perp(2)q}(x) \, .
-%	\equiv\frac{\la\kperp^2\ra_{f_{1T}^\perp}}{M_N^2}\,f_{1T}^{\perp(1)q}(x)
-\ea\end{subequations}
-%
-%
-% $xh_T^q(x,\kperp^2)        =-h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2)$
-% $xh_T^{\perp q}(x,\kperp^2)= h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2)$
-%
-% $xf_T^{\perp q}(x,\kperp^2) = f_{1T}^{\perp   q}(x,\kperp^2)$
-% $xf_T^{q}      (x,\kperp^2) =-f_{1T}^{\perp(1)q}(x,\kperp^2)$
-%
-% In our approach this is the only asymmetry which receives 2 contributions.
+In the next step we explore the WW-type approximations
+(\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8},~\ref{Eq:WW-type-fTperp}) to 
+relate 
+$x \, f_T^{\perp(2)q}(x) = 
+\frac{\la\kperp^2\ra_{f_{1T}^\perp}}{M_N^2}\,f_{1T}^{\perp (1)q}(x)$ and
+$-\,\frac12\,x \left(h_T^{(1)q}(x) + h_T^{\perp(1)q}(x)\right)
+= h_{1T}^{\perp(2)q}(x)$.
+
 The asymmetries $A_{UT}^{\sin (2 \phi_h-\phi_S)}=F_{UT}^{\sin (2 \phi_h-\phi_S)}/F_{UU}$  
-for Jefferson Lab 12 GeV are plotted in Fig.~\ref{autsin2phi_jlab}.
+are plotted in the right panel of Fig.~\ref{autsinphi_jlab} in comparison 
+to preliminary COMPASS data \cite{Parsamyan:2015dfa}. The predicted
+asymmetry is small and compatible with data which are consistent
+with a zero effect within error bars.
+
+\newpage
+\subsection{\boldmath Subleading twist  $A_{UU}^{\cos\phi_h}$ }
+\label{Sec-7.7:FUUcosphi}
+
+Historically this was the earliest azimuthal SIDIS asymmetry to be
+discussed in literature: the first prediction for this asymmetry from 
+intrinsic $k_\perp$ was made in \cite{Cheng:1972sy,Cahn:1978se}, a 
+first measurement
+was reported in \cite{Aubert:1983cz}.\footnote{First hints 
+	\cite{Dakin:1972db} of azimuthal modulations in SIDIS
+	date back to the early 1970s, i.e., 10 years before 
+	the CERN measurements, but (unfortunately) were 
+	discarded by the authors.}
+This structure function contains after the WW-type approximation initially
+two contributions, proportional to $f^\perp(x,\pperp)$ and $h^{q}(x,\kperp)$. 
+The latter is T-odd and obeys the sum rule (\ref{Eq:sum-rules-T-odd}). 
+We treat $h^{q}(x,\kperp)$ exactly as $f_T^q(x,\kperp)$ in 
+Sec.~\ref{Sec-7.6:FUTsinphiS}.
+Using the Gaussian Ansatz for $f^\perp(x,\kperp)$ in Eq.~(\ref{eq:fperpnew})
+of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} we obtain 
+\begin{subequations}\begin{alignat}{1}
+	F_{UU}^{\cos\phi_h}(x,z,\Phperp) 
+	= \frac{2M}{Q}\;x\sum_q e_q^2 & \Biggl[
+	- x\,f^{\perp(1)q}(x)\,D_1^q(z)\;b^{(1)}_{\rm B}\,
+	  \biggl(\frac{z \Phperp} {\lambda}\biggr)\, { \cal G}(\Phperp ) 
+	\Biggr] \label{Eq:XXXa}\\
+	F_{UU}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
+	= \frac{2M}{Q}\;x\sum_q e_q^2 & \Biggl[
+	-x\,f^{\perp(1)q}(x)\,D_1^q(z)\;c^{(1)}_{\rm B}\;
+	  \biggl(\frac{z}{\lambda^{1/2}}\biggr)
+	\Biggr] \label{Eq:XXXb}
+\end{alignat}\end{subequations}
+with $\lambda=z^2\la\kperp^2\ra_{f^\perp}+\la\pperp^2\ra_{D_1}$. The coefficients
+$b^{(1)}_i$ and $c^{(1)}_i$ are defined in App.~\ref{App:convol-details}.
+Note that Eq.~(\ref{Eq:XXXa}) is valid in the ``scheme'' of 
+footnote~\ref{Footnote:fT-single-Gauss}, but Eq.~(\ref{Eq:XXXa})
+holds independently how one implements the sum rule (\ref{Eq:sum-rules-T-odd})
+(as in footnote~\ref{Footnote:fT-single-Gauss} or 
+App.~\ref{App-B:comment-Todd-twist-3}).
+
+For $f^{\perp(1)}(x)$ we explore Eq.~(\ref{Eq:WW-type-Cahn}) as
+$xf^{\perp(1)q}(x) = \frac{\la\kperp^2\ra_{f_1}}{2M_N^2}\,f_{1}^q(x)$ and 
+estimate its Gaussian width as $\la\kperp^2\ra_{f^\perp}=\la\kperp^2\ra_{f_1}$.
+The latter means the Gaussian factors of 
+$F_{UU}^{\cos\phi_h}$ and $F_{UU}$ cancel out, i.e.\ at some point 
+for $\Phperp\gtrsim1\,$GeV we would obtain from (\ref{Eq:XXXa}) 
+an asymmetry $A_{UU}^{\cos\phi_h}=F_{UU}^{\cos\phi_h}/F_{UU}$ exceeding
+100$\,\%$ and violating unitarity. This is of course an artifact of our 
+approximations, and reminds us that Gaussian and WW-type approximations 
+as well as the entire TMD formalism must be applied to small $\Phperp\ll Q$.
+
+The asymmetries $A_{UU}^{\cos\phi_h}$ were measured in experiments at
+EMC \cite{Aubert:1983cz}, JLab \cite{Osipenko:2008aa,Mkrtchyan:2007sr}, 
+HERMES \cite{Airapetian:2012yg}, and COMPASS \cite{Adolph:2014pwc}.
+In Fig.~\ref{auucosphi_jlab} we compare our predictions 
+to the HERMES and COMPASS data. Clearly, the WW-type
+approximation strongly overestimates the data.
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2PhiminusPhiS_COMPASS_x.pdf} 
-\caption{\label{autsin2phi_jlab} $A_{UT}^{\sin(2\phi_h- \phi_S)}$  for COMPASS
-	\red{(GUNAR: here it says COMPASS, in text JLab)}}
+\includegraphics[width=0.45\textwidth]{\FigPath/Fig-AUUcosphi-COMP.pdf} 
+%\includegraphics[width=0.45\textwidth]{}
+\caption{\label{auucosphi_jlab} 
+	Left panel: asymmetry $A_{UU}^{\cos\phi_h}$ for positive and negative 
+	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}.
+	Right panel: the same for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}
+	\red{(Figure missing! Could not find data. Please, somebody
+	help to find data.)}}
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \newpage
-\section{Conclusions  \judge{0$\,\%$ okay}}
+\section{Conclusions}
 \label{Sec-8:conclusions}
 
-\red{\bf The following is just a collections of text fragments cut out
-from the main text and pasted here in the hope it might be useful.}
-
-\
-
-Regarding inequalities:
-This point has to be cautiously kept in mind. Future determinations 
-of not only of the Boer-Mulders functions but also all other TMDs
-from precision JLab data (and on long run from the EIC) will 
-improve the situation, and allow to test the positivity constraints
-more rigorously. In this way, the TMD leading-twist factorization
-approach will also be validated.
-
-\
-
-% , and show that in this approximation all leading- and
-% subleading--twist structure functions are expressed in terms of
-% a ``basis'' consisting of 6 twist-2 TMDs and 2 twist-2 fragmentation 
-% functions. 
-It is important to remark that the generalized parton model 
-approach of Ref.~\cite{Anselmino:2011ch} provides a description,
-which is largely equivalent to ours.
-
-\
+In this work a comprehensive and complete treatment of SIDIS
+spin and azimuthal asymmetries was presented. The leading--twist
+SIDIS structure functions for the production of unpolarized hadrons,
+which were proven to factorize, are unambiguously expressed in terms 
+of one of 8 twist-2 TMDs convoluted with one of 2 twist-2 FFs.
+For the subleading--twist SIDIS structure functions the situation
+is far more complex for two reasons. First, factorization is not 
+proven and must be assumed. 
+Second, each of the subleading--twist structure functions
+receives 4 or 6 contributions from various TMDs and FFs one of
+which is twist-2 and the other twist-3. Clearly, to make 
+predictions for new experiment or interpret early data, an
+organizing theoretical guideline is needed.
+
+In this work we have explored the so--called WW--type approximation
+as a candidate guideline for the description of SIDIS structure
+functions. This approximation consists of a systematic neglect 
+of $\bar qgq$-terms in the
+correlators defining the TMDs and FFs. We have shown that in such
+an approach all twist-2 and twist-3 structure functions can be
+described in terms of 8 basis functions: 6 TMDs and 2 FFs
+which are each twist-2. All other TMDs and FFs, assuming this
+approximation, are either related to the basis functions or
+vanish. To make this work self-contained
+we reviewed the phenomenological information available
+on the basis functions which is given in terms of 6 SIDIS
+structure functions. (Of course, one cannot extract 8 basis
+functions from 6 observables: in particular 2 basis functions,
+the unpolarized TMD and FF $f_1^q(x,\kperp)$ and $D_1^q(x,\pperp)$,
+are determined from other experiments, most notably Drell-Yan
+and hadron production in $e^+e^-$ annihilations.)
+
+The WW-type approximation for TMDs and FFs is inspired by the
+observation that the classical WW-approximation for the twist-3
+SIDIS structure function $g_2(x)$ (or PDF $g_T^q(x)$) works well. 
+This was predicted in theoretical studies in the instanton model 
+of the QCD vacuum, and confirmed by data and lattice QCD studies.
+The classic WW-approximation for $g_2(x)$ works with a relative
+accuracy of $\pm\,40\,\%$ or better. This is remarkable.
+The instanton vacuum model predicts an analog WW-approximation
+for the chirally odd twist-3 PDF $h_L^q(x)$ to work similarly
+well. This predictions remains to be tested in experiment.
+
+In each case, $g_T^q(x)$ and $h_L^q(x)$, we deal with nucleon
+matrix elements of different $\bar qgq$ correlators, which are 
+assumed to be small. Can one generalize these approximations to
+TMDs? This is a key question, which has been addressed in the
+past in literature in selected cases. This work is the first
+systematic investigation of this question.
+As in the unintegrated correlators one deals with different
+classes of operators, we prefer to speak of the
+WW-type approximation to distinguish from the colinear case.
+
+We have studied in detail all SIDIS structure function in 
+this approximation. This includes a review of results from 
+lattice QCD calculations, effective theories and models.
+We found that from theoretical point of view the WW-type
+approximations receive certain support, though the 
+evidence is less than in the colinear case.
+Most importantly, we have conducted systematic test of
+WW-approximations with available published or 
+preliminary (and soon to be published) SIDIS data
+from HERMES, COMPASS, and JLab.
+
+We found the following results. The two leading--twist 
+structure functions amenable to WW-type approximation 
+	$F_{LT}^{\cos(\phi_h -\phi_S)}$ and 
+	$F_{UL}^{\sin(2\phi_h)}$ 
+are well--described (the former) or at least compatible 
+(the latter) with the data in this approximation. For 
+$F_{UT}^{\sin(2\phi_h)}$ more precise data are needed, 
+but also in this case the trend is encouraging
+especially thanks to the recent COMPASS data.
+We have also shown that our approach satisfies positivity
+inequalities which is a non--trivial consistency check 
+considering the crude approximations (WW-type, Gaussian 
+Ansatz for TMDs) in our approach.
+
+At subleading twist the WW-type approximation for the
+structure functions 
+	$F_{LT}^{\cos\phi_S}$,
+	$F_{LT}^{\cos(2\phi_h-\phi_S)}$,
+	$F_{LL}^{\cos\phi_h}$,
+	$F_{UT}^{\sin\phi_S}$,
+	$F_{UT}^{\sin(2\phi_h-\phi_S)}$
+is compatible with data, too. Some of these asymmetries are
+predicted to be very small in the WW-type approximation,
+sometimes smaller than a fraction or a percent. This is
+compatible with the available data in the sense that the
+data are consistent with zero within their statistical
+accuracies. This cannot be considered a thorough evidence
+for the applicability of the WW-type approximations, but
+on the positive site we also observe no alarming hints
+that the WW-type approximations fail in these cases.
+Merely for $F_{UT}^{\sin\phi_S}$ in the region of large-$x$
+there is an indication that the asymmetry could be 
+non-zero while the WW-type approximation proposes
+a much smaller effect. But more higher-statistic data 
+are needed before we can draw definitive conclusions.
+
+In the case of the three subleading--twist structure functions 
+	$F_{UU}^{\cos(2\phi_h)}$, 
+	$F_{UL}^{\sin\phi_h}$,
+	$F_{LU}^{\sin\phi_h}$
+the situation is clearer and indicates that here the WW-type
+approximations do not work.
+Incidently, these asymmetries include: 	$F_{UU}^{\cos(2\phi_h)}$ which 
+is the very first non--zero azimuthal asymmetry measured in unpolarized SIDIS,
+$F_{UL}^{\sin\phi_h}$ which is the very first non--zero azimuthal target spin 
+asymmetry measured in SIDIS, and $F_{LU}^{\sin\phi_h}$ which is the 
+very first non--zero azimuthal beam spin asymmetry measured in SIDIS.
+The WW-type prediction for $F_{UU}^{\cos(2\phi_h)}$ suggest a large asymmetry
+which overshoots data by a factor of three. In the case of $F_{UL}^{\sin\phi_h}$
+the WW-type approximation undershoots data by a factor of 2 or so.
+Most interestingly, in the case of $F_{LU}^{\sin\phi_h}$ the WW-type
+approximation predicts exactly a zero asymmetry, but in experiment
+a small but clearly non-zero effect is seen.
+
+The non--aplicability of the WW--type approximation in these three
+cases should not be too surprizing. After all it is a crude method
+to model TMDs and FFs and an uncontrollable ``expansion''
+(in nuclear physics the concept of 2--body, 3--body, etc operators
+is well-justified and an effective expansion can be conducted; in
+the case of TMDs however it is less appropriate to speak about a
+systematic expansion in terms of $\bar qq$, $\bar qgq$, etc 
+correlators). It will be very interesting to learn whether e.g.\ 
+in $F_{LU}^{\sin\phi_h}$ or $F_{LU}^{\sin\phi_h}$ a single $\bar qgq$--term 
+is anomalously large, or whether it is a accumulative effect of 
+several small terms $\bar qgq$--terms adding up to the observed asymmetry.
+
+Among all SIDIS structure functions $F_{LU}^{\sin\phi_h}$ emerges as
+a particularly interesing case: this asymmetry is due to $\bar qgq$
+only with no contamination from $\bar qq$ terms.
+So $F_{LU}^{\sin\phi_h}$ offers a unique view on the physics of $\bar qgq$ 
+correlators which is worth--exploring for its own sake.
 
@@
 Second, the results are of use for experiments prepared in the near-term 
-(Jefferson Lab 12) or proposed in the long-term (Electron Ion Collider),
+(JLab 12) or proposed in the long-term (Electron Ion Collider),
 and provide helpful input for Monte Carlo event generators 
@@
 Third, our predictions will help to interpret data.
-The quality of the approximations can only be determined experimentally. 
-It is of importance to establish clear predictions, what we can expect 
-to see in experiments on the basis of the WW approximation.
-If our predictions will be confirmed, it will mean the WW-type approximations
-for TMDs work well and call for theoretical explanations why.
-If our predictions fail, it will mean that certain $\bar{q}gq$-terms are
-sizable and call for theoretical studies to explain why.
-In any case, we are going to learn important lessons
-
-\
-
-In the dedicated study \cite{Accardi:2009au} it was shown that the
-error bars of the present data are compatible with a violation of the 
-WW-approximation for $g_T^a(x)$ up to $40\,\%$ in certain regions of $x$. 
-Rephrased in a more optimistic way, one may interpret the findings of
-\cite{Accardi:2009au} as ``the WW approximation works to an accuracy of
- $40\,\%$ or better,'' and having an approximation with such a quality
-for TMDs would be very valuable. It would help to interpret first
-data, and allow us to make predictions for new experiments 
-(JLab 12, EIC) where unknown TMDs contribute.
-
-The aim of the presented study was to review what can be said about
-the quality of  WW-(type-)approximations on the basis of results
-from theory, models, and phenomenology. In particular, we have
-presented a complete treatment of SIDIS observables in the
-WW-type-approximation. This is what we found out.
-
-Bla, bla, bla.
+
+It is important to remark that the generalized parton model 
+approach of Ref.~\cite{Anselmino:2011ch} provides a description,
+which is largely equivalent to ours. As the quality of the 
+approximations can only be determined experimentally, future
+high--precision data will shed new light and allow us to 
+access new insights abour the quark-gluon structure
+of the nucleon.
 
 \section{Acknowledgments}
-The authors would like to thank their families for the constant support during work on this project. This work was partially supported by the U.S.\
-Department of Energy under Contract No.~DE-AC05-06OR23177 (A.P.) and by the National Science Foundation under Contract No. PHY-1623454 (A.P.).
+The authors would like to thank their families for patience and
+the constant support during work on this project. This work was 
+partially supported by the U.S.\ Department of Energy under 
+Contract No.~DE-AC05-06OR23177 (A.P.) and by the National 
+Science Foundation under Contract No.\ PHY-1623454 (A.P.)
+and Contract No.\ PHY-1406298 (P.S.).
 
@@
 and some recent \cite{Signori:2013mda} analyses employed flavor and 
-$x$- or $z$-independent widths $\avkperp$ and $\avpperp$.
+$x$-- or $z$--independent widths $\avkperp$ and $\avpperp$.
 In the analysis \cite{Anselmino:2013lza} 
@@
 whose range indicates flavor-dependence 
-(first number $u$-flavor,
-second number $d$-flavor). 
+(first number $u$--flavor,
+second number $d$--flavor). 
 Notice that this is the contribution of the flavor averaged
 over contributions from the respective quarks and antiquarks.
-Chiral theories predict significant differences in the $\kperp$-behavior
+Chiral theories predict significant differences in the $\kperp$--behavior
 of sea and valence quarks \cite{Schweitzer:2012hh}.
@@
 	The range of lattice values indicates flavor dependence
-        (first number refers to $u$-flavor, second number to $d$-flavor).}
+        (first number refers to $u$--flavor, second number to $d$--flavor).}
 \end{table}
@@
 
-In lack of phenomenological information on the $k_\perp$-dependence of
+In lack of phenomenological information on the $k_\perp$--dependence of
 $g_1^a(x,k_\perp^2)$ we explore lattice QCD results from \cite{Hagler:2009mb}
@@
 $\langle \kperp^2 \rangle_{g_1} = 0.19$ GeV$^2$.
-In our phenomenological study we use this value for $u$-quarks and for 
-simplicity also for $d$-quarks. Even though the lattice values indicate 
+In our phenomenological study we use this value for $u$--quarks and for 
+simplicity also for $d$--quarks. Even though the lattice values indicate 
 an interesting flavor dependence, see Table~\ref{Table:Gauss-paramaters},
-for a proton target this is a very good approximation due to $u$-quark 
+for a proton target this is a very good approximation due to $u$--quark 
 dominance. When precision data for deuterium and especially for $^3$He
-from Jefferson Lab become available, it will be interesting to 
+from JLab become available, it will be interesting to 
 re-investigate this point in detail.
@@
 where 
-$\la\kperp^2\ra$ could be $x$-dependent,  
-and $\la\pperp^2\ra$ $z$-dependent. 
+$\la\kperp^2\ra$ could be $x$--dependent,  
+and $\la\pperp^2\ra$ $z$--dependent. 
 Both could be flavor-dependent.
@@
 shows that $\pperp$ in $D_1^{q/h}(z,\pperp^2)$ exhibits a Gaussian distribution 
-with weakly $z$-dependent Gaussian width. The distribution of transverse 
+with weakly $z$--dependent Gaussian width. The distribution of transverse 
 momenta in $\left[D^a(z,z^2 k_T^2)\right]_{\mbox{\tiny Ref.\cite{Bacchetta:2006tn}}}$ 
-would require a strongly $z$-dependent Gaussian width. It is a matter of 
+would require a strongly $z$--dependent Gaussian width. It is a matter of 
 taste which one prefers to use.
@@
 \ps{
-
-\subsection{Gaussian Ans\"atze used in this work}
+\newpage
+\subsection{Gaussian Ans\"atze for the derived TMDs used in this work}
 \label{App-B:Gauss-Ansatz-non-basis-TMDs}
@@
 Besides the basis function we also need Ans\"atze for the 
-following 8 TMDs as listed below:
+following TMDs as listed below:
 \begin{subequations}\begin{align}
-	g^{\perp q}_{1T}(x,\kperp^2) 
-	  & =	g^{\perp (1) q}_{1T}(x)\,
+	g_{1T}^{\perp q}(x,\kperp^2) 
+	  &=	g_{1T}^{\perp (1) q}(x)\,
 		\frac{2 M_N^2}{\pi \avkperp_{g_{1T}^\perp}^2}\,
@@
 	h_{1L}^{\perp a}(x,\kperp^2) 
-	  & = 	h_{1L}^{\perp (1) a}(x)\,
-		\frac{2 M_N0^2}{\pi{\avkperp_{h_{1L}^\perp}^2}}\,
+	  &= 	h_{1L}^{\perp (1) a}(x)\,
+		\frac{2 M_N^2}{\pi{\avkperp_{h_{1L}^\perp}^2}}\,
 		e^{-\kperp^2/{\avkperp_{h_{1L}^\perp}^2}}
 	  && 	\mbox{cf.\ Sec.~\ref{Sec-6.2:FULsin2phi},}	
-		\label{eq:h1l_final}
+		\label{eq:h1l_final}\\
+	g^{q}_{T}(x,\kperp^2) 
+	  &=	g^{q}_{T}(x)\,\frac{1}{\pi \avkperp_{g_{T}}}\,
+		e^{-\kperp^2/{\avkperp_{g_{T}}}}\;,
+	  && 	\mbox{cf.\ Sec.~\ref{Sec-7.2:FLTcosphiS},}	
+		\label{eq:gtnew} \\
+	g^{\perp q}_{T}(x,\kperp^2) 
+	  &= 	g^{\perp (2) q}_{T}(x)\,\frac{2 M^4}{\pi \avkperp^3_{g_{T}^{\perp} }}\,
+		e^{-\kperp^2/{\avkperp_{g_{T}^{\perp} }}}\;,
+	  && 	\mbox{cf.\ Sec.~\ref{Sec-7.3:FLTcos2phi-phiS},}	
+		\label{eq:gtperpnew} \\
+	g_{L}^{\perp q}(x,\kperp^2) 
+	  &=	g_{L}^{\perp (1) q}(x)\,
+		\frac{2 M_N^2}{\pi \avkperp_{g_{L}^\perp}^2}\,
+		e^{-\kperp^2/{\avkperp_{g_{L}^\perp}}}  \,, 
+	  && 	\mbox{cf.\ Sec.~\ref{Sec-7.3:FLLcosphi},}
+		\label{eq:gLperp} \\
+	h_L^q(x,\kperp^2) 
+	  &= 	h_L^q(x) \,\frac{1}{\pi \avkperp_{h_{L}}}\,
+		e^{-\kperp^2/{\avkperp_{h_{L}}}}\;,
+	  && 	\mbox{cf.\ Sec.~\ref{Sec-7.4:FULsinphi},}
+		\label{eq:hLnew}\\
+	h_T^{\perp q}(x,\kperp^2) 
+	  &=	h_T^{\perp (1) q}(x)\,\frac{2 M^2}{\pi \avkperp_{h_{T}^\perp}^2}\,
+	  	e^{-\kperp^2/{\avkperp_{h_{T}^\perp}}}\;,
+	  && 	\mbox{cf.\ Sec.~\ref{Sec-7.6:FUTsinphiS},}
+		\label{eq:hTperpnew}\\
+	h_T^{q}(x,\kperp^2) 
+	  &=	h_T^{(1) q}(x) \,\frac{2 M^2}{\pi \avkperp_{h_{T}}^2}\,
+		e^{-\kperp^2/{\avkperp_{h_{T}}}}\;,
+	  && 	\mbox{cf.\ Sec.~\ref{Sec-7.6:FUTsinphiS},}
+		\label{eq:hTnew}\\
+	f^{\perp q}_{T}(x,\kperp^2) 
+	  &= 	f^{\perp (2) q}_{T}(x)\,\frac{2 M^4}{\pi \avkperp^3_{f_{T}^{\perp} }}\,
+		e^{-\kperp^2/{\avkperp_{f_{T}^{\perp} }}}\;,
+	  && 	\mbox{cf.\ Sec.~\ref{Sec-7.8:FUTsin2phi-phiS},}
+		\label{eq:ftperpnew}\\
+	f^{\perp q}(x,\kperp^2) 
+	  &= 	f^{\perp (1) q}(x) \,\frac{2 M^2}{\pi \avkperp_{f^\perp}^2}\,
+		e^{-\kperp^2/{\avkperp_{f^\perp}}}\;,
+	  && 	\mbox{cf.\ Sec.~\ref{Sec-7.7:FUUcosphi},}
+		\label{eq:fperpnew}
 \end{align}\end{subequations}
@@
 
+\subsection{Comment on TMDs subject to the sum rules (\ref{Eq:sum-rules-T-odd})}
+\label{App-B:comment-Todd-twist-3}
+
+In this section we comment on the twist-3 TMDs 
+$f_T^q(x,\kperp)$,  $h^q(x,\kperp)$, $e_L^q(x,\kperp)$,  
+which are T-odd, appear in the decompositions of the correlator with no 
+explicit $k_\perp^j$--prefactors, and would have colinear PDF counterparts. 
+But T-odd PDFs are forbidden by time-reversal and parity invariance of 
+strong interactions, which dictate the sum rules (\ref{Eq:sum-rules-T-odd}), 
+see Sec.~\ref{Sec-3.8:limitations}. 
+Such TMDs could be described by functions with a node in 
+$k_\perp$\footnote{The possibility of TMDs with nodes is not unrealistic.
+	For instance in the covariant parton model the helicity TMDs 
+	exhibit nodes for the $u$-- and $d$--flavor \cite{Efremov:2010mt}.
+	We will have to revise our description of $g_1^q(x,\kperp)$ 
+	in Eq.~(\ref{Eq:Gauss-g1}) and App.~\ref{App:basis-g1} to something 
+	of the type (\ref{Eq:multiple-Gauss}), if that prediction is 
+	confirmed experimentally. }
+such that they can integrate to zero in Eq.~(\ref{Eq:sum-rules-T-odd}).
+A single Gaussian has no node and is not adequate for that.
+However, one could work with a superposition of Gaussians
+with different widths, 
+\begin{alignat}{1}
+	x \, f_T^q(x,\kperp) =  - \, f_{1T}^{\perp (1)q}(x)\;
+	&\sum\limits_{i=1}^{n} a_i\;
+	\frac{\exp(-\kperp^2/\la\kperp^2\ra_i^{ })}{\pi\la\kperp^2\ra_i^{ }}\,,
+	\label{Eq:multiple-Gauss}\\
+	&\sum\limits_{i=1}^n a_i = 0\,, \;\;
+	\la\kperp^2\ra_i^{ }\neq\la\kperp^2\ra_j^{ }\;\;\forall\;i\neq j,
+	\; 1\le i,\,j\le n,\;n\ge 2.\nonumber
+\end{alignat}
+Notice that in (\ref{Eq:multiple-Gauss}) we cannot write ``$f_T^q(x)$'' 
+which would be zero according to (\ref{Eq:sum-rules-T-odd}) and we
+explore here the WW-type approximation (\ref{Eq:WW-type-fT}). 
+The minimal choice would be $n=2$ with $a_1=-a_2=1$ and
+$\la\kperp^2\ra_1^{ } = \la\kperp^2\ra_{f_{1T}^\perp}$ to make use 
+of the theoretical guidance provided by the WW-type approximation 
+(\ref{Eq:WW-type-fT}). 
+The second Gaussian width $\la\kperp^2\ra_2^{ }$ could be chosen
+very large $\la\kperp^2\ra_2^{ } \gg \la\kperp^2\ra_{f_1^\perp}$ to
+model the Gaussian description of $f_T^{q}(x,\kperp)$ similar to 
+that of $f_{1T}^{\perp(1)q}(x,\kperp^2)$ at intermediate $\kperp$.
+A very large parameter $\la\kperp^2\ra_2^{ }$ could be thought of as
+a relict which enters in the sum rule (\ref{Eq:sum-rules-T-odd}) 
+where the $\kperp$--integration formally extends up to infinity 
+where the TMD description does not apply. The theoretical
+understanding of higher--twist TMDs is too limited at
+the present stage, but in principle this could be a 
+pragmatic way of modelling the TMD $f_T^q(x,\kperp)$
+and analogously $h^q(x,\kperp)$, $e_L^q(x,\kperp)$.
+
+{}
+
 }
 
+\newpage
 \subsection{Convolution integrals in Gaussian Ansatz}
@@
 \end{document}
-
-\subsubsection*{Old review-type text from $A_{UU}^{\cos\phi}$, 
-to be saved partially?}
-
-The asymmetry $A_{UU}^{\cos\phi}$ was measured in several experiments,
-such as EMC \cite{Aubert:1983cz}, and more recently also at JLab 
-\cite{Osipenko:2008aa,Mkrtchyan:2007sr}, HERMES \cite{Giordano:2009hi} 
-and COMPASS \cite{Joosten:2009zz}.
-The asymmetry was also subject to several theoretical studies.
-In our context it is of interest to review two of them in some more 
-detail, namely Refs.~\cite{Anselmino:2005nn} and \cite{Schweitzer:2010tt}.
-
-In Ref.~\cite{Anselmino:2005nn} it was assumed that the EMC data on 
-$A_{UU}^{\cos\phi}$ is due to the Cahn effect only, and on the basis 
-of this assumption, the Gaussian widths of $f_1^a(x,\kperp)$ and 
-$D_1^a(z,\pperp)$ were extracted from the EMC data \cite{Aubert:1983cz}.
-In the WW-type approximation, the EMC data contain also contributions 
-from the Boer-Mulders effect, see Eq.~(\ref{Eq:WW-type-FUUcosphi}). 
-There are two reasons, why one may neglect this contribution with
-a presumably good approximation \cite{Schweitzer:2010tt}.
-First, one may expect it to be less dominant than the Cahn effect
-contribution because the Boer-Mulders and Collins functions
-are required by positivity inequalities to be smaller than
-$f_1^a$ and $D_1^a$, and phenomenologically $h_1^{\perp a}$ 
-and $H_1^{\perp a}$ are both observed to be clearly smaller than
-the respectively allowed upper bounds.
-Moreover, EMC has not detected specific final state hadrons, 
-but summed over all charged hadrons. In such sums the Collins 
-effect for positive and negative pions tends to cancel out largely.
-Charged pions yield the main part of charged hadrons, and the 
-Collins effect of for instance kaons is observed to be small.
-Therefore, the analysis of the EMC data of \cite{Anselmino:2005nn}
-gives insights mainly on the transverse momentum dependencies of 
-$f_1^a$ and $D_1^a$, {\sl provided} the WW-type approximation holds.
-
-In contrast to this in \cite{Schweitzer:2010tt} recent data
-on cross sections and mean transverse hadron momenta 
-from Jefferson Lab \cite{Osipenko:2008aa,Mkrtchyan:2007sr} and HERMES 
-\cite{Airapetian:2009jy} were studied. The results from 
-\cite{Schweitzer:2010tt} were also shown to be compatible
-with COMPASS data, see \cite{Rajotte:2010ir}. The important
-point is that the analysis of \cite{Schweitzer:2010tt} was free
-of any WW-type-approximations. Nevertheless, the phenomenological
-numbers from the studies \cite{Anselmino:2005nn} and
-\cite{Schweitzer:2010tt} are in good agreement
-(and both results are also supported by lattice QCD),
-see Sec.~\ref{Sec-5.1:FUU-basis}.
-The agreement of \cite{Anselmino:2005nn} and \cite{Schweitzer:2010tt}
-indicates that the neglect of $\bar qgq$-terms in $A_{UU}^{\cos\phi}$ 
-is, at least in the kinematics of the EMC experiment and within the
-accuracy of that data \cite{Aubert:1983cz}, 
-a useful assumption.
-
-It is necessary to make one cautious comment though. In the EMC experiment
-the data were taken with a $280\,{\rm GeV}$ muon beam, and one expects
-$\kperp$-broadening effects \cite{Schweitzer:2010tt,Aybat:2011zv} as compared 
-to HERMES or JLab energies. Without considering evolution effects,
-one obtains a good agreement of the descriptions of HERMES and EMC data
-with the same parameter set, see Fig.~\ref{Fig-02:EMC}.
-If one takes these effects phenomenologically \cite{Schweitzer:2010tt}
-or rigorously \cite{Aybat:2011zv} into account, one would expect
-the theoretical curve in Fig.~\ref{Fig-02:EMC} to
-overshoot the data by about $30\,\%$. This would indicate that the
-$\bar qgq$-terms in this observable could about about $30\,\%$.
-We stress that we would not expect WW-type approximations to
-work better then that.
-\ps{We probably can considerably shorten this lengthy review section
-to 2--3 sentences. Any objections?}
-
-{}
-
-\newpage
-\section{Convolution integrals and expressions in Gaussian Ansatz (OLD)}
-\label{App:factor-old}
-
-In this Appendix we explain the notation for convolution integrals
-of TMDs and FFs and give the explicit results obtained assuming the
-Gaussian Ansatz.
-
-\subsection{Notation for convolution integrals \label{old-ApendixB1}}
-
-Parton interpretation of structure functions can be obtained as convolution of distribution and fragmentation functions \cite{Mulders:1995dh,Bacchetta:2006tn,Anselmino:2011ch}
-\be
-{\cal C}\bigl[ w\slim f\slim D \bigr]
-=  x \,
-\sum_a e_a^2 \int d^2 {\bm p}_T \,  d^2 {\bm k}_T
-\, \delta^{(2)}\bigl({\bm p}_T - {\bm k}_T - {\bm P}_{h \perp}/z \bigr)
-\,w({\bm p}_T,{\bm k}_T)\,
-f^a( x ,p_T^2)\,D^a(z,z^2 k_T^2) ,
-\label{old-eq:convolution}
-\ee
-and the unit vector is defined as $\bfhp  ={\bm P}_{h \perp}/{P}_{h
-  \perp}$, here ${\bm p}_T$ is the transverse momentum of quark with respect to the proton, ${\bm k}_T$ is the transverse momentum of fragmenting quark with respect to the produced hadron, and  $- {\bm P}_{h \perp}/z \simeq {\bm q}_T$ the transverse momentum of the virtual photon; these momenta are defined in ``target - produced hadron" cm frame.
-
-Fragmentation function have probabilistic interpretation with respect to transverse momentum of produced hadron with respect to the fragmenting quark 
-\be
-{\bm P}_\perp\simeq -{z}\; {\bm k}_T\;,
-\ee
-so that for unpolarized fragmentation function one has
-\be
-D_{1 q/h}(z) \equiv  \int d^2 {\bm P}_\perp D_{1 q/h}(z, P_\perp^2) = z^2 \int d^2 {\bm k}_T D_{1 q/h}(z, z^2  k_T^2) \label{old-eq:D1}\;.
-\ee
-Experimental measurements are usually given in the photon-proton cm frame in which we can rewrite Eq.(\ref{old-eq:convolution}) using ``physical'' vector $ {\bm P}_\perp$
-\be
-{\cal C}\bigl[ w\slim f\slim D \bigr]
-=  x \,
-\sum_a e_a^2 \int d^2 \bfkperp\,  d^2 \bfpperp^{ }
-\, \delta^{(2)}\bigl(z\bfkperp + \bfpperp - \bfPhperp \bigr)
-\,w\left(\bfkperp,-\frac{\bfpperp^{ }}{z}\right)\,
-f^a( x ,\kperp^2)\,D^a(z,\pperp^2) ,
-\label{old-eq:convolution_our}
-\ee
-integrating $\delta$ function we obtain
-\be
-{\cal C}\bigl[ w\slim f\slim D \bigr]
-=  x \,
-\sum_a e_a^2 \int d^2 \bfkperp\, 
-\, 
-\,w\left(\bfkperp,-\frac{\left({\bm P}_{h \perp} - z\bfkperp\right)}{z}\right)\,
-f^a( x ,\kperp^2)\,D^a\left(z,({\bm P}_{h \perp} - z\bfkperp)^2\right) .
-\label{old-eq:convolution_our_main}
-\ee
-
-The notations of our paper can be readily compared to notations of other papers, such as Ref.~\cite{Anselmino:2011ch}, for instance, where $\bfpperp |_{our} \equiv {\bm p}_\perp |${\cite{Anselmino:2011ch}} and $\bfkperp |_{our} \equiv {\bm k}_\perp${\cite{Anselmino:2011ch}}.
-
-We are using the following definitions of moments of TMDs
-\ba
-f^{(n)}(x) &=& \int d^2 \bfkperp \left(\frac{\kperp^2}{2M^2}\right)^n f(x, \kperp^2)\;, \\
-D^{(n)}(z) &=& \int d^2 \bfpperp \left(\frac{\pperp^2}{2 z^2 m_h^2}\right)^n D(z, \pperp^2)\; .
-\label{old-eq:moments}
-\ea
-
-\subsection{Gaussian factors}
-
-The gaussian factor for $F_{UU}$:
-
-\be
-{ \cal G}_{UU}(x,z,\Phperp ) = \frac{1}{\pi \la \Phperp^2 \ra}e^{-\Phperp^2/\la \Phperp^2 \ra}, \; \la \Phperp^2 \ra =  z^2 \avkperp + \avpperp .
-\label{old-eq:factor_fuu}
-\ee
-
-The gaussian factor for $F_{LL}$:
-
-\be
-{ \cal G}_{LL}(x,z,\Phperp ) = \frac{1}{\pi \la \Phperp^2 \ra_{g_1}}e^{-\Phperp^2/\la \Phperp^2 \ra_{g_1}}, \; \la \Phperp^2 \ra_{g_1} =  z^2 \avkperp_{g_1} + \avpperp .
-\label{old-eq:factor_fll}
-\ee
-
-The gaussian factors for $F_{LT}^{\cos(\phi_h-\phi_S)}$:
-
-\be
-{ \cal G}_{LT}(x,z,\Phperp ) = \frac{M^2}{\pi \la \Phperp^2 \ra_{g_{1T}^\perp}^2}e^{-\Phperp^2/\la \Phperp^2 \ra_{g_{1T}^\perp}}, \; \la \Phperp^2 \ra_{g_{1T}^\perp} =  z^2 \avkperp_{g_{1T}^\perp} + \avpperp .
-\label{old-eq:factor_flt}
-\ee
-
-\be
-{\cal A}_{LT}^{\cos(\phi_h -\phi_S)} = \frac{M
-z \sqrt{\pi}}{\sqrt{\la \Phperp^2 \ra_{g_{1T}^\perp}}} .
-\label{old-eq:factor_aflt}
-\ee
-
-The gaussian factors for $F_{UL}^{\sin(2\phi_h)}$:
-\be
-{ \cal G}_{UL}^{\sin(2\phi_h)}(x,z,\Phperp ) = \frac{M^4}{\pi \la \Phperp^2 \ra_{h_{1L}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1L}^\perp}}, \; \la \Phperp^2 \ra_{h_{1L}^\perp} =  z^2 \avkperp_{h_{1L}^\perp} + \avpperp_{H_1^\perp} .
-\label{old-eq:factor_hlt}
-\ee
-
-\be
-{\cal A}_{UL}^{\sin(2\phi_h)} = \frac{4 m_h M 
-z^2}{ \la \Phperp^2 \ra_{h_{1L}^\perp}} .
-\label{old-eq:factor_ahlt}
-\ee
-
-The gaussian factors for $F_{UT}^{\sin(\phi_h+\phi_S)}$:
-\be
-{ \cal G}_{UT}^{\sin(\phi_h+\phi_S)}(x,z,\Phperp ) = \frac{M^2}{\pi \la \Phperp^2 \ra_{h_{1}}^2}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1}}}, \; \la \Phperp^2 \ra_{h_{1}} =  z^2 \avkperp_{h_{1}} + \avpperp_{H_1^\perp} .
-\label{old-eq:factor_h1}
-\ee
-
-\be
-{\cal A}_{UT}^{\sin(\phi_h+\phi_S)} = \frac{m_h 
-z \sqrt{\pi}}{ \sqrt{\la \Phperp^2 \ra_{h_{1}}}} .
-\label{old-eq:factor_ah1}
-\ee
-
-The gaussian factors for $F_{UT}^{\sin(\phi_h-\phi_S)}$:
-\be
-{ \cal G}_{UT}^{\sin(\phi_h-\phi_S)}(x,z,\Phperp ) = \frac{M^2}{\pi \la \Phperp^2 \ra_{f_{1T}^\perp}^2}e^{-\Phperp^2/\la \Phperp^2 \ra_{f_{1T}^\perp}}, \; \la \Phperp^2 \ra_{f_{1T}^\perp} =  z^2 \avkperp_{f_{1T}^\perp} + \avpperp .
-\label{old-eq:factor_f1t}
-\ee
-
-\be
-{\cal A}_{UT}^{\sin(\phi_h-\phi_S)} = \frac{M 
-z \sqrt{\pi}}{ \sqrt{\la \Phperp^2 \ra_{f_{1T}^\perp}}} .
-\label{old-eq:factor_af1t}
-\ee
-
-The gaussian factors for $F_{UT}^{\sin(3 \phi_h-\phi_S)}$:
-\be
-{ \cal G}_{UT}^{\sin(3 \phi_h-\phi_S)}(x,z,\Phperp ) = \frac{M^4 \avkperp_{h_{1T}^\perp}}{\pi \la \Phperp^2 \ra_{h_{1T}^\perp}^4}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1T}^\perp}}, \; \la \Phperp^2 \ra_{h_{1T}^\perp} =  z^2 \avkperp_{h_{1T}^\perp} + \avpperp_{H_1^\perp} .
-\label{old-eq:factor_h1tp}
-\ee
-
-\be
-{\cal A}_{UT}^{\sin(3 \phi_h-\phi_S)} = \frac{3 m_h \avkperp_{h_{1T}^\perp}
-z^3  \sqrt{\pi}}{ 2 \sqrt{\la \Phperp^2 \ra_{f_{1T}^\perp}^3}} .
-\label{old-eq:factor_ah1tp}
-\ee
-
-The gaussian factors for $F_{UU}^{\cos(2\phi_h)}$:
-\be
-{ \cal G}_{UU}^{\cos(2\phi_h)}(x,z,\Phperp ) = \frac{M^4}{\pi \la \Phperp^2 \ra_{h_{1}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1}^\perp}}, \; \la \Phperp^2 \ra_{h_{1}^\perp} =  z^2 \avkperp_{h_{1}^\perp} + \avpperp_{H_1^\perp} .
-\label{old-eq:factor_h1perp}
-\ee
-
-\be
-{\cal A}_{UU}^{\cos(2\phi_h)} = \frac{4 m_h M 
-z^2}{ \la \Phperp^2 \ra_{h_{1}^\perp}} .
-\label{old-eq:factor_ah1perp}
-\ee
-
-The gaussian factor for $F_{LT}^{\cos\phi_S}$:
-\be
-{ \cal G}_{LT}^{\cos\phi_S}(x,z,\Phperp ) = \frac{z^2\avkperp_{g_{1T}^\perp} (\Phperp^2+\avpperp) + \avpperp^2}{\pi \la \Phperp^2 \ra_{g_{1T}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{g_{1T}^\perp}}, \; \la \Phperp^2 \ra_{g_{1T}^\perp} =  z^2 \avkperp_{g_{1T}^\perp} + \avpperp .
-\label{old-eq:factor_gltcosphi}
-\ee
-
-The gaussian factors for $F_{UL}^{\sin \phi_h}$:
-\ba
-{ \cal G}_{UL}^{\sin \phi_h}(x,z,\Phperp ) &=& \frac{4 M^2 \left(z^2\avkperp_{h_{1L}^\perp} (\Phperp^2-z^2\avkperp_{h_{1L}^\perp}) + \avpperp^2_{H_1^\perp}\right)}{\pi \la \Phperp^2 \ra_{h_{1L}^\perp}^4}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1L}^\perp}}, \nonumber \\
-\la \Phperp^2 \ra_{h_{1L}^\perp} &= & z^2 \avkperp_{h_{1L}^\perp} + \avpperp_{H_1^\perp}  .
-\label{old-eq:factor_gulsinphi}
-\ea
-
-\be
-{\cal A}_{UL}^{\sin \phi_h} = \frac{m_h  
-z \sqrt{\pi} \left(2 \avpperp_{H_1^\perp} + z^2 \avkperp_{h_{1L}^\perp}\right)} { \sqrt{\la \Phperp^2 \ra_{h_{1L}^\perp}^3 }} \; .
-\label{old-eq:factor_aulsinphi}
-\ee
-
-The gaussian factors for $F_{LL}^{\cos\phi_h}$:
-\be
-{ \cal G}_{LL}^{\cos\phi_h}(x,z,\Phperp ) =\frac{\avkperp_{g_{1}}}{\pi \la \Phperp^2 \ra_{g_{1}}^2}e^{-\Phperp^2/\la \Phperp^2 \ra_{g_{1}}}, 
-\la \Phperp^2 \ra_{g_{1}} =  z^2 \avkperp_{g_{1}} + \avpperp .
-\label{old-eq:factor_gllcosphi}
-\ee
-
-\be
-{\cal A}_{LL}^{\cos\phi_h} = \frac{
-z \sqrt{\pi} \avkperp_{g_{1}}}{ 2 M \sqrt{\la \Phperp^2 \ra_{g_{1}}}} .
-\label{old-eq:factor_allcosphi}
-\ee
-
-  The gaussian factors for $F_{LT}^{\cos(2\phi_h-\phi_S)}$:
-
-\be
-{ \cal G}_{LT}^{\cos(2\phi_h-\phi_S)}(x,z,\Phperp ) = \frac{M^2 \avkperp_{g_{1T}^\perp}}{\pi \la \Phperp^2 \ra_{g_{1T}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{g_{1T}^\perp}}, \; \la \Phperp^2 \ra_{g_{1T}^\perp} =  z^2 \avkperp_{g_{1T}^\perp} + \avpperp .
-\label{old-eq:factor_gltcos2phi}
-\ee
-
-\be
-{\cal A}_{LT}^{\cos(2\phi_h -\phi_S)} = \frac{M^2 \avkperp_{g_{1T}^\perp}
-z^2 }{ \la \Phperp^2 \ra_{g_{1T}^\perp}} .
-\label{old-eq:factor_altcos2phi}
-\ee
-
-The gaussian factors for $F_{UU}^{\cos \phi_h}$:
-
-\ba
-{ \cal G}_{UU1}^{\cos \phi_h}(x,z,\Phperp ) = \frac{ 4 M^2 (\avpperp_{H_{1}^\perp}+z^2 \avkperp_{h_{1}^\perp} (  \Phperp^2  -z^2\avkperp_{h_{1}^\perp} ) }{\pi \la \Phperp^2 \ra_{h_{1}^\perp}^4}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1}^\perp}}, \nonumber \\
-\; \la \Phperp^2 \ra_{h_{1}^\perp} =  z^2 \avkperp_{h_{1}^\perp} + \avpperp_{H_{1}^\perp} .
-\label{old-eq:factor_guucosphi1}
-\ea
-
-\be
-{\cal A}_{UU1}^{\cos \phi_h} = \frac{m_h  
-z \sqrt{\pi} \left(2 \avpperp_{H_1^\perp} + z^2 \avkperp_{h_{1}^\perp}\right)} { \sqrt{\la \Phperp^2 \ra_{h_{1}^\perp}^3 }} \; .
-\label{old-eq:factor_auucosphi1}
-\ee
-
-\be
-{ \cal G}_{UU2}^{\cos\phi_h}(x,z,\Phperp ) =\frac{\avkperp}{\pi \la \Phperp^2 \ra^2}e^{-\Phperp^2/\la \Phperp^2 \ra}, \la \Phperp^2 \ra =  z^2 \avkperp + \avpperp .
-\label{old-eq:factor_guucosphi2}
-\ee
-
-\be
-{\cal A}_{UU2}^{\cos\phi_h} = \frac{
-z \sqrt{\pi} \avkperp}{ 2 M \sqrt{\la \Phperp^2 \ra}} .
-\label{old-eq:factor_auucosphi2}
-\ee
-
-The gaussian factors for $F_{UT}^{\sin\phi_S}$:
-\ba
-{ \cal G}_{UT1}^{\sin\phi_S}(x,z,\Phperp ) = \frac{z^2\avkperp_{f_{1T}^\perp} \left(\Phperp^2+\avpperp\right) + \avpperp^2}{\pi \la \Phperp^2 \ra_{f_{1T}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{f_{1T}^\perp}}, \nonumber \\
-\; \la \Phperp^2 \ra_{f_{1T}^\perp} =  z^2 \avkperp_{f_{1T}^\perp} + \avpperp .
-\label{old-eq:factor_gutsinphi1}
-\ea
-
-\be
-{ \cal G}_{UT2}^{\sin\phi_S}(x,z,\Phperp ) = \frac{\avkperp_{h_{1}} \left(-\Phperp^2+\la \Phperp^2 \ra_{h_{1}}\right)}{\pi \la \Phperp^2 \ra_{h_{1}}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1}}}, \; \la \Phperp^2 \ra_{h_{1}} =  z^2 \avkperp_{h_{1}} + \avpperp_{H_{1}^\perp} .
-\label{old-eq:factor_gutsinphi2}
-\ee
-
-The gaussian factors for $F_{UT}^{\sin( 2\phi_h -\phi_S)}$:
-
-\ba
-{ \cal G}_{UT1}^{\sin( 2\phi_h -\phi_S)}(x,z,\Phperp ) = \frac{M^2 \avkperp_{f_{1T}^\perp}  }{\pi \la \Phperp^2 \ra_{f_{1T}^\perp}^3}e^{-\Phperp^2/\la \Phperp^2 \ra_{f_{1T}^\perp}}, \; \nonumber \\
- \la \Phperp^2 \ra_{f_{1T}^\perp} =  z^2 \avkperp_{f_{1T}^\perp} + \avpperp. \nonumber \\
-\label{old-eq:factor_gutsin2phi1}
-\ea
-
-\be
-{\cal A}_{UT1}^{\sin( 2\phi_h -\phi_S)} = \frac{
-z^2 \avkperp_{f_{1T}^\perp}}{  \la \Phperp^2 \ra_{f_{1T}^\perp}} \; .
-\label{old-eq:factor_autsin2phi1}
-\ee
-
-\ba
-{ \cal G}_{UT2}^{\sin( 2\phi_h -\phi_S)}(x,z,\Phperp ) =  \frac{ 2 M^2 m_h \avkperp_{h_{1T}^\perp} \left(2 \avpperp_{H_{1}^\perp}^2+z^2 \avkperp_{h_{1T}^\perp} \left(  \Phperp^2  + \avpperp_{H_{1}^\perp} \right) - z^4 \avkperp_{h_{1T}^\perp}^2 \right) }{\pi \la \Phperp^2 \ra_{h_{1T}^\perp}^5} \times \nonumber \\ e^{-\Phperp^2/\la \Phperp^2 \ra_{h_{1T}^\perp}}, \nonumber \\
-\; \la \Phperp^2 \ra_{h_{1T}^\perp} =  z^2 \avkperp_{h_{1T}^\perp} + \avpperp_{H_{1}^\perp} \nonumber \\ 
-\label{old-eq:factor_gutsin2phi2}
-\ea
-
-\be
-{\cal A}_{UT2}^{\sin( 2\phi_h -\phi_S)} =  \frac{2 m_h  M
-z^2 \avkperp_{h_{1T}^\perp} \left(2 \avpperp_{H_1^\perp} + z^2 \avkperp_{h_{1T}^\perp}\right)} { \la \Phperp^2 \ra_{h_{1T}^\perp}^2 }.
-\label{old-eq:factor_autsin2phi2}
-\ee
-
-{}
-
-\newpage

### 2018-05-21 tex/test-WW-type-00v-PS.tex
lattice section

@@
 \ea
+where the amplitudes $\tilde{A}$ and constants $c$ are those of Ref.~\cite{Musch:2010ka}.
 We have thus expressed the left hand side of 
@@
 Before quoting numbers, a few more comments are in order. The overall 
-multiplicative renormalization had been fixed by setting the Gaussian 
+multiplicative renormalization in Ref.~\cite{Musch:2010ka} was fixed by setting the Gaussian 
 integral $c_{2,u-d}$ of the unpolarized TMD $f_1$ in the isovector channel 
-(u-d) to the nucleon quark content, namely, to 1. The validity the 
-assumption that renormalization is mutliplicative and flavor-independent 
-for the non-local lattice operators is under investigation 
-\cite{Yoon:2017qzo}. %PhysRevD.96.094508
+(u-d) to the nucleon quark content, namely, to 1. 
+One then assumes that the normalization of the lattice results for the unpolarized TMD $f_1$
+also fixes the normalization for polarized quantities correctly. 
+This assumption holds if renormalization is mutliplicative and flavor-independent 
+for the non-local lattice operators. This is not true for all lattice actions
+\cite{Yoon:2017qzo} %PhysRevD.96.094508
+but presumably it is true if the lattice action preserves chiral symmetry, as it does in the present case.
+The Gaussian fits along with the normalization prescription serve as
+a crude form of renormalization, and this is needed to attempt
+a comparison of left and right hand sides of equations  
+Eqs.~(\ref{Eq:WW-approx-g1T-d},~\ref{Eq:WW-approx-h1L-d}).
+
+There is yet another issue to be discussed. 
 The gauge link that goes into the evaluation of the quark-quark correlator 
-introduces a power divergence that has to be subtracted. The subtraction 
-scheme that was chosen on the lattice is not known to have a clear relation 
-to a ``real world'' subtraction scheme designed for experimental TMDs and 
+introduces a power divergence that has to be subtracted. 
+Ref.~\cite{Musch:2010ka} employs a subtraction scheme on the lattice
+but establishes no connection with a subtraction scheme designed for experimental TMDs and 
 the corresponding gauge link geometry. The gauge link renormalization mainly 
@@
 lattice calculations actually test. As mentioned above, in
-the lattice study \cite{Hagler:2007xi} a specific choice for
+the lattice study \cite{Hagler:2009mb,Musch:2010ka} a specific choice for
 the path of the gauge link was chosen, which is actually different
 from the paths required in SIDIS or Drell-Yan. With the path choice of
-\cite{Hagler:2007xi} there are effectively only (T-even)
+\cite{Hagler:2009mb,Musch:2010ka} there are effectively only (T-even)
 $A_i$ amplitudes, the $B_i$ amplitudes are absent.
@@
 exploratory status of the TMD lattice calculations
-\cite{Hagler:2007xi}, this is already a remarkable and very
+\cite{Hagler:2009mb,Musch:2010ka}, this is already a remarkable and very
 interesting result. Thus, apart from the instanton calculus
@@
 not really reach our goal of testing the WW-type approximations
-on the lattice. With the presently available lattice data
-this is not yet possible. Future lattice data on higher
-Mellin moments will provide further insights.
+on the lattice. We have to wait for better lattice data. 
 Meanwhile we may try to gain insights into the quality of

### 2018-05-23 tex/test-WW-type-00v-PS.tex
alexei

@@
 \preprint{JLAB-THY-18-XXXX}
+\preprint{version 00v-PS}
 
@@
 WW-relations for FFs are actually not needed: in Eqs.~%
-(\ref{Eqs:structure-functions-twist-2},~\ref{Eqs:structure-functions-twist-2})
+(\ref{Eqs:structure-functions-twist-2},~\ref{Eqs:structure-functions-twist-3})
 either twist-2 FFs $D_1^a$, $H_1^{\perp a}$ enter or tilde FFs, as a consequence 
@@
 	Left panel: 
-	leading-twist asymmetry $A_{LT}^{\cos(\cos\phi_h-\phi_S)}$ 
+	leading-twist asymmetry $A_{LT}^{\cos(\phi_h-\phi_S)}$ 
 	described in Sec.~\ref{Sec-6.1:FLTcosphi-phiS}.
@@
 	Right panel: 
-	subleading-twist $A_{LT}^{\cos(2\cos\phi_h-\phi_S)}$
+	subleading-twist $A_{LT}^{\cos(2\phi_h-\phi_S)}$
 	on which we comment in Sec.~\ref{Sec-7.3:FLTcos2phi-phiS}.}

### 2018-05-23 tex/test-WW-type-00v-PS.tex
alexei
Saman tests
"Hello world" at abstract

@@
 \author[a]{K.~Tezgin}
-\author[j]{W.~Vogelsang}
 
@@
 \emailAdd{kemal.tezgin@uconn.edu}
-\emailAdd{werner.vogelsang@uni-tuebingen.de}
 
@@
 \abstract{
+\SB{HELLO WORLD}
 We present the complete cross-section for pion production in semi-inclusive
@@
     	g_2(x) \stackrel{\rm WW}{\approx} g_2(x)_{\rm WW} \equiv
-	\frac{ d\;}{ d x}\;\Biggl[\frac{x}{2}\int_x^1\frac{ d y}{y}
+	\frac{ d\;}{ d x}\;\Biggl[x\int_x^1\frac{ d y}{y}
 	\;g_1(y)\Biggr]\,.\label{Eq:g2-in-WW-approximation}

### 2018-05-24 tex/test-WW-type-00v-PS.tex
alexei

--- 2018-05-23 tex/test-WW-type-00v-PS.tex
@@
 %\begin{abstract}
+
 \abstract{
@@
 (\ref{Eqs:structure-functions-twist-2},~\ref{Eqs:structure-functions-twist-3})
-either twist-2 FFs $D_1^a$, $H_1^{\perp a}$ enter or tilde FFs, as a consequence 
+either twist-2 FFs $D_1^q$, $H_1^{\perp q}$ enter or tilde FFs, as a consequence 
 of how the azimuthal angles are defined \cite{Bacchetta:2006tn}. 
@@
 $N_d=-0.97$ & $\alpha_d=0.44$ & $\beta_d=0.90$\\
-& $M_1^2=0.19\textrm{(GeV}^2$) &   \\
+& $M_1^2=0.19\; \textrm{(GeV}^2$) &   \\
 \hline
@@
 
-The following parametrizations was used in Ref.~\cite{Barone:2015ksa}:
+Ref.~\cite{Barone:2010gk} used the parametrization in which Boer-Mulders function is proportional to the Sivers functions, such that:
 \ba
@@
 - \,\frac{M}{M_{BM}}  
-\sqrt{2e}\; N_q 
+\sqrt{2e}\; N_{BM}^q N_q (x)
 \, f_{q/p} (x, Q)\frac{e^{-\kperp^2/\avkperp_{h_{1}^{\perp}}}}{\pi\avkperp},  
 \label{BM-dist}
+\ea
+ where  
+%
+\ba
+{\cal N}_q(x)= N_q \, x^{\alpha} (1-x)^{\beta} \,
+\frac{(\alpha + \beta)^{(\alpha +\beta)}}
+{\alpha^{\alpha} \beta^{\beta}}\; .
  \ea
@@
 
-%
-\begin{table}[htb]
+ \begin{table}
 \centering
-\begin{tabular}{l c l l c l}
+\begin{tabular}{crl}
 \hline
- $N_{u}$ &=& $-0.49 \pm 0.15$ & $N_{d}$ &=& $-1 \pm 0.2$\\
- $M_{BM}^2$ &=& $0.1 \pm  0.2$&\multicolumn{3}{l}{(GeV$^2$)}\\ 
+$N_{BM}^u=2.1\pm0.1$ & $N_{BM}^d=$&$-1.111\pm0.001$   \\
+Fixed & parameters: &  \\
+$N_u=0.35$ & $\alpha_u=0.73$ & $\beta_u=3.46$ \\
+$N_d=-0.9$ & $\alpha_d=1.08$ & $\beta_d=3.46$\\
+& $M_{BM}^2=$&$0.34\; \textrm{(GeV}^2$)    \\
 \hline
 \end{tabular}
-\caption{Fitted parameters of Boer-Mulders quark distributions. Values are from Ref.~\cite{Barone:2015ksa}}
+\caption{Fitted parameters of Boer-Mulders quark distributions. Values are from Ref.~\cite{Barone:2009hw}.}
 \label{fitparbm}
 \end{table}
+%
+%\begin{table}[htb]
+%\centering
+%\begin{tabular}{l c l l c l}
+%\hline
+ %$N_{u}$ &=& $-0.49 \pm 0.15$ & $N_{d}$ &=& $-1 \pm 0.2$\\
+% $M_{BM}^2$ &=& $0.1 \pm  0.2$&\multicolumn{3}{l}{(GeV$^2$)}\\ 
+%\hline
+%\end{tabular}
+%\caption{Fitted parameters of Boer-Mulders quark distributions. Values are from Ref.~\cite{Barone:2015ksa}}
+%\label{fitparbm}
+%\end{table}
 

### 2018-05-25 tex/test-WW-type-00v-PS.tex
alexei
math

@@
 How well does the WW approximation describe data if we allow for a
-theoretical ``uncertainty band'' of about $40\,\%$ as deduced in 
-\cite{Accardi:2009au}? To investigate this question, 
+theoretical ``uncertainty band'' of about $40\,\%$ as deduced in Ref.~\cite{Accardi:2009au}? To investigate this question, 
 we split this uncertainty in two parts, $\varepsilon_1=\pm 20\,\%$ and 
@@
 \begin{subequations}\ba
-	\frac{\kperp^2}{4M_N^2}\;(f_{1}^{q}(x,\kperp^2))^2 
+	\frac{\kperp^2}{4M_N^2}\;\left((f_{1}^{q}(x,\kperp^2))^2 -(g_{1}^{q}(x,\kperp^2))^2\right)
 	- (h^{\perp(1)q}_{1L}(x,\kperp^2))^2 
@@
 	& \ge & 0\,, \label{eq:positivity}\\
-	\frac{\kperp^2}{4M_N^2}\;(f_{1}^{q}(x,\kperp^2))^2 
+	\frac{\kperp^2}{4M_N^2}\;\left((f_{1}^{q}(x,\kperp^2))^2 -(g_{1}^{q}(x,\kperp^2))^2\right)
 	- (f_{1T}^{\perp(1)q}(x,\kperp^2))^2
 	- (g^{\perp(1)q}_{1T}(x,\kperp^2))^2 
-	& \ge & 0\,. \label{eq:positivity1}
+	& \ge & 0\,, \label{eq:positivity1}
 \ea\end{subequations}
+where $f^{(1)}(x,\kperp^2) \equiv \frac{\kperp^2}{2M_N^2} f(x,\kperp^2)$.
 The inequalities provide a non-trivial test of our approach.

### 2018-05-30 tex/test-WW-type-00v-PS.tex
new files

@@
 $Q^2 = 2.4$ GeV$^2$. Collinear $f_1^a(x)$ are from Ref.~\cite{Martin:2009iq},  
-$g_1^a(x)$ are from Ref.~\cite{Gluck:1998xa}, and $D_1^a)$ are from 
+$g_1^a(x)$ are from Ref.~\cite{Gluck:1998xa}, and $D_1^a$ are from 
 Ref.~\cite{deFlorian:2007aj}. The other four TMDs 
@@
 \ps{are plotted in Fig.~\ref{aut_h1_jlab} in comparison to HERMES data 
-on charged pion production from a proton target \cite{Airapetian:2009ae}.
+on charged pion production from a proton target \cite{Airapetian:2010ds}.
 Also in Fig.~\ref{aut_h1_jlab} we show the $x$-- and $P_{hT}$--dependencies 
@@
 	$\la x\ra = 0.1$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ 
-	\cite{Airapetian:2009ae}. The theoretical curves are based on 
-	the fit results of Ref.~\cite{Anselmino:2013vqa}.\newline
-	\red{Do we cite here the right HERMES paper? Please, double check.}}
+	\cite{Airapetian:2010ds}. The theoretical curves are based on 
+	the fit results of Ref.~\cite{Anselmino:2013vqa}.}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.3\textwidth]{\FigPath/g1t.pdf} \quad
-\includegraphics[width=0.3\textwidth]{\FigPath/h1Lperp.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/g1t.pdf} \quad
+\includegraphics[width=0.45\textwidth]{\FigPath/h1Lperp.pdf}
 	\caption{\label{g1t_h1l_functions} 
@@
 %\includegraphics[width=0.3\textwidth]{\FigPath/ALT_COMPASS_x.pdf}  
-\includegraphics[width=0.9\textwidth]{\FigPath/Fig-COMPASS-A_LT_Pr10.pdf}
+\includegraphics[width=0.95\textwidth]{\FigPath/Fig-COMPASS-A_LT_Pr10.pdf}
 	\caption{\label{g1t_jlab} 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/Fig-AUUcosphi-COMP.pdf} 
+\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
 %\includegraphics[width=0.45\textwidth]{}
@@
 correlators). It will be very interesting to learn whether e.g.\ 
-in $F_{LU}^{\sin\phi_h}$ or $F_{LU}^{\sin\phi_h}$ a single $\bar qgq$--term 
+in $F_{UL}^{\sin\phi_h}$ or $F_{LU}^{\sin\phi_h}$ a single $\bar qgq$--term 
 is anomalously large, or whether it is a accumulative effect of 
@@
 \section{Acknowledgments}
-The authors would like to thank their families for patience and
-the constant support during work on this project. This work was 
+First and foremost, the authors would like to thank their families for patience and
+constant support throughout writing this paper. This work was 
 partially supported by the U.S.\ Department of Energy under 

### 2018-05-30 tex/test-WW-type-00v-PS.tex
new files
a

@@
 \centering
-	\includegraphics[width=7.2cm]{\FigPath/Fig02a-kin-SIDIS-UT.eps}
+	\includegraphics[width=7.2cm]{\FigPath/Fig02a-kin-SIDIS-UT}
         \caption{\label{fig-kin-SIDIS}
@@
 If not otherwise stated the parametrizations are taken at the scale 
-$Q^2=2.5\,{\rm GeV}^2$.
+$Q^2=2.4\,{\rm GeV}^2$.
 

### 2018-05-31 tex/test-WW-type-00v-PS.tex
final plots

@@
 \bibliographystyle{JHEP}
+
+\usepackage{lineno} % page numbers
 
@@
 
+\linenumbers % line numbers
+
 \maketitle
@@
 further developments.}
+
+All results of this projects are publicly available via open source \texttt{github.com}\footnote{\href{https://github.com/prokudin/WW-SIDIS}{https://github.com/prokudin/WW-SIDIS}} in the form of a \texttt{mathematica}~\cite{Mathematica} package.
+A dedicated \texttt{Python} package will be released in the future.
+Details about implementation and description of the package can be found in Appendix~\ref{app:package}.
 
@@
 \centering
-\includegraphics[height=3cm]{\FigPath/Fig02a-JLab-ratio-pT-v5-NEW.pdf}  \quad
-\includegraphics[height=3cm]{\FigPath/hermes_pip.pdf} \quad
-\includegraphics[height=3cm]{\FigPath/compass_hp.pdf} 
+\includegraphics[height=3.2cm]{\FigPath/Fig02a-JLab-ratio-pT-v5-NEW.pdf}  \quad
+\includegraphics[height=3.2cm]{\FigPath/hermes_pip.pdf} \quad
+\includegraphics[height=3.2cm]{\FigPath/compass_hp.pdf} 
 \caption{\label{FUU-show-pT-dependence}
@@
 in (\ref{Eq:FUU-Phperp}) with its $\Phperp$--integrated counterpart
-(\ref{Eq:FUU}). In our effective description this is step is trivial. In 
+(\ref{Eq:FUU}). In our effective description this step is trivial. In 
 QCD the connection of TMDs to PDFs is subtle \cite{Collins:2016hqq}.
@@
 \centering
-\includegraphics[width=0.43\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
-\includegraphics[width=0.43\textwidth]{\FigPath/AUTSivers_PT.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_PT.pdf}
 \caption{\label{aut_f1t_jlab} The Sivers asymmetry $A_{UT}^{\sin(\phi_h-\phi_S)}$  
@@
 First and foremost, the authors would like to thank their families for patience and
-constant support throughout writing this paper. This work was 
+constant support throughout writing this paper. The authors would like to thank Werner Vogelsang for many useful discussions. This work was 
 partially supported by the U.S.\ Department of Energy under 
-Contract No.~DE-AC05-06OR23177 (A.P.) and by the National 
+Contract No.~DE-AC05-06OR23177 (A.P.) and within TMD Collaboration framework, and by the National 
 Science Foundation under Contract No.\ PHY-1623454 (A.P.)
@@
 
+\newpage
+\subsection{Mathematica package}
+\label{app:package}
+
 \bibliography{\BibPath/biblio_ww}

### 2018-06-01 tex/test-WW-type-00v-PS.tex
alexei

@@
 \author[f]{B.~U.~Musch} 
-\author[e]{B.~Parsamyan} 
+\author[k]{B.~Parsamyan} 
 \author[g,b]{A.~Prokudin} 
@@
 	PA 19610, USA}
+\affiliation[k]{CERN, 1211 Geneva 23, Switzerland}
 \affiliation[h]{Department of Physics, New Mexico State University, 
@@
 is therefore $A_{UT}^{\sin\phi_S}(x)=F_{UT}^{\sin\phi_S}(x)/F_{UU}(x)=0$.
-This is compatible with preliminary data from HERMES \cite{Schnell:2010zza}
+{\color{green} Even though this is compatible with preliminary data from HERMES \cite{Schnell:2010zza}
 and COMPASS \cite{Parsamyan:2015dfa} over a wide range of $x$, see 
-Fig.~\ref{autsinphi_jlab} below. Merely for negative hadrons at 
-large-$x$ there might be a disagreement with our prediction.
+Fig.~\ref{autsinphi_jlab} below, one must notice that for negative hadrons at 
+large-$x$ there is a disagreement with our prediction.
+
+In fact at this point we should notice that WW approximation has its limitations, especially for the case of $A_{UT}^{\sin\phi_S}(x)$ one would expect that this asymmetry is sensitive to $\tilde H$ (which we neglect in this approximation):
+\begin{equation}
+F_{UT}^{\sin\phi_S}(x,z) 
+	= -x \,\frac{2m_h}{Q}\;\sum_q e_q^2\,
+	h_1^{q}(x)\; \frac{\tilde H_1^{q}(z)}{z} 
+\end{equation}	
+As pointed out in Ref.~\cite{Kanazawa:2015ajw}, both $H_1^{\perp(1)q}$ and $\tilde H_1^{q}$ are related to integrals of underlying function $H_{FU}^{q,\Im}(z,z_1)$ and thus, strictly  speaking, neglecting $\tilde H_1^{q}$ would mean neglecting  $H_1^{\perp(1)q}$ as well.
+Thus, particularly in the fragmentation sector WW-type approximation has serious limitations.}
 

### 2018-06-26 tex/test-WW-type-00x-PS.tex
text

--- 2018-05-31 tex/test-WW-type-00v-PS.tex
@@
 
-\usepackage{graphicx,epsfig,wrapfig,amssymb,color,amsmath,bm}
+\usepackage{graphicx,epsfig,wrapfig,amssymb,color,amsmath,bm,breqn}
 
 \usepackage[T1]{fontenc} % if needed
+
+\allowdisplaybreaks
+
+%\usepackage[utf8]{inputenc}
 
@@
 \definecolor{darkgreen}{rgb}{0,0.65,0}
+\definecolor{orange}{rgb}{1,0.4,0.1}
 \newcommand{\darkgreen}[1]{{\color{darkgreen} #1}}
+\newcommand{\orange}[1]{{\color{orange} #1}}
 \newcommand{\ps}[1]{\blue{ #1}}
+\newcommand{\ak}[1]{\orange{ #1}}
+\newcommand{\ms}[1]{\darkgreen{ #1}}
 
@@
 
-\preprint{JLAB-THY-18-XXXX}
-\preprint{version 00v-PS}
+\preprint{\red{version ``00x''}; JLAB-THY-18-XXXX}
+%\preprint{version 00x-PS}
 
@@
 \abstract{
-We present the complete cross-section for pion production in semi-inclusive
+We present the complete cross-section 
+for the production of unpolarized hadrons in semi-inclusive
 deep-inelastic scattering up to power-suppressed ${\cal O}(1/Q^2)$ terms in
-the Wandzura--Wilczek-type approximation \ps{which consists in a systematic
-neglect of $\bar{q}gq$--terms with respect to $\bar{q}q$--correlators.}
+the Wandzura--Wilczek-type approximation \ps{which consists in systematically
+assuming that $\bar{q}gq$--terms are much smaller than $\bar{q}q$--correlators.}
 We compute all twist-2 and twist-3 structure functions and the corresponding 
@@
 	semi-inclusive deep inelastic scattering,
-	transverse momentum dependent distribution functions, 
-	spin and azimuthal asymmetries, leading and subleading twist}
+	transverse momentum dependent distribution and fragmentation 
+	functions, spin and azimuthal asymmetries, leading and subleading twist}
 
@@
 
+\vspace{1cm}
+
+\subsection*{Color Legend}
+
+General comments: 
+	\red{red color, command: {$\backslash{\rm red}\{\dots\}$}}\\
+Alexei's corrections: 
+	\AP{redish color, command: {$\backslash{\rm AP}\{\dots\}$}}\\
+Aram's corrections: 
+	\ak{orange color, command: {$\backslash{\rm ak}\{\dots\}$}}\\
+Marc's corrections: 
+	\ms{green color, command: {$\backslash{\rm ms}\{\dots\}$}}\\
+Peter's corrections: 
+	\ps{blue color, command: {$\backslash{\rm ps}\{\dots\}$}}\\
+Anatoli Vasilievich, Bakur, Bernie, Gunar, Kemal, Saman: \\
+	corrections already introduced in black color \& confirmed by e-mail.
+
+\newpage
 %======= SECTION 1: INTRODUCTION =====================================
@@
 nucleon is due to studies of parton distribution functions (PDFs) 
-in deep-inelastic reactions. leading--twist PDFs  tell us  how likely 
+in deep-inelastic reactions. Leading--twist PDFs  tell us  how likely 
 it is to find an unpolarized parton 
@@
 of the process, the formal description is given in terms of 
-transverse momentum dependent distribution functions TMDs) 
+transverse momentum dependent distribution functions (TMDs) 
 and fragmentation functions (FFs)
 which are defined in terms of quark-quark correlators 
-\cite{Mulders:1995dh,Boer:1997nt,Goeke:2005hb,Bacchetta:2006tn},
+\cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,Bacchetta:2006tn},
 and depend on two independent variables: the fraction $x$ of 
@@
 semi-inclusive deep-inelastic scattering (SIDIS) process.
-By exploring various possibilities for electron/muon beam and target 
-polarizations unambiguous information can be accessed on the 8 leading--twist 
+By exploring various possibilities for the lepton beam and target 
+polarizations\footnote{\ps{It is important to stress that this
+	information could not have been obtained without advances 
+	in target polarization techniques employed in the HERMES, 
+	COMPASS and JLab experiments 
+	\cite{Stock:1994vv,Crabb:1997cy,Goertz:2002vv}.}}
+unambiguous information can be accessed on the 8 leading--twist 
 TMDs \cite{Boer:1997nt} and, if one assumes factorization, on certain
@@
 quark-gluon-quark ($\bar{q}gq$) correlations or current quark mass 
-terms \cite{Wandzura:1977qf,Jaffe:1991ra}. 
-We shall refer to the latter generically as $\bar qgq$--terms, keeping in 
+terms \cite{Wandzura:1977qf,Jaffe:1991ra}
+\ms{(the index $a=q\,,\bar q$ does not include gluons for
+$h_1^a$, $h_L^a$ and other chiral odd TMDs below)}.
+We shall refer to the latter generically as $\bar{q}gq$--terms, keeping in 
 mind one deals in each case with matrix elements of different operators.
-The $\bar qgq$--correlations contain new insights on hadron structure 
+The $\bar{q}gq$--correlations contain new insights on hadron structure 
 which are worthwhile exploring for their own sake, 
@@
 
-The striking observation is that the $\bar qgq$--terms in $g_T^a(x)$ 
+The striking observation is that the $\bar{q}gq$--terms in $g_T^a(x)$ 
 and $h_L^a(x)$ are small: theoretical mechanisms predict this 
@@
 predictions \cite{Abe:1998wq,Anthony:2002hy,Airapetian:2011wu}.
-This approximation (``neglect of $\bar qgq$--terms'') is commonly 
+This approximation (``neglect of $\bar{q}gq$--terms'') is commonly 
 known as Wandzura--Wilczek (WW) approximation \cite{Wandzura:1977qf}.
@@
 
-In this work, after introducing the SIDIS process and defining TMDs and FFs 
-(Sec.~\ref{Sec-2:SIDIS+TMDs+FF}), we shall introduce the WW(-type) 
+The present work is the first study of all SIDIS structure functions up to 
+twist-3 in a unique approach. Our results are of importance for experiments 
+prepared in the near-term at Jefferson Lab (JLab) with 12$\,$GeV beam energy
+upgrade and COMPASS or proposed in the long-term (Electron Ion Collider), 
+and provide helpful input for Monte Carlo event generators 
+\cite{Avakian:2015vha}.
+
+Our predictions will either be confirmed within the expected accuracy
+or will not not supported by data. In either case our work will provide
+a useful benchmark, and either call for dedicated theoretical 
+studies to explain either the pertinent $\bar{q}gq$--terms are 
+so small or why they are so sizable. In either case our results will 
+deepen the understanding of  $\bar{q}gq$--correlations, \ps{pave the 
+way towards testing} the validity of the TMD factorization approach 
+at subleading twist, and help us to guide further developments.
+
+In this work, after introducing the SIDIS process and defining TMDs and 
+FFs (Sec.~\ref{Sec-2:SIDIS+TMDs+FF}), we shall introduce the WW(-type) 
 approximations, and review what is presently known about them 
@@
 conclude with a critical discussion (Sec.~\ref{Sec-8:conclusions}).
-
-This is the first study of all SIDIS structure functions up to twist-3 
-in a unique approach. Our results are of importance for experiments prepared 
-in the near-term at \ps{Jefferson Lab (JLab) with 12$\,$GeV beam energy
-upgrade and COMPASS} or proposed in the long-term  
-(Electron Ion Collider), and provide helpful input for Monte Carlo event
-generators \cite{Avakian:2015vha}.
-
-Our predictions will either be confirmed within the expected accuracy
-\ps{or not supported by data. This will call for dedicated theoretical 
-studies to explain either why the pertinent $\bar{q}gq$--terms are 
-so small or so sizable. In either case our results will deepen the 
-understanding of  $\bar{q}gq$--correlations and help to guide 
-further developments.}
-
-All results of this projects are publicly available via open source \texttt{github.com}\footnote{\href{https://github.com/prokudin/WW-SIDIS}{https://github.com/prokudin/WW-SIDIS}} in the form of a \texttt{mathematica}~\cite{Mathematica} package.
-A dedicated \texttt{Python} package will be released in the future.
-Details about implementation and description of the package can be found in Appendix~\ref{app:package}.
+The Appendices \ref{App:basis} and \ref{App:factor} contain 
+technical details. \ps{In App.~C we describe an open source 
+package publicly available on \texttt{github.com}\footnote{\href{%
+	https://github.com/prokudin/WW-SIDIS}{
+	https://github.com/prokudin/WW-SIDIS}} 
+	inplemented in \texttt{mathematica}~\cite{Mathematica} 
+	(already available) and \texttt{Python} 
+	(to be released in near future).}
 
@@
 %------ BEGIN FIGURE 1: Kinematics of SIDIS ---------------------------
-\begin{wrapfigure}[8]{RD}{8cm}
+\begin{wrapfigure}[9]{RD}{8cm}
 \vspace{-7mm}
 \centering
-	\includegraphics[width=7.2cm]{\FigPath/Fig02a-kin-SIDIS-UT}
+	\includegraphics[width=7.2cm]{\FigPath/Fig02a-kin-SIDIS-UT-NEW.pdf}
         \caption{\label{fig-kin-SIDIS}
@@
 
-The SIDIS process is sketched in 
+The SIDIS process  $lN\to l^\prime h X$ is sketched in 
 Fig.~\ref{fig-kin-SIDIS}. Here $l$ and $P$ are momenta of incoming 
 lepton and nucleon, and $l^\prime$ and $P_h$ are the momenta of the outgoing
-electron and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
+lepton and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
 selects a z-axis, and $l^\prime$ points in the direction of the x-axis 
@@
 \label{eq:xyz}\;\;\;\;\ea
+Note that we consider the production of unpolarized hadrons in DIS of 
+charged leptons (electrons, positrons, muons) at $Q^2 \ll M_Z^2$ 
+in the single photon exchange approximation.
 In addition to $x$, $y$, $z$ the cross section is also differential 
@@
 azimuthal angle $\psi_l$ characterizing the overall orientation of the 
-lepton scattering plane in a fixed lab frame.
-\ps{By analyzing the data in the reference frame in Fig.~\ref{fig-kin-SIDIS}
-all events are by definition in the ``bin'' $\psi_l=0$ (within detector
-resolution) and the variable $\psi_l$ is practically integrated out leaving 
-us with a 5-dimensional cross section. Below we keep the cross section 
-``differential'' in $\psi_l$ for symbolic reasons.} 
+lepton scattering plane in a fixed lab frame. \ak{The origin of this 
+angle can be chosen arbitrarily. For a transversely polarized target 
+it is convenient to choose the origin of the angle $\psi_l$ in the 
+direction of $\vec{S}_T$.}
 It is convenient to define the unpolarized 
@@
 \ba\label{Eq:sigma0-FUU}
-	% \sigma_0 \equiv 
 	\frac{d \hat{\sigma}}{dy} 
@@
 and a structure function (sometimes denoted as $F_{UU,L}$) arising from
-longitudinal polarization of the virtual photon (and analog for the 
+longitudinal polarization of the virtual photon (and analogous for the 
 structure function $\propto S_T\,\sin( \phi_h-\phi_S)$, see below).
@@
 
-\ps{In the partonic description the structure functions in 
+In the partonic description the structure functions in 
 (\ref{Eq:SIDIS-leading})    are ``twist-2.'' Those in
@@
 contributing to the $\sin(\phi_h-\phi_S)$ angular distribution 
-\cite{Bacchetta:2006tn}.}
+\cite{Bacchetta:2006tn}.
 
@@
 \ea\end{subequations}
-where (and analog for the other structure functions)
+where (and analogous for the other structure functions)
 \be\label{Eq:FUU-integrated}
@@
 where $\gamma=2M_Nx/Q$ signals the twist-3 character of $F_{LT}^{\cos\phi_S}(x,z)$.
-\ps{As we consequently neglect $1/Q^2$ effects, the twist-4 DIS structure 
-function $F_2(x)$ does not appear in (\ref{Eq:DIS-F1}).}
-$F_{UT}^{\sin\phi_S}(x,z)$ has no DIS 
-counterpart due to time reversal symmetry of strong interactions.
+Notice that $F_{UT}^{\sin\phi_S}(x,z)$ has no DIS counterpart due to time reversal
+symmetry of strong interactions, and \ak{terms suppressed by $1/Q^2$ are 
+consequently neglected troughout this work including the twist-4 DIS 
+structure function $F_L(x)$. }
 
@@
 	\ee
-where the % symbolic 
-Wilson-lines refer to the SIDIS process 
+where the Wilson-lines refer to the SIDIS process 
 \cite{Collins:2002kn}. For a generic four-vector $a^\mu$ we define
@@
 
-The 8 leading--twist TMDs \cite{Boer:1997nt} are 
-projected out from the correlator (\ref{Eq:correlator}) as follows
-(\blue{blue: 
-%(online only): 
-T-even}, \red{red:  
-%(online only): 
-T-odd};
- we suppress flavor and renormalization scale dependence)
+The 8 leading--twist TMDs \cite{Boer:1997nt} are projected out from 
+the correlator (\ref{Eq:correlator}) as follows (\blue{blue: T-even} TMDs, 
+\red{red: T-odd} TMDs; all TMDs depend on $x$, $k_\perp$, renormalization 
+scale and carry a flavor index which we do not indicate for brevity)
 \begin{subequations}\ba
@@
 \ea\end{subequations}
-Here besides scale and flavor dependence we also do not indicate
-the type of hadron $h$. Integration over transverse hadron momenta leaves
-us with $D_1(z)$, $E(z)$, $H(z)$ while the other structures drop out due to 
-their $\pperp$ dependence.
+The FFs depend on $z$, $P_\perp$, renormalization scale, quark flavor and 
+type of hadron which we do not indicate for brevity.
+Integration over transverse hadron momenta leaves us with $D_1(z)$, $E(z)$, 
+$H(z)$ while the other structures drop out due to their $\pperp$ dependence.
 
@@
    	+ r_h^{ }\,\, h_1^{\perp } \,\frac{\tilde{E}}{z} \biggr)\biggr]\;
-	\label{FLUsinphi}\\
+	\label{FLUsinphi}\;\;\;\;\;\\
 	F_{UL}^{\sin\phi_h} 
@@
    	+  r_h^{ }\,\,h_{1L}^{\perp } \frac{\tilde{E}}{z}\biggr)\biggr]
-	\label{FLLcosphi}\;\;\;\;\\
+	\label{FLLcosphi}\;\;\;\;\;\;\;\;\;\\
 	F_{UT}^{\sin \phi_S } 
@@
    	\biggl( x   f_T^{\perp } D_1
-   	- r_h^{ }\, \, h_{1T}^{\perp }  \frac{\tilde{H}}{z}\biggr) \biggr]
-\ea
-\ba
+   	- r_h^{ }\, \, h_{1T}^{\perp }  \frac{\tilde{H}}{z}\biggr) \biggr]\\
 	F_{LT}^{\cos(2\phi_h - \phi_S)} 
@@
 where $r_h = m_h/M_N$ and 
-$F_{XY}^{\rm weight}\equiv F_{XY}^{\rm weight}(x,z,\Phperp)$.
-The weight functions are defined as
+$F_{XY}^{\rm weight}\equiv F_{XY}^{\rm weight}(x,z,\Phperp)$. \ms{The 
+tilde-functions $\tilde{D}^{\perp },\,\tilde{G}^{\perp },\,\tilde{H},\,\tilde{E}$
+are defined in terms of $\bar{q}gq$-correlators, see 
+Sec.~\ref{Sec-3.2:WW-type-TMD-FF}.} The weight functions are defined as
 \ba
@@
 Eqs.~(\ref{Eq:FUUcosphi}--\ref{FLTsin(2phi-phiS)}) contain an explicit 
-factor $M/Q$. \ps{We also recall that we neglect two structure 
-functions, $F_{UU,L}$ and $F_{UT,L}^{\sin( \phi_h-\phi_S)}$ in the
-notation of \cite{Bacchetta:2006tn}, due to longitudinal virtual photon 
-polarization which are of order ${\cal O}(M^2/Q^2)$ in the TMD 
-factorization approach.}
+factor $M/Q$. We also recall that we neglect two structure functions
+(denoted in  \cite{Bacchetta:2006tn} 
+as $F_{UU,L}$ and $F_{UT,L}^{\sin( \phi_h-\phi_S)}$) 
+due to longitudinal virtual photon polarization which are 
+of order ${\cal O}(M^2/Q^2)$ in the TMD partonic description.
 
@@
 \ea\end{subequations}
-Having established the notation we now define and discuss the
-approximations.
-
+
+Before introducing the WW-type approximations in the next section, 
+\ms{we would like to add a comment on TMD factorization: the 
+partonic description of the leading-twist structure functions in 
+(\ref{Eqs:structure-functions-twist-2}) is based on factorization 
+theorems \cite{Collins:1981uk,Ji:2004wu,Ji:2004xq,Collins:2011zzd,
+Echevarria:2012js}. In contrast to this, the partonic description 
+of the subleading-twist structure functions in 
+(\ref{Eqs:structure-functions-twist-3}) is based on the
+{\it assumption} that that SIDIS cross section factorizes.
+
+In fact, a lot of progress has been achieved in recent years in the 
+theoretical understanding of leading twist observables within the TMD 
+framework --- including definition, renormalization and evolution of 
+leading-twist TMDs \cite{Aybat:2011zv,Aybat:2011ge,Echevarria:2014xaa},
+NLO corrections within the TMD framework \cite{Ma:2013aca}, and  
+phenomenological fits with evolution \cite{Aybat:2011ta,Kang:2015msa}.
+In contrast to this, the theory for subleading-twist TMD observables is 
+only pourly developed. Still to the present day, the state-of-the-art 
+approach to subleading twist TMD observables is the one of 
+Refs.~\cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,
+Bacchetta:2006tn}, 
+based on a TMD tree-level formalism which we adopt here.
+In fact, the results of Refs.~\cite{Metz:2004je,Gamberg:2006ru}
+indicate doubts even in the tree-level formalism. 
+Recently, an attempt was made to remedy these doubts \cite{Chen:2016hgw}.
+Keeping in mind these ``words of warning,'' still the formulas 
+(\ref{Eqs:structure-functions-twist-3}) 
+are the best that theory has to offer currently. We may consider 
+(\ref{Eqs:structure-functions-twist-3}) as a model itself for 
+the twist-3 SIDIS observables. We hope that the phenomenological 
+approach based on WW-type approximations pursued in this work might 
+lead to more insight into these observables, and eventually might 
+trigger more theory efforts in the future.
+}
+
+%\newpage
 %======= SECTION 3: WW APPROXIMATIONS ================================
@@
 and $\bar{q}gq$--terms and assumes that the latter can be neglected 
-with respect to the leading $\bar{q}q$--terms with a useful accuracy,
+with respect to the leading $\bar{q}q$--terms with a useful accuracy
+(here the $\la\dots\ra$ denote symbolically the matrix elements 
+which enter the definitions of TMDs or FFs)
 \be\label{Eq:WW-generic}
@@
 of QCD equations of motion in twist-2 parts, and pure twist-3 
-(interaction dependent) $\bar qgq$--terms and current quark mass
-terms. We denote $\bar qgq$--terms and mass-terms collectively 
+(interaction dependent) $\bar{q}gq$--terms and current quark mass
+terms. We denote $\bar{q}gq$--terms and mass-terms collectively 
 and symbolically by functions with a tilde.
@@
 Rather they are classified according to the ``working definition'' 
-\cite{Jaffe:1996zw}  
-(a function is ``twist $t$'' if it contributes to cross sections
-suppressed by $(M/Q)^{t-2}$ with $M$ a generic hadronic and $Q$ the 
-hard scale).
+of twist \cite{Jaffe:1996zw}
+(a function is ``twist $t$'' if, in addition to overall kinematic
+prefactors, it contributes to cross sections in a partonic 
+description suppressed by $(M/Q)^{t-2}$ where $M$ is a generic 
+hadronic and $Q$ the hard scale).
 The two definitions coincide for twist-2 quantities, but higher twist
@@
 to cancel a $\delta(x)$--type singularity \cite{Efremov:2002qh}.
-After introducing the WW-type approximations for TMDs and FFs,
-we will come back to (\ref{Eq:WW-original1},~\ref{Eq:WW-original2}) and 
-review the theoretical predictions and experimental data supporting them.
+
+\ms{The relations (\ref{Eq:WW-original1}--\ref{Eq:WW-original-e})
+have been derived basically using operator product expansion
+techniques \cite{Wandzura:1977qf,Jaffe:1991ra}. Notice that the 
+operators defining $g_T^a$ and and $h_L^a$ can also be decomposed 
+within the TMD framework by means of a combination of relations 
+derived from the QCD equations of motion and further 
+constraint relations, called Lorentz-Invariance Relations (LIRs), 
+(see recent review \cite{Kanazawa:2015ajw} and references therein) 
+into a twist-2 part, and dynamical twist-3 (interactions dependent) 
+$\bar{q}gq$-terms and current quark mass terms.}
+
+We will come back to (\ref{Eq:WW-original1},~\ref{Eq:WW-original2}) and 
+review the theoretical predictions and supporting experiments, but before
+we will introduce the WW-type approximations for TMDs and FFs.
 
@@
 
-Analog to WW approximations for PDFs discussed in 
+Analogous to WW approximations for PDFs discussed in 
 Sec.~\ref{Sec-3.1:WW-classic}, also certain TMDs and FFs
@@
 The latter may be assumed, in the spirit of (\ref{Eq:WW-generic}),
-to be small. Hereby it is important to keep in mind that one deals 
-with different types of (``unintegrated'') $\bar qgq$--correlations,
+to be small. Hereby it is important to keep in mind that for each TMD
+or FF one deals 
+with different types of (``unintegrated'') $\bar{q}gq$--correlations,
 and we prefer to refer to them as WW-type approximations.
@@
 xh^q(x,\kperp^2)           	&\stackrel{\rm WW-type}{\approx}& 
-                       	- 2\,{h_1^{\perp(1)}(x,\kperp^2)},\phantom{\frac11 XXXXx} 
+                       	- 2\,{h_1^{\perp(1)}(x,\kperp^2)}.\phantom{\frac11 XXXXx} 
                        	\label{Eq:WW-type-last} 
 \ea\end{subequations}
-where the superscript ``(1)'' denotes transverse 
+The superscript ``(1)'' denotes the first transverse 
 moments of TMDs defined generically as  
@@
 WW-type approximations (\ref{Eq:WW-type-gT},~\ref{Eq:WW-type-6}).
-This yields \cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv}
+This yields \cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv}%
 \begin{subequations}\ba
@@
 \ea\end{subequations}
-Aspects and phenomenological applications of some of the above
-WW-type approximations were discussed in 
+Some of the above WW-type approximations were discussed in 
 \cite{Tangerman:1994bb,Kotzinian:1995cz,Mulders:1995dh,Kotzinian:1997wt,
 Kotzinian:2006dw,Avakian:2007mv,Metz:2008ib,Teckentrup:2009tk}.
-
 WW-relations for FFs are actually not needed: in Eqs.~%
@@
 in the following what is currently known from theory and experiment 
-about our approximations.
+about the WW(-type) approximations.
 
@@
 by no means obvious which small parameter in the strong interaction 
-regime would allow one to explain such results 	.
-
-A powerful non-perturbative approach is provided by the instanton model 
-of the QCD vacuum \cite{Shuryak:1981ff,Diakonov:1983hh,Diakonov:1995qy}.
+regime would allow one to explain such results. An appeling 
+non-perturbative approach is provided by the instanton model of 
+the QCD vacuum \cite{Shuryak:1981ff,Diakonov:1983hh,Diakonov:1995qy}.
 This semi-classical approach assumes that properties of the QCD vacuum 
@@
 breaking, the dominant feature of strong interactions in the nonperturbative
-regime. It was shown with variational and numerical methods that the strongly
-interacting instanton medium is dilute. The ratio of average instanton size 
-$\rho_{\rm av}$ and average instanton separation $R_{\rm av}$ is a non-trivial
-small parameter, numerically $\rho_{\rm av}/R_{\rm av}\sim1/3$ 
-\cite{Shuryak:1981ff,Diakonov:1983hh,Diakonov:1995qy}, 
-which can be explored.
+regime. It was shown with variational and numerical methods that the 
+instantons form a dilute medium characterized by a non-trivial small paramater
+$\rho/R\sim1/3$ \cite{Shuryak:1981ff,Diakonov:1983hh,Diakonov:1995qy}
+where $\rho$ and $R$ denote respectively the average instanton size $\rho$
+and separation $R$.
 
 Applying the instanton vacuum model to studies of $g_T^a(x)$ and $h_L^a(x)$
-it was predicted that matrix elements of the $\bar qgq$ operators defining 
+it was predicted that matrix elements of the $\bar{q}gq$ operators defining 
 $\tilde{g}_T^a(x)$ \cite{Balla:1997hf} and $\tilde{h}_L^a(x)$ 
 \cite{Dressler:1999hc} are strongly suppressed by powers of the small
-parameter $\rho_{\rm av}/R_{\rm av}$ with respect to contributions from the 
-respective twist-2 parts which are of the order $(\rho_{\rm av}/R_{\rm av})^0$. 
-Numerically it was found 
+parameter $\rho/R$ with respect to contributions from the 
+respective twist-2 parts which are of order $(\rho/R)^0$. 
+For Mellin moments it was found \cite{Balla:1997hf,Dressler:1999hc}
 \be\label{Eq:WW-instanoton}
-	\biggl|\frac{\la\bar{q}gq\ra}{\la\bar{q}q\ra}\biggr| \sim 
+	\frac{\tilde{g}_T^q}{g_T^q} \sim \frac{\tilde{h}_L^q}{h_L^q} 
+	\sim \frac{\la\bar{q}gq\ra}{\la\bar{q}q\ra} \sim 
 	\biggl(\frac{\rho}{R}\biggr)^{\!4} \log\biggl(\frac{\rho}{R}\biggr)
@@
 \ee
-in these 2 cases. This result strongly supports the generic approximation
+which strongly supports the generic approximation
 in Eq.~(\ref{Eq:WW-generic}) with the instanton packing fraction providing 
 the non-trivial small parameter justifying the neglect of tilde-terms. 
+The predictions for $\tilde{g}_T^a(x)$ \cite{Balla:1997hf}
+were made before the advent of the first precise data on $g_2(x)$
+which we discuss next.
 The instanton calculus has not yet been applied to $\tilde{e}^a(x)$.
 
-Noteworthy, the instanton vacuum predictions for $\tilde{g}_T^a(x)$
-\cite{Balla:1997hf}
-were made before the advent of the first precise data on $g_2(x)$
-which we discuss in the next section.
-
-\newpage
+%\newpage
 \subsection{Tests of WW approximation in DIS experiments}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
+\begin{figure}[t!]
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/g2.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/g2-HERMES.pdf} 
+\includegraphics[width=0.48\textwidth]{\FigPath/g2.pdf} 
+\includegraphics[width=0.48\textwidth]{\FigPath/g2-HERMES.pdf} 
 \caption{\label{Fig:g2} 
@@
 Eq.~(\ref{Eq:g2-in-WW-approximation}), for proton (P) and neutron (N) targets. 
-Left panel: data from E144 and E155 experiments at $\la Q^2\ra=7.1\,{\rm GeV}^2$ \cite{Anthony:2002hy,Abe:1998wq}. Right panel: HERMES data 
-at $\la Q^2\ra=2.4\,{\rm GeV}^2$ \cite{Airapetian:2011wu}.
+Left panel: data from E144 and E155 experiments at 
+$\la Q^2\ra=7.1\,{\rm GeV}^2$ \cite{Anthony:2002hy,Abe:1998wq}. 
+Right panel: HERMES data \ps{for $Q^2>1\,{\rm GeV}^2$ with}
+$\la Q^2\ra=2.4\,{\rm GeV}^2$ \cite{Airapetian:2011wu}.
 The estimate of the theoretical uncertainty is described in the text.}
@@
 
-We present calculations of $g_2(x)_{WW}$ in Fig.~\ref{Fig:g2}.
-How well does the WW approximation describe data if we allow for a
-theoretical ``uncertainty band'' of about $40\,\%$ as deduced in Ref.~\cite{Accardi:2009au}? To investigate this question, 
-we split this uncertainty in two parts, $\varepsilon_1=\pm 20\,\%$ and 
+We present calculations of $g_2(x)_{\rm WW}$ in Fig.~\ref{Fig:g2}.
+\ps{This result is obtained using the LO $g_1^a(x)$-parametrization 
+\cite{Gluck:1998xa}. In order to display the theoretical ``uncertainty 
+band'' of this WW-approximation of about $40\,\%$ as deduced in 
+Ref.~\cite{Accardi:2009au} we proceed as follows: we split the 
+$40\,\%$ uncertainty} in two parts, $\varepsilon_1=\pm 20\,\%$ and 
 $\varepsilon_2(x)=\pm 20\,\%(1-x)^\epsilon$ with a small $\epsilon>0$,
@@
 uncertainties. 
-We conclude that the WW--approximation works reasonably well
-possibly except for very small $x$ at HERMES, see Fig.~\ref{Fig:g2}.
+We conclude that the WW--approximation works reasonably well, 
+see Fig.~\ref{Fig:g2}.
 
@@
 For the time being, we content ourselves with rather crude comparisons 
-based on the data published in Refs.~\cite{Hagler:2009mb,Musch:2010ka}. 
+based on the \ak{lattice data}
+published in Refs.~\cite{Hagler:2009mb,Musch:2010ka}. 
 These early works explored all nucleon and quark polarizations, but 
@@
 Before quoting numbers, a few more comments are in order. The overall 
-multiplicative renormalization in Ref.~\cite{Musch:2010ka} was fixed by setting the Gaussian 
-integral $c_{2,u-d}$ of the unpolarized TMD $f_1$ in the isovector channel 
-(u-d) to the nucleon quark content, namely, to 1. 
-One then assumes that the normalization of the lattice results for the unpolarized TMD $f_1$
-also fixes the normalization for polarized quantities correctly. 
-This assumption holds if renormalization is mutliplicative and flavor-independent 
-for the non-local lattice operators. This is not true for all lattice actions
-\cite{Yoon:2017qzo} %PhysRevD.96.094508
-but presumably it is true if the lattice action preserves chiral symmetry, as it does in the present case.
+multiplicative renormalization in Ref.~\cite{Musch:2010ka} was fixed by 
+setting the Gaussian integral $c_{2,u-d}$ of the unpolarized TMD $f_1$ 
+in the isovector channel (u-d) to the nucleon quark content, namely, to 1.
+ One then assumes that the normalization of the lattice results for the 
+unpolarized TMD $f_1$ also fixes the normalization for polarized quantities 
+correctly. This assumption holds if renormalization is multiplicative and 
+flavor-independent for the non-local lattice operators. This is not true 
+for all lattice actions \cite{Yoon:2017qzo} %PhysRevD.96.094508
+but presumably it is true if the lattice action preserves chiral symmetry, 
+as it does in the present case.
 The Gaussian fits along with the normalization prescription serve as
@@
 Ref.~\cite{Musch:2010ka} employs a subtraction scheme on the lattice
-but establishes no connection with a subtraction scheme designed for experimental TMDs and 
-the corresponding gauge link geometry. The gauge link renormalization mainly 
+but establishes no connection with a subtraction scheme designed for 
+experimental TMDs and the corresponding gauge link geometry. 
+The gauge link renormalization mainly 
 influences the width of the Gaussian fits; the amplitudes are only slightly 
@@
 somewhat heavier pions and nucleons. All that matters in our
-context is that the relative size of $\bar qgq$--matrix elements
-is small with respect to $\bar qq$--matrix elements.
-% (Other lattice artifacts, such as finite lattice spacing and
-% finite volume effects could potentially play a role, but in the
-% context of TMDs such effects are presently beyond systematic control,
-% and we assume the associated uncertainties to be not larger than
-% the statistical error bars of the lattice data.)
+context is that the relative size of $\bar{q}gq$--matrix elements
+is small with respect to $\bar{q}q$--matrix elements.
 
@@
 (\ref{Eq:WW-original1},~\ref{Eq:WW-original2}), which corresponds to the
-Burkardt-Cottingham sum rule for $g_T^a(x)$ and an analog sum rule for
+Burkardt-Cottingham sum rule for $g_T^a(x)$ and an analogous sum rule for
 $h_L^a(x)$, see \cite{Jaffe:1996zw} and references there in.
@@
 degrees of freedom certain relations among TMDs hold, the 
-so-called quark model Lorentz-invariance relations (qLIRs).
-%\cite{Metz:2008ib,Teckentrup:2009tk}. 
+so-called quark model Lorentz-invariance relations (qLIRs)
+\cite{Tangerman:1994bb,Mulders:1995dh}.\footnote{\ms{Notice that
+	the qLIRs of \cite{Tangerman:1994bb,Mulders:1995dh} are 
+	valid only in quark models with no gluons and should not
+	be confused with the LIRs of \cite{Kanazawa:2015ajw} which 
+	are exact relations in QCD, see Sec.~\ref{Sec-3.1:WW-classic}.
+	In literature both are often simply referred to as LIRs.
+	This ambiguity is unfortunate.}}
 Initially thought to be exact \cite{Tangerman:1994bb,Mulders:1995dh}
-qLIRs were shown in models with gluons \cite{Kundu:2001pk,Schlegel:2004rg} 
-and in QCD \cite{Goeke:2003az} to be invalid.
+qLIRs were shown  to be invalid in models with gluons 
+\cite{Kundu:2001pk,Schlegel:2004rg} and in QCD \cite{Goeke:2003az}.
 They originate from decomposing the (completely unintegrated)
@@
 In the covariant parton model with intrinsic 3D-symmetric parton 
-orbital motion \cite{Zavada:1996kp}  quarks are free, $\bar qgq$ 
+orbital motion \cite{Zavada:1996kp}  quarks are free, $\bar{q}gq$ 
 correlations absent, and all WW and WW-type relations exact
@@
 The phenomenological success of this approach \cite{Zavada:1996kp} may 
-hint at a general smallness of $\bar qgq$ terms, although many of the 
+hint at a general smallness of $\bar{q}gq$ terms, although many of the 
 predictions from this model have yet to be tested \cite{Efremov:2010mt}.
 
-\ps{Noteworthy is the result from the chiral quark soliton
+Noteworthy is the result from the chiral quark soliton
 model where the WW-type approximation (\ref{Eq:WW-type-Cahn})
@@
 becomes exact at the low initial scale of this model of 
-$\mu_0\sim 0.6\,{\rm GeV}$.}
+$\mu_0\sim 0.6\,{\rm GeV}$.
 
@@
 dynamical reasons for the smallness of the {\sl matrix elements} of
-$\bar qgq$--operators. This requires the consideration of chiral symmetry 
+$\bar{q}gq$--operators. This requires the consideration of chiral symmetry 
 breaking effects reflected in the hadronic spectrum, as considered in the
@@
 
+%\newpage
 \subsection{Basis functions for the WW-type approximations}
@@
 Below we shall see that, under the assumption of the validity of WW-type 
-approximations, it is possible to express all SIDIS structure
+approximations, it is possible to express all SIDIS structure functions
 in terms of the basis functions. 
@@
 
-These basis functions allow us to describe in WW-type approximation all other 
-TMDs, and experiments will decide how well the approximations work.
+These basis functions allow us to describe, in WW-type approximation,
+all other TMDs. The experiment will tell us how well the approximations work.
 In some cases, however, we know in advance that the WW-type approximations 
@@
 
-\subsection{Limitation of WW-type approximation for certain T-odd TMDs}
+\subsection{Limitation of WW-type approximation}
 \label{Sec-3.8:limitations}
 
-The WW-type approximations have limitations in the description of 
-those twist-3 T-odd TMDs which appear in the decomposition of the 
+\ps{The approximation may work in the case when: TMD or FF 
+$=\la\bar{q}q\ra + \la\bar{q}gq\ra \approx \la\bar{q}q\ra \neq 0$ with 
+a ``controlled approximation'' in the spirit of Eq.~(\ref{Eq:WW-generic}).
+We know cases where this works, see
+Secs.~\ref{Sec-3.3:WW-classic-instanton}, \ref{Sec-3.4:WW-classic-experiment},
+but it has to be checked case by case whether
+$| \la\bar{q}gq\ra  | \ll  |\la\bar{q}q\ra|$ for a given operator.
+At least in such cases the approximation has a chance to work.
+
+However, it may happen that after applying the QCD equations
+of motion one ends up in the situation that: a given function 
+$=\la\bar{q}q\ra + \la\bar{q}gq\ra$ with $\la\bar{q}q\ra = 0$.
+This happens for the T-even TMD 
+	$e^a$ in Eqs.~(\ref{Eq:WW-original-e},~\ref{Eq:WW-type-1}), 
+for the T-odd TMDs 
+	$e_L^q$, 
+	$e_T^q$,
+	$e_T^{\perp q}$, 
+	$f_L^{\perp q}$,
+	$g^{\perp q}$ in Eqs.~(\ref{Eq:WW-type-eLperp}--\ref{Eq:WW-type-fLperp}), 
+and for the FFs
+	$E^q$, 
+	$G^{\perp q}$ in Eqs.~(\ref{Eq:WW-type-FF-1},~\ref{Eq:WW-type-FF-2})
+(actually, all twist-3 FFs are affected, we will discuss this in detail below). 
+In this situation the ``leading term'' is absent, so neglecting the 
+``subleading (pure twist-3) term'' actually constitutes an error of $100\,\%$
+even if the neglected matrix element  $\la\bar{q}gq\ra$ is very small.
+Notice that this type occurs for all subleading twist FFs, which enter 
+SIDIS structure functions only in the shape of tilde-FFs, see 
+Sec.~\ref{Sec-2:SIDIS+TMDs+FF} and 
+Eqs.~(\ref{Eqs:structure-functions-twist-3}). 
+We shall see that some structure functions are potentially more and 
+others potentially less affected by this generic limitation. In any 
+case phenomenological work has to be carried out to find out whether 
+or not the approximation works.
+
+For both FFs and TMDs there are also limitations 
+which go beyond this generic issue. To illustrate this for FFs
+we recall that} that both $H_1^{\perp(1)q}$ and $\tilde H_1^{q}$ are 
+related to integrals of an underlying function $H_{FU}^{q,\Im}(z,z_1)$
+as pointed out in Ref.~\cite{Kanazawa:2015ajw}. Therefore, if one 
+literally assumed $\tilde H^q(z)$ to be zero, this would imply that 
+also $H_1^{\perp(1)q}$ would vanish, indicating that the WW-type 
+approximation has to be used with care in the chiral-odd FF sector.
+
+Similar limitations exist also for TMDs. This is manifest in particular 
+for those twist-3 T-odd TMDs which appear in the decomposition of the 
 correlator (\ref{Eq:correlator}) with no prefactor of $\kperp$.
@@
 The situation for the chirally and T-odd twist-3 
-TMD $h^a(x,k_\perp)$ is analog. The third 
+TMD $h^a(x,k_\perp)$ is analogous. The third 
 function in (\ref{Eq:sum-rules-T-odd}) causes no issues since 
@@
 
-Does this mean WW-type approximations fail for $f_T^a(x,k_\perp)$ 
-and $h^a(x,k_\perp)$? Not necessarily. One has to keep in mind
-the formal character of the sum rules (\ref{Eq:sum-rules-T-odd})
-which include integration in the large-$k_\perp$ region where the TMD 
-description does not apply. Thus, issues with the sum rules 
+Does it mean WW-type approximations fail for $f_T^a(x,k_\perp)$ 
+and $h^a(x,k_\perp)$? Not necessarily. \ms{The approximations may
+work in some but not all regions of $\kperp$, but the sum rules 
+(\ref{Eq:sum-rules-T-odd}) include integration over all $k_\perp$. 
+Notice also that e.g.\ $f_{1T}^{\perp (1),q}(x)$ is related to the 
+soft-gluon-pole matrix element $F_{FT}(x,x)$ \cite{Boer:2003cm,Ji:2006ub}
+which is a $\bar{q}gq$-term that one would naturally neglect 
+in WW-type approximation.
+In this sense (\ref{Eq:WW-type-fT}) could be consistent.}
+Thus, issues with the sum rules 
 (\ref{Eq:sum-rules-T-odd}) do not need to exclude the
@@
 
+\newpage
 \subsection{Subleading structure functions in WW-type approximations}
@@
 	{g_T^{\perp a}\to g_1^a}
-	{Eqs.~(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T}),}
-\ea
-\ba
+	{Eqs.~(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T}),}\\
 F_{UL}^{\sin\phi_h} &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,{\cal C}\biggl[
@@
 
-\ps{
-
-\subsection{Gaussian Ansatz for TMDs}
+\subsection{Gaussian Ansatz for TMDs and FFs}
 \label{Sec-4.3:evaluation}
@@
 are numerically within the accuracy expected for this approach.
-\red{However, for the structure functions discussed in
+However, for the structure functions discussed in
 Secs.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi}
@@
 this in more detail in 
-Secs.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi}.}
+Secs.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi}.
 
@@
 terms of the basis TMDs or their adequate transverse moments.
-}
-
-\newpage
+
+\subsection{Phenomenological information on basis functions}
+\label{Sec-4.3:plot-basis-functions}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Phenomenological information on basis functions}
-\label{Sec-4.3:plot-basis-functions}
 
@@
 Ref.~\cite{deFlorian:2007aj}. The other four TMDs 
-\ps{have no collinear counterparts. 
+have no collinear counterparts. 
 For $f_{1T}^{\perp a},\;h_1^{\perp a},\;H_1^{\perp a}$ it is convenient to 
-consider their (1)-moments, and for $ h_{1T}^{\perp a}$  the (2)-moment.
+consider their (1)-moments, for $ h_{1T}^{\perp a}$  the (2)-moment,
+see Eq.~(\ref{eq:moments}) for definitions.
 This has two important advantages. First, this step simplifies 
@@
 models but is very cumbersome to define in QCD).
-Thus the parametrizations for the basis functions read}
+The parametrizations for the basis functions read
 \begin{subequations}\ba
@@
 
+%\newpage
 %======= SECTION 5: TWIST-2 AND BASIS FUNCTIONS ======================
@@
 is given by Eqs.~(\ref{Eq:Gauss-f1},~\ref{Eq:Gauss-D1}).
-The parameters $\avkperp_{f_1}$ and $\avpperp_{D_1}$ can
-be assumed to be flavor- and $x$-- or $z$--dependent, as present
-data do not allow us to constrain too many parameters, see
+The parameters $\avkperp_{f_1}$ and $\avpperp_{D_1}$ can be 
+assumed to be flavor- and $x$-- or $z$--independent, as present
+data hardly allow us to constrain too many parameters, see
 App.~\ref{App:basis-f1-D1} for a review. This assumption can be
-relaxed, e.g. theoretical studies in chiral effective field theories 
+relaxed, e.g.\ theoretical studies in chiral effective theories 
 predict a strong flavor-dependence in the $\kperp$--behavior
@@
 Figure~\ref{FUU-show-pT-dependence} illustrates how the Gaussian Ansatz
-describes selected SIDIS data:
-the left panel shows CLAS data \cite{Osipenko:2008aa} on $\pi^+$ production 
-from proton with a 5.75 GeV beam which exhibit Gaussian $P_{hT}$--dependence
-over 2 orders of magnitude, see \cite{Schweitzer:2010tt} for details.
-The middle panel in Fig.~\ref{FUU-show-pT-dependence} displays the 
+describes selected SIDIS data.
+
+\ps{Let us begin with JLab where, in the pre-12$\,$GeV era, electron beams 
+from CEBAF with energies in the range $4.3$ to $5.7$ GeV were scattered 
+off proton or deuterium targets in the typical kinematics 
+$1 \,{\rm GeV}^2 < Q^2 < 4.5 \,{\rm GeV}^2$, $W > 2\,{\rm Gev}$, 
+$0.1 < x < 0.6$, $y < 0.85$, $0.5<z<0.8$.
+The left panel of Fig.~\ref{FUU-show-pT-dependence} shows basically
+the SIDIS structure function $F_{UU}(P_{hT}^2)$ normalized with respect
+to its value at zero transverse hadron momentum\footnote{Strictly 
+	speaking in \cite{Osipenko:2008aa} data for the normalized 
+	SIDIS cross section was presented. But these data correspond 
+	to $F_{UU}(P_{hT}^2)/F_{UU}(0) \equiv
+	F_{UU}(\la x\ra,\la z\ra,P_{hT}^2)/F_{UU}(\la x\ra,\la z\ra,0)$
+	up to $1/Q^2$-suppressed terms.}
+for $\pi^+$ production from a proton target measured in the CLAS experiment 
+with a $5.75$ GeV beam for the kinematics $\la Q^2\ra=2.37\,{\rm GeV}^2$, 
+$\la x\ra=0.24$, $\la z\ra=0.30$ \cite{Osipenko:2008aa}. Clearly, the 
+Gaussian model works for the entire region of $P_{hT}$ covered in this 
+experiment where structure function $F_{UU}$ falls down by 2 orders of 
+magnitude \cite{Schweitzer:2010tt}.
+
+Next we discuss a representative plot from the HERMES experiment 
+where pions or kaons were measured in the scattering of 27.6 GeV 
+positrons from the HERA polarized positron storage ring at DESY 
+off proton and deuteron targets in the SIDIS kinematics 
+$Q^2 > 1 \,{\rm GeV}^2$, $W > 2\,{\rm Gev}$, 
+$0.023 < x < 0.4$, $y < 0.85$, $0.2<z<0.7$. 
+The middle panel of Fig.~\ref{FUU-show-pT-dependence} displays the 
 HERMES multiplicity~\cite{Airapetian:2012ki}
@@
 	M_n^h(x,z,\Phperp) \equiv 
+	\ak{\frac{d\sigma_{\rm SIDIS}(x,z,\Phperp)/dx\,dz\,d\Phperp}
+	{d\sigma_{\rm DIS}(x,z)/dx}} =
 	2 \pi \Phperp \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
@@
 at $\la Q^2\ra=2.87\,{\rm GeV}^2$, $\la x\ra=0.15$, $\la z\ra=0.22$ 
-for $\pi^+$ production on the proton target. The right panel of
+for $\pi^+$ production on the proton target \cite{Airapetian:2012ki}.
+
+Finally we show also a representative plot from the COMPASS experiment 
+where charged pions, kaons, or hadrons were measured with 160 GeV 
+longitudinally polarized muons scattered off proton and deuteron 
+targets in the typical SIDIS kinematics 
+$Q^2 > 1 \,{\rm GeV}^2$, $W > 5\,{\rm Gev}$, 
+$0.003 < x < 0.7$, $0.1<y < 0.9$, $0.2<z<1$. 
+The right panel of
 Fig.~\ref{FUU-show-pT-dependence} shows the COMPASS multiplicity 
@@
 \be\label{Eq:multiplicity-COMPASS}
-	n^h(x,z,\Phperp)  \equiv 
-	\pi \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
+	n^h(x,z,\Phperp^2)  \equiv 
+	\ak{\frac{d\sigma_{\rm SIDIS}(x,z,\Phperp^2)/dx\,dz\,d\Phperp^2}
+	{d\sigma_{\rm DIS}(x,z)/dx}} =
+	\pi \frac{F_{UU}(x,z,\Phperp^2) }{ x \sum_q e_q^2\,f^q_1(x)}\;
 \ee
 at $\la Q^2\ra=20\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.2$ 
-for $h^+$ production on the deuterium target.
+for $h^+$ production on the deuterium target \cite{Aghasyan:2017ctw}.}
 
@@
 
-%\newpage
+\ps{The description of the HERMES and COMPASS multiplicities in
+Fig.~\ref{FUU-show-pT-dependence} is good and sufficient for our
+purposes, but it is not perfect. The descriptions of the COMPASS 
+data in the region of small $\Phperp^2$ and that of the HERMES data 
+for $\Phperp \gtrsim 0.3\,{\rm GeV}$ are not ideal.
+However, notice that in our description we use the Gaussian widths 
+as fitted and employed in the original extractions of the TMDs. These 
+values were not optimised to fit the HERMES or COMPASS multiplicities.
+Keeping this in mind, the description in Fig.~\ref{FUU-show-pT-dependence}
+can be considered as satisfactory. We also remark that we do not take 
+into account $\kperp$-broadening effects between HERMES and 
+COMPASS energies. Through dedicated fits to the HERMES, COMPASS
+(and other) data and the consideration of $\kperp$-evolution effects
+it is possible to obtain a better description than shown in
+Fig.~\ref{FUU-show-pT-dependence}, see Ref.~\cite{Bacchetta:2017gcc}.}
+
+\newpage
 %========= SECTION 6: TESTING APPROACH WITH A_LL =====================
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure}[b]
 \centering 
-\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pip}  
-\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pi0}  
-\includegraphics[width=0.32\textwidth]{\FigPath/all_jlab_pim}  
+\includegraphics[width=0.3\textwidth]{\FigPath/all_jlab_pip}  
+\includegraphics[width=0.3\textwidth]{\FigPath/all_jlab_pi0}  
+\includegraphics[width=0.3\textwidth]{\FigPath/all_jlab_pim}  
 \caption{\label{jlab_ALL} 
@@
  	for $\pi^+$, $\pi^0$, $\pi^-$. The solid lines are 
-	our computations for the mean values of kinematical variable
+	our results for the mean values of kinematical variable
 	$\langle x \rangle = 0.25$, 
@@
 
-The first experimental results on the 
-$\Phperp$--dependence of $A_{LL} = F_{LL}/F_{UU}$ were presented by
-Jefferson Lab (JLab) \cite{Avakian:2010ae}. The definition of the asymmetry 
-in  \cite{Avakian:2010ae} was
+The definition of the asymmetry in  the JLab experiment \cite{Avakian:2010ae} 
+was
 \be\label{Eq:ALLy}
@@
 Therefore the comparison of our results to JLab data \cite{Avakian:2010ae} 
-shown in Fig.~\ref{jlab_ALL} provides several important tests.\footnote{
-	Another important test was already presented in 
-	\cite{Avakian:2010ae}: the $\Phperp$--integrated (``collinear'')
-	asymmetry (\ref{Eq:FLL}) is compatible with data
-	from other experiments and with theoretical results obtained from
-	parametrizations of $f_1^a(x)$, $g_1^a(x)$, $D_1^a(z)$. This 
-	shows that even at the moderate beam energies of the pre-12GeV 
-	era one was indeed probing DIS at JLab,
-	at least to a very good approximation \cite{Avakian:2010ae}.}
+shown in Fig.~\ref{jlab_ALL} provides several important tests.
 First, the JLab data \cite{Avakian:2010ae} are compatible
@@
 description of the data.
+	(Another important test was already presented in 
+	\cite{Avakian:2010ae}: the $\Phperp$--integrated (``collinear'')
+	asymmetry (\ref{Eq:FLL}) is compatible with data
+	from other experiments and theoretical results obtained from
+	parametrizations of $f_1^a(x)$, $g_1^a(x)$, $D_1^a(z)$. This 
+	shows that even at the moderate beam energies of the pre-12GeV 
+	era one was, to a good approximation, indeed probing DIS at JLab
+	\cite{Avakian:2010ae}.)
 
@@
 
-\newpage
 \subsection{\boldmath Leading twist $A_{UT}^{\sin(\phi_h-\phi_S)}$ Sivers asymmetry}
@@
 nucleon, and it generates a dipole deformation in momentum space.
-Over the years, the Sivers function has been extracted from SIDIS data
+The Sivers function has been extracted from SIDIS data
 by several groups, with consistent results 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_COMPASS_x.pdf}
+\caption{\label{aut_f1t_jlab} \ps{Sivers asymmetry 
+	$A_{UT}^{\sin(\phi_h-\phi_S)}$ from proton target as function of $ x $ 
+	based on the fit \cite{Anselmino:2011gs} in comparison to 
+	(left panel) HERMES \cite{Airapetian:2009ae}
+	% refer to the mean values
+	% $\la x\ra = 0.1$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ 
+	and (right panel) COMPASS data \cite{Adolph:2012sp}.}
+	\red{(Alexei: 
+	is it possible to add here the
+	labels ``HERMES'' and ``COMPASS''
+	on the plots?)}}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Notice that integrating structure functions over $\Phperp$
@@
 The asymmetries $A_{UT}^{\sin(\phi_h-\phi_S)}= F_{UT}^{\sin(\phi_h-\phi_S)}/F_{UU}$  
-\ps{are plotted in Fig.~\ref{aut_f1t_jlab} in comparison to HERMES data 
-on charged pion production from a proton target \cite{Airapetian:2009ae}.
-The $x$-- and $P_{hT}$--dependencies of the asymmetry are displayed. The 
-latter shows that the Gaussian model works well also in this case.
-COMPASS data are described equally well by the fit \cite{Anselmino:2011gs}. }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_PT.pdf}
-\caption{\label{aut_f1t_jlab} The Sivers asymmetry $A_{UT}^{\sin(\phi_h-\phi_S)}$  
-	as a function of $ x $ (left panel) and $P_{hT}$ (right panel).
-	The data are from the HERMES experiment and refer to the mean values
-	$\la x\ra = 0.1$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ 
-	\cite{Airapetian:2009ae}. The theoretical curves are based on 
-	the fit results of Ref.~\cite{Anselmino:2011gs}.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\ps{obtained from the fit \cite{Anselmino:2011gs}
+are plotted in Fig.~\ref{aut_f1t_jlab} as functions of $x$ in comparison 
+to HERMES \cite{Airapetian:2009ae} and COMPASS \cite{Adolph:2012sp} data 
+on respectively charged pion and hadron production from a proton target.
+The $P_{hT}$--dependencies of the data are equally well described which
+confirms that the Gaussian model works also in this case.}
 
@@
 The $F_{UT}^{\sin(\phi_h+\phi_S)}$ modulation of the SIDIS cross section is due 
-to the convolution of the transversity distribution $h_1$ \ps{and the Collins 
+to the convolution of the transversity distribution $h_1$ and the Collins 
 FF $H_1^\perp$. Transversity can in principle be accessed also as a PDF in
-Drell-Yan. It describes the distribution of transversely polarized quarks
-in a transversely polarized nucleon, and} is the only source of information 
+Drell-Yan \ps{or in dihadron production 
+\cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,Bacchetta:2012ty,
+Radici:2015mwa,Radici:2018iag}.}
+It describes the distribution of transversely polarized quarks
+in a transversely polarized nucleon, and is the only source of information 
 on the tensor charge of the nucleon. The Collins FF $H_1^\perp$ decodes the 
@@
 The asymmetries $A_{UT}^{\sin(\phi_h+\phi_S)}= F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$  
-\ps{are plotted in Fig.~\ref{aut_h1_jlab} in comparison to HERMES data 
-on charged pion production from a proton target \cite{Airapetian:2010ds}.
-Also in Fig.~\ref{aut_h1_jlab} we show the $x$-- and $P_{hT}$--dependencies 
-of this azimuthal spin asymmetry. The right panel of Fig.~\ref{aut_h1_jlab}
-on the $P_{hT}$--dependence shows that the data are compatible with the 
-Gaussian Ansatz. Let us remark that the COMPASS data are described equally 
-well by the fit of Ref.~\cite{Anselmino:2013vqa}.}
+are plotted in Fig.~\ref{aut_h1_jlab} as functions of $x$ in comparison 
+to HERMES \cite{Airapetian:2010ds} and COMPASS \cite{Adolph:2014zba} 
+data on charged pion production from proton targets.
+We remark that the description of the $P_{hT}$--dependencies of 
+this azimuthal spin asymmetry is equally satisfactory by the 
+fit of Ref.~\cite{Anselmino:2013vqa}, which implies that the 
+data are compatible with the Gaussian Ansatz also in this case.
 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_x.pdf}  
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_PT.pdf}
-\caption{\label{aut_h1_jlab} The Collins asymmetry $A_{UT}^{\sin(\phi_h+\phi_S)}$  
-	as a function of $ x $ (left panel) and $P_{hT}$ (right panel).
-	The data are from the HERMES experiment and refer to the mean values
-	$\la x\ra = 0.1$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ 
-	\cite{Airapetian:2010ds}. The theoretical curves are based on 
-	the fit results of Ref.~\cite{Anselmino:2013vqa}.}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_COMPASS_x.pdf}
+\caption{\label{aut_h1_jlab}  \ps{Collins asymmetry 
+	$A_{UT}^{\sin(\phi_h+\phi_S)}$ from proton target as function of $ x $ 
+	based on the fit \cite{Anselmino:2013vqa} in comparison to 
+	(left panel) HERMES \cite{Airapetian:2010ds}
+	% refer to the mean values
+	% $\la x\ra = 0.1$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ 
+	and (right panel) COMPASS data \cite{Adolph:2014zba} (where
+	$(-1)A_{UT}^{\sin(\phi_h+\phi_S)}$ is shown since for historical
+	reasons the COMPASS collaboration likes to analyze their data
+	with an opposite sign convention.)}
+	\red{(Alexei: 
+	is it possible to add here the
+	labels ``HERMES'' and ``COMPASS''
+	on the plots?)}}
 \end{figure}
@@
 
-The structure function $F_{UU}^{\cos(2\phi_h)}$ reads
+\ps{The structure function $F_{UU}^{\cos(2\phi_h)}$ arises from a convultion of
+the Collins fragmention function and the TMD $h_{1}^{\perp q}$ which describes
+the distribution of transversely polarized partons inside an unpolarized
+target. The expression of this structure function is given by}
 \begin{subequations}\ba
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_x.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_PT.pdf}
-\caption{\label{auu_cos2phi_jlab} Comparison of calculation of 
-	$A_{UU}^{\cos(2\phi_h)}$  using fit results of Ref.~\cite{Barone:2015ksa} 
-	as a function of $x$ (left panel), and as a function of $P_{hT}$ 
-	(right panel) at $\la x\ra = 0.15$, $\la z\ra = 0.34$, 
-	$\la Q^2\ra = 2.4$ GeV$^2$ and HERMES data \cite{Airapetian:2012yg}.
-}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_COMPASS_x.pdf}
+\caption{\label{auu_cos2phi_jlab} \ps{The asymmetry 
+	$A_{UU}^{\cos(2\phi_h)}$ from proton target as function of $ x $ 
+	based on the fit \cite{Barone:2015ksa} \red{[Alexei,
+	we changed the reference, is this the correct paper?]}
+	in comparison to (left panel) HERMES \cite{Airapetian:2012yg}
+	and (right panel) COMPASS data \cite{Adolph:2014pwc}.}
+	\red{(Alexei: 
+	is it possible to add here the
+	labels ``HERMES'' and ``COMPASS''
+	on the plots?)}}
 \end{figure}
@@
 
-Asymmetries $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$  for HERMES 
+Asymmetries $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$ for 
+HERMES \cite{Airapetian:2012yg} and COMPASS \cite{Adolph:2014pwc}
 are plotted in Fig.~\ref{auu_cos2phi_jlab} where we only considered the
@@
 
+\ps{The pretzelosity TMD $h_{1T}^{\perp q}$ is the least known of the basis 
+functions. It is of interest as it allows one to measure the deviation 
+of the nucleon spin density from spherical shape \cite{Miller:2007ae},
+is related to the only leading-twist SIDIS structure function where the 
+small-$P_{hT}$ description in terms of TMDs and the large-$P_{hT}$ expansion 
+in perturbative QCD mismatch \cite{Bacchetta:2008xw}, and is the only
+TMD where a clear relation to quark orbital angular momentum
+could be established (albeit only within quark models)
+\cite{Avakian:2008dz,She:2009jq,Avakian:2010br,Lorce:2011kn}.
+}
+
 The structure function $F_{UT}^{\sin(3\phi_h-\phi_S)}$ reads
@@
 see App.~\ref{App:convol-details}.
+\ps{In Eq.~(\ref{eq:asymmetry_aut_h1tp}) we see that this structure 
+function suffers a cubic suppression for small transverse hadron
+momenta. This is the strongest $P_{hT}$-suppression of all SIDIS 
+structure functions through leading and subleading twist, making
+it challenging to measure.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_x.pdf}  
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_PT.pdf}
+\caption{\label{aut_h1tp_jlab}  $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  
+	as a function of $ x $ (left panel) and $P_{hT}$ (right panel) 
+	at $\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 3.6$ GeV$^2$ 
+	on the basis of fits from \cite{Lefky:2014eia} 
+	vs preliminary COMPASS data \cite{Parsamyan:2010se}.
+	\red{\sf PRELIMINARY COMPASS DATA have disappeared from the plot!
+	(related to Alexei's ``illegal figure''?)
+	Bakur: can you produce the left panel of Fig.~18 as {\bf separate}
+	figure to show here? ALSO: I would propose to skip the $P_{hT}$-plot,
+	which does not give much insight.}}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_x.pdf}  
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_PT.pdf}
-\caption{\label{aut_h1tp_jlab}  $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  
-	as a function of $ x $ (left panel) and $P_{hT}$ (right panel) 
-	at $\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 3.6$ GeV$^2$ 
-	on the basis of fits from \cite{Lefky:2014eia} 
-	vs preliminary COMPASS data \cite{Parsamyan:2010se}.
+\ps{
+
+\subsection{Statistical and systematic uncertainties of basis functions}
+
+Even the well known colinear functions $f_1^a(x)$, $g_1^a(x)$ have 
+statistical uncertainties and systematic uncertainties (the latter
+introduced by choosing a certain fit Ansatz which however can be 
+avoided through neural network techniques \cite{Ball:2014uwa}).
+These uncertainties as well as those of $D_1^a(z)$ can safely
+be neglected for our purposes. 
+For TMDs the situation is different. Already the transverse
+momentum descriptions of $f_1^a(x,\kperp)$ and $D_1^a(z,\pperp)$ 
+are associated with non-negligible statistical uncertainties
+which are reviewed in App.~\ref{App:basis}, and with systematic
+uncertainties which are very difficult to assess as they are
+related to model bias (because of Gaussian model and its limitations).
+The statistical and systematic uncertainties are significant
+when we deal with the basis functions 
+$f_{1T}^{\perp q}$, $h_{1}^{q}$, $H_{1}^{\perp q}$.
+The least well-controlled uncertainties are associated with the 
+Boer-Mulders function $h_1^{\perp q}$ and pretzelosity $h_{1T}^{\perp q}$.
+
+In this work we are not interested in these uncertainties, which
+future data will allow us to diminish --- even though in pratice 
+they may be sizable. Rather in this work we are interested in
+making projections based on the WW-type approximation. To avoid
+cumbersome and difficult to interpret figures we will therefore
+refrain from indicating the uncertainties associated with our
+current knowledge of the basis functions. In the following
+we will only display the estimated systematic uncertainty
+associated with the WW-type approximations {\it assuming}
+it works within a relative accuracy of $\pm40\%$.
+We stress that this is only to simplify the presentation. The 
+actual uncertainty of the predictions may be larger.
+
 }
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
+
 %======= SECTION 6: TWIST-2 AND WW-APROXIMATION ======================
@@
 
-Two out of the 8 leading--twist structure functions can be 
-described in WW-type approximation thanks to 
-Eqs.~(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}) which 
-relate $g_{1T}^{\perp (1) q}(x)$ and $h_{1L}^{\perp (1) q}(x)$ to the
-basis functions $g_1^q(x)$ and $h_1^a(x)$, see Fig.~\ref{g1t_h1l_functions}.
-In this section we discuss the associated asymmetries.
-
-\begin{figure}[h!]
+\begin{figure}[b!]
 \centering
@@
 \end{figure}
+
+Two out of the 8 leading--twist structure functions 
+can be described in WW-type approximation thanks to 
+Eqs.~(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}) which 
+relate $g_{1T}^{\perp (1) q}(x)$ and $h_{1L}^{\perp (1) q}(x)$ to the
+basis functions $g_1^q(x)$ and $h_1^a(x)$, see Fig.~\ref{g1t_h1l_functions}.
+\ps{These TMDs are sometimes referred to as ``gear worms:'' 
+$g_{1T}^{\perp q}$ describes the distributions of longitudinally 
+polarized quarks inside a transversely polarized nucleon,
+$h_{1L}^{\perp q}$ the opposite constallation, namely transversely 
+polarized quarks inside a longitudinally polarized nucleon.
+It is interesting that both cases can be expressed in the
+WW-type approximation in terms of the basis functions.}
+In this section we discuss the associated asymmetries.
 
@@
 \cite{Huang:2011bc,Parsamyan:2015dfa}. Left panel of Fig.~\ref{g1t_jlab} 
-shows 2010 COMPASS data \cite{Parsamyan:2015dfa} measured with 160 GeV 
-longitudinally polarized muons impinging on a transversely polarized proton 
-(NH$_3$) target \cite{Goertz:2002vv}. We approximate the charged hadrons
-($90\,\%$ of which are $\pi^\pm$ at COMPASS) by charged pions, see 
-App.~\ref{App:basis-f1-D1}.
+shows 2010 COMPASS data \cite{Parsamyan:2015dfa}. We approximate the 
+charged hadrons ($90\,\%$ of which are $\pi^\pm$ at COMPASS) by 
+charged pions, see App.~\ref{App:basis-f1-D1}.
 Our results are shown as a shaded area which indicates a rough estimate
@@
 supported by lattice data \cite{Hagler:2009mb}.
-From (\ref{Eq:WW-approx-h1L}) we obtain the WW-type estimate
+>From (\ref{Eq:WW-approx-h1L}) we obtain the WW-type estimate
 for $h_{1L}^{\perp(1) a}(x)$ shown in Fig.~\ref{g1t_h1l_functions}. 
@@
 \cite{Parsamyan:2015dfa}, and JLab \cite{Avakian:2010ae,Jawalkar:2017ube}.
-In Fig.~\ref{aul_jlab} proton data are shown. At HERMES $\pi^\pm$ 
-were produced in scattering of 27.6 GeV positrons from the HERA 
-polarized positron storage ring at DESY off nuclear-polarized 
-hydrogen internal gas target \cite{Stock:1994vv} 
-for $1\,{\rm GeV}^2 < Q^2 < 15 \,{\rm GeV}^2$, $W > 2\,{\rm Gev}$,
-$0.023 < x < 0.4$ and $y < 0.85$. The COMPASS data show the 
-asymmetry for charged hadrons (in practice mainly pions).
+In Fig.~\ref{aul_jlab} proton data are shown for $\pi^\pm$ in the
+HERMES experiment which were measured with the 27.6 GeV positron
+beam from the HERA polarized positron storage ring at DESY for 
+$1\,{\rm GeV}^2 < Q^2 < 15 \,{\rm GeV}^2$, $W > 2\,{\rm Gev}$,
+$0.023 < x < 0.4$ and $y < 0.85$. 
+The COMPASS data were taken with a 160 GeV muon beam and show 
+the asymmetry for charged hadrons (in practice mainly pions).
 Since $y$--dependent prefactors were included in the analyses 
@@
 
-\ps{
-
 \subsection{Inequalities and a cross check}
@@
 \begin{subequations}\ba
-	\frac{\kperp^2}{4M_N^2}\;\left((f_{1}^{q}(x,\kperp^2))^2 -(g_{1}^{q}(x,\kperp^2))^2\right)
+	\frac{\kperp^2}{4M_N^2}\;
+	\left((f_{1}^{q}(x,\kperp^2))^2 -(g_{1}^{q}(x,\kperp^2))^2\right)
 	- (h^{\perp(1)q}_{1L}(x,\kperp^2))^2 
 	- (h_{1}^{\perp(1)q}(x,\kperp^2))^2
-	& \ge & 0\,, \label{eq:positivity}\\
-	\frac{\kperp^2}{4M_N^2}\;\left((f_{1}^{q}(x,\kperp^2))^2 -(g_{1}^{q}(x,\kperp^2))^2\right)
+	& \ge & 0\,, \quad \label{eq:positivity}\\
+	\frac{\kperp^2}{4M_N^2}\;
+	\left((f_{1}^{q}(x,\kperp^2))^2 -(g_{1}^{q}(x,\kperp^2))^2\right)
 	- (f_{1T}^{\perp(1)q}(x,\kperp^2))^2
 	- (g^{\perp(1)q}_{1T}(x,\kperp^2))^2 
-	& \ge & 0\,, \label{eq:positivity1}
+	& \ge & 0\,, \quad \label{eq:positivity1}
 \ea\end{subequations}
@@
 \centering
-\includegraphics[width=0.3\textwidth]{\FigPath/g1t_positivity.pdf}  \quad
-\includegraphics[width=0.3\textwidth]{\FigPath/h1lperp_positivity.pdf}  
+\includegraphics[width=0.45\textwidth]{\FigPath/h1lperp_positivity.pdf} \quad  
+\includegraphics[width=0.45\textwidth]{\FigPath/g1t_positivity.pdf}  
 	\caption{\label{h1l_pos} 
 	The normalized inequalities for $g^{\perp(1)q}_{1T}(x)$ and
-	$h^{\perp(1)q}_{1L}(x)$ vs $x$. The normalized inequalities
-	are defined such that they must be positive (and smaller
-	than one), see text for details. Clearly, our approach
-	respects both positivity conditions.}
+	$h^{\perp(1)q}_{1L}(x)$ vs $x$ which are obtained by integrating
+	(\ref{eq:positivity}) and (\ref{eq:positivity1}) over $\kperp$,
+	and normalizing with respect to the sum of the absolute
+	values of the individual terms. The result must be positive and 
+	smaller than unity {\it if} the WW-type approximations
+	and the application of the Gaussian model are compatible
+	with positivity, see text. Clearly, our approach respects 
+	this test of the positivity conditions.}
 \end{figure}
@@
 
-}
-
 \newpage
@@
 
-WW-type approximations can be applied to all 8 subleading--twist observables,
-as shown in Sec.~\ref{Sec-4.2:WW-twist-3}. In view of the complex 
-structure of SIDIS at subleading--twist, WW-type approximations
-are potentially very useful for the interpretation of twist-3 observables.
+WW-type approximations can be applied to all 8 subleading--twist asymmetries,
+see Sec.~\ref{Sec-4.2:WW-twist-3}. \ps{In this section we discuss all of them,
+starting with less complex cases and proceeding then to those structure 
+functions whose description in WW-type approximation is more involved.}
 
@@
 
-Data from JLab, HERMES \ps{and COMPASS} show a small 
-but clearly non-zero effect of the order of (2-3)\,$\%$ 
-\cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,Aghasyan:2011ha,
-Adolph:2014pwc,Gohn:2014zbz}. At first glance this may seem a failure 
-of our approach. However, the numerator of the asymmetry is proportional 
-to $\bar q g q$--correlators, while the denominator ($f_1^aD_1^a$) is a 
-$q q$--correlator. Therefore we may express this observation as
+\ps{In this asymmetry we encounter the generic limitation of the 
+WW-type approximation in most extreme form. As discussed in 
+Sec.~\ref{Sec-3.8:limitations}, if we have a function
+$=\la\bar{q}q\ra + \la\bar{q}gq\ra$ the necessary condition for 
+the approximation to work is that $\la\bar{q}q\ra \neq 0$ and the 
+sufficient condition would be $|\la\bar{q}q\ra|\gg|\la\bar{q}gq\ra|$.
+Remarkably, none of the twist-3 TMDs or FFs entering this structure 
+function satisfy even the necessary condition. In this situation we 
+do not expect the WW-type approximation to be applicable.
+
+Indeed, data from JLab, HERMES and COMPASS show a clearly non-zero 
+asymmetry $A_{LU}^{\sin\phi_h} = F_{LU}^{\sin\phi_h}/F_{UU}$ of the order of 2\,$\%$ 
+\cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,
+Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz}. 
+On the one hand this is interesting: this observable provides a unique 
+opportunity to learn about the physics of $\bar{q}gq$-terms. On the other
+hand, this observable is beyond the applicability of the WW-type approximation
+and we cannot make a non-trivial prediction for this asymmetry.
+
+With the numerator of the asymmetry proportional to $\bar{q}gq$--terms
+and the denominator given in terms of $\bar{q} q$--terms, one could be 
+tempted to interpret this observation as
 \be\label{Eq:ALU-small}
-    	|A_{LU}^{\sin\phi_h}|
-	\;\; \propto \;\;\frac{\la\bar qgq\ra}{\la\bar qq\ra}
-    	\;\;\stackrel{\rm exp}{\lesssim} \;\; 
-	{\cal O}(3\,\%)
+    	A_{LU}^{\sin\phi_h}
+	\;\; \propto \;\;\frac{\la\bar{q}gq\ra}{\la\bar{q}q\ra}
+    	\;\;\stackrel{\rm exp}{\sim} \;\; 
+	{\cal O}(2\,\%)
     	\;.
 \ee
-We should keep in mind several reservations. First,
-the experimental result quoted in (\ref{Eq:ALU-small})
-contains also kinematic prefactors which help to reduce the value. 
+Thus, in some sense the observed effect hints at the smallness of the 
+involved $\bar{q}gq$--terms. While in principle a correct observation,
+one should keep in mind several reservations. First,
+the experimental result (\ref{Eq:ALU-small})
+contains kinematic prefactors which help to reduce the value. 
 Second, the denominator contains $f_1^a$ and $D_1^a$ which are the
 largest TMD and FF because of positivity constraints. Third, the 
-numerator is a sum of 4 terms, so its overall smallness could also 
-result from cancellation of different terms, rather than indicating
-that all 4 terms are small.
-Keeping these reservations cautiously in mind, we may nevertheless 
-consider the experimental observation of a (2-3)\,$\%$ asymmetry 
-$A_{LU}^{\sin\phi_h}$ 
-\cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,Aghasyan:2011ha,
-Adolph:2014pwc,Gohn:2014zbz}
-as an encouraging indication that $\bar qgq$--terms are smaller than 
-$\bar qq$ terms, in line with the generic expectation (\ref{Eq:WW-generic}).
+numerator is a sum of 4 terms, so its overall smallness could result 
+from cancellation of different terms, rather than indicating that 
+each single $\bar{q}gq$--term is small. Fourth, some asymmetries 
+predicted to be non-zero in WW-approximation are not much larger and 
+in some cases even smaller than the result in (\ref{Eq:ALU-small}).
 
 To conclude, the WW-type approximation predicts $A_{LU}^{\sin\phi}\approx 0$
-which is ``compatible'' with experiment in the sense that the data show a 
-small asymmetry. Notice however that some asymmetries appear in experiment
-even smaller (compatible with zero) despite being non-zero in WW-type
-approximation. Further work is needed before we can draw definite
-conclusions. In any case, $F_{LU}^{\sin\phi}$ is the only twist-3 SIDIS 
-structure not ``contaminated'' by leading twist which provides a
-unique window into higher twist physics.
+in contradiction with experiment. The size of the observed effect seems
+in line with the WW-type approximation, as
+$A_{LU}^{\sin\phi_h}\sim\la\bar{q}gq\ra/\la\bar{q}q\ra \sim {\cal O}(2\,\%)$
+is not large, although this interpretation has reservations.
+$F_{LU}^{\sin\phi}$ is the only twist-3 SIDIS structure function not 
+``contaminated'' by leading twist. Attempts to describe this observable
+and relevant model studies have been reported 
+\cite{Efremov:2002qh,
+Lorce:2014hxa,
+Schweitzer:2003uy,Ohnishi:2003mf,Cebulla:2007ej,
+Efremov:2002ut,Afanasev:2003ze,Yuan:2003gu,Gamberg:2003pz,Metz:2004je,Afanasev:2006gw,Mao:2012dk,Mao:2014dva,Courtoy:2014xea,Yang:2016mxl}.
+But more phenomenological work and dedicated studies on the basis of models 
+of $\bar{q}gq$ terms are needed to fully understand this asymmetry.}
 
@@
 In  WW-type approximation the structure function
-$F_{LT}^{\cos\phi_S}$ is due to $g_T^a(x,\kperp)$ and $D_1^a(z,\pperp)$ 
+$F_{LT}^{\cos\phi_S}$ arises from $g_T^a(x,\kperp)$ and $D_1^a(z,\pperp)$ 
 whose collinear counterparts are more or less known, see
@@
 We assume the Gaussian Ansatz for $g_T^a(x,\kperp)$ shown in
-Eq.~(\ref{eq:gtnew}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} 
+Eq.~(\ref{eqg:tnew}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} 
 with ${\avkperp_{g_T}}={\avkperp_{g_1}}$. We then determine $g^{q}_{T}(x)$ 
@@
 asymmetry is small and compatible with the COMPASS data within
-error bars. More precise data is necessary to judge the how
+error bars. More precise data ara necessary to judge how
 well the WW-type approximation works in this case. Such data
@@
 	c^{(2)}_{C}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!2}\,
-	\label{eq:asymmetry_auu_cos2phi}
+	\label{eq:asymmetry_auu_cos2phi-phiS}
 \ea\end{subequations}
@@
 available data, see Fig.~\ref{allcosphi_jlab}.
-
-\
-
-\
+\ps{We remark that previously this assymmetry was studied in
+\cite{Anselmino:2006yc} and more recently in \cite{Mao:2016hdi}.}
 
@@
 \caption{\label{aulsinphi_jlab} The asymmetry $A_{UL}^{\sin\phi_h}$ 
-	as function of $x$ from WW-type approximation in comparison to: 
+	as function of $x$ from WW-type approximation in comparison to
+	proton target data from: 
 	(upper panel left) HERMES \cite{Airapetian:2005jc},
@@
 
-The third interesting feature not seen in
-previous sections is the occurence of a term which
-drops out upon integrating the structure function over $\Phperp$, cf.\ 
-Eq.~(\ref{Eq:FUTsinphiS-final-PhT}) vs.\ (\ref{Eq:FUTsinphiS-final}).
-This is a property of the weight $\omega^{\{2\}}_{\rm B}$ 
-in Eq.~(\ref{FUTsinphiS}),
-see Eq.~(\ref{Eq:wi}) and App.~\ref{App:factor}, which appears
-also in $F_{LT}^{\cos\phi_S}$, Eq.~(\ref{FLTcosphiS}), where it however drops
-out in WW-type approximation. In principle, this property could  help to 
+The third interesting feature not seen previously is the occurence of a 
+term which drops out upon integrating the structure function over $\Phperp$, 
+cf.\ Eq.~(\ref{Eq:FUTsinphiS-final-PhT}) vs.\ (\ref{Eq:FUTsinphiS-final}).
+This is a property of the weight $\omega^{\{2\}}_{\rm B}$, see 
+Eq.~(\ref{Eq:wi}) and App.~\ref{App:factor} (which appears also in 
+$F_{LT}^{\cos\phi_S}$, Eq.~(\ref{FLTcosphiS}), where it drops
+out in WW-type approximation). In principle, this property could  help to 
 discriminate experimentally the terms associated with this weight.
@@
 WW-type approximation, see Eq.~(\ref{Eq:FUT-collinear}). Our prediction 
-is therefore $A_{UT}^{\sin\phi_S}(x)=F_{UT}^{\sin\phi_S}(x)/F_{UU}(x)=0$.
-This is compatible with preliminary data from HERMES \cite{Schnell:2010zza}
-and COMPASS \cite{Parsamyan:2015dfa} over a wide range of $x$, see 
-Fig.~\ref{autsinphi_jlab} below. Merely for negative hadrons at 
-large-$x$ there might be a disagreement with our prediction.
+is therefore $A_{UT}^{\sin\phi_S}(x)=0$.
+\ps{This is compatible with preliminary HERMES \cite{Schnell:2010zza}
+and COMPASS \cite{Parsamyan:2015dfa} data over a wide range of $x$, 
+see Fig.~\ref{autsinphi_jlab}. But for negative hadrons at large $x$ 
+there is an indication that the WW-type approximation does not seem
+to work.}
+
+\newpage
 
@@
 $xf^{\perp(1)q}(x) = \frac{\la\kperp^2\ra_{f_1}}{2M_N^2}\,f_{1}^q(x)$ and 
-estimate its Gaussian width as $\la\kperp^2\ra_{f^\perp}=\la\kperp^2\ra_{f_1}$.
+assume for its Gaussian width $\la\kperp^2\ra_{f^\perp}=\la\kperp^2\ra_{f_1}$.
 The latter means the Gaussian factors of 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
-%\includegraphics[width=0.45\textwidth]{}
 \caption{\label{auucosphi_jlab} 
 	Left panel: asymmetry $A_{UU}^{\cos\phi_h}$ for positive and negative 
-	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}.
-	Right panel: the same for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}
-	\red{(Figure missing! Could not find data. Please, somebody
-	help to find data.)}}
+	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}. Right 
+	panel: the same for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.
+	\red{(Alexei, please, could you add here HERMES data \& include
+	labels ``HERMES'' and ``COMPASS''?)}}
 \end{figure}
-
-{}
 
@@
 functions. This approximation consists of a systematic neglect 
-of $\bar qgq$-terms in the
+of $\bar{q}gq$-terms in the
 correlators defining the TMDs and FFs. We have shown that in such
@@
 accuracy of $\pm\,40\,\%$ or better. This is remarkable.
-The instanton vacuum model predicts an analog WW-approximation
+The instanton vacuum model predicts an analogous WW-approximation
 for the chirally odd twist-3 PDF $h_L^q(x)$ to work similarly
@@
 In each case, $g_T^q(x)$ and $h_L^q(x)$, we deal with nucleon
-matrix elements of different $\bar qgq$ correlators, which are 
+matrix elements of different $\bar{q}gq$ correlators, which are 
 assumed to be small. Can one generalize these approximations to
@@
 In the case of the three subleading--twist structure functions 
-	$F_{UU}^{\cos(2\phi_h)}$, 
+	$F_{UU}^{\cos\phi_h}$, 
 	$F_{UL}^{\sin\phi_h}$,
@@
 the case of TMDs however it is less appropriate to speak about a
-systematic expansion in terms of $\bar qq$, $\bar qgq$, etc 
+systematic expansion in terms of $\bar{q}q$, $\bar{q}gq$, etc 
 correlators). It will be very interesting to learn whether e.g.\ 
-in $F_{UL}^{\sin\phi_h}$ or $F_{LU}^{\sin\phi_h}$ a single $\bar qgq$--term 
+in $F_{UL}^{\sin\phi_h}$ or $F_{LU}^{\sin\phi_h}$ a single $\bar{q}gq$--term 
 is anomalously large, or whether it is a accumulative effect of 
-several small terms $\bar qgq$--terms adding up to the observed asymmetry.
+several small terms $\bar{q}gq$--terms adding up to the observed asymmetry.
 
 Among all SIDIS structure functions $F_{LU}^{\sin\phi_h}$ emerges as
-a particularly interesing case: this asymmetry is due to $\bar qgq$
-only with no contamination from $\bar qq$ terms.
-So $F_{LU}^{\sin\phi_h}$ offers a unique view on the physics of $\bar qgq$ 
+a particularly interesing case: this asymmetry is due to $\bar{q}gq$
+only with no contamination from $\bar{q}q$ terms.
+So $F_{LU}^{\sin\phi_h}$ offers a unique view on the physics of $\bar{q}gq$ 
 correlators which is worth--exploring for its own sake.
@@
 \section{Acknowledgments}
-First and foremost, the authors would like to thank their families for patience and
-constant support throughout writing this paper. The authors would like to thank Werner Vogelsang for many useful discussions. This work was 
-partially supported by the U.S.\ Department of Energy under 
-Contract No.~DE-AC05-06OR23177 (A.P.) and within TMD Collaboration framework, and by the National 
+First and foremost, the authors would like to thank their families 
+for patience and constant support throughout writing this paper. 
+The authors would like to thank Werner Vogelsang for many useful 
+discussions. This work was partially supported by the U.S.\ 
+Department of Energy under Contract No.~DE-AC05-06OR23177 (A.P.) 
+and within TMD Collaboration framework, and by the National 
 Science Foundation under Contract No.\ PHY-1623454 (A.P.)
@@
 
-\ps{
 \newpage
@@
 
-{}
-
+\newpage
 \subsection{Comment on TMDs subject to the sum rules (\ref{Eq:sum-rules-T-odd})}
@@
 and analogously $h^q(x,\kperp)$, $e_L^q(x,\kperp)$.
-
-{}
-
-}
 
@@
 			&
-	\label{Eq:Gaussian-integrals-working-III}
+	\label{Eq:Gaussian-integrals-working-IV}
 \end{alignat}
@@
 \newpage
-\subsection{Mathematica package}
+\section{Mathematica package}
 \label{app:package}
 
+Bla, bla. \red{Alexei: please, paste here your text.}
+
+\newpage
 \bibliography{\BibPath/biblio_ww}

### 2018-07-10 tex/test-WW-type-00x-PS.tex
alexei

@@
 The Appendices \ref{App:basis} and \ref{App:factor} contain 
-technical details. \ps{In App.~C we describe an open source 
+technical details. \AP{In App.~C we describe an open source 
 package publicly available on \texttt{github.com}\footnote{\href{%
@@
 	https://github.com/prokudin/WW-SIDIS}} 
-	inplemented in \texttt{mathematica}~\cite{Mathematica} 
+	implemented in \texttt{mathematica}~\cite{Mathematica} 
 	(already available) and \texttt{Python} 
-	(to be released in near future).}
+	(to be released in the near future).}
 
@@
 
-Bla, bla. \red{Alexei: please, paste here your text.}
+\AP{The package available to wide physics community is needed for several reasons.
+First of all it is intended to facilitate visualization, reproduction, and verification of our results presented in this paper.
+Second, the package may prove useful for experimental community that needs estimates of measured quantities for certain kinematics of a particular experiment.
+Third, the phenomenological community will have an easy access to our result for comparison and/or use in phenomenological or theoretical papers.
+The authors believe that the open source access to the codes used in a project is the right way of handling scientific information in the 21$^{st}$ century.
+Collinear parton distribution functions are well tabulated in \texttt{LHAPDF} project \cite{Buckley:2014ana}, collinear fragmentation function still need a dedicated repository.
+There exist already several databases already being developed for extensions of collinear one dimensional picture of the nucleon structure.
+Generalized Parton Distributions are present in the framework, called \texttt{PARTONS} \cite{Berthou:2015oaw}, several extractions of Transverse Momentum Dependent distributions are tabulated in \texttt{TMDlib} project \cite{Hautmann:2014kza}.
+
+If you use this package, please, site this paper and the link to the repository.
+Please, acknowledge using any of the extracted TMDs present in this package.
+The corresponding \texttt{bibitem} codes are present in the description of each TMD function.
+
+The source code of the project can be downloaded or cloned from the open source repository: \texttt{https://github.com/prokudin/WW-SIDIS}.
+Using  \texttt{Mathematica}  run the  file named \texttt{example.nb}, you will see an example of usage of the code, code description and several visualizations of functions, asymmetries, and SIDIS cross-sections.
+Make sure that you do not move \texttt{example.nb} to another directory as it uses grids for TMDs, PDFs, and FFs.
+
+SIDIS cross section examples are present in Fig.~\ref{fig:package} .
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/cross_section_phih.pdf} 
+\includegraphics[width=0.45\textwidth]{\FigPath/cross_section_phiS.pdf} 
+\caption{\label{fig:package} 
+	Left panel:  $\phi_h$ dependence of the SIDIS cross section at $\phi_S = \pi/2$. 
+	Right panel:  $\phi_S$ dependence of the SIDIS cross section at $\phi_h = 0$. 
+	 Also $x = 0.3$, $z=0.2$, $\Phperp = 0.5$ GeV, 
+	$Q^2$ = 2.4 GeV$^2$, and the beam energy $E_{beam}$ = 5.7 GeV, averaged over beam helicities,  transverse proton target polarization.}
+\end{figure}
+}
 

### 2018-07-15 tex/test-WW-type-00y-PS.tex
text

--- 2018-07-10 tex/test-WW-type-00x-PS.tex
@@
 %Editing commands
-\newcommand{\TD}{{\bf TODO:}}
+\newcommand{\TD}[1]{{{\bf TODO:} \color[rgb]{0.65,0,0.15} #1}}
 \newcommand{\AP}[1]{{\bf AP:} {\color{red} #1}}
@@
 \newcommand{\darkgreen}[1]{{\color{darkgreen} #1}}
-\newcommand{\orange}[1]{{\color{orange} #1}}
-\newcommand{\ps}[1]{\blue{ #1}}
-\newcommand{\ak}[1]{\orange{ #1}}
-\newcommand{\ms}[1]{\darkgreen{ #1}}
+\newcommand{\orange}[1]{{\color{orange}#1}}
+
+\newcommand{\ak}[1]{\orange{#1}}
+\newcommand{\ps}[1]{\blue{#1}}
+\newcommand{\gs}[1]{{\color[rgb]{0.65,0,0.65}#1}}
+\newcommand{\ms}[1]{\darkgreen{#1}}
+\newcommand{\kt}[1]{{\color[rgb]{0.1,0.5,0}#1}}
 
@@
 
-\preprint{\red{version ``00x''}; JLAB-THY-18-XXXX}
-%\preprint{version 00x-PS}
+\preprint{\red{version ``00y''}; JLAB-THY-18-XXXX}
 
@@
 deep-inelastic scattering up to power-suppressed ${\cal O}(1/Q^2)$ terms in
-the Wandzura--Wilczek-type approximation \ps{which consists in systematically
-assuming that $\bar{q}gq$--terms are much smaller than $\bar{q}q$--correlators.}
+the Wandzura--Wilczek-type approximation which consists in systematically
+assuming that $\bar{q}gq$--terms are much smaller than $\bar{q}q$--correlators.
 We compute all twist-2 and twist-3 structure functions and the corresponding 
@@
 
-\vspace{1cm}
-
 \subsection*{Color Legend}
@@
 General comments: 
-	\red{red color, command: {$\backslash{\rm red}\{\dots\}$}}\\
+	\TD{dark red color, command: {$\backslash{\rm TD}\{\dots\}$}}\\
 Alexei's corrections: 
@@
 	\ak{orange color, command: {$\backslash{\rm ak}\{\dots\}$}}\\
+Gunar's corrections: 
+	\gs{violett color, command: {$\backslash{\rm gs}\{\dots\}$}}\\
+Kemal's corrections: 
+	\kt{greenish color, command: {$\backslash{\rm kt}\{\dots\}$}}\\
 Marc's corrections: 
@@
 	\ps{blue color, command: {$\backslash{\rm ps}\{\dots\}$}}\\
-Anatoli Vasilievich, Bakur, Bernie, Gunar, Kemal, Saman: \\
+Anatoli Vasilievich, Bakur, Bernie, Saman: \\
 	corrections already introduced in black color \& confirmed by e-mail.
@@
 By exploring various possibilities for the lepton beam and target 
-polarizations\footnote{\ps{It is important to stress that this
-	information could not have been obtained without advances 
-	in target polarization techniques employed in the HERMES, 
-	COMPASS and JLab experiments 
-	\cite{Stock:1994vv,Crabb:1997cy,Goertz:2002vv}.}}
-unambiguous information can be accessed on the 8 leading--twist 
+polarizations unambiguous information can be accessed on the 8 leading--twist 
 TMDs \cite{Boer:1997nt} and, if one assumes factorization, on certain
@@
 \cite{Goeke:2005hb,Bacchetta:2006tn}.
+	It is important to stress that this information could not have 
+	been obtained without advances in target polarization techniques 
+	employed in the HERMES, COMPASS and JLab experiments 
+	\cite{Stock:1994vv,Crabb:1997cy,Goertz:2002vv}.
 Complementary information can be obtained 
@@
 terms \cite{Wandzura:1977qf,Jaffe:1991ra}
-\ms{(the index $a=q\,,\bar q$ does not include gluons for
-$h_1^a$, $h_L^a$ and other chiral odd TMDs below)}.
+(the index $a=q\,,\bar q$ does not include gluons for
+$h_1^a$, $h_L^a$ and other chiral odd TMDs below).
 We shall refer to the latter generically as $\bar{q}gq$--terms, keeping in 
@@
 upgrade and COMPASS or proposed in the long-term (Electron Ion Collider), 
-and provide helpful input for Monte Carlo event generators 
+and provide helpful input for the development of Monte Carlo event generators 
 \cite{Avakian:2015vha}.
@@
 Our predictions will either be confirmed within the expected accuracy
-or will not not supported by data. In either case our work will provide
-a useful benchmark, and either call for dedicated theoretical 
-studies to explain either the pertinent $\bar{q}gq$--terms are 
-so small or why they are so sizable. In either case our results will 
-deepen the understanding of  $\bar{q}gq$--correlations, \ps{pave the 
-way towards testing} the validity of the TMD factorization approach 
+or will not be supported by data. In either case our work will provide
+a useful benchmark, and call for dedicated theoretical 
+studies to explain (i) why the pertinent $\bar{q}gq$--terms are 
+small or (ii) why they are sizable. In either case our results will 
+deepen the understanding of  $\bar{q}gq$--correlations, pave the 
+way towards testing the validity of the TMD factorization approach 
 at subleading twist, and help us to guide further developments.
@@
 The Appendices \ref{App:basis} and \ref{App:factor} contain 
-technical details. \AP{In App.~C we describe an open source 
+technical details. 
+	In App.~C we describe an open source 
 	package publicly available on \texttt{github.com}\footnote{\href{%
@@
 	(already available) and \texttt{Python} 
-	(to be released in the near future).}
+	(to be released in the near future).
 
@@
 Fig.~\ref{fig-kin-SIDIS}. Here $l$ and $P$ are momenta of incoming 
-lepton and nucleon, and $l^\prime$ and $P_h$ are the momenta of the outgoing
+lepton and nucleon, $l^\prime$ and $P_h$ are the momenta of the outgoing
 lepton and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
-selects a z-axis, and $l^\prime$ points in the direction of the x-axis 
+selects the z-axis, and $l^\prime$ points in the direction of the x-axis 
 from which azimuthal angles are counted. The relevant kinematic invariants 
@@
 azimuthal angle $\psi_l$ characterizing the overall orientation of the 
-lepton scattering plane in a fixed lab frame. \ak{The origin of this 
+lepton scattering plane in a fixed lab frame. The origin of this 
 angle can be chosen arbitrarily. For a transversely polarized target 
 it is convenient to choose the origin of the angle $\psi_l$ in the 
-direction of $\vec{S}_T$.}
+direction of $\vec{S}_T$.
 It is convenient to define the unpolarized 
@@
 Notice that $F_{UT}^{\sin\phi_S}(x,z)$ has no DIS counterpart due to time reversal
-symmetry of strong interactions, and \ak{terms suppressed by $1/Q^2$ are 
+symmetry of strong interactions, and terms suppressed by $1/Q^2$ are 
 consequently neglected troughout this work including the twist-4 DIS 
-structure function $F_L(x)$. }
+structure function $F_L(x)$.
 
@@
 where $r_h = m_h/M_N$ and 
-$F_{XY}^{\rm weight}\equiv F_{XY}^{\rm weight}(x,z,\Phperp)$. \ms{The 
+$F_{XY}^{\rm weight}\equiv F_{XY}^{\rm weight}(x,z,\Phperp)$. The 
 tilde-functions $\tilde{D}^{\perp },\,\tilde{G}^{\perp },\,\tilde{H},\,\tilde{E}$
 are defined in terms of $\bar{q}gq$-correlators, see 
-Sec.~\ref{Sec-3.2:WW-type-TMD-FF}.} The weight functions are defined as
+Sec.~\ref{Sec-3.2:WW-type-TMD-FF}. The weight functions are defined as
 \ba
@@
 Before introducing the WW-type approximations in the next section, 
-\ms{we would like to add a comment on TMD factorization: the 
+we would like to add a comment on TMD factorization: the 
 partonic description of the leading-twist structure functions in 
@@
 In fact, a lot of progress has been achieved in recent years in the 
-theoretical understanding of leading twist observables within the TMD 
+theoretical understanding of leading-twist observables within the TMD 
 framework --- including definition, renormalization and evolution of 
@@
 trigger more theory efforts in the future.
-}
 
@@
 
-\ms{The relations (\ref{Eq:WW-original1}--\ref{Eq:WW-original-e})
+The relations (\ref{Eq:WW-original1}--\ref{Eq:WW-original-e})
 have been derived basically using operator product expansion
@@
 into a twist-2 part, and dynamical twist-3 (interactions dependent) 
-$\bar{q}gq$-terms and current quark mass terms.}
+$\bar{q}gq$-terms and current quark mass terms.
 
@@
 $\la Q^2\ra=7.1\,{\rm GeV}^2$ \cite{Anthony:2002hy,Abe:1998wq}. 
-Right panel: HERMES data \ps{for $Q^2>1\,{\rm GeV}^2$ with}
+Right panel: HERMES data for $Q^2>1\,{\rm GeV}^2$ with
 $\la Q^2\ra=2.4\,{\rm GeV}^2$ \cite{Airapetian:2011wu}.
@@
 We present calculations of $g_2(x)_{\rm WW}$ in Fig.~\ref{Fig:g2}.
-\ps{This result is obtained using the LO $g_1^a(x)$-parametrization 
+This result is obtained using the LO $g_1^a(x)$-parametrization 
 \cite{Gluck:1998xa}. In order to display the theoretical ``uncertainty 
@@
 Ref.~\cite{Accardi:2009au} we proceed as follows: we split the 
-$40\,\%$ uncertainty} in two parts, $\varepsilon_1=\pm 20\,\%$ and 
+$40\,\%$ uncertainty in two parts, $\varepsilon_1=\pm 20\,\%$ and 
 $\varepsilon_2(x)=\pm 20\,\%(1-x)^\epsilon$ with a small $\epsilon>0$,
@@
 For the time being, we content ourselves with rather crude comparisons 
-based on the \ak{lattice data}
+based on the lattice data
 published in Refs.~\cite{Hagler:2009mb,Musch:2010ka}. 
@@
 	= -2 \tilde{A}_{7,q}( \ell = 0 ) 
-	\stackrel{\text{Gaussian}}{=} -c_{7,q}\\
+	\stackrel{\text{\scriptsize Gaussian}}{=} -c_{7,q} \quad \quad \\
     	\int_{-1}^1 d x\; h_{1L}^{\perp(1)q}(x) 
@@
 	= -2 \tilde{A}_{10,q}( \ell = 0 )
-	\stackrel{\text{Gaussian}}{=} -c_{10,q}
+	\stackrel{\text{\scriptsize Gaussian}}{=} -c_{10,q} \quad \quad
 \ea
@@
 For the test of Eq.~(\ref{Eq:WW-approx-g1T-d}), we use the numbers 
-$\int d x\;g_{1T}^{\perp(1)u}(x)\stackrel{\text{Gaussian}}{=}-c_{7,u}= 0.1041(85)$ 
-and
-$\int d x\;g_{1T}^{\perp(1)d}(x)\stackrel{\text{Gaussian}}{=}-c_{7,d}=-0.0232(42)$
+$\int d x\;g_{1T}^{\perp(1)u}(x)\stackrel{\text{\scriptsize Gaussian}}{=}
+-c_{7,u}= 0.1041(85)$ and
+$\int d x\;g_{1T}^{\perp(1)d}(x)\stackrel{\text{\scriptsize Gaussian}}{=}
+-c_{7,d}=-0.0232(42)$
 from \cite{Musch:2010ka}. %[Phys.Rev. D83 (2011) 094507]:
@@
 % $\int d x\;h_{1L}^{\perp(1)d}(x) = 0.0130(40)$ from \cite{Hagler:2009mb}
-$\int dx\;h_{1L}^{\perp(1)u}(x)\stackrel{\text{Gaussian}}{=}-c_{10,u}=-0.0881(72)$ 
+$\int dx\;h_{1L}^{\perp(1)u}(x)\stackrel{\text{\scriptsize Gaussian}}{=}
+-c_{10,u}=-0.0881(72)$ 
 and
-$\int dx\;h_{1L}^{\perp(1)d}(x)\stackrel{\text{Gaussian}}{=}-c_{10,d}=0.0137(34)$
+$\int dx\;h_{1L}^{\perp(1)d}(x)\stackrel{\text{\scriptsize Gaussian}}{=}
+-c_{10,d}=0.0137(34)$
 from \cite{Musch:2010ka} and the lattice data 
@@
 (\ref{Eq:WW-original1},~\ref{Eq:WW-original2}), which corresponds to the
-Burkardt-Cottingham sum rule for $g_T^a(x)$ and an analogous sum rule for
+Burkhardt-Cottingham sum rule for $g_T^a(x)$ and an analogous sum rule for
 $h_L^a(x)$, see \cite{Jaffe:1996zw} and references there in.
@@
 so-called quark model Lorentz-invariance relations (qLIRs)
-\cite{Tangerman:1994bb,Mulders:1995dh}.\footnote{\ms{Notice that
+\cite{Tangerman:1994bb,Mulders:1995dh}.\footnote{Notice that
 	the qLIRs of \cite{Tangerman:1994bb,Mulders:1995dh} are 
@@
 	In literature both are often simply referred to as LIRs.
-	This ambiguity is unfortunate.}}
+	This ambiguity is unfortunate.}
 Initially thought to be exact \cite{Tangerman:1994bb,Mulders:1995dh}
@@
 
+\newpage
+
 %\newpage
@@
 $f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a}$
-and 2 FFs $D_1^a, \; H_1^{\perp a}$ provide a basis.
+and 2 FFs $D_1^a, \; H_1^{\perp a}$ provide a basis
+\kt{in the sense that in WW-type approximation all other TMDs and FFs 
+can either be expressed in terms of these basis functions or vanish.}
 Below we shall see that, under the assumption of the validity of WW-type 
@@
 
-\ps{The approximation may work in the case when: TMD or FF 
+The approximation may work in the case when: TMD or FF 
 $=\la\bar{q}q\ra + \la\bar{q}gq\ra \approx \la\bar{q}q\ra \neq 0$ with 
@@
 which go beyond this generic issue. To illustrate this for FFs
-we recall that} that both $H_1^{\perp(1)q}$ and $\tilde H_1^{q}$ are 
+we recall that both $H_1^{\perp(1)q}$ and $\tilde H_1^{q}$ are 
 related to integrals of an underlying function $H_{FU}^{q,\Im}(z,z_1)$
@@
 Does it mean WW-type approximations fail for $f_T^a(x,k_\perp)$ 
-and $h^a(x,k_\perp)$? Not necessarily. \ms{The approximations may
+and $h^a(x,k_\perp)$? Not necessarily. The approximations may
 work in some but not all regions of $\kperp$, but the sum rules 
@@
 in WW-type approximation.
-In this sense (\ref{Eq:WW-type-fT}) could be consistent.}
+In this sense (\ref{Eq:WW-type-fT}) could be consistent.
 Thus, issues with the sum rules 
@@
 
-The Gaussian Ansatz is compatible with many WW-type type approximations
+The Gaussian Ansatz is compatible with many WW-type approximations
 but not all. The trivial approximations (\ref{Eq:WW-type-1}) and
@@
 To summarize, our procedure is to solve first the convolution 
-integrals in Gauss Ansatz, and use then WW-type approximations.
+integrals in Gaussian Ansatz, and use then WW-type approximations.
 When implementing this procedure we will see that the results 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{\FigPath/f1} 
-\includegraphics[width=0.4\textwidth]{\FigPath/f1Tperp}
-
-\includegraphics[width=0.4\textwidth]{\FigPath/g1}  
-\includegraphics[width=0.4\textwidth]{\FigPath/h1perpBM}
-
-\includegraphics[width=0.4\textwidth]{\FigPath/h1}  
-\includegraphics[width=0.4\textwidth]{\FigPath/h1Tperp}
-
-\includegraphics[width=0.4\textwidth]{\FigPath/D1} 
-\includegraphics[width=0.4\textwidth]{\FigPath/H1perp} 
+\includegraphics[width=0.37\textwidth]{\FigPath/f1} 
+\includegraphics[width=0.37\textwidth]{\FigPath/f1Tperp}
+
+\includegraphics[width=0.37\textwidth]{\FigPath/g1}  
+\includegraphics[width=0.37\textwidth]{\FigPath/h1perpBM}
+
+\includegraphics[width=0.37\textwidth]{\FigPath/h1}  
+\includegraphics[width=0.37\textwidth]{\FigPath/h1Tperp}
+
+\includegraphics[width=0.37\textwidth]{\FigPath/D1} 
+\includegraphics[width=0.37\textwidth]{\FigPath/H1perp} 
 \caption{\label{basis} 
@@
 the Gaussian model expressions, and the Gaussian width parameters are
-largely absorbed in the definitions of the transverse moments which 
-helps to minimize the model-dependence. Second,
+largely absorbed in the definitions of the transverse moments.
+% which helps to minimize the model-dependence. 
+Second,
 the $k_\perp$--moments of these TMDs have in principle simple definitions
@@
 
-\ps{Let us begin with JLab where, in the pre-12$\,$GeV era, electron beams 
+Let us begin with JLab where, in the pre-12$\,$GeV era, electron beams 
 from CEBAF with energies in the range $4.3$ to $5.7$ GeV were scattered 
 off proton or deuterium targets in the typical kinematics 
-$1 \,{\rm GeV}^2 < Q^2 < 4.5 \,{\rm GeV}^2$, $W > 2\,{\rm Gev}$, 
+$1 \,{\rm GeV}^2 < Q^2 < 4.5 \,{\rm GeV}^2$, $W > 2\,{\rm GeV}$, 
 $0.1 < x < 0.6$, $y < 0.85$, $0.5<z<0.8$.
@@
 off proton and deuteron targets in the SIDIS kinematics 
-$Q^2 > 1 \,{\rm GeV}^2$, $W > 2\,{\rm Gev}$, 
+$Q^2 > 1 \,{\rm GeV}^2$, $W > 2\,{\rm GeV}$, 
 $0.023 < x < 0.4$, $y < 0.85$, $0.2<z<0.7$. 
@@
 	M_n^h(x,z,\Phperp) \equiv 
-	\ak{\frac{d\sigma_{\rm SIDIS}(x,z,\Phperp)/dx\,dz\,d\Phperp}
-	{d\sigma_{\rm DIS}(x,z)/dx}} =
+	\frac{d\sigma_{\rm SIDIS}(x,z,\Phperp)/dx\,dz\,d\Phperp}
+	{d\sigma_{\rm DIS}(x,z)/dx} =
 	2 \pi \Phperp \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
@@
 targets in the typical SIDIS kinematics 
-$Q^2 > 1 \,{\rm GeV}^2$, $W > 5\,{\rm Gev}$, 
+$Q^2 > 1 \,{\rm GeV}^2$, $W > 5\,{\rm GeV}$, 
 $0.003 < x < 0.7$, $0.1<y < 0.9$, $0.2<z<1$. 
@@
 	n^h(x,z,\Phperp^2)  \equiv 
-	\ak{\frac{d\sigma_{\rm SIDIS}(x,z,\Phperp^2)/dx\,dz\,d\Phperp^2}
-	{d\sigma_{\rm DIS}(x,z)/dx}} =
+	\frac{d\sigma_{\rm SIDIS}(x,z,\Phperp^2)/dx\,dz\,d\Phperp^2}
+	{d\sigma_{\rm DIS}(x,z)/dx} =
 	\pi \frac{F_{UU}(x,z,\Phperp^2) }{ x \sum_q e_q^2\,f^q_1(x)}\;
@@
 at $\la Q^2\ra=20\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.2$ 
-for $h^+$ production on the deuterium target \cite{Aghasyan:2017ctw}.}
+for $h^+$ production on the deuterium target \cite{Aghasyan:2017ctw}.
 
@@
 
-\ps{The description of the HERMES and COMPASS multiplicities in
+The description of the HERMES and COMPASS multiplicities in
 Fig.~\ref{FUU-show-pT-dependence} is good and sufficient for our
@@
 into account $\kperp$-broadening effects between HERMES and 
-COMPASS energies. Through dedicated fits to the HERMES, COMPASS
-(and other) data and the consideration of $\kperp$-evolution effects
-it is possible to obtain a better description than shown in
-Fig.~\ref{FUU-show-pT-dependence}, see Ref.~\cite{Bacchetta:2017gcc}.}
+COMPASS energies \gs{and that the HERMES data actually represent 
+multiplicities integrated (separately for numerator and denominator) 
+over the kinematic ranges of each bin while the curve is plotted for 
+a fixed set of kinematics.} Through dedicated fits to the HERMES, COMPASS
+(and other) data and consideration of $\kperp$-evolution effects
+it is possible to obtain a better description than in
+Fig.~\ref{FUU-show-pT-dependence}, see \cite{Bacchetta:2017gcc}.
 
@@
 Signori:2013mda,Anselmino:2013lza}, but nothing is known about its 
-applicability to spin assymetries. The JLab data \cite{Avakian:2010ae} 
+applicability to spin asymetries. The JLab data \cite{Avakian:2010ae} 
 on $A_{LL}(\Phperp)$ put us in the position to conduct a first ``test'' 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_COMPASS_x.pdf}
-\caption{\label{aut_f1t_jlab} \ps{Sivers asymmetry 
+\caption{\label{aut_f1t_jlab} Sivers asymmetry 
 	$A_{UT}^{\sin(\phi_h-\phi_S)}$ from proton target as function of $ x $ 
@@
 	(left panel) HERMES \cite{Airapetian:2009ae}
-	% refer to the mean values
-	% $\la x\ra = 0.1$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ 
 	and (right panel) COMPASS data \cite{Adolph:2012sp}.}
-	\red{(Alexei: 
-	is it possible to add here the
-	labels ``HERMES'' and ``COMPASS''
-	on the plots?)}}
 \end{figure}
@@
 The asymmetries $A_{UT}^{\sin(\phi_h-\phi_S)}= F_{UT}^{\sin(\phi_h-\phi_S)}/F_{UU}$  
-\ps{obtained from the fit \cite{Anselmino:2011gs}
+obtained from the fit \cite{Anselmino:2011gs}
 are plotted in Fig.~\ref{aut_f1t_jlab} as functions of $x$ in comparison 
@@
 The $P_{hT}$--dependencies of the data are equally well described which
-confirms that the Gaussian model works also in this case.}
+confirms that the Gaussian model works also in this case.
 
@@
 FF $H_1^\perp$. Transversity can in principle be accessed also as a PDF in
-Drell-Yan \ps{or in dihadron production 
+Drell-Yan or in dihadron production 
 \cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,Bacchetta:2012ty,
-Radici:2015mwa,Radici:2018iag}.}
+Radici:2015mwa,Radici:2018iag}.
 It describes the distribution of transversely polarized quarks
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_COMPASS_x.pdf}
-\caption{\label{aut_h1_jlab}  \ps{Collins asymmetry 
+\caption{\label{aut_h1_jlab}  Collins asymmetry 
 	$A_{UT}^{\sin(\phi_h+\phi_S)}$ from proton target as function of $ x $ 
 	based on the fit \cite{Anselmino:2013vqa} in comparison to 
-	(left panel) HERMES \cite{Airapetian:2010ds}
-	% refer to the mean values
-	% $\la x\ra = 0.1$, $\la z\ra = 0.34$, $\la Q^2\ra = 2.4$ GeV$^2$ 
-	and (right panel) COMPASS data \cite{Adolph:2014zba} (where
+	(left panel) HERMES \cite{Airapetian:2010ds} and 
+	(right panel) COMPASS data \cite{Adolph:2014zba} (where
 	$(-1)A_{UT}^{\sin(\phi_h+\phi_S)}$ is shown since for historical
@@
 	with an opposite sign convention.)}
-	\red{(Alexei: 
-	is it possible to add here the
-	labels ``HERMES'' and ``COMPASS''
-	on the plots?)}}
 \end{figure}
@@
 
-\ps{The structure function $F_{UU}^{\cos(2\phi_h)}$ arises from a convultion of
+The structure function $F_{UU}^{\cos(2\phi_h)}$ arises from a convolution of
 the Collins fragmention function and the TMD $h_{1}^{\perp q}$ which describes
 the distribution of transversely polarized partons inside an unpolarized
-target. The expression of this structure function is given by}
+target. The expression of this structure function is given by
 \begin{subequations}\ba
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AUUcos2phi_COMPASS_x.pdf}
-\caption{\label{auu_cos2phi_jlab} \ps{The asymmetry 
+\caption{\label{auu_cos2phi_jlab} The asymmetry 
 	$A_{UU}^{\cos(2\phi_h)}$ from proton target as function of $ x $ 
-	based on the fit \cite{Barone:2015ksa} \red{[Alexei,
-	we changed the reference, is this the correct paper?]}
-	in comparison to (left panel) HERMES \cite{Airapetian:2012yg}
-	and (right panel) COMPASS data \cite{Adolph:2014pwc}.}
-	\red{(Alexei: 
-	is it possible to add here the
-	labels ``HERMES'' and ``COMPASS''
-	on the plots?)}}
+	based on the fit \cite{Barone:2015ksa} in comparison to 
+	(left panel) HERMES \cite{Airapetian:2012yg} and 
+	(right panel) COMPASS data \cite{Adolph:2014pwc}.
+	\TD{I thought we use now different parametrization, 
+	not \cite{Barone:2015ksa}. please, check!}}
 \end{figure}
@@
 
-\ps{The pretzelosity TMD $h_{1T}^{\perp q}$ is the least known of the basis 
+The pretzelosity TMD $h_{1T}^{\perp q}$ is the least known of the basis 
 functions. It is of interest as it allows one to measure the deviation 
@@
 \cite{Avakian:2008dz,She:2009jq,Avakian:2010br,Lorce:2011kn}.
-}
 
@@
 see App.~\ref{App:convol-details}.
-\ps{In Eq.~(\ref{eq:asymmetry_aut_h1tp}) we see that this structure 
+In Eq.~(\ref{eq:asymmetry_aut_h1tp}) we see that this structure 
 function suffers a cubic suppression for small transverse hadron
@@
 structure functions through leading and subleading twist, making
-it challenging to measure.}
+it challenging to measure.
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_x.pdf}  
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_PT.pdf}
+%\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_x.pdf}  
+%\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_PT.pdf}
+\includegraphics[width=0.37\textwidth]{\FigPath/Screenshot-Fig-COMPASS-A_UT_Pr10-left-panel-up.png} \quad
+\includegraphics[width=0.37\textwidth]{\FigPath/Screenshot-Fig-COMPASS-A_UT_Pr10-left-panel-down.png}
 \caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  
-	as a function of $ x $ (left panel) and $P_{hT}$ (right panel) 
-	at $\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 3.6$ GeV$^2$ 
-	on the basis of fits from \cite{Lefky:2014eia} 
-	vs preliminary COMPASS data \cite{Parsamyan:2010se}.
-	\red{\sf PRELIMINARY COMPASS DATA have disappeared from the plot!
-	(related to Alexei's ``illegal figure''?)
-	Bakur: can you produce the left panel of Fig.~18 as {\bf separate}
-	figure to show here? ALSO: I would propose to skip the $P_{hT}$-plot,
-	which does not give much insight.}}
+	as a function of $ x $ 
+	\ps{from COMPASS \cite{Parsamyan:2010se} and the central value 
+	of the best fit (whose 1-$\sigma$ uncertainty band is compatible 
+	with zero) from \cite{Lefky:2014eia}. For comparison we show the
+	model results \cite{Kotzinian:2008fe,Boffi:2009sh}.}
+	\TD{\sf screenshot of 
+	{\tt Fig-COMPASS-A\_UT\_Pr10.pdf} which was previously shown in 
+	Fig.~\ref{autsinphi_jlab}. Bakur: please, can you produce such plot 
+	with Alexei's ``best fit'' from \cite{Lefky:2014eia}?}}
 \end{figure}
@@
 to significantly improve our knowledge of this TMD.
-
-\ps{
 
@@
 
-}
-
 %======= SECTION 6: TWIST-2 AND WW-APROXIMATION ======================
@@
 basis functions $g_1^q(x)$ and $h_1^a(x)$, see Fig.~\ref{g1t_h1l_functions}.
-\ps{These TMDs are sometimes referred to as ``gear worms:'' 
+These TMDs are sometimes referred to as ``gear worms:'' 
 $g_{1T}^{\perp q}$ describes the distributions of longitudinally 
@@
 It is interesting that both cases can be expressed in the
-WW-type approximation in terms of the basis functions.}
+WW-type approximation in terms of the basis functions.
 In this section we discuss the associated asymmetries.
@@
 %\includegraphics[width=0.3\textwidth]{\FigPath/ALT_COMPASS_x.pdf}  
-\includegraphics[width=0.95\textwidth]{\FigPath/Fig-COMPASS-A_LT_Pr10.pdf}
+\includegraphics[width=0.9\textwidth]{\FigPath/Fig-COMPASS-A_LT_Pr10.pdf}
 	\caption{\label{g1t_jlab} 
@@
 	subleading-twist $A_{LT}^{\cos(2\phi_h-\phi_S)}$
-	on which we comment in Sec.~\ref{Sec-7.3:FLTcos2phi-phiS}.}
+	on which we comment in Sec.~\ref{Sec-7.3:FLTcos2phi-phiS}.
+	\TD{(Bakur: can you prepare separate plots for these asymmetries?)}}
 \end{figure}
@@
 \centering
-\includegraphics[height=3.4cm]{\FigPath/Fig-COMPASS-A_2_Pr0711_Zgt02.pdf} \quad
-\includegraphics[height=3.4cm]{\FigPath/AULsin2phi_JLAB_x.pdf}  
+\includegraphics[height=3.1cm]{\FigPath/Fig-COMPASS-A_2_Pr0711_Zgt02.pdf} \quad
+\includegraphics[height=3.0cm]{\FigPath/AULsin2phi_JLAB_x.pdf}
+
+\vspace{-5mm}
+
 	\caption{\label{aul_jlab} 
@@
 beam from the HERA polarized positron storage ring at DESY for 
-$1\,{\rm GeV}^2 < Q^2 < 15 \,{\rm GeV}^2$, $W > 2\,{\rm Gev}$,
+$1\,{\rm GeV}^2 < Q^2 < 15 \,{\rm GeV}^2$, $W > 2\,{\rm GeV}$,
 $0.023 < x < 0.4$ and $y < 0.85$. 
@@
 (For PDFs it is known that positivity can be preserved in some 
-schemes but violated in other schemes. For TMDs not much is 
+schemes and violated in others. For TMDs not much is 
 known about positivity conditions beyond leading order.)
@@
 strong model assumptions (WW-type approximations for $g^{\perp q}_{1T}$ 
-and $h^{\perp q}_{1L}$ and Gauss Ansatz for all TMDs), and (ii) we deal 
+and $h^{\perp q}_{1L}$ and Gaussian Ansatz for all TMDs), and (ii) we deal 
 with first extractions which have sizable uncertainties including 
@@
 WW-type approximations can be applied to all 8 subleading--twist asymmetries,
-see Sec.~\ref{Sec-4.2:WW-twist-3}. \ps{In this section we discuss all of them,
+see Sec.~\ref{Sec-4.2:WW-twist-3}. In this section we discuss all of them,
 starting with less complex cases and proceeding then to those structure 
-functions whose description in WW-type approximation is more involved.}
+functions whose description in WW-type approximation is more involved.
 
@@
 
-\ps{In this asymmetry we encounter the generic limitation of the 
+In this asymmetry we encounter the generic limitation of the 
 WW-type approximation in most extreme form. As discussed in 
@@
 But more phenomenological work and dedicated studies on the basis of models 
-of $\bar{q}gq$ terms are needed to fully understand this asymmetry.}
+of $\bar{q}gq$ terms are needed to fully understand this asymmetry.
 
@@
 We assume the Gaussian Ansatz for $g_T^a(x,\kperp)$ shown in
-Eq.~(\ref{eqg:tnew}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} 
+Eq.~(\ref{eq:gtnew}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} 
 with ${\avkperp_{g_T}}={\avkperp_{g_1}}$. We then determine $g^{q}_{T}(x)$ 
@@
 Sec.~\ref{Sec-4.4:evaluation}: first assume Gaussian Ansatz, then apply 
-WW-type type approximation. For some structure functions the order of 
+WW-type approximation. For some structure functions the order of 
 these steps is not relevant, but here it is. It is instructive to 
@@
 asymmetry is small and compatible with the COMPASS data within
-error bars. More precise data ara necessary to judge how
+error bars. More precise data are necessary to judge how
 well the WW-type approximation works in this case. Such data
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
+\begin{figure}[b!]
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/ALTcosPhi_COMPASS_x.pdf} 
+\includegraphics[width=0.37\textwidth]{\FigPath/ALTcosPhi_COMPASS_x.pdf} 
 \caption{\label{altcosphi_jlab} Predictions for the double--spin asymmetry
@@
 	at JLab 12.
-}
+	\TD{Bakur: can you prepare a separate plot for this asymmetry 
+	based on the middle panel of Fig.~\ref{g1t_jlab}?
+	Then we could skip here the prediction.}}
 \end{figure}
@@
 	it is $M_N/Q$ suppressed. Second, it is proportional to
-	$P_{hT}^2$ with $P_{hT}\ll Q$ in TMD approach.}
+	$P_{hT}^2$ with $P_{hT}\ll Q$ in TMD approach.
+	\TD{Bakur: can you prepare a separate plot for this asymmetry 
+	based on the right panel of Fig.~\ref{g1t_jlab}?
+	Then we could skip here the prediction.}}
 \end{figure}
@@
 In WW-type approximation the only contribution to $F_{LL}^{\cos\phi_h}$
-is due to $g_{L}^{\perp q}(x,k_\perp)$ which we assume to be have a
+is due to $g_{L}^{\perp q}(x,k_\perp)$ which we assume to have a
 Gaussian $k_\perp$--behavior according to Eq.~(\ref{eq:gLperp})
-in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, where assume
-for the Gaussian width $\avkperp_{g_{L}^\perp}=\avkperp_{g_1}$. 
+in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} with 
+the Gaussian width $\avkperp_{g_{L}^\perp}=\avkperp_{g_1}$. 
 The structure function $F_{UL}^{\cos\phi_h}$ reads
@@
 available data, see Fig.~\ref{allcosphi_jlab}.
-\ps{We remark that previously this assymmetry was studied in
-\cite{Anselmino:2006yc} and more recently in \cite{Mao:2016hdi}.}
+We remark that previously this asymmetry was studied in
+\cite{Anselmino:2006yc} and more recently in \cite{Mao:2016hdi}.
 
@@
 \centering
+
+\vspace{1cm}
 \includegraphics[width=0.8\textwidth]{\FigPath/Fig-COMPASS-A_LL_Pr0711_Zgt02.pdf}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} 
-\includegraphics[width=0.8\textwidth]{\FigPath/Fig-COMPASS-A_UL1_Pr0711_Zgt02.pdf}
+\includegraphics[width=0.35\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
+\includegraphics[width=0.35\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} 
+\includegraphics[width=0.7\textwidth]{\FigPath/Fig-COMPASS-A_UL1_Pr0711_Zgt02.pdf}
 \caption{\label{aulsinphi_jlab} The asymmetry $A_{UL}^{\sin\phi_h}$ 
@@
 	(upper panel right) JLab \cite{Jawalkar:2017ube}, and 
-	(lower panel) preliminary COMPASS \cite{Parsamyan:2015dfa} data.}
+	(lower panel) preliminary COMPASS \cite{Parsamyan:2015dfa} data.
+	\TD{Bakur: could you remove the ``rescaled HERMES data''?}
+	\TD{Gunar sent $\pi^0$ data, email from Thu, July 12, 2018,
+	file: sinphi\_UL\_pi0\_HERMES.txt. Alexei, please
+	can you include these data?}}
 \end{figure}
@@
 In the structure function $F_{UT}^{\sin\phi_S}$ several interesting features
-occur not encontered before. Let us summarize the result and follow up 
+occur not encountered before. Let us summarize the result and follow up 
 with some comments.
@@
 WW-type approximation, see Eq.~(\ref{Eq:FUT-collinear}). Our prediction 
-is therefore $A_{UT}^{\sin\phi_S}(x)=0$.
-\ps{This is compatible with preliminary HERMES \cite{Schnell:2010zza}
-and COMPASS \cite{Parsamyan:2015dfa} data over a wide range of $x$, 
-see Fig.~\ref{autsinphi_jlab}. But for negative hadrons at large $x$ 
-there is an indication that the WW-type approximation does not seem
-to work.}
+is therefore $A_{UT}^{\sin\phi_S}(x)=0$. \gs{For positive pions or hadrons
+respectively preliminary HERMES \cite{Schnell:2010zza} and COMPASS 
+\cite{Parsamyan:2015dfa} data are compatible with this prediction.
+However, for negative pions or hadrons the signal is clearly non-zero
+and thus inconsistent with the WW prediction,} see Fig.~\ref{autsinphi_jlab}.
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{\FigPath/Fig-COMPASS-A_UT_Pr10.pdf}
-
-\vspace{-5mm}
+\includegraphics[width=0.6\textwidth]{\FigPath/Fig-COMPASS-A_UT_Pr10.pdf}
 
 \caption{\label{autsinphi_jlab} 
-	Preliminary data for azimuthal transverse target single--spin 
-	asymmetries as functions of $x$ from the COMPASS experiment 
-	\cite{Parsamyan:2015dfa}.
+%	Preliminary data for azimuthal transverse target single--spin 
+%	asymmetries as functions of $x$ from the COMPASS experiment 
+%	\cite{Parsamyan:2015dfa}.
+%	Left panel: 
+%	leading--twist $A_{UT}^{\sin(3\phi_h-\phi_S)}(x)$ which 
+%	determines the pretzelosity TMD, one of our basis functions. 
+%	This asymmetry was discussed in Sec.~\ref{Sec-5.6:pretzel-basis} 
+%	and is included here for completeness. 
 	Left panel: 
-	leading--twist $A_{UT}^{\sin(3\phi_h-\phi_S)}(x)$ which 
-	determines the pretzelosity TMD, one of our basis functions. 
-	This asymmetry was discussed in Sec.~\ref{Sec-5.6:pretzel-basis} 
-	and is included here for completeness. 
+        \TD{remove and show in Fig.~\ref{aut_h1tp_jlab} instead.}
 	Middle panel:
@@
 	Right panel: 
-	leading--twist $A_{UT}^{\sin(2\phi_h-\phi_S)}(x)$.}
+	leading--twist $A_{UT}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to the 
+	WW-type prediction described in Sec.~\ref{Sec-7.8:FUTsin2phi-phiS}.
+	\TD{Bakur: please, can you re-do these plots in separate figures?}}
 \end{figure}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
+\includegraphics[width=0.37\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
 \caption{\label{auucosphi_jlab} 
@@
 	panel: the same for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.
-	\red{(Alexei, please, could you add here HERMES data \& include
-	labels ``HERMES'' and ``COMPASS''?)}}
+	\TD{Gunar sent data, email from Thu, July 12, 2018,
+	file: cosNphi\_UU\_HERMES.txt. Maybe we show HERMES $\pi^\pm$ from 
+	proton or deuterium (but not both).
+	\underline{SUGGESTIONS}: include labels ``COMPASS proton data'' and 
+	``HERMES proton (or deuteron) data'' on the figures.
+	Plot range on $y$-axis: -0.35 to 0.}}
 \end{figure}
@@
 which is twist-2 and the other twist-3. Clearly, to make 
-predictions for new experiment or interpret early data, an
+predictions for new experiments or interpret early data, an
 organizing theoretical guideline is needed.
@@
 approximation, are either related to the basis functions or
-vanish. To make this work self-contained
-we reviewed the phenomenological information available
-on the basis functions which is given in terms of 6 SIDIS
-structure functions. (Of course, one cannot extract 8 basis
-functions from 6 observables: in particular 2 basis functions,
+vanish.
+
+To make this work self-contained we included a review of the 
+available phenomenological information on the basis functions 
+which is given in terms of 6 SIDIS structure functions. 
+(Of course, one cannot extract 8 basis
+functions from 6 observables: the extraction of 2 basis functions,
 the unpolarized TMD and FF $f_1^q(x,\kperp)$ and $D_1^q(x,\pperp)$,
-are determined from other experiments, most notably Drell-Yan
+makes also use of other experiments, most notably Drell-Yan
 and hadron production in $e^+e^-$ annihilations.)
@@
 for the chirally odd twist-3 PDF $h_L^q(x)$ to work similarly
-well. This predictions remains to be tested in experiment.
+well. This prediction remains to be tested in experiment.
 
@@
 We found that from theoretical point of view the WW-type
-approximations receive certain support, though the 
-evidence is less than in the colinear case.
-Most importantly, we have conducted systematic test of
+approximations receive certain support, though there is 
+less evidence than in the colinear case.
+Most importantly, we have conducted systematic tests of
 WW-approximations with available published or 
@@
 (the latter) with the data in this approximation. For 
-$F_{UT}^{\sin(2\phi_h)}$ more precise data are needed, 
+$F_{UL}^{\sin(2\phi_h)}$ more precise data are needed, 
 but also in this case the trend is encouraging
@@
   & & & & \cr
-\ fit of \cite{Anselmino:2005nn} & 5, 0.1, 0.3
+\ fit of \cite{Anselmino:2005nn} & 5.0, 0.1, 0.3
 	& $\sim 0.25$ 
@@
 	& -- \cr
-\ lattice \cite{Hagler:2009mb}  & 4, -- , --
+\ lattice \cite{Hagler:2009mb}  & 4.0, -- , --
 	& 0.14--0.15   
@@
 We can rewrite parametrizations of Boer-Mulders functions as
-
 \ba
@@
 
-\AP{The package available to wide physics community is needed for several reasons.
-First of all it is intended to facilitate visualization, reproduction, and verification of our results presented in this paper.
-Second, the package may prove useful for experimental community that needs estimates of measured quantities for certain kinematics of a particular experiment.
-Third, the phenomenological community will have an easy access to our result for comparison and/or use in phenomenological or theoretical papers.
-The authors believe that the open source access to the codes used in a project is the right way of handling scientific information in the 21$^{st}$ century.
-Collinear parton distribution functions are well tabulated in \texttt{LHAPDF} project \cite{Buckley:2014ana}, collinear fragmentation function still need a dedicated repository.
-There exist already several databases already being developed for extensions of collinear one dimensional picture of the nucleon structure.
-Generalized Parton Distributions are present in the framework, called \texttt{PARTONS} \cite{Berthou:2015oaw}, several extractions of Transverse Momentum Dependent distributions are tabulated in \texttt{TMDlib} project \cite{Hautmann:2014kza}.
-
-If you use this package, please, site this paper and the link to the repository.
-Please, acknowledge using any of the extracted TMDs present in this package.
-The corresponding \texttt{bibitem} codes are present in the description of each TMD function.
-
-The source code of the project can be downloaded or cloned from the open source repository: \texttt{https://github.com/prokudin/WW-SIDIS}.
-Using  \texttt{Mathematica}  run the  file named \texttt{example.nb}, you will see an example of usage of the code, code description and several visualizations of functions, asymmetries, and SIDIS cross-sections.
-Make sure that you do not move \texttt{example.nb} to another directory as it uses grids for TMDs, PDFs, and FFs.
-
-SIDIS cross section examples are present in Fig.~\ref{fig:package} .
+A package available to a wide physics community is needed for several 
+reasons. First of all it is intended to facilitate visualization, 
+reproduction, and verification of our results presented in this paper. 
+Second, the package may prove useful for \ps{experimentalists in need of}
+estimates of measured quantities for certain kinematics of a particular 
+experiment. Third, the \ps{phenomenological workers in the} community 
+will have an easy access to our results for comparison and/or use in 
+phenomenological or theoretical papers. The authors believe that the 
+open source access to the codes used in a project is the right way of 
+handling scientific information in the 21$^{st}$ century. \ps{For example,}
+collinear parton distribution functions are well tabulated in 
+the \texttt{LHAPDF} project \cite{Buckley:2014ana}, but collinear 
+fragmentation function still need a dedicated repository. There exist 
+already several databases \ps{which are} being developed for extensions 
+of collinear one-dimensional picture of the nucleon structure.  
+Generalized Parton Distributions are present in the framework 
+called \texttt{PARTONS} \cite{Berthou:2015oaw}, several extractions 
+of Transverse Momentum Dependent distributions are tabulated in 
+\texttt{TMDlib} project \cite{Hautmann:2014kza}.
+
+If you use this package, please, \ps{cite} this paper and the link to 
+the repository. Please, acknowledge using any of the extracted TMDs 
+\ps{presented} in this package. The corresponding \texttt{bibitem} 
+codes are \ps{included} in the description of each TMD function.
+
+The source code of the project can be downloaded or cloned from the 
+open source repository: \texttt{https://github.com/prokudin/WW-SIDIS}. 
+Using \texttt{Mathematica}  run the  file named \texttt{example.nb}, 
+you will see an example of usage of the code, code description and 
+several visualizations of functions, asymmetries, and SIDIS cross-sections. 
+Make sure that you do not move \texttt{example.nb} to another directory 
+as it uses grids for TMDs, PDFs, and FFs.
+
+SIDIS cross section examples are presented in Fig.~\ref{fig:package} .
 
@@
 \centering
+
+\vspace{5mm}
+
 \includegraphics[width=0.45\textwidth]{\FigPath/cross_section_phih.pdf} 
@@
 \caption{\label{fig:package} 
-	Left panel:  $\phi_h$ dependence of the SIDIS cross section at $\phi_S = \pi/2$. 
-	Right panel:  $\phi_S$ dependence of the SIDIS cross section at $\phi_h = 0$. 
+	Left panel:  
+	$\phi_h$ dependence of the SIDIS cross section at $\phi_S = \pi/2$. 
+	Right panel:  
+	$\phi_S$ dependence of the SIDIS cross section at $\phi_h = 0$. 
 	Also $x = 0.3$, $z=0.2$, $\Phperp = 0.5$ GeV, 
-	$Q^2$ = 2.4 GeV$^2$, and the beam energy $E_{beam}$ = 5.7 GeV, averaged over beam helicities,  transverse proton target polarization.}
+	$Q^2$ = 2.4 GeV$^2$, and the beam energy $E_{beam}$ = 5.7 GeV, 
+	averaged over beam helicities,  transverse proton target polarization.}
 \end{figure}
-}
 

### 2018-07-18 tex/test-WW-type-00z.tex
version 00z

--- 2018-07-15 tex/test-WW-type-00y-PS.tex
@@
 \newcommand{\gs}[1]{{\color[rgb]{0.65,0,0.65}#1}}
+\newcommand{\bp}[1]{{\color[rgb]{0,0.65,0.35}#1}}
 \newcommand{\ms}[1]{\darkgreen{#1}}
@@
 	\ak{orange color, command: {$\backslash{\rm ak}\{\dots\}$}}\\
+Bakur's corrections: 
+	\bp{green-blue color, command: {$\backslash{\rm bp}\{\dots\}$}}\\
 Gunar's corrections: 
@@
 \cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,Bacchetta:2006tn},
-and depend on two independent variables: the fraction $x$ of 
-nucleon momentum carried by parton, and intrinsic transverse 
-momentum $\kperp$ of the parton.
-Being a vector in the plane transverse with respect to the
-light-cone direction singled out by the hard momentum flow in the process,
+and depend on two independent variables: \bp{for TMDs,} 
+on the fraction $x$ of nucleon 
+momentum carried by parton and intrinsic transverse momentum $\kperp$ 
+of the parton, \bp{For FFs, on the fraction $z$ of the parton momentum 
+transferred to the hadron for and the transverse momentum of the hadron
+acquired during the fragmentation process}. 
+Being a vector in the plane transverse with respect to 
+the light-cone direction singled out by the hard momentum flow in the process,
 $\kperp$ allows us to access novel information on the nucleon spin structure 
@@
 Experience from collinear PDFs encourages to explore this possibility: 
-the twist-3 $g_T^a(x)$ and $h_L^a(x)$ can be expressed in terms of 
-contributions from twist-2 $g_1^a(x)$ and $h_1^a(x)$, and additional 
-quark-gluon-quark ($\bar{q}gq$) correlations or current quark mass 
-terms \cite{Wandzura:1977qf,Jaffe:1991ra}
+the twist-3 $g_T^a(x)$ and $h_L^a(x)$ can be \bp{respectively} expressed 
+in terms of contributions from twist-2 $g_1^a(x)$ and $h_1^a(x)$, and 
+additional quark-gluon-quark ($\bar{q}gq$) correlations or current 
+quark mass terms \cite{Wandzura:1977qf,Jaffe:1991ra}
 (the index $a=q\,,\bar q$ does not include gluons for
@@
 twist-3 in a unique approach. Our results are of importance for experiments 
-prepared in the near-term at Jefferson Lab (JLab) with 12$\,$GeV beam energy
-upgrade and COMPASS or proposed in the long-term (Electron Ion Collider), 
-and provide helpful input for the development of Monte Carlo event generators 
-\cite{Avakian:2015vha}.
-
-Our predictions will either be confirmed within the expected accuracy
-or will not be supported by data. In either case our work will provide
-a useful benchmark, and call for dedicated theoretical 
-studies to explain (i) why the pertinent $\bar{q}gq$--terms are 
-small or (ii) why they are sizable. In either case our results will 
-deepen the understanding of  $\bar{q}gq$--correlations, pave the 
+\bp{performed or in preparation at HERMES, COMPASS,} Jefferson Lab (JLab) with 
+12$\,$GeV beam energy upgrade, or proposed in the long-term 
+(Electron Ion Collider), and provide helpful input for the 
+development of Monte Carlo event generators \cite{Avakian:2015vha}.
+
+\bp{Our predictions, whether confirmed or not supported by current and 
+future experimental data, will in any case provide a useful benchmark,}
+and call for dedicated theoretical studies to explain (i) why the 
+pertinent $\bar{q}gq$--terms are small or (ii) why they are sizable. 
+In either case our results will deepen the understanding of 
+$\bar{q}gq$--correlations, pave the 
 way towards testing the validity of the TMD factorization approach 
@@
 technical details. 
-	In App.~C we describe an open source 
-	package publicly available on \texttt{github.com}\footnote{\href{%
+	In App.~C we describe \bp{an open source package implemented 
+	in \texttt{mathematica}~\cite{Mathematica} (already available) 
+	and \texttt{Python} (to be released in the near future) which is 
+	made publicly available on \texttt{github.com}.}\footnote{\href{%
 	https://github.com/prokudin/WW-SIDIS}{
 	https://github.com/prokudin/WW-SIDIS}}
-	implemented in \texttt{mathematica}~\cite{Mathematica} 
-	(already available) and \texttt{Python} 
-	(to be released in the near future).
 
@@
 lepton and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
-selects the z-axis, and $l^\prime$ points in the direction of the x-axis 
+\bp{defines} the z-axis, and $l^\prime$ points in the direction of the x-axis 
 from which azimuthal angles are counted. The relevant kinematic invariants 
@@
 charged leptons (electrons, positrons, muons) at $Q^2 \ll M_Z^2$ 
-in the single photon exchange approximation.
+in the single photon exchange approximation,
+\bp{where $M_Z$ denotes the mass of the $Z^0$ electroweak gauge boson.}
 In addition to $x$, $y$, $z$ the cross section is also differential 
@@
 of its momentum component $\Phperp$ perpendicular with respect to the 
-virtual photon momentum. 
-In principle the cross section is also differential with respect to the
-azimuthal angle $\psi_l$ characterizing the overall orientation of the 
-lepton scattering plane in a fixed lab frame. The origin of this 
-angle can be chosen arbitrarily. For a transversely polarized target 
-it is convenient to choose the origin of the angle $\psi_l$ in the 
-direction of $\vec{S}_T$.
+virtual photon momentum.  The cross section is also 
+differential with respect to the azimuthal angle $\psi_l$ 
+\bp{characterizing the overall orientation of the lepton scattering plane 
+around the incoming lepton direction. The angle is calculated with respect 
+to an arbitrary reference axis, which in case of transversely polarized 
+targets is chosen to be the direction of $S_T$. In DIS limit 
+$\psi_l \approx \phi_S$, where the latter is the azimuthal angle of 
+the spin-vector defined as in Fig.~\ref{fig-kin-SIDIS}.}
 It is convenient to define the unpolarized 
@@
 	\frac{4 \pi \alpha_{em}^2}{x\,y\,Q^2}
-	\biggl(1-y+\frac12y^2\biggr)\;
+	\biggl(1-y+\frac12y^2\biggr)\;.
 \ea
@@
         + \cos(2\phi_h)\,   p_1\,A_{UU}^{\cos(2\phi_h)} \nonumber\\
-   && \hspace{2cm}
+   && \hspace{1cm}
   	+ S_L\sin(2\phi_h)\,p_1\,A_{UL}^{\sin(2\phi_h)}    
 	+ \lambda\,S_L\,    p_2\,A_{LL}  \phantom{\frac11}\nonumber\\
-   && \hspace{2cm}
-	+ \lambda\,S_T\cos(\phi_h-\phi_S)\,p_2\,A_{LT}^{\cos( \phi_h-\phi_S)}
-       	+ S_T\sin( \phi_h-\phi_S)\, A_{UT}^{\sin( \phi_h-\phi_S)} \phantom{\frac11}
+   && \hspace{1cm}
+       	+ S_T\sin( \phi_h-\phi_S)\, A_{UT}^{\sin( \phi_h-\phi_S)}
+	+ S_T\sin( \phi_h+\phi_S)\,p_1\,A_{UT}^{\sin( \phi_h+\phi_S)} 
+	 \phantom{\frac11}
 	\nonumber\\ 
-   && \hspace{2cm}
-	+ S_T\sin( \phi_h+\phi_S)\,p_1\,A_{UT}^{\sin( \phi_h+\phi_S)} 
-        + S_T\sin(3\phi_h-\phi_S)\,p_1\,A_{UT}^{\sin(3\phi_h-\phi_S)}\Biggr\}
-    \hspace{1cm} \label{Eq:SIDIS-leading}
+   && \hspace{1cm}
+        + S_T\sin(3\phi_h-\phi_S)\,p_1\,A_{UT}^{\sin(3\phi_h-\phi_S)}
+	+ \lambda\,S_T\cos(\phi_h-\phi_S)\,p_2\,A_{LT}^{\cos( \phi_h-\phi_S)}\Biggr\}
+	\,. \hspace{12mm} \label{Eq:SIDIS-leading}
 \ea
-where $F_{UU}$ is the structure function due to transverse
+Here $F_{UU}$ is the structure function due to transverse
 polarization of the virtual photon (sometimes denoted as $F_{UU,T}$),
-and we systematically neglect $1/Q^2$ corrections in kinematic factors 
+and we %systematically 
+neglect $1/Q^2$ corrections in kinematic factors 
 and a structure function (sometimes denoted as $F_{UU,L}$) arising from
-longitudinal polarization of the virtual photon (and analogous for the 
+longitudinal polarization of the virtual photon (and \bp{another} the 
 structure function $\propto S_T\,\sin( \phi_h-\phi_S)$, see below).
@@
    && \hspace{2cm}
-	+ \lambda\sin(\phi_h)\,p_4\,A_{LU}^{\sin(\phi_h)}+ S_L\sin(\phi_h)\,p_3\,A_{UL}^{\sin(\phi_h)}    
-	+ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)} \phantom{\frac11}\nonumber\\ 
+	+ \lambda\sin(\phi_h)\,p_4\,A_{LU}^{\sin(\phi_h)}
+	+ S_L\sin(\phi_h)\,p_3\,A_{UL}^{\sin(\phi_h)}    
+	+ \lambda\,S_L\cos(\phi_h)\,p_4\,A_{LL}^{\cos(\phi_h)}\phantom{\frac11}
+	\nonumber\\
    && \hspace{2cm}
 	+ S_T\sin(2\phi_h-\phi_S)\,p_3\,A_{UT}^{\sin(2\phi_h-\phi_S)}
-        + \lambda\,S_L\cos(\phi_h)\,p_4\,A_{LL}^{\cos(\phi_h)}\phantom{\frac11}
-	\nonumber\\
+        + S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)} \phantom{\frac11}\nonumber\\ 
    && \hspace{2cm}
@@
 \ee
-and the asymmetries are defined as 
+and the asymmetries are defined as \bp{follows}
 \be
@@
 \ee
-Hereby the first index $X=U(L)$ denotes the unpolarized beam
-(longitudinally polarized beam with helicity $\lambda$).
-The second index $Y=U(L,T)$ refers to the target which can be unpolarized
+Here the first \bp{subscript} $X=U(L)$ denotes the unpolarized beam
+(longitudinally polarized beam with helicity $\lambda$). The second 
+\bp{subscript} $Y=U(L,T)$ refers to the target which can be unpolarized
 (or longitudinally, transversely polarized with respect to virtual photon).
@@
 (\ref{Eq:SIDIS-subleading}) are ``twist-3'' and contain a
-factor $M/Q$ in their definitions, see below. In our treatment to $1/Q^2$ 
+factor $M_N/Q$ in their definitions, see below, 
+\bp{where $M_N$ is the nucleon mass.} In our treatment to $1/Q^2$ 
 accuracy we neglect two structure functions due to longitudinal virtual 
-photon polarization which contribute at order ${\cal O}(M^2/Q^2)$ in the 
+photon polarization which contribute at order ${\cal O}(M_N^2/Q^2)$ in the 
 partonic description of the process, one being $F_{UU,L}$ and the other 
@@
 symmetry of strong interactions, and terms suppressed by $1/Q^2$ are 
-consequently neglected troughout this work including the twist-4 DIS 
+consequently neglected throughout this work including the twist-4 DIS 
 structure function $F_L(x)$.
@@
 \ea
-and the 16 subleading twist TMDs \cite{Mulders:1995dh,Bacchetta:2006tn}
+and the 16 subleading-twist TMDs \cite{Mulders:1995dh,Bacchetta:2006tn}
 are given by
@@
 	&=& 
-	\frac{2M}{Q}\,{\cal C}\biggl[\phantom{-}
+	\frac{2M_N}{Q}\,{\cal C}\biggl[\phantom{-}
    	\omega^{\{1\}}_{\rm A} 
@@
 	&=& 
-	\frac{2M}{Q}\,{\cal C}\biggl[ \phantom{-}
+	\frac{2M_N}{Q}\,{\cal C}\biggl[ \phantom{-}
 	\omega^{\{1\}}_{\rm A}
@@
  	&=& 
-	\frac{2M}{Q}\,{\cal C}\biggl[\phantom{-}
+	\frac{2M_N}{Q}\,{\cal C}\biggl[\phantom{-}
    	\omega^{\{1\}}_{\rm A}
@@
  	&=& 
-	\frac{2M}{Q}\,{\cal C}\biggl[ 
+	\frac{2M_N}{Q}\,{\cal C}\biggl[ 
 	-\omega^{\{1\}}_{\rm A}
@@
 	&=&  
-	\frac{2M}{Q}\,{\cal C}\biggl[ \phantom{-}
+	\frac{2M_N}{Q}\,{\cal C}\biggl[ \phantom{-}
 	\omega^{\{0\}}\,\biggl(x   f_T   D_1 \;
@@
 	&=& 
-	\frac{2M}{Q}\,{\cal C}\biggl[
+	\frac{2M_N}{Q}\,{\cal C}\biggl[
    	- \omega^{\{0\}}\,\biggl(x   g_T   D_1
@@
 	&=& 
-	\frac{2M}{Q}\,{\cal C}\biggl[\phantom{-}
+	\frac{2M_N}{Q}\,{\cal C}\biggl[\phantom{-}
    	\frac{\omega^{\{2\}}_{\rm AB}}{2}\,
@@
 	F_{LT}^{\cos(2\phi_h - \phi_S)} 
-	&=& \frac{2M}{Q}\,{\cal C}\biggl[
+	&=& \frac{2M_N}{Q}\,{\cal C}\biggl[
    	- \frac{\omega^{\{2\}}_{\rm AB}}{2}
@@
 and index $i$ (if any) distinguishes different types of contributions
-at the given order $N$. 
+at the given order $n$. 
  Notice that twist-3 structure functions in 
@@
 In contrast to this, the theory for subleading-twist TMD observables is 
-only pourly developed. Still to the present day, the state-of-the-art 
-approach to subleading twist TMD observables is the one of 
+only poorly developed. Still to the present day, the state-of-the-art 
+approach to subleading-twist TMD observables is the one of 
 Refs.~\cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,
@@
 by no means obvious which small parameter in the strong interaction 
-regime would allow one to explain such results. An appeling 
+regime would allow one to explain such results. An appealing 
 non-perturbative approach is provided by the instanton model of 
@@
 regime. It was shown with variational and numerical methods that the 
-instantons form a dilute medium characterized by a non-trivial small paramater
+instantons form a dilute medium characterized by a non-trivial small parameter
 $\rho/R\sim1/3$ \cite{Shuryak:1981ff,Diakonov:1983hh,Diakonov:1995qy}
@@
 (\ref{Eq:WW-original1}) one can write $g_2(x)$ as a total derivative
-expressed in terms of the experimentally well known twist-2
+expressed in terms of the experimentally well-known twist-2
 structure function $g_1(x)$ as follows
@@
 for a subset of observables, and the quantities calculated are not in a 
-form that lends itself to straighforward tests of the WW-type relations 
+form that lends itself to straightforward tests of the WW-type relations 
 as presented in this paper. Details about recent works and future 
@@
 In Fourier-space, the aforementioned divergent behavior for large $\bfkperp$ 
-translates into strong lattice scale and scheme dependences at short distances
+translates into strong lattice scale and scheme dependencies at short distances
 $\bflperp$ between the quark operators. The $\bfkperp$ integrals needed for 
@@
 a crude regularization of the divergences that appear in TMDs at large 
-$\bfkperp$ and manifest themselves as short range artefacts on the lattice. 
+$\bfkperp$ and manifest themselves as short range artifacts on the lattice. 
 Casting this line of thought into mathematics, we get
@@
 
-For the test of Eq.~(\ref{Eq:WW-approx-g1T-d}), we use the numbers 
+For the test of E.~(\ref{Eq:WW-approx-g1T-d}), we use the numbers 
 $\int d x\;g_{1T}^{\perp(1)u}(x)\stackrel{\text{\scriptsize Gaussian}}{=}
@@
 
+\newpage
 \subsection{Tests in models}
@@
 
-\newpage
-
-%\newpage
 \subsection{Basis functions for the WW-type approximations}
@@
 and 2 FFs $D_1^a, \; H_1^{\perp a}$ provide a basis
-\kt{in the sense that in WW-type approximation all other TMDs and FFs 
-can either be expressed in terms of these basis functions or vanish.}
+in the sense that in WW-type approximation all other TMDs and FFs 
+can either be expressed in terms of these basis functions or vanish.
 Below we shall see that, under the assumption of the validity of WW-type 
@@
 even if the neglected matrix element  $\la\bar{q}gq\ra$ is very small.
-Notice that this type occurs for all subleading twist FFs, which enter 
+Notice that this type occurs for all subleading-twist FFs, which enter 
 SIDIS structure functions only in the shape of tilde-FFs, see 
@@
 
-Presently too little is known in the theory of subleading twist TMDs. 
+Presently too little is known in the theory of subleading-twist TMDs. 
 Below in Sec.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi} we 
@@
 
-\newpage
 \subsection{Subleading structure functions in WW-type approximations}
@@
 
-In the case of the subleading twist structure functions the WW-type 
+In the case of the subleading-twist structure functions the WW-type 
 approximations in Eqs.~(\ref{Eq:WW-type-1}--\ref{Eq:WW-type-last})
@@
 	\label{Eq:WW-type-FLUsinphi}\\
-F_{LT}^{\cos \phi_S}&\stackrel{\rm WW}{=}& \frac{2M}{Q}\,
+F_{LT}^{\cos \phi_S}&\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,
 	{\cal C}\biggl[-  \omega^{\{0\}}\, x\,g_T D_1 \biggr]
@@
 	{Eq.~(\ref{Eq:WW-original1}),}\\
-F_{LL}^{\cos \phi_h} &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,{\cal C}\biggl[ 
+F_{LL}^{\cos \phi_h} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[ 
    	-\omega^{\{1\}}_{\rm B}\,
@@
 	{Eq.~(\ref{Eq:WW-type-gLperp}),}\\
-F_{LT}^{\cos(2\phi_h - \phi_S)} &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,{\cal C}\biggl[
+F_{LT}^{\cos(2\phi_h - \phi_S)} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
    	- \omega^{\{2\}}_{\rm C}\,
@@
 	{Eqs.~(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T}),}\\
-F_{UL}^{\sin\phi_h} &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,{\cal C}\biggl[
+F_{UL}^{\sin\phi_h} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
    	\phantom{-}\omega^{\{1\}}_{\rm A}\,
@@
 	\label{Eq:WW-type-FULsinphi}\\
-F_{UU}^{\cos\phi_h} &\stackrel{\rm WW}{=}&\frac{2M}{Q}\,{\cal C}\biggl[\phantom{-}
+F_{UU}^{\cos\phi_h} &\stackrel{\rm WW}{=}&\frac{2M_N}{Q}\,{\cal C}\biggl[\phantom{-}
 	 \omega^{\{1\}}_{\rm A}\,x\,h\,H_{1}^{\perp } 
@@
 	\label{Eq:WW-type-FUUcosphi}\\
-F_{UT}^{\sin \phi_S } &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,
+F_{UT}^{\sin \phi_S } &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,
 	{\cal C}\biggl[ \phantom{-}\omega^{\{0\}} \, x\,f_TD_1
@@
 	\label{Eq:WW-type-FUTsinphiS}\\
-F_{UT}^{\sin(2\phi_h -\phi_S)} &\stackrel{\rm WW}{=}& \frac{2M}{Q}\,{\cal C}\biggl[
+F_{UT}^{\sin(2\phi_h -\phi_S)} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
    	\;\omega^{\{2\}}_{\rm C}\,
@@
 Of course this Ansatz is only a rough approximation. For instance, 
-it is not consistent with general matching expectations when $\kperp$ 
-becomes large \cite{Bacchetta:2008xw}.
+it is not consistent with general matching expectations for large 
+$\kperp$ \cite{Bacchetta:2008xw}.
 
@@
 \centering
-\includegraphics[width=0.37\textwidth]{\FigPath/f1} 
-\includegraphics[width=0.37\textwidth]{\FigPath/f1Tperp}
-
-\includegraphics[width=0.37\textwidth]{\FigPath/g1}  
-\includegraphics[width=0.37\textwidth]{\FigPath/h1perpBM}
-
-\includegraphics[width=0.37\textwidth]{\FigPath/h1}  
-\includegraphics[width=0.37\textwidth]{\FigPath/h1Tperp}
-
-\includegraphics[width=0.37\textwidth]{\FigPath/D1} 
-\includegraphics[width=0.37\textwidth]{\FigPath/H1perp} 
+\includegraphics[width=0.32\textwidth]{\FigPath/f1} 
+\includegraphics[width=0.32\textwidth]{\FigPath/g1}  
+\includegraphics[width=0.32\textwidth]{\FigPath/h1}
+
+\includegraphics[width=0.32\textwidth]{\FigPath/f1Tperp}
+\includegraphics[width=0.32\textwidth]{\FigPath/h1perpBM}  
+\includegraphics[width=0.32\textwidth]{\FigPath/h1Tperp}
+
+\includegraphics[width=0.33\textwidth]{\FigPath/D1} 
+\includegraphics[width=0.33\textwidth]{\FigPath/H1perp} 
 \caption{\label{basis} 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[height=3.2cm]{\FigPath/Fig02a-JLab-ratio-pT-v5-NEW.pdf}  \quad
-\includegraphics[height=3.2cm]{\FigPath/hermes_pip.pdf} \quad
-\includegraphics[height=3.2cm]{\FigPath/compass_hp.pdf} 
-\caption{\label{FUU-show-pT-dependence}
-Examples of the 
-	description of transverse momenta of hadrons in unpolarized SIDIS. 
-Left panel: 
-	$F_{UU}(P_{hT}^2)$ for $\pi^+$ production normalized with 
-	respect to its value at zero transverse momentum at 
-	$\la Q^2\ra=2.37\,{\rm GeV}^2$, $\la x\ra=0.24$, $\la z\ra=0.30$ 
-	at JLab with 5.75 GeV beam \cite{Osipenko:2008aa}, cf.\  
-	\cite{Schweitzer:2010tt}.
-Middle panel: 
-	HERMES multiplicity (\ref{Eq:multiplicity-HERMES}) at 
-	$\la Q^2\ra=2.87\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.22$
-	from \cite{Airapetian:2012ki}.
-Right panel: 
-	COMPASS multiplicity (\ref{Eq:multiplicity-COMPASS}) at 
-	$\la Q^2\ra=20\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.2$
-	from \cite{Aghasyan:2017ctw}.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 The structure function $F_{UU}$ needed for our analysis reads
@@
 with the understanding that the convenient abbreviation $\lambda$ is expressed 
-in terms of the Gaussian widths of the {\it preceeding} TMD and FF. Notice 
+in terms of the Gaussian widths of the {\it preceding} TMD and FF. Notice 
 that ${\cal G}(\Phperp)\equiv {\cal G}(x,z,\Phperp)$ and that in general
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t!]
+\centering
+\includegraphics[height=3.2cm]{\FigPath/Fig02a-JLab-ratio-pT-v5-NEW.pdf}  \quad
+\includegraphics[height=3.2cm]{\FigPath/hermes_pip.pdf} \quad
+\includegraphics[height=3.2cm]{\FigPath/compass_hp.pdf} 
+\caption{\label{FUU-show-pT-dependence}
+Left panel: 
+	$F_{UU}(P_{hT}^2)/F_{UU}(0)$ for $\pi^+$ 
+	production 
+	% for $\la Q^2\ra=2.37\,{\rm GeV}^2$, $\la x\ra=0.24$, $\la z\ra=0.30$ 
+	at JLab with 5.75 GeV beam \cite{Osipenko:2008aa}.
+Middle panel: 
+	HERMES multiplicity (\ref{Eq:multiplicity-HERMES}) at 
+	$\la Q^2\ra=2.87\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.22$
+	from \cite{Airapetian:2012ki}.
+Right panel: 
+	COMPASS multiplicity (\ref{Eq:multiplicity-COMPASS}) at 
+	$\la Q^2\ra=20\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.2$
+	from \cite{Aghasyan:2017ctw}.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Next we discuss a representative plot from the HERMES experiment 
@@
 as fitted and employed in the original extractions of the TMDs. These 
-values were not optimised to fit the HERMES or COMPASS multiplicities.
+values were not optimized to fit the HERMES or COMPASS multiplicities.
 Keeping this in mind, the description in Fig.~\ref{FUU-show-pT-dependence}
@@
 into account $\kperp$-broadening effects between HERMES and 
-COMPASS energies \gs{and that the HERMES data actually represent 
+COMPASS energies and that the HERMES data actually represent 
 multiplicities integrated (separately for numerator and denominator) 
 over the kinematic ranges of each bin while the curve is plotted for 
-a fixed set of kinematics.} Through dedicated fits to the HERMES, COMPASS
+a fixed set of kinematics. Through dedicated fits to the HERMES, COMPASS
 (and other) data and consideration of $\kperp$-evolution effects
@@
 Signori:2013mda,Anselmino:2013lza}, but nothing is known about its 
-applicability to spin asymetries. The JLab data \cite{Avakian:2010ae} 
+applicability to spin asymmetries. The JLab data \cite{Avakian:2010ae} 
 on $A_{LL}(\Phperp)$ put us in the position to conduct a first ``test'' 
@@
 \caption{\label{jlab_ALL} 
-	$A_{LL,\la y\ra}$ asymmetry compared to JLab data \cite{Avakian:2010ae}
+	$A_{LL,\la y\ra}$ as function of $P_{hT}$ vs 
+	JLab data \cite{Avakian:2010ae}
  	for $\pi^+$, $\pi^0$, $\pi^-$. The solid lines are 
-	our results for the mean values of kinematical variable
+	our results for the mean values of kinematical variables
 	$\langle x \rangle = 0.25$, 
@@
 
+\newpage
+
 \subsection{\boldmath Leading twist $A_{UT}^{\sin(\phi_h-\phi_S)}$ Sivers asymmetry}
@@
 	$A_{UU}^{\cos(2\phi_h)}$ from proton target as function of $ x $ 
-	based on the fit \cite{Barone:2015ksa} in comparison to 
+	based on the fit \cite{Barone:2009hw} in comparison to 
 	(left panel) HERMES \cite{Airapetian:2012yg} and 
-	(right panel) COMPASS data \cite{Adolph:2014pwc}.
-	\TD{I thought we use now different parametrization, 
-	not \cite{Barone:2015ksa}. please, check!}}
+	(right panel) COMPASS data \cite{Adolph:2014pwc}.}
 \end{figure}
@@
 %\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_PT.pdf}
-\includegraphics[width=0.37\textwidth]{\FigPath/Screenshot-Fig-COMPASS-A_UT_Pr10-left-panel-up.png} \quad
-\includegraphics[width=0.37\textwidth]{\FigPath/Screenshot-Fig-COMPASS-A_UT_Pr10-left-panel-down.png}
+\includegraphics[width=0.3\textwidth]{\FigPath/Screenshot-Fig-COMPASS-A_UT_Pr10-left-panel-up.png} \ 
+\includegraphics[width=0.3\textwidth]{\FigPath/Screenshot-Fig-COMPASS-A_UT_Pr10-left-panel-down.png}
+\includegraphics[width=0.3\textwidth]{\FigPath/AUTPretzelosity_HERMES_x.pdf}
+
 \caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  
-	as a function of $ x $ 
-	\ps{from COMPASS \cite{Parsamyan:2010se} and the central value 
-	of the best fit (whose 1-$\sigma$ uncertainty band is compatible 
-	with zero) from \cite{Lefky:2014eia}. For comparison we show the
-	model results \cite{Kotzinian:2008fe,Boffi:2009sh}.}
-	\TD{\sf screenshot of 
-	{\tt Fig-COMPASS-A\_UT\_Pr10.pdf} which was previously shown in 
-	Fig.~\ref{autsinphi_jlab}. Bakur: please, can you produce such plot 
-	with Alexei's ``best fit'' from \cite{Lefky:2014eia}?}}
+	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2010se} 
+	and HERMES \cite{Schnell:2010zza} in comparison to the best fit 
+	(whose 1-$\sigma$ uncertainty band is compatible with zero) 
+	from \cite{Lefky:2014eia}. For comparison the COMPASS plots
+	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
+	\TD{\sf screenshot of {\tt Fig-COMPASS-A\_UT\_Pr10.pdf} 
+	which was previously shown in Fig.~\ref{autsinphi_jlab}. 
+	Bakur: please, can you produce such plot with Alexei's 
+	``best fit'' from \cite{Lefky:2014eia}?}}
 \end{figure}
@@
 
-Even the well known colinear functions $f_1^a(x)$, $g_1^a(x)$ have 
+Even the well-known collinear functions $f_1^a(x)$, $g_1^a(x)$ have 
 statistical uncertainties and systematic uncertainties (the latter
@@
 In this work we are not interested in these uncertainties, which
-future data will allow us to diminish --- even though in pratice 
+future data will allow us to diminish --- even though in practice 
 they may be sizable. Rather in this work we are interested in
@@
 polarized quarks inside a transversely polarized nucleon,
-$h_{1L}^{\perp q}$ the opposite constallation, namely transversely 
+$h_{1L}^{\perp q}$ the opposite \bp{configuration}, namely transversely 
 polarized quarks inside a longitudinally polarized nucleon.
@@
 %\includegraphics[width=0.3\textwidth]{\FigPath/ALT_COMPASS_x.pdf}  
-\includegraphics[width=0.9\textwidth]{\FigPath/Fig-COMPASS-A_LT_Pr10.pdf}
+\includegraphics[width=0.9\textwidth]{\FigPath/LT_Pr10.pdf}
 	\caption{\label{g1t_jlab} 
@@
 We observe that the WW-type approximation describes the data within 
-their experimemental uncertainties.
+their experimental uncertainties.
 For comparison results from the theoretical works 
@@
 \centering
-\includegraphics[height=3.1cm]{\FigPath/Fig-COMPASS-A_2_Pr0711_Zgt02.pdf} \quad
+\includegraphics[height=3.1cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \quad
 \includegraphics[height=3.0cm]{\FigPath/AULsin2phi_JLAB_x.pdf}
@@
 	\caption{\label{aul_jlab} 
-	$A_{UL}^{\sin(2\phi_h)}$ as function of $x$ from HERMES
-	\cite{Airapetian:1999tv} and COMPASS \cite{Parsamyan:2015dfa} 
-	experiments (left panel) and at JLab 
-	\cite{Jawalkar:2017ube} in comparison to predictions from
-	WW-type approximation. Predictions from \cite{Avakian:2007mv}
-	are shown for comparison.}
+	$A_{UL}^{\sin(2\phi_h)}$ vs $x$ from the WW-type 
+	approximation in comparison to data from
+	HERMES \cite{Airapetian:1999tv}, 
+	COMPASS \cite{Parsamyan:2015dfa} (left panel), and
+	JLab \cite{Jawalkar:2017ube} (right panel). Results  
+	from \cite{Avakian:2007mv} are also shown.}
 \end{figure}
@@
 
-The Kotzinian-Mulders function $h^{\perp q}_{1L}$ in conjuction with 
-the Boer-Mulders function, and the TMD $g^{\perp q}_{1T}$ in conjuction 
+The Kotzinian-Mulders function $h^{\perp q}_{1L}$ in conjunction with 
+the Boer-Mulders function, and the TMD $g^{\perp q}_{1T}$ in conjunction 
 with the Sivers function obey the positivity bounds 
@@
 Fig.~\ref{h1l_pos} shows that the results of our approach for the 
-``normalized inequalities'' for both TMDs lie between between
+``normalized inequalities'' for both TMDs lie between 
 zero and one, as it is dictated by positivity constraints.
@@
 %========= SECTION 8: TWIST-3 IN WW-TYPE APPROXIMATION ===============
-\section{Subleading twist asymmetries in WW-type approximation}
+\section{subleading-twist asymmetries in WW-type approximation}
 \label{Sec-7:twist-3-and-WW}
@@
 
-\subsection{\boldmath Subleading twist  $A_{LU}^{\sin\phi_h}$}
+\subsection{\boldmath subleading-twist  $A_{LU}^{\sin\phi_h}$}
 \label{Sec-7.1:FLU}
@@
 
-\subsection{\boldmath Subleading twist  $A_{LT}^{\cos\phi_S}$}
+\subsection{\boldmath subleading-twist  $A_{LT}^{\cos\phi_S}$}
 \label{Sec-7.2:FLTcosphiS}
@@
 	F_{LT}^{\cos\phi_S}(x,z,\Phperp) 
-	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\,g_T^q(x)\,D_1^q(z)\;   
+	&=& -\frac{2M_N}{Q}\; x^2 \sum_q e_q^2\,g_T^q(x)\,D_1^q(z)\;   
 	{ \cal G}(\Phperp)\, , \label{Eq:FLTcosphiS-Gauss}\\
 	F_{LT}^{\cos\phi_S}(x,z)
-	&=& -\frac{2M}{Q}\; x^2 \sum_q e_q^2\, g_T^q(x)\,D_1^q(z)\, ,
+	&=& -\frac{2M_N}{Q}\; x^2 \sum_q e_q^2\, g_T^q(x)\,D_1^q(z)\, ,
 	\label{Eq:FLTcosphiS-Gauss-b}
@@
 less bulky) expression in (\ref{Eq:FLTcosphiS-Gauss}) automatically 
-yields (\ref{Eq:FLTcosphiS-Gauss-b}) which is the correct colinear
+yields (\ref{Eq:FLTcosphiS-Gauss-b}) which is the correct collinear
 result for this SIDIS function in Eq.~(\ref{Eq:FLT-collinear})
-in WW-type approximation. This technical remark confirms that
+in WW-type approximation. This technical remark confirms the
 consistency of the scheme suggested in Sec.~\ref{Sec-4.4:evaluation}.
@@
 \newpage
-\subsection{\boldmath Subleading twist  $A_{LT}^{\cos(2\phi_h - \phi_S)}$}
+\subsection{\boldmath subleading-twist  $A_{LT}^{\cos(2\phi_h - \phi_S)}$}
 \label{Sec-7.3:FLTcos2phi-phiS}
@@
 	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\Phperp) 
-	&=& -\frac{2M}{Q} x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\; 
+	&=& -\frac{2M_N}{Q} x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\; 
 	b^{(2)}_{C}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\,
@@
 	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\la\Phperp\ra) 
-	&=& -\frac{2M}{Q} x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\;  
+	&=& -\frac{2M_N}{Q} x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\;  
 	c^{(2)}_{C}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!2}\,
@@
 
-\subsection{\boldmath   Subleading twist  $A_{LL}^{\cos\phi_h}$}
+\subsection{\boldmath   subleading-twist  $A_{LL}^{\cos\phi_h}$}
 \label{Sec-7.3:FLLcosphi}
@@
 	F_{LL}^{\cos \phi_h}(x,z,\Phperp)
-	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
+	&=& -\,\frac{2M_N}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\; 
 	b^{(1)}_{\rm B}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
@@
 	F_{LL}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
-	&=& -\,\frac{2M}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\;
+	&=& -\,\frac{2M_N}{Q}\;x\sum_q e_q^2\,x\,g_{L}^{\perp (1) q}(x)\,D_1^{q}(z)\;
 	c^{(1)}_{\rm B}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\, , 
@@
 \vspace{1cm}
-\includegraphics[width=0.8\textwidth]{\FigPath/Fig-COMPASS-A_LL_Pr0711_Zgt02.pdf}
+\includegraphics[width=0.6\textwidth]{\FigPath/A_LL0_Pr0711_Zgt02.pdf}
 	\caption{\label{allcosphi_jlab} $A_{LL}^{\cos(\phi_h)}$  
-	as a function of $ x $ from a proton target for the COMPASS
-	kinematics. The theoretical curves obtained from the WW-type 
-	approximation are compared to the preliminary COMPASS data 
+	as a function of $ x $ from the WW-type approximation in 
+	comparison to the preliminary COMPASS data 
 	\cite{Parsamyan:2015dfa}. }
@@
 \newpage
-\subsection{\boldmath Subleading twist $A_{UL}^{\sin\phi_h}$ }
+\subsection{\boldmath subleading-twist $A_{UL}^{\sin\phi_h}$ }
 \label{Sec-7.4:FULsinphi}
 
-In the WW-type approximation the asymmetry is described by 
+In WW-type approximation $A_{UL}^{\sin\phi_h}$ is described by 
 $h_L^q(x,\kperp)$ for which we assume the Gaussian Ansatz 
@@
 with $\avkperp_{h_L}=\avkperp_{h_1}$. We explore (\ref{Eq:WW-type-6}) 
-to estimate $xh_L^q(x) = -2 h_{1L}^{\perp(1)q}(x)$ and express
+to estimate $x\,h_L^q(x) = -2 h_{1L}^{\perp(1)q}(x)$ and express
 $h_{1L}^{\perp(1)q}(x)$ through $h_1^a(x)$ according to 
-(\ref{Eq:WW-approx-h1L}). 
-This yield for the structure function the result
+(\ref{Eq:WW-approx-h1L}). This yields 
 \begin{subequations}\ba
 	F_{UL}^{\sin\phi_h}(x,z,\Phperp) 
-	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\; 
+	&=& \frac{2M_N}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\; 
 	b^{(1)}_{\rm A}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
@@
 	F_{UL}^{\sin\phi_h}(x,z,\la\Phperp\ra) 
-	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\;  
+	&=& \frac{2M_N}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\;  
 	c^{(1)}_{\rm A}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,
@@
 \includegraphics[width=0.35\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
-\includegraphics[width=0.35\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} 
-\includegraphics[width=0.7\textwidth]{\FigPath/Fig-COMPASS-A_UL1_Pr0711_Zgt02.pdf}
-\caption{\label{aulsinphi_jlab} The asymmetry $A_{UL}^{\sin\phi_h}$ 
-	as function of $x$ from WW-type approximation in comparison to
-	proton target data from: 
-	(upper panel left) HERMES \cite{Airapetian:2005jc},
-	(upper panel right) JLab \cite{Jawalkar:2017ube}, and 
-	(lower panel) preliminary COMPASS \cite{Parsamyan:2015dfa} data.
-	\TD{Bakur: could you remove the ``rescaled HERMES data''?}
-	\TD{Gunar sent $\pi^0$ data, email from Thu, July 12, 2018,
-	file: sinphi\_UL\_pi0\_HERMES.txt. Alexei, please
-	can you include these data?}}
+\includegraphics[width=0.35\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
+\includegraphics[width=0.7\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}
+\caption{\label{aulsinphi_jlab} 
+	$A_{UL}^{\sin\phi_h}$ for proton target vs $x$ from WW-type 
+	approximation in comparison to data for the following hadrons.
+	Upper panel left: $\pi^\pm$ from HERMES \cite{Airapetian:2005jc}.
+	Upper panel right: $\pi^0$ from HERMES (blue) \cite{Airapetian:2001eg} 
+	and JLab (red) \cite{Jawalkar:2017ube}.
+	Lower panel: preliminary $h^\pm$ COMPASS data \cite{Parsamyan:2015dfa}.}
 \end{figure}
@@
 asymmetry is provided by neutral pions where in WW-type approximation
-the contributions for Collins fragmentation function largely cancel.
+the contributions of Collins fragmentation function largely cancel.
 The WW-type approximation is not able to explain the large effect
-observed at JLab for $\pi^0$ in the large--$x$ region $0.2< x < 0.4$
-in Fig.~\ref{aulsinphi_jlab}.
+observed at HERMES and JLab for $\pi^0$ in the large--$x$ region 
+$0.1< x < 0.5$ in Fig.~\ref{aulsinphi_jlab}. 
+\ps{Overall, the WW-type approximation is not adequate to catch the
+flavor dependence of this asymmetry. This indicates that here the 
+tilde-terms are not negligible, and have a characteristic flavor 
+dependence which is distinct from that of the Collins effect.}
 
@@
 
-\subsection{\boldmath Subleading twist  $A_{UT}^{\sin\phi_S}$}
+\subsection{\boldmath subleading-twist  $A_{UT}^{\sin\phi_S}$}
 \label{Sec-7.6:FUTsinphiS}
 
-In the structure function $F_{UT}^{\sin\phi_S}$ several interesting features
-occur not encountered before. Let us summarize the result and follow up 
-with some comments.
+In this structure function some interesting new features occur.
+The first feature is that after applying the WW-type approximation 
+not one but three terms are left, cf.\ 
+Eqs.~(\ref{FUTsinphiS},~\ref{Eq:WW-type-FUTsinphiS}):
+two terms proportional to $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$,
+and one term proportional to $f_T^q(x,\kperp)$ which is associated with
+the second interesting feature. This T-odd TMD must satisfy the sum rule 
+$\int d^2\kperp \,f_T^q(x,\kperp)=0$, see Eq.~(\ref{Eq:sum-rules-T-odd})
+and Sec.~\ref{Sec-3.8:limitations}. 
+This could be implemented in two ways: one could describe it with a 
+superposition of Gaussians, see App.~\ref{App-B:comment-Todd-twist-3}. 
+But at this point we have no guidance from phenomenology or theory to 
+fix additional parameters. So we choose an alternative 
+and pragmatic solution, namely to neglect the contribution of 
+$f_T^q(x,\kperp)$.\footnote{\label{Footnote:fT-single-Gauss} This
+	corresponds to using a ``single Gaussian'' as 
+	$f_T^q(x,\kperp) = f_T^q(x)\;
+	\frac{\exp(-\kperp^2/\la\kperp^2\ra_{f_T}^{ })}
+	{\pi\la\kperp^2\ra_{f_T}^{ }}$
+	with the ``coefficient'' $f_T^q(x)=0$ as dictated 
+	by the sum rule (\ref{Eq:sum-rules-T-odd}).}
 Assuming Gaussian Ans\"atze (\ref{eq:hTperpnew},~\ref{eq:hTnew}) 
-for the TMDs $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
-in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, we obtain 
+for $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ in 
+App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} and relating 
+them to transversity via the WW-type approximations
+(\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}), the expression 
+for $F_{UT}^{\sin\phi_S}$ is given in terms a single term
 \begin{subequations}\begin{alignat}{1}
 	F_{UT}^{\sin\phi_S}(x,z,\Phperp) 
-	&= \,\frac{2M}{Q}\;x\sum_q e_q^2\,
+	&= \,\frac{2M_N}{Q}\;x\sum_q e_q^2\,
 	h_1^{(1)q}(x)\,H_1^{\perp(1)q}(z)\; \frac{4z^2 m_h\,M_N}{\lambda} 
@@
 $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_1^{ }}$. 
-We can then use (\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}) to relate 
-in the WW-type approximation 
-$-\,\frac12\,x (h_T^{(1)q}(x) - h_T^{\perp(1)q}(x))
-= h_1^{(1)q}(x) = \frac{\la\kperp^2\ra_{h_1}}{2M_N^2}\,h_1^q(x)$.
-
-Some comments are in order. The first interesting feature 
-is that after applying the WW-type approximation more than 
-a single term is left.  Out of the 6 terms contributing to this 
-structure function in (\ref{FUTsinphiS}) after WW-type approximation 
-initially the 3 terms shown in Eq.~(\ref{Eq:WW-type-FUTsinphiS}) 
-remain one of which is proportional to the TMD $f_T^q(x,\kperp)$.
-
-The second interesting feature not encountered before is 
-associated with $f_T^q(x,\kperp)$. This T-odd TMD must 
-satisfy the sum rule (\ref{Eq:sum-rules-T-odd}), see the
-discussion in Sec.~\ref{Sec-3.8:limitations}. This could be
-implemented in two ways: one could describe it with a superposition 
-of Gaussians, see App.~\ref{App-B:comment-Todd-twist-3}.
-At this point, however, we have no guidance from phenomenology or theory 
-to fix additional parameters. Alternatively one could choose a pragmatic 
-and simple solution, namely to neglect the contribution of the TMD
-$f_T^q(x,\kperp)$.\footnote{\label{Footnote:fT-single-Gauss} Notice 
-	that this would correspond to using a ``single Gaussian'' as 
-	$f_T^q(x,\kperp) = f_T^q(x)\;
-	\frac{\exp(-\kperp^2/\la\kperp^2\ra_{f_T}^{ })}
-	{\pi\la\kperp^2\ra_{f_T}^{ }}$
-	with the ``coeffiecient'' $f_T^q(x)=0$ as dictated 
-	by the sum rule (\ref{Eq:sum-rules-T-odd}).}
-The result shown in Eq.~(\ref{Eq:FUTsinphiS-final-PhT})
-is obtained using this second ``pragmatic'' solution.
-
-Interestingly, for the $x$-- and $z$--dependence of the
-structure function $F_{UT}^{\sin\phi_S}(x,z)$ it plays no role
-(footnote~\ref{Footnote:fT-single-Gauss} 
-vs App.~\ref{App-B:comment-Todd-twist-3}) how we model $f_T^q(x,\kperp)$: 
-the result is Eq.~(\ref{Eq:FUTsinphiS-final}) in either case due to the 
-requirement of the sum rule (\ref{Eq:sum-rules-T-odd}).
-Notice that most of the time we focus on the $x$--dependence of 
-asymmetries since this allows us to more directly test the WW-type 
-approximations for TMDs, as opposed to e.g.\ the $P_{hT}$--dependence 
-where in addition we would test at the same time also the Gaussian Ansatz.
-
-The third interesting feature not seen previously is the occurence of a 
-term which drops out upon integrating the structure function over $\Phperp$, 
-cf.\ Eq.~(\ref{Eq:FUTsinphiS-final-PhT}) vs.\ (\ref{Eq:FUTsinphiS-final}).
+The third interesting feature is the occurrence of a term which drops 
+out upon integrating the structure function over $\Phperp$, cf.\ 
+Eq.~(\ref{Eq:FUTsinphiS-final-PhT}) vs.\ (\ref{Eq:FUTsinphiS-final}).
 This is a property of the weight $\omega^{\{2\}}_{\rm B}$, see 
-Eq.~(\ref{Eq:wi}) and App.~\ref{App:factor} (which appears also in 
-$F_{LT}^{\cos\phi_S}$, Eq.~(\ref{FLTcosphiS}), where it drops
-out in WW-type approximation). In principle, this property could  help to 
-discriminate experimentally the terms associated with this weight.
-
-The final result in Eq.~(\ref{Eq:FUTsinphiS-final}) is the
-consistent result for the structure function $F_{UT}^{\sin\phi_S}(x,z)$ in 
-WW-type approximation, see Eq.~(\ref{Eq:FUT-collinear}). Our prediction 
-is therefore $A_{UT}^{\sin\phi_S}(x)=0$. \gs{For positive pions or hadrons
-respectively preliminary HERMES \cite{Schnell:2010zza} and COMPASS 
-\cite{Parsamyan:2015dfa} data are compatible with this prediction.
-However, for negative pions or hadrons the signal is clearly non-zero
-and thus inconsistent with the WW prediction,} see Fig.~\ref{autsinphi_jlab}.
+Eq.~(\ref{Eq:wi}) and App.~\ref{App:factor} (which appears also 
+in $F_{LT}^{\cos\phi_S}$, Eq.~(\ref{FLTcosphiS}), where it drops
+out in WW-type approximation). This property can help 
+to discriminate experimentally the terms associated with this weight.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.4\textwidth]{\FigPath/AUTsinphiS_HERMES_x.pdf}
+\caption{\label{Fig-AUTsinphiS-HERMES} 
+ 	Subleading--twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which 
+	is predicted to vanish in the WW-type approximation, in 
+	comparison to preliminary HERMES data \cite{Schnell:2010zza}.}
+\end{figure}
+
+The final result in Eq.~(\ref{Eq:FUTsinphiS-final}) is the consistent 
+result for the structure function $F_{UT}^{\sin\phi_S}(x,z)$ in WW-type 
+approximation, see Eq.~(\ref{Eq:FUT-collinear}). Our prediction is 
+therefore $A_{UT}^{\sin\phi_S}(x)=0$. 
+\ps{Preliminary 
+HERMES \cite{Schnell:2010zza} (Fig.~\ref{Fig-AUTsinphiS-HERMES}) and 
+COMPASS \cite{Parsamyan:2015dfa} (Fig.~\ref{autsinphi_jlab}) data 
+indicate that at $x\gtrsim 0.1$ the signal is clearly non-zero and 
+thus inconsistent with this WW-type prediction.}
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{\FigPath/Fig-COMPASS-A_UT_Pr10.pdf}
+\includegraphics[width=0.6\textwidth]{\FigPath/UT_Pr10.pdf}
+\includegraphics[width=0.3\textwidth]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf}
 
@@
 
-\subsection{\boldmath Subleading twist  $A_{UT}^{\sin(2\phi_h-\phi_S)}$ }
+\subsection{\boldmath subleading-twist  $A_{UT}^{\sin(2\phi_h-\phi_S)}$ }
 \label{Sec-7.8:FUTsin2phi-phiS}
@@
 	=
-	\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
+	\frac{2M_N}{Q}\;x\sum_q e_q^2\,\Biggl[
 	x \, f_T^{\perp(2)q}(x) \; D_1(z) \;b^{(2)}_{\rm C}\;
@@
 	= \; 
-	\frac{2M}{Q}\;x\sum_q e_q^2\,\Biggl[
+	\frac{2M_N}{Q}\;x\sum_q e_q^2\,\Biggl[
 	x \; f_T^{\perp(2)q}(x) \; D_1(z) \; c^{(2)}_{\rm C} \;
@@
 \newpage
-\subsection{\boldmath Subleading twist  $A_{UU}^{\cos\phi_h}$ }
+\subsection{\boldmath subleading-twist  $A_{UU}^{\cos\phi_h}$ }
 \label{Sec-7.7:FUUcosphi}
@@
 	F_{UU}^{\cos\phi_h}(x,z,\Phperp) 
-	= \frac{2M}{Q}\;x\sum_q e_q^2 & \Biggl[
+	= \frac{2M_N}{Q}\;x\sum_q e_q^2 & \Biggl[
 	- x\,f^{\perp(1)q}(x)\,D_1^q(z)\;b^{(1)}_{\rm B}\,
@@
 	F_{UU}^{\cos\phi_h}(x,z,\la\Phperp\ra) 
-	= \frac{2M}{Q}\;x\sum_q e_q^2 & \Biggl[
+	= \frac{2M_N}{Q}\;x\sum_q e_q^2 & \Biggl[
 	-x\,f^{\perp(1)q}(x)\,D_1^q(z)\;c^{(1)}_{\rm B}\;
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.37\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
+\includegraphics[width=0.37\textwidth]{\FigPath/AUUcosphi_HERMES_x.pdf}
+\caption{\label{auucosphi_jlab} 
+	Left panel: asymmetry $A_{UU}^{\cos\phi_h}$ for positive and negative 
+	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}. Right 
+	panel: the same for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.}
+\end{figure}
+
 The asymmetries $A_{UU}^{\cos\phi_h}$ were measured in experiments at
@@
 HERMES \cite{Airapetian:2012yg}, and COMPASS \cite{Adolph:2014pwc}.
-In Fig.~\ref{auucosphi_jlab} we compare our predictions 
-to the HERMES and COMPASS data. Clearly, the WW-type
-approximation strongly overestimates the data.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.37\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
-\caption{\label{auucosphi_jlab} 
-	Left panel: asymmetry $A_{UU}^{\cos\phi_h}$ for positive and negative 
-	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}. Right 
-	panel: the same for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.
-	\TD{Gunar sent data, email from Thu, July 12, 2018,
-	file: cosNphi\_UU\_HERMES.txt. Maybe we show HERMES $\pi^\pm$ from 
-	proton or deuterium (but not both).
-	\underline{SUGGESTIONS}: include labels ``COMPASS proton data'' and 
-	``HERMES proton (or deuteron) data'' on the figures.
-	Plot range on $y$-axis: -0.35 to 0.}}
-\end{figure}
+In Fig.~\ref{auucosphi_jlab} we compare our predictions to the HERMES and 
+COMPASS data. 
+\ps{The WW-type approximation tends to overstimate the data at
+COMPASS especially in the small-$x$ region. It is also not
+compatible with the flavor dependence seen at HERMES. 
+However both experiments seem not to agree for instance on the shape
+of the asymmetry for negative pions or hadrons. More experimental and
+theoretical work is need to clarify whether this could be due to
+power corrections.}
 
@@
 In this work a comprehensive and complete treatment of SIDIS
-spin and azimuthal asymmetries was presented. The leading--twist
-SIDIS structure functions for the production of unpolarized hadrons,
-which were proven to factorize, are unambiguously expressed in terms 
-of one of 8 twist-2 TMDs convoluted with one of 2 twist-2 FFs.
-For the subleading--twist SIDIS structure functions the situation
+spin and azimuthal asymmetries was presented. 
+The theoretical and phenomenological understanding of most of the
+leading--twist SIDIS structure functions for the production of 
+unpolarized hadrons is relatively advanced: factorization is
+proven, and each structure functions is unambiguously expressed in 
+terms of one of 8 twist-2 TMDs convoluted with one of 2 twist-2 FFs.
+For subleading--twist SIDIS structure functions the situation
 is far more complex for two reasons. First, factorization is not 
@@
 vanish. 
+We remark that the generalized parton model 
+approach of Ref.~\cite{Anselmino:2011ch} provides a description,
+which is largely equivalent to ours.
 
@@
 classes of operators, we prefer to speak of the
-WW-type approximation to distinguish from the colinear case.
+WW-type approximation to distinguish from the collinear case.
 
@@
 approximations receive certain support, though there is 
-less evidence than in the colinear case.
+less evidence than in the collinear case.
 Most importantly, we have conducted systematic tests of
@@
 	$F_{LL}^{\cos\phi_h}$,
-	$F_{UT}^{\sin\phi_S}$,
 	$F_{UT}^{\sin(2\phi_h-\phi_S)}$
@@
 that the WW-type approximations fail in these cases.
-Merely for $F_{UT}^{\sin\phi_S}$ in the region of large-$x$
-there is an indication that the asymmetry could be 
-non-zero while the WW-type approximation proposes
-a much smaller effect. But more higher-statistic data 
-are needed before we can draw definitive conclusions.
 
@@
 	$F_{UL}^{\sin\phi_h}$,
-	$F_{LU}^{\sin\phi_h}$
+	$F_{LU}^{\sin\phi_h}$,
+	$F_{UT}^{\sin\phi_S}$
 the situation is clearer and indicates that here the WW-type
 approximations do not work.
-Incidently, these asymmetries include: 	$F_{UU}^{\cos(2\phi_h)}$ which 
-is the very first non--zero azimuthal asymmetry measured in unpolarized SIDIS,
-$F_{UL}^{\sin\phi_h}$ which is the very first non--zero azimuthal target spin 
-asymmetry measured in SIDIS, and $F_{LU}^{\sin\phi_h}$ which is the 
-very first non--zero azimuthal beam spin asymmetry measured in SIDIS.
-The WW-type prediction for $F_{UU}^{\cos(2\phi_h)}$ suggest a large asymmetry
-which overshoots data by a factor of three. In the case of $F_{UL}^{\sin\phi_h}$
-the WW-type approximation undershoots data by a factor of 2 or so.
+Incidently, these asymmetries include the very first non--zero azimuthal 
+asymmetry measured in unpolarized SIDIS ($F_{UU}^{\cos(\phi_h)}$),
+the very first non--zero target single spin asymmetry measured in SIDIS
+($F_{UL}^{\sin\phi_h}$), and the very first non--zero beam single spin 
+asymmetry measured in SIDIS ($F_{LU}^{\sin\phi_h}$).
+The WW-type prediction for $F_{UU}^{\cos(\phi_h)}$ tends to overshoot
+the data. In the case of $F_{UL}^{\sin\phi_h}$ the WW-type approximation 
+undershoots data by a factor of 2 or so.
 Most interestingly, in the case of $F_{LU}^{\sin\phi_h}$ the WW-type
-approximation predicts exactly a zero asymmetry, but in experiment
-a small but clearly non-zero effect is seen.
-
-The non--aplicability of the WW--type approximation in these three
-cases should not be too surprizing. After all it is a crude method
+approximation predicts exactly a zero asymmetry, but experiments
+see small but non-zero effect.
+
+The non-applicability of the WW--type approximation in these three
+cases should not be too surprising. After all it is a crude method
 to model TMDs and FFs and an uncontrollable ``expansion''
@@
 Among all SIDIS structure functions $F_{LU}^{\sin\phi_h}$ emerges as
-a particularly interesing case: this asymmetry is due to $\bar{q}gq$
+a particularly interesting case: this asymmetry is due to $\bar{q}gq$
 only with no contamination from $\bar{q}q$ terms.
@@
 The results presented in this work are of importance for several reasons.
-First, to the best of our knowledge it is the first complete study 
-of all SIDIS structure functions up to twist-3 in a unique approach. 
-Second, the results are of use for experiments prepared in the near-term 
-(JLab 12) or proposed in the long-term (Electron Ion Collider),
-and provide helpful input for Monte Carlo event generators 
-\cite{Avakian:2015vha}.
-Third, our predictions will help to interpret data.
-
-It is important to remark that the generalized parton model 
-approach of Ref.~\cite{Anselmino:2011ch} provides a description,
-which is largely equivalent to ours. As the quality of the 
-approximations can only be determined experimentally, future
-high--precision data will shed new light and allow us to 
-access new insights abour the quark-gluon structure
-of the nucleon.
+To the best of our knowledge it is the first complete study of all SIDIS 
+structure functions up to twist-3 in a unique approach. The results are 
+useful for experiments prepared in the near-term (JLab 12) or proposed 
+in the long-term (Electron Ion Collider), and provide helpful input for 
+Monte Carlo event generators \cite{Avakian:2015vha}.
+Our predictions will help to pave the way
+towards a better understanding of the quark-gluon structure
+of the nucleon beyond leading twist.
+
+\newpage
 
@@
 and within TMD Collaboration framework, and by the National 
-Science Foundation under Contract No.\ PHY-1623454 (A.P.)
-and Contract No.\ PHY-1406298 (P.S.).
+Science Foundation under Contract No.\ PHY-1623454 (A.P.) and 
+Contract No.\ PHY-1406298 (P.S.) and the Wilhelm Schuler Stiftung (P.S.).
 
@@
 
-\subsection{\boldmath Unpolarised functions $f_1^a(x,k_\perp^2)$ 
-			and $D_1(z,P_\perp^2)$}
+\subsection{\boldmath Unpolarized functions $f_1^a(x,k_\perp^2)$ 
+			and $D_1^a(z,P_\perp^2)$}
 \label{App:basis-f1-D1}
@@
 
-The parameters resulting from calculations or extractions are presented in
-Table~\ref{Table:Gauss-paramaters}. 
-As most extractions of TMDs that we will use are done with the choice of 
-$\avkperp_{f_1} = 0.25$ GeV$^2$, $\avpperp_{D_1}= 0.2$ GeV$^2$, for our numerical estimates in this work  we will use these fixed widths.
-
-Some comments are in order.
-In \cite{Anselmino:2005nn} no attempt was made to assign an uncertainty of the 
-best fit result. The uncertainty of the numbers from \cite{Schweitzer:2010tt}
-includes only the statistical uncertainty, but no systematic uncertainty.
-For comparison lattice results from \cite{Hagler:2009mb} are included
-whose range indicates flavor-dependence 
-(first number $u$--flavor,
-second number $d$--flavor). 
-Notice that this is the contribution of the flavor averaged
-over contributions from the respective quarks and antiquarks.
-Chiral theories predict significant differences in the $\kperp$--behavior
-of sea and valence quarks \cite{Schweitzer:2012hh}.
-We will comment more on the lattice results in the next section.
-In view of the large (and partly underestimated) uncertainties and the 
-fact that those parameters are anti-correlated the numbers from the 
-different approaches quoted in Table~\ref{Table:Gauss-paramaters} 
-can be considered to be in good agreement.
-
-\begin{table}[h!]
+\begin{table}[b!]
 \centering
-\begin{tabular}{|r|l|c|c|c|}
+\begin{tabular}{rlccc}
 \hline
-  & & & & \cr
+%  & & & & \cr
   study \ \ \ \ 
@@
   	& {\footnotesize $[{\rm GeV}^2]$} \cr
-  & & & & \cr
+%  & & & & \cr
 \hline
-  & & & & \cr
+%  & & & & \cr
 \ fit of \cite{Anselmino:2005nn} & 5.0, 0.1, 0.3
@@
 	& 0.11-0.15 \cr
-  & & & & \cr 
+ % & & & & \cr 
 \hline
@@
 \end{table}
+
+The parameters resulting from calculations or extractions are presented in
+Table~\ref{Table:Gauss-paramaters}. 
+As most extractions of TMDs that we will use are done with the choice of 
+$\avkperp_{f_1} = 0.25$ GeV$^2$, $\avpperp_{D_1}= 0.2$ GeV$^2$, for our numerical estimates in this work  we will use these fixed widths.
+
+Some comments are in order.
+In \cite{Anselmino:2005nn} no attempt was made to assign an uncertainty of the 
+best fit result. The uncertainty of the numbers from \cite{Schweitzer:2010tt}
+includes only the statistical uncertainty, but no systematic uncertainty.
+For comparison lattice results from \cite{Hagler:2009mb} are included
+whose range indicates flavor-dependence 
+(first number $u$--flavor,
+second number $d$--flavor). 
+Notice that this is the contribution of the flavor averaged
+over contributions from the respective quarks and antiquarks.
+Chiral theories predict significant differences in the $\kperp$--behavior
+of sea and valence quarks \cite{Schweitzer:2012hh}.
+We will comment more on the lattice results in the next section.
+In view of the large (and partly underestimated) uncertainties and the 
+fact that those parameters are anti-correlated the numbers from the 
+different approaches quoted in Table~\ref{Table:Gauss-paramaters} 
+can be considered to be in good agreement.
 
@@
 \centering
-\begin{tabular}{ccc}
+\begin{tabular}{cccc}
 \hline
-$N_u=0.40$ & $\alpha_u=0.35$ & $\beta_u=2.6$ \\
-$N_d=-0.97$ & $\alpha_d=0.44$ & $\beta_d=0.90$\\
-& $M_1^2=0.19\; \textrm{(GeV}^2$) &   \\
+$N_u=0.40$ & $\alpha_u=0.35$ & $\beta_u=2.6$ & \\
+$N_d=-0.97$ & $\alpha_d=0.44$ & $\beta_d=0.90$ & $M_1^2=0.19\;\textrm{(GeV}^2$)\\
 \hline
 \end{tabular}
-\caption{Best values of the fit of the Sivers functions. Table from Ref.~\cite{Anselmino:2011gs}}
+	\caption{Best values of the fit of the Sivers functions. 
+	Table from Ref.~\cite{Anselmino:2011gs}}
 \label{tab:a}
@@
 \renewcommand{\arraystretch}{1.2} % enlarge line spacing
-\begin{tabular}{@{ }ll}
+\begin{tabular}{@{ }lll}
  \hline
  $N_{u}^{\T}$ = $0.46^{+0.20}_{-0.14}$ & $N_{d}^{\T}$ = $ -1.00^{+1.17}_{-0.00}$ \\
- $\alpha$ =  $1.11^{+0.89}_{-0.66}$ & $\beta$  = $3.64^{+5.80}_{-3.37}$ \\
- $\avkperp_{h_1} = 0.25$ (GeV$^2$) & \\
+ $\alpha$ =  $1.11^{+0.89}_{-0.66}$ & $\beta$  = $3.64^{+5.80}_{-3.37}$ &
+ $\avkperp_{h_1} = 0.25$ (GeV$^2$) \\
  \hline
@@
  $-1.00^{+0.38}_{-0.00}$ \\
- $\gamma$  = $1.06^{+0.45}_{-0.32}$  & $\delta$   = $0.07^{+0.42}_{-0.07}$    \\
- $M^2_C = 1.50^{+2.00}_{-1.12}$ (GeV$^2$) & \\
+ $\gamma$  = $1.06^{+0.45}_{-0.32}$  & $\delta$   = $0.07^{+0.42}_{-0.07}$  &
+ $M^2_C = 1.50^{+2.00}_{-1.12}$ (GeV$^2$) \\
  \hline
 \end{tabular}
-\caption{
-Best values of the 9 free parameters fixing the $u$ and $d$ quark
-transversity distribution functions and the favored and
-disfavored Collins fragmentation functions. The table is from Ref.~\cite{Anselmino:2013vqa}.
+	\caption{Best values of the 9 free parameters fixing 
+	the $u$ and $d$ quark transversity distribution functions and 
+	favored and disfavored Collins fragmentation functions. 
+	The table is from Ref.~\cite{Anselmino:2013vqa}.
 \label{fitpar}}
@@
 
-\subsection{\boldmath Boer-Mulders function $h_{1}^{\perp}(x,k_\perp)$} 
+\subsection{\boldmath Boer-Mulders function $h_{1}^{\perp q}(x,k_\perp)$} 
 \label{App:basis-h1perp}
@@
 \centering
-\begin{tabular}{crl}
+\begin{tabular}{crll}
 \hline
@@
 $N_u=0.35$ & $\alpha_u=0.73$ & $\beta_u=3.46$ \\
-$N_d=-0.9$ & $\alpha_d=1.08$ & $\beta_d=3.46$\\
-& $M_{BM}^2=$&$0.34\; \textrm{(GeV}^2$)    \\
+$N_d=-0.9$ & $\alpha_d=1.08$ & $\beta_d=3.46$
+& $M_{BM}^2=0.34\; \textrm{(GeV}^2$)    \\
 \hline
@@
 
-\subsection{\boldmath Pretzelosity distribution $h_{1T}^{\perp}(x,k_\perp)$}
+\subsection{\boldmath Pretzelosity distribution $h_{1T}^{\perp q}(x,k_\perp)$}
 \label{App:basis-h1Tperp}
@@
 \centering
-\begin{tabular}{l c l l c l}
+\begin{tabular}{l c l l c l l}
 \hline
 $\alpha$ &=& $2.5\pm1.5$ & $\beta$ &=& $2$ fixed \\
- $N_{u}$ &=& $1 \pm 1.4$ & $N_{d}$ &=& $-1 \pm 1.3$\\
- $M_{TT}^2$ &=& $0.18 \pm  0.7$&\multicolumn{3}{l}{(GeV$^2$)}\\ 
+ $N_{u}$ &=& $1 \pm 1.4$ & $N_{d}$ &=& $-1 \pm 1.3$ &
+ $M_{TT}^2=0.18 \pm  0.7$ GeV$^2$\\ 
 \hline
@@
 
-\newpage
 \subsection{Gaussian Ans\"atze for the derived TMDs used in this work}
@@
 
-The Gaussian Ans\"atze for the 8 basis functions were shown 
-in Eqs.~(\ref{Eq:Gauss-f1}--\ref{Eq:Gauss-h1Tperp}) in 
-Sec.~\ref{Sec-4.4:evaluation}, and the pertinent parameters
-and parametrizations were reviewed in App.~\ref{App:basis}.
-Besides the basis function we also need Ans\"atze for the 
-following TMDs as listed below:
+Having discussed the Gaussian Ans\"atze for the 8 basis functions
+in Eqs.~(\ref{Eq:Gauss-f1}--\ref{Eq:Gauss-h1Tperp}) of
+Sec.~\ref{Sec-4.4:evaluation} and in App.~\ref{App:basis},
+we list here the Ans\"atze for the following derived TMDs:
 \begin{subequations}\begin{align}
@@
 which are T-odd, appear in the decompositions of the correlator with no 
-explicit $k_\perp^j$--prefactors, and would have colinear PDF counterparts. 
+explicit $k_\perp^j$--prefactors, and would have collinear PDF counterparts. 
 But T-odd PDFs are forbidden by time-reversal and parity invariance of 
@@
 the present stage, but in principle this could be a 
-pragmatic way of modelling the TMD $f_T^q(x,\kperp)$
+pragmatic way of modeling the TMD $f_T^q(x,\kperp)$
 and analogously $h^q(x,\kperp)$, $e_L^q(x,\kperp)$.
@@
 reproduction, and verification of our results presented in this paper. 
-Second, the package may prove useful for \ps{experimentalists in need of}
+Second, the package may prove useful for experimentalists in need of
 estimates of measured quantities for certain kinematics of a particular 
-experiment. Third, the \ps{phenomenological workers in the} community 
+experiment. Third, the phenomenological workers in the community 
 will have an easy access to our results for comparison and/or use in 
@@
 open source access to the codes used in a project is the right way of 
-handling scientific information in the 21$^{st}$ century. \ps{For example,}
+handling scientific information in the 21$^{st}$ century. For example,
 collinear parton distribution functions are well tabulated in 
@@
 fragmentation function still need a dedicated repository. There exist 
-already several databases \ps{which are} being developed for extensions 
+already several databases which are being developed for extensions 
 of collinear one-dimensional picture of the nucleon structure.  
@@
 
-If you use this package, please, \ps{cite} this paper and the link to 
+If you use this package, please, cite this paper and the link to 
 the repository. Please, acknowledge using any of the extracted TMDs 
-\ps{presented} in this package. The corresponding \texttt{bibitem} 
-codes are \ps{included} in the description of each TMD function.
+presented in this package. The corresponding \texttt{bibitem} 
+codes are included in the description of each TMD function.
 
@@
 several visualizations of functions, asymmetries, and SIDIS cross-sections. 
+Please note that, for now, the package can compute the aforementioned 
+observables for a proton target, detected charged pions and beam 
+helicities \ps{$\pm1$ or $0$ (with the latter denoting an unpolarized beam).}
 Make sure that you do not move \texttt{example.nb} to another directory 

### 2018-07-20 tex/test-WW-type-00z_old.tex
final

--- 2018-07-18 tex/test-WW-type-00z.tex
@@
 \centering
-%\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_x.pdf}  
-%\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_PT.pdf}
-\includegraphics[width=0.3\textwidth]{\FigPath/Screenshot-Fig-COMPASS-A_UT_Pr10-left-panel-up.png} \ 
-\includegraphics[width=0.3\textwidth]{\FigPath/Screenshot-Fig-COMPASS-A_UT_Pr10-left-panel-down.png}
-\includegraphics[width=0.3\textwidth]{\FigPath/AUTPretzelosity_HERMES_x.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pip.pdf}  
+\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pim.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_HERMES_x.pdf}
 
@@
 	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2010se} 
-	and HERMES \cite{Schnell:2010zza} in comparison to the best fit 
+	and $A_{UT, < y >}^{\sin(3 \phi_h - \phi_S)}$ HERMES \cite{Schnell:2010zza} in comparison to the best fit 
 	(whose 1-$\sigma$ uncertainty band is compatible with zero) 

### 2018-07-20 tex/test-WW-type-00z.tex
final

@@
 \allowdisplaybreaks
+
+% section 5.4 - is transversity really the only information on the tensor charge. how about lattice?
+% FIgure 7: is it the <y> asymmetry (including prefactors)?
+% section 5.6 (lines 819 ff) partially repetition (cubic Phperp suppression) and need reference to HERMES plot.
+% figure 16 claims to be A_{LL}^{\cos\phi} but is just A_{LL}
 
@@
 %Editing commands
-\newcommand{\TD}[1]{{{\bf TODO:} \color[rgb]{0.65,0,0.15} #1}}
-\newcommand{\AP}[1]{{\bf AP:} {\color{red} #1}}
+%\newcommand{\TD}[1]{{{\bf TODO:} \color[rgb]{0.65,0,0.15} #1}}
+%\newcommand{\AP}[1]{{\bf AP:} {\color{red} #1}}
 
@@
 
-\newcommand{\ak}[1]{\orange{#1}}
-\newcommand{\ps}[1]{\blue{#1}}
-\newcommand{\gs}[1]{{\color[rgb]{0.65,0,0.65}#1}}
-\newcommand{\bp}[1]{{\color[rgb]{0,0.65,0.35}#1}}
-\newcommand{\ms}[1]{\darkgreen{#1}}
-\newcommand{\kt}[1]{{\color[rgb]{0.1,0.5,0}#1}}
-
-\newcommand{\SB}[1]{{\bf SB:} {\color{magenta} #1}}
+%\newcommand{\ak}[1]{\orange{#1}}
+%\newcommand{\ps}[1]{\blue{#1}}
+%\newcommand{\gs}[1]{{\color[rgb]{0.65,0,0.65}#1}}
+%\newcommand{\bp}[1]{{\color[rgb]{0,0.65,0.35}#1}}
+%\newcommand{\ms}[1]{\darkgreen{#1}}
+%\newcommand{\kt}[1]{{\color[rgb]{0.1,0.5,0}#1}}
+
+%\newcommand{\SB}[1]{{\bf SB:} {\color{magenta} #1}}
 
@@
 \newcommand{\asympre}[2]{{A_{#1,\langle y\rangle}^{#2}}}
+
+\newcommand{\WWtype}{\ensuremath{\stackrel{\text{\scriptsize WW--type}}{\approx}}}
 
@@
 
-\preprint{\red{version ``00y''}; JLAB-THY-18-XXXX}
+\preprint{\red{version ``00z''}; \today; JLAB-THY-18-XXXX}
 
@@
 	10125 Torino, Italy}
-\affiliation[f]{Institut f\"ur Theoretische Physik, Universit\"at 
+\affiliation[f]{Institut f\''ur Theoretische Physik, Universit\''at 
   	Regensburg, 93040 Regensburg, Germany}
@@
 	IKERBASQUE, Basque Foundation for Science, 48013 Bilbao, Spain}
-\affiliation[j]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
-	D-72076 T\"ubingen, Germany} % Auf der Morgenstelle 14,
+\affiliation[j]{Institute for Theoretical Physics, Universit\''at T\''ubingen,
+	D-72076 T\''ubingen, Germany} % Auf der Morgenstelle 14,
 
@@
 	Wandzura--Wilczek approximation, 
-	semi-inclusive deep inelastic scattering,
+	semi-inclusive deep-inelastic scattering,
 	transverse momentum dependent distribution and fragmentation 
@@
 
-\linenumbers % line numbers
+%\linenumbers % line numbers
 
@@
 \flushbottom
-
-\subsection*{Color Legend}
-
-General comments: 
-	\TD{dark red color, command: {$\backslash{\rm TD}\{\dots\}$}}\\
-Alexei's corrections: 
-	\AP{redish color, command: {$\backslash{\rm AP}\{\dots\}$}}\\
-Aram's corrections: 
-	\ak{orange color, command: {$\backslash{\rm ak}\{\dots\}$}}\\
-Bakur's corrections: 
-	\bp{green-blue color, command: {$\backslash{\rm bp}\{\dots\}$}}\\
-Gunar's corrections: 
-	\gs{violett color, command: {$\backslash{\rm gs}\{\dots\}$}}\\
-Kemal's corrections: 
-	\kt{greenish color, command: {$\backslash{\rm kt}\{\dots\}$}}\\
-Marc's corrections: 
-	\ms{green color, command: {$\backslash{\rm ms}\{\dots\}$}}\\
-Peter's corrections: 
-	\ps{blue color, command: {$\backslash{\rm ps}\{\dots\}$}}\\
-Anatoli Vasilievich, Bakur, Bernie, Saman: \\
-	corrections already introduced in black color \& confirmed by e-mail.
-
 \newpage
+%\subsection*{Color Legend}
+
+%General comments: 
+%	\TD{dark red color, command: {$\backslash{\rm TD}\{\dots\}$}}\\
+%Alexei's corrections: 
+%	\AP{redish color, command: {$\backslash{\rm AP}\{\dots\}$}}\\
+%Aram's corrections: 
+%	\ak{orange color, command: {$\backslash{\rm ak}\{\dots\}$}}\\
+%Bakur's corrections: 
+%	\bp{green-blue color, command: {$\backslash{\rm bp}\{\dots\}$}}\\
+%Gunar's corrections: 
+%	\gs{violett color, command: {$\backslash{\rm gs}\{\dots\}$}}\\
+%Kemal's corrections: 
+%	\kt{greenish color, command: {$\backslash{\rm kt}\{\dots\}$}}\\
+%Marc's corrections: 
+%	\ms{green color, command: {$\backslash{\rm ms}\{\dots\}$}}\\
+%Peter's corrections: 
+%	\ps{blue color, command: {$\backslash{\rm ps}\{\dots\}$}}\\
+%Anatoli Vasilievich, Bakur, Bernie, Saman: \\
+%	corrections already introduced in black color \& confirmed by e-mail.
+
 %======= SECTION 1: INTRODUCTION =====================================
@@
 A great deal of what is known about the quark-gluon structure of 
-nucleon is due to studies of parton distribution functions (PDFs) 
-in deep-inelastic reactions. Leading--twist PDFs  tell us  how likely 
+nucleons is due to studies of parton distribution functions (PDFs) 
+in deep-inelastic reactions. Leading-twist PDFs  tell us  how likely 
 it is to find an unpolarized parton 
@@
 One way to do this consists in a systematic inclusion of transverse 
-parton momenta $\kperp$ whose effects manifest themselves in terms of
+parton momenta $\kperp$, whose effects manifest themselves in terms of
 transverse momenta of the reaction products in the final state.
@@
 transverse momentum dependent distribution functions (TMDs) 
-and fragmentation functions (FFs)
+and fragmentation functions (FFs),
 which are defined in terms of quark-quark correlators 
 \cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,Bacchetta:2006tn},
-and depend on two independent variables: \bp{for TMDs,} 
+and depend on two independent variables: for TMDs, 
 on the fraction $x$ of nucleon 
-momentum carried by parton and intrinsic transverse momentum $\kperp$ 
-of the parton, \bp{For FFs, on the fraction $z$ of the parton momentum 
+momentum carried by the parton and intrinsic transverse momentum $\kperp$ 
+of the parton. For FFs, on the fraction $z$ of the parton momentum 
 transferred to the hadron for and the transverse momentum of the hadron
-acquired during the fragmentation process}. 
+acquired during the fragmentation process. 
 Being a vector in the plane transverse with respect to 
@@
 $\kperp$ allows us to access novel information on the nucleon spin structure 
-through correlations of $\kperp$ with nucleon and/or parton spin. The 
+through correlations of $\kperp$ with the nucleon and/or parton spin. The 
 latter is a well-defined concept for twist-2 TMDs interpreted in 
-the infinite momentum frame or in lightcone quantization formalism.
+the infinite momentum frame or in the lightcone quantization formalism.
 
@@
 By exploring various possibilities for the lepton beam and target 
-polarizations unambiguous information can be accessed on the 8 leading--twist 
+polarizations unambiguous information can be accessed on the 8 leading-twist 
 TMDs \cite{Boer:1997nt} and, if one assumes factorization, on certain
-linear combinations of the 16 subleading--twist TMDs 
+linear combinations of the 16 subleading-twist TMDs 
 \cite{Goeke:2005hb,Bacchetta:2006tn}.
@@
 Complementary information can be obtained 
-from the Drell-Yan process \cite{Arnold:2008kf}, 
+from the Drell--Yan process \cite{Arnold:2008kf}, 
 and $e^+e^-$ annihilation \cite{Metz:2016swz}.
@@
 Experience from collinear PDFs encourages to explore this possibility: 
-the twist-3 $g_T^a(x)$ and $h_L^a(x)$ can be \bp{respectively} expressed 
+the twist-3 $g_T^a(x)$ and $h_L^a(x)$ can be respectively expressed 
 in terms of contributions from twist-2 $g_1^a(x)$ and $h_1^a(x)$, and 
-additional quark-gluon-quark ($\bar{q}gq$) correlations or current 
-quark mass terms \cite{Wandzura:1977qf,Jaffe:1991ra}
+additional quark-gluon-quark ($\bar{q}gq$) correlations or current-quark 
+mass terms \cite{Wandzura:1977qf,Jaffe:1991ra}
 (the index $a=q\,,\bar q$ does not include gluons for
-$h_1^a$, $h_L^a$ and other chiral odd TMDs below).
+$h_1^a$, $h_L^a$ and other chiral-odd TMDs below).
 We shall refer to the latter generically as $\bar{q}gq$--terms, keeping in 
 mind one deals in each case with matrix elements of different operators.
-The $\bar{q}gq$--correlations contain new insights on hadron structure 
+The $\bar{q}gq$--correlations contain new insights on hadron structure,
 which are worthwhile exploring for their own sake, 
@@
 The present work is the first study of all SIDIS structure functions up to 
-twist-3 in a unique approach. Our results are of importance for experiments 
-\bp{performed or in preparation at HERMES, COMPASS,} Jefferson Lab (JLab) with 
-12$\,$GeV beam energy upgrade, or proposed in the long-term 
+twist-3 in a unique approach. Our results are of importance for measurements 
+performed or in preparation at HERMES, COMPASS, Jefferson Lab (JLab) with 
+12$\,$GeV beam-energy upgrade, or proposed in the long-term 
 (Electron Ion Collider), and provide helpful input for the 
@@
 
-\bp{Our predictions, whether confirmed or not supported by current and 
-future experimental data, will in any case provide a useful benchmark,}
+Our predictions, whether confirmed or not supported by current and 
+future experimental data, will in any case provide a useful benchmark,
 and call for dedicated theoretical studies to explain (i) why the 
@@
 We will systematically apply the WW and/or WW-type approximations
-to SIDIS structure at leading (Sec.~\ref{Sec-6:twist-2-and-WW}) 
+to SIDIS structure functions at leading (Sec.~\ref{Sec-6:twist-2-and-WW}) 
 and subleading (Sec.~\ref{Sec-7:twist-3-and-WW}) twist, and
@@
 technical details. 
-	In App.~C we describe \bp{an open source package implemented 
+	In App.~C we describe an open-source package implemented 
 	in \texttt{mathematica}~\cite{Mathematica} (already available) 
-	and \texttt{Python} (to be released in the near future) which is 
-	made publicly available on \texttt{github.com}.}\footnote{\href{%
+	and \texttt{Python} (to be released in the near future) that is 
+	made publicly available on \texttt{github.com}: {\href{
 	https://github.com/prokudin/WW-SIDIS}{
@@
 
-\newpage
 %======= SECTION 2: SIDIS & TMDs & FFs ===============================
@@
 describe the SIDIS structure functions.
-
+\newpage
 \subsection{The SIDIS process}
@@
         \caption{\label{fig-kin-SIDIS}
-    	Kinematics of SIDIS process $lN\to l^\prime h X$
-	in 1-photon exchange approximation.}
+    	Kinematics of the SIDIS process $lN\to l^\prime h X$
+	in the 1-photon exchange approximation.}
 \vspace{-5mm}
@@
 The SIDIS process  $lN\to l^\prime h X$ is sketched in 
-Fig.~\ref{fig-kin-SIDIS}. Here $l$ and $P$ are momenta of incoming 
+Fig.~\ref{fig-kin-SIDIS}. Here, $l$ and $P$ are the momenta of the incoming 
 lepton and nucleon, $l^\prime$ and $P_h$ are the momenta of the outgoing
-lepton and produced hadron. The virtual photon momentum $q=l-l^\prime$ 
-\bp{defines} the z-axis, and $l^\prime$ points in the direction of the x-axis 
+lepton and produced hadron. The virtual-photon momentum $q=l-l^\prime$ 
+defines the z-axis, and $l^\prime$ points in the direction of the x-axis 
 from which azimuthal angles are counted. The relevant kinematic invariants 
@@
 charged leptons (electrons, positrons, muons) at $Q^2 \ll M_Z^2$ 
-in the single photon exchange approximation,
-\bp{where $M_Z$ denotes the mass of the $Z^0$ electroweak gauge boson.}
+in the single-photon exchange approximation,
+where $M_Z$ denotes the mass of the $Z^0$ electroweak gauge boson.
 In addition to $x$, $y$, $z$ the cross section is also differential 
@@
 of its momentum component $\Phperp$ perpendicular with respect to the 
-virtual photon momentum.  The cross section is also 
+virtual-photon momentum.  The cross section is also 
 differential with respect to the azimuthal angle $\psi_l$ 
-\bp{characterizing the overall orientation of the lepton scattering plane 
+ characterizing the overall orientation of the lepton scattering plane 
 around the incoming lepton direction. The angle is calculated with respect 
 to an arbitrary reference axis, which in case of transversely polarized 
-targets is chosen to be the direction of $S_T$. In DIS limit 
+targets is chosen to be the direction of $S_T$. In the DIS limit 
 $\psi_l \approx \phi_S$, where the latter is the azimuthal angle of 
-the spin-vector defined as in Fig.~\ref{fig-kin-SIDIS}.}
+the spin-vector defined as in Fig.~\ref{fig-kin-SIDIS}.
 It is convenient to define the unpolarized 
@@
 and a structure function (sometimes denoted as $F_{UU,L}$) arising from
-longitudinal polarization of the virtual photon (and \bp{another} the 
+longitudinal polarization of the virtual photon (and another  
 structure function $\propto S_T\,\sin( \phi_h-\phi_S)$, see below).
@@
 	p_3 = \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2} 	\, , \;\;\;
-	p_4 = \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2}     	\, .
+	p_4 = \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2}     	\, ,
 \ee
-and the asymmetries are defined as \bp{follows}
+and the asymmetries are defined as follows
 \be
@@
 \ee
-Here the first \bp{subscript} $X=U(L)$ denotes the unpolarized beam
+Here the first subscript $X=U(L)$ denotes the unpolarized beam
 (longitudinally polarized beam with helicity $\lambda$). The second 
-\bp{subscript} $Y=U(L,T)$ refers to the target which can be unpolarized
-(or longitudinally, transversely polarized with respect to virtual photon).
+subscript $Y=U(L\text{ or }T)$ refers to the target, which can be unpolarized
+(longitudinally or transversely polarized with respect to virtual photon).
 The superscript ``weight'' indicates the azimuthal dependence with no index 
@@
 factor $M_N/Q$ in their definitions, see below, 
-\bp{where $M_N$ is the nucleon mass.} In our treatment to $1/Q^2$ 
-accuracy we neglect two structure functions due to longitudinal virtual 
-photon polarization which contribute at order ${\cal O}(M_N^2/Q^2)$ in the 
+where $M_N$ is the nucleon mass. In our treatment to $1/Q^2$ 
+accuracy we neglect two structure functions due to longitudinal virtual-photon 
+polarization, which contribute at order ${\cal O}(M_N^2/Q^2)$ in the 
 partonic description of the process, one being $F_{UU,L}$ and the other 
@@
 corresponding asymmetries $\asympre{XY}{\rm weight}$.
-For instance, in unpolarized case one has 
+For instance, in the unpolarized case one has 
 \be
@@
 where $\gamma=2M_Nx/Q$ signals the twist-3 character of $F_{LT}^{\cos\phi_S}(x,z)$.
-Notice that $F_{UT}^{\sin\phi_S}(x,z)$ has no DIS counterpart due to time reversal
+Notice that $F_{UT}^{\sin\phi_S}(x,z)$ has no DIS counterpart due to time-reversal
 symmetry of strong interactions, and terms suppressed by $1/Q^2$ are 
@@
 $a^\pm=(a^0\pm a^3)/\sqrt{2}$. 
-The light-cone direction is singled out by the virtual photon momentum 
+The light-cone direction is singled out by the virtual-photon momentum 
 and transverse vectors like $\bfkperp$ are perpendicular to it. In the
-virtual-photon--nucleon center-of-mass frame, nucleon and the partons 
+virtual-photon--nucleon center-of-mass frame, the nucleon and the partons 
 inside it move in the $(+)$--lightcone direction, while the struck 
-quark and the produced hadron move in $(-)$--light-cone direction.
+quark and the produced hadron move in the $(-)$--light-cone direction.
 In the nucleon rest frame the polarization vector is given by 
@@
 
-The 8 leading--twist TMDs \cite{Boer:1997nt} are projected out from 
+The 8 leading-twist TMDs \cite{Boer:1997nt} are projected out from 
 the correlator (\ref{Eq:correlator}) as follows (\blue{blue: T-even} TMDs, 
 \red{red: T-odd} TMDs; all TMDs depend on $x$, $k_\perp$, renormalization 
-scale and carry a flavor index which we do not indicate for brevity)
+scale and carry a flavor index which we do not indicate for brevity):
 \begin{subequations}\ba
@@
     	S_L\,\blue{h_L} + \frac{\bfkperp\cdot{\bm S}_T}{M_N}\,\blue{h_T}
-    	\biggr]. \label{Eq:TMD-pdfs-VI}
+    	\biggr], \label{Eq:TMD-pdfs-VI}
 \ea\end{subequations}
@@
     \ee
-In this work we will consider only unpolarized final state hadrons.
-If the produced hadron moves fast in the $(-)$ light cone direction, 
+In this work we will consider only unpolarized final-state hadrons.
+If the produced hadron moves fast in the $(-)$ light-cone direction, 
 the twist-2 FFs are projected out as 
@@
 Eqs.~(\ref{Eq:SIDIS-leading},~\ref{Eq:SIDIS-subleading}) are described 
-in Bjorken limit at tree level in terms of convolutions of TMDs 
+in the Bjorken limit at tree level in terms of convolutions of TMDs 
 and FFs. We define the unit vector $\bfhp   = \bfPhperp/\Phperp$ 
@@
 \ba
- F_{UU}	&=&{\cal C}\biggl[\;\omega^{\{0\}}\,f_1 D_1 \;\biggr] \label{FUU}\\
- F_{LL}	&=&{\cal C}\biggl[\;\omega^{\{0\}}\,g_1 D_1 \;\biggr] \label{FLL}\\
+ F_{UU}	&=&{\cal C}\biggl[\;\omega^{\{0\}}\,f_1 D_1 \;\biggr] \, , \label{FUU}\\
+ F_{LL}	&=&{\cal C}\biggl[\;\omega^{\{0\}}\,g_1 D_1 \;\biggr] \, , \label{FLL}\\
  F_{UT}^{\sin\left(\phi_h +\phi_S\right)} 
-	&=& {\cal C}\biggl[\;\omega^{\{1\}}_{\rm A} \,h_{1} H_1^{\perp}\;\biggr]
+	&=& {\cal C}\biggl[\;\omega^{\{1\}}_{\rm A} \,h_{1} H_1^{\perp}\;\biggr] \, ,
 	\label{Eq:FUTCol}\\
  F_{UT}^{\sin\left(\phi_h -\phi_S\right)} 
-	&=& {\cal C}\biggl[-\,\omega^{\{1\}}_{\rm B} \,f_{1T}^{\perp } D_1\,\biggr]
+	&=& {\cal C}\biggl[-\,\omega^{\{1\}}_{\rm B} \,f_{1T}^{\perp } D_1\,\biggr] \, ,
 	\label{Eq:FUTSiv}\\
  F_{LT}^{\cos(\phi_h -\phi_S)} 
-	&=& {\cal C}\biggl[\,\omega^{\{1\}}_{\rm B} \,g_{1T}^\perp D_1\biggr] 
+	&=& {\cal C}\biggl[\,\omega^{\{1\}}_{\rm B} \,g_{1T}^\perp D_1\biggr] \, ,
 	\label{Eq:FLT-twist-2}\\
@@
 	&=& {\cal C}\biggl[\;\omega^{\{2\}}_{\rm AB}\,h_{1}^{\perp }\,H_{1}^{\perp }\;
-	\biggr] \label{F_UUcos2phi}\\
+	\biggr] \, , \label{F_UUcos2phi}\\
  F_{UL}^{\sin 2\phi_h} 	
 	&=& {\cal C}\biggl[\;\omega^{\{2\}}_{\rm AB}\,h_{1L}^{\perp } H_{1}^{\perp }\; 
-	\biggr] \label{F_UUsin2phi}\\
+	\biggr] \, , \label{F_UUsin2phi}\\
  F_{UT}^{\sin\left(3\phi_h -\phi_S\right)} 
@@
 	- \omega^{\{1\}}_{\rm B} \biggl( x  f^{\perp } D_1
-   	+ r_h^{ }\,\,h_{1}^{\perp } \frac{\tilde{H}}{z}\biggr)\biggr]\;
+   	+ r_h^{ }\,\,h_{1}^{\perp } \frac{\tilde{H}}{z}\biggr)\biggr] ,
 	\label{Eq:FUUcosphi}\\
@@
    	\biggl( x   g^{\perp }  D_1 
-   	+ r_h^{ }\,\, h_1^{\perp } \,\frac{\tilde{E}}{z} \biggr)\biggr]\;
+   	+ r_h^{ }\,\, h_1^{\perp } \,\frac{\tilde{E}}{z} \biggr)\biggr] ,
 	\label{FLUsinphi}\;\;\;\;\;\\
@@
     	\biggl( x  f_{L}^{\perp }  D_1 \!
-   	- r_h^{ }\,\, h_{1L}^{\perp }  \frac{\tilde{H}}{z}\biggr)\biggr]\;
+   	- r_h^{ }\,\, h_{1L}^{\perp }  \frac{\tilde{H}}{z}\biggr)\biggr] ,
 	\label{FULsinphi}\\
@@
    	\biggl( x   g_L^{\perp }   D_1
-   	+  r_h^{ }\,\,h_{1L}^{\perp } \frac{\tilde{E}}{z}\biggr)\biggr]
+   	+  r_h^{ }\,\,h_{1L}^{\perp } \frac{\tilde{E}}{z}\biggr)\biggr]  ,
 	\label{FLLcosphi}\;\;\;\;\;\;\;\;\;\\
@@
 	+ r_h^{ }\, f_{1T}^{\perp } \,\frac{\tilde{D}^{\perp }}{z}
-   	\biggr) \biggr]\; \label{FUTsinphiS}\\ 
+   	\biggr) \biggr]\, , \label{FUTsinphiS}\\ 
 	F_{LT}^{\cos \phi_S} 
@@
    	+ r_h^{ }\,f_{1T}^{\perp }\,\frac{\tilde{G}^{\perp }}{z}\biggr)\biggr]
-	\; \label{FLTcosphiS} \\ \hspace{-5mm}
+	\, , \label{FLTcosphiS} \\ \hspace{-5mm}
 	F_{UT}^{\sin(2\phi_h -\phi_S)} 
@@
    	\biggl( x   f_T^{\perp } D_1
-   	- r_h^{ }\, \, h_{1T}^{\perp }  \frac{\tilde{H}}{z}\biggr) \biggr]\\
+   	- r_h^{ }\, \, h_{1T}^{\perp }  \frac{\tilde{H}}{z}\biggr) \biggr] \, , \\
 	F_{LT}^{\cos(2\phi_h - \phi_S)} 
@@
    	\biggl( x   g_T^{\perp }   D_1
-   	+ r_h^{ }\, \, h_{1T}^{\perp }  \frac{\tilde{E}}{z}\biggr)\biggr]\; 
+   	+ r_h^{ }\, \, h_{1T}^{\perp }  \frac{\tilde{E}}{z}\biggr)\biggr]\, ,
 	\label{FLTsin(2phi-phiS)}
@@
  as $F_{UU,L}$ and $F_{UT,L}^{\sin( \phi_h-\phi_S)}$) 
- due to longitudinal virtual photon polarization which are 
+ due to longitudinal virtual-photon polarization, which are 
  of order ${\cal O}(M^2/Q^2)$ in the TMD partonic description.
 
-The structures surviving $\Phperp$--integration of the SIDIS cross section in 
+The structure functions surviving $\Phperp$--integration of the SIDIS cross section in 
 (\ref{Eq:SIDIS-leading-integrated},~\ref{Eq:SIDIS-subleading-integrated})
@@
 terms of collinear PDFs and FFs as follows (here the 
-sum rules (\ref{Eq:sum-rules-T-odd}) are used)
+sum rules (\ref{Eq:sum-rules-T-odd}) are used):
 \begin{subequations}\ba
-	F_{UU}(x,z) &=& x\sum\limits_ae_a^2\,f_1^a(x)\,D_1^a(z)
+	F_{UU}(x,z) &=& x\sum\limits_ae_a^2\,f_1^a(x)\,D_1^a(z) \, ,
 	\label{Eq:FUU-collinear}\\
-	F_{LL}(x,z) &=& x\sum\limits_ae_a^2\,g_1^a(x)\,D_1^a(z)
+	F_{LL}(x,z) &=& x\sum\limits_ae_a^2\,g_1^a(x)\,D_1^a(z) \, ,
 	\label{Eq:FLL-collinear}\\
  	F_{LT}^{\cos\phi_S}(x,z) &=& -\,\frac{2M_N}{Q}\; x\sum_a e_a^2\,
-	\biggl(x\,g_T^q(x)\,D_1^a(z)+r_h\,h_1^a(x)\frac{\tilde{E}^a(z)}{z}\biggr)
+	\biggl(x\,g_T^q(x)\,D_1^a(z)+r_h\,h_1^a(x)\frac{\tilde{E}^a(z)}{z}\biggr) \, ,
 	\label{Eq:FLT-collinear}\\
 	 F_{UT}^{\sin\phi_S}(x,z) &=& -\,\frac{2\,m_h}{Q}\; x\sum_a e_a^2\,
-	h_1^a(x)\frac{\tilde{H}^a(z)}{z}
+	h_1^a(x)\frac{\tilde{H}^a(z)}{z} \, .
 	\label{Eq:FUT-collinear}
@@
 Finally, integrating over $z$, summing over hadrons, and 
-using the sum rules for the T-odd FFs 
+using the sum rules for the T-odd FFs, 
 $\sum_h\int d z\;\tilde{E}^a(z)=0$ and
-$\sum_h\int d z\;\tilde{H}^a(z)=0$ we recover
+$\sum_h\int d z\;\tilde{H}^a(z)=0$, we recover
 Eqs.~(\ref{Eq:DIS-F1}--\ref{Eq:DIS-zero}) and obtain for the DIS structure 
@@
 \begin{subequations}\ba
-    F_1(x) & = & \frac{1}{2}\sum_a e_a^2\,f_1^a(x) \label{Eq:DIS-F1-II}\\
-    g_1(x) & = & \frac{1}{2}\sum_a e_a^2\,g_1^a(x) \label{Eq:DIS-g1-II}\\
-    g_2(x) & = & \frac{1}{2}\sum_a e_a^2\,g_T^a(x)\;-\;g_1(x) \label{Eq:DIS-g2}
+    F_1(x) & = & \frac{1}{2}\sum_a e_a^2\,f_1^a(x) \, , \label{Eq:DIS-F1-II}\\
+    g_1(x) & = & \frac{1}{2}\sum_a e_a^2\,g_1^a(x) \, , \label{Eq:DIS-g1-II}\\
+    g_2(x) & = & \frac{1}{2}\sum_a e_a^2\,g_T^a(x)\;-\;g_1(x)  \; .\label{Eq:DIS-g2}
 	\hspace{25mm}
@@
 
-In fact, a lot of progress has been achieved in recent years in the 
+A lot of progress has been achieved in recent years in the 
 theoretical understanding of leading-twist observables within the TMD 
-framework --- including definition, renormalization and evolution of 
+framework, including definition, renormalization and evolution of 
 leading-twist TMDs \cite{Aybat:2011zv,Aybat:2011ge,Echevarria:2014xaa},
@@
 Bacchetta:2006tn}, 
-based on a TMD tree-level formalism which we adopt here.
+based on a TMD tree-level formalism, which we adopt here.
 In fact, the results of Refs.~\cite{Metz:2004je,Gamberg:2006ru}
@@
 
-%\newpage
+%
 %======= SECTION 3: WW APPROXIMATIONS ================================
@@
 (here the $\la\dots\ra$ denote symbolically the matrix elements 
-which enter the definitions of TMDs or FFs)
+which enter the definitions of TMDs or FFs):
 \be\label{Eq:WW-generic}
@@
 of QCD equations of motion in twist-2 parts, and pure twist-3 
-(interaction dependent) $\bar{q}gq$--terms and current quark mass
-terms. We denote $\bar{q}gq$--terms and mass-terms collectively 
+(interaction dependent) $\bar{q}gq$--terms and current-quark mass
+terms. We denote $\bar{q}gq$--terms and mass terms collectively 
 and symbolically by functions with a tilde.
@@
 hadronic and $Q$ the hard scale).
-The two definitions coincide for twist-2 quantities, but higher twist
+The two definitions coincide for twist-2 quantities, but higher-twist
 observables in general contain ``contaminations'' by leading twist.
@@
 approximations \cite{Wandzura:1977qf,Jaffe:1991ra} (keep in mind 
-here tilde terms contain pure twist-3 and current quark mass terms)
+here tilde terms contain pure twist-3 and current-quark mass terms)
 \begin{subequations}\begin{alignat}{3}
@@
    	x\,e^a(x) &=& x\,&\tilde{e}^a(x) \;\stackrel{\rm WW}{\approx} 
-	\;\;\;\; 0 \label{Eq:WW-original-e}
+	\;\;\;\; 0 \, , \label{Eq:WW-original-e}
 \end{alignat}\end{subequations}
@@
 into a twist-2 part, and dynamical twist-3 (interactions dependent) 
-$\bar{q}gq$-terms and current quark mass terms.
+$\bar{q}gq$-terms and current-quark mass terms.
 
@@
 \begin{subequations}\ba
-xe^q(x,\kperp^2)	&\stackrel{\rm WW-type}{\approx}& 
+xe^q(x,\kperp^2)	&\WWtype& 
 			0, 
 			\label{Eq:WW-type-1}\\
-xf^{\perp q}(x,\kperp^2)  &\stackrel{\rm WW-type}{\approx}& 
+xf^{\perp q}(x,\kperp^2)  &\WWtype& 
 			f_{1}^q(x,\kperp^2),
 			\label{Eq:WW-type-Cahn}\phantom{\frac11}\\
-xg_L^{\perp q}(x,\kperp^2)&\stackrel{\rm WW-type}{\approx}& 
+xg_L^{\perp q}(x,\kperp^2)&\WWtype& 
 			g_{1}^q(x,\kperp^2),
 			\label{Eq:WW-type-gLperp}\phantom{\frac11}\\
-xg_T^{\perp q}(x,\kperp^2)&\stackrel{\rm WW-type}{\approx}& 
+xg_T^{\perp q}(x,\kperp^2)&\WWtype& 
 			g_{1T}^{\perp q}(x,\kperp^2),\phantom{\frac11}
 			\label{Eq:WW-type-gTperp}\\
-xg_T^q(x,\kperp^2)   	&\stackrel{\rm WW-type}{\approx}& 
+xg_T^q(x,\kperp^2)   	&\WWtype& 
              		g_{1T}^{\perp(1)q}(x,\kperp^2), 
 			\label{Eq:WW-type-gT}\\
-xh_L^q(x,\kperp^2)	&\stackrel{\rm WW-type}{\approx}& -2 \,
+xh_L^q(x,\kperp^2)	&\WWtype& -2 \,
                        	h_{1L}^{\perp(1)q}(x,\kperp^2),\phantom{\frac11}
                        	\label{Eq:WW-type-6}\\
-xh_T^q(x,\kperp^2)      &\stackrel{\rm WW-type}{\approx}& 
+xh_T^q(x,\kperp^2)      &\WWtype& 
                        	- h_1^q(x,\kperp^2) - h_{1T}^{\perp(1)}(x,\kperp^2),
                        	\label{Eq:WW-type-7}\\
-xh_T^{\perp q}(x,\kperp^2)&\stackrel{\rm WW-type}{\approx}& 
+xh_T^{\perp q}(x,\kperp^2)&\WWtype& 
                        	\phantom{-}h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2).
@@
 \begin{subequations}\ba
-xe_L^q(x,\kperp^2)         	&\stackrel{\rm WW-type}{\approx}& 0, 
+xe_L^q(x,\kperp^2)         	&\WWtype& 0, 
 			\label{Eq:WW-type-eLperp}\\
-xe_T^q(x,\kperp^2)         	&\stackrel{\rm WW-type}{\approx}& 0, \\
-xe_T^{\perp q}(x,\kperp^2) 	&\stackrel{\rm WW-type}{\approx}& 0, \\
-xg^{\perp q}(x,\kperp^2)   	&\stackrel{\rm WW-type}{\approx}& 0, 
+xe_T^q(x,\kperp^2)         	&\WWtype& 0, \\
+xe_T^{\perp q}(x,\kperp^2) 	&\WWtype& 0, \\
+xg^{\perp q}(x,\kperp^2)   	&\WWtype& 0, 
                        	\label{Eq:WW-type-gperp}\\
-xf_L^{\perp q}(x,\kperp^2) 	&\stackrel{\rm WW-type}{\approx}& 0, 
+xf_L^{\perp q}(x,\kperp^2) 	&\WWtype& 0, 
 			\label{Eq:WW-type-fLperp}\phantom{\frac11}\\
-xf_T^{\perp q}(x,\kperp^2) 	&\stackrel{\rm WW-type}{\approx}& 
+xf_T^{\perp q}(x,\kperp^2) 	&\WWtype& 
                        	\phantom{-}\,f_{1T}^{\perp q}(x,\kperp^2),
@@
                        	\label{Eq:WW-type-fTperp}\\
-xf_T^{q}(x,\kperp^2)       	&\stackrel{\rm WW-type}{\approx}& 
+xf_T^{q}(x,\kperp^2)       	&\WWtype& 
                        	-\,f_{1T}^{\perp(1)q}(x,\kperp^2), \label{Eq:WW-type-fT}\\
-xh^q(x,\kperp^2)           	&\stackrel{\rm WW-type}{\approx}& 
+xh^q(x,\kperp^2)           	&\WWtype& 
                        	- 2\,{h_1^{\perp(1)}(x,\kperp^2)}.\phantom{\frac11 XXXXx} 
@@
 \begin{subequations}\ba
-   	g_{1T}^{\perp(1)a}(x)&\stackrel{\rm WW-type}{\approx}& 
+   	g_{1T}^{\perp(1)a}(x)&\WWtype& 
         \phantom{-} x\,\int_x^1\frac{d y}{y\;}\,g_1^a(y) \;,
 	\label{Eq:WW-approx-g1T}\\
-    	h_{1L}^{\perp(1)a}(x)&\stackrel{\rm WW-type}{\approx}& -
+    	h_{1L}^{\perp(1)a}(x)&\WWtype& -
 	x^2\!\int_x^1\frac{d y}{y^2\;}\,h_1^a(y)\;.
@@
 \begin{subequations}\ba
-	E(z,\pperp^2)      &\stackrel{\rm WW-type}{\approx}& 0 \, ,
+	E(z,\pperp^2)      &\WWtype& 0 \, ,
 	\label{Eq:WW-type-FF-1}\\
-	G^\perp(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}& 0 \, ,
+	G^\perp(z,\pperp^2) &\WWtype& 0 \, ,
 	\label{Eq:WW-type-FF-2}\\
-	D^\perp(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}
+	D^\perp(z,\pperp^2) &\WWtype
 	& \hspace{11mm}z\,D_1(z,\pperp^2)\,, \label{Eq:WW-type-FF-3}\\
-	H(z,\pperp^2) &\stackrel{\rm WW-type}{\approx}& 
+	H(z,\pperp^2) &\WWtype& 
 	-\frac{\pperp^2}{zM_h^2}\;H_1^\perp(z,\pperp^2)\,. \label{Eq:WW-type-FF-4}
 \ea\end{subequations}
-Having introduced the WW- and WW-type approximations, we will review
+Having introduced the WW and WW-type approximations, we will review
 in the following what is currently known from theory and experiment 
@@
 gluon field configurations, which form a strongly interacting medium.
-The approach provides a natural mechanism for dynamical chiral symmetry 
+The approach provides a natural mechanism for dynamical chiral-symmetry 
 breaking, the dominant feature of strong interactions in the nonperturbative
@@
 instantons form a dilute medium characterized by a non-trivial small parameter
-$\rho/R\sim1/3$ \cite{Shuryak:1981ff,Diakonov:1983hh,Diakonov:1995qy}
+$\rho/R\sim1/3$ \cite{Shuryak:1981ff,Diakonov:1983hh,Diakonov:1995qy},
 where $\rho$ and $R$ denote respectively the average instanton size $\rho$
@@
 parameter $\rho/R$ with respect to contributions from the 
-respective twist-2 parts which are of order $(\rho/R)^0$. 
+respective twist-2 parts, which are of order $(\rho/R)^0$. 
 For Mellin moments it was found \cite{Balla:1997hf,Dressler:1999hc}
@@
 in Eq.~(\ref{Eq:WW-generic}) with the instanton packing fraction providing 
-the non-trivial small parameter justifying the neglect of tilde-terms. 
+the non-trivial small parameter justifying the neglect of tilde terms. 
 The predictions for $\tilde{g}_T^a(x)$ \cite{Balla:1997hf}
-were made before the advent of the first precise data on $g_2(x)$
+were made before the advent of the first precise data on $g_2(x)$,
 which we discuss next.
@@
 
-%\newpage
+%
 \subsection{Tests of WW approximation in DIS experiments}
@@
 The $x$--dependence of $\varepsilon_2$ preserves $\lim_{x\to1}g_2(x)= 0$; 
-we use $\epsilon=0.05$ which yields $\varepsilon_2\approx 20\,\%$ up to 
+we use $\epsilon=0.05$, which yields $\varepsilon_2\approx 20\,\%$ up to 
 the highest measured $x$--bin.
@@
 the WW approximation (\ref{Eq:WW-original2}) for $h_L^a(x)$ could 
-be tested experimentally in Drell-Yan \cite{Koike:2008du}.
+be tested experimentally in Drell--Yan \cite{Koike:2008du}.
 
@@
 they used a gauge link that does not incorporate the final or initial 
-state interactions present in SIDIS or Drell-Yan experiments. In other 
+state interactions present in SIDIS or Drell--Yan experiments. In other 
 words, the transverse momentum dependent quantities computed in
@@
         \int_{-1}^1 d x\;x^N
-       g_{1T}^{\perp(1)q}(x)&\stackrel{\rm WW-type}{\approx}&
+       g_{1T}^{\perp(1)q}(x)&\WWtype&
         \phantom{-} \,\frac{1}{N+2} \int_{-1}^1 d x \;x^{N+1}g_1^q(x)
@@
         \int_{-1}^1 d x\;x^N
-        h_{1L}^{\perp(1)q}(x)&\stackrel{\rm WW-type}{\approx}&
+        h_{1L}^{\perp(1)q}(x)&\WWtype&
         -\,\frac{1}{N+3} \int_{-1}^1 d x\: x^{N+1}\,h_1^q(x)
@@
 but establishes no connection with a subtraction scheme designed for 
-experimental TMDs and the corresponding gauge link geometry. 
-The gauge link renormalization mainly 
+experimental TMDs and the corresponding gauge-link geometry. 
+The gauge-link renormalization mainly 
 influences the width of the Gaussian fits; the amplitudes are only slightly 
@@
         _{= 0.104(9) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
-        \hspace{3mm} , \nonumber \\
+        \hspace{2mm} , \nonumber \\
         \underbrace{\int d x\;g_{1T}^{\perp(1)d}(x)}
@@
         _{= -0.025(9) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
-        \hspace{3mm}, 
+        \hspace{2mm}, 
         \label{Eq:test-WW-type-lattice-g1T}
@@
         _{= -0.093(3) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
-        \hspace{3mm} , \hspace{7mm} \nonumber \\
+        \hspace{2mm} , \hspace{7mm} \nonumber \\
         \underbrace{\int d x\;h_{1L}^{\perp(1)d}(x)}
@@
         _{= 0.018(1) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
-        \hspace{3mm}. 
+        \hspace{2mm}, 
         \label{Eq:test-WW-type-lattice-h1L}
@@
 lattice calculations actually test. As mentioned above, in
-the lattice study \cite{Hagler:2009mb,Musch:2010ka} a specific choice for
+the lattice study \cite{Hagler:2009mb,Musch:2010ka}, a specific choice for
 the path of the gauge link was chosen, which is actually different
-from the paths required in SIDIS or Drell-Yan. With the path choice of
+from the paths required in SIDIS or Drell--Yan. With the path choice of
 \cite{Hagler:2009mb,Musch:2010ka} there are effectively only (T-even)
@@
 interesting result. Thus, apart from the instanton calculus
-\cite{Dressler:1999hc} also lattice data provide support for
+\cite{Dressler:1999hc}, also lattice data provide support for
 the validity of the WW approximation (\ref{Eq:WW-original2}).
@@
 
-\newpage
 \subsection{Tests in models}
@@
 degrees of freedom certain relations among TMDs hold, the 
-so-called quark model Lorentz-invariance relations (qLIRs)
+so-called quark-model Lorentz-invariance relations (qLIRs)
 \cite{Tangerman:1994bb,Mulders:1995dh}.\footnote{Notice that
@@
 	valid only in quark models with no gluons and should not
-	be confused with the LIRs of \cite{Kanazawa:2015ajw} which 
+	be confused with the LIRs of \cite{Kanazawa:2015ajw}, which 
 	are exact relations in QCD, see Sec.~\ref{Sec-3.1:WW-classic}.
-	In literature both are often simply referred to as LIRs.
+	In the literature, both are often simply referred to as LIRs.
 	This ambiguity is unfortunate.}
-Initially thought to be exact \cite{Tangerman:1994bb,Mulders:1995dh}
+Initially thought to be exact \cite{Tangerman:1994bb,Mulders:1995dh},
 qLIRs were shown  to be invalid in models with gluons 
@@
 When gluons are absent, the correlator consists
-of 12 amplitudes \cite{Tangerman:1994bb,Mulders:1995dh}, i.e.\ fewer 
+of 12 amplitudes \cite{Tangerman:1994bb,Mulders:1995dh}, i.e., fewer 
 amplitudes than TMDs which implies relations: the qLIRs. 
 In QCD the correct Lorentz decomposition requires the consideration of 
-gauge links which introduces further amplitudes. As a result one has 
+gauge links, which introduces further amplitudes. As a result one has 
 as many amplitudes as TMDs and no relations exist \cite{Goeke:2003az}. 
@@
 $N_c$ is the number of colors) with the nucleon described as a 
-chiral soliton. In general the model predicts non-zero tilde-terms, for 
+chiral soliton. In general, the model predicts non-zero tilde-terms, for 
 instance $\tilde{e}^a(x)\neq 0$ 
@@
 functions uniquely: the 8 basis functions appear in 6 SIDIS structure functions.
-It is crucial to take advantage of other processes: Drell-Yan for PDFs and TMDs
+It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
 and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
@@
 In some cases, however, we know in advance that the WW-type approximations 
-have limitations, see next section.
+have limitations, see next Section.
 
@@
 
-The approximation may work in the case when: TMD or FF 
+The approximation may work in the case when the TMD or FF 
 $=\la\bar{q}q\ra + \la\bar{q}gq\ra \approx \la\bar{q}q\ra \neq 0$ with 
@@
 However, it may happen that after applying the QCD equations
-of motion one ends up in the situation that: a given function 
+of motion one ends up in the situation that a given function 
 $=\la\bar{q}q\ra + \la\bar{q}gq\ra$ with $\la\bar{q}q\ra = 0$.
@@
 others potentially less affected by this generic limitation. In any 
-case phenomenological work has to be carried out to find out whether 
+case, phenomenological work has to be carried out to find out whether 
 or not the approximation works.
@@
 Similar limitations exist also for TMDs. This is manifest in particular 
-for those twist-3 T-odd TMDs which appear in the decomposition of the 
+for those twist-3 T-odd TMDs that appear in the decomposition of the 
 correlator (\ref{Eq:correlator}) with no prefactor of $\kperp$.
@@
 TMDs because they drop out from the $\kperp$--integrated correlator due to 
-explicit factors of e.g.\ $\kperp^j$ in the case of the Sivers function.
+explicit factors of, e.g., $\kperp^j$ in the case of the Sivers function.
 
@@
 have $xf_T^a(x,k_\perp)=x\tilde{f}_T^a(x,k_\perp)-f_{1T}^{\perp(1)a}(x,k_\perp)$ 
-from QCD equations of motion \cite{Bacchetta:2006tn} which yields
+from QCD equations of motion \cite{Bacchetta:2006tn}, which yields
 (\ref{Eq:WW-type-fT}). The point is that in this case it is 
@@
 Does it mean WW-type approximations fail for $f_T^a(x,k_\perp)$ 
-and $h^a(x,k_\perp)$? Not necessarily. The approximations may
+and $h^a(x,k_\perp)$? Not necessarily! The approximations may
 work in some but not all regions of $\kperp$, but the sum rules 
 (\ref{Eq:sum-rules-T-odd}) include integration over all $k_\perp$. 
-Notice also that e.g.\ $f_{1T}^{\perp (1),q}(x)$ is related to the 
-soft-gluon-pole matrix element $F_{FT}(x,x)$ \cite{Boer:2003cm,Ji:2006ub}
+Notice also that, e.g., $f_{1T}^{\perp (1),q}(x)$ is related to the 
+soft-gluon-pole matrix element $F_{FT}(x,x)$ \cite{Boer:2003cm,Ji:2006ub},
 which is a $\bar{q}gq$-term that one would naturally neglect 
@@
 Below in Sec.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi} we 
-will present a pragmatic solution how to deal with the TMDs 
+will present a pragmatic solution for how to deal with the TMDs 
 $f_T^a(x,k_\perp)$ and $h^a(x,k_\perp)$ phenomenologically. 
@@
 
-%\newpage
+%
 %======= SECTION 4: SIDIS IN WW APPROXIMATION ========================
-\section{SIDIS in WW-type approximation and Gaussian model}
+\section{SIDIS in the WW-type approximation and Gaussian model}
 \label{Sec-4:SIDIS-in-WW-approximation}
 
-In this section we consequently apply the WW- and WW-type approximation
+In this section, we consequently apply the WW and WW-type approximation
 to SIDIS, and describe our procedure to evaluate the structure 
@@
 
-The WW- and WW-type approximations are useful for the following
-two leading--twist structure functions 
+The WW and WW-type approximations are useful for the following
+two leading-twist structure functions:
 \begin{subequations}\ba
@@
 	{\cal C}\biggl[\omega^{\{1\}}_{\rm B}\, {g_{1T}^\perp}D_1 \biggr]
-        \with{ }{g_{1T}^{\perp a}\to g_1^a}{Eq.~(\ref{Eq:WW-approx-g1T})}
+        \with{ }{g_{1T}^{\perp a}\to g_1^a}{Eq.~(\ref{Eq:WW-approx-g1T})} \; ,
         \label{F_LTcos(phi-phiS)-WW} \\
@@
     	{h_{1L}^{\perp }} H_{1}^{\perp }\biggr]  
-        \with{ }{h_{1L}^{\perp a}\to h_1^a}{Eq.~(\ref{Eq:WW-approx-h1L})} 
+        \with{ }{h_{1L}^{\perp a}\to h_1^a}{Eq.~(\ref{Eq:WW-approx-h1L})}  \; .
         \label{F_UUsin2phi-WW}
@@
 	{g_T^a\to g_1^a}
-	{Eq.~(\ref{Eq:WW-original1}),}\\
+	{Eq.~(\ref{Eq:WW-original1})}  \\
 F_{LL}^{\cos \phi_h} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[ 
@@
 	{g_L^{\perp a}\to g_1^a}
-	{Eq.~(\ref{Eq:WW-type-gLperp}),}\\
+	{Eq.~(\ref{Eq:WW-type-gLperp})}  \\
 F_{LT}^{\cos(2\phi_h - \phi_S)} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
@@
 	{g_T^{\perp a}\to g_1^a}
-	{Eqs.~(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T}),}\\
+	{Eqs.~(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T})}   \\
 F_{UL}^{\sin\phi_h} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
@@
 	{h_L^a\to h_{1L}^{\perp a}}
-	{with Eq.~(\ref{Eq:WW-type-6}),}
+	{with Eq.~(\ref{Eq:WW-type-6})}  
 	\label{Eq:WW-type-FULsinphi}\\
@@
 	{f^{\perp a}\to f_1^a, \; h^a\to h_1^{\perp a}}
-	{with Eqs.~(\ref{Eq:WW-type-Cahn},~\ref{Eq:WW-type-last}),}
+	{with Eqs.~(\ref{Eq:WW-type-Cahn},~\ref{Eq:WW-type-last})} 
 	\label{Eq:WW-type-FUUcosphi}\\
@@
 	{h_T^a-h_T^{\perp a}\to h_1^a}
-	{(\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}),}
+	{(\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8})}  
 	\label{Eq:WW-type-FUTsinphiS}\\
@@
 	{(h_T^a+h_T^{\perp a})\to h_{1T}^{\perp a}}{with 
-	(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}).}
+	(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8})} \!.
 	\;\;\;\;
@@
 transverse momenta (of hadrons produced in SIDIS, dileptons produced
-in the Drell-Yan process, etc) are small compared to the hard
+in the Drell--Yan process, etc) are small compared to the hard
 scale in the process, then the Ansatz works quantitatively
@@
 
-The Gaussian Ansatz is compatible with many WW-type approximations
+The Gaussian Ansatz is compatible with many WW-type approximations,
 but not all. The trivial approximations (\ref{Eq:WW-type-1}) and
-(\ref{Eq:WW-type-eLperp}--\ref{Eq:WW-type-fLperp}) of course 
-cause no issue. 
+(\ref{Eq:WW-type-eLperp}--\ref{Eq:WW-type-fLperp}) cause no issue. 
 The Gaussian Ansatz can also be applied to the nontrivial approximations 
@@
 $xg_T^q(x,\kperp^2)\approx\frac{k_\perp^2}{2M_N^2}\,g_{1T}^{q}(x,\kperp^2)$,
-i.e.\ if $g_{1T}^q(x,\kperp^2)$ was exactly Gaussian then 
+i.e., if $g_{1T}^q(x,\kperp^2)$ was exactly Gaussian then 
 $g_T^q(x,\kperp^2)$ certainly could not be Gaussian. If one wanted to take
@@
 with Gaussian Ansatz.
-In general this would yield different (and bulkier) analytical 
+In general, this would yield different (and bulkier) analytical 
 expressions, but we convinced ourselves that the differences 
@@
 However, for the structure functions discussed in
-Secs.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi}
+Secs.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi},
 such an ``alternative scheme'' would give results at
-variance with the sum rules in for the twist-3 T-odd TMDs
+variance with the sum rules for the twist-3 T-odd TMDs
 in Eq.~(\ref{Eq:sum-rules-T-odd}), as discussed in 
@@
 the $k_\perp$--moments of these TMDs have in principle simple definitions
-in QCD (whereas e.g.\ the function $f_{1T}^{\perp q}(x)$ can be computed in
+in QCD (whereas, e.g., the function $f_{1T}^{\perp q}(x)$ can be computed in
 models but is very cumbersome to define in QCD).
@@
 
-%\newpage
+%
 %======= SECTION 5: TWIST-2 AND BASIS FUNCTIONS ======================
-\section{Leading twist asymmetries and basis functions}
+\section{Leading-twist asymmetries and basis functions}
 \label{Sec-5:twist-2+basis}
 In this section we review how the basis functions describe available
-SIDIS data. This is of importance to asses the reliability of the
+SIDIS data. This is of importance to assess the reliability of the
 predictions presented in the next sections.
 
-\subsection{\boldmath Leading twist $F_{UU}$ and Gaussian Ansatz}
+\subsection{\boldmath Leading-twist $F_{UU}$ and Gaussian Ansatz}
 \label{Sec-5.1:FUU-basis}
@@
 App.~\ref{App:basis-f1-D1} for a review. This assumption can be
-relaxed, e.g.\ theoretical studies in chiral effective theories 
+relaxed, e.g., theoretical studies in chiral effective theories 
 predict a strong flavor-dependence in the $\kperp$--behavior
@@
 
-Let us begin with JLab where, in the pre-12$\,$GeV era, electron beams 
+Let us begin with Jefferson Lab where, in the pre-12$\,$GeV era, electron beams 
 from CEBAF with energies in the range $4.3$ to $5.7$ GeV were scattered 
@@
 Gaussian model works for the entire region of $P_{hT}$ covered in this 
-experiment where structure function $F_{UU}$ falls down by 2 orders of 
+experiment, in which the structure function $F_{UU}$ falls down by 2 orders of 
 magnitude \cite{Schweitzer:2010tt}.
@@
 	% for $\la Q^2\ra=2.37\,{\rm GeV}^2$, $\la x\ra=0.24$, $\la z\ra=0.30$ 
-	at JLab with 5.75 GeV beam \cite{Osipenko:2008aa}.
+	at Jefferson Lab with 5.75 GeV beam \cite{Osipenko:2008aa}.
 Middle panel: 
@@
 	$\la Q^2\ra=2.87\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.22$
-	from \cite{Airapetian:2012ki}.
+	 \cite{Airapetian:2012ki}.
 Right panel: 
@@
 	$\la Q^2\ra=20\,{\rm GeV}^2$, $\la x\ra  =0.15$, $\la z\ra  =0.2$
-	from \cite{Aghasyan:2017ctw}.}
+	 \cite{Aghasyan:2017ctw}.}
 \end{figure}
@@
 off proton and deuteron targets in the SIDIS kinematics 
-$Q^2 > 1 \,{\rm GeV}^2$, $W > 2\,{\rm GeV}$, 
+$Q^2 > 1 \,{\rm GeV}^2$, $W^{2} > 10\,{\rm GeV}^{2}$, 
 $0.023 < x < 0.4$, $y < 0.85$, $0.2<z<0.7$. 
@@
 	\frac{d\sigma_{\rm SIDIS}(x,z,\Phperp)/dx\,dz\,d\Phperp}
-	{d\sigma_{\rm DIS}(x,z)/dx} =
+	{d\sigma_{\rm DIS}(x)/dx} =
 	2 \pi \Phperp \frac{F_{UU}(x,z,\Phperp) }{ x \sum_q e_q^2\,f^q_1(x)}
@@
 at $\la Q^2\ra=2.87\,{\rm GeV}^2$, $\la x\ra=0.15$, $\la z\ra=0.22$ 
-for $\pi^+$ production on the proton target \cite{Airapetian:2012ki}.
+for $\pi^+$ production on the proton target~\cite{Airapetian:2012ki}.
 
@@
 	\frac{d\sigma_{\rm SIDIS}(x,z,\Phperp^2)/dx\,dz\,d\Phperp^2}
-	{d\sigma_{\rm DIS}(x,z)/dx} =
+	{d\sigma_{\rm DIS}(x)/dx} =
 	\pi \frac{F_{UU}(x,z,\Phperp^2) }{ x \sum_q e_q^2\,f^q_1(x)}\;
@@
 
-\newpage
 %========= SECTION 6: TESTING APPROACH WITH A_LL =====================
-\subsection{\boldmath Leading twist $A_{LL}$ and first test of Gaussian Ansatz
+\subsection{\boldmath Leading-twist $A_{LL}$ and first test of Gaussian Ansatz
 	in polarized scattering}
@@
 Signori:2013mda,Anselmino:2013lza}, but nothing is known about its 
-applicability to spin asymmetries. The JLab data \cite{Avakian:2010ae} 
+applicability to spin asymmetries. The Jefferson Lab data \cite{Avakian:2010ae} 
 on $A_{LL}(\Phperp)$ put us in the position to conduct a first ``test'' 
@@
 \centering 
-\includegraphics[width=0.3\textwidth]{\FigPath/all_jlab_pip}  
-\includegraphics[width=0.3\textwidth]{\FigPath/all_jlab_pi0}  
-\includegraphics[width=0.3\textwidth]{\FigPath/all_jlab_pim} 
+\includegraphics[width=0.45\textwidth]{\FigPath/all_jlab_pip}  
+\includegraphics[width=0.45\textwidth]{\FigPath/all_jlab_pi0}  
+\includegraphics[width=0.45\textwidth]{\FigPath/all_jlab_pim} 
 \caption{\label{jlab_ALL} 
@@
 
-The definition of the asymmetry in  the JLab experiment \cite{Avakian:2010ae} 
+The definition of the asymmetry in  the Jefferson Lab experiment \cite{Avakian:2010ae} 
 was
@@
 and tested through other observables in Sec.~\ref{Sec-5.1:FUU-basis}.
-Therefore the comparison of our results to JLab data \cite{Avakian:2010ae} 
+Therefore the comparison of our results to the Jefferson Lab data \cite{Avakian:2010ae} 
 shown in Fig.~\ref{jlab_ALL} provides several important tests.
-First, the JLab data \cite{Avakian:2010ae} are compatible
-with the Gaussian Ansatz within error bars. Second, the lattice results
-in the way we use them in App.~\ref{App:basis-g1} give an appropriate 
+First, the Jefferson Lab data \cite{Avakian:2010ae} are compatible
+with the Gaussian Ansatz within uncertainties. Second, the lattice 
+results---in the way we use them in App.~\ref{App:basis-g1}---give an appropriate 
 description of the data.
@@
 	parametrizations of $f_1^a(x)$, $g_1^a(x)$, $D_1^a(z)$. This 
-	shows that even at the moderate beam energies of the pre-12GeV 
-	era one was, to a good approximation, indeed probing DIS at JLab
-	\cite{Avakian:2010ae}.)
+	shows that even at the moderate beam energies of the pre-12~GeV 
+	era one was, to a good approximation, indeed probing DIS at 
+	Jefferson Lab~\cite{Avakian:2010ae}.)
 
@@
 $g_{1T}^{\perp(1)a}$ and $h_{1L}^{\perp(1)a}$.
-Of course, at this point one could argue that the WW- and WW-type 
+Of course, at this point one could argue that the WW and WW-type 
 approximations (\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}) also
@@
 
-\newpage
-
-\subsection{\boldmath Leading twist $A_{UT}^{\sin(\phi_h-\phi_S)}$ Sivers asymmetry}
+\subsection{\boldmath Leading-twist $A_{UT}^{\sin(\phi_h-\phi_S)}$ Sivers asymmetry}
 \label{Sec-5.3:Sivers-basis}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_COMPASS_x.pdf}
+\caption{\label{aut_f1t_jlab} Sivers asymmetry 
+	$A_{UT}^{\sin(\phi_h-\phi_S)}$ from proton target as function of $ x $ 
+	based on the fit \cite{Anselmino:2011gs} in comparison to 
+	(left panel) HERMES \cite{Airapetian:2009ae}
+	and (right panel) COMPASS data \cite{Adolph:2012sp}.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The $F_{UT}^{\sin(\phi_h-\phi_S)}$ structure function is related to the 
 Sivers function~\cite{Sivers:1989cc}, which describes the distribution
-of unpolarized quarks inside a transversely polarized proton, has so far 
+of unpolarized quarks inside a transversely polarized proton. It has so far 
 received the widest attention, from both phenomenological and experimental 
@@
 
-The Sivers function $f_{1T}^\perp$ is related to initial and final state 
+The Sivers function $f_{1T}^\perp$ is related to initial and final-state 
 interactions of the struck quark and the rest of the nucleon and could 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_COMPASS_x.pdf}
-\caption{\label{aut_f1t_jlab} Sivers asymmetry 
-	$A_{UT}^{\sin(\phi_h-\phi_S)}$ from proton target as function of $ x $ 
-	based on the fit \cite{Anselmino:2011gs} in comparison to 
-	(left panel) HERMES \cite{Airapetian:2009ae}
-	and (right panel) COMPASS data \cite{Adolph:2012sp}.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 Notice that integrating structure functions over $\Phperp$
@@
 We stress this important point by displaying the dependence of 
-the structure functions on the mean hadron momenta, for instance
+the structure functions on the mean transverse hadron momenta, for instance
 $F_{UT}^{\sin(\phi_h-\phi_S)}(x,z,\la\Phperp\ra) = 
@@
 on respectively charged pion and hadron production from a proton target.
-The $P_{hT}$--dependencies of the data are equally well described which
+The $P_{hT}$--dependences of the data are equally well described, which
 confirms that the Gaussian model works also in this case.
 
-\newpage
-\subsection{\boldmath Leading twist $A_{UT}^{\sin(\phi_h+\phi_S)}$ Collins asymmetry}
+\subsection{\boldmath Leading-twist $A_{UT}^{\sin(\phi_h+\phi_S)}$ Collins asymmetry}
 \label{Sec-5.4:Collins-basis}
@@
 FF $H_1^\perp$. Transversity can in principle be accessed also as a PDF in
-Drell-Yan or in dihadron production 
+Drell--Yan or in dihadron production 
 \cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,Bacchetta:2012ty,
@@
 
-The asymmetries $A_{UT}^{\sin(\phi_h+\phi_S)}= F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$  
+The asymmetries $A_{UT, \langle y \rangle}^{\sin(\phi_h+\phi_S)}= (1-y)F_{UT}^{\sin(\phi_h+\phi_S)}/((1-y + y^2/2)F_{UU})$  
 are plotted in Fig.~\ref{aut_h1_jlab} as functions of $x$ in comparison 
-to HERMES \cite{Airapetian:2010ds} and COMPASS \cite{Adolph:2014zba} 
+to HERMES \cite{Airapetian:2010ds} and $A_{UT}^{\sin(\phi_h+\phi_S)}= F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$  for COMPASS \cite{Adolph:2014zba} 
 data on charged pion production from proton targets.
@@
 \caption{\label{aut_h1_jlab}  Collins asymmetry 
-	$A_{UT}^{\sin(\phi_h+\phi_S)}$ from proton target as function of $ x $ 
+	$A_{UT,  \langle y\rangle}^{\sin(\phi_h+\phi_S)}$ from proton target as function of $ x $ 
 	based on the fit \cite{Anselmino:2013vqa} in comparison to 
@@
 
-\newpage
-\subsection{\boldmath Leading twist $A_{UU}^{\cos(2\phi_h)}$ Boer-Mulders asymmetry}
+\subsection{\boldmath Leading-twist $A_{UU}^{\cos(2\phi_h)}$ Boer--Mulders asymmetry}
 \label{Sec-5.5:BM-basis}
@@
 \caption{\label{auu_cos2phi_jlab} The asymmetry 
-	$A_{UU}^{\cos(2\phi_h)}$ from proton target as function of $ x $ 
+	$A_{UU, \langle y\rangle}^{\cos(2\phi_h)}$ from proton target as function of $ x $ 
 	based on the fit \cite{Barone:2009hw} in comparison to 
-	(left panel) HERMES \cite{Airapetian:2012yg} and 
+	(left panel) HERMES \cite{Airapetian:2012yg} and $A_{UU}^{\cos(2\phi_h)}$
 	(right panel) COMPASS data \cite{Adolph:2014pwc}.}
@@
 
-Asymmetries $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$ for 
-HERMES \cite{Airapetian:2012yg} and COMPASS \cite{Adolph:2014pwc}
-are plotted in Fig.~\ref{auu_cos2phi_jlab} where we only considered the
-Boer-Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$ which does not describe
+Asymmetries  for $A_{UU, \langle y\rangle}^{\cos(2\phi_h)}=(1-y)F_{UU}^{\cos(2\phi_h)}/((1-y + y^2/2)F_{UU})$
+HERMES \cite{Airapetian:2012yg} and $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$ COMPASS \cite{Adolph:2014pwc}
+are plotted in Fig.~\ref{auu_cos2phi_jlab}, where we only considered the
+Boer--Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$, which does not describe
 the data accurately. In fact, it is suspected that this observable receives 
 a significant contribution from the Cahn effect \cite{Cahn:1978se}, a 
-term of higher twist character of the type $\la\Phperp^2\ra/Q^2$ which 
-is not negligible in fixed target experiments \cite{Schweitzer:2010tt}. 
+term of higher-twist character of the type $\la\Phperp^2\ra/Q^2$ which 
+is not negligible in fixed-target experiments \cite{Schweitzer:2010tt}. 
 This contribution was estimated and corrected for in the phenomenological 
-works \cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} which was of
-importance to obtain a picture of the Boer-Mulders function undistorted 
+works \cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa}, which was of
+importance to obtain a picture of the Boer--Mulders function undistorted 
 from Cahn effect. The point is that this substantial twist-4 contamination 
@@
 order $1/Q^2$, and do so also in Fig.~\ref{auu_cos2phi_jlab}. 
-Nevertheless we of course use the parametrizations of 
+Nevertheless, we of course use the parametrizations of 
 \cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} offering
-the best currently available parametrizations for $h_1^{\perp}$
-which were corrected for Cahn effect as good as it is possible at
+the best currently available parametrizations for $h_1^{\perp}$,
+which were corrected for the Cahn effect as good as it is possible at
 the current state of art. It is unknown whether other asymmetries
@@
 
-\newpage
-\subsection{\boldmath Leading twist $A_{UT}^{\sin(3\phi_h-\phi_S)}$  asymmetry}
+\subsection{\boldmath Leading-twist $A_{UT}^{\sin(3\phi_h-\phi_S)}$  asymmetry}
 \label{Sec-5.6:pretzel-basis}
@@
 of the nucleon spin density from spherical shape \cite{Miller:2007ae},
-is related to the only leading-twist SIDIS structure function where the 
+as it is related to the only leading-twist SIDIS structure function where the 
 small-$P_{hT}$ description in terms of TMDs and the large-$P_{hT}$ expansion 
-in perturbative QCD mismatch \cite{Bacchetta:2008xw}, and is the only
+in perturbative QCD mismatch \cite{Bacchetta:2008xw}, and as it is the only
 TMD where a clear relation to quark orbital angular momentum
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2010se} 
-	and HERMES \cite{Schnell:2010zza} in comparison to the best fit 
+	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ HERMES \cite{Schnell:2010zza} in comparison to the best fit 
 	(whose 1-$\sigma$ uncertainty band is compatible with zero) 
@@
 	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
-	\TD{\sf screenshot of {\tt Fig-COMPASS-A\_UT\_Pr10.pdf} 
-	which was previously shown in Fig.~\ref{autsinphi_jlab}. 
-	Bakur: please, can you produce such plot with Alexei's 
-	``best fit'' from \cite{Lefky:2014eia}?}}
+	}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The preliminary COMPASS data \cite{Parsamyan:2010se} for 
-$A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The preliminary COMPASS data \cite{Parsamyan:2010se} for $A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ and the preliminary HERMES data \cite{Schnell:2010zza} for 
+$A_{UT, \langle y \rangle}^{\sin(3 \phi_h - \phi_S)}=(1-y)F_{UT}^{\sin(3 \phi_h - \phi_S)}/((1-y + y^2/2)F_{UU})$ 
 are plotted in Fig.~\ref{aut_h1tp_jlab}.
@@
 momentum descriptions of $f_1^a(x,\kperp)$ and $D_1^a(z,\pperp)$ 
-are associated with non-negligible statistical uncertainties
+are associated with non-negligible statistical uncertainties,
 which are reviewed in App.~\ref{App:basis}, and with systematic
-uncertainties which are very difficult to assess as they are
+uncertainties that are very difficult to assess as they are
 related to model bias (because of Gaussian model and its limitations).
@@
 The least well-controlled uncertainties are associated with the 
-Boer-Mulders function $h_1^{\perp q}$ and pretzelosity $h_{1T}^{\perp q}$.
+Boer--Mulders function $h_1^{\perp q}$ and pretzelosity $h_{1T}^{\perp q}$.
 
 In this work we are not interested in these uncertainties, which
-future data will allow us to diminish --- even though in practice 
+future data will allow us to diminish, even though in practice 
 they may be sizable. Rather in this work we are interested in
@@
 %======= SECTION 6: TWIST-2 AND WW-APROXIMATION ======================
-\section{Leading twist asymmetries in WW-type approximation}
+\section{Leading-twist asymmetries in WW-type approximation}
 \label{Sec-6:twist-2-and-WW}
-
-\begin{figure}[b!]
+\begin{figure}[htb]
 \centering
@@
 	for $u$-- and $d$--flavor 
-	as predicted by the WW-ype approximations in
+	as predicted by the WW-type approximations in
 	Eqs.~(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}).}
@@
 polarized quarks inside a transversely polarized nucleon,
-$h_{1L}^{\perp q}$ the opposite \bp{configuration}, namely transversely 
+$h_{1L}^{\perp q}$ the opposite configuration, namely transversely 
 polarized quarks inside a longitudinally polarized nucleon.
@@
 
-\newpage
-\subsection{\boldmath Leading twist $A_{LT}^{\cos(\phi_h-\phi_S)}$}
+\subsection{\boldmath Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$}
 \label{Sec-6.1:FLTcosphi-phiS}
@@
 see also \cite{Kotzinian:2006dw}, and evaluate $g^{\perp (1) q}_{1T}(x)$ 
-using Eq.~(\ref{Eq:WW-approx-g1T}) which yields the result 
+using Eq.~(\ref{Eq:WW-approx-g1T}), which yields the result 
 shown in Fig.~\ref{g1t_h1l_functions}.
@@
 
+This asymmetry was measured at Jefferson Lab~\cite{Huang:2011bc}, COMPASS~\cite{Parsamyan:2015dfa} and HERMES~\cite{Pappalardo:2011cu,Pappalardo:2012zz} (for the latter two experiments only preliminary results are available so far).
+ Fig.~\ref{cosphihphis} 
+shows the preliminary results from the 2010 COMPASS data \cite{Parsamyan:2015dfa}. 
+We approximate the 
+charged hadrons ($90\,\%$ of which are $\pi^\pm$ at COMPASS) by 
+charged pions, see App.~\ref{App:basis-f1-D1}.
+Our results are shown as a shaded area, which indicates a rough estimate
+of the uncertainty of the WW-type approximation.
+We observe that the WW-type approximation describes the data within 
+their experimental uncertainties.
+For comparison also results from the theoretical works 
+\cite{Kotzinian:2006dw,Kotzinian:2008fe,Boffi:2009sh} are shown.
+Our results are also compatible with the Jefferson Lab data, which was 
+taken with a neutron ($^3$He) target \cite{Huang:2011bc} and has 
+larger statistical uncertainty than the preliminary COMPASS data. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-%\includegraphics[width=0.3\textwidth]{\FigPath/ALT_COMPASS_x.pdf}  
-\includegraphics[width=0.9\textwidth]{\FigPath/LT_Pr10.pdf}
-	\caption{\label{g1t_jlab} 
-	Asymmetries as functions of $x$ from scattering of 160 GeV
-	longitudinally polarized muons off a transversely polarized 
-	proton target \cite{Parsamyan:2015dfa}.
-	Left panel: 
-	leading-twist asymmetry $A_{LT}^{\cos(\phi_h-\phi_S)}$ 
-	described in Sec.~\ref{Sec-6.1:FLTcosphi-phiS}.
-	Middle panel: 
-	subleading-twist $A_{LT}^{\cos\phi_S}$ 
-	discussed in Sec.~\ref{Sec-7.2:FLTcosphiS}.
-	Right panel: 
-	subleading-twist $A_{LT}^{\cos(2\phi_h-\phi_S)}$
-	on which we comment in Sec.~\ref{Sec-7.3:FLTcos2phi-phiS}.
-	\TD{(Bakur: can you prepare separate plots for these asymmetries?)}}
+\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip}
+\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim}
+	\caption{\label{cosphihphis} 
+	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$ 
+	 in comparison to the preliminary COMPASS data \cite{Parsamyan:2015dfa}.
+	}
 \end{figure}
@@
 
-This asymmetry was measured at JLab and COMPASS 
-\cite{Huang:2011bc,Parsamyan:2015dfa}. Left panel of Fig.~\ref{g1t_jlab} 
-shows 2010 COMPASS data \cite{Parsamyan:2015dfa}. We approximate the 
-charged hadrons ($90\,\%$ of which are $\pi^\pm$ at COMPASS) by 
-charged pions, see App.~\ref{App:basis-f1-D1}.
-Our results are shown as a shaded area which indicates a rough estimate
-of the uncertainty of the WW-type approximation.
-We observe that the WW-type approximation describes the data within 
-their experimental uncertainties.
-For comparison results from the theoretical works 
-\cite{Kotzinian:2006dw,Kotzinian:2008fe,Boffi:2009sh} are shown.
-Our results are also compatible with the JLab data which was 
-taken with a neutron ($^3$He) target \cite{Huang:2011bc} and has 
-larger statistical uncertainty than COMPASS data. The middle and right 
-panels of Fig.~\ref{g1t_jlab} will be discussed in 
-Secs.~\ref{Sec-7.2:FLTcosphiS},~\ref{Sec-7.3:FLTcos2phi-phiS}.
-
-\newpage
-
 \subsection{\boldmath 
-	Leading twist $A_{UL}^{\sin2\phi_h}$ Kotzinian-Mulders  asymmetry}
+	Leading-twist $A_{UL}^{\sin2\phi_h}$ Kotzinian--Mulders  asymmetry}
 	\label{Sec-6.2:FULsin2phi}
 
-We use the Gaussian form for the Kotzinian-Mulders function 
+We use the Gaussian form for the Kotzinian--Mulders function 
 $h_{1L}^{\perp a}$, Eq.~(\ref{eq:h1l_final}) in
@@
 supported by lattice data \cite{Hagler:2009mb}.
->From (\ref{Eq:WW-approx-h1L}) we obtain the WW-type estimate
+From (\ref{Eq:WW-approx-h1L}) we obtain the WW-type estimate
 for $h_{1L}^{\perp(1) a}(x)$ shown in Fig.~\ref{g1t_h1l_functions}. 
@@
 \centering
-\includegraphics[height=3.1cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \quad
-\includegraphics[height=3.0cm]{\FigPath/AULsin2phi_JLAB_x.pdf}
-
+\includegraphics[width=0.8\textwidth]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \quad
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_JLAB_x.pdf} 
 \vspace{-5mm}
@@
 	\caption{\label{aul_jlab} 
-	$A_{UL}^{\sin(2\phi_h)}$ vs $x$ from the WW-type 
+	Leading twist $A_{UL}^{\sin(2\phi_h)}$ vs $x$ from the WW-type 
 	approximation in comparison to data from
-	HERMES \cite{Airapetian:1999tv}, 
-	COMPASS \cite{Parsamyan:2015dfa} (left panel), and
-	JLab \cite{Jawalkar:2017ube} (right panel). Results  
+	HERMES \cite{Airapetian:1999tv}, and $A_{UL}^{\sin(2\phi_h)}$
+	COMPASS \cite{Parsamyan:2015dfa} (left panel), and $A_{UL,  \langle y\rangle}^{\sin(2\phi_h)}$ 
+	Jefferson Lab \cite{Jawalkar:2017ube} (right panel). Results  
 	from \cite{Avakian:2007mv} are also shown.}
@@
 studied at HERMES \cite{Airapetian:1999tv,Airapetian:2002mf}, COMPASS 
-\cite{Parsamyan:2015dfa}, and JLab \cite{Avakian:2010ae,Jawalkar:2017ube}.
+\cite{Parsamyan:2015dfa}, and Jefferson Lab \cite{Avakian:2010ae,Jawalkar:2017ube}.
 In Fig.~\ref{aul_jlab} proton data are shown for $\pi^\pm$ in the
@@
 $A_{UL}^{\sin(2\phi_h)}$  can be expected to be smaller than 
-$A_{LT}^{\cos(\phi_h -\phi_S)}$ discussed in previous section,
+$A_{LT}^{\cos(\phi_h -\phi_S)}$ discussed in the previous section,
 even though both are leading twist. This is because 
@@
 of the size of $g_{1T}^{\perp(1)q}(x)$.
-The data support these expectations. HERMES and JLab data are compatible
-with zero for this asymmetry. So are COMPASS data except for the region
+The data support these expectations. HERMES and Jefferson Lab data are compatible
+with zero for this asymmetry. So are the preliminary COMPASS data except for the region
 $x>0.1$ for negative hadrons, where the trend of the data provides a first 
@@
 with the WW-type approximation for $h_{1L}^{\perp(1)q}(x)$.
-
-\newpage
 
@@
 
-The Kotzinian-Mulders function $h^{\perp q}_{1L}$ in conjunction with 
-the Boer-Mulders function, and the TMD $g^{\perp q}_{1T}$ in conjunction 
+The Kotzinian--Mulders function $h^{\perp q}_{1L}$ in conjunction with 
+the Boer--Mulders function, and the TMD $g^{\perp q}_{1T}$ in conjunction 
 with the Sivers function obey the positivity bounds 
@@
 The inequalities (\ref{eq:positivity},~\ref{eq:positivity1}) 
-must be strictly satisfied by the {\it exact} leading--order QCD 
+must be strictly satisfied by the {\it exact} leading-order QCD 
 expressions for the TMDs.  
@@
 Therefore, considering that we deal with approximations 
-(WW-type, Gauss) and considering the current state of TMD-extractions, 
+(WW-type, Gauss) and considering the current state of TMD extractions, 
 the inequalities (\ref{eq:positivity},~\ref{eq:positivity1}) constitute
@@
 
-To conduct a test we use the Gaussian Ans\"atze 
+To conduct a test we use the Gaussian Ans\''atze 
 (\ref{Eq:Gauss-f1}, \ref{Eq:Gauss-h1}, \ref{Eq:Gauss-f1Tperp}, 
@@
 
-\newpage
 %========= SECTION 8: TWIST-3 IN WW-TYPE APPROXIMATION ===============
-\section{subleading-twist asymmetries in WW-type approximation}
+\section{Subleading-twist asymmetries in WW-type approximation}
 \label{Sec-7:twist-3-and-WW}
@@
 
-\subsection{\boldmath subleading-twist  $A_{LU}^{\sin\phi_h}$}
+\subsection{\boldmath Subleading-twist  $A_{LU}^{\sin\phi_h}$}
 \label{Sec-7.1:FLU}
@@
 $\tilde{G}^{\perp a}$ and $\tilde{E}^a$ and neglected; the other 2
-terms are proportional to the twist-3 TMDs $e^a$ and $g^{\perp a}$ which
+terms are proportional to the twist-3 TMDs $e^a$ and $g^{\perp a}$, which
 also turn out to be given in terms of pure twist-3 terms upon the 
 inspection of Eqs.~(\ref{Eq:WW-type-1},~\ref{Eq:WW-type-gperp}).
-Hence, after consequently applying the WW-type approximation we are left 
+Hence, after consequently applying the WW-type approximation, we are left 
 with no term. Our approximation predicts this structure function to be zero.
@@
 
-Indeed, data from JLab, HERMES and COMPASS show a clearly non-zero 
+Indeed, data from Jefferson Lab, HERMES and COMPASS show a clearly non-zero 
 asymmetry $A_{LU}^{\sin\phi_h} = F_{LU}^{\sin\phi_h}/F_{UU}$ of the order of 2\,$\%$ 
@@
 To conclude, the WW-type approximation predicts $A_{LU}^{\sin\phi}\approx 0$
-in contradiction with experiment. The size of the observed effect seems
+in contradiction to experiment. The size of the observed effect seems
 in line with the WW-type approximation, as
@@
 
-\newpage
-
-\subsection{\boldmath subleading-twist  $A_{LT}^{\cos\phi_S}$}
+\subsection{\boldmath Subleading-twist  $A_{LT}^{\cos\phi_S}$}
 \label{Sec-7.2:FLTcosphiS}
@@
 with ${\avkperp_{g_T}}={\avkperp_{g_1}}$. We then determine $g^{q}_{T}(x)$ 
-according to Eq.~(\ref{Eq:WW-original1}) which is a well-tested
+according to Eq.~(\ref{Eq:WW-original1}), which is a well-tested
 approximation in DIS, see Sec.~\ref{Sec-3.4:WW-classic-experiment}.
@@
 (due to the weight $\kperp^2/(2M_N^2)$ in the (1)-moment) implies a kinematical 
-zero in $\kperp$ as $g^{q}_{T}(x, 0) = 0$  which is not supported by model 
+zero in $\kperp$ as $g^{q}_{T}(x, 0) = 0$,  which is not supported by model 
 calculations \cite{Avakian:2010br}. Second, the more economic (because 
@@
 
-In the middle panel of Fig.~\ref{g1t_jlab} our predictions
+Fig.~\ref{altcosphis} shows our predictions
 for $A_{LT}^{\cos\phi_S}$ are shown in comparison to preliminary
@@
 asymmetry is small and compatible with the COMPASS data within
-error bars. More precise data are necessary to judge how
+uncertainties. 
+Preliminary HERMES data~\cite{Pappalardo:2012zz} confirm a small asymmetry. 
+More precise data are necessary to judge how
 well the WW-type approximation works in this case. Such data
-could come from JLab 12 experiments, see Fig.~\ref{altcosphi_jlab}.
+could come from JLab12 experiments.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
+\begin{figure}[htb!]
 \centering
-\includegraphics[width=0.37\textwidth]{\FigPath/ALTcosPhi_COMPASS_x.pdf} 
-\caption{\label{altcosphi_jlab} Predictions for the double--spin asymmetry
-	$A_{LT}^{\cos\phi_S}$  as a function of $x$ from a proton target
-	at JLab 12.
-	\TD{Bakur: can you prepare a separate plot for this asymmetry 
-	based on the middle panel of Fig.~\ref{g1t_jlab}?
-	Then we could skip here the prediction.}}
+\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphis_pip.pdf} 
+\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphis_pim.pdf} 
+\caption{\label{altcosphis} Subleading-twist $A_{LT}^{\cos\phi_S}$ 
+	  as functions of $x$ from scattering of 160 GeV
+	longitudinally polarized muons off a transversely polarized 
+	proton target \cite{Parsamyan:2015dfa}.
+	}
 \end{figure}
@@
 
-\newpage
-\subsection{\boldmath subleading-twist  $A_{LT}^{\cos(2\phi_h - \phi_S)}$}
+\subsection{\boldmath Subleading-twist  $A_{LT}^{\cos(2\phi_h - \phi_S)}$}
 \label{Sec-7.3:FLTcos2phi-phiS}
@@
 In the WW-type approximation this asymmetry is expressed in terms of
-$g_T^{\perp a}(x,\kperp)$ for which we assume a Gaussian Ansatz according to 
+$g_T^{\perp a}(x,\kperp)$, for which we assume a Gaussian Ansatz according to 
 Eq.~(\ref{eq:gtperpnew}) in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs},
@@
 $A_{LT}^{\cos(2\phi_h -\phi_S)}=F_{LT}^{\cos(2\phi_h -\phi_S)}/F_{UU}$ as function 
-of $x$ are displayed in the right panel of Fig.~\ref{g1t_jlab} in
+of $x$ are displayed in  Fig.~\ref{altcos2phihphis} in
 comparison to preliminary COMPASS data from Ref.~\cite{Parsamyan:2015dfa}. 
-The asymmetry is very small, so we show our predictions on a larger
-scale in Fig.~\ref{altcos2phi_jlab}. At the current stage one may
+The asymmetry is very small, so at the current stage one may
 conclude that the WW-type approximation for the asymmetry 
 $A_{LT}^{\cos(2\phi_h -\phi_S)}$ is compatible with available data. In view 
-of the smallness of the effect, cf.\  Fig.~\ref{altcos2phi_jlab}, 
+of the smallness of the effect, cf.\  Fig.~\ref{altcos2phihphis}, 
 it might be difficult to obtain more quantitative insights
 in near future. 
-
-\
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/ALTcos2PhiminusPhiS_COMPASS_x.pdf} 
-\caption{\label{altcos2phi_jlab} $A_{LT}^{\cos(2\phi_h - \phi_S)}$ 
-	as a function of $ x $ from a proton target for the COMPASS
-	kinematics (enlarged detail of right panel Fig.~\ref{g1t_jlab} 
-	where also the preliminary COMPASS data \cite{Parsamyan:2015dfa}
-	are shown). The smallness
+\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pip}
+\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pim} 
+\caption{\label{altcos2phihphis} $A_{LT}^{\cos(2\phi_h - \phi_S)}$ 
+	as a function of $ x $ from a proton target in comparison to the preliminary COMPASS data \cite{Parsamyan:2015dfa}. The smallness
 	of this asymmetry has two natural reasons. First, being twist-3
 	it is $M_N/Q$ suppressed. Second, it is proportional to
-	$P_{hT}^2$ with $P_{hT}\ll Q$ in TMD approach.
-	\TD{Bakur: can you prepare a separate plot for this asymmetry 
-	based on the right panel of Fig.~\ref{g1t_jlab}?
-	Then we could skip here the prediction.}}
+	$P_{hT}^2$ with $P_{hT}\ll Q$ in TMD approach.}
 \end{figure}
@@
 
-\newpage
-
-\subsection{\boldmath   subleading-twist  $A_{LL}^{\cos\phi_h}$}
+\subsection{\boldmath   Subleading-twist  $A_{LL}^{\cos\phi_h}$}
 \label{Sec-7.3:FLLcosphi}
@@
 In WW-type approximation the only contribution to $F_{LL}^{\cos\phi_h}$
-is due to $g_{L}^{\perp q}(x,k_\perp)$ which we assume to have a
+is due to $g_{L}^{\perp q}(x,k_\perp)$, which we assume to have a
 Gaussian $k_\perp$--behavior according to Eq.~(\ref{eq:gLperp})
@@
 \centering
-
-\vspace{1cm}
-\includegraphics[width=0.6\textwidth]{\FigPath/A_LL0_Pr0711_Zgt02.pdf}
+%\vspace{1cm}
+\includegraphics[width=0.9\textwidth]{\FigPath/A_LL_Pr0711_Zgt02.pdf}
 	\caption{\label{allcosphi_jlab} $A_{LL}^{\cos(\phi_h)}$  
@@
 
-\newpage
-\subsection{\boldmath subleading-twist $A_{UL}^{\sin\phi_h}$ }
+\subsection{\boldmath Subleading-twist $A_{UL}^{\sin\phi_h}$ }
 \label{Sec-7.4:FULsinphi}
@@
 In WW-type approximation $A_{UL}^{\sin\phi_h}$ is described by 
-$h_L^q(x,\kperp)$ for which we assume the Gaussian Ansatz 
+$h_L^q(x,\kperp)$, for which we assume the Gaussian Ansatz 
 (\ref{eq:hLnew}) in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}
@@
 \centering
-\includegraphics[width=0.35\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
-\includegraphics[width=0.35\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
-\includegraphics[width=0.7\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
+\includegraphics[width=0.9\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}
 \caption{\label{aulsinphi_jlab} 
@@
 The asymmetries $A_{UL}^{\sin\phi_h}=F_{UL}^{\sin\phi_h}/F_{UU}$ are compared
-to HERMES, JLab, and preliminary COMPASS data in Fig.~\ref{aulsinphi_jlab}.
+to HERMES, Jefferson Lab, and preliminary COMPASS data in Fig.~\ref{aulsinphi_jlab}.
 The WW-type approximation reproduces the positive sign of the asymmetry
@@
 The WW-type approximation is not able to explain the large effect
-observed at HERMES and JLab for $\pi^0$ in the large--$x$ region 
+observed at HERMES and Jefferson Lab for $\pi^0$ in the large--$x$ region 
 $0.1< x < 0.5$ in Fig.~\ref{aulsinphi_jlab}. 
-\ps{Overall, the WW-type approximation is not adequate to catch the
+Overall, the WW-type approximation is not adequate to catch the
 flavor dependence of this asymmetry. This indicates that here the 
 tilde-terms are not negligible, and have a characteristic flavor 
-dependence which is distinct from that of the Collins effect.}
-
-\newpage
-
-\subsection{\boldmath subleading-twist  $A_{UT}^{\sin\phi_S}$}
+dependence that is distinct from that of the Collins effect.
+
+\subsection{\boldmath Subleading-twist  $A_{UT}^{\sin\phi_S}$}
 \label{Sec-7.6:FUTsinphiS}
@@
 In this structure function some interesting new features occur.
-The first feature is that after applying the WW-type approximation 
+The first feature is that after applying the WW-type approximation, 
 not one but three terms are left, cf.\ 
@@
 two terms proportional to $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$,
-and one term proportional to $f_T^q(x,\kperp)$ which is associated with
+and one term proportional to $f_T^q(x,\kperp)$, which is associated with
 the second interesting feature. This T-odd TMD must satisfy the sum rule 
@@
 	by the sum rule (\ref{Eq:sum-rules-T-odd}).}
-Assuming Gaussian Ans\"atze (\ref{eq:hTperpnew},~\ref{eq:hTnew}) 
+Assuming Gaussian Ans\''atze (\ref{eq:hTperpnew},~\ref{eq:hTnew}) 
 for $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ in 
@@
 (\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8}), the expression 
-for $F_{UT}^{\sin\phi_S}$ is given in terms a single term
+for $F_{UT}^{\sin\phi_S}$ is given in terms of a single term
 \begin{subequations}\begin{alignat}{1}
@@
 $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_1^{ }}$. 
-The third interesting feature is the occurrence of a term which drops 
+The third interesting feature is the occurrence of a term that drops 
 out upon integrating the structure function over $\Phperp$, cf.\ 
@@
 \centering
-\includegraphics[width=0.4\textwidth]{\FigPath/AUTsinphiS_HERMES_x.pdf}
-\caption{\label{Fig-AUTsinphiS-HERMES} 
- 	Subleading--twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which 
+\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sinphis_pip.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sinphis_pim.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphiS_HERMES_x.pdf}
+\caption{\label{autsinphis} 
+ 	Subleading-twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which 
 	is predicted to vanish in the WW-type approximation, in 
-	comparison to preliminary HERMES data \cite{Schnell:2010zza}.}
+	comparison to preliminary COMPASS~\cite{Parsamyan:2015dfa} and HERMES data \cite{Schnell:2010zza}.}
 \end{figure}
@@
 therefore $A_{UT}^{\sin\phi_S}(x)=0$. 
-\ps{Preliminary 
-HERMES \cite{Schnell:2010zza} (Fig.~\ref{Fig-AUTsinphiS-HERMES}) and 
-COMPASS \cite{Parsamyan:2015dfa} (Fig.~\ref{autsinphi_jlab}) data 
+Preliminary 
+HERMES \cite{Schnell:2010zza} (Fig.~\ref{autsinphis}) and 
+COMPASS \cite{Parsamyan:2015dfa} (Fig.~\ref{autsinphis}) data 
 indicate that at $x\gtrsim 0.1$ the signal is clearly non-zero and 
-thus inconsistent with this WW-type prediction.}
-
-\newpage
+thus inconsistent with this WW-type prediction.
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{\FigPath/UT_Pr10.pdf}
-\includegraphics[width=0.3\textwidth]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf}
-
-\caption{\label{autsinphi_jlab} 
-%	Preliminary data for azimuthal transverse target single--spin 
-%	asymmetries as functions of $x$ from the COMPASS experiment 
-%	\cite{Parsamyan:2015dfa}.
-%	Left panel: 
-%	leading--twist $A_{UT}^{\sin(3\phi_h-\phi_S)}(x)$ which 
-%	determines the pretzelosity TMD, one of our basis functions. 
-%	This asymmetry was discussed in Sec.~\ref{Sec-5.6:pretzel-basis} 
-%	and is included here for completeness. 
-	Left panel: 
-        \TD{remove and show in Fig.~\ref{aut_h1tp_jlab} instead.}
-	Middle panel:
-	subleading--twist $A_{UT}^{\sin\phi_S}(x)$ which is predicted to vanish
-	in the WW-type approximation, see Sec.~\ref{Sec-7.6:FUTsinphiS}.
-	Right panel: 
-	leading--twist $A_{UT}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to the 
-	WW-type prediction described in Sec.~\ref{Sec-7.8:FUTsin2phi-phiS}.
-	\TD{Bakur: please, can you re-do these plots in separate figures?}}
+\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sin2phihphis_pip}
+\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sin2phihphis_pip}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf}
+\caption{\label{autsin2phihphis} 
+	Subleading--twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison with preliminary COMPASS data~\cite{Parsamyan:2015dfa}, and 	
+	subleading--twist $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to the 
+	preliminary HERMES data~\cite{Schnell:2010zza}.
+	}
 \end{figure}
@@
 
-\subsection{\boldmath subleading-twist  $A_{UT}^{\sin(2\phi_h-\phi_S)}$ }
+\subsection{\boldmath Subleading-twist  $A_{UT}^{\sin(2\phi_h-\phi_S)}$ }
 \label{Sec-7.8:FUTsin2phi-phiS}
 
-Also in this asymmetry we end up more than one surviving 
-contribution in our treatment. We assume Gaussian Ans\"atze for 
+Also in this asymmetry we end up with more than one surviving 
+contribution in our treatment. We assume Gaussian Ans\''atze for 
 $f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
@@
 The asymmetries $A_{UT}^{\sin (2 \phi_h-\phi_S)}=F_{UT}^{\sin (2 \phi_h-\phi_S)}/F_{UU}$  
-are plotted in the right panel of Fig.~\ref{autsinphi_jlab} in comparison 
-to preliminary COMPASS data \cite{Parsamyan:2015dfa}. The predicted
-asymmetry is small and compatible with data which are consistent
-with a zero effect within error bars.
-
-\newpage
-\subsection{\boldmath subleading-twist  $A_{UU}^{\cos\phi_h}$ }
+are plotted in Fig.~\ref{autsin2phihphis} in comparison 
+to preliminary COMPASS \cite{Parsamyan:2015dfa} and 
+HERMES \cite{Schnell:2010zza} data. The predicted
+asymmetry is small and compatible with the data that are consistent
+with a zero effect within uncertainties.
+
+\subsection{\boldmath Subleading-twist  $A_{UU}^{\cos\phi_h}$ }
 \label{Sec-7.7:FUUcosphi}
@@
 \centering
-\includegraphics[width=0.37\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
-\includegraphics[width=0.37\textwidth]{\FigPath/AUUcosphi_HERMES_x.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
+\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_HERMES_x.pdf}
 \caption{\label{auucosphi_jlab} 
@@
 	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}. Right 
-	panel: the same for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.}
+	panel: the same asymmetry $A_{UU, \langle y \rangle}^{\cos\phi_h}$ for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.}
 \end{figure}
 
-The asymmetries $A_{UU}^{\cos\phi_h}$ were measured in experiments at
-EMC \cite{Aubert:1983cz}, JLab \cite{Osipenko:2008aa,Mkrtchyan:2007sr}, 
+The asymmetries $A_{UU}^{\cos\phi_h}$ were measured by
+EMC \cite{Aubert:1983cz}, at Jefferson Lab \cite{Osipenko:2008aa,Mkrtchyan:2007sr}, 
 HERMES \cite{Airapetian:2012yg}, and COMPASS \cite{Adolph:2014pwc}.
@@
 COMPASS data. 
-\ps{The WW-type approximation tends to overstimate the data at
+The WW-type approximation tends to overstimate the data at
 COMPASS especially in the small-$x$ region. It is also not
 compatible with the flavor dependence seen at HERMES. 
-However both experiments seem not to agree for instance on the shape
+However, both experiments seem not to agree for instance on the shape
 of the asymmetry for negative pions or hadrons. More experimental and
 theoretical work is need to clarify whether this could be due to
-power corrections.}
+power corrections.
 
 %======= SECTION 9: CONCLUSIONS ======================================
-\newpage
 \section{Conclusions}
@@
 The theoretical and phenomenological understanding of most of the
-leading--twist SIDIS structure functions for the production of 
+leading-twist SIDIS structure functions for the production of 
 unpolarized hadrons is relatively advanced: factorization is
@@
 terms of one of 8 twist-2 TMDs convoluted with one of 2 twist-2 FFs.
-For subleading--twist SIDIS structure functions the situation
+For subleading-twist SIDIS structure functions the situation
 is far more complex for two reasons. First, factorization is not 
 proven and must be assumed. 
-Second, each of the subleading--twist structure functions
+Second, each of the subleading-twist structure functions
 receives 4 or 6 contributions from various TMDs and FFs one of
@@
 
-In this work we have explored the so--called WW--type approximation
+In this work we have explored the so-called WW-type approximation
 as a candidate guideline for the description of SIDIS structure
@@
 an approach all twist-2 and twist-3 structure functions can be
-described in terms of 8 basis functions: 6 TMDs and 2 FFs
+described in terms of 8 basis functions: 6 TMDs and 2 FFs,
 which are each twist-2. All other TMDs and FFs, assuming this
@@
 We remark that the generalized parton model 
-approach of Ref.~\cite{Anselmino:2011ch} provides a description,
-which is largely equivalent to ours.
+approach of Ref.~\cite{Anselmino:2011ch} provides a description
+that is largely equivalent to ours.
 
@@
 the unpolarized TMD and FF $f_1^q(x,\kperp)$ and $D_1^q(x,\pperp)$,
-makes also use of other experiments, most notably Drell-Yan
+makes also use of other experiments, most notably Drell--Yan
 and hadron production in $e^+e^-$ annihilations.)
@@
 of the QCD vacuum, and confirmed by data and lattice QCD studies.
-The classic WW-approximation for $g_2(x)$ works with a relative
+The classic WW approximation for $g_2(x)$ works with a relative
 accuracy of $\pm\,40\,\%$ or better. This is remarkable.
-The instanton vacuum model predicts an analogous WW-approximation
+The instanton vacuum model predicts an analogous WW approximation
 for the chirally odd twist-3 PDF $h_L^q(x)$ to work similarly
@@
 Most importantly, we have conducted systematic tests of
-WW-approximations with available published or 
+WW approximations with available published or 
 preliminary (and soon to be published) SIDIS data
-from HERMES, COMPASS, and JLab.
-
-We found the following results. The two leading--twist 
-structure functions amenable to WW-type approximation 
+from HERMES, COMPASS, and Jefferson Lab.
+
+We found the following results. The two leading-twist 
+structure functions amenable to WW-type approximations, 
 	$F_{LT}^{\cos(\phi_h -\phi_S)}$ and 
-	$F_{UL}^{\sin(2\phi_h)}$ 
-are well--described (the former) or at least compatible 
+	$F_{UL}^{\sin(2\phi_h)}$, 
+are well-described (the former) or at least compatible 
 (the latter) with the data in this approximation. For 
@@
 but also in this case the trend is encouraging
-especially thanks to the recent COMPASS data.
+especially thanks to the recent preliminary COMPASS data.
 We have also shown that our approach satisfies positivity
-inequalities which is a non--trivial consistency check 
+inequalities, which is a non-trivial consistency check 
 considering the crude approximations (WW-type, Gaussian 
@@
 predicted to be very small in the WW-type approximation,
-sometimes smaller than a fraction or a percent. This is
+sometimes smaller than a fraction of a percent. This is
 compatible with the available data in the sense that the
@@
 
-In the case of the three subleading--twist structure functions 
+In the case of the three subleading-twist structure functions 
 	$F_{UU}^{\cos\phi_h}$, 
 	$F_{UL}^{\sin\phi_h}$,
-	$F_{LU}^{\sin\phi_h}$,
+	$F_{LU}^{\sin\phi_h}$, and
 	$F_{UT}^{\sin\phi_S}$
@@
 approximations do not work.
-Incidently, these asymmetries include the very first non--zero azimuthal 
-asymmetry measured in unpolarized SIDIS ($F_{UU}^{\cos(\phi_h)}$),
-the very first non--zero target single spin asymmetry measured in SIDIS
-($F_{UL}^{\sin\phi_h}$), and the very first non--zero beam single spin 
+Incidently, these asymmetries include the very first non-zero azimuthal 
+asymmetry measured in unpolarized SIDIS ($F_{UU}^{\cos\phi_h}$),
+the very first non-zero target single-spin asymmetry measured in SIDIS
+($F_{UL}^{\sin\phi_h}$), and the very first non-zero beam single-spin 
 asymmetry measured in SIDIS ($F_{LU}^{\sin\phi_h}$).
@@
 is well-justified and an effective expansion can be conducted; in
-the case of TMDs however it is less appropriate to speak about a
+the case of TMDs, however, it is less appropriate to speak about a
 systematic expansion in terms of $\bar{q}q$, $\bar{q}gq$, etc 
-correlators). It will be very interesting to learn whether e.g.\ 
+correlators). It will be very interesting to learn whether, e.g., 
 in $F_{UL}^{\sin\phi_h}$ or $F_{LU}^{\sin\phi_h}$ a single $\bar{q}gq$--term 
@@
 a particularly interesting case: this asymmetry is due to $\bar{q}gq$
-only with no contamination from $\bar{q}q$ terms.
-So $F_{LU}^{\sin\phi_h}$ offers a unique view on the physics of $\bar{q}gq$ 
-correlators which is worth--exploring for its own sake.
+only, without ``contamination'' from $\bar{q}q$ terms.
+Thus $F_{LU}^{\sin\phi_h}$ offers a unique view on the physics of $\bar{q}gq$ 
+correlators, worth exploring for its own sake.
 
 The results presented in this work are of importance for several reasons.
-To the best of our knowledge it is the first complete study of all SIDIS 
+To the best of our knowledge, it is the first complete study of all SIDIS 
 structure functions up to twist-3 in a unique approach. The results are 
-useful for experiments prepared in the near-term (JLab 12) or proposed 
-in the long-term (Electron Ion Collider), and provide helpful input for 
+useful for experiments prepared in the near term (JLab 12) or proposed 
+in the long term (Electron Ion Collider), and provide helpful input for 
 Monte Carlo event generators \cite{Avakian:2015vha}.
@@
 of the nucleon beyond leading twist.
-
-\newpage
 
@@
 Department of Energy under Contract No.~DE-AC05-06OR23177 (A.P.) 
-and within TMD Collaboration framework, and by the National 
+and within the TMD Collaboration framework, and by the National 
 Science Foundation under Contract No.\ PHY-1623454 (A.P.) and 
-Contract No.\ PHY-1406298 (P.S.) and the Wilhelm Schuler Stiftung (P.S.).
-
-\newpage
+Contract No.\ PHY-1406298 (P.S.), and the Wilhelm Schuler Stiftung (P.S.).
+
 \appendix
 
-\section{\boldmath The ``minimal basis" of TMDs and FFs}
+\section{\boldmath The ``minimal basis'' of TMDs and FFs}
 \label{App:basis}
@@
 might be related to the fact that the lattice predictions \cite{Hagler:2009mb}
-do not refer to TMDs entering in SIDIS (or Drell-Yan or other process) 
+do not refer to TMDs entering in SIDIS (or Drell--Yan or other process) 
 because a different gauge link was chosen, see Sec.~\ref{Sec-3.5:WW-lattice}. 
@@
 
-\newpage
 \section{Convolution integrals and expressions in Gaussian Ansatz}
@@
 
-\subsection{Gaussian Ans\"atze for the derived TMDs used in this work}
+\subsection{Gaussian Ans\''atze for the derived TMDs used in this work}
 \label{App-B:Gauss-Ansatz-non-basis-TMDs}
 
-Having discussed the Gaussian Ans\"atze for the 8 basis functions
+Having discussed the Gaussian Ans\''atze for the 8 basis functions
 in Eqs.~(\ref{Eq:Gauss-f1}--\ref{Eq:Gauss-h1Tperp}) of
 Sec.~\ref{Sec-4.4:evaluation} and in App.~\ref{App:basis},
-we list here the Ans\"atze for the following derived TMDs:
+we list here the Ans\''atze for the following derived TMDs:
 \begin{subequations}\begin{align}
@@
 
-\newpage
 \subsection{Comment on TMDs subject to the sum rules (\ref{Eq:sum-rules-T-odd})}
@@
 
-\newpage
 \subsection{Convolution integrals in Gaussian Ansatz}
@@
 
-\newpage
 \section{Mathematica package}
@@
 observables for a proton target, detected charged pions and beam 
-helicities \ps{$\pm1$ or $0$ (with the latter denoting an unpolarized beam).}
+helicities $\pm1$ or $0$ (with the latter denoting an unpolarized beam).
 Make sure that you do not move \texttt{example.nb} to another directory 
@@
 
-\newpage
 \bibliography{\BibPath/biblio_ww}

### 2018-07-20 tex/test-WW-type-00z.tex
final

@@
 	10125 Torino, Italy}
-\affiliation[f]{Institut f\''ur Theoretische Physik, Universit\''at 
+\affiliation[f]{Institut f\"ur Theoretische Physik, Universit\"at 
   	Regensburg, 93040 Regensburg, Germany}
@@
 	IKERBASQUE, Basque Foundation for Science, 48013 Bilbao, Spain}
-\affiliation[j]{Institute for Theoretical Physics, Universit\''at T\''ubingen,
-	D-72076 T\''ubingen, Germany} % Auf der Morgenstelle 14,
+\affiliation[j]{Institute for Theoretical Physics, Universit\"at T\"ubingen,
+	D-72076 T\"ubingen, Germany} % Auf der Morgenstelle 14,
 
@@
 to SIDIS, and describe our procedure to evaluate the structure 
-functions in this approximation and the Gaussian Ansatz which we use
+functions in this approximation and the Gaussian Ans\"atze which we use
 to model the $k_\perp$ dependence of TMDs.
@@
 
-\subsection{Gaussian Ansatz for TMDs and FFs}
+\subsection{Gaussian Ans\"atze for TMDs and FFs}
 \label{Sec-4.3:evaluation}
 
-In this work we will use the so-called Gaussian Ansatz for the TMDs and FFs.
-This Ansatz, which for a generic TMD or FF is given by
+In this work we will use the so-called Gaussian Ans\"atze for the TMDs and FFs.
+This Ans\"atze, which for a generic TMD or FF is given by
 \be\label{Eq:Gauss-generic}
@@
 (\ref{Eq:def-convolution-integral}) can be solved analytically 
-with this Ansatz. Far more important is the fact that it works 
+with this Ans\"atze. Far more important is the fact that it works 
 phenomenologically with a good accuracy in many practical applications
@@
 Signori:2013mda,Anselmino:2013lza}.
-Of course this Ansatz is only a rough approximation. For instance, 
+Of course this Ans\"atze is only a rough approximation. For instance, 
 it is not consistent with general matching expectations for large 
@@
 in the Drell--Yan process, etc) are small compared to the hard
-scale in the process, then the Ansatz works quantitatively
+scale in the process, then the Ans\"atze works quantitatively
 very well. The most recent and detailed tests were reported in 
-\cite{Schweitzer:2010tt}, where the Gaussian Ansatz was shown to
+\cite{Schweitzer:2010tt}, where the Gaussian Ans\"atze was shown to
 describe the most recent SIDIS data: no deviations were observed 
@@
 with expectations from QCD \cite{Aybat:2011zv}.
-The Gaussian Ansatz is approximately compatible with 
+The Gaussian Ans\"atze is approximately compatible with 
 the $\kperp$--shapes obtained from evolution \cite{Aybat:2011zv}
@@
 high \cite{Efremov:2009ze} renormalization scales support this
-Ansatz as a good approximation.
+Ans\"atze as a good approximation.
 
@@
 
-The Gaussian Ansatz is compatible with many WW-type approximations,
+The Gaussian Ans\"atze is compatible with many WW-type approximations,
 but not all. The trivial approximations (\ref{Eq:WW-type-1}) and
 (\ref{Eq:WW-type-eLperp}--\ref{Eq:WW-type-fLperp}) cause no issue. 
-The Gaussian Ansatz can also be applied to the nontrivial approximations 
+The Gaussian Ans\"atze can also be applied to the nontrivial approximations 
 in Eqs.~(\ref{Eq:WW-type-Cahn}--\ref{Eq:WW-type-gTperp})
@@
 are related to transverse moments of twist-2 TMDs. In such cases the 
-Gaussian Ansatz is not compatible with the WW-type approximations:
+Gaussian Ans\"atze is not compatible with the WW-type approximations:
 for instance, the approximation (\ref{Eq:WW-type-gT}) relates
@@
 $g_T^q(x,\kperp^2)$ certainly could not be Gaussian. If one wanted to take
-the Gaussian Ansatz and WW-type approximations literally, one clearly
+the Gaussian Ans\"atze and WW-type approximations literally, one clearly
 would deal with an incompatibility. However, we of course must keep 
@@
 Some comments are in order to understand how the usage of the Gaussian 
-Ansatz and the WW-type approximations can be reconciled.
+Ans\"atze and the WW-type approximations can be reconciled.
 First, let us remark that the individual TMDs, say 
@@
 WW-type approximations and then solve convolution integrals 
-with Gaussian Ansatz.
+with Gaussian Ans\"atze.
 In general, this would yield different (and bulkier) analytical 
@@
 To summarize, our procedure is to solve first the convolution 
-integrals in Gaussian Ansatz, and use then WW-type approximations.
+integrals in Gaussian Ans\"atze, and use then WW-type approximations.
 When implementing this procedure we will see that the results 
@@
 
-\subsection{\boldmath Leading-twist $F_{UU}$ and Gaussian Ansatz}
+\subsection{\boldmath Leading-twist $F_{UU}$ and Gaussian Ans\"atze}
 \label{Sec-5.1:FUU-basis}
 
-As explained in Sec.~\ref{Sec-4.3:evaluation} the Gaussian Ansatz is chosen
+As explained in Sec.~\ref{Sec-4.3:evaluation} the Gaussian Ans\"atze is chosen
 not only because it considerably simplifies the calculations, but more 
@@
 
-The Gaussian Ansatz for the unpolarized TMD and FF 
+The Gaussian Ans\"atze for the unpolarized TMD and FF 
 is given by Eqs.~(\ref{Eq:Gauss-f1},~\ref{Eq:Gauss-D1}).
@@
 QCD the connection of TMDs to PDFs is subtle \cite{Collins:2016hqq}.
-Figure~\ref{FUU-show-pT-dependence} illustrates how the Gaussian Ansatz
+Figure~\ref{FUU-show-pT-dependence} illustrates how the Gaussian Ans\"atze
 describes selected SIDIS data.
@@
 on the used parametrizations (App.~\ref{App:basis}), and for 
-technical details on the Gaussian Ansatz (App.~\ref{App:factor}).
+technical details on the Gaussian Ans\"atze (App.~\ref{App:factor}).
 
@@
 %========= SECTION 6: TESTING APPROACH WITH A_LL =====================
-\subsection{\boldmath Leading-twist $A_{LL}$ and first test of Gaussian Ansatz
+\subsection{\boldmath Leading-twist $A_{LL}$ and first test of Gaussian Ans\"atze
 	in polarized scattering}
@@
 
-The Gaussian Ansatz is useful in unpolarized case 
+The Gaussian Ans\"atze is useful in unpolarized case 
 \cite{Anselmino:2005nn,Collins:2005ie,D'Alesio:2007jt,Schweitzer:2010tt,
@@
 First, the Jefferson Lab data \cite{Avakian:2010ae} are compatible
-with the Gaussian Ansatz within uncertainties. Second, the lattice 
+with the Gaussian Ans\"atze within uncertainties. Second, the lattice 
 results---in the way we use them in App.~\ref{App:basis-g1}---give an appropriate 
@@
 fit of Ref.~\cite{Anselmino:2013vqa}, which implies that the 
-data are compatible with the Gaussian Ansatz also in this case.
+data are compatible with the Gaussian Ans\"atze also in this case.
 
@@
 statistical uncertainties and systematic uncertainties (the latter
-introduced by choosing a certain fit Ansatz which however can be 
+introduced by choosing a certain fit Ans\"atze which however can be 
 avoided through neural network techniques \cite{Ball:2014uwa}).
@@
 
-We assume for $g^{\perp}_{1T}$ the Gaussian Ansatz as shown 
-in Eq.~(\ref{eq:g1t}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, 
+We assume for $g^{\perp}_{1T}$ the Gaussian Ans\"atze as shown 
+in Eq.~(\ref{eq:g1t}) of App.~\ref{App-B:Gauss-Ans\"atze-non-basis-TMDs}, 
 see also \cite{Kotzinian:2006dw}, and evaluate $g^{\perp (1) q}_{1T}(x)$ 
@@
 
-In the Gaussian Ansatz the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$ 
+In the Gaussian Ans\"atze the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$ 
 has the form
@@
 $h_{1L}^{\perp a}$, Eq.~(\ref{eq:h1l_final}) in
-App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, with
+App.~\ref{App-B:Gauss-Ans\"atze-non-basis-TMDs}, with
 $\avkperp_{h_{1L}^\perp} = \avkperp_{h_{1}}$ as
@@
 strong model assumptions (WW-type approximations for $g^{\perp q}_{1T}$ 
-and $h^{\perp q}_{1L}$ and Gaussian Ansatz for all TMDs), and (ii) we deal 
+and $h^{\perp q}_{1L}$ and Gaussian Ans\"atze for all TMDs), and (ii) we deal 
 with first extractions which have sizable uncertainties including 
@@
 
-To conduct a test we use the Gaussian Ans\''atze 
+To conduct a test we use the Gaussian Ans\"atze 
 (\ref{Eq:Gauss-f1}, \ref{Eq:Gauss-h1}, \ref{Eq:Gauss-f1Tperp}, 
@@
 Secs.~\ref{Sec-3.4:WW-classic-experiment} and \ref{Sec-5.1:FUU-basis}.
-We assume the Gaussian Ansatz for $g_T^a(x,\kperp)$ shown in
-Eq.~(\ref{eq:gtnew}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} 
+We assume the Gaussian Ans\"atze for $g_T^a(x,\kperp)$ shown in
+Eq.~(\ref{eq:gtnew}) of App.~\ref{App-B:Gauss-Ans\"atze-non-basis-TMDs} 
 with ${\avkperp_{g_T}}={\avkperp_{g_1}}$. We then determine $g^{q}_{T}(x)$ 
@@
 Notice that we followed here the scheme explained in 
-Sec.~\ref{Sec-4.4:evaluation}: first assume Gaussian Ansatz, then apply 
+Sec.~\ref{Sec-4.4:evaluation}: first assume Gaussian Ans\"atze, then apply 
 WW-type approximation. For some structure functions the order of 
@@
 in the convolution integral (\ref{Eq:WW-original1}) and then solve the
-convolution integral with Gaussian Ansatz. The result is an
+convolution integral with Gaussian Ans\"atze. The result is an
 analytical expression which is bulkier than (\ref{Eq:FLTcosphiS-Gauss})  
@@
 In the WW-type approximation this asymmetry is expressed in terms of
-$g_T^{\perp a}(x,\kperp)$, for which we assume a Gaussian Ansatz according to 
-Eq.~(\ref{eq:gtperpnew}) in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs},
+$g_T^{\perp a}(x,\kperp)$, for which we assume a Gaussian Ans\"atze according to 
+Eq.~(\ref{eq:gtperpnew}) in App.~\ref{App-B:Gauss-Ans\"atze-non-basis-TMDs},
 and use the WW-type approximation (\ref{Eq:WW-type-gTperp}) as
@@
 Gaussian $k_\perp$--behavior according to Eq.~(\ref{eq:gLperp})
-in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} with 
+in App.~\ref{App-B:Gauss-Ans\"atze-non-basis-TMDs} with 
 the Gaussian width $\avkperp_{g_{L}^\perp}=\avkperp_{g_1}$. 
@@
 In WW-type approximation $A_{UL}^{\sin\phi_h}$ is described by 
-$h_L^q(x,\kperp)$, for which we assume the Gaussian Ansatz 
-(\ref{eq:hLnew}) in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}
+$h_L^q(x,\kperp)$, for which we assume the Gaussian Ans\"atze 
+(\ref{eq:hLnew}) in App.~\ref{App-B:Gauss-Ans\"atze-non-basis-TMDs}
 with $\avkperp_{h_L}=\avkperp_{h_1}$. We explore (\ref{Eq:WW-type-6}) 
@@
 	by the sum rule (\ref{Eq:sum-rules-T-odd}).}
-Assuming Gaussian Ans\''atze (\ref{eq:hTperpnew},~\ref{eq:hTnew}) 
+Assuming Gaussian Ans\"atze (\ref{eq:hTperpnew},~\ref{eq:hTnew}) 
 for $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ in 
-App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} and relating 
+App.~\ref{App-B:Gauss-Ans\"atze-non-basis-TMDs} and relating 
 them to transversity via the WW-type approximations
@@
 Also in this asymmetry we end up with more than one surviving 
-contribution in our treatment. We assume Gaussian Ans\''atze for 
+contribution in our treatment. We assume Gaussian Ans\"atze for 
 $f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
 according to Eqs.~(\ref{eq:hTperpnew},~\ref{eq:hTnew},~\ref{eq:ftperpnew}) 
-in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} with
+in App.~\ref{App-B:Gauss-Ans\"atze-non-basis-TMDs} with
 $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_{1T}^\perp}$
@@
 Sec.~\ref{Sec-7.6:FUTsinphiS}.
-Using the Gaussian Ansatz for $f^\perp(x,\kperp)$ in Eq.~(\ref{eq:fperpnew})
-of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} we obtain 
+Using the Gaussian Ans\"atze for $f^\perp(x,\kperp)$ in Eq.~(\ref{eq:fperpnew})
+of App.~\ref{App-B:Gauss-Ans\"atze-non-basis-TMDs} we obtain 
 \begin{subequations}\begin{alignat}{1}
@@
 considering the crude approximations (WW-type, Gaussian 
-Ansatz for TMDs) in our approach.
+Ans\"atze for TMDs) in our approach.
 
@@
 To describe the transverse momentum dependence of $f_1^a(x,k_\perp^2)$ 
-and $D_1(z,P_\perp^2)$ we use the Gaussian Ansatz in 
+and $D_1(z,P_\perp^2)$ we use the Gaussian Ans\"atze in 
 Eqs.~(\ref{Eq:Gauss-f1},~\ref{Eq:Gauss-D1}). All early 
@@
 require to relax these assumptions. However, one may also expect that the 
-Gaussian Ansatz will remain a useful {\it approximation} as long as one is 
+Gaussian Ans\"atze will remain a useful {\it approximation} as long as one is 
 interested in describing data on transverse hadron momenta $\Phperp \ll Q $.
@@
 
-\section{Convolution integrals and expressions in Gaussian Ansatz}
+\section{Convolution integrals and expressions in Gaussian Ans\"atze}
 \label{App:factor}
@@
 of TMDs and FFs and give the explicit results obtained assuming the
-Gaussian Ansatz.
+Gaussian Ans\"atze.
 
@@
 
-\subsection{Gaussian Ansatz}
-
-For a generic TMD and FF the Gaussian Ansatz is given by 
+\subsection{Gaussian Ans\"atze}
+
+For a generic TMD and FF the Gaussian Ans\"atze is given by 
 \be
@@
 
-\subsection{Gaussian Ans\''atze for the derived TMDs used in this work}
-\label{App-B:Gauss-Ansatz-non-basis-TMDs}
-
-Having discussed the Gaussian Ans\''atze for the 8 basis functions
+\subsection{Gaussian Ans\"atze for the derived TMDs used in this work}
+\label{App-B:Gauss-Ans\"atze-non-basis-TMDs}
+
+Having discussed the Gaussian Ans\"atze for the 8 basis functions
 in Eqs.~(\ref{Eq:Gauss-f1}--\ref{Eq:Gauss-h1Tperp}) of
 Sec.~\ref{Sec-4.4:evaluation} and in App.~\ref{App:basis},
-we list here the Ans\''atze for the following derived TMDs:
+we list here the Ans\"atze for the following derived TMDs:
 \begin{subequations}\begin{align}
@@
 
-\subsection{Convolution integrals in Gaussian Ansatz}
+\subsection{Convolution integrals in Gaussian Ans\"atze}
 \label{App:convol-details}
@@
 Solving the convolution integrals relevant for SIDIS in the 
-Gaussian Ansatz yields 
+Gaussian Ans\"atze yields 
 \begin{subequations}\label{Eq:Gaussian-integrals-RAW}\ba

### 2018-07-21 tex/test-WW-type-00z.tex
final

--- 2018-07-20 tex/test-WW-type-00z.tex
@@
 \allowdisplaybreaks
-
-% section 5.4 - is transversity really the only information on the tensor charge. how about lattice?
-% FIgure 7: is it the <y> asymmetry (including prefactors)?
-% section 5.6 (lines 819 ff) partially repetition (cubic Phperp suppression) and need reference to HERMES plot.
-% figure 16 claims to be A_{LL}^{\cos\phi} but is just A_{LL}
 
@@
 asymmetries, and discuss the applicability of the Wandzura--Wilczek-type 
-approximations on the basis of available data. We make predictions which 
+approximations on the basis of available data. We make predictions that 
 can be tested by data from Jefferson Lab, COMPASS, HERMES, and the future 
@@
 \newpage
-%\subsection*{Color Legend}
-
-%General comments: 
-%	\TD{dark red color, command: {$\backslash{\rm TD}\{\dots\}$}}\\
-%Alexei's corrections: 
-%	\AP{redish color, command: {$\backslash{\rm AP}\{\dots\}$}}\\
-%Aram's corrections: 
-%	\ak{orange color, command: {$\backslash{\rm ak}\{\dots\}$}}\\
-%Bakur's corrections: 
-%	\bp{green-blue color, command: {$\backslash{\rm bp}\{\dots\}$}}\\
-%Gunar's corrections: 
-%	\gs{violett color, command: {$\backslash{\rm gs}\{\dots\}$}}\\
-%Kemal's corrections: 
-%	\kt{greenish color, command: {$\backslash{\rm kt}\{\dots\}$}}\\
-%Marc's corrections: 
-%	\ms{green color, command: {$\backslash{\rm ms}\{\dots\}$}}\\
-%Peter's corrections: 
-%	\ps{blue color, command: {$\backslash{\rm ps}\{\dots\}$}}\\
-%Anatoli Vasilievich, Bakur, Bernie, Saman: \\
-%	corrections already introduced in black color \& confirmed by e-mail.
 
@@
 which are defined in terms of quark-quark correlators 
-\cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,Bacchetta:2006tn},
-and depend on two independent variables: for TMDs, 
-on the fraction $x$ of nucleon 
-momentum carried by the parton and intrinsic transverse momentum $\kperp$ 
-of the parton. For FFs, on the fraction $z$ of the parton momentum 
-transferred to the hadron for and the transverse momentum of the hadron
+\cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,Bacchetta:2006tn}.
+Both of them depend on two independent variables: in the case of TMDs, 
+on the fraction $x$ of nucleon momentum carried by the parton and intrinsic transverse momentum $\kperp$ 
+of the parton, while in the case of FFs, on the fraction $z$ of the parton momentum 
+transferred to the hadron and the transverse momentum of the hadron
 acquired during the fragmentation process. 
@@
 To summarize, our procedure is to solve first the convolution 
-integrals in Gaussian Ansatz, and use then WW-type approximations.
+integrals with a Gaussian Ansatz, and use then WW-type approximations.
 When implementing this procedure we will see that the results 
@@
 \caption{\label{aut_f1t_jlab} Sivers asymmetry 
-	$A_{UT}^{\sin(\phi_h-\phi_S)}$ from proton target as function of $ x $ 
+	$A_{UT}^{\sin(\phi_h-\phi_S)}$ for a proton target as function of $ x $ 
 	based on the fit \cite{Anselmino:2011gs} in comparison to 
 	(left panel) HERMES \cite{Airapetian:2009ae}
-	and (right panel) COMPASS data \cite{Adolph:2012sp}.}
+	and (right panel) COMPASS  \cite{Adolph:2012sp} data.}
 \end{figure}
@@
 \caption{\label{aut_h1_jlab}  Collins asymmetry 
-	$A_{UT,  \langle y\rangle}^{\sin(\phi_h+\phi_S)}$ from proton target as function of $ x $ 
+	$A_{UT,  \langle y\rangle}^{\sin(\phi_h+\phi_S)}$ for a proton target as function of $ x $ 
 	based on the fit \cite{Anselmino:2013vqa} in comparison to 
@@
 \caption{\label{auu_cos2phi_jlab} The asymmetry 
-	$A_{UU, \langle y\rangle}^{\cos(2\phi_h)}$ from proton target as function of $ x $ 
+	$A_{UU, \langle y\rangle}^{\cos(2\phi_h)}$ for a proton target as function of $ x $ 
 	based on the fit \cite{Barone:2009hw} in comparison to 
@@
 
-Asymmetries  for $A_{UU, \langle y\rangle}^{\cos(2\phi_h)}=(1-y)F_{UU}^{\cos(2\phi_h)}/((1-y + y^2/2)F_{UU})$
-HERMES \cite{Airapetian:2012yg} and $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$ COMPASS \cite{Adolph:2014pwc}
+The asymmetries  $A_{UU, \langle y\rangle}^{\cos(2\phi_h)}=(1-y)F_{UU}^{\cos(2\phi_h)}/((1-y + y^2/2)F_{UU})$
+for HERMES \cite{Airapetian:2012yg} and $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$ for COMPASS \cite{Adolph:2014pwc}
 are plotted in Fig.~\ref{auu_cos2phi_jlab}, where we only considered the
@@
 	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2010se} 
-	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ HERMES \cite{Schnell:2010zza} in comparison to the best fit 
+	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES \cite{Schnell:2010zza} in comparison to the best fit 
 	(whose 1-$\sigma$ uncertainty band is compatible with zero) 
@@
 Two out of the 8 leading--twist structure functions 
-can be described in WW-type approximation thanks to 
-Eqs.~(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}) which 
+can be described in the WW-type approximation thanks to 
+Eqs.~(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}), which 
 relate $g_{1T}^{\perp (1) q}(x)$ and $h_{1L}^{\perp (1) q}(x)$ to the
 basis functions $g_1^q(x)$ and $h_1^a(x)$, see Fig.~\ref{g1t_h1l_functions}.
-These TMDs are sometimes referred to as ``gear worms:'' 
+These TMDs are sometimes referred to as ``worm gear'' functions, where 
 $g_{1T}^{\perp q}$ describes the distributions of longitudinally 
 polarized quarks inside a transversely polarized nucleon,
-$h_{1L}^{\perp q}$ the opposite configuration, namely transversely 
+and $h_{1L}^{\perp q}$ the opposite configuration, namely transversely 
 polarized quarks inside a longitudinally polarized nucleon.
@@
 \cite{Kotzinian:2006dw,Kotzinian:2008fe,Boffi:2009sh} are shown.
-Our results are also compatible with the Jefferson Lab data, which was 
-taken with a neutron ($^3$He) target \cite{Huang:2011bc} and has 
-larger statistical uncertainty than the preliminary COMPASS data. 
+Our results are also compatible with the Jefferson Lab data, which were 
+taken with a neutron ($^3$He) target \cite{Huang:2011bc} and have 
+larger statistical uncertainties than the preliminary COMPASS and HERMES data. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 momenta $P_{hT}\ll Q$, while $F_{LT}^{\cos(\phi_h -\phi_S)}$ is linear. 
-In addition, the former is proportional to the Collins function 
+In addition, the former is proportional to the Collins function, 
 which is smaller than $D_1^q(z)$, and the WW-type approximation 
@@
 
-To conduct a test we use the Gaussian Ans\''atze 
+To conduct a test we use the Gaussian Ansatz 
 (\ref{Eq:Gauss-f1}, \ref{Eq:Gauss-h1}, \ref{Eq:Gauss-f1Tperp}, 
@@
 
-Fig.~\ref{h1l_pos} shows that the results of our approach for the 
+Figure~\ref{h1l_pos} shows that the results of our approach for the 
 ``normalized inequalities'' for both TMDs lie between 
@@
 
-Fig.~\ref{altcosphis} shows our predictions
-for $A_{LT}^{\cos\phi_S}$ are shown in comparison to preliminary
-COMPASS data from Ref.~\cite{Parsamyan:2015dfa}. The predicted
+Figure~\ref{altcosphis} shows our predictions
+for $A_{LT}^{\cos\phi_S}$ in comparison to preliminary
+COMPASS data~\cite{Parsamyan:2015dfa}. The predicted
 asymmetry is small and compatible with the COMPASS data within
@@
 Our predictions for the asymmetry  
-$A_{LT}^{\cos(2\phi_h -\phi_S)}=F_{LT}^{\cos(2\phi_h -\phi_S)}/F_{UU}$ as function 
+$A_{LT}^{\cos(2\phi_h -\phi_S)}=F_{LT}^{\cos(2\phi_h -\phi_S)}/F_{UU}$ as a function 
 of $x$ are displayed in  Fig.~\ref{altcos2phihphis} in
@@
 \caption{\label{altcos2phihphis} $A_{LT}^{\cos(2\phi_h - \phi_S)}$ 
-	as a function of $ x $ from a proton target in comparison to the preliminary COMPASS data \cite{Parsamyan:2015dfa}. The smallness
-	of this asymmetry has two natural reasons. First, being twist-3
-	it is $M_N/Q$ suppressed. Second, it is proportional to
+	as a function of $ x $ from a proton target in comparison to preliminary COMPASS data \cite{Parsamyan:2015dfa}. The smallness
+	of this asymmetry has two natural reasons: first, being twist-3
+	it is $M_N/Q$ suppressed; and second, it is proportional to
 	$P_{hT}^2$ with $P_{hT}\ll Q$ in TMD approach.}
@@
 The asymmetry $A_{LL}^{\cos \phi_h}=F_{LL}^{\cos \phi_h}/F_{UU}$ predicted by the
-WW-type approximation in this case is small and compatible with presently 
-available data, see Fig.~\ref{allcosphi_jlab}.
+WW-type approximation in this case is small and compatible with preliminary COMPASS (see Fig.~\ref{allcosphi_jlab}) and HERMES data.
 We remark that previously this asymmetry was studied in
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b]
+\begin{figure}[t]
 \centering
@@
 	by the sum rule (\ref{Eq:sum-rules-T-odd}).}
-Assuming Gaussian Ans\''atze (\ref{eq:hTperpnew},~\ref{eq:hTnew}) 
+Assuming Gaussian Ansatz (\ref{eq:hTperpnew},~\ref{eq:hTnew}) 
 for $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ in 
@@
 therefore $A_{UT}^{\sin\phi_S}(x)=0$. 
-Preliminary 
-HERMES \cite{Schnell:2010zza} (Fig.~\ref{autsinphis}) and 
-COMPASS \cite{Parsamyan:2015dfa} (Fig.~\ref{autsinphis}) data 
+Preliminary COMPASS \cite{Parsamyan:2015dfa}
+ (Fig.~\ref{autsinphis} top) and 
+HERMES \cite{Schnell:2010zza} (Fig.~\ref{autsinphis} bottom) data 
 indicate that at $x\gtrsim 0.1$ the signal is clearly non-zero and 
@@
 \caption{\label{autsin2phihphis} 
-	Subleading--twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison with preliminary COMPASS data~\cite{Parsamyan:2015dfa}, and 	
-	subleading--twist $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to the 
+	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison to preliminary COMPASS data~\cite{Parsamyan:2015dfa}, and 	
+	similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to  
 	preliminary HERMES data~\cite{Schnell:2010zza}.
@@
 Also in this asymmetry we end up with more than one surviving 
-contribution in our treatment. We assume Gaussian Ans\''atze for 
+contribution in our treatment. We assume Gaussian Ansatz for 
 $f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
@@
 	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}. Right 
-	panel: the same asymmetry $A_{UU, \langle y \rangle}^{\cos\phi_h}$ for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.}
+	panel: the corresponding $A_{UU, \langle y \rangle}^{\cos\phi_h}$ for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.}
 \end{figure}
@@
 
-\subsection{Gaussian Ans\''atze for the derived TMDs used in this work}
+\subsection{Gaussian Ansatz for the derived TMDs used in this work}
 \label{App-B:Gauss-Ansatz-non-basis-TMDs}
 
-Having discussed the Gaussian Ans\''atze for the 8 basis functions
+Having discussed the Gaussian Ansatz for the 8 basis functions
 in Eqs.~(\ref{Eq:Gauss-f1}--\ref{Eq:Gauss-h1Tperp}) of
 Sec.~\ref{Sec-4.4:evaluation} and in App.~\ref{App:basis},
-we list here the Ans\''atze for the following derived TMDs:
+we list here the Ans\"atze for the following derived TMDs:
 \begin{subequations}\begin{align}
@@
 
-SIDIS cross section examples are presented in Fig.~\ref{fig:package} .
-
-\begin{figure}[ht]
+SIDIS cross section examples are presented in Fig.~\ref{fig:package}.
+
+\begin{figure}[t]
 \centering
-
-\vspace{5mm}
-
+%\vspace{5mm}
 \includegraphics[width=0.45\textwidth]{\FigPath/cross_section_phih.pdf} 

### 2018-07-23 tex/test-WW-type-00z.tex
v01a

@@
 
+\newcommand{\AP}[1]{\red{#1}}
 %\newcommand{\ak}[1]{\orange{#1}}
@@
 
-\preprint{\red{version ``00z''}; \today; JLAB-THY-18-XXXX}
+\preprint{\red{version ``01a''}; \today; JLAB-THY-18-XXXX}
 
@@
 \ee
-and the asymmetries are defined as follows
+and the asymmetries \AP{$A_{XY}^{\rm weight}$,  are defined in terms of structure functions $F_{XY}^{\rm weight}$, as follows}
 \be
@@
 Experimental collaborations often define asymmetries in terms of counts 
-$N(\phi_h)$. This means the kinematic prefactors $p_i$ and $1/(x\,y\,Q^2)$ 
+$N(\phi_h)$. This means the kinematic prefactors $p_i$ %and $1/(x\,y\,Q^2)$ 
 are included in the numerators or denominators of the asymmetries which
@@
 	\ee
-where the Wilson-lines refer to the SIDIS process 
+where the Wilson-lines \AP{${\cal W}_{(0,\,\infty)}
+	{\cal W}_{(\infty,\xi)}$} refer to the SIDIS process 
 \cite{Collins:2002kn}. For a generic four-vector $a^\mu$ we define
@@
 
-The fragmentation functions are similarly defined in terms of the correlator
+\AP{Fragmentation functions are defined through the following correlator [10]
+  (where $\bfpperp$ denotes the transverse momentum of the produced hadrons
+  acquired during the fragmentation process with respect to the quark)}
 \be\label{Eq:correlator-FF}
@@
  F_{UU}	&=&{\cal C}\biggl[\;\omega^{\{0\}}\,f_1 D_1 \;\biggr] \, , \label{FUU}\\
+  F_{UU}^{\cos 2\phi_h} 	
+	&=& {\cal C}\biggl[\;\omega^{\{2\}}_{\rm AB}\,h_{1}^{\perp }\,H_{1}^{\perp }\;
+	\biggr] \, , \label{F_UUcos2phi}\\
+F_{UL}^{\sin 2\phi_h} 	
+	&=& {\cal C}\biggl[\;\omega^{\{2\}}_{\rm AB}\,h_{1L}^{\perp } H_{1}^{\perp }\; 
+	\biggr] \, , \label{F_UUsin2phi}\\
  F_{LL}	&=&{\cal C}\biggl[\;\omega^{\{0\}}\,g_1 D_1 \;\biggr] \, , \label{FLL}\\
+ F_{LT}^{\cos(\phi_h -\phi_S)} 
+	&=& {\cal C}\biggl[\,\omega^{\{1\}}_{\rm B} \,g_{1T}^\perp D_1\biggr] \, ,
+	\label{Eq:FLT-twist-2}\\
  F_{UT}^{\sin\left(\phi_h +\phi_S\right)} 
@@
 	\label{Eq:FUTSiv}\\
- F_{LT}^{\cos(\phi_h -\phi_S)} 
-	&=& {\cal C}\biggl[\,\omega^{\{1\}}_{\rm B} \,g_{1T}^\perp D_1\biggr] \, ,
-	\label{Eq:FLT-twist-2}\\
- F_{UU}^{\cos 2\phi_h} 	
-	&=& {\cal C}\biggl[\;\omega^{\{2\}}_{\rm AB}\,h_{1}^{\perp }\,H_{1}^{\perp }\;
-	\biggr] \, , \label{F_UUcos2phi}\\
- F_{UL}^{\sin 2\phi_h} 	
-	&=& {\cal C}\biggl[\;\omega^{\{2\}}_{\rm AB}\,h_{1L}^{\perp } H_{1}^{\perp }\; 
-	\biggr] \, , \label{F_UUsin2phi}\\
  F_{UT}^{\sin\left(3\phi_h -\phi_S\right)} 
@@
  Eqs.~(\ref{Eq:FUUcosphi}--\ref{FLTsin(2phi-phiS)}) contain an explicit 
- factor $M/Q$. We also recall that we neglect two structure functions
+ factor $M_N/Q$. We also recall that we neglect two structure functions
  (denoted in  \cite{Bacchetta:2006tn} 
@@
 
-In the T-even case one obtains the following approximations,
+In the T-even case one obtains the following approximations \footnote{\AP{
+Notice that Ref.~\cite{Bacchetta:2006tn} uses four-vector notations for transverse vectors, while in this paper we always utilize two-vectors for transverse vectors, such that e.g.
+${\kperp^2}_{\rm our} = -{{\bm p}_T^2}_{\tiny \rm Ref.\cite{Bacchetta:2006tn}}$
+  and analog for other scalar products of {\it transverse} vectors.}},
 where the terms on the left-hand-side are twist-3, those on the 
@@
 \begin{subequations}\ba
-	E(z,\pperp^2)      &\WWtype& 0 \, ,
+	E(z,\pperp^2)      &\WWtype& 0 ,
 	\label{Eq:WW-type-FF-1}\\
-	G^\perp(z,\pperp^2) &\WWtype& 0 \, ,
+	G^\perp(z,\pperp^2) &\WWtype& 0 ,
 	\label{Eq:WW-type-FF-2}\\
@@
 Data support (\ref{Eq:g2-in-WW-approximation}) to a good accuracy
-\cite{Anthony:2002hy,Abe:1998wq,Airapetian:2011wu}, although especially 
+\cite{Anthony:2002hy,Adams:1994id,Abe:1998wq,Airapetian:2011wu}, although especially 
 at smaller $x$ more stringent tests are not yet possible. Overall it has 
@@
 Notice that SIDIS alone is of course not sufficient to determine the basis
-functions uniquely: the 8 basis functions appear in 6 SIDIS structure functions.
-It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
-and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
-play also important roles.
+functions uniquely: \AP{8 twist-2 TMDs (or 6 ``basis'' TMDs) and 2 twist-2 TMD FFs appear in 15 structure functions (8 twist-2 and 5 sub-leading). 
+Definitely hadron production in $e^+e^-$ annihilation data is needed, each FF couples with 4 different twist-2 TMD PDFs, and so for each FF we have a case with 5 unknowns accessible in 4 twist-2 observables.
+It is crucial to take advantage of  Drell--Yan process for TMDs
+and other processes 
+play also important roles.}
 
@@
 \begin{subequations}\ba
+F_{UU}^{\cos\phi_h} &\stackrel{\rm WW}{=}&\frac{2M_N}{Q}\,{\cal C}\biggl[\phantom{-}
+	 \omega^{\{1\}}_{\rm A}\,x\,h\,H_{1}^{\perp } 
+   	-\omega^{\{1\}}_{\rm B}\,x\,f^\perp D_1\biggr]
+        \with{ }
+	{f^{\perp a}\to f_1^a, \; h^a\to h_1^{\perp a}}
+	{with Eqs.~(\ref{Eq:WW-type-Cahn},~\ref{Eq:WW-type-last})} 
+	\label{Eq:WW-type-FUUcosphi}\\
+	F_{UL}^{\sin\phi_h} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
+   	\phantom{-}\omega^{\{1\}}_{\rm A}\,
+    	x\,h_L  H_1^{\perp } \biggr]
+        \with{ }
+	{h_L^a\to h_{1L}^{\perp a}}
+	{with Eq.~(\ref{Eq:WW-type-6})}  
+	\label{Eq:WW-type-FULsinphi}\\
+F_{UT}^{\sin \phi_S } &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,
+	{\cal C}\biggl[ \phantom{-}\omega^{\{0\}} \, x\,f_TD_1
+	-\frac{\omega^{\{2\}}_{\rm B}}{2}\,(xh_T-xh_T^\perp)\,H_{1}^{\perp } \biggr]
+        \with
+	{f_T^a \to f_{1T}^{\perp a},}
+	{h_T^a-h_T^{\perp a}\to h_1^a}
+	{(\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8})}  
+	\label{Eq:WW-type-FUTsinphiS}\\
+F_{UT}^{\sin(2\phi_h -\phi_S)} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
+   	\;\omega^{\{2\}}_{\rm C}\,
+   	{  x\,f_T^\perp}D_1
+        + \frac{\omega^{\{2\}}_{\rm AB}}{2} 
+	{x(h_T+h_T^\perp)}H_1^\perp \biggr]
+        \with
+	{f_T^{\perp a}\to f_{1T}^{\perp a},}
+	{(h_T^a+h_T^{\perp a})\to h_{1T}^{\perp a}}{with 
+	(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8})} \!
+	\;\;\;\;\\
 F_{LU}^{\sin\phi_h} &\stackrel{\rm WW}{=}& 0\,, \phantom{\frac11}
@@
 	{g_T^{\perp a}\to g_1^a}
-	{Eqs.~(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T})}   \\
-F_{UL}^{\sin\phi_h} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
-   	\phantom{-}\omega^{\{1\}}_{\rm A}\,
-    	x\,h_L  H_1^{\perp } \biggr]
-        \with{ }
-	{h_L^a\to h_{1L}^{\perp a}}
-	{with Eq.~(\ref{Eq:WW-type-6})}  
-	\label{Eq:WW-type-FULsinphi}\\
-F_{UU}^{\cos\phi_h} &\stackrel{\rm WW}{=}&\frac{2M_N}{Q}\,{\cal C}\biggl[\phantom{-}
-	 \omega^{\{1\}}_{\rm A}\,x\,h\,H_{1}^{\perp } 
-   	-\omega^{\{1\}}_{\rm B}\,x\,f^\perp D_1\biggr]
-        \with{ }
-	{f^{\perp a}\to f_1^a, \; h^a\to h_1^{\perp a}}
-	{with Eqs.~(\ref{Eq:WW-type-Cahn},~\ref{Eq:WW-type-last})} 
-	\label{Eq:WW-type-FUUcosphi}\\
-F_{UT}^{\sin \phi_S } &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,
-	{\cal C}\biggl[ \phantom{-}\omega^{\{0\}} \, x\,f_TD_1
-	-\frac{\omega^{\{2\}}_{\rm B}}{2}\,(xh_T-xh_T^\perp)\,H_{1}^{\perp } \biggr]
-        \with
-	{f_T^a \to f_{1T}^{\perp a},}
-	{h_T^a-h_T^{\perp a}\to h_1^a}
-	{(\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8})}  
-	\label{Eq:WW-type-FUTsinphiS}\\
-F_{UT}^{\sin(2\phi_h -\phi_S)} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
-   	\;\omega^{\{2\}}_{\rm C}\,
-   	{  x\,f_T^\perp}D_1
-        + \frac{\omega^{\{2\}}_{\rm AB}}{2} 
-	{x(h_T+h_T^\perp)}H_1^\perp \biggr]
-        \with
-	{f_T^{\perp a}\to f_{1T}^{\perp a},}
-	{(h_T^a+h_T^{\perp a})\to h_{1T}^{\perp a}}{with 
-	(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8})} \!.
-	\;\;\;\;
+	{Eqs.~(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T})}   
 \ea\end{subequations}
@@
 on respectively charged pion and hadron production from a proton target.
-The $P_{hT}$--dependences of the data are equally well described, which
+\AP{Notice that COMPASS points are lower than theoretical calculation, that may indicate evolution effects~\cite{Aybat:2011ta, Anselmino:2012aa}}.
+The $P_{hT}$--dependences of the data are well described, which
 confirms that the Gaussian model works also in this case.
@@
 
-The $F_{UT}^{\sin(\phi_h+\phi_S)}$ modulation of the SIDIS cross section is due 
+The $F_{UT}^{\sin(\phi_h+\phi_S)}$ \AP{structure function} of the SIDIS cross section is due 
 to the convolution of the transversity distribution $h_1$ and the Collins 
@@
 \cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,Bacchetta:2012ty,
-Radici:2015mwa,Radici:2018iag}.
+Radici:2015mwa,Radici:2018iag}. \AP{The first polarized Drell-Yan data were measured by COMPASS~\cite{Aghasyan:2017jop,Parsamyan:2018zju}.}
 It describes the distribution of transversely polarized quarks
@@
 The structure function $F_{UU}^{\cos(2\phi_h)}$ arises from a convolution of
-the Collins fragmention function and the TMD $h_{1}^{\perp q}$ which describes
+the Collins fragmention function and the \AP{Boer-Mulders} TMD $h_{1}^{\perp q}$ which describes
 the distribution of transversely polarized partons inside an unpolarized
@@
 Boer--Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$, which does not describe
-the data accurately. In fact, it is suspected that this observable receives 
+the data well, \AP{especially for COMPASS one can see that calculation and the data are of opposite signs}. In fact, it is suspected that this observable receives 
 a significant contribution from the Cahn effect \cite{Cahn:1978se}, a 
@@
 function suffers a cubic suppression for small transverse hadron
-momenta. This is the strongest $P_{hT}$-suppression of all SIDIS 
-structure functions through leading and subleading twist, making
-it challenging to measure.
+momenta.
 
@@
 
-This asymmetry was measured at Jefferson Lab~\cite{Huang:2011bc}, COMPASS~\cite{Parsamyan:2015dfa} and HERMES~\cite{Pappalardo:2011cu,Pappalardo:2012zz} (for the latter two experiments only preliminary results are available so far).
+This asymmetry was measured at Jefferson Lab~\cite{Huang:2011bc}, COMPASS~\cite{
+Parsamyan:2007ju,Parsamyan:2018evv,Parsamyan:2015dfa} and HERMES~\cite{Pappalardo:2011cu,Pappalardo:2012zz} (for the latter two experiments only preliminary results are available so far).
  Fig.~\ref{cosphihphis} 
-shows the preliminary results from the 2010 COMPASS data \cite{Parsamyan:2015dfa}. 
+shows the preliminary results from the 2010 COMPASS data \cite{Parsamyan:2013fia}. 
 We approximate the 
-charged hadrons ($90\,\%$ of which are $\pi^\pm$ at COMPASS) by 
+charged hadrons ($70-80\,\%$ of which are $\pi^\pm$ at COMPASS) by 
 charged pions, see App.~\ref{App:basis-f1-D1}.
@@
 	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$ 
-	 in comparison to the preliminary COMPASS data \cite{Parsamyan:2015dfa}.
+	 in comparison to the preliminary COMPASS data \cite{Parsamyan:2018ovx}.
 	}
@@
 studied at HERMES \cite{Airapetian:1999tv,Airapetian:2002mf}, COMPASS 
-\cite{Parsamyan:2015dfa}, and Jefferson Lab \cite{Avakian:2010ae,Jawalkar:2017ube}.
+\cite{Parsamyan:2018ovx}, and Jefferson Lab \cite{Avakian:2010ae,Jawalkar:2017ube}.
 In Fig.~\ref{aul_jlab} proton data are shown for $\pi^\pm$ in the
@@
 $0.023 < x < 0.4$ and $y < 0.85$. 
-The COMPASS data were taken with a 160 GeV muon beam and show 
+The COMPASS data were taken in 2007 (160 GeV) and 2011 (200 GeV) and show 
 the asymmetry for charged hadrons (in practice mainly pions).
@@
 \cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,
-Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz}. 
+Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz}, \AP{these 2\% come after $1/Q$ suppression. Unsuppressed effect at large $x$ at COMPASS would reach 10\%.} 
 On the one hand this is interesting: this observable provides a unique 
@@
 for $A_{LT}^{\cos\phi_S}$ in comparison to preliminary
-COMPASS data~\cite{Parsamyan:2015dfa}. The predicted
+COMPASS data~\cite{Parsamyan:2013fia}. The predicted
 asymmetry is small and compatible with the COMPASS data within
@@
 	longitudinally polarized muons off a transversely polarized 
-	proton target \cite{Parsamyan:2015dfa}.
+	proton target \cite{Parsamyan:2013fia}.
 	}
@@
 of $x$ are displayed in  Fig.~\ref{altcos2phihphis} in
-comparison to preliminary COMPASS data from Ref.~\cite{Parsamyan:2015dfa}. 
+comparison to preliminary COMPASS data from Ref.~\cite{Parsamyan:2013fia}. 
 The asymmetry is very small, so at the current stage one may
@@
 \caption{\label{altcos2phihphis} $A_{LT}^{\cos(2\phi_h - \phi_S)}$ 
-	as a function of $ x $ from a proton target in comparison to preliminary COMPASS data \cite{Parsamyan:2015dfa}. The smallness
+	as a function of $ x $ from a proton target in comparison to preliminary COMPASS data \cite{Parsamyan:2013fia}. The smallness
 	of this asymmetry has two natural reasons: first, being twist-3
@@
 The asymmetry $A_{LL}^{\cos \phi_h}=F_{LL}^{\cos \phi_h}/F_{UU}$ predicted by the
-WW-type approximation in this case is small and compatible with preliminary COMPASS (see Fig.~\ref{allcosphi_jlab}) and HERMES data.
+WW-type approximation in this case is compatible with preliminary COMPASS \cite{Parsamyan:2018ovx} (see Fig.~\ref{allcosphi_jlab}) and HERMES data.
 We remark that previously this asymmetry was studied in
@@
 	comparison to the preliminary COMPASS data 
-	\cite{Parsamyan:2015dfa}. }
+	\cite{Parsamyan:2018ovx}. }
 \end{figure}
@@
 	and JLab (red) \cite{Jawalkar:2017ube}.
-	Lower panel: preliminary $h^\pm$ COMPASS data \cite{Parsamyan:2015dfa}.}
+	Lower panel: preliminary $h^\pm$ COMPASS data \cite{Parsamyan:2018ovx}.}
 \end{figure}
@@
 but underestimates its magnitude. The results for negative pions and 
-hadrons at HERMES and COMPASS are compatible. An important test for this
+hadrons at HERMES and COMPASS \cite{Parsamyan:2018ovx} are compatible. An important test for this
 asymmetry is provided by neutral pions where in WW-type approximation
@@
 	is predicted to vanish in the WW-type approximation, in 
-	comparison to preliminary COMPASS~\cite{Parsamyan:2015dfa} and HERMES data \cite{Schnell:2010zza}.}
+	comparison to preliminary COMPASS~\cite{Parsamyan:2013fia} and HERMES data \cite{Schnell:2010zza}.}
 \end{figure}
@@
 therefore $A_{UT}^{\sin\phi_S}(x)=0$. 
-Preliminary COMPASS \cite{Parsamyan:2015dfa}
+Preliminary COMPASS \cite{Parsamyan:2013fia}
  (Fig.~\ref{autsinphis} top) and 
@@
 \caption{\label{autsin2phihphis} 
-	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison to preliminary COMPASS data~\cite{Parsamyan:2015dfa}, and 	
+	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison to preliminary COMPASS data~\cite{Parsamyan:2013fia}, and 	
 	similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to  
@@
 are plotted in Fig.~\ref{autsin2phihphis} in comparison 
-to preliminary COMPASS \cite{Parsamyan:2015dfa} and 
+to preliminary COMPASS \cite{Parsamyan:2013fia} and 
 HERMES \cite{Schnell:2010zza} data. The predicted
@@
 the very first non-zero target single-spin asymmetry measured in SIDIS
-($F_{UL}^{\sin\phi_h}$), and the very first non-zero beam single-spin 
-asymmetry measured in SIDIS ($F_{LU}^{\sin\phi_h}$).
+($F_{UL}^{\sin\phi_h}$), and \AP{is the only single-spin beam-spin asymmetry} measured in SIDIS ($F_{LU}^{\sin\phi_h}$).
 The WW-type prediction for $F_{UU}^{\cos(\phi_h)}$ tends to overshoot

### 2018-07-24 tex/test-WW-type-00z.tex
alexei

@@
 Experimental collaborations often define asymmetries in terms of counts 
-$N(\phi_h)$. This means the kinematic prefactors $p_i$ %and $1/(x\,y\,Q^2)$ 
+$N(\phi_h)$. This means the kinematic prefactors $p_i$ and $1/(x\,y\,Q^2)$ 
 are included in the numerators or denominators of the asymmetries which
@@
 approximations, it is possible to express all SIDIS structure functions
-in terms of the basis functions. 
-Notice that SIDIS alone is of course not sufficient to determine the basis
-functions uniquely: \AP{8 twist-2 TMDs (or 6 ``basis'' TMDs) and 2 twist-2 TMD FFs appear in 15 structure functions (8 twist-2 and 5 sub-leading). 
-Definitely hadron production in $e^+e^-$ annihilation data is needed, each FF couples with 4 different twist-2 TMD PDFs, and so for each FF we have a case with 5 unknowns accessible in 4 twist-2 observables.
-It is crucial to take advantage of  Drell--Yan process for TMDs
-and other processes 
+in terms of the basis functions. \AP{Notice that SIDIS alone is of course not sufficient to determine the basis
+functions uniquely: the 8 basis functions appear in 6 SIDIS structure functions.
+It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
+and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
 play also important roles.}
+%Notice that SIDIS alone is of course not sufficient to determine the basis
+%functions uniquely: \AP{8 twist-2 TMDs (or 6 ``basis'' TMDs) and 2 twist-2 TMD FFs appear in 15 structure functions (8 twist-2 and 5 sub-leading). 
+%Definitely hadron production in $e^+e^-$ annihilation data is needed, each FF couples with 4 different twist-2 TMD PDFs, and so for each FF we have a case with 5 unknowns accessible in 4 twist-2 observables.
+%It is crucial to take advantage of  Drell--Yan process for TMDs
+%and other processes 
+%play also important roles.}
 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pim.pdf}
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTPretzelosity_HERMES_x.pdf}
+\includegraphics[width=0.55\textwidth]{\FigPath/AUTPretzelosity_HERMES_x.pdf}
 
@@
 \centering
-\includegraphics[width=0.8\textwidth]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \quad
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_JLAB_x.pdf} 
+\includegraphics[width=0.9\textwidth]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \quad
+\includegraphics[width=0.55\textwidth]{\FigPath/AULsin2phi_JLAB_x.pdf} 
 \vspace{-5mm}
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
-\includegraphics[width=0.9\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}
+\includegraphics[width=0.8\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}
 \caption{\label{aulsinphi_jlab} 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sinphis_pim.pdf}
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTsinphiS_HERMES_x.pdf}
+\includegraphics[width=0.55\textwidth]{\FigPath/AUTsinphiS_HERMES_x.pdf}
 \caption{\label{autsinphis} 
@@
 \includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sin2phihphis_pip}
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf}
+\includegraphics[width=0.55\textwidth]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf}
 \caption{\label{autsin2phihphis} 

### 2018-07-25 tex/test-WW-type-00z.tex
final

@@
 Notice that Ref.~\cite{Bacchetta:2006tn} uses four-vector notations for transverse vectors, while in this paper we always utilize two-vectors for transverse vectors, such that e.g.
-${\kperp^2}_{\rm our} = -{{\bm p}_T^2}_{\tiny \rm Ref.\cite{Bacchetta:2006tn}}$
-  and analog for other scalar products of {\it transverse} vectors.}},
+${\bfkperp^2}_{\rm our} = -{{p}_T^2}_{\rm \tiny Ref.\cite{Bacchetta:2006tn}}$ and analog for other scalar products of {\it transverse} vectors.}},
 where the terms on the left-hand-side are twist-3, those on the 
@@
 approximations, it is possible to express all SIDIS structure functions
-in terms of the basis functions. \AP{Notice that SIDIS alone is of course not sufficient to determine the basis
-functions uniquely: the 8 basis functions appear in 6 SIDIS structure functions.
-It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
-and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
-play also important roles.}
+in terms of the basis functions. \AP{Notice that SIDIS alone is of course not sufficient to determine
+   the basis functions uniquely because the 8 basis functions appear
+   in 6 SIDIS leading-twist structure functions. It is crucial to take advantage of
+   other processes (such as Drell-Yan and hadron production in
+   $e^+e^-$ annihilation, which are indispensable for the determination
+   of $f_1^a$ and $D_1^a$).}
+%\AP{Notice that SIDIS alone is of course not sufficient to determine the basis
+%functions uniquely: the 8 basis functions appear in 6 \AP{leading-twist} SIDIS structure functions.
+%It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
+%and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
+%play also important roles.}
 %Notice that SIDIS alone is of course not sufficient to determine the basis
@@
 \cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,
-Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz}, \AP{these 2\% come after $1/Q$ suppression. Unsuppressed effect at large $x$ at COMPASS would reach 10\%.} 
+Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz}, \AP{these 2\% come after $1/Q$ suppression. Unsuppressed effect at large $x$ at COMPASS would reach 10\% \cite{private}.} 
 On the one hand this is interesting: this observable provides a unique 
@@
 approximations do not work.
-Incidently, these asymmetries include the very first non-zero azimuthal 
+Incidentally, these asymmetries include the very first non-zero azimuthal 
 asymmetry measured in unpolarized SIDIS ($F_{UU}^{\cos\phi_h}$),
 the very first non-zero target single-spin asymmetry measured in SIDIS
-($F_{UL}^{\sin\phi_h}$), and \AP{is the only single-spin beam-spin asymmetry} measured in SIDIS ($F_{LU}^{\sin\phi_h}$).
+($F_{UL}^{\sin\phi_h}$), and \AP{and the beam-spin asymmetry } ($F_{LU}^{\sin\phi_h}$).
 The WW-type prediction for $F_{UU}^{\cos(\phi_h)}$ tends to overshoot

### 2018-07-26 tex/test-WW-type-00z.tex
alexei
final

@@
 
-\preprint{\red{version ``01a''}; \today; JLAB-THY-18-XXXX}
+\preprint{\red{version ``01a''}; \today; JLAB-THY-18-2775}
 
@@
 form that lends itself to straightforward tests of the WW-type relations 
-as presented in this paper. Details about recent works and future 
-perspectives are discussed at the end of this section.
+as presented in this paper. \AP{This assumption holds if renormalization is multiplicative and
+   flavor-independent for the non-local lattice operators. This is
+   not true for all lattice actions [64]. But presumably it is true
+   if the lattice action preserves chiral symmetry, as it does in
+   the present case. For the latest developments we refer the
+   interested reader to Refs.~\cite{Alexandrou:2017dzj,Ishikawa:2017faj,Ji:2017oey,Yoon:2017qzo,Green:2017xeu,Zhang:2017bzy}.}
 
@@
 
-The leading--twist 6 TMDs 
+The 6 leading--twist TMDs 
 $f_1^a, \; f_{1T}^{\perp a}, \; g_1^a, \; h_1^a, \;h_1^{\perp a},\; h_{1T}^{\perp a}$
-and 2 FFs $D_1^a, \; H_1^{\perp a}$ provide a basis
+and 2 leading--twist FFs $D_1^a, \; H_1^{\perp a}$ provide a basis
 in the sense that in WW-type approximation all other TMDs and FFs 
@@
 In some cases, however, we know in advance that the WW-type approximations 
-have limitations, see next Section.
+have limitations, see next Section~\ref{Sec-3.8:limitations}.
 

### 2018-08-09 arxiv/test-WW-type.tex
arxiv

--- 2018-07-26 tex/test-WW-type-00z.tex
@@
 
-\newcommand{\AP}[1]{\red{#1}}
+%\newcommand{\AP}[1]{\red{#1}}
 %\newcommand{\ak}[1]{\orange{#1}}
@@
 
-\newcommand*{\FigPath}{./figs}%  
+\newcommand*{\FigPath}{.}%  
 \newcommand*{\BibPath}{.}%
@@
 
-\preprint{\red{version ``01a''}; \today; JLAB-THY-18-2775}
+\preprint{JLAB-THY-18-2775}
 
@@
 Neglecting $1/Q^2$ corrections, the kinematic prefactors $p_i$ are given by 
-% \ba\label{Eq:y-prefactors}
-% &&	p_1 = \varepsilon \equiv  
-%        \frac{1-y -\frac{1}{4}\slim \gamma^2 y^2}{1-y
-%        + \frac{1}{2}\slim y^2 +\frac{1}{4}\slim \gamma^2 y^2} 
-%        \approx \frac{1-y}{1-y+\frac12\,y^2} 		\;,\nonumber\\
-% &&	p_2 = \sqrt{1-\epsilon^2} \approx
-%        \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2} 	\;,\nonumber\\
-% &&	p_3 =  \sqrt{2\varepsilon(1+\varepsilon)}
-%        \approx \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2}\;,\nonumber\\
-% &&	p_4 =  \sqrt{2\varepsilon(1-\varepsilon)}
-%        \approx \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2} 	\;,\;\;\;
-% \ea
 \be\label{Eq:y-prefactors}
@@
 \ee
-and the asymmetries \AP{$A_{XY}^{\rm weight}$,  are defined in terms of structure functions $F_{XY}^{\rm weight}$, as follows}
+and the asymmetries $A_{XY}^{\rm weight}$,  are defined in terms of structure functions $F_{XY}^{\rm weight}$, as follows
 \be
@@
 	\ee
-where the Wilson-lines \AP{${\cal W}_{(0,\,\infty)}
-	{\cal W}_{(\infty,\xi)}$} refer to the SIDIS process 
+where the Wilson-lines ${\cal W}_{(0,\,\infty)}
+	{\cal W}_{(\infty,\xi)}$ refer to the SIDIS process 
 \cite{Collins:2002kn}. For a generic four-vector $a^\mu$ we define
@@
 
-\AP{Fragmentation functions are defined through the following correlator [10]
+Fragmentation functions are defined through the following correlator [10]
   (where $\bfpperp$ denotes the transverse momentum of the produced hadrons
-  acquired during the fragmentation process with respect to the quark)}
+  acquired during the fragmentation process with respect to the quark)
 \be\label{Eq:correlator-FF}
@@
 
-In the T-even case one obtains the following approximations \footnote{\AP{
+In the T-even case one obtains the following approximations \footnote{
 Notice that Ref.~\cite{Bacchetta:2006tn} uses four-vector notations for transverse vectors, while in this paper we always utilize two-vectors for transverse vectors, such that e.g.
-${\bfkperp^2}_{\rm our} = -{{p}_T^2}_{\rm \tiny Ref.\cite{Bacchetta:2006tn}}$ and analog for other scalar products of {\it transverse} vectors.}},
+${\bfkperp^2}_{\rm our} = -{{p}_T^2}_{\mbox{\rm Ref.\citep{Bacchetta:2006tn}}}$ and analog for other scalar products of {\it transverse} vectors.},
 where the terms on the left-hand-side are twist-3, those on the 
@@
 form that lends itself to straightforward tests of the WW-type relations 
-as presented in this paper. \AP{This assumption holds if renormalization is multiplicative and
+as presented in this paper. This assumption holds if renormalization is multiplicative and
    flavor-independent for the non-local lattice operators. This is
@@
    the present case. For the latest developments we refer the
-   interested reader to Refs.~\cite{Alexandrou:2017dzj,Ishikawa:2017faj,Ji:2017oey,Yoon:2017qzo,Green:2017xeu,Zhang:2017bzy}.}
+   interested reader to Refs.~\cite{Alexandrou:2017dzj,Ishikawa:2017faj,Ji:2017oey,Yoon:2017qzo,Green:2017xeu,Zhang:2017bzy}.
 
@@
 approximations, it is possible to express all SIDIS structure functions
-in terms of the basis functions. \AP{Notice that SIDIS alone is of course not sufficient to determine
+in terms of the basis functions\footnote{Notice that SIDIS alone is of course not sufficient to determine
    the basis functions uniquely because the 8 basis functions appear
@@
    $e^+e^-$ annihilation, which are indispensable for the determination
-   of $f_1^a$ and $D_1^a$).}
-%\AP{Notice that SIDIS alone is of course not sufficient to determine the basis
-%functions uniquely: the 8 basis functions appear in 6 \AP{leading-twist} SIDIS structure functions.
-%It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
-%and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
-%play also important roles.}
-%Notice that SIDIS alone is of course not sufficient to determine the basis
-%functions uniquely: \AP{8 twist-2 TMDs (or 6 ``basis'' TMDs) and 2 twist-2 TMD FFs appear in 15 structure functions (8 twist-2 and 5 sub-leading). 
-%Definitely hadron production in $e^+e^-$ annihilation data is needed, each FF couples with 4 different twist-2 TMD PDFs, and so for each FF we have a case with 5 unknowns accessible in 4 twist-2 observables.
-%It is crucial to take advantage of  Drell--Yan process for TMDs
-%and other processes 
-%play also important roles.}
-
+   of $f_1^a$ and $D_1^a$).}.
 These basis functions allow us to describe, in WW-type approximation,
@@
 on respectively charged pion and hadron production from a proton target.
-\AP{Notice that COMPASS points are lower than theoretical calculation, that may indicate evolution effects~\cite{Aybat:2011ta, Anselmino:2012aa}}.
+Notice that COMPASS points are lower than theoretical calculation, that may indicate evolution effects~\cite{Aybat:2011ta, Anselmino:2012aa}.
 The $P_{hT}$--dependences of the data are well described, which
@@
 
-The $F_{UT}^{\sin(\phi_h+\phi_S)}$ \AP{structure function} of the SIDIS cross section is due 
+The $F_{UT}^{\sin(\phi_h+\phi_S)}$ structure function of the SIDIS cross section is due 
 to the convolution of the transversity distribution $h_1$ and the Collins 
@@
 \cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,Bacchetta:2012ty,
-Radici:2015mwa,Radici:2018iag}. \AP{The first polarized Drell-Yan data were measured by COMPASS~\cite{Aghasyan:2017jop,Parsamyan:2018zju}.}
+Radici:2015mwa,Radici:2018iag}. The first polarized Drell-Yan data were measured by COMPASS~\cite{Aghasyan:2017jop,Parsamyan:2018zju}.
 It describes the distribution of transversely polarized quarks
@@
 The structure function $F_{UU}^{\cos(2\phi_h)}$ arises from a convolution of
-the Collins fragmention function and the \AP{Boer-Mulders} TMD $h_{1}^{\perp q}$ which describes
+the Collins fragmention function and the Boer-Mulders TMD $h_{1}^{\perp q}$ which describes
 the distribution of transversely polarized partons inside an unpolarized
@@
 Boer--Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$, which does not describe
-the data well, \AP{especially for COMPASS one can see that calculation and the data are of opposite signs}. In fact, it is suspected that this observable receives 
+the data well, especially for COMPASS one can see that calculation and the data are of opposite signs. In fact, it is suspected that this observable receives 
 a significant contribution from the Cahn effect \cite{Cahn:1978se}, a 
@@
 \cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,
-Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz}, \AP{these 2\% come after $1/Q$ suppression. Unsuppressed effect at large $x$ at COMPASS would reach 10\% \cite{private}.} 
+Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz}, these 2\% come after $1/Q$ suppression. Unsuppressed effect at large $x$ at COMPASS would reach 10\% \cite{private}.
 On the one hand this is interesting: this observable provides a unique 
@@
 the very first non-zero target single-spin asymmetry measured in SIDIS
-($F_{UL}^{\sin\phi_h}$), and \AP{and the beam-spin asymmetry } ($F_{LU}^{\sin\phi_h}$).
+($F_{UL}^{\sin\phi_h}$), and and the beam-spin asymmetry  ($F_{LU}^{\sin\phi_h}$).
 The WW-type prediction for $F_{UU}^{\cos(\phi_h)}$ tends to overshoot
@@
 
-\bibliography{\BibPath/biblio_ww}
+\providecommand{\href}[2]{#2}\begingroup\raggedright\begin{thebibliography}{100}
+
+\bibitem{Kotzinian:1994dv}
+A.~Kotzinian, \emph{New quark distributions and semiinclusive electroproduction
+  on the polarized nucleons}, {\emph{Nucl. Phys.} {\bf B441} (1995) 234--248},
+  [\href{https://arxiv.org/abs/hep-ph/9412283}{{\tt hep-ph/9412283}}].
+
+\bibitem{Mulders:1995dh}
+P.~J. Mulders and R.~D. Tangerman, \emph{{The complete tree-level result up to
+  order 1/Q for polarized deep-inelastic leptoproduction}},
+  \href{http://dx.doi.org/10.1016/0550-3213(95)00632-X}{\emph{Nucl. Phys.} {\bf
+  B461} (1996) 197--237}, [\href{https://arxiv.org/abs/hep-ph/9510301}{{\tt
+  hep-ph/9510301}}].
+
+\bibitem{Boer:1997nt}
+D.~Boer and P.~J. Mulders, \emph{{Time-reversal odd distribution functions in
+  leptoproduction}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.57.5780}{\emph{Phys. Rev.} {\bf D57}
+  (1998) 5780--5786}, [\href{https://arxiv.org/abs/hep-ph/9711485}{{\tt
+  hep-ph/9711485}}].
+
+\bibitem{Goeke:2005hb}
+K.~Goeke, A.~Metz and M.~Schlegel, \emph{{Parameterization of the quark-quark
+  correlator of a spin-1/2 hadron}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2005.05.037}{\emph{Phys. Lett.}
+  {\bf B618} (2005) 90--96}, [\href{https://arxiv.org/abs/hep-ph/0504130}{{\tt
+  hep-ph/0504130}}].
+
+\bibitem{Bacchetta:2006tn}
+A.~Bacchetta et~al., \emph{{Semi-inclusive deep inelastic scattering at small
+  transverse momentum}}, {\emph{JHEP} {\bf 02} (2007) 093},
+  [\href{https://arxiv.org/abs/hep-ph/0611265}{{\tt hep-ph/0611265}}].
+
+\bibitem{Stock:1994vv}
+F.~Stock et~al., \emph{{The FILTEX / HERMES polarized hydrogen atomic beam
+  source}}, \href{http://dx.doi.org/10.1016/0168-9002(94)90210-0}{\emph{Nucl.
+  Instrum. Meth.} {\bf A343} (1994) 334--342}.
+
+\bibitem{Crabb:1997cy}
+D.~G. Crabb and W.~Meyer, \emph{{Solid polarized targets for nuclear and
+  particle physics experiments}},
+  \href{http://dx.doi.org/10.1146/annurev.nucl.47.1.67}{\emph{Ann. Rev. Nucl.
+  Part. Sci.} {\bf 47} (1997) 67--109}.
+
+\bibitem{Goertz:2002vv}
+S.~Goertz, W.~Meyer and G.~Reicherz, \emph{{Polarized H, D and He-3 targets for
+  particle physics experiments}},
+  \href{http://dx.doi.org/10.1016/S0146-6410(02)00159-X}{\emph{Prog. Part.
+  Nucl. Phys.} {\bf 49} (2002) 403--489}.
+
+\bibitem{Arnold:2008kf}
+S.~Arnold, A.~Metz and M.~Schlegel, \emph{{Dilepton production from polarized
+  hadron hadron collisions}},  \href{https://arxiv.org/abs/0809.2262}{{\tt
+  0809.2262}}.
+
+\bibitem{Metz:2016swz}
+A.~Metz and A.~Vossen, \emph{{Parton Fragmentation Functions}},
+  \href{http://dx.doi.org/10.1016/j.ppnp.2016.08.003}{\emph{Prog. Part. Nucl.
+  Phys.} {\bf 91} (2016) 136--202},
+  [\href{https://arxiv.org/abs/1607.02521}{{\tt 1607.02521}}].
+
+\bibitem{Miller:2007ae}
+G.~A. Miller, \emph{{Densities, Parton Distributions, and Measuring the
+  Non-Spherical Shape of the Nucleon}},
+  \href{http://dx.doi.org/10.1103/PhysRevC.76.065209}{\emph{Phys. Rev.} {\bf
+  C76} (2007) 065209}, [\href{https://arxiv.org/abs/0708.2297}{{\tt
+  0708.2297}}].
+
+\bibitem{Burkardt:2007rv}
+M.~Burkardt, \emph{{Spin-orbit correlations and single-spin asymmetries}},
+  \href{https://arxiv.org/abs/0709.2966}{{\tt 0709.2966}}.
+
+\bibitem{Burkardt:2009rf}
+M.~Burkardt, \emph{{The g(2) Structure Function}},
+  \href{http://dx.doi.org/10.1063/1.3203298}{\emph{AIP Conf.Proc.} {\bf 1155}
+  (2009) 26--34}, [\href{https://arxiv.org/abs/0905.4079}{{\tt 0905.4079}}].
+
+\bibitem{Bacchetta:1999kz}
+A.~Bacchetta, M.~Boglione, A.~Henneman and P.~J. Mulders, \emph{{Bounds on
+  transverse momentum dependent distribution and fragmentation functions}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.85.712}{\emph{Phys. Rev. Lett.}
+  {\bf 85} (2000) 712--715}, [\href{https://arxiv.org/abs/hep-ph/9912490}{{\tt
+  hep-ph/9912490}}].
+
+\bibitem{Wandzura:1977qf}
+S.~Wandzura and F.~Wilczek, \emph{{Sum Rules for Spin Dependent
+  Electroproduction: Test of Relativistic Constituent Quarks}},
+  \href{http://dx.doi.org/10.1016/0370-2693(77)90700-6}{\emph{Phys. Lett.} {\bf
+  B72} (1977) 195}.
+
+\bibitem{Jaffe:1991ra}
+R.~Jaffe and X.~Ji, \emph{{Chiral odd parton distributions and Drell--Yan
+  processes}},
+  \href{http://dx.doi.org/10.1016/0550-3213(92)90110-W}{\emph{Nucl. Phys.} {\bf
+  B375} (1992) 527--560}.
+
+\bibitem{Jaffe:1989xx}
+R.~Jaffe, \emph{{G(2): The Nucleon's Other Spin Dependent Structure Function}},
+  {\emph{Comments Nucl. Part. Phys.} {\bf 19} (1990) 239}.
+
+\bibitem{Balla:1997hf}
+J.~Balla, M.~V. Polyakov and C.~Weiss, \emph{{Nucleon matrix elements of higher
+  twist operators from the instanton vacuum}},
+  \href{http://dx.doi.org/10.1016/S0550-3213(98)00638-5}{\emph{Nucl. Phys.}
+  {\bf B510} (1998) 327--364},
+  [\href{https://arxiv.org/abs/hep-ph/9707515}{{\tt hep-ph/9707515}}].
+
+\bibitem{Dressler:1999hc}
+B.~Dressler and M.~V. Polyakov, \emph{{On the twist-three contribution to h(L)
+  in the instanton vacuum}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.61.097501}{\emph{Phys. Rev.} {\bf
+  D61} (2000) 097501}, [\href{https://arxiv.org/abs/hep-ph/9912376}{{\tt
+  hep-ph/9912376}}].
+
+\bibitem{Gockeler:2000ja}
+M.~Gockeler, R.~Horsley, W.~Kurzinger, H.~Oelrich, D.~Pleiter et~al., \emph{{A
+  Lattice calculation of the nucleon's spin dependent structure function g(2)
+  revisited}}, \href{http://dx.doi.org/10.1103/PhysRevD.63.074506}{\emph{Phys.
+  Rev.} {\bf D63} (2001) 074506},
+  [\href{https://arxiv.org/abs/hep-lat/0011091}{{\tt hep-lat/0011091}}].
+
+\bibitem{Gockeler:2005vw}
+{Gockeler, M. and Horsley, R. and Pleiter, D. and Rakow, Paul E.L. and
+  Sch\"afer, A. and others}, \emph{{Investigation of the second moment of the
+  nucleon's g(1) and g(2) structure functions in two-flavor lattice QCD}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.72.054507}{\emph{Phys. Rev.} {\bf
+  D72} (2005) 054507}, [\href{https://arxiv.org/abs/hep-lat/0506017}{{\tt
+  hep-lat/0506017}}].
+
+\bibitem{Abe:1998wq}
+{\scshape E143} collaboration, K.~Abe et~al., \emph{{Measurements of the proton
+  and deuteron spin structure functions $g_{1}$ and $g_{2}$}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.58.112003}{\emph{Phys. Rev.} {\bf
+  D58} (1998) 112003}, [\href{https://arxiv.org/abs/hep-ph/9802357}{{\tt
+  hep-ph/9802357}}].
+
+\bibitem{Anthony:2002hy}
+{\scshape E155} collaboration, P.~L. Anthony et~al., \emph{{Precision
+  measurement of the proton and deuteron spin structure functions g2 and
+  asymmetries A(2)}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(02)03015-0}{\emph{Phys. Lett.}
+  {\bf B553} (2003) 18--24}, [\href{https://arxiv.org/abs/hep-ex/0204028}{{\tt
+  hep-ex/0204028}}].
+
+\bibitem{Airapetian:2011wu}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Measurement of
+  the virtual-photon asymmetry $A_2$ and the spin-structure function $g_2$ of
+  the proton}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-012-1921-5}{\emph{Eur. Phys. J.}
+  {\bf C72} (2012) 1921}, [\href{https://arxiv.org/abs/1112.5584}{{\tt
+  1112.5584}}].
+
+\bibitem{Kotzinian:1995cz}
+A.~M. Kotzinian and P.~J. Mulders, \emph{{Longitudinal quark polarization in
+  transversely polarized nucleons}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.54.1229}{\emph{Phys. Rev.} {\bf D54}
+  (1996) 1229--1232}, [\href{https://arxiv.org/abs/hep-ph/9511420}{{\tt
+  hep-ph/9511420}}].
+
+\bibitem{Kotzinian:1997wt}
+A.~M. Kotzinian and P.~J. Mulders, \emph{{Probing transverse quark polarization
+  via azimuthal asymmetries in leptoproduction}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(97)00708-9}{\emph{Phys. Lett.}
+  {\bf B406} (1997) 373--380},
+  [\href{https://arxiv.org/abs/hep-ph/9701330}{{\tt hep-ph/9701330}}].
+
+\bibitem{Kotzinian:2006dw}
+A.~Kotzinian, B.~Parsamyan and A.~Prokudin, \emph{{Predictions for double spin
+  asymmetry A(LT) in semi inclusive DIS}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.73.114017}{\emph{Phys. Rev.} {\bf
+  D73} (2006) 114017}, [\href{https://arxiv.org/abs/hep-ph/0603194}{{\tt
+  hep-ph/0603194}}].
+
+\bibitem{Avakian:2007mv}
+H.~Avakian et~al., \emph{{Are there approximate relations among transverse
+  momentum dependent distribution functions?}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.77.014023}{\emph{Phys. Rev.} {\bf
+  D77} (2008) 014023}, [\href{https://arxiv.org/abs/0709.3253}{{\tt
+  0709.3253}}].
+
+\bibitem{Metz:2008ib}
+A.~Metz, P.~Schweitzer and T.~Teckentrup, \emph{{Lorentz invariance relations
+  between parton distributions and the Wandzura-Wilczek approximation}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2009.08.052}{\emph{Phys. Lett.}
+  {\bf B680} (2009) 141--147}, [\href{https://arxiv.org/abs/0810.5212}{{\tt
+  0810.5212}}].
+
+\bibitem{Teckentrup:2009tk}
+T.~Teckentrup, A.~Metz and P.~Schweitzer, \emph{{Lorentz invariance relations
+  and Wandzura-Wilczek approximation}},
+  \href{http://dx.doi.org/10.1142/S0217732309001169}{\emph{Mod. Phys. Lett.}
+  {\bf A24} (2009) 2950--2959}, [\href{https://arxiv.org/abs/0910.2567}{{\tt
+  0910.2567}}].
+
+\bibitem{Tangerman:1994bb}
+R.~Tangerman and P.~Mulders, \emph{{Polarized twist-three distributions g(T)
+  and h(L) and the role of intrinsic transverse momentum}},
+  \href{https://arxiv.org/abs/hep-ph/9408305}{{\tt hep-ph/9408305}}.
+
+\bibitem{Avakian:2015vha}
+H.~Avakian, H.~Matevosyan, B.~Pasquini and P.~Schweitzer, \emph{{Studying the
+  information content of TMDs using Monte Carlo generators}},
+  \href{http://dx.doi.org/10.1088/0954-3899/42/3/034015}{\emph{J. Phys.} {\bf
+  G42} (2015) 034015}.
+
+\bibitem{Mathematica}
+W.~R. Inc., ``Mathematica, {V}ersion 11.3.''
+
+\bibitem{Collins:2002kn}
+J.~C. Collins, \emph{{Leading-twist single-transverse-spin asymmetries:
+  Drell--Yan and deep-inelastic scattering}}, {\emph{Phys. Lett.} {\bf B536}
+  (2002) 43--48}, [\href{https://arxiv.org/abs/hep-ph/0204004}{{\tt
+  hep-ph/0204004}}].
+
+\bibitem{Ralston:1979ys}
+J.~P. Ralston and D.~E. Soper, \emph{{Production of Dimuons from High-Energy
+  Polarized Proton Proton Collisions}},
+  \href{http://dx.doi.org/10.1016/0550-3213(79)90082-8}{\emph{Nucl. Phys.} {\bf
+  B152} (1979) 109}.
+
+\bibitem{Collins:1981uk}
+J.~C. Collins and D.~E. Soper, \emph{{Back-To-Back Jets in QCD}},
+  \href{http://dx.doi.org/10.1016/0550-3213(81)90339-4}{\emph{Nucl. Phys.} {\bf
+  B193} (1981) 381}.
+
+\bibitem{Ji:2004wu}
+X.~Ji, J.-p. Ma and F.~Yuan, \emph{{QCD factorization for semi-inclusive
+  deep-inelastic scattering at low transverse momentum}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.71.034005}{\emph{Phys. Rev.} {\bf
+  D71} (2005) 034005}, [\href{https://arxiv.org/abs/hep-ph/0404183}{{\tt
+  hep-ph/0404183}}].
+
+\bibitem{Ji:2004xq}
+X.~Ji, J.-P. Ma and F.~Yuan, \emph{{QCD factorization for spin-dependent cross
+  sections in DIS and Drell-Yan processes at low transverse momentum}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2004.07.026}{\emph{Phys. Lett.}
+  {\bf B597} (2004) 299--308},
+  [\href{https://arxiv.org/abs/hep-ph/0405085}{{\tt hep-ph/0405085}}].
+
+\bibitem{Collins:2011zzd}
+J.~Collins, \emph{{Foundations of perturbative QCD}}, {\emph{Camb. Monogr.
+  Part. Phys. Nucl. Phys. Cosmol.} {\bf 32} (2011) 1--624}.
+
+\bibitem{Echevarria:2012js}
+M.~G. Echevarr\'ia, A.~Idilbi and I.~Scimemi, \emph{{Soft and Collinear
+  Factorization and Transverse Momentum Dependent Parton Distribution
+  Functions}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2013.09.003}{\emph{Phys. Lett.}
+  {\bf B726} (2013) 795--801}, [\href{https://arxiv.org/abs/1211.1947}{{\tt
+  1211.1947}}].
+
+\bibitem{Aybat:2011zv}
+S.~M. Aybat and T.~C. Rogers, \emph{{TMD Parton Distribution and Fragmentation
+  Functions with QCD Evolution}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.83.114042}{\emph{Phys. Rev.} {\bf
+  D83} (2011) 114042}, [\href{https://arxiv.org/abs/1101.5057}{{\tt
+  1101.5057}}].
+
+\bibitem{Aybat:2011ge}
+S.~M. Aybat, J.~C. Collins, J.-W. Qiu and T.~C. Rogers, \emph{{The QCD
+  Evolution of the Sivers Function}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.85.034043}{\emph{Phys. Rev.} {\bf
+  D85} (2012) 034043}, [\href{https://arxiv.org/abs/1110.6428}{{\tt
+  1110.6428}}].
+
+\bibitem{Echevarria:2014xaa}
+M.~G. Echevarria, A.~Idilbi, Z.-B. Kang and I.~Vitev, \emph{{QCD Evolution of
+  the Sivers Asymmetry}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.89.074013}{\emph{Phys. Rev.} {\bf
+  D89} (2014) 074013}, [\href{https://arxiv.org/abs/1401.5078}{{\tt
+  1401.5078}}].
+
+\bibitem{Ma:2013aca}
+J.~P. Ma and G.~P. Zhang, \emph{{QCD Corrections of All Structure Functions in
+  Transverse Momentum Dependent Factorization for Drell-Yan Processes}},
+  \href{http://dx.doi.org/10.1007/JHEP02(2014)100}{\emph{JHEP} {\bf 02} (2014)
+  100}, [\href{https://arxiv.org/abs/1308.2044}{{\tt 1308.2044}}].
+
+\bibitem{Aybat:2011ta}
+S.~M. Aybat, A.~Prokudin and T.~C. Rogers, \emph{{Calculation of TMD Evolution
+  for Transverse Single Spin Asymmetry Measurements}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.108.242003}{\emph{Phys. Rev.
+  Lett.} {\bf 108} (2012) 242003}, [\href{https://arxiv.org/abs/1112.4423}{{\tt
+  1112.4423}}].
+
+\bibitem{Kang:2015msa}
+Z.-B. Kang, A.~Prokudin, P.~Sun and F.~Yuan, \emph{{Extraction of Quark
+  Transversity Distribution and Collins Fragmentation Functions with QCD
+  Evolution}}, \href{http://dx.doi.org/10.1103/PhysRevD.93.014009}{\emph{Phys.
+  Rev.} {\bf D93} (2016) 014009}, [\href{https://arxiv.org/abs/1505.05589}{{\tt
+  1505.05589}}].
+
+\bibitem{Metz:2004je}
+A.~Metz and M.~Schlegel, \emph{{Twist three single spin asymmetries in
+  semiinclusive deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1140/epja/i2004-10050-8}{\emph{Eur. Phys. J.} {\bf
+  A22} (2004) 489--494}, [\href{https://arxiv.org/abs/hep-ph/0403182}{{\tt
+  hep-ph/0403182}}].
+
+\bibitem{Gamberg:2006ru}
+L.~P. Gamberg, D.~S. Hwang, A.~Metz and M.~Schlegel, \emph{{Light-cone
+  divergence in twist-3 correlation functions}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2006.07.005}{\emph{Phys. Lett.}
+  {\bf B639} (2006) 508--512},
+  [\href{https://arxiv.org/abs/hep-ph/0604022}{{\tt hep-ph/0604022}}].
+
+\bibitem{Chen:2016hgw}
+A.~P. Chen and J.~P. Ma, \emph{{Light-Cone Singularities and
+  Transverse-Momentum-Dependent Factorization at Twist-3}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2017.03.015}{\emph{Phys. Lett.}
+  {\bf B768} (2017) 380--386}, [\href{https://arxiv.org/abs/1610.08634}{{\tt
+  1610.08634}}].
+
+\bibitem{Efremov:2002qh}
+A.~Efremov and P.~Schweitzer, \emph{{The Chirally odd twist 3 distribution
+  e(a)(x)}}, {\emph{JHEP} {\bf 0308} (2003) 006},
+  [\href{https://arxiv.org/abs/hep-ph/0212044}{{\tt hep-ph/0212044}}].
+
+\bibitem{Jaffe:1996zw}
+R.~L. Jaffe, \emph{{Spin, twist and hadron structure in deep inelastic
+  processes}},  \href{https://arxiv.org/abs/hep-ph/9602236}{{\tt
+  hep-ph/9602236}}.
+
+\bibitem{Kanazawa:2015ajw}
+K.~Kanazawa, Y.~Koike, A.~Metz, D.~Pitonyak and M.~Schlegel, \emph{{Operator
+  Constraints for Twist-3 Functions and Lorentz Invariance Properties of
+  Twist-3 Observables}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.93.054024}{\emph{Phys. Rev.} {\bf
+  D93} (2016) 054024}, [\href{https://arxiv.org/abs/1512.07233}{{\tt
+  1512.07233}}].
+
+\bibitem{Shuryak:1981ff}
+E.~V. Shuryak, \emph{{The Role of Instantons in Quantum Chromodynamics. 1.
+  Physical Vacuum}},
+  \href{http://dx.doi.org/10.1016/0550-3213(82)90478-3}{\emph{Nucl. Phys.} {\bf
+  B203} (1982) 93}.
+
+\bibitem{Diakonov:1983hh}
+D.~Diakonov and V.~Y. Petrov, \emph{{Instanton Based Vacuum from Feynman
+  Variational Principle}},
+  \href{http://dx.doi.org/10.1016/0550-3213(84)90432-2}{\emph{Nucl. Phys.} {\bf
+  B245} (1984) 259}.
+
+\bibitem{Diakonov:1995qy}
+D.~Diakonov, M.~V. Polyakov and C.~Weiss, \emph{{Hadronic matrix elements of
+  gluon operators in the instanton vacuum}},
+  \href{http://dx.doi.org/10.1016/0550-3213(95)00675-3}{\emph{Nucl. Phys.} {\bf
+  B461} (1996) 539--580}, [\href{https://arxiv.org/abs/hep-ph/9510232}{{\tt
+  hep-ph/9510232}}].
+
+\bibitem{Adams:1994id}
+{\scshape Spin Muon (SMC)} collaboration, D.~Adams et~al., \emph{{Spin
+  asymmetry in muon - proton deep inelastic scattering on a transversely
+  polarized target}},
+  \href{http://dx.doi.org/10.1016/0370-2693(94)00968-6}{\emph{Phys. Lett.} {\bf
+  B336} (1994) 125--130}, [\href{https://arxiv.org/abs/hep-ex/9408001}{{\tt
+  hep-ex/9408001}}].
+
+\bibitem{Accardi:2009au}
+A.~Accardi, A.~Bacchetta, W.~Melnitchouk and M.~Schlegel, \emph{{What can break
+  the Wandzura--Wilczek relation?}},
+  \href{http://dx.doi.org/10.1088/1126-6708/2009/11/093}{\emph{JHEP} {\bf 11}
+  (2009) 093}, [\href{https://arxiv.org/abs/0907.2942}{{\tt 0907.2942}}].
+
+\bibitem{Gluck:1998xa}
+M.~Gluck, E.~Reya and A.~Vogt, \emph{{Dynamical parton distributions
+  revisited}}, \href{http://dx.doi.org/10.1007/s100520050289}{\emph{Eur. Phys.
+  J.} {\bf C5} (1998) 461--470},
+  [\href{https://arxiv.org/abs/hep-ph/9806404}{{\tt hep-ph/9806404}}].
+
+\bibitem{Efremov:2006qm}
+A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{Collins effect in
+  semi-inclusive deeply inelastic scattering and in $e^{+} e^{-}$
+  annihilation}, {\emph{Phys. Rev.} {\bf D73} (2006) 094025}.
+
+\bibitem{Anselmino:2007fs}
+M.~Anselmino et~al., \emph{{Transversity and Collins functions from SIDIS and
+  $e^{+} e^{-}$ data}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.75.054032}{\emph{Phys. Rev.} {\bf
+  D75} (2007) 054032}, [\href{https://arxiv.org/abs/hep-ph/0701006}{{\tt
+  hep-ph/0701006}}].
+
+\bibitem{Anselmino:2008jk}
+M.~Anselmino et~al., \emph{{Update on transversity and Collins functions from
+  SIDIS and $e^{+} e^{-}$ data}},
+  \href{http://dx.doi.org/10.1016/j.nuclphysbps.2009.03.117}{\emph{Nucl. Phys.
+  Proc. Suppl.} {\bf 191} (2009) 98--107},
+  [\href{https://arxiv.org/abs/0812.4366}{{\tt 0812.4366}}].
+
+\bibitem{Koike:2008du}
+Y.~Koike, K.~Tanaka and S.~Yoshida, \emph{{Drell-Yan double-spin asymmetry
+  A(LT) in polarized p anti-p collisions: Wandzura-Wilczek contribution}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2008.08.049}{\emph{Phys. Lett.}
+  {\bf B668} (2008) 286--292}, [\href{https://arxiv.org/abs/0805.2289}{{\tt
+  0805.2289}}].
+
+\bibitem{Hagler:2009mb}
+{H\"agler, Ph. and Musch, B. U. and Negele, J. W. and Sch\"afer, A.},
+  \emph{{Intrinsic quark transverse momentum in the nucleon from lattice QCD}},
+  \href{http://dx.doi.org/10.1209/0295-5075/88/61001}{\emph{Europhys. Lett.}
+  {\bf 88} (2009) 61001}, [\href{https://arxiv.org/abs/0908.1283}{{\tt
+  0908.1283}}].
+
+\bibitem{Musch:2010ka}
+{Musch, Bernhard U. and H\"agler, Philipp and Negele, John W. and Sch\"afer,
+  Andreas}, \emph{{Exploring quark transverse momentum distributions with
+  lattice QCD}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.83.094507}{\emph{Phys. Rev.} {\bf
+  D83} (2011) 094507}, [\href{https://arxiv.org/abs/1011.1213}{{\tt
+  1011.1213}}].
+
+\bibitem{Yoon:2017qzo}
+B.~Yoon, M.~Engelhardt, R.~Gupta, T.~Bhattacharya, J.~R. Green, B.~U. Musch
+  et~al., \emph{{Nucleon Transverse Momentum-dependent Parton Distributions in
+  Lattice QCD: Renormalization Patterns and Discretization Effects}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.96.094508}{\emph{Phys. Rev.} {\bf
+  D96} (2017) 094508}, [\href{https://arxiv.org/abs/1706.03406}{{\tt
+  1706.03406}}].
+
+\bibitem{Engelhardt:2015xja}
+{Engelhardt, M. and H\"agler, P. and Musch, B. and Negele, J. and Sch\"afer,
+  A.}, \emph{{Lattice QCD study of the Boer-Mulders effect in a pion}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.93.054501}{\emph{Phys. Rev.} {\bf
+  D93} (2016) 054501}, [\href{https://arxiv.org/abs/1506.07826}{{\tt
+  1506.07826}}].
+
+\bibitem{Ji:2014hxa}
+X.~Ji, P.~Sun, X.~Xiong and F.~Yuan, \emph{{Soft factor subtraction and
+  transverse momentum dependent parton distributions on the lattice}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.91.074009}{\emph{Phys. Rev.} {\bf
+  D91} (2015) 074009}, [\href{https://arxiv.org/abs/1405.7640}{{\tt
+  1405.7640}}].
+
+\bibitem{Musch:2011er}
+{Musch, B. U. and H\"agler, Ph. and Engelhardt, M. and Negele, J. W. and
+  Sch\"afer, A.}, \emph{{Sivers and Boer-Mulders observables from lattice
+  QCD}}, \href{http://dx.doi.org/10.1103/PhysRevD.85.094510}{\emph{Phys. Rev.}
+  {\bf D85} (2012) 094510}, [\href{https://arxiv.org/abs/1111.4249}{{\tt
+  1111.4249}}].
+
+\bibitem{Alexandrou:2017dzj}
+C.~Alexandrou, S.~Bacchio, K.~Cichy, M.~Constantinou, K.~Hadjiyiannakou,
+  K.~Jansen et~al., \emph{{Computation of parton distributions from the
+  quasi-PDF approach at the physical point}},
+  \href{http://dx.doi.org/10.1051/epjconf/201817514008}{\emph{EPJ Web Conf.}
+  {\bf 175} (2018) 14008}, [\href{https://arxiv.org/abs/1710.06408}{{\tt
+  1710.06408}}].
+
+\bibitem{Ishikawa:2017faj}
+T.~Ishikawa, Y.-Q. Ma, J.-W. Qiu and S.~Yoshida, \emph{{Renormalizability of
+  quasiparton distribution functions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.96.094019}{\emph{Phys. Rev.} {\bf
+  D96} (2017) 094019}, [\href{https://arxiv.org/abs/1707.03107}{{\tt
+  1707.03107}}].
+
+\bibitem{Ji:2017oey}
+X.~Ji, J.-H. Zhang and Y.~Zhao, \emph{{Renormalization in Large Momentum
+  Effective Theory of Parton Physics}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.120.112001}{\emph{Phys. Rev.
+  Lett.} {\bf 120} (2018) 112001},
+  [\href{https://arxiv.org/abs/1706.08962}{{\tt 1706.08962}}].
+
+\bibitem{Green:2017xeu}
+J.~Green, K.~Jansen and F.~Steffens, \emph{{Nonperturbative renormalization of
+  nonlocal quark bilinears for quasi-PDFs on the lattice using an auxiliary
+  field}}, \href{http://dx.doi.org/10.1103/PhysRevLett.121.022004}{\emph{Phys.
+  Rev. Lett.} {\bf 121} (2018) 022004},
+  [\href{https://arxiv.org/abs/1707.07152}{{\tt 1707.07152}}].
+
+\bibitem{Zhang:2017bzy}
+J.-H. Zhang, J.-W. Chen, X.~Ji, L.~Jin and H.-W. Lin, \emph{{Pion Distribution
+  Amplitude from Lattice QCD}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.95.094514}{\emph{Phys. Rev.} {\bf
+  D95} (2017) 094514}, [\href{https://arxiv.org/abs/1702.00008}{{\tt
+  1702.00008}}].
+
+\bibitem{Hagler:2003is}
+{\scshape LHPC} collaboration, LHPC et~al., \emph{{Transverse structure of
+  nucleon parton distributions from lattice QCD}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.93.112001}{\emph{Phys. Rev.
+  Lett.} {\bf 93} (2004) 112001},
+  [\href{https://arxiv.org/abs/hep-lat/0312014}{{\tt hep-lat/0312014}}].
+
+\bibitem{Hagler:2007xi}
+{\scshape LHPC Collaborations} collaboration, {H\"agler, Ph. and others},
+  \emph{{Nucleon Generalized Parton Distributions from Full Lattice QCD}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.77.094502}{\emph{Phys. Rev.} {\bf
+  D77} (2008) 094502}, [\href{https://arxiv.org/abs/0705.4295}{{\tt
+  0705.4295}}].
+
+\bibitem{Gockeler:2005cj}
+{\scshape QCDSF} collaboration, M.~Gockeler et~al., \emph{{Quark helicity flip
+  generalized parton distributions from two-flavor lattice QCD}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2005.09.002}{\emph{Phys. Lett.}
+  {\bf B627} (2005) 113--123},
+  [\href{https://arxiv.org/abs/hep-lat/0507001}{{\tt hep-lat/0507001}}].
+
+\bibitem{Burkardt:2001iy}
+M.~Burkardt and Y.~Koike, \emph{{Violation of sum rules for twist three parton
+  distributions in QCD}},
+  \href{http://dx.doi.org/10.1016/S0550-3213(02)00263-8}{\emph{Nucl. Phys.}
+  {\bf B632} (2002) 311--329},
+  [\href{https://arxiv.org/abs/hep-ph/0111343}{{\tt hep-ph/0111343}}].
+
+\bibitem{Bass:2003vp}
+S.~D. Bass, \emph{{Fixed poles, polarized glue and nucleon spin structure}},
+  {\emph{Acta Phys. Polon.} {\bf B34} (2003) 5893--5926},
+  [\href{https://arxiv.org/abs/hep-ph/0311174}{{\tt hep-ph/0311174}}].
+
+\bibitem{Stratmann:1993aw}
+M.~Stratmann, \emph{{Bag model predictions for polarized structure functions
+  and their Q**2 evolutions}},
+  \href{http://dx.doi.org/10.1007/BF01558408}{\emph{Z. Phys.} {\bf C60} (1993)
+  763--772}.
+
+\bibitem{Signal:1996ct}
+A.~Signal, \emph{{Calculations of higher twist distribution functions in the
+  MIT bag model}},
+  \href{http://dx.doi.org/10.1016/S0550-3213(97)00231-9}{\emph{Nucl. Phys.}
+  {\bf B497} (1997) 415--434},
+  [\href{https://arxiv.org/abs/hep-ph/9610480}{{\tt hep-ph/9610480}}].
+
+\bibitem{Avakian:2010br}
+H.~Avakian, A.~Efremov, P.~Schweitzer and F.~Yuan, \emph{{The transverse
+  momentum dependent distribution functions in the bag model}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.81.074035}{\emph{Phys. Rev.} {\bf
+  D81} (2010) 074035}, [\href{https://arxiv.org/abs/1001.5467}{{\tt
+  1001.5467}}].
+
+\bibitem{Jakob:1997wg}
+R.~Jakob, P.~Mulders and J.~Rodrigues, \emph{{Modeling quark distribution and
+  fragmentation functions}},
+  \href{http://dx.doi.org/10.1016/S0375-9474(97)00588-5}{\emph{Nucl. Phys.}
+  {\bf A626} (1997) 937--965},
+  [\href{https://arxiv.org/abs/hep-ph/9704335}{{\tt hep-ph/9704335}}].
+
+\bibitem{Wakamatsu:2000ex}
+M.~Wakamatsu, \emph{{Polarized structure functions g(2)(x) in the chiral quark
+  soliton model}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(00)00790-5}{\emph{Phys. Lett.}
+  {\bf B487} (2000) 118--124},
+  [\href{https://arxiv.org/abs/hep-ph/0006212}{{\tt hep-ph/0006212}}].
+
+\bibitem{Pasquini:2008ax}
+B.~Pasquini, S.~Cazzaniga and S.~Boffi, \emph{{Transverse momentum dependent
+  parton distributions in a light-cone quark model}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.78.034025}{\emph{Phys. Rev.} {\bf
+  D78} (2008) 034025}, [\href{https://arxiv.org/abs/0806.2298}{{\tt
+  0806.2298}}].
+
+\bibitem{Lorce:2011dv}
+C.~Lorc\'e, B.~Pasquini and M.~Vanderhaeghen, \emph{{Unified framework for
+  generalized and transverse-momentum dependent parton distributions within a
+  3Q light-cone picture of the nucleon}},
+  \href{http://dx.doi.org/10.1007/JHEP05(2011)041}{\emph{JHEP} {\bf 1105}
+  (2011) 041}, [\href{https://arxiv.org/abs/1102.4704}{{\tt 1102.4704}}].
+
+\bibitem{Kundu:2001pk}
+R.~Kundu and A.~Metz, \emph{{Higher twist and transverse momentum dependent
+  parton distributions: A Light front Hamiltonian approach}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.65.014009}{\emph{Phys. Rev.} {\bf
+  D65} (2002) 014009}, [\href{https://arxiv.org/abs/hep-ph/0107073}{{\tt
+  hep-ph/0107073}}].
+
+\bibitem{Schlegel:2004rg}
+M.~Schlegel and A.~Metz, \emph{{On the validity of Lorentz invariance relations
+  between parton distributions}},
+  \href{https://arxiv.org/abs/hep-ph/0406289}{{\tt hep-ph/0406289}}.
+
+\bibitem{Goeke:2003az}
+K.~Goeke, A.~Metz, P.~Pobylitsa and M.~Polyakov, \emph{{Lorentz invariance
+  relations among parton distributions revisited}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(03)00870-0}{\emph{Phys. Lett.}
+  {\bf B567} (2003) 27--30}, [\href{https://arxiv.org/abs/hep-ph/0302028}{{\tt
+  hep-ph/0302028}}].
+
+\bibitem{Lorce:2014hxa}
+C.~Lorc\'e, B.~Pasquini and P.~Schweitzer, \emph{{Unpolarized transverse
+  momentum dependent parton distribution functions beyond leading twist in
+  quark models}}, \href{http://dx.doi.org/10.1007/JHEP01(2015)103}{\emph{JHEP}
+  {\bf 01} (2015) 103}, [\href{https://arxiv.org/abs/1411.2550}{{\tt
+  1411.2550}}].
+
+\bibitem{Lorce:2016ugb}
+C.~Lorc\'e, B.~Pasquini and P.~Schweitzer, \emph{{Transverse pion structure
+  beyond leading twist in constituent models}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-016-4257-8}{\emph{Eur. Phys. J.}
+  {\bf C76} (2016) 415}, [\href{https://arxiv.org/abs/1605.00815}{{\tt
+  1605.00815}}].
+
+\bibitem{Zavada:1996kp}
+P.~Zavada, \emph{{The Structure functions and parton momenta distribution in
+  the hadron rest system}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.55.4290}{\emph{Phys. Rev.} {\bf D55}
+  (1997) 4290--4299}, [\href{https://arxiv.org/abs/hep-ph/9609372}{{\tt
+  hep-ph/9609372}}].
+
+\bibitem{Efremov:2010mt}
+A.~V. Efremov, P.~Schweitzer, O.~V. Teryaev and P.~Zavada, \emph{{The relation
+  between TMDs and PDFs in the covariant parton model approach}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.83.054025}{\emph{Phys. Rev.} {\bf
+  D83} (2011) 054025}, [\href{https://arxiv.org/abs/1012.5296}{{\tt
+  1012.5296}}].
+
+\bibitem{Efremov:2009ze}
+A.~V. Efremov, P.~Schweitzer, O.~V. Teryaev and P.~Zavada, \emph{{Transverse
+  momentum dependent distribution functions in a covariant parton model
+  approach with quark orbital motion}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.80.014021}{\emph{Phys. Rev.} {\bf
+  D80} (2009) 014021}, [\href{https://arxiv.org/abs/0903.3490}{{\tt
+  0903.3490}}].
+
+\bibitem{Schweitzer:2003uy}
+P.~Schweitzer, \emph{{The Chirally odd twist three distribution function
+  e**alpha(x) in the chiral quark soliton model}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.67.114010}{\emph{Phys. Rev.} {\bf
+  D67} (2003) 114010}, [\href{https://arxiv.org/abs/hep-ph/0303011}{{\tt
+  hep-ph/0303011}}].
+
+\bibitem{Ohnishi:2003mf}
+Y.~Ohnishi and M.~Wakamatsu, \emph{{pi N sigma term and chiral odd twist three
+  distribution function e(x) of the nucleon in the chiral quark soliton
+  model}}, \href{http://dx.doi.org/10.1103/PhysRevD.69.114002}{\emph{Phys.
+  Rev.} {\bf D69} (2004) 114002},
+  [\href{https://arxiv.org/abs/hep-ph/0312044}{{\tt hep-ph/0312044}}].
+
+\bibitem{Cebulla:2007ej}
+C.~Cebulla, J.~Ossmann, P.~Schweitzer and D.~Urbano, \emph{{The Twist-3 parton
+  distribution function e**a(x) in large-N(c) chiral theory}}, {\emph{Acta
+  Phys. Polon.} {\bf B39} (2008) 609--640},
+  [\href{https://arxiv.org/abs/0710.3103}{{\tt 0710.3103}}].
+
+\bibitem{Meissner:2007rx}
+S.~Meissner, A.~Metz and K.~Goeke, \emph{{Relations between generalized and
+  transverse momentum dependent parton distributions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.76.034002}{\emph{Phys. Rev.} {\bf
+  D76} (2007) 034002}, [\href{https://arxiv.org/abs/hep-ph/0703176}{{\tt
+  hep-ph/0703176}}].
+
+\bibitem{Mukherjee:2009uy}
+A.~Mukherjee, \emph{{Twist Three Distribution e(x): Sum Rules and Equation of
+  Motion Relations}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2010.03.023}{\emph{Phys. Lett.}
+  {\bf B687} (2010) 180--183}, [\href{https://arxiv.org/abs/0912.1446}{{\tt
+  0912.1446}}].
+
+\bibitem{Harindranath:1997qn}
+A.~Harindranath and W.-M. Zhang, \emph{{Examination of Wandzura-Wilczek
+  relation for g2 (x, q**2) in pQCD}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(97)00771-5}{\emph{Phys. Lett.}
+  {\bf B408} (1997) 347--356},
+  [\href{https://arxiv.org/abs/hep-ph/9706419}{{\tt hep-ph/9706419}}].
+
+\bibitem{Boer:2003cm}
+D.~Boer, P.~J. Mulders and F.~Pijlman, \emph{{Universality of T-odd effects in
+  single spin and azimuthal asymmetries}},
+  \href{http://dx.doi.org/10.1016/S0550-3213(03)00527-3}{\emph{Nucl. Phys.}
+  {\bf B667} (2003) 201--241},
+  [\href{https://arxiv.org/abs/hep-ph/0303034}{{\tt hep-ph/0303034}}].
+
+\bibitem{Ji:2006ub}
+X.~Ji, J.-W. Qiu, W.~Vogelsang and F.~Yuan, \emph{{A unified picture for single
+  transverse-spin asymmetries in hard processes}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.97.082002}{\emph{Phys. Rev.
+  Lett.} {\bf 97} (2006) 082002},
+  [\href{https://arxiv.org/abs/hep-ph/0602239}{{\tt hep-ph/0602239}}].
+
+\bibitem{Anselmino:2005nn}
+M.~Anselmino et~al., \emph{{The role of Cahn and Sivers effects in deep
+  inelastic scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.71.074006}{\emph{Phys. Rev.} {\bf
+  D71} (2005) 074006}, [\href{https://arxiv.org/abs/hep-ph/0501196}{{\tt
+  hep-ph/0501196}}].
+
+\bibitem{Collins:2005ie}
+J.~C. Collins et~al., \emph{Sivers effect in semi-inclusive deeply inelastic
+  scattering}, {\emph{Phys. Rev.} {\bf D73} (2006) 014021},
+  [\href{https://arxiv.org/abs/hep-ph/0509076}{{\tt hep-ph/0509076}}].
+
+\bibitem{D'Alesio:2007jt}
+U.~D'Alesio and F.~Murgia, \emph{{Azimuthal and Single Spin Asymmetries in Hard
+  Scattering Processes}},
+  \href{http://dx.doi.org/10.1016/j.ppnp.2008.01.001}{\emph{Prog. Part. Nucl.
+  Phys. 61} {\bf 2008} (2008) 394--454},
+  [\href{https://arxiv.org/abs/0712.4328}{{\tt 0712.4328}}].
+
+\bibitem{Schweitzer:2010tt}
+P.~Schweitzer, T.~Teckentrup and A.~Metz, \emph{{Intrinsic transverse parton
+  momenta in deeply inelastic reactions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.81.094019}{\emph{Phys. Rev.} {\bf
+  D81} (2010) 094019}, [\href{https://arxiv.org/abs/1003.2190}{{\tt
+  1003.2190}}].
+
+\bibitem{Signori:2013mda}
+A.~Signori, A.~Bacchetta, M.~Radici and G.~Schnell, \emph{{Investigations into
+  the flavor dependence of partonic transverse momentum}},
+  \href{http://dx.doi.org/10.1007/JHEP11(2013)194}{\emph{JHEP} {\bf 11} (2013)
+  194}, [\href{https://arxiv.org/abs/1309.3507}{{\tt 1309.3507}}].
+
+\bibitem{Anselmino:2013lza}
+M.~Anselmino, M.~Boglione, J.~O. Gonzalez~Hernandez, S.~Melis and A.~Prokudin,
+  \emph{{Unpolarised Transverse Momentum Dependent Distribution and
+  Fragmentation Functions from SIDIS Multiplicities}},
+  \href{http://dx.doi.org/10.1007/JHEP04(2014)005}{\emph{JHEP} {\bf 04} (2014)
+  005}, [\href{https://arxiv.org/abs/1312.6261}{{\tt 1312.6261}}].
+
+\bibitem{Bacchetta:2008xw}
+A.~Bacchetta, D.~Boer, M.~Diehl and P.~J. Mulders, \emph{{Matches and
+  mismatches in the descriptions of semi- inclusive processes at low and high
+  transverse momentum}},
+  \href{http://dx.doi.org/10.1088/1126-6708/2008/08/023}{\emph{JHEP} {\bf 08}
+  (2008) 023}, [\href{https://arxiv.org/abs/0803.0227}{{\tt 0803.0227}}].
+
+\bibitem{Landry:2002ix}
+F.~Landry, R.~Brock, P.~M. Nadolsky and C.~Yuan, \emph{{Tevatron Run-1 $Z$
+  boson data and Collins-Soper-Sterman resummation formalism}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.67.073016}{\emph{Phys. Rev.} {\bf
+  D67} (2003) 073016}, [\href{https://arxiv.org/abs/hep-ph/0212159}{{\tt
+  hep-ph/0212159}}].
+
+\bibitem{Martin:2009iq}
+A.~D. Martin, W.~J. Stirling, R.~S. Thorne and G.~Watt, \emph{{Parton
+  distributions for the LHC}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-009-1072-5}{\emph{Eur. Phys. J.}
+  {\bf C63} (2009) 189--285}, [\href{https://arxiv.org/abs/0901.0002}{{\tt
+  0901.0002}}].
+
+\bibitem{deFlorian:2007aj}
+D.~de~Florian, R.~Sassot and M.~Stratmann, \emph{{Global analysis of
+  fragmentation functions for pions and kaons and their uncertainties}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.75.114010}{\emph{Phys. Rev.} {\bf
+  D75} (2007) 114010}, [\href{https://arxiv.org/abs/hep-ph/0703242}{{\tt
+  hep-ph/0703242}}].
+
+\bibitem{Schweitzer:2012hh}
+P.~Schweitzer, M.~Strikman and C.~Weiss, \emph{{Intrinsic transverse momentum
+  and parton correlations from dynamical chiral symmetry breaking}},
+  \href{http://dx.doi.org/10.1007/JHEP01(2013)163}{\emph{JHEP} {\bf 01} (2013)
+  163}, [\href{https://arxiv.org/abs/1210.1267}{{\tt 1210.1267}}].
+
+\bibitem{Collins:2016hqq}
+J.~Collins, L.~Gamberg, A.~Prokudin, T.~C. Rogers, N.~Sato and B.~Wang,
+  \emph{{Relating Transverse Momentum Dependent and Collinear Factorization
+  Theorems in a Generalized Formalism}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.94.034014}{\emph{Phys. Rev.} {\bf
+  D94} (2016) 034014}, [\href{https://arxiv.org/abs/1605.00671}{{\tt
+  1605.00671}}].
+
+\bibitem{Osipenko:2008aa}
+{\scshape CLAS} collaboration, M.~Osipenko et~al., \emph{{Measurement of
+  unpolarized semi-inclusive pi+ electroproduction off the proton}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.80.032004}{\emph{Phys. Rev.} {\bf
+  D80} (2009) 032004}, [\href{https://arxiv.org/abs/0809.1153}{{\tt
+  0809.1153}}].
+
+\bibitem{Airapetian:2012ki}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Multiplicities of
+  charged pions and kaons from semi-inclusive deep-inelastic scattering by the
+  proton and the deuteron}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.87.074029}{\emph{Phys. Rev.} {\bf
+  D87} (2013) 074029}, [\href{https://arxiv.org/abs/1212.5407}{{\tt
+  1212.5407}}].
+
+\bibitem{Aghasyan:2017ctw}
+{\scshape COMPASS} collaboration, M.~Aghasyan et~al.,
+  \emph{{Transverse-momentum-dependent Multiplicities of Charged Hadrons in
+  Muon-Deuteron Deep Inelastic Scattering}},
+  \href{https://arxiv.org/abs/1709.07374}{{\tt 1709.07374}}.
+
+\bibitem{Bacchetta:2017gcc}
+A.~Bacchetta, F.~Delcarro, C.~Pisano, M.~Radici and A.~Signori,
+  \emph{{Extraction of partonic transverse momentum distributions from
+  semi-inclusive deep-inelastic scattering, Drell-Yan and Z-boson production}},
+  \href{http://dx.doi.org/10.1007/JHEP06(2017)081}{\emph{JHEP} {\bf 06} (2017)
+  081}, [\href{https://arxiv.org/abs/1703.10157}{{\tt 1703.10157}}].
+
+\bibitem{Avakian:2010ae}
+{\scshape CLAS} collaboration, H.~Avakian et~al., \emph{{Measurement of Single
+  and Double Spin Asymmetries in Deep Inelastic Pion Electroproduction with a
+  Longitudinally Polarized Target}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.105.262002}{\emph{Phys. Rev.
+  Lett.} {\bf 105} (2010) 262002}, [\href{https://arxiv.org/abs/1003.4549}{{\tt
+  1003.4549}}].
+
+\bibitem{Anselmino:2011gs}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia and A.~Prokudin,
+  \emph{{Sivers Distribution Functions and the Latest SIDIS Data}},  in
+  \emph{{19th International Workshop on Deep-Inelastic Scattering and Related
+  Subjects (DIS 2011) Newport News, Virginia, April 11-15, 2011}}, 2011.
+\newblock \href{https://arxiv.org/abs/1107.4446}{{\tt 1107.4446}}.
+
+\bibitem{Airapetian:2009ae}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Observation of
+  the Naive-T-odd Sivers Effect in Deep-Inelastic Scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.103.152002}{\emph{Phys. Rev.
+  Lett.} {\bf 103} (2009) 152002}, [\href{https://arxiv.org/abs/0906.3918}{{\tt
+  0906.3918}}].
+
+\bibitem{Adolph:2012sp}
+{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{II Experimental
+  investigation of transverse spin asymmetries in $\mu$-p SIDIS processes:
+  Sivers asymmetries}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2012.09.056}{\emph{Phys. Lett.}
+  {\bf B717} (2012) 383--389}, [\href{https://arxiv.org/abs/1205.5122}{{\tt
+  1205.5122}}].
+
+\bibitem{Sivers:1989cc}
+D.~W. Sivers, \emph{Single spin production asymmetries from the hard scattering
+  of point-like constituents}, {\emph{Phys. Rev.} {\bf D41} (1990) 83}.
+
+\bibitem{Anselmino:2010bs}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia and A.~Prokudin,
+  \emph{{New insight on the Sivers transverse momentum dependent distribution
+  function}}, \href{http://dx.doi.org/10.1088/1742-6596/295/1/012062}{\emph{J.
+  Phys. Conf. Ser.} {\bf 295} (2011) 012062},
+  [\href{https://arxiv.org/abs/1012.3565}{{\tt 1012.3565}}].
+
+\bibitem{Anselmino:2005ea}
+M.~Anselmino et~al., \emph{Extracting the sivers function from polarized sidis
+  data and making predictions}, {\emph{Phys. Rev.} {\bf D72} (2005) 094007},
+  [\href{https://arxiv.org/abs/hep-ph/0507181}{{\tt hep-ph/0507181}}].
+
+\bibitem{Anselmino:2005an}
+M.~Anselmino et~al., \emph{{Comparing extractions of Sivers functions}},
+  \href{https://arxiv.org/abs/hep-ph/0511017}{{\tt hep-ph/0511017}}.
+
+\bibitem{Vogelsang:2005cs}
+W.~Vogelsang and F.~Yuan, \emph{Single-transverse spin asymmetries: From dis to
+  hadronic collisions}, {\emph{Phys. Rev.} {\bf D72} (2005) 054028}.
+
+\bibitem{Anselmino:2008sga}
+M.~Anselmino et~al., \emph{{Sivers Effect for Pion and Kaon Production in Semi-
+  Inclusive Deep Inelastic Scattering}},
+  \href{http://dx.doi.org/10.1140/epja/i2008-10697-y}{\emph{Eur. Phys. J.} {\bf
+  A39} (2009) 89--100}, [\href{https://arxiv.org/abs/0805.2677}{{\tt
+  0805.2677}}].
+
+\bibitem{Bacchetta:2011gx}
+A.~Bacchetta and M.~Radici, \emph{{Constraining quark angular momentum through
+  semi-inclusive measurements}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.107.212001}{\emph{Phys. Rev.
+  Lett.} {\bf 107} (2011) 212001}, [\href{https://arxiv.org/abs/1107.5755}{{\tt
+  1107.5755}}].
+
+\bibitem{Anselmino:2012aa}
+M.~Anselmino, M.~Boglione and S.~Melis, \emph{{A Strategy towards the
+  extraction of the Sivers function with TMD evolution}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.86.014028}{\emph{Phys. Rev.} {\bf
+  D86} (2012) 014028}, [\href{https://arxiv.org/abs/1204.1239}{{\tt
+  1204.1239}}].
+
+\bibitem{Bacchetta:2002ux}
+A.~Bacchetta and M.~Radici, \emph{{Partial wave analysis of two hadron
+  fragmentation functions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.67.094002}{\emph{Phys. Rev.} {\bf
+  D67} (2003) 094002}, [\href{https://arxiv.org/abs/hep-ph/0212300}{{\tt
+  hep-ph/0212300}}].
+
+\bibitem{Bacchetta:2003vn}
+A.~Bacchetta and M.~Radici, \emph{{Two hadron semiinclusive production
+  including subleading twist}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.69.074026}{\emph{Phys. Rev.} {\bf
+  D69} (2004) 074026}, [\href{https://arxiv.org/abs/hep-ph/0311173}{{\tt
+  hep-ph/0311173}}].
+
+\bibitem{Bacchetta:2011ip}
+A.~Bacchetta, A.~Courtoy and M.~Radici, \emph{{First glances at the
+  transversity parton distribution through dihadron fragmentation functions}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.107.012001}{\emph{Phys. Rev.
+  Lett.} {\bf 107} (2011) 012001}, [\href{https://arxiv.org/abs/1104.3855}{{\tt
+  1104.3855}}].
+
+\bibitem{Bacchetta:2012ty}
+A.~Bacchetta, A.~Courtoy and M.~Radici, \emph{{First extraction of valence
+  transversities in a collinear framework}},
+  \href{http://dx.doi.org/10.1007/JHEP03(2013)119}{\emph{JHEP} {\bf 03} (2013)
+  119}, [\href{https://arxiv.org/abs/1212.3568}{{\tt 1212.3568}}].
+
+\bibitem{Radici:2015mwa}
+M.~Radici, A.~Courtoy, A.~Bacchetta and M.~Guagnelli, \emph{{Improved
+  extraction of valence transversity distributions from inclusive dihadron
+  production}}, \href{http://dx.doi.org/10.1007/JHEP05(2015)123}{\emph{JHEP}
+  {\bf 05} (2015) 123}, [\href{https://arxiv.org/abs/1503.03495}{{\tt
+  1503.03495}}].
+
+\bibitem{Radici:2018iag}
+M.~Radici and A.~Bacchetta, \emph{{First Extraction of Transversity from a
+  Global Analysis of Electron-Proton and Proton-Proton Data}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.120.192001}{\emph{Phys. Rev.
+  Lett.} {\bf 120} (2018) 192001},
+  [\href{https://arxiv.org/abs/1802.05212}{{\tt 1802.05212}}].
+
+\bibitem{Aghasyan:2017jop}
+{\scshape COMPASS} collaboration, M.~Aghasyan et~al., \emph{{First measurement
+  of transverse-spin-dependent azimuthal asymmetries in the Drell-Yan
+  process}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.119.112002}{\emph{Phys. Rev.
+  Lett.} {\bf 119} (2017) 112002},
+  [\href{https://arxiv.org/abs/1704.00488}{{\tt 1704.00488}}].
+
+\bibitem{Parsamyan:2018zju}
+B.~Parsamyan, \emph{{First measurement of transverse-spin-dependent azimuthal
+  asymmetries in the Drell-Yan process}}, {\emph{PoS} {\bf DIS2017} (2018)
+  243}, [\href{https://arxiv.org/abs/1801.01487}{{\tt 1801.01487}}].
+
+\bibitem{Collins:1992kk}
+J.~C. Collins, \emph{Fragmentation of transversely polarized quarks probed in
+  transverse momentum distributions}, {\emph{Nucl. Phys.} {\bf B396} (1993)
+  161--182}.
+
+\bibitem{Anselmino:2013vqa}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia and A.~Prokudin,
+  \emph{{Simultaneous extraction of transversity and Collins functions from new
+  SIDIS and $e^{+}e^{-}$ data}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.87.094019}{\emph{Phys. Rev.} {\bf
+  D87} (2013) 094019}, [\href{https://arxiv.org/abs/1303.3822}{{\tt
+  1303.3822}}].
+
+\bibitem{Kang:2014zza}
+Z.-B. Kang, A.~Prokudin, P.~Sun and F.~Yuan, \emph{{Nucleon tensor charge from
+  Collins azimuthal asymmetry measurements}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.91.071501}{\emph{Phys. Rev.} {\bf
+  D91} (2015) 071501}, [\href{https://arxiv.org/abs/1410.4877}{{\tt
+  1410.4877}}].
+
+\bibitem{Anselmino:2015sxa}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, J.~O. Gonzalez~Hernandez, S.~Melis,
+  F.~Murgia et~al., \emph{{Collins functions for pions from SIDIS and new
+  $e^+e^-$ data: a first glance at their transverse momentum dependence}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.92.114023}{\emph{Phys. Rev.} {\bf
+  D92} (2015) 114023}, [\href{https://arxiv.org/abs/1510.05389}{{\tt
+  1510.05389}}].
+
+\bibitem{Airapetian:2010ds}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Effects of
+  transversity in deep-inelastic scattering by polarized protons}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2010.08.012}{\emph{Phys. Lett.}
+  {\bf B693} (2010) 11--16}, [\href{https://arxiv.org/abs/1006.4221}{{\tt
+  1006.4221}}].
+
+\bibitem{Adolph:2014zba}
+{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{Collins and Sivers
+  asymmetries in muonproduction of pions and kaons off transversely polarised
+  protons}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2015.03.056}{\emph{Phys. Lett.}
+  {\bf B744} (2015) 250--259}, [\href{https://arxiv.org/abs/1408.4405}{{\tt
+  1408.4405}}].
+
+\bibitem{Barone:2009hw}
+V.~Barone, S.~Melis and A.~Prokudin, \emph{{The Boer-Mulders effect in
+  unpolarized SIDIS: An Analysis of the COMPASS and HERMES data on the cos2phi
+  asymmetry}}, \href{http://dx.doi.org/10.1103/PhysRevD.81.114026}{\emph{Phys.
+  Rev.} {\bf D81} (2010) 114026}, [\href{https://arxiv.org/abs/0912.5194}{{\tt
+  0912.5194}}].
+
+\bibitem{Airapetian:2012yg}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Azimuthal
+  distributions of charged hadrons, pions, and kaons produced in deep-inelastic
+  scattering off unpolarized protons and deuterons}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.87.012010}{\emph{Phys. Rev.} {\bf
+  D87} (2013) 012010}, [\href{https://arxiv.org/abs/1204.4161}{{\tt
+  1204.4161}}].
+
+\bibitem{Adolph:2014pwc}
+{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{Measurement of
+  azimuthal hadron asymmetries in semi-inclusive deep inelastic scattering off
+  unpolarised nucleons}},
+  \href{http://dx.doi.org/10.1016/j.nuclphysb.2014.07.019}{\emph{Nucl. Phys.}
+  {\bf B886} (2014) 1046--1077}, [\href{https://arxiv.org/abs/1401.6284}{{\tt
+  1401.6284}}].
+
+\bibitem{Cahn:1978se}
+R.~N. Cahn, \emph{{Azimuthal Dependence in Leptoproduction: A Simple Parton
+  Model Calculation}},
+  \href{http://dx.doi.org/10.1016/0370-2693(78)90020-5}{\emph{Phys. Lett.} {\bf
+  B78} (1978) 269}.
+
+\bibitem{Barone:2010gk}
+V.~Barone, S.~Melis and A.~Prokudin, \emph{{Azimuthal asymmetries in
+  unpolarized Drell-Yan processes and the Boer-Mulders distributions of
+  antiquarks}}, \href{http://dx.doi.org/10.1103/PhysRevD.82.114025}{\emph{Phys.
+  Rev.} {\bf D82} (2010) 114025}, [\href{https://arxiv.org/abs/1009.3423}{{\tt
+  1009.3423}}].
+
+\bibitem{Barone:2015ksa}
+V.~Barone, M.~Boglione, J.~O. Gonzalez~Hernandez and S.~Melis,
+  \emph{{Phenomenological analysis of azimuthal asymmetries in unpolarized
+  semi-inclusive deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.91.074019}{\emph{Phys. Rev.} {\bf
+  D91} (2015) 074019}, [\href{https://arxiv.org/abs/1502.04214}{{\tt
+  1502.04214}}].
+
+\bibitem{Avakian:2008dz}
+H.~Avakian, A.~V. Efremov, P.~Schweitzer and F.~Yuan, \emph{{Transverse
+  momentum dependent distribution function $h_{1T}^\perp$ and the single spin
+  asymmetry $A_{UT}^{\sin(3\phi-\phi_S)}$}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.78.114024}{\emph{Phys. Rev.} {\bf
+  D78} (2008) 114024}, [\href{https://arxiv.org/abs/0805.3355}{{\tt
+  0805.3355}}].
+
+\bibitem{She:2009jq}
+J.~She, J.~Zhu and B.-Q. Ma, \emph{{Pretzelosity h(1T)**perpendicular and quark
+  orbital angular momentum}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.79.054008}{\emph{Phys. Rev.} {\bf
+  D79} (2009) 054008}, [\href{https://arxiv.org/abs/0902.3718}{{\tt
+  0902.3718}}].
+
+\bibitem{Lorce:2011kn}
+C.~Lorce and B.~Pasquini, \emph{{Pretzelosity TMD and Quark Orbital Angular
+  Momentum}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2012.03.025}{\emph{Phys. Lett.}
+  {\bf B710} (2012) 486--488}, [\href{https://arxiv.org/abs/1111.6069}{{\tt
+  1111.6069}}].
+
+\bibitem{Parsamyan:2010se}
+B.~Parsamyan, \emph{{Transverse spin dependent azimuthal asymmetries at
+  COMPASS}}, {\emph{J. Phys. Conf. Ser.} {\bf 295} (2011) 012046},
+  [\href{https://arxiv.org/abs/1012.0155}{{\tt 1012.0155}}].
+
+\bibitem{Schnell:2010zza}
+{\scshape HERMES} collaboration, G.~Schnell, \emph{{The Sivers and other
+  semi-inclusive single-spin asymmetries at HERMES}}, {\emph{PoS} {\bf DIS2010}
+  (2010) 247}.
+
+\bibitem{Lefky:2014eia}
+C.~Lefky and A.~Prokudin, \emph{{Extraction of the distribution function
+  $h^{\perp}_{1T}$ from experimental data}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.91.034010}{\emph{Phys. Rev.} {\bf
+  D91} (2015) 034010}, [\href{https://arxiv.org/abs/1411.0580}{{\tt
+  1411.0580}}].
+
+\bibitem{Kotzinian:2008fe}
+A.~Kotzinian, \emph{{SIDIS Asymmetries in Quark-Diquark Model}},  in
+  \emph{{Transversity 2008: 2nd International Workshop on Transverse
+  Polarization Phenomena in Hard Processes Ferrara, Italy, May 28-31, 2008}},
+  2008.
+\newblock \href{https://arxiv.org/abs/0806.3804}{{\tt 0806.3804}}.
+\newblock \href{http://dx.doi.org/10.1142/9789814277785_0029}{DOI}.
+
+\bibitem{Boffi:2009sh}
+S.~Boffi, A.~V. Efremov, B.~Pasquini and P.~Schweitzer, \emph{{Azimuthal spin
+  asymmetries in light-cone constituent quark models}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.79.094012}{\emph{Phys. Rev.} {\bf
+  D79} (2009) 094012}, [\href{https://arxiv.org/abs/0903.1271}{{\tt
+  0903.1271}}].
+
+\bibitem{Ball:2014uwa}
+{\scshape NNPDF} collaboration, R.~D. Ball et~al., \emph{{Parton distributions
+  for the LHC Run II}},
+  \href{http://dx.doi.org/10.1007/JHEP04(2015)040}{\emph{JHEP} {\bf 04} (2015)
+  040}, [\href{https://arxiv.org/abs/1410.8849}{{\tt 1410.8849}}].
+
+\bibitem{Huang:2011bc}
+{\scshape Jefferson Lab Hall A} collaboration, J.~Huang et~al.,
+  \emph{{Beam-Target Double Spin Asymmetry $A_{LT}$ in Charged Pion Production
+  from Deep Inelastic Scattering on a Transversely Polarized He-3 Target at
+  $1.4 < Q^2 < 2.7 GeV^2$}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.108.052001}{\emph{Phys. Rev.
+  Lett.} {\bf 108} (2012) 052001}, [\href{https://arxiv.org/abs/1108.0489}{{\tt
+  1108.0489}}].
+
+\bibitem{Parsamyan:2007ju}
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{New target transverse
+  spin dependent azimuthal asymmetries from COMPASS experiment}},
+  \href{http://dx.doi.org/10.1140/epjst/e2008-00780-1}{\emph{Eur. Phys. J. ST}
+  {\bf 162} (2008) 89--96}, [\href{https://arxiv.org/abs/0709.3440}{{\tt
+  0709.3440}}].
+
+\bibitem{Parsamyan:2018evv}
+B.~Parsamyan, \emph{{Measurement of target-polarization dependent azimuthal
+  asymmetries in SIDIS and Drell-Yan processes at COMPASS experiment}},
+  {\emph{PoS} {\bf QCDEV2017} (2018) 042}.
+
+\bibitem{Parsamyan:2015dfa}
+B.~Parsamyan, \emph{{Transverse spin azimuthal asymmetries in SIDIS at COMPASS:
+  Multidimensional analysis}},
+  \href{http://dx.doi.org/10.1142/S2010194516600296}{\emph{Int. J. Mod. Phys.
+  Conf. Ser.} {\bf 40} (2016) 1660029},
+  [\href{https://arxiv.org/abs/1504.01599}{{\tt 1504.01599}}].
+
+\bibitem{Pappalardo:2011cu}
+{\scshape HERMES} collaboration, L.~L. Pappalardo and M.~Diefenthaler,
+  \emph{{Measurements of Double-Spin Asymmetries in SIDIS of Longitudinally
+  Polarized Leptons off Transversely Polarized Protons}},
+  \href{https://arxiv.org/abs/1107.4227}{{\tt 1107.4227}}.
+
+\bibitem{Pappalardo:2012zz}
+{\scshape HERMES} collaboration, L.~L. Pappalardo, \emph{{Accessing TMDs at
+  HERMES}}, \href{http://dx.doi.org/10.1063/1.3700519}{\emph{AIP Conf. Proc.}
+  {\bf 1441} (2012) 229--232}.
+
+\bibitem{Parsamyan:2013fia}
+B.~Parsamyan, \emph{{Transverse spin asymmetries at COMPASS: beyond Collins and
+  Sivers effects}}, {\emph{PoS} {\bf DIS2013} (2013) 231},
+  [\href{https://arxiv.org/abs/1307.0183}{{\tt 1307.0183}}].
+
+\bibitem{Parsamyan:2018ovx}
+B.~Parsamyan, \emph{{Measurement of longitudinal-target-polarization dependent
+  azimuthal asymmetries in SIDIS at COMPASS experiment}}, {\emph{PoS} {\bf
+  DIS2017} (2018) 259}, [\href{https://arxiv.org/abs/1801.01488}{{\tt
+  1801.01488}}].
+
+\bibitem{Airapetian:1999tv}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Observation of a
+  single spin azimuthal asymmetry in semiinclusive pion electro production}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.84.4047}{\emph{Phys. Rev. Lett.}
+  {\bf 84} (2000) 4047--4051},
+  [\href{https://arxiv.org/abs/hep-ex/9910062}{{\tt hep-ex/9910062}}].
+
+\bibitem{Jawalkar:2017ube}
+S.~Jawalkar et~al., \emph{{Semi-Inclusive $\pi_0$ target and beam-target
+  asymmetries from 6 GeV electron scattering with CLAS}},
+  \href{https://arxiv.org/abs/1709.10054}{{\tt 1709.10054}}.
+
+\bibitem{Airapetian:2002mf}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Measurement of
+  single spin azimuthal asymmetries in semiinclusive electroproduction of pions
+  and kaons on a longitudinally polarized deuterium target}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(03)00566-5}{\emph{Phys. Lett.}
+  {\bf B562} (2003) 182--192},
+  [\href{https://arxiv.org/abs/hep-ex/0212039}{{\tt hep-ex/0212039}}].
+
+\bibitem{Avakian:2003pk}
+{\scshape CLAS} collaboration, H.~Avakian et~al., \emph{{Measurement of
+  beam-spin asymmetries for pi + electroproduction above the baryon resonance
+  region}}, \href{http://dx.doi.org/10.1103/PhysRevD.69.112004}{\emph{Phys.
+  Rev.} {\bf D69} (2004) 112004},
+  [\href{https://arxiv.org/abs/hep-ex/0301005}{{\tt hep-ex/0301005}}].
+
+\bibitem{Airapetian:2006rx}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Beam-Spin
+  Asymmetries in the Azimuthal Distribution of Pion Electroproduction}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2007.03.015}{\emph{Phys. Lett.}
+  {\bf B648} (2007) 164--170},
+  [\href{https://arxiv.org/abs/hep-ex/0612059}{{\tt hep-ex/0612059}}].
+
+\bibitem{Gohn:2009zz}
+W.~Gohn, H.~Avakian, K.~Joo and M.~Ungaro, \emph{{Beam spin asymmetries from
+  semi-inclusive pion electroproduction in deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1063/1.3215689}{\emph{AIP Conf. Proc.} {\bf 1149}
+  (2009) 461--464}.
+
+\bibitem{Aghasyan:2011ha}
+M.~Aghasyan, H.~Avakian, P.~Rossi, E.~De~Sanctis, D.~Hasch et~al.,
+  \emph{{Precise Measurements of Beam Spin Asymmetries in Semi-Inclusive
+  $\pi^0$ production}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2011.09.044}{\emph{Phys. Lett.}
+  {\bf B704} (2011) 397--402}, [\href{https://arxiv.org/abs/1106.2293}{{\tt
+  1106.2293}}].
+
+\bibitem{Gohn:2014zbz}
+{\scshape CLAS} collaboration, W.~Gohn et~al., \emph{{Beam-spin asymmetries
+  from semi-inclusive pion electroproduction}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.89.072011}{\emph{Phys. Rev.} {\bf
+  D89} (2014) 072011}, [\href{https://arxiv.org/abs/1402.4097}{{\tt
+  1402.4097}}].
+
+\bibitem{private}
+\emph{{Private communications with B. Parsamyan}}, .
+
+\bibitem{Efremov:2002ut}
+A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Azimuthal asymmetries at
+  CLAS: extraction of e**a(x) and prediction of A(UL)}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.67.114014}{\emph{Phys. Rev.} {\bf
+  D67} (2003) 114014}, [\href{https://arxiv.org/abs/hep-ph/0208124}{{\tt
+  hep-ph/0208124}}].
+
+\bibitem{Afanasev:2003ze}
+A.~Afanasev and C.~E. Carlson, \emph{{Single spin beam asymmetry in
+  semiexclusive deep inelastic electroproduction}},  in \emph{{Intersections of
+  particle and nuclear physics. Proceedings, 8th Conference, CIPANP 2003, New
+  York, USA, May 19-24, 2003}}, 2003.
+\newblock \href{https://arxiv.org/abs/hep-ph/0308163}{{\tt hep-ph/0308163}}.
+
+\bibitem{Yuan:2003gu}
+F.~Yuan, \emph{{The Beam single spin asymmetry in semiinclusive deep inelastic
+  scattering}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2004.03.040}{\emph{Phys. Lett.}
+  {\bf B589} (2004) 28--34}, [\href{https://arxiv.org/abs/hep-ph/0310279}{{\tt
+  hep-ph/0310279}}].
+
+\bibitem{Gamberg:2003pz}
+L.~P. Gamberg, D.~S. Hwang and K.~A. Oganessyan, \emph{{Chiral odd
+  fragmentation functions in single pion inclusive electroproduction}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2004.01.054}{\emph{Phys. Lett.}
+  {\bf B584} (2004) 276--284},
+  [\href{https://arxiv.org/abs/hep-ph/0311221}{{\tt hep-ph/0311221}}].
+
+\bibitem{Afanasev:2006gw}
+A.~V. Afanasev and C.~E. Carlson, \emph{{Beam Single-Spin Asymmetry in
+  Semi-Inclusive Deep Inelastic Scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.74.114027}{\emph{Phys. Rev.} {\bf
+  D74} (2006) 114027}, [\href{https://arxiv.org/abs/hep-ph/0603269}{{\tt
+  hep-ph/0603269}}].
+
+\bibitem{Mao:2012dk}
+W.~Mao and Z.~Lu, \emph{{Beam single spin asymmetry of neutral pion production
+  in semi-inclusive deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.87.014012}{\emph{Phys. Rev.} {\bf
+  D87} (2013) 014012}, [\href{https://arxiv.org/abs/1210.4790}{{\tt
+  1210.4790}}].
+
+\bibitem{Mao:2014dva}
+W.~Mao and Z.~Lu, \emph{{On the beam spin asymmetries of electroproduction of
+  charged hadrons off the nucleon targets}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-014-2910-7}{\emph{Eur. Phys. J.}
+  {\bf C74} (2014) 2910}, [\href{https://arxiv.org/abs/1401.4653}{{\tt
+  1401.4653}}].
+
+\bibitem{Courtoy:2014xea}
+A.~Courtoy, \emph{{Phenomenology of hadron structure --- why low energy physics
+  matters}}, \href{http://dx.doi.org/10.1088/1742-6596/651/1/012007}{\emph{J.
+  Phys. Conf. Ser.} {\bf 651} (2015) 012007},
+  [\href{https://arxiv.org/abs/1405.6567}{{\tt 1405.6567}}].
+
+\bibitem{Yang:2016mxl}
+Y.~Yang, Z.~Lu and I.~Schmidt, \emph{{Twist-3 T-odd fragmentation functions
+  $G^\perp$ and $\tilde{G}^\perp$ in a spectator model}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2016.08.053}{\emph{Phys. Lett.}
+  {\bf B761} (2016) 333--339}, [\href{https://arxiv.org/abs/1607.01638}{{\tt
+  1607.01638}}].
+
+\bibitem{Anselmino:2006yc}
+M.~Anselmino, A.~Efremov, A.~Kotzinian and B.~Parsamyan, \emph{{Transverse
+  momentum dependence of the quark helicity distributions and the Cahn effect
+  in double-spin asymmetry A(LL) in semi inclusive DIS}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.74.074015}{\emph{Phys. Rev.} {\bf
+  D74} (2006) 074015}, [\href{https://arxiv.org/abs/hep-ph/0608048}{{\tt
+  hep-ph/0608048}}].
+
+\bibitem{Mao:2016hdi}
+W.~Mao, X.~Wang, X.~Du, Z.~Lu and B.-Q. Ma, \emph{{On the cos $\phi_h$
+  asymmetry in electroproduction of pions in double longitudinally polarized
+  process}},
+  \href{http://dx.doi.org/10.1016/j.nuclphysa.2015.10.004}{\emph{Nucl. Phys.}
+  {\bf A945} (2016) 153--167}.
+
+\bibitem{Airapetian:2005jc}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Subleading-twist
+  effects in single-spin asymmetries in semi-inclusive deep-inelastic
+  scattering on a longitudinally polarized hydrogen target}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2005.06.067}{\emph{Phys. Lett.}
+  {\bf B622} (2005) 14--22}, [\href{https://arxiv.org/abs/hep-ex/0505042}{{\tt
+  hep-ex/0505042}}].
+
+\bibitem{Airapetian:2001eg}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Single spin
+  azimuthal asymmetries in electroproduction of neutral pions in semiinclusive
+  deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.64.097101}{\emph{Phys. Rev.} {\bf
+  D64} (2001) 097101}, [\href{https://arxiv.org/abs/hep-ex/0104005}{{\tt
+  hep-ex/0104005}}].
+
+\bibitem{Cheng:1972sy}
+T.~P. Cheng and A.~Zee, \emph{{Coincidence electroproduction and scaling in the
+  regge region}}, \href{http://dx.doi.org/10.1103/PhysRevD.6.885}{\emph{Phys.
+  Rev.} {\bf D6} (1972) 885--893}.
+
+\bibitem{Aubert:1983cz}
+{\scshape European Muon} collaboration, J.~J. Aubert et~al., \emph{{Measurement
+  of Hadronic Azimuthal Distributions in Deep Inelastic Muon Proton
+  Scattering}},
+  \href{http://dx.doi.org/10.1016/0370-2693(83)91076-6}{\emph{Phys. Lett.} {\bf
+  130B} (1983) 118--122}.
+
+\bibitem{Dakin:1972db}
+J.~T. Dakin, G.~J. Feldman, W.~L. Lakin, F.~Martin, M.~L. Perl, E.~W. Petraske
+  et~al., \emph{Preliminary results on the inclusive electroproduction of
+  hadrons},  1972.
+
+\bibitem{Mkrtchyan:2007sr}
+H.~Mkrtchyan, P.~Bosted, G.~Adams, A.~Ahmidouch, T.~Angelescu et~al.,
+  \emph{{Transverse momentum dependence of semi-inclusive pion production}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2008.05.047}{\emph{Phys. Lett.}
+  {\bf B665} (2008) 20--25}, [\href{https://arxiv.org/abs/0709.3020}{{\tt
+  0709.3020}}].
+
+\bibitem{Anselmino:2011ch}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia et~al.,
+  \emph{{General Helicity Formalism for Polarized Semi-Inclusive Deep Inelastic
+  Scattering}}, \href{http://dx.doi.org/10.1103/PhysRevD.83.114019}{\emph{Phys.
+  Rev.} {\bf D83} (2011) 114019}, [\href{https://arxiv.org/abs/1101.1011}{{\tt
+  1101.1011}}].
+
+\bibitem{Efremov:2004tp}
+A.~V. Efremov, K.~Goeke, S.~Menzel, A.~Metz and P.~Schweitzer, \emph{{Sivers
+  effect in semi-inclusive DIS and in the Drell-Yan process}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2005.03.010}{\emph{Phys. Lett.}
+  {\bf B612} (2005) 233--244},
+  [\href{https://arxiv.org/abs/hep-ph/0412353}{{\tt hep-ph/0412353}}].
+
+\bibitem{Gamberg:2013kla}
+L.~Gamberg, Z.-B. Kang and A.~Prokudin, \emph{{Indication on the
+  process-dependence of the Sivers effect}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.110.232301}{\emph{Phys. Rev.
+  Lett.} {\bf 110} (2013) 232301}, [\href{https://arxiv.org/abs/1302.3218}{{\tt
+  1302.3218}}].
+
+\bibitem{Sun:2013dya}
+P.~Sun and F.~Yuan, \emph{{Energy Evolution for the Sivers Asymmetries in Hard
+  Processes}}, \href{http://dx.doi.org/10.1103/PhysRevD.88.034016}{\emph{Phys.
+  Rev.} {\bf D88} (2013) 034016}, [\href{https://arxiv.org/abs/1304.5037}{{\tt
+  1304.5037}}].
+
+\bibitem{Gluck:2000dy}
+M.~Gluck, E.~Reya, M.~Stratmann and W.~Vogelsang, \emph{{Models for the
+  polarized parton distributions of the nucleon}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.63.094005}{\emph{Phys. Rev.} {\bf
+  D63} (2001) 094005}, [\href{https://arxiv.org/abs/hep-ph/0011215}{{\tt
+  hep-ph/0011215}}].
+
+\bibitem{Buckley:2014ana}
+A.~Buckley, J.~Ferrando, S.~Lloyd, K.~Nordström, B.~Page, M.~Rüfenacht et~al.,
+  \emph{{LHAPDF6: parton density access in the LHC precision era}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-015-3318-8}{\emph{Eur. Phys. J.}
+  {\bf C75} (2015) 132}, [\href{https://arxiv.org/abs/1412.7420}{{\tt
+  1412.7420}}].
+
+\bibitem{Berthou:2015oaw}
+B.~Berthou et~al., \emph{{PARTONS: PARtonic Tomography Of Nucleon Software}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-018-5948-0}{\emph{Eur. Phys. J.}
+  {\bf C78} (2018) 478}, [\href{https://arxiv.org/abs/1512.06174}{{\tt
+  1512.06174}}].
+
+\bibitem{Hautmann:2014kza}
+F.~Hautmann, H.~Jung, M.~Krämer, P.~J. Mulders, E.~R. Nocera, T.~C. Rogers
+  et~al., \emph{{TMDlib and TMDplotter: library and plotting tools for
+  transverse-momentum-dependent parton distributions}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-014-3220-9}{\emph{Eur. Phys. J.}
+  {\bf C74} (2014) 3220}, [\href{https://arxiv.org/abs/1408.3015}{{\tt
+  1408.3015}}].
+
+\end{thebibliography}\endgroup
 

### 2018-09-04 tex/test-WW-type-00z.tex
tex

@@
 approximations, it is possible to express all SIDIS structure functions
-in terms of the basis functions. \AP{Notice that SIDIS alone is of course not sufficient to determine
+in terms of the basis functions\footnote{\AP{Notice that SIDIS alone is of course not sufficient to determine
    the basis functions uniquely because the 8 basis functions appear
@@
    $e^+e^-$ annihilation, which are indispensable for the determination
-   of $f_1^a$ and $D_1^a$).}
-%\AP{Notice that SIDIS alone is of course not sufficient to determine the basis
-%functions uniquely: the 8 basis functions appear in 6 \AP{leading-twist} SIDIS structure functions.
-%It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
-%and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
-%play also important roles.}
-%Notice that SIDIS alone is of course not sufficient to determine the basis
-%functions uniquely: \AP{8 twist-2 TMDs (or 6 ``basis'' TMDs) and 2 twist-2 TMD FFs appear in 15 structure functions (8 twist-2 and 5 sub-leading). 
-%Definitely hadron production in $e^+e^-$ annihilation data is needed, each FF couples with 4 different twist-2 TMD PDFs, and so for each FF we have a case with 5 unknowns accessible in 4 twist-2 observables.
-%It is crucial to take advantage of  Drell--Yan process for TMDs
-%and other processes 
-%play also important roles.}
-
+   of $f_1^a$ and $D_1^a$).}}.
 These basis functions allow us to describe, in WW-type approximation,

### 2018-10-03 tex/test-WW-type-01b.tex
new tex

--- 2018-07-26 tex/test-WW-type-00z.tex
@@
 %\setlength{\textwidth}{17cm}
-%\setlength{\textheight}{26.2cm}
+%\setlength{\textheight}{22cm} {}
 %\setlength{\topmargin}{-1cm}
@@
 %\newcommand{\ak}[1]{\orange{#1}}
-%\newcommand{\ps}[1]{\blue{#1}}
+\newcommand{\ps}[1]{\blue{#1}}
 %\newcommand{\gs}[1]{{\color[rgb]{0.65,0,0.65}#1}}
@@
 
-\preprint{\red{version ``01a''}; \today; JLAB-THY-18-2775}
+\preprint{\red{version ``01b''}; 14 Sep 2018; JLAB-THY-18-2775}
 
@@
 Electron-Ion Collider. The results of this paper can be readily used for 
-phenomenology and for event generators, and will help to improve our 
-understanding of the TMD theory beyond leading twist.
-} 
+phenomenology and for event generators, and will help 
+   {to improve the description of semi-inclusive deep-inelastic processes 
+   in terms of transverse momentum dependent parton distribution functions 
+   and fragmentation functions beyond the leading twist}.} 
 %\end{abstract}
@@
 	been obtained without advances in target polarization techniques 
-	employed in the HERMES, COMPASS and JLab experiments 
+	employed in the HERMES, COMPASS and Jefferson Lab (JLab) experiments 
 	\cite{Stock:1994vv,Crabb:1997cy,Goertz:2002vv}.
@@
 which are worthwhile exploring for their own sake, 
-see \cite{Jaffe:1989xx} on $g_T^a(x)$.
+see \ps{for instance Ref.~}\cite{Jaffe:1989xx} on $g_T^a(x)$.
 
@@
 twist-3 in a unique approach. Our results are of importance for measurements 
-performed or in preparation at HERMES, COMPASS, Jefferson Lab (JLab) with 
+performed or in preparation at HERMES, COMPASS, JLab with 
 12$\,$GeV beam-energy upgrade, or proposed in the long-term 
@@
 
+\ps{On the theoretical side it is also important to note that the
+theory for subleading-twist TMD observables is only poorly developed
+as compared to the current state-of-the-art of leading-twist observables.
+In order to address subleading-twist TMD observables one has 
+to restrict oneself to the tree-level formalism 
+\cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,
+Bacchetta:2006tn} which may not be free of doubts
+\cite{Metz:2004je,Gamberg:2006ru}.}
+
 Our predictions, whether confirmed or not supported by current and 
@@
 and call for dedicated theoretical studies to explain (i) why the 
-pertinent $\bar{q}gq$--terms are small or (ii) why they are sizable. 
+pertinent $\bar{q}gq$--terms are small or (ii) why they are sizable,
+\ps{depending on the outcome of the experiments.} 
 In either case our results will deepen the understanding of 
@@
 
+\newpage
 %======= SECTION 2: SIDIS & TMDs & FFs ===============================
@@
 describe the SIDIS structure functions.
-\newpage
+
+%\newpage
 \subsection{The SIDIS process}
@@
 \ee
-and the asymmetries \AP{$A_{XY}^{\rm weight}$,  are defined in terms of structure functions $F_{XY}^{\rm weight}$, as follows}
+and the asymmetries {$A_{XY}^{\rm weight}$,  are defined in terms of 
+structure functions $F_{XY}^{\rm weight}$, as follows}
 \be
@@
 	\;e^{ik\xi}\;\la N(P,S)|\bar\psi_j(0)\,{\cal W}_{(0,\,\infty)}
-	{\cal W}_{(\infty,\xi)}\,\psi_i(\xi)|N(P,S)\ra
+	{\cal W}_{(\infty,\,\xi)}\,\psi_i(\xi)|N(P,S)\ra
     	\with{ }{\xi^+\!=\!0}{$k^+ = xP^+$}
 	\ee
-where the Wilson-lines \AP{${\cal W}_{(0,\,\infty)}
-	{\cal W}_{(\infty,\xi)}$} refer to the SIDIS process 
+where the Wilson-lines  {${\cal W}_{(0,\,\infty)}{\cal W}_{(\infty,\,\xi)}$} 
+refer to the SIDIS process 
 \cite{Collins:2002kn}. For a generic four-vector $a^\mu$ we define
@@
 \cite{Ralston:1979ys,Jaffe:1991ra}, namely at twist-2 level
+
+\newpage
 \begin{subequations}\ba
@@
 
-\AP{Fragmentation functions are defined through the following correlator [10]
+{Fragmentation functions are defined through the following correlator %[10]
+\cite{Metz:2016swz}
 (where $\bfpperp$ denotes the transverse momentum of the produced hadrons
@@
 \ea\end{subequations}
+
+\newpage
+
+\noindent
 The FFs depend on $z$, $P_\perp$, renormalization scale, quark flavor and 
@@
 \ba
-	F_{UU}^{\cos\phi_h}  
+	\ \hspace{-1cm}	F_{UU}^{\cos\phi_h}  
 	&=& 
@@
 	\label{Eq:FUUcosphi}\\
-	F_{LU}^{\sin\phi_h}  
+	\ \hspace{-1cm}	F_{LU}^{\sin\phi_h}  
 	&=& 
@@
 	\label{FLUsinphi}\;\;\;\;\;\\
-	F_{UL}^{\sin\phi_h} 
+	\ \hspace{-1cm}	F_{UL}^{\sin\phi_h} 
  	&=& 
@@
 	\label{FULsinphi}\\
-	F_{LL}^{\cos \phi_h} 
+	\ \hspace{-1cm}	F_{LL}^{\cos \phi_h} 
  	&=& 
@@
 	\label{FLLcosphi}\;\;\;\;\;\;\;\;\;\\
-	F_{UT}^{\sin \phi_S } 
+	\ \hspace{-1cm}	F_{UT}^{\sin \phi_S } 
 	&=&  
@@
 	+ r_h^{ }\, f_{1T}^{\perp } \,\frac{\tilde{D}^{\perp }}{z}
-   	\biggr) \biggr]\, , \label{FUTsinphiS}\\ 
-	F_{LT}^{\cos \phi_S} 
+   	\biggr) \biggr]\, , \label{FUTsinphiS}
+\ea
+\ba 
+	\ \hspace{-1cm}	F_{LT}^{\cos \phi_S} 
 	&=& 
@@
 	\, , \label{FLTcosphiS} \\ \hspace{-5mm}
-	F_{UT}^{\sin(2\phi_h -\phi_S)} 
+	\ \hspace{-1cm}	F_{UT}^{\sin(2\phi_h -\phi_S)} 
 	&=& 
@@
    	- r_h^{ }\, \, h_{1T}^{\perp }  \frac{\tilde{H}}{z}\biggr) \biggr] \, , \\
-	F_{LT}^{\cos(2\phi_h - \phi_S)} 
+	\ \hspace{-1cm}	F_{LT}^{\cos(2\phi_h - \phi_S)} 
 	&=& \frac{2M_N}{Q}\,{\cal C}\biggl[
@@
 framework, including definition, renormalization and evolution of 
-leading-twist TMDs \cite{Aybat:2011zv,Aybat:2011ge,Echevarria:2014xaa},
-NLO corrections within the TMD framework \cite{Ma:2013aca}, and  
-phenomenological fits with evolution \cite{Aybat:2011ta,Kang:2015msa}.
+leading-twist TMDs 
+\cite{Aybat:2011zv,Aybat:2011ge,Echevarria:2014xaa,Collins:2014jpa},  
+%\ps{(PS: \cite{Collins:2014jpa} ADDED)}
+\ps{next-to-leading order} corrections within the TMD framework 
+\cite{Ma:2013aca}, and phenomenological fits with evolution 
+\cite{Aybat:2011ta,Kang:2015msa}.
+\ps{The matching of twist-2 collinear and TMD quantities was 
+studied to next-to-leading and next-to-next-to-leading order 
+\cite{Gutierrez-Reyes:2017glx,Gutierrez-Reyes:2018qez}.}
+%
+% ``and it was shown that evolution of higher twist operators is 
+%   generically different from the leading twist ones.''
+%
+% PS: this comment (added by AP) is too trivial. OF COURSE is the
+% evolution of twist-3 DIFFERENT from twist-2. Well known from colinear
+% case! So no surprize it is different for TMDs. Not sure which point
+% you would like to make. I propose to skip, or to make this point
+% more specific.
+% Remark: in early 1990s Braun-et-al derived evolution equations for 
+% \tilde{g}_T(x), later Belitsky+Mueller derived evolution equations 
+% for \tilde{h}_L, \tilde{e}_L. Highly complex evolution pattern
+% (Mellin moments mix under evolution! Simple DGLAP only in large-Nc limit).
+% People know this, do not expect any better for TMDs.
+%
+\ps{The WW approximation has been used recently in Ref.~\cite{Scimemi:2018mmi}
+to connect the twist-2 TMDs $f_{1T}^\perp$, $g_{1T}^\perp$, $h_{1}^\perp$, 
+$h_{1L}^\perp$ to certain higher twist collinear matrix elements.}
+
 In contrast to this, the theory for subleading-twist TMD observables is 
@@
 
-In the T-even case one obtains the following approximations \footnote{\AP{
-Notice that Ref.~\cite{Bacchetta:2006tn} uses four-vector notations for transverse vectors, while in this paper we always utilize two-vectors for transverse vectors, such that e.g.
-${\bfkperp^2}_{\rm our} = -{{p}_T^2}_{\rm \tiny Ref.\cite{Bacchetta:2006tn}}$ and analog for other scalar products of {\it transverse} vectors.}},
+In the T-even case one obtains the following approximations \footnote{%
+	Notice that Ref.~\cite{Bacchetta:2006tn} uses four-vector notation 
+	for transverse vectors, while in this paper we always utilize 
+	two-vectors for transverse vectors, such that e.g.\ 
+	${\bfkperp^2}_{\rm our} = -{{p}_T^2}_{\mbox{\tiny Ref.~\cite{Bacchetta:2006tn}}}$ 
+	and analog for other scalar products of {\it transverse} vectors.
+	\ps{Notice that in our notation transverse vector 
+	are never understood as four-vectors such that 
+	${\bfkperp^2}_{\rm our} \equiv {\kperp^2}_{\rm our}$.}},
 where the terms on the left-hand-side are twist-3, those on the 
@@
 f^{(1)}(x,\kperp^2) = \frac{\kperp^2}{2M^2}\,f(x, \kperp^2)\; , \;\;\;
-f^{(1)}(x ) = \int d^2 \bfkperp f^{(1)}(x,\kperp^2) \; . 
+f^{(1)}(x ) = \int d^2 \kperp f^{(1)}(x,\kperp^2) \; . 
 \ea
@@
 WW-type approximations (\ref{Eq:WW-type-gT},~\ref{Eq:WW-type-6}).
-This yields \cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv}%
+\ps{The resulting relations are the only WW-type relations applicable
+to twist-2 TMDs and are given by the following expressions} 
+\cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv},
+
+\newpage
+
 \begin{subequations}\ba
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t!]
+\begin{figure}[b!]
 \centering
-\includegraphics[width=0.48\textwidth]{\FigPath/g2.pdf} 
-\includegraphics[width=0.48\textwidth]{\FigPath/g2-HERMES.pdf} 
+\includegraphics[width=0.45\textwidth]{\FigPath/g2.pdf} 
+\includegraphics[width=0.45\textwidth]{\FigPath/g2-HERMES.pdf} 
 \caption{\label{Fig:g2} 
@@
 form that lends itself to straightforward tests of the WW-type relations 
-as presented in this paper. \AP{This assumption holds if renormalization is multiplicative and
+as presented in this paper. 
+   {This assumption holds if renormalization is multiplicative and
    flavor-independent for the non-local lattice operators. This is
-   not true for all lattice actions [64]. But presumably it is true
+   not true for all lattice actions \cite{Musch:2010ka}. % PS: [66]? CHECK!!
+   But presumably it is true
    if the lattice action preserves chiral symmetry, as it does in
    the present case. For the latest developments we refer the
-   interested reader to Refs.~\cite{Alexandrou:2017dzj,Ishikawa:2017faj,Ji:2017oey,Yoon:2017qzo,Green:2017xeu,Zhang:2017bzy}.}
+   interested reader to Refs.~\cite{Alexandrou:2017dzj,Ishikawa:2017faj,
+	Engelhardt:2015xja,%Phys.Rev. D93 (2016) no.5, 054501, 
+	Ji:2014hxa,%Phys.Rev. D91 (2015) 074009, 
+	Musch:2011er,%Phys.Rev. D85 (2012) 094510
+   Ji:2017oey,Yoon:2017qzo,Green:2017xeu,Zhang:2017bzy}.}
 
@@
 \ea
-with the understanding that
+\ps{Here the} %with the understanding that
 negative $x$ refer to antiquark distributions
@@
 not give up at this point and take a look at the lattice observables of 
-Ref.~\cite{Musch:2010ka}. Here, the TMDs are obtained from amplitudes 
+Ref.~\cite{Musch:2010ka} \ps{where} TMDs \ps{were} obtained from amplitudes 
 $\tilde A_i(l^2,\ldots)$ in Fourier space, where $\bfkperp$ is encoded 
@@
 
-There is yet another issue to be discussed. 
+There is another issue to discuss. 
 The gauge link that goes into the evaluation of the quark-quark correlator 
@@
 In view of the long debate on the validity of those sum rules
-\cite{Burkardt:2001iy,Bass:2003vp,Efremov:2002qh}, this is in
+\cite{Burkardt:2001iy,Bass:2003vp,Efremov:2002qh}, this is
 an interesting result in itself.
@@
 approximations, it is possible to express all SIDIS structure functions
-in terms of the basis functions. \AP{Notice that SIDIS alone is of course not sufficient to determine
-   the basis functions uniquely because the 8 basis functions appear
-   in 6 SIDIS leading-twist structure functions. It is crucial to take advantage of
-   other processes (such as Drell-Yan and hadron production in
+in terms of the basis functions.\footnote{%
+   Notice that SIDIS alone is not sufficient to determine
+   the \ps{8 basis functions uniquely which} appear in 6 SIDIS 
+   leading-twist structure functions. It is crucial to take 
+   advantage of other processes (like Drell-Yan and hadron production in
    $e^+e^-$ annihilation, which are indispensable for the determination
-   of $f_1^a$ and $D_1^a$).}
-%\AP{Notice that SIDIS alone is of course not sufficient to determine the basis
-%functions uniquely: the 8 basis functions appear in 6 \AP{leading-twist} SIDIS structure functions.
-%It is crucial to take advantage of other processes: Drell--Yan for PDFs and TMDs
-%and hadron production in $e^+e^-$ annihilation for FFs. Other processes 
-%play also important roles.}
-%Notice that SIDIS alone is of course not sufficient to determine the basis
-%functions uniquely: \AP{8 twist-2 TMDs (or 6 ``basis'' TMDs) and 2 twist-2 TMD FFs appear in 15 structure functions (8 twist-2 and 5 sub-leading). 
-%Definitely hadron production in $e^+e^-$ annihilation data is needed, each FF couples with 4 different twist-2 TMD PDFs, and so for each FF we have a case with 5 unknowns accessible in 4 twist-2 observables.
-%It is crucial to take advantage of  Drell--Yan process for TMDs
-%and other processes 
-%play also important roles.}
-
+   of $f_1^a$, $D_1^a$,~\ps{$H_1^{\perp a}$}).}
 These basis functions allow us to describe, in WW-type approximation,
@@
 where the left-hand side is finite while the right-hand side vanishes.
-However, such incompatibilities are washed out and not apparent after
-the convolution integrals defining the structure functions are solved.
+%
+% PS: this was ``old scheme''. Superseded by ``new scheme''!
+%
+% However, such incompatibilities are washed out and not apparent after
+% the convolution integrals defining the structure functions are solved.
 Notice that the failure of the WW-type approximations
@@
 	f_{1T}^{\perp a}, \;h_1^{\perp a},\; h_{1T}^{\perp a}; \; 
-	D_1^a, \; H_1^{\perp a} \,$. For details see App.~\ref{App:basis}.}
+	D_1^a, \; H_1^{\perp a} \,$. 
+	The parametrizations of the basis functions and the Gaussian 
+	model parameters are described in detail in App.~\ref{App:basis}.}
 \end{figure}
@@
 twist-2 collinear functions. All collinear functions are calculated at 
-$Q^2 = 2.4$ GeV$^2$. Collinear $f_1^a(x)$ are from Ref.~\cite{Martin:2009iq},  
-$g_1^a(x)$ are from Ref.~\cite{Gluck:1998xa}, and $D_1^a$ are from 
-Ref.~\cite{deFlorian:2007aj}. The other four TMDs 
+$Q^2 = 2.4$ GeV$^2$ \ps{with} $f_1^a(x)$ from \cite{Martin:2009iq},  
+$g_1^a(x)$ from \cite{Gluck:1998xa}, $D_1^a(z)$ from 
+\cite{deFlorian:2007aj}. The other four TMDs 
 have no collinear counterparts. 
@@
 the Gaussian model expressions, and the Gaussian width parameters are
-largely absorbed in the definitions of the transverse moments.
-% which helps to minimize the model-dependence. 
-Second,
+largely absorbed in the definitions of the transverse moments. Second,
 the $k_\perp$--moments of these TMDs have in principle simple definitions
@@
 \ea\end{subequations}
-The parametrizations of the basis functions and the Gaussian model
-parameters are described in detail in App.~\ref{App:basis}.
+
+\newpage
 
@@
 
-Let us begin with Jefferson Lab where, in the pre-12$\,$GeV era, electron beams 
+Let us begin with JLab where, in the pre-12$\,$GeV era, electron beams 
 from CEBAF with energies in the range $4.3$ to $5.7$ GeV were scattered 
@@
 	% for $\la Q^2\ra=2.37\,{\rm GeV}^2$, $\la x\ra=0.24$, $\la z\ra=0.30$ 
-	at Jefferson Lab with 5.75 GeV beam \cite{Osipenko:2008aa}.
+	at JLab with 5.75 GeV beam \cite{Osipenko:2008aa}.
 Middle panel: 
@@
 Signori:2013mda,Anselmino:2013lza}, but nothing is known about its 
-applicability to spin asymmetries. The Jefferson Lab data \cite{Avakian:2010ae} 
+applicability to spin asymmetries. The JLab data \cite{Avakian:2010ae} 
 on $A_{LL}(\Phperp)$ put us in the position to conduct a first ``test'' 
@@
 \centering 
-\includegraphics[width=0.45\textwidth]{\FigPath/all_jlab_pip}  
-\includegraphics[width=0.45\textwidth]{\FigPath/all_jlab_pi0}  
-\includegraphics[width=0.45\textwidth]{\FigPath/all_jlab_pim} 
+\includegraphics[width=0.333\textwidth]{\FigPath/all_jlab_pip}%
+\includegraphics[width=0.333\textwidth]{\FigPath/all_jlab_pi0}%  
+\includegraphics[width=0.333\textwidth]{\FigPath/all_jlab_pim} 
 \caption{\label{jlab_ALL} 
@@
 
-The definition of the asymmetry in  the Jefferson Lab experiment \cite{Avakian:2010ae} 
+The definition of the asymmetry in  the JLab experiment \cite{Avakian:2010ae} 
 was
@@
 and tested through other observables in Sec.~\ref{Sec-5.1:FUU-basis}.
-Therefore the comparison of our results to the Jefferson Lab data \cite{Avakian:2010ae} 
+Therefore the comparison of our results to the JLab data \cite{Avakian:2010ae} 
 shown in Fig.~\ref{jlab_ALL} provides several important tests.
-First, the Jefferson Lab data \cite{Avakian:2010ae} are compatible
+First, the JLab data \cite{Avakian:2010ae} are compatible
 with the Gaussian Ansatz within uncertainties. Second, the lattice 
@@
 	parametrizations of $f_1^a(x)$, $g_1^a(x)$, $D_1^a(z)$. This 
-	shows that even at the moderate beam energies of the pre-12~GeV 
-	era one was, to a good approximation, indeed probing DIS at 
-	Jefferson Lab~\cite{Avakian:2010ae}.)
+	shows that in the pre-12~GeV era one was, to a good 
+	approximation, indeed already probing DIS \cite{Avakian:2010ae}.)
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_COMPASS_x.pdf}
+\includegraphics[width=0.35\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
+\includegraphics[width=0.35\textwidth]{\FigPath/AUTSivers_COMPASS_x.pdf}
 \caption{\label{aut_f1t_jlab} Sivers asymmetry 
@@
 on respectively charged pion and hadron production from a proton target. 
-\AP{Notice that COMPASS points are lower than theoretical calculation, that may indicate evolution effects~\cite{Aybat:2011ta, Anselmino:2012aa}}.
-The $P_{hT}$--dependences of the data are well described, which
-confirms that the Gaussian model works also in this case.
+	{Notice that the COMPASS data points \ps{seem to be} below the 
+	theoretical curves which may indicate evolution 
+	effects~\cite{Aybat:2011ta,Anselmino:2012aa}}.
+\ps{We do not show here the description of} the $P_{hT}$--dependence of the 
+data {but it is well-described by the fit of \cite{Anselmino:2011gs}} 
+which confirms that the Gaussian model works also in this case.
 
@@
 
-The $F_{UT}^{\sin(\phi_h+\phi_S)}$ \AP{structure function} of the SIDIS cross section is due 
-to the convolution of the transversity distribution $h_1$ and the Collins 
+The $F_{UT}^{\sin(\phi_h+\phi_S)}$ structure function of the SIDIS cross section is 
+due to the convolution of the transversity distribution $h_1$ and the Collins 
 FF $H_1^\perp$. Transversity can in principle be accessed also as a PDF in
@@
 \cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,Bacchetta:2012ty,
-Radici:2015mwa,Radici:2018iag}. \AP{The first polarized Drell-Yan data were measured by COMPASS~\cite{Aghasyan:2017jop,Parsamyan:2018zju}.}
+Radici:2015mwa,Radici:2018iag}. The first polarized Drell-Yan data were 
+measured by COMPASS~\cite{Aghasyan:2017jop,Parsamyan:2018zju}.
 It describes the distribution of transversely polarized quarks
@@
 The structure function $F_{UU}^{\cos(2\phi_h)}$ arises from a convolution of
-the Collins fragmention function and the \AP{Boer-Mulders} TMD $h_{1}^{\perp q}$ which describes
+the Collins fragmention function and the Boer-Mulders TMD $h_{1}^{\perp q}$ 
+which describes
 the distribution of transversely polarized partons inside an unpolarized
@@
 Boer--Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$, which does not describe
-the data well, \AP{especially for COMPASS one can see that calculation and the data are of opposite signs}. In fact, it is suspected that this observable receives 
-a significant contribution from the Cahn effect \cite{Cahn:1978se}, a 
-term of higher-twist character of the type $\la\Phperp^2\ra/Q^2$ which 
-is not negligible in fixed-target experiments \cite{Schweitzer:2010tt}. 
-This contribution was estimated and corrected for in the phenomenological 
-works \cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa}, which was of
-importance to obtain a picture of the Boer--Mulders function undistorted 
+the data well, especially for COMPASS one can see that calculation and 
+data are of opposite signs. In fact, it is suspected that this observable 
+receives a significant contribution from the Cahn effect \cite{Cahn:1978se}, 
+a term of higher-twist character of the type $\la\Phperp^2\ra/Q^2$ which 
+is not negligible in fixed-target experiments \ps{as shown in
+phenomenological \cite{Schweitzer:2010tt} and model \cite{Cao:2018qqf} studies}.
+\ps{In the phenomenological works 
+\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} an attempt was
+made to estimate and correct for this contribution in order}
+to obtain a picture of the Boer--Mulders function undistorted 
 from Cahn effect. The point is that this substantial twist-4 contamination 
@@
 
-The pretzelosity TMD $h_{1T}^{\perp q}$ is the least known of the basis 
-functions. It is of interest as it allows one to measure the deviation 
+The pretzelosity TMD $h_{1T}^{\perp q}$ is the least known basis 
+function. It is of interest as it allows one to measure the deviation 
 of the nucleon spin density from spherical shape \cite{Miller:2007ae},
-as it is related to the only leading-twist SIDIS structure function where the 
+is related to the only leading-twist SIDIS structure function where the 
 small-$P_{hT}$ description in terms of TMDs and the large-$P_{hT}$ expansion 
-in perturbative QCD mismatch \cite{Bacchetta:2008xw}, and as it is the only
-TMD where a clear relation to quark orbital angular momentum
+in perturbative QCD mismatch \cite{Bacchetta:2008xw}, and is the only TMD 
+where a clear relation to quark orbital angular momentum
 could be established (albeit only within quark models)
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pip.pdf}  
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pim.pdf}
-\includegraphics[width=0.55\textwidth]{\FigPath/AUTPretzelosity_HERMES_x.pdf}
-
-\caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  
-	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2010se} 
-	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES \cite{Schnell:2010zza} in comparison to the best fit 
-	(whose 1-$\sigma$ uncertainty band is compatible with zero) 
-	from \cite{Lefky:2014eia}. For comparison the COMPASS plots
-	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 The preliminary COMPASS data \cite{Parsamyan:2010se} for $A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ and the preliminary HERMES data \cite{Schnell:2010zza} for 
@@
 to significantly improve our knowledge of this TMD.
+
+\ps{For comparison Fig.~\ref{altcos2phihphis} shows also the results
+from the quark-diquark model calculation of Ref.~\cite{Kotzinian:2008fe},
+and from the light-cone constituent quark model of Ref.~\cite{Boffi:2009sh}.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
+\centering
+\includegraphics[height=3.7cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf}%
+\includegraphics[height=3.7cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf}%
+\includegraphics[height=3.5cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}%
+
+\caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$  
+	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2010se} 
+	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES 
+	\cite{Schnell:2010zza} in comparison to the best fit 
+	(whose 1-$\sigma$ uncertainty band is compatible with zero) 
+	from \cite{Lefky:2014eia}. For comparison the COMPASS plots
+	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
+	}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
 
@@
 \label{Sec-6:twist-2-and-WW}
-\begin{figure}[htb]
+\begin{figure}[b]
 \centering
@@
 
-This asymmetry was measured at Jefferson Lab~\cite{Huang:2011bc}, COMPASS~\cite{
+This asymmetry was measured at JLab~\cite{Huang:2011bc}, COMPASS~\cite{
 Parsamyan:2007ju,Parsamyan:2018evv,Parsamyan:2015dfa} and HERMES~\cite{Pappalardo:2011cu,Pappalardo:2012zz} (for the latter two experiments only preliminary results are available so far).
@@
 \cite{Kotzinian:2006dw,Kotzinian:2008fe,Boffi:2009sh} are shown.
-Our results are also compatible with the Jefferson Lab data, which were 
+Our results are also compatible with the JLab data, which were 
 taken with a neutron ($^3$He) target \cite{Huang:2011bc} and have 
 larger statistical uncertainties than the preliminary COMPASS and HERMES data.
+
+\ps{\ \\ 
+PS: HERE IS ENOUGH SPACE TO 
+\begin{itemize}
+\item 	SHOW PLOTS WITH JLAB DATA \cite{Huang:2011bc} FOR PI$\pm$ FROM NEUTRON,
+\item	OR WRITE SOME MORE BLA, BLA, BLA. 
+\end{itemize}
+I HAVE NO INSPIRATION FOR BLA, BLA HERE. \\
+\red{SHOULD WE ADD THE JLAB HALL-A FIGURES?} \\ }
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
+\begin{figure}[h]
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip}
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim}
 	\caption{\label{cosphihphis} 
@@
 
+\newpage
+
 \subsection{\boldmath 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \quad
-\includegraphics[width=0.55\textwidth]{\FigPath/AULsin2phi_JLAB_x.pdf} 
-\vspace{-5mm}
-
+\includegraphics[height=3.5cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \ 
+\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_JLAB_x.pdf} 
 	\caption{\label{aul_jlab} 
@@
 	HERMES \cite{Airapetian:1999tv}, and $A_{UL}^{\sin(2\phi_h)}$
-	COMPASS \cite{Parsamyan:2015dfa} (left panel), and $A_{UL,  \langle y\rangle}^{\sin(2\phi_h)}$ 
-	Jefferson Lab \cite{Jawalkar:2017ube} (right panel). Results  
+	COMPASS \cite{Parsamyan:2015dfa} (left panel), 
+	and $A_{UL,  \langle y\rangle}^{\sin(2\phi_h)}$ 
+	JLab \cite{Jawalkar:2017ube} (right panel). Results  
 	from \cite{Avakian:2007mv} are also shown.}
@@
 studied at HERMES \cite{Airapetian:1999tv,Airapetian:2002mf}, COMPASS 
-\cite{Parsamyan:2018ovx}, and Jefferson Lab \cite{Avakian:2010ae,Jawalkar:2017ube}.
+\cite{Parsamyan:2018ovx}, and JLab \cite{Avakian:2010ae,Jawalkar:2017ube}.
 In Fig.~\ref{aul_jlab} proton data are shown for $\pi^\pm$ in the
-HERMES experiment which were measured with the 27.6 GeV positron
+HERMES experiment measured with the 27.6 GeV positron
 beam from the HERA polarized positron storage ring at DESY for 
 $1\,{\rm GeV}^2 < Q^2 < 15 \,{\rm GeV}^2$, $W > 2\,{\rm GeV}$,
-$0.023 < x < 0.4$ and $y < 0.85$. 
+$0.023 < x < 0.4$, $y < 0.85$. 
 The COMPASS data were taken in 2007 (160 GeV) and 2011 (200 GeV) and show 
@@
 $A_{UL}^{\sin(2\phi_h)}$  can be expected to be smaller than 
-$A_{LT}^{\cos(\phi_h -\phi_S)}$ discussed in the previous section,
+$A_{LT}^{\cos(\phi_h -\phi_S)}$ discussed in Sec.~\ref{Sec-6.1:FLTcosphi-phiS},
 even though both are leading twist. This is because 
 $F_{UL}^{\sin(2\phi_h)}$ is quadratic in the hadron transverse 
-momenta $P_{hT}\ll Q$, while $F_{LT}^{\cos(\phi_h -\phi_S)}$ is linear. 
+momenta $P_{hT}$, while $F_{LT}^{\cos(\phi_h -\phi_S)}$ is linear. 
 In addition, the former is proportional to the Collins function, 
@@
 of the size of $g_{1T}^{\perp(1)q}(x)$.
-The data support these expectations. HERMES and Jefferson Lab data are compatible
-with zero for this asymmetry. So are the preliminary COMPASS data except for the region
+The data support these expectations. HERMES and JLab data are compatible
+with zero for this asymmetry. So are the preliminary COMPASS data except 
+for the region
 $x>0.1$ for negative hadrons, where the trend of the data provides a first 
-encouraging confirmation for our results. The current data are compatible
+encouraging confirmation for our results. Thus current data are compatible
 with the WW-type approximation for $h_{1L}^{\perp(1)q}(x)$.
@@
 
-Indeed, data from Jefferson Lab, HERMES and COMPASS show a clearly non-zero 
+Indeed, data from JLab, HERMES and COMPASS show a clearly non-zero 
 asymmetry $A_{LU}^{\sin\phi_h} = F_{LU}^{\sin\phi_h}/F_{UU}$ of the order of 2\,$\%$ 
 \cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,
-Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz}, \AP{these 2\% come after $1/Q$ suppression. Unsuppressed effect at large $x$ at COMPASS would reach 10\% \cite{private}.} 
-On the one hand this is interesting: this observable provides a unique 
-opportunity to learn about the physics of $\bar{q}gq$-terms. On the other
-hand, this observable is beyond the applicability of the WW-type approximation
-and we cannot make a non-trivial prediction for this asymmetry.
+Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz} (\ps{which includes 
+the $1/Q$ factor intrinsic in twist-3 observables; without this factor 
+the asymmetry would} reach $10\%$ at large $x$ at COMPASS \cite{private}). 
+This observable provides a unique opportunity to learn about the 
+physics of $\bar{q}gq$-terms, but is beyond the applicability of 
+the WW-type approximation.
+% and we cannot make a non-trivial prediction for this asymmetry.
 
@@
 and relevant model studies have been reported 
-\cite{Efremov:2002qh,
-Lorce:2014hxa,
-Schweitzer:2003uy,Ohnishi:2003mf,Cebulla:2007ej,
-Efremov:2002ut,Afanasev:2003ze,Yuan:2003gu,Gamberg:2003pz,Metz:2004je,Afanasev:2006gw,Mao:2012dk,Mao:2014dva,Courtoy:2014xea,Yang:2016mxl}.
+\cite{Efremov:2002qh,Schweitzer:2003uy,Ohnishi:2003mf,Cebulla:2007ej,
+Efremov:2002ut,Afanasev:2003ze,Yuan:2003gu,Gamberg:2003pz,Metz:2004je,Afanasev:2006gw,Mao:2012dk,Mao:2013waa,Mao:2014dva,Lorce:2014hxa,Courtoy:2014ixa,Yang:2016mxl}.
 But more phenomenological work and dedicated studies on the basis of models 
@@
 
+\newpage
 \subsection{\boldmath Subleading-twist  $A_{LT}^{\cos\phi_S}$}
@@
 these steps is not relevant, but here it is. It is instructive to 
-discuss what the opposite order of these steps yields. 
-One may first plug in the WW-type approximation (\ref{Eq:WW-type-gT}) 
-in the convolution integral (\ref{Eq:WW-original1}) and then solve the
-convolution integral with Gaussian Ansatz. The result is an
-analytical expression which is bulkier than (\ref{Eq:FLTcosphiS-Gauss})  
-though it yields a numerically similar result. But there are 2 critical
-issues with that. First, the WW-type approximation (\ref{Eq:WW-type-gT}) 
-relates $g^{q}_{T}(x,\kperp^2)$ to $g^{\perp(1)q}_{1T}(x,\kperp^2)$ which
-(due to the weight $\kperp^2/(2M_N^2)$ in the (1)-moment) implies a kinematical 
-zero in $\kperp$ as $g^{q}_{T}(x, 0) = 0$,  which is not supported by model 
-calculations \cite{Avakian:2010br}. Second, the more economic (because 
+discuss what the opposite order of these steps \ps{would yield. 
+Using first the WW-type approximation (\ref{Eq:WW-type-gT}) 
+in the convolution integral (\ref{Eq:WW-original1}) and then 
+using the Gaussian Ansatz yields a bulkier}
+analytical expression than (\ref{Eq:FLTcosphiS-Gauss}) though 
+a numerically similar result. But there are two critical issues 
+with that. First, the WW-type approximation (\ref{Eq:WW-type-gT}) 
+relates $xg^{q}_{T}(x,\kperp^2)=g^{\perp(1)q}_{1T}(x,\kperp^2)$ which
+\ps{would imply} $g^{q}_{T}(x, \kperp^2) \to 0$ for $\kperp\to0$
+due to the weight $\kperp^2/(2M_N^2)$ in the (1)-moment,
+which is not supported by model calculations \cite{Avakian:2010br}. 
+Second, the more economic (because 
 less bulky) expression in (\ref{Eq:FLTcosphiS-Gauss}) automatically 
@@
 consistency of the scheme suggested in Sec.~\ref{Sec-4.4:evaluation}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
+\centering
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pip.pdf} 
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pim.pdf} 
+\caption{\label{altcosphis} Subleading-twist asymmetry $A_{LT}^{\cos\phi_S}$ 
+	as function of $x$ from scattering of 160 GeV
+	longitudinally polarized muons off a transversely polarized 
+	proton target \cite{Parsamyan:2013fia}.
+	}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 could come from JLab12 experiments.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htb!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphis_pip.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphis_pim.pdf} 
-\caption{\label{altcosphis} Subleading-twist $A_{LT}^{\cos\phi_S}$ 
-	  as functions of $x$ from scattering of 160 GeV
-	longitudinally polarized muons off a transversely polarized 
-	proton target \cite{Parsamyan:2013fia}.
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\ps{For further model studies of this asymmetry we refer to 
+Refs.~\cite{Mao:2014fma,Wang:2016dti}.}
 
@@
 	&=& -\frac{2M_N}{Q} x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\; 
-	b^{(2)}_{C}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\,
-	{ \cal G}(\Phperp)\, , \\
+	b^{(2)}_{C}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\!
+	{ \cal G}(\Phperp), \quad \\
 	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\la\Phperp\ra) 
@@
 in near future.
+
+\ps{For completeness Fig.~\ref{altcos2phihphis} shows results from a 
+quark-diquark model calculation were a more sizable asymmetry was predicted
+\cite{Kotzinian:2008fe}. Let us remark that the $A_{LT}^{\cos(2\phi_h -\phi_S)}$ 
+asymmetry was also studied in a different spectator model in 
+Ref.~\cite{Mao:2014fma} which predicts asymmetries of the same 
+sign but smaller magnitudes of ${\cal O}(1\,\%)$.}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[ht]
+\begin{figure}[h]
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pip}
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pim} 
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pip}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pim} 
 \caption{\label{altcos2phihphis} $A_{LT}^{\cos(2\phi_h - \phi_S)}$ 
-	as a function of $ x $ from a proton target in comparison to preliminary COMPASS data \cite{Parsamyan:2013fia}. The smallness
+	as a function of $ x $ from a proton target in comparison to 
+	preliminary COMPASS data \cite{Parsamyan:2013fia}. The smallness
 	of this asymmetry has two natural reasons: first, being twist-3
 	it is $M_N/Q$ suppressed; and second, it is proportional to
-	$P_{hT}^2$ with $P_{hT}\ll Q$ in TMD approach.}
+	$P_{hT}^2$  in TMD approach.}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
 
@@
 The asymmetry $A_{LL}^{\cos \phi_h}=F_{LL}^{\cos \phi_h}/F_{UU}$ predicted by the
-WW-type approximation in this case is compatible with preliminary COMPASS \cite{Parsamyan:2018ovx} (see Fig.~\ref{allcosphi_jlab}) and HERMES data.
-We remark that previously this asymmetry was studied in
-\cite{Anselmino:2006yc} and more recently in \cite{Mao:2016hdi}.
+WW-type approximation in this case is compatible with preliminary COMPASS 
+\cite{Parsamyan:2018ovx} (see Fig.~\ref{allcosphi_jlab}) and HERMES data.
+We remark that previously this asymmetry was studied in basically
+WW-type approximation in \cite{Anselmino:2006yc} and more recently 
+also in the model study \cite{Mao:2016hdi}. The predictions from
+both works are included in Fig.~\ref{allcosphi_jlab} for 
+comparison.
+
+\
 
@@
 \centering
-%\vspace{1cm}
+\vspace{5mm}
 \includegraphics[width=0.9\textwidth]{\FigPath/A_LL_Pr0711_Zgt02.pdf}
@@
 
+%\newpage
 \subsection{\boldmath Subleading-twist $A_{UL}^{\sin\phi_h}$ }
 \label{Sec-7.4:FULsinphi}
+
+\ps{This was historically the first measurement of a single spin 
+asymmetry in SIDIS, by HERMES \cite{Airapetian:1999tv,Airapetian:2001eg},
+and consequently subject to numerous phenomenological and model studies
+\cite{DeSanctis:2000fh,Oganessian:2000um,Efremov:2001ia,Efremov:2002td,
+Efremov:2002sd,Ma:2001ie,Ma:2002ns,Schweitzer:2003yr}. A more recent
+smodel study was reported in \cite{Lu:2014fva}.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure}[b]
 \centering
@@
 The asymmetries $A_{UL}^{\sin\phi_h}=F_{UL}^{\sin\phi_h}/F_{UU}$ are compared
-to HERMES, Jefferson Lab, and preliminary COMPASS data in Fig.~\ref{aulsinphi_jlab}.
-The WW-type approximation reproduces the positive sign of the asymmetry
-seen consistently at HERMES and COMPASS for $\pi^+$ and positive hadrons
-but underestimates its magnitude. The results for negative pions and 
-hadrons at HERMES and COMPASS \cite{Parsamyan:2018ovx} are compatible. An important test for this
-asymmetry is provided by neutral pions where in WW-type approximation
-the contributions of Collins fragmentation function largely cancel.
-The WW-type approximation is not able to explain the large effect
-observed at HERMES and Jefferson Lab for $\pi^0$ in the large--$x$ region 
+to HERMES, JLab, and preliminary COMPASS data in Fig.~\ref{aulsinphi_jlab}.
+The WW-type approximation \ps{seems not incompatible with data for negative 
+pions and hadrons, but understimates the magnitude of the asymmetry for
+positive pions and hadrons at HERMES and COMPASS. For neutral pions the 
+approximation predicts a negligibly small effect (due to cancelling 
+contributions from favored und unfavored Collins fragmentation function)
+and is} not able to explain the large effect
+observed at HERMES and JLab for $\pi^0$ in the large--$x$ region 
 $0.1< x < 0.5$ in Fig.~\ref{aulsinphi_jlab}. 
-Overall, the WW-type approximation is not adequate to catch the
-flavor dependence of this asymmetry. This indicates that here the 
+%Overall, the WW-type approximation is not adequate to catch the
+%flavor dependence of this asymmetry. 
+This indicates that in this asymmetry the 
 tilde-terms are not negligible, and have a characteristic flavor 
@@
 
-\begin{figure}[h!]
+The final result in Eq.~(\ref{Eq:FUTsinphiS-final}) is the consistent 
+result for $F_{UT}^{\sin\phi_S}(x,z)$ in WW-type 
+approximation, see Eq.~(\ref{Eq:FUT-collinear}). Our prediction is 
+therefore $A_{UT}^{\sin\phi_S}(x)=0$. Preliminary 
+COMPASS \cite{Parsamyan:2013fia} (Fig.~\ref{autsinphis} top) and 
+HERMES \cite{Schnell:2010zza} (Fig.~\ref{autsinphis} bottom) data 
+indicate that at $x\gtrsim 0.1$ the signal is clearly non-zero and 
+thus inconsistent with this WW-type prediction. \ps{In order to
+describe the data it is therefore necessary to explicitly model
+the involved tilde-functions. For a recent model study we refer
+to \cite{Mao:2014aoa}.}
+
+\begin{figure}[h]
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sinphis_pip.pdf}
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sinphis_pim.pdf}
-\includegraphics[width=0.55\textwidth]{\FigPath/AUTsinphiS_HERMES_x.pdf}
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pip.pdf}
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pim.pdf}
+\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_HERMES_x.pdf}
 \caption{\label{autsinphis} 
@@
 	is predicted to vanish in the WW-type approximation, in 
-	comparison to preliminary COMPASS~\cite{Parsamyan:2013fia} and HERMES data \cite{Schnell:2010zza}.}
+	comparison to preliminary COMPASS~\cite{Parsamyan:2013fia} 
+	and HERMES data \cite{Schnell:2010zza}.}
 \end{figure}
 
-The final result in Eq.~(\ref{Eq:FUTsinphiS-final}) is the consistent 
-result for the structure function $F_{UT}^{\sin\phi_S}(x,z)$ in WW-type 
-approximation, see Eq.~(\ref{Eq:FUT-collinear}). Our prediction is 
-therefore $A_{UT}^{\sin\phi_S}(x)=0$. 
-Preliminary COMPASS \cite{Parsamyan:2013fia}
- (Fig.~\ref{autsinphis} top) and 
-HERMES \cite{Schnell:2010zza} (Fig.~\ref{autsinphis} bottom) data 
-indicate that at $x\gtrsim 0.1$ the signal is clearly non-zero and 
-thus inconsistent with this WW-type prediction.
+\newpage
+\subsection{\boldmath Subleading-twist  $A_{UT}^{\sin(2\phi_h-\phi_S)}$ }
+\label{Sec-7.8:FUTsin2phi-phiS}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure}[b]
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sin2phihphis_pip}
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sin2phihphis_pip}
-\includegraphics[width=0.55\textwidth]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf}
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip}%
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip}%
+\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf}
 \caption{\label{autsin2phihphis} 
-	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison to preliminary COMPASS data~\cite{Parsamyan:2013fia}, and 	
+	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison 
+	to preliminary COMPASS data~\cite{Parsamyan:2013fia}, and 	
 	similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to  
@@
 
-\subsection{\boldmath Subleading-twist  $A_{UT}^{\sin(2\phi_h-\phi_S)}$ }
-\label{Sec-7.8:FUTsin2phi-phiS}
-
-Also in this asymmetry we end up with more than one surviving 
-contribution in our treatment. We assume Gaussian Ansatz for 
+Also in this asymmetry we end up with more than one contribution 
+\ps{surviving the WW-type approximation}. We assume Gaussian Ansatz for 
 $f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ 
@@
 $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_{1T}^\perp}$
-and $\la\kperp^2\ra_{f_T^\perp}=\la\kperp^2\ra_{f_{1T}^\perp}$ and obtain
+and $\la\kperp^2\ra_{f_T^\perp}=\la\kperp^2\ra_{f_{1T}^\perp}$. The obtained
+expressions are given by
 \begin{subequations}\begin{alignat}{1}
@@
 with a zero effect within uncertainties.
-
+\ps{For comparison Fig.~\ref{altcos2phihphis} shows also the predictions
+from the quark-diquark model calculation of Ref.~\cite{Kotzinian:2008fe}. 
+More recently the $A_{UT}^{\sin(2\phi_h -\phi_S)}$ was also studied in the
+model approach of Ref.~\cite{Mao:2014aoa}.}
+
+\newpage
 \subsection{\boldmath Subleading-twist  $A_{UU}^{\cos\phi_h}$ }
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_HERMES_x.pdf}
-\caption{\label{auucosphi_jlab} 
-	Left panel: asymmetry $A_{UU}^{\cos\phi_h}$ for positive and negative 
-	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}. Right 
-	panel: the corresponding $A_{UU, \langle y \rangle}^{\cos\phi_h}$ for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.}
-\end{figure}
-
 The asymmetries $A_{UU}^{\cos\phi_h}$ were measured by
-EMC \cite{Aubert:1983cz}, at Jefferson Lab \cite{Osipenko:2008aa,Mkrtchyan:2007sr}, 
+EMC \cite{Aubert:1983cz}, at JLab \cite{Osipenko:2008aa,Mkrtchyan:2007sr}, 
 HERMES \cite{Airapetian:2012yg}, and COMPASS \cite{Adolph:2014pwc}.
@@
 power corrections.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.35\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf} 
+\includegraphics[width=0.35\textwidth]{\FigPath/AUUcosphi_HERMES_x.pdf}
+\caption{\label{auucosphi_jlab} 
+	Left panel: asymmetry $A_{UU}^{\cos\phi_h}$ for positive and negative 
+	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}. Right 
+	panel: the corresponding $A_{UU, \langle y \rangle}^{\cos\phi_h}$ for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 preliminary (and soon to be published) SIDIS data
-from HERMES, COMPASS, and Jefferson Lab.
+from HERMES, COMPASS, and JLab.
 
@@
 the very first non-zero target single-spin asymmetry measured in SIDIS
-($F_{UL}^{\sin\phi_h}$), and \AP{and the beam-spin asymmetry } ($F_{LU}^{\sin\phi_h}$).
+($F_{UL}^{\sin\phi_h}$), and {and the beam-spin asymmetry} ($F_{LU}^{\sin\phi_h}$).
 The WW-type prediction for $F_{UU}^{\cos(\phi_h)}$ tends to overshoot
@@
 $N_{BM}^u=2.1\pm0.1$ & $N_{BM}^d=$&$-1.111\pm0.001$   \\
-Fixed & parameters: &  \\
 $N_u=0.35$ & $\alpha_u=0.73$ & $\beta_u=3.46$ \\
@@
 \end{tabular}
-\caption{Fitted parameters of Boer-Mulders quark distributions. Values are from Ref.~\cite{Barone:2009hw}.}
+\caption{Fitted parameters \ps{(those with error bars)}
+and fixed parameters \ps{(those without error bars)}
+of the Boer-Mulders quark distributions from Ref.~\cite{Barone:2009hw}.}
 \label{fitparbm}
@@
 
-  We use Eq.~(\ref{eq:moments}) to calculate the second moment of $ h_{1T}^{\perp a}(x,\kperp^2)$
-of Eq.~(\ref{eq:h1Tperp}) and obtain:
-\be
-h_{1T}^{\perp (2) a}(x) =  \frac{h^{\perp a}_{1T}(x) \avkperp_{h_{1T}^\perp}^3}{2 M^2 M_{TT}^2 \avkperp} \, .
-\ee
-
-We can rewrite parametrization of pretzelosity   functions as
-
-\ba
-h_{1T}^{\perp q}(x,\kperp^2) =  h_{1T}^{\perp (2) q}(x)   \frac{2 M^4}{\pi \avkperp_{h_{1T}^\perp}^3} e^{-\kperp^2/{\avkperp_{h_{1T}^\perp}}}
-\label{pretzelosity_new} \ .
-\ea
-
 %
-\begin{table}[htb]
+\begin{table}[b]
 \centering
@@
 %
+
+We use Eq.~(\ref{eq:moments}) to obtain for the second moment 
+of $ h_{1T}^{\perp a}(x,\kperp^2)$ in (\ref{eq:h1Tperp}) the result
+shown below, and use it to rewrite parametrization of pretzelosity 
+functions as
+\ba
+h_{1T}^{\perp (2) a}(x) =  \frac{h^{\perp a}_{1T}(x) \avkperp_{h_{1T}^\perp}^3}{2 M^2 M_{TT}^2 \avkperp} \, , \quad 
+h_{1T}^{\perp q}(x,\kperp^2) =  h_{1T}^{\perp (2) q}(x)   \frac{2 M^4}{\pi \avkperp_{h_{1T}^\perp}^3} e^{-\kperp^2/{\avkperp_{h_{1T}^\perp}}}
+\label{pretzelosity_new} \ .
+\ea
 

### 2018-11-29 tex/test-WW-type-01b.tex
new tex

@@
 
-The preliminary COMPASS data \cite{Parsamyan:2010se} for $A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ and the preliminary HERMES data \cite{Schnell:2010zza} for 
+The preliminary COMPASS data \cite{Parsamyan:2013fia} for $A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ and the preliminary HERMES data \cite{Schnell:2010zza} for
 $A_{UT, \langle y \rangle}^{\sin(3 \phi_h - \phi_S)}=(1-y)F_{UT}^{\sin(3 \phi_h - \phi_S)}/((1-y + y^2/2)F_{UU})$
@@
 \caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$
-	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2010se} 
+	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2013fia}
 	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES
@@
 This asymmetry was measured at JLab~\cite{Huang:2011bc}, COMPASS~\cite{
-Parsamyan:2007ju,Parsamyan:2018evv,Parsamyan:2015dfa} and HERMES~\cite{Pappalardo:2011cu,Pappalardo:2012zz} (for the latter two experiments only preliminary results are available so far).
+Parsamyan:2007ju,Parsamyan:2015dfa,Parsamyan:2018evv} and HERMES~\cite{Pappalardo:2011cu,Pappalardo:2012zz} (for the latter two experiments only preliminary results are available so far).
  Fig.~\ref{cosphihphis}
@@
 	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$
-	 in comparison to the preliminary COMPASS data \cite{Parsamyan:2018ovx}.
+	 in comparison to the preliminary COMPASS data \cite{Parsamyan:2013fia}.
 	}
@@
 	HERMES \cite{Airapetian:1999tv}, and $A_{UL}^{\sin(2\phi_h)}$
-	COMPASS \cite{Parsamyan:2015dfa} (left panel), 
+	COMPASS \cite{Parsamyan:2018ovx,Parsamyan:2018evv} (left panel),
 	and $A_{UL,  \langle y\rangle}^{\sin(2\phi_h)}$
@@
 studied at HERMES \cite{Airapetian:1999tv,Airapetian:2002mf}, COMPASS
-\cite{Parsamyan:2018ovx}, and JLab \cite{Avakian:2010ae,Jawalkar:2017ube}.
+\cite{Parsamyan:2018ovx,Parsamyan:2018evv}, and JLab \cite{Avakian:2010ae,Jawalkar:2017ube}.
 In Fig.~\ref{aul_jlab} proton data are shown for $\pi^\pm$ in the
@@
 WW-type approximation in this case is compatible with preliminary COMPASS
-\cite{Parsamyan:2018ovx} (see Fig.~\ref{allcosphi_jlab}) and HERMES data.
+\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (see Fig.~\ref{allcosphi_jlab}) and HERMES \cite{Airapetian:2018rlq} data.
 We remark that previously this asymmetry was studied in basically
@@
 	comparison to the preliminary COMPASS data
-	\cite{Parsamyan:2018ovx}. }
+	\cite{Parsamyan:2018ovx,Parsamyan:2018evv}. }
 \end{figure}
@@
 	and JLab (red) \cite{Jawalkar:2017ube}.
-	Lower panel: preliminary $h^\pm$ COMPASS data \cite{Parsamyan:2018ovx}.}
+	Lower panel: preliminary $h^\pm$ COMPASS data \cite{Parsamyan:2018ovx,Parsamyan:2018evv}.}
 \end{figure}

### 2018-11-30 tex/test-WW-type-01a.tex
tex

--- 2018-09-04 tex/test-WW-type-00z.tex
@@
 Electron-Ion Collider. The results of this paper can be readily used for 
-phenomenology and for event generators, and will help to improve our 
-understanding of the TMD theory beyond leading twist.
+phenomenology and for event generators, and will help \AP{to improve the description of
+semi-inclusive deep-inelastic processes in terms of transverse momentum
+dependent parton distribution functions and fragmentation functions
+beyond the leading twist}.
 } 
@@
 NLO corrections within the TMD framework \cite{Ma:2013aca}, and  
-phenomenological fits with evolution \cite{Aybat:2011ta,Kang:2015msa}.
+phenomenological fits with evolution \cite{Aybat:2011ta,Kang:2015msa}. \AP{In particular, the studies of matching of collinear and TMD quantities was performed 
+at leading twist-2 level at NLO and NNLO in ~\cite{Gutierrez-Reyes:2017glx} and ~\cite{Gutierrez-Reyes:2018qez} accordingly, and it was shown that evolution of higher twist operators is generically different from the leading twist ones.} \AP{The Wandzura--Wilczek approximation has been used recently for for TMD Sivers, Boer-Mulders and worm-gear functions observables in Ref.~\cite{Scimemi:2018mmi} to connect TMDs and higher twist collinear matrix elements}.
 In contrast to this, the theory for subleading-twist TMD observables is 

### 2019-01-07 tex/test-WW-type-01c.tex
new tex

--- 2018-11-29 tex/test-WW-type-01b.tex
@@
 
-\preprint{\red{version ``01b''}; 14 Sep 2018; JLAB-THY-18-2775}
+\preprint{\red{version ``01c''}; 7 Jan 2019; JLAB-THY-18-2775}
 
@@
 
-\ps{On the theoretical side it is also important to note that the
+On the theoretical side it is also important to note that the
 theory for subleading-twist TMD observables is only poorly developed
@@
 Bacchetta:2006tn} which may not be free of doubts
-\cite{Metz:2004je,Gamberg:2006ru}.}
+\cite{Metz:2004je,Gamberg:2006ru}.
 
@@
 pertinent $\bar{q}gq$--terms are small or (ii) why they are sizable,
-\ps{depending on the outcome of the experiments.}
+depending on the outcome of the experiments.
 In either case our results will deepen the understanding of
@@
 \cite{Aybat:2011zv,Aybat:2011ge,Echevarria:2014xaa,Collins:2014jpa},
-%\ps{(PS: \cite{Collins:2014jpa} ADDED)}
-\ps{next-to-leading order} corrections within the TMD framework
+next-to-leading order corrections within the TMD framework
 \cite{Ma:2013aca}, and phenomenological fits with evolution
 \cite{Aybat:2011ta,Kang:2015msa}.
-\ps{The matching of twist-2 collinear and TMD quantities was
+The matching of twist-2 collinear and TMD quantities was
 studied to next-to-leading and next-to-next-to-leading order
-\cite{Gutierrez-Reyes:2017glx,Gutierrez-Reyes:2018qez}.}
-%
-% ``and it was shown that evolution of higher twist operators is
-%   generically different from the leading twist ones.''
-%
-% PS: this comment (added by AP) is too trivial. OF COURSE is the
-% evolution of twist-3 DIFFERENT from twist-2. Well known from colinear
-% case! So no surprize it is different for TMDs. Not sure which point
-% you would like to make. I propose to skip, or to make this point
-% more specific.
-% Remark: in early 1990s Braun-et-al derived evolution equations for
-% \tilde{g}_T(x), later Belitsky+Mueller derived evolution equations
-% for \tilde{h}_L, \tilde{e}_L. Highly complex evolution pattern
-% (Mellin moments mix under evolution! Simple DGLAP only in large-Nc limit).
-% People know this, do not expect any better for TMDs.
-%
-\ps{The WW approximation has been used recently in Ref.~\cite{Scimemi:2018mmi}
+\cite{Gutierrez-Reyes:2017glx,Gutierrez-Reyes:2018qez}.
+The WW approximation has been used recently in Ref.~\cite{Scimemi:2018mmi}
 to connect the twist-2 TMDs $f_{1T}^\perp$, $g_{1T}^\perp$, $h_{1}^\perp$,
-$h_{1L}^\perp$ to certain higher twist collinear matrix elements.}
+$h_{1L}^\perp$ to certain higher twist collinear matrix elements.
 
@@
 	and analog for other scalar products of {\it transverse} vectors.
-	\ps{Notice that in our notation transverse vector
+	Notice that in our notation transverse vector
 	are never understood as four-vectors such that
-	${\bfkperp^2}_{\rm our} \equiv {\kperp^2}_{\rm our}$.}},
+	${\bfkperp^2}_{\rm our} \equiv {\kperp^2}_{\rm our}$.},
 where the terms on the left-hand-side are twist-3, those on the
@@
 WW-type approximations (\ref{Eq:WW-type-gT},~\ref{Eq:WW-type-6}).
-\ps{The resulting relations are the only WW-type relations applicable
-to twist-2 TMDs and are given by the following expressions}
+The resulting relations are the only WW-type relations applicable
+to twist-2 TMDs and are given by the following expressions
 \cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv},
@@
 \ea
-\ps{Here the} %with the understanding that
+Here the 
 negative $x$ refer to antiquark distributions
@@
 not give up at this point and take a look at the lattice observables of
-Ref.~\cite{Musch:2010ka} \ps{where} TMDs \ps{were} obtained from amplitudes
+Ref.~\cite{Musch:2010ka} where TMDs were obtained from amplitudes
 $\tilde A_i(l^2,\ldots)$ in Fourier space, where $\bfkperp$ is encoded
@@
    Notice that SIDIS alone is not sufficient to determine
-   the \ps{8 basis functions uniquely which} appear in 6 SIDIS
+   the 8 basis functions uniquely which appear in 6 SIDIS
    leading-twist structure functions. It is crucial to take
@@
    $e^+e^-$ annihilation, which are indispensable for the determination
-   of $f_1^a$, $D_1^a$,~\ps{$H_1^{\perp a}$}).}
+   of $f_1^a$, $D_1^a$, $H_1^{\perp a}$).}
 These basis functions allow us to describe, in WW-type approximation,
@@
 twist-2 collinear functions. All collinear functions are calculated at
-$Q^2 = 2.4$ GeV$^2$ \ps{with} $f_1^a(x)$ from \cite{Martin:2009iq},
+$Q^2 = 2.4$ GeV$^2$ with $f_1^a(x)$ from \cite{Martin:2009iq},
 $g_1^a(x)$ from \cite{Gluck:1998xa}, $D_1^a(z)$ from
@@
 on respectively charged pion and hadron production from a proton target.
-	{Notice that the COMPASS data points \ps{seem to be} below the
+	Notice that the COMPASS data points seem to be below the
 	theoretical curves which may indicate evolution
-	effects~\cite{Aybat:2011ta,Anselmino:2012aa}}.
-\ps{We do not show here the description of} the $P_{hT}$--dependence of the
-data {but it is well-described by the fit of \cite{Anselmino:2011gs}}
+	effects~\cite{Aybat:2011ta,Anselmino:2012aa}.
+We do not show here the description of the $P_{hT}$--dependence of the
+data but it is well-described by the fit of \cite{Anselmino:2011gs}
 which confirms that the Gaussian model works also in this case.
@@
 a term of higher-twist character of the type $\la\Phperp^2\ra/Q^2$ which
-is not negligible in fixed-target experiments \ps{as shown in
-phenomenological \cite{Schweitzer:2010tt} and model \cite{Cao:2018qqf} studies}.
-\ps{In the phenomenological works
+is not negligible in fixed-target experiments as shown in
+phenomenological \cite{Schweitzer:2010tt} and model \cite{Cao:2018qqf} studies.
+In the phenomenological works
 \cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} an attempt was
-made to estimate and correct for this contribution in order}
+made to estimate and correct for this contribution in order
 to obtain a picture of the Boer--Mulders function undistorted
@@
 
-\ps{For comparison Fig.~\ref{altcos2phihphis} shows also the results
+For comparison Fig.~\ref{altcos2phihphis} shows also the results
 from the quark-diquark model calculation of Ref.~\cite{Kotzinian:2008fe},
-and from the light-cone constituent quark model of Ref.~\cite{Boffi:2009sh}.}
+and from the light-cone constituent quark model of Ref.~\cite{Boffi:2009sh}.
 
@@
 \centering
-\includegraphics[height=3.7cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf}%
-\includegraphics[height=3.7cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf}%
-\includegraphics[height=3.5cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}%
-
+\includegraphics[height=3.7cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf} {\tiny (a)}%
+\includegraphics[height=3.7cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf} {\tiny (b)}%
+
+\includegraphics[height=3.3cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}{\tiny (c)}%
+\includegraphics[height=3.5cm]{\FigPath/AUTPretzelosity_x.pdf}{\tiny (d)}%
 \caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$
-	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2013fia}
+	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2013fia} (a,b)
 	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES
-	\cite{Schnell:2010zza} in comparison to the best fit
-	(whose 1-$\sigma$ uncertainty band is compatible with zero)
-	from \cite{Lefky:2014eia}. For comparison the COMPASS plots
+	\cite{Schnell:2010zza}(c) in comparison to the best fit from \cite{Lefky:2014eia}
+	(whose 1-$\sigma$ uncertainty band is compatible with zero), and our calculation for COMPASS kinematics (d). For comparison the COMPASS plots
 	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
@@
 
-\ps{\ \\
-PS: HERE IS ENOUGH SPACE TO
-\begin{itemize}
-\item 	SHOW PLOTS WITH JLAB DATA \cite{Huang:2011bc} FOR PI$\pm$ FROM NEUTRON,
-\item	OR WRITE SOME MORE BLA, BLA, BLA.
-\end{itemize}
-I HAVE NO INSPIRATION FOR BLA, BLA HERE. \\
-\red{SHOULD WE ADD THE JLAB HALL-A FIGURES?} \\ }
+%\ps{\ \\
+%PS: HERE IS ENOUGH SPACE TO
+%\begin{itemize}
+%\item 	SHOW PLOTS WITH JLAB DATA \cite{Huang:2011bc} FOR PI$\pm$ FROM NEUTRON,
+%\item	OR WRITE SOME MORE BLA, BLA, BLA.
+%\end{itemize}
+%I HAVE NO INSPIRATION FOR BLA, BLA HERE. \\
+%\red{SHOULD WE ADD THE JLAB HALL-A FIGURES?} \\ }
 
@@
 \centering
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip}
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip} {\tiny (a)}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim} {\tiny (b)}
+\includegraphics[width=0.37\textwidth]{\FigPath/ALT_COMPASS_x.pdf} {\tiny (c)}
 	\caption{\label{cosphihphis}
 	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$
-	 in comparison to the preliminary COMPASS data \cite{Parsamyan:2013fia}.
+	 in comparison to the preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b), and our calculation for COMPASS kinematics (c) .
 	}
@@
 \centering
-\includegraphics[height=3.5cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \
-\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_JLAB_x.pdf}
+\includegraphics[height=3.5cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} {\tiny (a)}
+
+\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_JLAB_x.pdf} {\tiny (b)}
+\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_COMPASS_x} {\tiny (c)}
 	\caption{\label{aul_jlab}
@@
 	HERMES \cite{Airapetian:1999tv}, and $A_{UL}^{\sin(2\phi_h)}$
-	COMPASS \cite{Parsamyan:2018ovx,Parsamyan:2018evv} (left panel),
+	COMPASS \cite{Parsamyan:2018ovx,Parsamyan:2018evv} (a),
 	and $A_{UL,  \langle y\rangle}^{\sin(2\phi_h)}$
-	JLab \cite{Jawalkar:2017ube} (right panel). Results
+	JLab \cite{Jawalkar:2017ube} (b),  and our calculation for COMPASS kinematics (c). Results
 	from \cite{Avakian:2007mv} are also shown.}
@@
 \cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,
-Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz} (\ps{which includes
+Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz} (which includes
 the $1/Q$ factor intrinsic in twist-3 observables; without this factor
-the asymmetry would} reach $10\%$ at large $x$ at COMPASS \cite{private}).
+the asymmetry would reach $10\%$ at large $x$ at COMPASS).
 This observable provides a unique opportunity to learn about the
@@
 the WW-type approximation.
-% and we cannot make a non-trivial prediction for this asymmetry.
 
@@
 these steps is not relevant, but here it is. It is instructive to
-discuss what the opposite order of these steps \ps{would yield.
+discuss what the opposite order of these steps would yield.
 Using first the WW-type approximation (\ref{Eq:WW-type-gT})
 in the convolution integral (\ref{Eq:WW-original1}) and then
-using the Gaussian Ansatz yields a bulkier}
+using the Gaussian Ansatz yields a bulkier
 analytical expression than (\ref{Eq:FLTcosphiS-Gauss}) though
@@
 relates $xg^{q}_{T}(x,\kperp^2)=g^{\perp(1)q}_{1T}(x,\kperp^2)$ which
-\ps{would imply} $g^{q}_{T}(x, \kperp^2) \to 0$ for $\kperp\to0$
+would imply $g^{q}_{T}(x, \kperp^2) \to 0$ for $\kperp\to0$
 due to the weight $\kperp^2/(2M_N^2)$ in the (1)-moment,
@@
 \centering
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pip.pdf}
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pim.pdf}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pip.pdf} {\tiny (a)}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pim.pdf} {\tiny (b)}
+\includegraphics[width=0.35\textwidth]{\FigPath/ALTcosPhi_COMPASS_x} {\tiny (c)}
 \caption{\label{altcosphis} Subleading-twist asymmetry $A_{LT}^{\cos\phi_S}$
@@
 	longitudinally polarized muons off a transversely polarized
-	proton target \cite{Parsamyan:2013fia}.
+	proton target \cite{Parsamyan:2013fia} (a,b),  and our calculation for COMPASS kinematics (c).
 	}
@@
 could come from JLab12 experiments.
-\ps{For further model studies of this asymmetry we refer to
-Refs.~\cite{Mao:2014fma,Wang:2016dti}.}
+For further model studies of this asymmetry we refer to
+Refs.~\cite{Mao:2014fma,Wang:2016dti}.
 
@@
 
-\ps{For completeness Fig.~\ref{altcos2phihphis} shows results from a
+For completeness Fig.~\ref{altcos2phihphis} shows results from a
 quark-diquark model calculation were a more sizable asymmetry was predicted
@@
 Ref.~\cite{Mao:2014fma} which predicts asymmetries of the same
-sign but smaller magnitudes of ${\cal O}(1\,\%)$.}
+sign but smaller magnitudes of ${\cal O}(1\,\%)$.
 
@@
 \centering
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pip}
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pim}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pip} {\tiny (a)}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pim} {\tiny (b)}
+\includegraphics[width=0.35\textwidth]{\FigPath/ALTcos2PhiminusPhiS_COMPASS_x} {\tiny (c)}
 \caption{\label{altcos2phihphis} $A_{LT}^{\cos(2\phi_h - \phi_S)}$
 	as a function of $ x $ from a proton target in comparison to
-	preliminary COMPASS data \cite{Parsamyan:2013fia}. The smallness
+	preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b), and our calculation for COMPASS kinematics (c). The smallness
 	of this asymmetry has two natural reasons: first, being twist-3
@@
 \vspace{5mm}
-\includegraphics[width=0.9\textwidth]{\FigPath/A_LL_Pr0711_Zgt02.pdf}
+\includegraphics[width=0.7\textwidth]{\FigPath/A_LL_Pr0711_Zgt02.pdf} {\tiny (a)}
+\includegraphics[width=0.35\textwidth]{\FigPath/ALLcosphi_COMPASS_x} {\tiny (b)}
 	\caption{\label{allcosphi_jlab} $A_{LL}^{\cos(\phi_h)}$
@@
 	comparison to the preliminary COMPASS data
-	\cite{Parsamyan:2018ovx,Parsamyan:2018evv}. }
+	\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (a), and our calculation for COMPASS kinematics (b). }
 \end{figure}
@@
 
-\ps{This was historically the first measurement of a single spin
+This was historically the first measurement of a single spin
 asymmetry in SIDIS, by HERMES \cite{Airapetian:1999tv,Airapetian:2001eg},
@@
 Efremov:2002sd,Ma:2001ie,Ma:2002ns,Schweitzer:2003yr}. A more recent
-smodel study was reported in \cite{Lu:2014fva}.}
+smodel study was reported in \cite{Lu:2014fva}.
 
@@
 to HERMES, JLab, and preliminary COMPASS data in Fig.~\ref{aulsinphi_jlab}.
-The WW-type approximation \ps{seems not incompatible with data for negative
+The WW-type approximation seems not incompatible with data for negative
 pions and hadrons, but understimates the magnitude of the asymmetry for
@@
 contributions from favored und unfavored Collins fragmentation function)
-and is} not able to explain the large effect
+and is not able to explain the large effect
 observed at HERMES and JLab for $\pi^0$ in the large--$x$ region
 $0.1< x < 0.5$ in Fig.~\ref{aulsinphi_jlab}.
-%Overall, the WW-type approximation is not adequate to catch the
-%flavor dependence of this asymmetry.
 This indicates that in this asymmetry the
@@
 indicate that at $x\gtrsim 0.1$ the signal is clearly non-zero and
-thus inconsistent with this WW-type prediction. \ps{In order to
+thus inconsistent with this WW-type prediction. In order to
 describe the data it is therefore necessary to explicitly model
 the involved tilde-functions. For a recent model study we refer
-to \cite{Mao:2014aoa}.}
+to \cite{Mao:2014aoa}.
 
@@
 \centering
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pip.pdf}
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pim.pdf}
-\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_HERMES_x.pdf}
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pip.pdf}  {\tiny (a)}
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pim.pdf}  {\tiny (b)}
+\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_HERMES_x.pdf}  {\tiny (c)}
+\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_COMPASS_x}  {\tiny (d)}
 \caption{\label{autsinphis}
@@
 	is predicted to vanish in the WW-type approximation, in
-	comparison to preliminary COMPASS~\cite{Parsamyan:2013fia}
-	and HERMES data \cite{Schnell:2010zza}.}
+	comparison to preliminary COMPASS~\cite{Parsamyan:2013fia} (a,b) 
+	and HERMES data \cite{Schnell:2010zza} (c), and our calculation for COMPASS kinematics (d).}
 \end{figure}
@@
 \centering
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip}%
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip}%
-\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf}
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (a)}%
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (b)}%
+\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf} {\tiny (c)}
+\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_COMPASS_x} {\tiny (d)}
 \caption{\label{autsin2phihphis}
 	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison
-	to preliminary COMPASS data~\cite{Parsamyan:2013fia}, and 	
+	to preliminary COMPASS data~\cite{Parsamyan:2013fia} (a,b), and 	
 	similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to
-	preliminary HERMES data~\cite{Schnell:2010zza}.
+	preliminary HERMES data~\cite{Schnell:2010zza} (c), and our calculation for COMPASS kinematics (d).
 	}
@@
 Also in this asymmetry we end up with more than one contribution
-\ps{surviving the WW-type approximation}. We assume Gaussian Ansatz for
+surviving the WW-type approximation. We assume Gaussian Ansatz for
 $f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$
@@
 with a zero effect within uncertainties.
-\ps{For comparison Fig.~\ref{altcos2phihphis} shows also the predictions
+For comparison Fig.~\ref{altcos2phihphis} shows also the predictions
 from the quark-diquark model calculation of Ref.~\cite{Kotzinian:2008fe}.
 More recently the $A_{UT}^{\sin(2\phi_h -\phi_S)}$ was also studied in the
-model approach of Ref.~\cite{Mao:2014aoa}.}
+model approach of Ref.~\cite{Mao:2014aoa}.
 
@@
 \end{tabular}
-\caption{Fitted parameters \ps{(those with error bars)}
-and fixed parameters \ps{(those without error bars)}
+\caption{Fitted parameters (those with error bars)
+and fixed parameters (those without error bars)
 of the Boer-Mulders quark distributions from Ref.~\cite{Barone:2009hw}.}

### 2019-01-07 tex/test-WW-type-01c.tex
new tex

@@
 \centering
-\includegraphics[height=3.7cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf} {\tiny (a)}%
-\includegraphics[height=3.7cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf} {\tiny (b)}%
-
-\includegraphics[height=3.3cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}{\tiny (c)}%
-\includegraphics[height=3.5cm]{\FigPath/AUTPretzelosity_x.pdf}{\tiny (d)}%
+\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf} {\tiny (a)}%
+\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf} {\tiny (b)}%
+\includegraphics[height=3.2cm]{\FigPath/AUTPretzelosity_x.pdf}{\tiny (c)}%
+
+\includegraphics[height=3.3cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}{\tiny (d)}%
 \caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$
@@
 	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES
-	\cite{Schnell:2010zza}(c) in comparison to the best fit from \cite{Lefky:2014eia}
-	(whose 1-$\sigma$ uncertainty band is compatible with zero), and our calculation for COMPASS kinematics (d). For comparison the COMPASS plots
+	\cite{Schnell:2010zza}(d) in comparison to the best fit from \cite{Lefky:2014eia}
+	(whose 1-$\sigma$ uncertainty band is compatible with zero), and our calculation for COMPASS kinematics (c). For comparison the COMPASS plots
 	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.

### 2019-01-13 tex/test-WW-type-01c.tex
text

@@
 which are worthwhile exploring for their own sake,
-see \ps{for instance Ref.~}\cite{Jaffe:1989xx} on $g_T^a(x)$.
+see for instance Ref.~\cite{Jaffe:1989xx} on $g_T^a(x)$.
 

### 2019-01-13 arxiv1/test-WW-type.tex
arxiv

--- 2018-08-09 arxiv/test-WW-type.tex
@@
 
-%\newcommand{\AP}[1]{\red{#1}}
+\newcommand{\AP}[1]{\red{#1}}
 %\newcommand{\ak}[1]{\orange{#1}}
-%\newcommand{\ps}[1]{\blue{#1}}
+\newcommand{\ps}[1]{\blue{#1}}
 %\newcommand{\gs}[1]{{\color[rgb]{0.65,0,0.65}#1}}
@@
 
-\newcommand*{\FigPath}{.}%  
+\newcommand*{\FigPath}{./figs}%
 \newcommand*{\BibPath}{.}%
@@
 Electron-Ion Collider. The results of this paper can be readily used for
-phenomenology and for event generators, and will help to improve our 
-understanding of the TMD theory beyond leading twist.
-} 
+phenomenology and for event generators, and will help
+   {to improve the description of semi-inclusive deep-inelastic processes
+   in terms of transverse momentum dependent parton distribution functions
+   and fragmentation functions beyond the leading twist}.}
 %\end{abstract}
@@
 	been obtained without advances in target polarization techniques
-	employed in the HERMES, COMPASS and JLab experiments 
+	employed in the HERMES, COMPASS and Jefferson Lab (JLab) experiments
 	\cite{Stock:1994vv,Crabb:1997cy,Goertz:2002vv}.
@@
 which are worthwhile exploring for their own sake,
-see \cite{Jaffe:1989xx} on $g_T^a(x)$.
+see for instance Ref.~\cite{Jaffe:1989xx} on $g_T^a(x)$.
 
@@
 twist-3 in a unique approach. Our results are of importance for measurements
-performed or in preparation at HERMES, COMPASS, Jefferson Lab (JLab) with 
+performed or in preparation at HERMES, COMPASS, JLab with
 12$\,$GeV beam-energy upgrade, or proposed in the long-term
@@
 
+On the theoretical side it is also important to note that the
+theory for subleading-twist TMD observables is only poorly developed
+as compared to the current state-of-the-art of leading-twist observables.
+In order to address subleading-twist TMD observables one has
+to restrict oneself to the tree-level formalism
+\cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,
+Bacchetta:2006tn} which may not be free of doubts
+\cite{Metz:2004je,Gamberg:2006ru}.
+
 Our predictions, whether confirmed or not supported by current and
@@
 and call for dedicated theoretical studies to explain (i) why the
-pertinent $\bar{q}gq$--terms are small or (ii) why they are sizable. 
+pertinent $\bar{q}gq$--terms are small or (ii) why they are sizable,
+depending on the outcome of the experiments.
 In either case our results will deepen the understanding of
@@
 Neglecting $1/Q^2$ corrections, the kinematic prefactors $p_i$ are given by
+% \ba\label{Eq:y-prefactors}
+% &&	p_1 = \varepsilon \equiv
+%        \frac{1-y -\frac{1}{4}\slim \gamma^2 y^2}{1-y
+%        + \frac{1}{2}\slim y^2 +\frac{1}{4}\slim \gamma^2 y^2}
+%        \approx \frac{1-y}{1-y+\frac12\,y^2} 		\;,\nonumber\\
+% &&	p_2 = \sqrt{1-\epsilon^2} \approx
+%        \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2} 	\;,\nonumber\\
+% &&	p_3 =  \sqrt{2\varepsilon(1+\varepsilon)}
+%        \approx \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2}\;,\nonumber\\
+% &&	p_4 =  \sqrt{2\varepsilon(1-\varepsilon)}
+%        \approx \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2} 	\;,\;\;\;
+% \ea
 \be\label{Eq:y-prefactors}
@@
 \ee
-and the asymmetries $A_{XY}^{\rm weight}$,  are defined in terms of structure functions $F_{XY}^{\rm weight}$, as follows
+and the asymmetries {$A_{XY}^{\rm weight}$,  are defined in terms of
+structure functions $F_{XY}^{\rm weight}$, as follows}
 \be
@@
 	\;e^{ik\xi}\;\la N(P,S)|\bar\psi_j(0)\,{\cal W}_{(0,\,\infty)}
-	{\cal W}_{(\infty,\xi)}\,\psi_i(\xi)|N(P,S)\ra
+	{\cal W}_{(\infty,\,\xi)}\,\psi_i(\xi)|N(P,S)\ra
     	\with{ }{\xi^+\!=\!0}{$k^+ = xP^+$}
 	\ee
-where the Wilson-lines ${\cal W}_{(0,\,\infty)}
-	{\cal W}_{(\infty,\xi)}$ refer to the SIDIS process 
+where the Wilson-lines  {${\cal W}_{(0,\,\infty)}{\cal W}_{(\infty,\,\xi)}$}
+refer to the SIDIS process
 \cite{Collins:2002kn}. For a generic four-vector $a^\mu$ we define
@@
 
-Fragmentation functions are defined through the following correlator [10]
+{Fragmentation functions are defined through the following correlator %[10]
+\cite{Metz:2016swz}
 (where $\bfpperp$ denotes the transverse momentum of the produced hadrons
-  acquired during the fragmentation process with respect to the quark)
+acquired during the fragmentation process with respect to the quark)}
 \be\label{Eq:correlator-FF}
@@
 \ea\end{subequations}
+
+\newpage
+
+\noindent
 The FFs depend on $z$, $P_\perp$, renormalization scale, quark flavor and
@@
 \ba
-	F_{UU}^{\cos\phi_h}  
+	\ \hspace{-1cm}	F_{UU}^{\cos\phi_h}
 	&=&
@@
 	\label{Eq:FUUcosphi}\\
-	F_{LU}^{\sin\phi_h}  
+	\ \hspace{-1cm}	F_{LU}^{\sin\phi_h}
 	&=&
@@
 	\label{FLUsinphi}\;\;\;\;\;\\
-	F_{UL}^{\sin\phi_h} 
+	\ \hspace{-1cm}	F_{UL}^{\sin\phi_h}
  	&=&
@@
 	\label{FULsinphi}\\
-	F_{LL}^{\cos \phi_h} 
+	\ \hspace{-1cm}	F_{LL}^{\cos \phi_h}
  	&=&
@@
 	\label{FLLcosphi}\;\;\;\;\;\;\;\;\;\\
-	F_{UT}^{\sin \phi_S } 
+	\ \hspace{-1cm}	F_{UT}^{\sin \phi_S }
 	&=&
@@
 	+ r_h^{ }\, f_{1T}^{\perp } \,\frac{\tilde{D}^{\perp }}{z}
-   	\biggr) \biggr]\, , \label{FUTsinphiS}\\ 
-	F_{LT}^{\cos \phi_S} 
+   	\biggr) \biggr]\, , \label{FUTsinphiS}
+\ea
+\ba
+	\ \hspace{-1cm}	F_{LT}^{\cos \phi_S}
 	&=&
@@
 	\, , \label{FLTcosphiS} \\ \hspace{-5mm}
-	F_{UT}^{\sin(2\phi_h -\phi_S)} 
+	\ \hspace{-1cm}	F_{UT}^{\sin(2\phi_h -\phi_S)}
 	&=&
@@
    	- r_h^{ }\, \, h_{1T}^{\perp }  \frac{\tilde{H}}{z}\biggr) \biggr] \, , \\
-	F_{LT}^{\cos(2\phi_h - \phi_S)} 
+	\ \hspace{-1cm}	F_{LT}^{\cos(2\phi_h - \phi_S)}
 	&=& \frac{2M_N}{Q}\,{\cal C}\biggl[
@@
 framework, including definition, renormalization and evolution of
-leading-twist TMDs \cite{Aybat:2011zv,Aybat:2011ge,Echevarria:2014xaa},
-NLO corrections within the TMD framework \cite{Ma:2013aca}, and  
-phenomenological fits with evolution \cite{Aybat:2011ta,Kang:2015msa}.
+leading-twist TMDs
+\cite{Aybat:2011zv,Aybat:2011ge,Echevarria:2014xaa,Collins:2014jpa},
+next-to-leading order corrections within the TMD framework
+\cite{Ma:2013aca}, and phenomenological fits with evolution
+\cite{Aybat:2011ta,Kang:2015msa}.
+The matching of twist-2 collinear and TMD quantities was
+studied to next-to-leading and next-to-next-to-leading order
+\cite{Gutierrez-Reyes:2017glx,Gutierrez-Reyes:2018qez}.
+The WW approximation has been used recently in Ref.~\cite{Scimemi:2018mmi}
+to connect the twist-2 TMDs $f_{1T}^\perp$, $g_{1T}^\perp$, $h_{1}^\perp$,
+$h_{1L}^\perp$ to certain higher twist collinear matrix elements.
+
 In contrast to this, the theory for subleading-twist TMD observables is
@@
 
-In the T-even case one obtains the following approximations \footnote{
-Notice that Ref.~\cite{Bacchetta:2006tn} uses four-vector notations for transverse vectors, while in this paper we always utilize two-vectors for transverse vectors, such that e.g.
-${\bfkperp^2}_{\rm our} = -{{p}_T^2}_{\mbox{\rm Ref.\citep{Bacchetta:2006tn}}}$ and analog for other scalar products of {\it transverse} vectors.},
+In the T-even case one obtains the following approximations \footnote{%
+	Notice that Ref.~\cite{Bacchetta:2006tn} uses four-vector notation
+	for transverse vectors, while in this paper we always utilize
+	two-vectors for transverse vectors, such that e.g.\
+	${\bfkperp^2}_{\rm our} = -{{p}_T^2}_{\mbox{\tiny Ref.~\cite{Bacchetta:2006tn}}}$
+	and analog for other scalar products of {\it transverse} vectors.
+	Notice that in our notation transverse vector
+	are never understood as four-vectors such that
+	${\bfkperp^2}_{\rm our} \equiv {\kperp^2}_{\rm our}$.},
 where the terms on the left-hand-side are twist-3, those on the
@@
 f^{(1)}(x,\kperp^2) = \frac{\kperp^2}{2M^2}\,f(x, \kperp^2)\; , \;\;\;
-f^{(1)}(x ) = \int d^2 \bfkperp f^{(1)}(x,\kperp^2) \; . 
+f^{(1)}(x ) = \int d^2 \kperp f^{(1)}(x,\kperp^2) \; .
 \ea
@@
 WW-type approximations (\ref{Eq:WW-type-gT},~\ref{Eq:WW-type-6}).
-This yields \cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv}%
+The resulting relations are the only WW-type relations applicable
+to twist-2 TMDs and are given by the following expressions
+\cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv},
+
+\newpage
+
 \begin{subequations}\ba
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t!]
+\begin{figure}[b!]
 \centering
-\includegraphics[width=0.48\textwidth]{\FigPath/g2.pdf} 
-\includegraphics[width=0.48\textwidth]{\FigPath/g2-HERMES.pdf} 
+\includegraphics[width=0.45\textwidth]{\FigPath/g2.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/g2-HERMES.pdf}
 \caption{\label{Fig:g2}
@@
 form that lends itself to straightforward tests of the WW-type relations
-as presented in this paper. This assumption holds if renormalization is multiplicative and
+as presented in this paper.
+   {This assumption holds if renormalization is multiplicative and
    flavor-independent for the non-local lattice operators. This is
-   not true for all lattice actions [64]. But presumably it is true
+   not true for all lattice actions \cite{Musch:2010ka}. % PS: [66]? CHECK!!
+   But presumably it is true
    if the lattice action preserves chiral symmetry, as it does in
    the present case. For the latest developments we refer the
-   interested reader to Refs.~\cite{Alexandrou:2017dzj,Ishikawa:2017faj,Ji:2017oey,Yoon:2017qzo,Green:2017xeu,Zhang:2017bzy}.
+   interested reader to Refs.~\cite{Alexandrou:2017dzj,Ishikawa:2017faj,
+	Engelhardt:2015xja,%Phys.Rev. D93 (2016) no.5, 054501,
+	Ji:2014hxa,%Phys.Rev. D91 (2015) 074009,
+	Musch:2011er,%Phys.Rev. D85 (2012) 094510
+   Ji:2017oey,Yoon:2017qzo,Green:2017xeu,Zhang:2017bzy}.}
 
@@
 \ea
-with the understanding that
+Here the 
 negative $x$ refer to antiquark distributions
@@
 not give up at this point and take a look at the lattice observables of
-Ref.~\cite{Musch:2010ka}. Here, the TMDs are obtained from amplitudes 
+Ref.~\cite{Musch:2010ka} where TMDs were obtained from amplitudes
 $\tilde A_i(l^2,\ldots)$ in Fourier space, where $\bfkperp$ is encoded
@@
 
-There is yet another issue to be discussed. 
+There is another issue to discuss.
 The gauge link that goes into the evaluation of the quark-quark correlator
@@
 approximations, it is possible to express all SIDIS structure functions
-in terms of the basis functions\footnote{Notice that SIDIS alone is of course not sufficient to determine
-   the basis functions uniquely because the 8 basis functions appear
-   in 6 SIDIS leading-twist structure functions. It is crucial to take advantage of
-   other processes (such as Drell-Yan and hadron production in
+in terms of the basis functions.\footnote{%
+   Notice that SIDIS alone is not sufficient to determine
+   the 8 basis functions uniquely which appear in 6 SIDIS
+   leading-twist structure functions. It is crucial to take
+   advantage of other processes (like Drell-Yan and hadron production in
    $e^+e^-$ annihilation, which are indispensable for the determination
-   of $f_1^a$ and $D_1^a$).}.
+   of $f_1^a$, $D_1^a$, $H_1^{\perp a}$).}
 These basis functions allow us to describe, in WW-type approximation,
@@
 	f_{1T}^{\perp a}, \;h_1^{\perp a},\; h_{1T}^{\perp a}; \;
-	D_1^a, \; H_1^{\perp a} \,$. For details see App.~\ref{App:basis}.}
+	D_1^a, \; H_1^{\perp a} \,$.
+	The parametrizations of the basis functions and the Gaussian
+	model parameters are described in detail in App.~\ref{App:basis}.}
 \end{figure}
@@
 twist-2 collinear functions. All collinear functions are calculated at
-$Q^2 = 2.4$ GeV$^2$. Collinear $f_1^a(x)$ are from Ref.~\cite{Martin:2009iq},  
-$g_1^a(x)$ are from Ref.~\cite{Gluck:1998xa}, and $D_1^a$ are from 
-Ref.~\cite{deFlorian:2007aj}. The other four TMDs 
+$Q^2 = 2.4$ GeV$^2$ with $f_1^a(x)$ from \cite{Martin:2009iq},
+$g_1^a(x)$ from \cite{Gluck:1998xa}, $D_1^a(z)$ from
+\cite{deFlorian:2007aj}. The other four TMDs
 have no collinear counterparts.
@@
 \ea\end{subequations}
-The parametrizations of the basis functions and the Gaussian model
-parameters are described in detail in App.~\ref{App:basis}.
+
+%\newpage
 
@@
 
-Let us begin with Jefferson Lab where, in the pre-12$\,$GeV era, electron beams 
+Let us begin with JLab where, in the pre-12$\,$GeV era, electron beams
 from CEBAF with energies in the range $4.3$ to $5.7$ GeV were scattered
@@
 	% for $\la Q^2\ra=2.37\,{\rm GeV}^2$, $\la x\ra=0.24$, $\la z\ra=0.30$
-	at Jefferson Lab with 5.75 GeV beam \cite{Osipenko:2008aa}.
+	at JLab with 5.75 GeV beam \cite{Osipenko:2008aa}.
 Middle panel:
@@
 Signori:2013mda,Anselmino:2013lza}, but nothing is known about its
-applicability to spin asymmetries. The Jefferson Lab data \cite{Avakian:2010ae} 
+applicability to spin asymmetries. The JLab data \cite{Avakian:2010ae}
 on $A_{LL}(\Phperp)$ put us in the position to conduct a first ``test''
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/all_jlab_pip}  
-\includegraphics[width=0.45\textwidth]{\FigPath/all_jlab_pi0}  
-\includegraphics[width=0.45\textwidth]{\FigPath/all_jlab_pim} 
+\includegraphics[width=0.333\textwidth]{\FigPath/all_jlab_pip}%
+\includegraphics[width=0.333\textwidth]{\FigPath/all_jlab_pi0}%
+\includegraphics[width=0.333\textwidth]{\FigPath/all_jlab_pim}
 \caption{\label{jlab_ALL}
@@
 
-The definition of the asymmetry in  the Jefferson Lab experiment \cite{Avakian:2010ae} 
+The definition of the asymmetry in  the JLab experiment \cite{Avakian:2010ae}
 was
@@
 and tested through other observables in Sec.~\ref{Sec-5.1:FUU-basis}.
-Therefore the comparison of our results to the Jefferson Lab data \cite{Avakian:2010ae} 
+Therefore the comparison of our results to the JLab data \cite{Avakian:2010ae}
 shown in Fig.~\ref{jlab_ALL} provides several important tests.
-First, the Jefferson Lab data \cite{Avakian:2010ae} are compatible
+First, the JLab data \cite{Avakian:2010ae} are compatible
 with the Gaussian Ansatz within uncertainties. Second, the lattice
@@
 	parametrizations of $f_1^a(x)$, $g_1^a(x)$, $D_1^a(z)$. This
-	shows that even at the moderate beam energies of the pre-12~GeV 
-	era one was, to a good approximation, indeed probing DIS at 
-	Jefferson Lab~\cite{Avakian:2010ae}.)
+	shows that in the pre-12~GeV era one was, to a good
+	approximation, indeed already probing DIS \cite{Avakian:2010ae}.)
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
-\includegraphics[width=0.45\textwidth]{\FigPath/AUTSivers_COMPASS_x.pdf}
+\includegraphics[width=0.35\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
+\includegraphics[width=0.35\textwidth]{\FigPath/AUTSivers_COMPASS_x.pdf}
 \caption{\label{aut_f1t_jlab} Sivers asymmetry
@@
 on respectively charged pion and hadron production from a proton target.
-Notice that COMPASS points are lower than theoretical calculation, that may indicate evolution effects~\cite{Aybat:2011ta, Anselmino:2012aa}.
-The $P_{hT}$--dependences of the data are well described, which
-confirms that the Gaussian model works also in this case.
+	Notice that the COMPASS data points seem to be below the
+	theoretical curves which may indicate evolution
+	effects~\cite{Aybat:2011ta,Anselmino:2012aa}.
+We do not show here the description of the $P_{hT}$--dependence of the
+data but it is well-described by the fit of \cite{Anselmino:2011gs}
+which confirms that the Gaussian model works also in this case.
 
@@
 
-The $F_{UT}^{\sin(\phi_h+\phi_S)}$ structure function of the SIDIS cross section is due 
-to the convolution of the transversity distribution $h_1$ and the Collins 
+The $F_{UT}^{\sin(\phi_h+\phi_S)}$ structure function of the SIDIS cross section is
+due to the convolution of the transversity distribution $h_1$ and the Collins
 FF $H_1^\perp$. Transversity can in principle be accessed also as a PDF in
@@
 \cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,Bacchetta:2012ty,
-Radici:2015mwa,Radici:2018iag}. The first polarized Drell-Yan data were measured by COMPASS~\cite{Aghasyan:2017jop,Parsamyan:2018zju}.
+Radici:2015mwa,Radici:2018iag}. The first polarized Drell-Yan data were
+measured by COMPASS~\cite{Aghasyan:2017jop,Parsamyan:2018zju}.
 It describes the distribution of transversely polarized quarks
@@
 see App.~\ref{App:convol-details} for details.
-
-The asymmetries $A_{UT, \langle y \rangle}^{\sin(\phi_h+\phi_S)}= (1-y)F_{UT}^{\sin(\phi_h+\phi_S)}/((1-y + y^2/2)F_{UU})$  
-are plotted in Fig.~\ref{aut_h1_jlab} as functions of $x$ in comparison 
-to HERMES \cite{Airapetian:2010ds} and $A_{UT}^{\sin(\phi_h+\phi_S)}= F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$  for COMPASS \cite{Adolph:2014zba} 
-data on charged pion production from proton targets.
-We remark that the description of the $P_{hT}$--dependencies of 
-this azimuthal spin asymmetry is equally satisfactory by the 
-fit of Ref.~\cite{Anselmino:2013vqa}, which implies that the 
-data are compatible with the Gaussian Ansatz also in this case.
 
@@
 
+The asymmetries $A_{UT, \langle y \rangle}^{\sin(\phi_h+\phi_S)}= (1-y)F_{UT}^{\sin(\phi_h+\phi_S)}/((1-y + y^2/2)F_{UU})$
+are plotted in Fig.~\ref{aut_h1_jlab} as functions of $x$ in comparison
+to HERMES \cite{Airapetian:2010ds} and $A_{UT}^{\sin(\phi_h+\phi_S)}= F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$  for COMPASS \cite{Adolph:2014zba}
+data on charged pion production from proton targets.
+We remark that the description of the $P_{hT}$--dependencies of
+this azimuthal spin asymmetry is equally satisfactory by the
+fit of Ref.~\cite{Anselmino:2013vqa}, which implies that the
+data are compatible with the Gaussian Ansatz also in this case.
+
 \subsection{\boldmath Leading-twist $A_{UU}^{\cos(2\phi_h)}$ Boer--Mulders asymmetry}
@@
 The structure function $F_{UU}^{\cos(2\phi_h)}$ arises from a convolution of
-the Collins fragmention function and the Boer-Mulders TMD $h_{1}^{\perp q}$ which describes
+the Collins fragmention function and the Boer-Mulders TMD $h_{1}^{\perp q}$
+which describes
 the distribution of transversely polarized partons inside an unpolarized
@@
 Boer--Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$, which does not describe
-the data well, especially for COMPASS one can see that calculation and the data are of opposite signs. In fact, it is suspected that this observable receives 
-a significant contribution from the Cahn effect \cite{Cahn:1978se}, a 
-term of higher-twist character of the type $\la\Phperp^2\ra/Q^2$ which 
-is not negligible in fixed-target experiments \cite{Schweitzer:2010tt}. 
-This contribution was estimated and corrected for in the phenomenological 
-works \cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa}, which was of
-importance to obtain a picture of the Boer--Mulders function undistorted 
+the data well, especially for COMPASS one can see that calculation and
+data are of opposite signs. In fact, it is suspected that this observable
+receives a significant contribution from the Cahn effect \cite{Cahn:1978se},
+a term of higher-twist character of the type $\la\Phperp^2\ra/Q^2$ which
+is not negligible in fixed-target experiments as shown in
+phenomenological \cite{Schweitzer:2010tt} and model \cite{Cao:2018qqf} studies.
+In the phenomenological works
+\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} an attempt was
+made to estimate and correct for this contribution in order
+to obtain a picture of the Boer--Mulders function undistorted
 from Cahn effect. The point is that this substantial twist-4 contamination
@@
 
-The pretzelosity TMD $h_{1T}^{\perp q}$ is the least known of the basis 
-functions. It is of interest as it allows one to measure the deviation 
+The pretzelosity TMD $h_{1T}^{\perp q}$ is the least known basis
+function. It is of interest as it allows one to measure the deviation
 of the nucleon spin density from spherical shape \cite{Miller:2007ae},
-as it is related to the only leading-twist SIDIS structure function where the 
+is related to the only leading-twist SIDIS structure function where the
 small-$P_{hT}$ description in terms of TMDs and the large-$P_{hT}$ expansion
-in perturbative QCD mismatch \cite{Bacchetta:2008xw}, and as it is the only
-TMD where a clear relation to quark orbital angular momentum
+in perturbative QCD mismatch \cite{Bacchetta:2008xw}, and is the only TMD
+where a clear relation to quark orbital angular momentum
 could be established (albeit only within quark models)
@@
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pip.pdf}  
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_pretzelosity_pim.pdf}
-\includegraphics[width=0.55\textwidth]{\FigPath/AUTPretzelosity_HERMES_x.pdf}
-
+\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf} {\tiny (a)}%
+\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf} {\tiny (b)}%
+\includegraphics[height=3.2cm]{\FigPath/AUTPretzelosity_x.pdf}{\tiny (c)}%
+
+\includegraphics[height=3.3cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}{\tiny (d)}%
 \caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$
-	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2010se} 
-	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES \cite{Schnell:2010zza} in comparison to the best fit 
-	(whose 1-$\sigma$ uncertainty band is compatible with zero) 
-	from \cite{Lefky:2014eia}. For comparison the COMPASS plots
+	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2013fia} (a,b)
+	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES
+	\cite{Schnell:2010zza}(d) in comparison to the best fit from \cite{Lefky:2014eia}
+	(whose 1-$\sigma$ uncertainty band is compatible with zero), and our calculation for COMPASS kinematics (c). For comparison the COMPASS plots
 	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
@@
 to significantly improve our knowledge of this TMD.
+
+For comparison Fig.~\ref{altcos2phihphis} shows also the results
+from the quark-diquark model calculation of Ref.~\cite{Kotzinian:2008fe},
+and from the light-cone constituent quark model of Ref.~\cite{Boffi:2009sh}.
+
+%\newpage
 
@@
 which is supported by lattice results \cite{Hagler:2009mb}.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip} {\tiny (a)}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim} {\tiny (b)}
+\includegraphics[width=0.37\textwidth]{\FigPath/ALT_COMPASS_x.pdf} {\tiny (c)}
+	\caption{\label{cosphihphis}
+	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$
+	 in comparison to the preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b), and our calculation for COMPASS kinematics (c) .
+	}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 In the Gaussian Ansatz the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$
@@
 
-This asymmetry was measured at Jefferson Lab~\cite{Huang:2011bc}, COMPASS~\cite{
-Parsamyan:2007ju,Parsamyan:2018evv,Parsamyan:2015dfa} and HERMES~\cite{Pappalardo:2011cu,Pappalardo:2012zz} (for the latter two experiments only preliminary results are available so far).
+This asymmetry was measured at JLab~\cite{Huang:2011bc}, COMPASS~\cite{
+Parsamyan:2007ju,Parsamyan:2015dfa,Parsamyan:2018evv} and HERMES~\cite{Pappalardo:2011cu,Pappalardo:2012zz} (for the latter two experiments only preliminary results are available so far).
  Fig.~\ref{cosphihphis}
@@
 \cite{Kotzinian:2006dw,Kotzinian:2008fe,Boffi:2009sh} are shown.
-Our results are also compatible with the Jefferson Lab data, which were 
+Our results are also compatible with the JLab data, which were
 taken with a neutron ($^3$He) target \cite{Huang:2011bc} and have
 larger statistical uncertainties than the preliminary COMPASS and HERMES data.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip}
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim}
-	\caption{\label{cosphihphis} 
-	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$ 
-	 in comparison to the preliminary COMPASS data \cite{Parsamyan:2018ovx}.
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\ps{\ \\
+%PS: HERE IS ENOUGH SPACE TO
+%\begin{itemize}
+%\item 	SHOW PLOTS WITH JLAB DATA \cite{Huang:2011bc} FOR PI$\pm$ FROM NEUTRON,
+%\item	OR WRITE SOME MORE BLA, BLA, BLA.
+%\end{itemize}
+%I HAVE NO INSPIRATION FOR BLA, BLA HERE. \\
+%\red{SHOULD WE ADD THE JLAB HALL-A FIGURES?} \\ }
+
+%\newpage
 
@@
 supported by lattice data \cite{Hagler:2009mb}.
-From (\ref{Eq:WW-approx-h1L}) we obtain the WW-type estimate
+>From (\ref{Eq:WW-approx-h1L}) we obtain the WW-type estimate
 for $h_{1L}^{\perp(1) a}(x)$ shown in Fig.~\ref{g1t_h1l_functions}.
@@
 \centering
-\includegraphics[width=0.9\textwidth]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \quad
-\includegraphics[width=0.55\textwidth]{\FigPath/AULsin2phi_JLAB_x.pdf} 
-\vspace{-5mm}
-
+\includegraphics[height=3.45cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} {\tiny (a)}
+\hskip -0.2cm\includegraphics[height=3.45cm]{\FigPath/AULsin2phi_COMPASS_x} {\tiny (b)}
+
+\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_JLAB_x.pdf} {\tiny (c)}
 	\caption{\label{aul_jlab}
@@
 	HERMES \cite{Airapetian:1999tv}, and $A_{UL}^{\sin(2\phi_h)}$
-	COMPASS \cite{Parsamyan:2015dfa} (left panel), and $A_{UL,  \langle y\rangle}^{\sin(2\phi_h)}$ 
-	Jefferson Lab \cite{Jawalkar:2017ube} (right panel). Results  
+	COMPASS \cite{Parsamyan:2018ovx,Parsamyan:2018evv} (a),
+	and $A_{UL,  \langle y\rangle}^{\sin(2\phi_h)}$
+	JLab \cite{Jawalkar:2017ube} (c),  and our calculation for COMPASS kinematics (b). Results
 	from \cite{Avakian:2007mv} are also shown.}
@@
 studied at HERMES \cite{Airapetian:1999tv,Airapetian:2002mf}, COMPASS
-\cite{Parsamyan:2018ovx}, and Jefferson Lab \cite{Avakian:2010ae,Jawalkar:2017ube}.
+\cite{Parsamyan:2018ovx,Parsamyan:2018evv}, and JLab \cite{Avakian:2010ae,Jawalkar:2017ube}.
 In Fig.~\ref{aul_jlab} proton data are shown for $\pi^\pm$ in the
-HERMES experiment which were measured with the 27.6 GeV positron
+HERMES experiment measured with the 27.6 GeV positron
 beam from the HERA polarized positron storage ring at DESY for
 $1\,{\rm GeV}^2 < Q^2 < 15 \,{\rm GeV}^2$, $W > 2\,{\rm GeV}$,
-$0.023 < x < 0.4$ and $y < 0.85$. 
+$0.023 < x < 0.4$, $y < 0.85$.
 The COMPASS data were taken in 2007 (160 GeV) and 2011 (200 GeV) and show
@@
 (see Sec.~\ref{Sec-2.1:SIDIS+structure-functions}),
-the HERMES data is adequately (``$D(y)$--'')rescaled.
+the HERMES data is adequately (``$D(y)$~--'')rescaled.
 The CLAS $\pi^0$ data in the right panel were measured using 6$\,$GeV
@@
 $A_{UL}^{\sin(2\phi_h)}$  can be expected to be smaller than
-$A_{LT}^{\cos(\phi_h -\phi_S)}$ discussed in the previous section,
+$A_{LT}^{\cos(\phi_h -\phi_S)}$ discussed in Sec.~\ref{Sec-6.1:FLTcosphi-phiS},
 even though both are leading twist. This is because
 $F_{UL}^{\sin(2\phi_h)}$ is quadratic in the hadron transverse
-momenta $P_{hT}\ll Q$, while $F_{LT}^{\cos(\phi_h -\phi_S)}$ is linear. 
+momenta $P_{hT}$, while $F_{LT}^{\cos(\phi_h -\phi_S)}$ is linear.
 In addition, the former is proportional to the Collins function,
@@
 of the size of $g_{1T}^{\perp(1)q}(x)$.
-The data support these expectations. HERMES and Jefferson Lab data are compatible
-with zero for this asymmetry. So are the preliminary COMPASS data except for the region
+The data support these expectations. HERMES and JLab data are compatible
+with zero for this asymmetry. So are the preliminary COMPASS data except
+for the region
 $x>0.1$ for negative hadrons, where the trend of the data provides a first
-encouraging confirmation for our results. The current data are compatible
+encouraging confirmation for our results. Thus current data are compatible
 with the WW-type approximation for $h_{1L}^{\perp(1)q}(x)$.
@@
 Before proceeding with twist-3 let us pause and revisit positivity
-bounds \cite{Bacchetta:1999kz}. % which offer unique cross checks.
-
+bounds \cite{Bacchetta:1999kz}. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/h1lperp_positivity.pdf} \quad
+\includegraphics[width=0.45\textwidth]{\FigPath/g1t_positivity.pdf}
+	\caption{\label{h1l_pos}
+	The normalized inequalities for $g^{\perp(1)q}_{1T}(x)$ and
+	$h^{\perp(1)q}_{1L}(x)$ vs $x$ which are obtained by integrating
+	(\ref{eq:positivity}) and (\ref{eq:positivity1}) over $\kperp$,
+	and normalizing with respect to the sum of the absolute
+	values of the individual terms. The result must be positive and
+	smaller than unity {\it if} the WW-type approximations
+	and the application of the Gaussian model are compatible
+	with positivity, see text. Clearly, our approach respects
+	this test of the positivity conditions.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The Kotzinian--Mulders function $h^{\perp q}_{1L}$ in conjunction with
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/h1lperp_positivity.pdf} \quad  
-\includegraphics[width=0.45\textwidth]{\FigPath/g1t_positivity.pdf}  
-	\caption{\label{h1l_pos} 
-	The normalized inequalities for $g^{\perp(1)q}_{1T}(x)$ and
-	$h^{\perp(1)q}_{1L}(x)$ vs $x$ which are obtained by integrating
-	(\ref{eq:positivity}) and (\ref{eq:positivity1}) over $\kperp$,
-	and normalizing with respect to the sum of the absolute
-	values of the individual terms. The result must be positive and 
-	smaller than unity {\it if} the WW-type approximations
-	and the application of the Gaussian model are compatible
-	with positivity, see text. Clearly, our approach respects 
-	this test of the positivity conditions.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 To conduct a test we use the Gaussian Ansatz
@@
 
-Indeed, data from Jefferson Lab, HERMES and COMPASS show a clearly non-zero 
+Indeed, data from JLab, HERMES and COMPASS show a clearly non-zero
 asymmetry $A_{LU}^{\sin\phi_h} = F_{LU}^{\sin\phi_h}/F_{UU}$ of the order of 2\,$\%$
 \cite{Avakian:2003pk,Airapetian:2006rx,Gohn:2009zz,
-Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz}, these 2\% come after $1/Q$ suppression. Unsuppressed effect at large $x$ at COMPASS would reach 10\% \cite{private}.
-On the one hand this is interesting: this observable provides a unique 
-opportunity to learn about the physics of $\bar{q}gq$-terms. On the other
-hand, this observable is beyond the applicability of the WW-type approximation
-and we cannot make a non-trivial prediction for this asymmetry.
+Aghasyan:2011ha,Adolph:2014pwc,Gohn:2014zbz} (which includes
+the $1/Q$ factor intrinsic in twist-3 observables; without this factor
+the asymmetry would reach $10\%$ at large $x$ at COMPASS).
+This observable provides a unique opportunity to learn about the
+physics of $\bar{q}gq$-terms, but is beyond the applicability of
+the WW-type approximation.
 
@@
 and relevant model studies have been reported
-\cite{Efremov:2002qh,
-Lorce:2014hxa,
-Schweitzer:2003uy,Ohnishi:2003mf,Cebulla:2007ej,
-Efremov:2002ut,Afanasev:2003ze,Yuan:2003gu,Gamberg:2003pz,Metz:2004je,Afanasev:2006gw,Mao:2012dk,Mao:2014dva,Courtoy:2014xea,Yang:2016mxl}.
+\cite{Efremov:2002qh,Schweitzer:2003uy,Ohnishi:2003mf,Cebulla:2007ej,
+Efremov:2002ut,Afanasev:2003ze,Yuan:2003gu,Gamberg:2003pz,Metz:2004je,Afanasev:2006gw,Mao:2012dk,Mao:2013waa,Mao:2014dva,Lorce:2014hxa,Courtoy:2014ixa,Yang:2016mxl}.
 But more phenomenological work and dedicated studies on the basis of models
@@
 
+%\newpage
 \subsection{\boldmath Subleading-twist  $A_{LT}^{\cos\phi_S}$}
@@
 in the Gaussian ${\cal G}(\Phperp)$.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htb!]
+\centering
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pip.pdf} {\tiny (a)}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pim.pdf} {\tiny (b)}
+\includegraphics[width=0.35\textwidth]{\FigPath/ALTcosPhi_COMPASS_x} {\tiny (c)}
+\caption{\label{altcosphis} Subleading-twist asymmetry $A_{LT}^{\cos\phi_S}$
+	as function of $x$ from scattering of 160 GeV
+	longitudinally polarized muons off a transversely polarized
+	proton target \cite{Parsamyan:2013fia} (a,b),  and our calculation for COMPASS kinematics (c).
+	}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Notice that we followed here the scheme explained in
@@
 these steps is not relevant, but here it is. It is instructive to
-discuss what the opposite order of these steps yields. 
-One may first plug in the WW-type approximation (\ref{Eq:WW-type-gT}) 
-in the convolution integral (\ref{Eq:WW-original1}) and then solve the
-convolution integral with Gaussian Ansatz. The result is an
-analytical expression which is bulkier than (\ref{Eq:FLTcosphiS-Gauss})  
-though it yields a numerically similar result. But there are 2 critical
-issues with that. First, the WW-type approximation (\ref{Eq:WW-type-gT}) 
-relates $g^{q}_{T}(x,\kperp^2)$ to $g^{\perp(1)q}_{1T}(x,\kperp^2)$ which
-(due to the weight $\kperp^2/(2M_N^2)$ in the (1)-moment) implies a kinematical 
-zero in $\kperp$ as $g^{q}_{T}(x, 0) = 0$,  which is not supported by model 
-calculations \cite{Avakian:2010br}. Second, the more economic (because 
+discuss what the opposite order of these steps would yield.
+Using first the WW-type approximation (\ref{Eq:WW-type-gT})
+in the convolution integral (\ref{Eq:WW-original1}) and then
+using the Gaussian Ansatz yields a bulkier
+analytical expression than (\ref{Eq:FLTcosphiS-Gauss}) though
+a numerically similar result. But there are two critical issues
+with that. First, the WW-type approximation (\ref{Eq:WW-type-gT})
+relates $xg^{q}_{T}(x,\kperp^2)=g^{\perp(1)q}_{1T}(x,\kperp^2)$ which
+would imply $g^{q}_{T}(x, \kperp^2) \to 0$ for $\kperp\to0$
+due to the weight $\kperp^2/(2M_N^2)$ in the (1)-moment,
+which is not supported by model calculations \cite{Avakian:2010br}.
+Second, the more economic (because
 less bulky) expression in (\ref{Eq:FLTcosphiS-Gauss}) automatically
@@
 could come from JLab12 experiments.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htb!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphis_pip.pdf} 
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cosphis_pim.pdf} 
-\caption{\label{altcosphis} Subleading-twist $A_{LT}^{\cos\phi_S}$ 
-	  as functions of $x$ from scattering of 160 GeV
-	longitudinally polarized muons off a transversely polarized 
-	proton target \cite{Parsamyan:2013fia}.
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+For further model studies of this asymmetry we refer to
+Refs.~\cite{Mao:2014fma,Wang:2016dti}.
 
@@
 	&=& -\frac{2M_N}{Q} x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\;
-	b^{(2)}_{C}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\,
-	{ \cal G}(\Phperp)\, , \\
+	b^{(2)}_{C}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\!
+	{ \cal G}(\Phperp), \quad \\
 	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\la\Phperp\ra)
@@
 in near future.
+
+For completeness Fig.~\ref{altcos2phihphis} shows results from a
+quark-diquark model calculation were a more sizable asymmetry was predicted
+\cite{Kotzinian:2008fe}. Let us remark that the $A_{LT}^{\cos(2\phi_h -\phi_S)}$
+asymmetry was also studied in a different spectator model in
+Ref.~\cite{Mao:2014fma} which predicts asymmetries of the same
+sign but smaller magnitudes of ${\cal O}(1\,\%)$.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[ht]
+\begin{figure}[h]
 \centering
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pip}
-\includegraphics[width=0.45\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pim} 
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pip} {\tiny (a)}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pim} {\tiny (b)}
+\includegraphics[width=0.35\textwidth]{\FigPath/ALTcos2PhiminusPhiS_COMPASS_x} {\tiny (c)}
 \caption{\label{altcos2phihphis} $A_{LT}^{\cos(2\phi_h - \phi_S)}$
-	as a function of $ x $ from a proton target in comparison to preliminary COMPASS data \cite{Parsamyan:2013fia}. The smallness
+	as a function of $ x $ from a proton target in comparison to
+	preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b), and our calculation for COMPASS kinematics (c). The smallness
 	of this asymmetry has two natural reasons: first, being twist-3
 	it is $M_N/Q$ suppressed; and second, it is proportional to
-	$P_{hT}^2$ with $P_{hT}\ll Q$ in TMD approach.}
+	$P_{hT}^2$  in TMD approach.}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\newpage
 
@@
 The asymmetry $A_{LL}^{\cos \phi_h}=F_{LL}^{\cos \phi_h}/F_{UU}$ predicted by the
-WW-type approximation in this case is compatible with preliminary COMPASS \cite{Parsamyan:2018ovx} (see Fig.~\ref{allcosphi_jlab}) and HERMES data.
-We remark that previously this asymmetry was studied in
-\cite{Anselmino:2006yc} and more recently in \cite{Mao:2016hdi}.
+WW-type approximation in this case is compatible with preliminary COMPASS
+\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (see Fig.~\ref{allcosphi_jlab}) and HERMES \cite{Airapetian:2018rlq} data.
+We remark that previously this asymmetry was studied in basically
+WW-type approximation in \cite{Anselmino:2006yc} and more recently
+also in the model study \cite{Mao:2016hdi}. The predictions from
+both works are included in Fig.~\ref{allcosphi_jlab} for
+comparison.
+
+\
 
@@
 \centering
-%\vspace{1cm}
-\includegraphics[width=0.9\textwidth]{\FigPath/A_LL_Pr0711_Zgt02.pdf}
+\vspace{5mm}
+\includegraphics[width=0.7\textwidth]{\FigPath/A_LL_Pr0711_Zgt02.pdf} {\tiny (a)}
+\includegraphics[width=0.35\textwidth]{\FigPath/ALLcosphi_COMPASS_x} {\tiny (b)}
 	\caption{\label{allcosphi_jlab} $A_{LL}^{\cos(\phi_h)}$
@@
 	comparison to the preliminary COMPASS data
-	\cite{Parsamyan:2018ovx}. }
+	\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (a), and our calculation for COMPASS kinematics (b). }
 \end{figure}
@@
 
+%\newpage
 \subsection{\boldmath Subleading-twist $A_{UL}^{\sin\phi_h}$ }
 \label{Sec-7.4:FULsinphi}
+
+This was historically the first measurement of a single spin
+asymmetry in SIDIS, by HERMES \cite{Airapetian:1999tv,Airapetian:2001eg},
+and consequently subject to numerous phenomenological and model studies
+\cite{DeSanctis:2000fh,Oganessian:2000um,Efremov:2001ia,Efremov:2002td,
+Efremov:2002sd,Ma:2001ie,Ma:2002ns,Schweitzer:2003yr}. A more recent
+smodel study was reported in \cite{Lu:2014fva}.
 
@@
 The asymmetries $A_{UL}^{\sin\phi_h}=F_{UL}^{\sin\phi_h}/F_{UU}$ are compared
-to HERMES, Jefferson Lab, and preliminary COMPASS data in Fig.~\ref{aulsinphi_jlab}.
-The WW-type approximation reproduces the positive sign of the asymmetry
-seen consistently at HERMES and COMPASS for $\pi^+$ and positive hadrons
-but underestimates its magnitude. The results for negative pions and 
-hadrons at HERMES and COMPASS \cite{Parsamyan:2018ovx} are compatible. An important test for this
-asymmetry is provided by neutral pions where in WW-type approximation
-the contributions of Collins fragmentation function largely cancel.
-The WW-type approximation is not able to explain the large effect
-observed at HERMES and Jefferson Lab for $\pi^0$ in the large--$x$ region 
+to HERMES, JLab, and preliminary COMPASS data in Fig.~\ref{aulsinphi_jlab}.
+The WW-type approximation seems not incompatible with data for negative
+pions and hadrons, but understimates the magnitude of the asymmetry for
+positive pions and hadrons at HERMES and COMPASS. For neutral pions the
+approximation predicts a negligibly small effect (due to cancelling
+contributions from favored und unfavored Collins fragmentation function)
+and is not able to explain the large effect
+observed at HERMES and JLab for $\pi^0$ in the large--$x$ region
 $0.1< x < 0.5$ in Fig.~\ref{aulsinphi_jlab}.
-Overall, the WW-type approximation is not adequate to catch the
-flavor dependence of this asymmetry. This indicates that here the 
+This indicates that in this asymmetry the
 tilde-terms are not negligible, and have a characteristic flavor
@@
 and Sec.~\ref{Sec-3.8:limitations}.
+
+\begin{figure}[htb]
+\centering
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pip.pdf}  {\tiny (a)}
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pim.pdf}  {\tiny (b)}
+\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_COMPASS_x}  {\tiny (c)}
+\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_HERMES_x.pdf}  {\tiny (d)}
+\caption{\label{autsinphis}
+ 	Subleading-twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which
+	is predicted to vanish in the WW-type approximation, in
+	comparison to preliminary COMPASS~\cite{Parsamyan:2013fia} (a,b) 
+	and HERMES data \cite{Schnell:2010zza} (d), and our calculation for COMPASS kinematics (c).}
+\end{figure}
+
 This could be implemented in two ways: one could describe it with a
@@
 
-\begin{figure}[h!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sinphis_pip.pdf}
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sinphis_pim.pdf}
-\includegraphics[width=0.55\textwidth]{\FigPath/AUTsinphiS_HERMES_x.pdf}
-\caption{\label{autsinphis} 
- 	Subleading-twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which 
-	is predicted to vanish in the WW-type approximation, in 
-	comparison to preliminary COMPASS~\cite{Parsamyan:2013fia} and HERMES data \cite{Schnell:2010zza}.}
-\end{figure}
-
 The final result in Eq.~(\ref{Eq:FUTsinphiS-final}) is the consistent
-result for the structure function $F_{UT}^{\sin\phi_S}(x,z)$ in WW-type 
+result for $F_{UT}^{\sin\phi_S}(x,z)$ in WW-type
 approximation, see Eq.~(\ref{Eq:FUT-collinear}). Our prediction is
-therefore $A_{UT}^{\sin\phi_S}(x)=0$. 
-Preliminary COMPASS \cite{Parsamyan:2013fia}
- (Fig.~\ref{autsinphis} top) and 
+therefore $A_{UT}^{\sin\phi_S}(x)=0$. Preliminary
+COMPASS \cite{Parsamyan:2013fia} (Fig.~\ref{autsinphis} top) and
 HERMES \cite{Schnell:2010zza} (Fig.~\ref{autsinphis} bottom) data
 indicate that at $x\gtrsim 0.1$ the signal is clearly non-zero and
-thus inconsistent with this WW-type prediction.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sin2phihphis_pip}
-\includegraphics[width=0.45\textwidth]{\FigPath/UT_Pr10_sin2phihphis_pip}
-\includegraphics[width=0.55\textwidth]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf}
-\caption{\label{autsin2phihphis} 
-	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison to preliminary COMPASS data~\cite{Parsamyan:2013fia}, and 	
-	similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to  
-	preliminary HERMES data~\cite{Schnell:2010zza}.
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+thus inconsistent with this WW-type prediction. In order to
+describe the data it is therefore necessary to explicitly model
+the involved tilde-functions. For a recent model study we refer
+to \cite{Mao:2014aoa}.
+
+%\newpage
 \subsection{\boldmath Subleading-twist  $A_{UT}^{\sin(2\phi_h-\phi_S)}$ }
@@
 
-Also in this asymmetry we end up with more than one surviving 
-contribution in our treatment. We assume Gaussian Ansatz for 
+Also in this asymmetry we end up with more than one contribution
+surviving the WW-type approximation. We assume Gaussian Ansatz for
 $f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$
@@
 \end{alignat}\end{subequations}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[htb]
+\centering
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (a)}%
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (b)}%
+\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_COMPASS_x} {\tiny (c)}
+\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf} {\tiny (d)}
+\caption{\label{autsin2phihphis}
+	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison
+	to preliminary COMPASS data~\cite{Parsamyan:2013fia} (a,b), and 	
+	similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to
+	preliminary HERMES data~\cite{Schnell:2010zza} (d), and our calculation for COMPASS kinematics (c).
+	}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 with respectively
@@
 with a zero effect within uncertainties.
-
+For comparison Fig.~\ref{altcos2phihphis} shows also the predictions
+from the quark-diquark model calculation of Ref.~\cite{Kotzinian:2008fe}.
+More recently the $A_{UT}^{\sin(2\phi_h -\phi_S)}$ was also studied in the
+model approach of Ref.~\cite{Mao:2014aoa}.
+
+\newpage
 \subsection{\boldmath Subleading-twist  $A_{UU}^{\cos\phi_h}$ }
@@
 
+The asymmetries $A_{UU}^{\cos\phi_h}$ were measured by
+EMC \cite{Aubert:1983cz}, at JLab \cite{Osipenko:2008aa,Mkrtchyan:2007sr},
+HERMES \cite{Airapetian:2012yg}, and COMPASS \cite{Adolph:2014pwc}.
+In Fig.~\ref{auucosphi_jlab} we compare our predictions to the HERMES and
+COMPASS data.
+The WW-type approximation tends to overstimate the data at
+COMPASS especially in the small-$x$ region. It is also not
+compatible with the flavor dependence seen at HERMES.
+However, both experiments seem not to agree for instance on the shape
+of the asymmetry for negative pions or hadrons. More experimental and
+theoretical work is need to clarify whether this could be due to
+power corrections.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{figure}
-
-The asymmetries $A_{UU}^{\cos\phi_h}$ were measured by
-EMC \cite{Aubert:1983cz}, at Jefferson Lab \cite{Osipenko:2008aa,Mkrtchyan:2007sr}, 
-HERMES \cite{Airapetian:2012yg}, and COMPASS \cite{Adolph:2014pwc}.
-In Fig.~\ref{auucosphi_jlab} we compare our predictions to the HERMES and 
-COMPASS data. 
-The WW-type approximation tends to overstimate the data at
-COMPASS especially in the small-$x$ region. It is also not
-compatible with the flavor dependence seen at HERMES. 
-However, both experiments seem not to agree for instance on the shape
-of the asymmetry for negative pions or hadrons. More experimental and
-theoretical work is need to clarify whether this could be due to
-power corrections.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 the very first non-zero target single-spin asymmetry measured in SIDIS
-($F_{UL}^{\sin\phi_h}$), and and the beam-spin asymmetry  ($F_{LU}^{\sin\phi_h}$).
+($F_{UL}^{\sin\phi_h}$), and {and the beam-spin asymmetry} ($F_{LU}^{\sin\phi_h}$).
 The WW-type prediction for $F_{UU}^{\cos(\phi_h)}$ tends to overshoot
@@
 \end{tabular}
-\caption{Fitted parameters of Boer-Mulders quark distributions. Values are from Ref.~\cite{Barone:2009hw}.}
+\caption{Fitted parameters (those with error bars)
+and fixed parameters (those without error bars)
+of the Boer-Mulders quark distributions from Ref.~\cite{Barone:2009hw}.}
 \label{fitparbm}
@@
 %
+
+We use Eq.~(\ref{eq:moments}) to obtain for the second moment
+of $ h_{1T}^{\perp a}(x,\kperp^2)$ in (\ref{eq:h1Tperp}) the result
+shown below, and use it to rewrite parametrization of pretzelosity
+functions as
+\ba
+h_{1T}^{\perp (2) a}(x) =  \frac{h^{\perp a}_{1T}(x) \avkperp_{h_{1T}^\perp}^3}{2 M^2 M_{TT}^2 \avkperp} \, , \quad
+h_{1T}^{\perp q}(x,\kperp^2) =  h_{1T}^{\perp (2) q}(x)   \frac{2 M^4}{\pi \avkperp_{h_{1T}^\perp}^3} e^{-\kperp^2/{\avkperp_{h_{1T}^\perp}}}
+\label{pretzelosity_new} \ .
+\ea
 
@@
 Make sure that you do not move \texttt{example.nb} to another directory
-as it uses grids for TMDs, PDFs, and FFs.
-
-SIDIS cross section examples are presented in Fig.~\ref{fig:package}.
+as it uses grids for TMDs, PDFs, and FFs. SIDIS cross section examples are presented in Fig.~\ref{fig:package}.
 
@@
 
+%\bibliography{\BibPath/biblio_ww}
+
 \providecommand{\href}[2]{#2}\begingroup\raggedright\begin{thebibliography}{100}
@@
 
+\bibitem{Metz:2004je}
+A.~Metz and M.~Schlegel, \emph{{Twist three single spin asymmetries in
+  semiinclusive deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1140/epja/i2004-10050-8}{\emph{Eur. Phys. J.} {\bf
+  A22} (2004) 489--494}, [\href{https://arxiv.org/abs/hep-ph/0403182}{{\tt
+  hep-ph/0403182}}].
+
+\bibitem{Gamberg:2006ru}
+L.~P. Gamberg, D.~S. Hwang, A.~Metz and M.~Schlegel, \emph{{Light-cone
+  divergence in twist-3 correlation functions}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2006.07.005}{\emph{Phys. Lett.}
+  {\bf B639} (2006) 508--512},
+  [\href{https://arxiv.org/abs/hep-ph/0604022}{{\tt hep-ph/0604022}}].
+
 \bibitem{Mathematica}
@@
 
+\bibitem{Collins:2014jpa}
+J.~Collins and T.~Rogers, \emph{{Understanding the large-distance behavior of
+  transverse-momentum-dependent parton densities and the Collins-Soper
+  evolution kernel}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.91.074020}{\emph{Phys. Rev.} {\bf
+  D91} (2015) 074020}, [\href{https://arxiv.org/abs/1412.3820}{{\tt
+  1412.3820}}].
+
 \bibitem{Ma:2013aca}
@@
 
-\bibitem{Metz:2004je}
-A.~Metz and M.~Schlegel, \emph{{Twist three single spin asymmetries in
-  semiinclusive deep inelastic scattering}},
-  \href{http://dx.doi.org/10.1140/epja/i2004-10050-8}{\emph{Eur. Phys. J.} {\bf
-  A22} (2004) 489--494}, [\href{https://arxiv.org/abs/hep-ph/0403182}{{\tt
-  hep-ph/0403182}}].
-
-\bibitem{Gamberg:2006ru}
-L.~P. Gamberg, D.~S. Hwang, A.~Metz and M.~Schlegel, \emph{{Light-cone
-  divergence in twist-3 correlation functions}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2006.07.005}{\emph{Phys. Lett.}
-  {\bf B639} (2006) 508--512},
-  [\href{https://arxiv.org/abs/hep-ph/0604022}{{\tt hep-ph/0604022}}].
+\bibitem{Gutierrez-Reyes:2017glx}
+D.~Gutiérrez-Reyes, I.~Scimemi and A.~A. Vladimirov, \emph{{Twist-2 matching of
+  transverse momentum dependent distributions}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2017.03.031}{\emph{Phys. Lett.}
+  {\bf B769} (2017) 84--89}, [\href{https://arxiv.org/abs/1702.06558}{{\tt
+  1702.06558}}].
+
+\bibitem{Gutierrez-Reyes:2018qez}
+D.~Gutierrez-Reyes, I.~Scimemi, W.~J. Waalewijn and L.~Zoppi, \emph{{Transverse
+  momentum dependent distributions with jets}},
+  \href{https://arxiv.org/abs/1807.07573}{{\tt 1807.07573}}.
+
+\bibitem{Scimemi:2018mmi}
+I.~Scimemi and A.~Vladimirov, \emph{{Matching of transverse momentum dependent
+  distributions at twist-3}},  \href{https://arxiv.org/abs/1804.08148}{{\tt
+  1804.08148}}.
 
@@
 \bibitem{Parsamyan:2018zju}
-B.~Parsamyan, \emph{{First measurement of transverse-spin-dependent azimuthal
-  asymmetries in the Drell-Yan process}}, {\emph{PoS} {\bf DIS2017} (2018)
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{First measurement of
+  transverse-spin-dependent azimuthal asymmetries in the Drell-Yan process}},
+  \href{http://dx.doi.org/10.22323/1.297.0243}{\emph{PoS} {\bf DIS2017} (2018)
   243}, [\href{https://arxiv.org/abs/1801.01487}{{\tt 1801.01487}}].
@@
 
+\bibitem{Cao:2018qqf}
+X.~Cao, \emph{{Parton distributions and $\cos 2\phi_h$ asymmetry induced by
+  anomalous photon-quark coupling}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.97.114010}{\emph{Phys. Rev.} {\bf
+  D97} (2018) 114010}, [\href{https://arxiv.org/abs/1802.02417}{{\tt
+  1802.02417}}].
+
 \bibitem{Barone:2010gk}
@@
 
-\bibitem{Parsamyan:2010se}
-B.~Parsamyan, \emph{{Transverse spin dependent azimuthal asymmetries at
-  COMPASS}}, {\emph{J. Phys. Conf. Ser.} {\bf 295} (2011) 012046},
-  [\href{https://arxiv.org/abs/1012.0155}{{\tt 1012.0155}}].
+\bibitem{Parsamyan:2013fia}
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Transverse spin
+  asymmetries at COMPASS: beyond Collins and Sivers effects}}, {\emph{PoS} {\bf
+  DIS2013} (2013) 231}, [\href{https://arxiv.org/abs/1307.0183}{{\tt
+  1307.0183}}].
 
@@
 
-\bibitem{Parsamyan:2018evv}
-B.~Parsamyan, \emph{{Measurement of target-polarization dependent azimuthal
-  asymmetries in SIDIS and Drell-Yan processes at COMPASS experiment}},
-  {\emph{PoS} {\bf QCDEV2017} (2018) 042}.
-
 \bibitem{Parsamyan:2015dfa}
-B.~Parsamyan, \emph{{Transverse spin azimuthal asymmetries in SIDIS at COMPASS:
-  Multidimensional analysis}},
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Transverse spin
+  azimuthal asymmetries in SIDIS at COMPASS: Multidimensional analysis}},
   \href{http://dx.doi.org/10.1142/S2010194516600296}{\emph{Int. J. Mod. Phys.
@@
   [\href{https://arxiv.org/abs/1504.01599}{{\tt 1504.01599}}].
+
+\bibitem{Parsamyan:2018evv}
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Measurement of
+  target-polarization dependent azimuthal asymmetries in SIDIS and Drell-Yan
+  processes at COMPASS experiment}}, {\emph{PoS} {\bf QCDEV2017} (2018) 042}.
 
@@
   {\bf 1441} (2012) 229--232}.
-
-\bibitem{Parsamyan:2013fia}
-B.~Parsamyan, \emph{{Transverse spin asymmetries at COMPASS: beyond Collins and
-  Sivers effects}}, {\emph{PoS} {\bf DIS2013} (2013) 231},
-  [\href{https://arxiv.org/abs/1307.0183}{{\tt 1307.0183}}].
-
-\bibitem{Parsamyan:2018ovx}
-B.~Parsamyan, \emph{{Measurement of longitudinal-target-polarization dependent
-  azimuthal asymmetries in SIDIS at COMPASS experiment}}, {\emph{PoS} {\bf
-  DIS2017} (2018) 259}, [\href{https://arxiv.org/abs/1801.01488}{{\tt
-  1801.01488}}].
 
@@
   [\href{https://arxiv.org/abs/hep-ex/9910062}{{\tt hep-ex/9910062}}].
+
+\bibitem{Parsamyan:2018ovx}
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Measurement of
+  longitudinal-target-polarization dependent azimuthal asymmetries in SIDIS at
+  COMPASS experiment}}, {\emph{PoS} {\bf DIS2017} (2018) 259},
+  [\href{https://arxiv.org/abs/1801.01488}{{\tt 1801.01488}}].
 
@@
 
-\bibitem{private}
-\emph{{Private communications with B. Parsamyan}}, .
-
 \bibitem{Efremov:2002ut}
@@
 
+\bibitem{Mao:2013waa}
+W.~Mao and Z.~Lu, \emph{{Beam spin asymmetries of charged and neutral pion
+  production in semi-inclusive DIS}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-013-2557-9}{\emph{Eur. Phys. J.}
+  {\bf C73} (2013) 2557}, [\href{https://arxiv.org/abs/1306.1004}{{\tt
+  1306.1004}}].
+
 \bibitem{Mao:2014dva}
@@
 
-\bibitem{Courtoy:2014xea}
-A.~Courtoy, \emph{{Phenomenology of hadron structure --- why low energy physics
-  matters}}, \href{http://dx.doi.org/10.1088/1742-6596/651/1/012007}{\emph{J.
-  Phys. Conf. Ser.} {\bf 651} (2015) 012007},
-  [\href{https://arxiv.org/abs/1405.6567}{{\tt 1405.6567}}].
+\bibitem{Courtoy:2014ixa}
+A.~Courtoy, \emph{{Insights into the higher-twist distribution $e(x)$ at
+  CLAS}},  \href{https://arxiv.org/abs/1405.7659}{{\tt 1405.7659}}.
 
@@
   1607.01638}}].
+
+\bibitem{Mao:2014fma}
+W.~Mao, Z.~Lu, B.-Q. Ma and I.~Schmidt, \emph{{Double spin asymmetries
+  $A_{LT}^{\cos\phi_S}$ and $A_{LT}^{\cos(2\phi_h -\phi_S)}$ in semi-inclusive
+  DIS}}, \href{http://dx.doi.org/10.1103/PhysRevD.91.034029}{\emph{Phys. Rev.}
+  {\bf D91} (2015) 034029}, [\href{https://arxiv.org/abs/1412.7390}{{\tt
+  1412.7390}}].
+
+\bibitem{Wang:2016dti}
+X.~Wang, W.~Mao and Z.~Lu, \emph{{Double-spin asymmetry $A^{\cos\phi_S}_{LT}$
+  in semi-inclusive DIS at CLAS12 and EIC within the collinear framework}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.94.074014}{\emph{Phys. Rev.} {\bf
+  D94} (2016) 074014}, [\href{https://arxiv.org/abs/1606.01649}{{\tt
+  1606.01649}}].
+
+\bibitem{Airapetian:2018rlq}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Longitudinal
+  double-spin asymmetries in semi-inclusive deep-inelastic scattering of
+  electrons and positrons by protons and deuterons}},
+  \href{https://arxiv.org/abs/1810.07054}{{\tt 1810.07054}}.
 
@@
 
+\bibitem{Airapetian:2001eg}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Single spin
+  azimuthal asymmetries in electroproduction of neutral pions in semiinclusive
+  deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.64.097101}{\emph{Phys. Rev.} {\bf
+  D64} (2001) 097101}, [\href{https://arxiv.org/abs/hep-ex/0104005}{{\tt
+  hep-ex/0104005}}].
+
+\bibitem{DeSanctis:2000fh}
+E.~De~Sanctis, W.~D. Nowak and K.~A. Oganesian, \emph{{Single spin azimuthal
+  asymmetries in the `Reduced twist - three approximation'}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(00)00596-7}{\emph{Phys. Lett.}
+  {\bf B483} (2000) 69--73}, [\href{https://arxiv.org/abs/hep-ph/0002091}{{\tt
+  hep-ph/0002091}}].
+
+\bibitem{Oganessian:2000um}
+K.~A. Oganessian, N.~Bianchi, E.~De~Sanctis and W.~D. Nowak,
+  \emph{{Investigation of single spin asymmetries in pi+ electroproduction}},
+  \href{http://dx.doi.org/10.1016/S0375-9474(00)00609-6}{\emph{Nucl. Phys.}
+  {\bf A689} (2001) 784--792},
+  [\href{https://arxiv.org/abs/hep-ph/0010261}{{\tt hep-ph/0010261}}].
+
+\bibitem{Efremov:2001ia}
+A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Predictions for azimuthal
+  asymmetries in pion and kaon production in SIDIS off a longitudinally
+  polarized deuterium target at HERMES}},
+  \href{http://dx.doi.org/10.1007/s100520200918}{\emph{Eur. Phys. J.} {\bf C24}
+  (2002) 407--412}, [\href{https://arxiv.org/abs/hep-ph/0112166}{{\tt
+  hep-ph/0112166}}].
+
+\bibitem{Efremov:2002td}
+A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Azimuthal asymmetry in
+  electroproduction of neutral pions in semiinclusive DIS}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(01)01258-8,
+  10.1016/S0370-2693(02)02518-2}{\emph{Phys. Lett.} {\bf B522} (2001) 37--48},
+  [\href{https://arxiv.org/abs/hep-ph/0108213}{{\tt hep-ph/0108213}}].
+
+\bibitem{Efremov:2002sd}
+A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Azimuthal asymmetries and
+  Collins analyzing power}},
+  \href{http://dx.doi.org/10.1016/S0375-9474(02)01199-5}{\emph{Nucl. Phys.}
+  {\bf A711} (2002) 84--88}, [\href{https://arxiv.org/abs/hep-ph/0206267}{{\tt
+  hep-ph/0206267}}].
+
+\bibitem{Ma:2001ie}
+B.-Q. Ma, I.~Schmidt and J.-J. Yang, \emph{{Azimuthal spin asymmetries of pion
+  electroproduction}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.65.034010}{\emph{Phys. Rev.} {\bf
+  D65} (2002) 034010}, [\href{https://arxiv.org/abs/hep-ph/0110324}{{\tt
+  hep-ph/0110324}}].
+
+\bibitem{Ma:2002ns}
+B.-Q. Ma, I.~Schmidt and J.-J. Yang, \emph{{Reanalysis of azimuthal spin
+  asymmetries of meson electroproduction}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.66.094001}{\emph{Phys. Rev.} {\bf
+  D66} (2002) 094001}, [\href{https://arxiv.org/abs/hep-ph/0209114}{{\tt
+  hep-ph/0209114}}].
+
+\bibitem{Schweitzer:2003yr}
+P.~Schweitzer and A.~Bacchetta, \emph{{Azimuthal single spin asymmetries in
+  SIDIS in the light of chiral symmetry breaking}},
+  \href{http://dx.doi.org/10.1016/j.nuclphysa.2003.12.010}{\emph{Nucl. Phys.}
+  {\bf A732} (2004) 106--124},
+  [\href{https://arxiv.org/abs/hep-ph/0310318}{{\tt hep-ph/0310318}}].
+
+\bibitem{Lu:2014fva}
+Z.~Lu, \emph{{Single-spin asymmetries in electroproduction of pions on the
+  longitudinally polarized nucleon targets}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.90.014037}{\emph{Phys. Rev.} {\bf
+  D90} (2014) 014037}, [\href{https://arxiv.org/abs/1404.4229}{{\tt
+  1404.4229}}].
+
 \bibitem{Airapetian:2005jc}
@@
 
-\bibitem{Airapetian:2001eg}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Single spin
-  azimuthal asymmetries in electroproduction of neutral pions in semiinclusive
-  deep inelastic scattering}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.64.097101}{\emph{Phys. Rev.} {\bf
-  D64} (2001) 097101}, [\href{https://arxiv.org/abs/hep-ex/0104005}{{\tt
-  hep-ex/0104005}}].
+\bibitem{Mao:2014aoa}
+W.~Mao, Z.~Lu and B.-Q. Ma, \emph{{Transverse single-spin asymmetries of pion
+  production in semi-inclusive DIS at subleading twist}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.90.014048}{\emph{Phys. Rev.} {\bf
+  D90} (2014) 014048}, [\href{https://arxiv.org/abs/1405.3876}{{\tt
+  1405.3876}}].
 

### 2019-01-13 tex/test-WW-type-01c.tex
arxiv

@@
 
-\newpage
+%\newpage
 
@@
 
-The asymmetries $A_{UT, \langle y \rangle}^{\sin(\phi_h+\phi_S)}= (1-y)F_{UT}^{\sin(\phi_h+\phi_S)}/((1-y + y^2/2)F_{UU})$
-are plotted in Fig.~\ref{aut_h1_jlab} as functions of $x$ in comparison
-to HERMES \cite{Airapetian:2010ds} and $A_{UT}^{\sin(\phi_h+\phi_S)}= F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$  for COMPASS \cite{Adolph:2014zba}
-data on charged pion production from proton targets.
-We remark that the description of the $P_{hT}$--dependencies of
-this azimuthal spin asymmetry is equally satisfactory by the
-fit of Ref.~\cite{Anselmino:2013vqa}, which implies that the
-data are compatible with the Gaussian Ansatz also in this case.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The asymmetries $A_{UT, \langle y \rangle}^{\sin(\phi_h+\phi_S)}= (1-y)F_{UT}^{\sin(\phi_h+\phi_S)}/((1-y + y^2/2)F_{UU})$
+are plotted in Fig.~\ref{aut_h1_jlab} as functions of $x$ in comparison
+to HERMES \cite{Airapetian:2010ds} and $A_{UT}^{\sin(\phi_h+\phi_S)}= F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$  for COMPASS \cite{Adolph:2014zba}
+data on charged pion production from proton targets.
+We remark that the description of the $P_{hT}$--dependencies of
+this azimuthal spin asymmetry is equally satisfactory by the
+fit of Ref.~\cite{Anselmino:2013vqa}, which implies that the
+data are compatible with the Gaussian Ansatz also in this case.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
+\centering
+\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf} {\tiny (a)}%
+\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf} {\tiny (b)}%
+\includegraphics[height=3.2cm]{\FigPath/AUTPretzelosity_x.pdf}{\tiny (c)}%
+
+\includegraphics[height=3.3cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}{\tiny (d)}%
+\caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$
+	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2013fia} (a,b)
+	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES
+	\cite{Schnell:2010zza}(d) in comparison to the best fit from \cite{Lefky:2014eia}
+	(whose 1-$\sigma$ uncertainty band is compatible with zero), and our calculation for COMPASS kinematics (c). For comparison the COMPASS plots
+	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
+	}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The preliminary COMPASS data \cite{Parsamyan:2013fia} for $A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ and the preliminary HERMES data \cite{Schnell:2010zza} for
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf} {\tiny (a)}%
-\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf} {\tiny (b)}%
-\includegraphics[height=3.2cm]{\FigPath/AUTPretzelosity_x.pdf}{\tiny (c)}%
-
-\includegraphics[height=3.3cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}{\tiny (d)}%
-\caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$
-	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2013fia} (a,b)
-	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES
-	\cite{Schnell:2010zza}(d) in comparison to the best fit from \cite{Lefky:2014eia}
-	(whose 1-$\sigma$ uncertainty band is compatible with zero), and our calculation for COMPASS kinematics (c). For comparison the COMPASS plots
-	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
+%\newpage
 
@@
 \label{Sec-6:twist-2-and-WW}
-\begin{figure}[b]
+\begin{figure}[htb]
 \centering
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip} {\tiny (a)}
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim} {\tiny (b)}
-\includegraphics[width=0.37\textwidth]{\FigPath/ALT_COMPASS_x.pdf} {\tiny (c)}
-	\caption{\label{cosphihphis}
-	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$
-	 in comparison to the preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b), and our calculation for COMPASS kinematics (c) .
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newpage
+%\newpage
 
@@
 \centering
-\includegraphics[height=3.5cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} {\tiny (a)}
-
-\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_JLAB_x.pdf} {\tiny (b)}
-\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_COMPASS_x} {\tiny (c)}
+\includegraphics[height=3.45cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} {\tiny (a)}
+\hskip -0.2cm\includegraphics[height=3.45cm]{\FigPath/AULsin2phi_COMPASS_x} {\tiny (b)}
+
+\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_JLAB_x.pdf} {\tiny (c)}
 	\caption{\label{aul_jlab}
@@
 	and $A_{UL,  \langle y\rangle}^{\sin(2\phi_h)}$
-	JLab \cite{Jawalkar:2017ube} (b),  and our calculation for COMPASS kinematics (c). Results
+	JLab \cite{Jawalkar:2017ube} (c),  and our calculation for COMPASS kinematics (b). Results
 	from \cite{Avakian:2007mv} are also shown.}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/h1lperp_positivity.pdf} \quad
-\includegraphics[width=0.45\textwidth]{\FigPath/g1t_positivity.pdf}
-	\caption{\label{h1l_pos}
-	The normalized inequalities for $g^{\perp(1)q}_{1T}(x)$ and
-	$h^{\perp(1)q}_{1L}(x)$ vs $x$ which are obtained by integrating
-	(\ref{eq:positivity}) and (\ref{eq:positivity1}) over $\kperp$,
-	and normalizing with respect to the sum of the absolute
-	values of the individual terms. The result must be positive and
-	smaller than unity {\it if} the WW-type approximations
-	and the application of the Gaussian model are compatible
-	with positivity, see text. Clearly, our approach respects
-	this test of the positivity conditions.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 To conduct a test we use the Gaussian Ansatz
@@
 
-\newpage
+%\newpage
 \subsection{\boldmath Subleading-twist  $A_{LT}^{\cos\phi_S}$}
@@
 consistency of the scheme suggested in Sec.~\ref{Sec-4.4:evaluation}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pip.pdf} {\tiny (a)}
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pim.pdf} {\tiny (b)}
-\includegraphics[width=0.35\textwidth]{\FigPath/ALTcosPhi_COMPASS_x} {\tiny (c)}
-\caption{\label{altcosphis} Subleading-twist asymmetry $A_{LT}^{\cos\phi_S}$
-	as function of $x$ from scattering of 160 GeV
-	longitudinally polarized muons off a transversely polarized
-	proton target \cite{Parsamyan:2013fia} (a,b),  and our calculation for COMPASS kinematics (c).
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{figure}[h]
-\centering
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pip.pdf}  {\tiny (a)}
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pim.pdf}  {\tiny (b)}
-\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_HERMES_x.pdf}  {\tiny (c)}
-\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_COMPASS_x}  {\tiny (d)}
-\caption{\label{autsinphis}
- 	Subleading-twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which
-	is predicted to vanish in the WW-type approximation, in
-	comparison to preliminary COMPASS~\cite{Parsamyan:2013fia} (a,b) 
-	and HERMES data \cite{Schnell:2010zza} (c), and our calculation for COMPASS kinematics (d).}
-\end{figure}
-
-\newpage
+%\newpage
 \subsection{\boldmath Subleading-twist  $A_{UT}^{\sin(2\phi_h-\phi_S)}$ }
 \label{Sec-7.8:FUTsin2phi-phiS}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b]
-\centering
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (a)}%
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (b)}%
-\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf} {\tiny (c)}
-\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_COMPASS_x} {\tiny (d)}
-\caption{\label{autsin2phihphis}
-	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison
-	to preliminary COMPASS data~\cite{Parsamyan:2013fia} (a,b), and 	
-	similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to
-	preliminary HERMES data~\cite{Schnell:2010zza} (c), and our calculation for COMPASS kinematics (d).
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \centering
-\includegraphics[width=0.35\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf}
-\includegraphics[width=0.35\textwidth]{\FigPath/AUUcosphi_HERMES_x.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_HERMES_x.pdf}
 \caption{\label{auucosphi_jlab}

### 2019-01-13 arxiv1/test-WW-type.tex
mostly minor edits by Gunar

@@
 
-\title{	Semi-Inclusive Deep Inelastic Scattering
-	in Wandzura-Wilczek-type approximation}
+\title{	Semi-Inclusive Deep-Inelastic Scattering
+	in Wandzura--Wilczek-type approximation}
 
@@
 deep-inelastic scattering up to power-suppressed ${\cal O}(1/Q^2)$ terms in
-the Wandzura--Wilczek-type approximation which consists in systematically
+the Wandzura--Wilczek-type approximation, which consists in systematically
 assuming that $\bar{q}gq$--terms are much smaller than $\bar{q}q$--correlators.
@@
 approximations on the basis of available data. We make predictions that
-can be tested by data from Jefferson Lab, COMPASS, HERMES, and the future
+can be tested by data from COMPASS, HERMES, Jefferson Lab, and the future
 Electron-Ion Collider. The results of this paper can be readily used for
@@
 it is to find an unpolarized parton
-(described by PDF $f_1^a(x)$, $a=q,\,\bar q,\,g$)
+[described by PDF $f_1^a(x)$, $a=q,\,\bar q,\,g$]
 or a longitudinally polarized parton
-(described by PDF $g_1^a(x)$, $a=q,\,\bar q,\,g$)
+[described by PDF $g_1^a(x)$, $a=q,\,\bar q,\,g$]
 in a fast-moving unpolarized or longitudinally polarized nucleon,
@@
 and gluon distributions) they can be considered as rather
-well-known, and the frontier has been extended in the last years
+well known, and the frontier has been extended in the last years
 to go beyond the one-dimensional picture offered by those PDFs.
@@
 Being a vector in the plane transverse with respect to
-the light-cone direction singled out by the hard momentum flow in the process,
+the light-cone direction singled out by the hard-momentum flow in the process,
 $\kperp$ allows us to access novel information on the nucleon spin structure
@@
 twist-3 in a unique approach. Our results are of importance for measurements
-performed or in preparation at HERMES, COMPASS, JLab with
+performed or in preparation at COMPASS, HERMES, and JLab with
 12$\,$GeV beam-energy upgrade, or proposed in the long-term
-(Electron Ion Collider), and provide helpful input for the
+(Electron-Ion Collider), and provide helpful input for the
 development of Monte Carlo event generators \cite{Avakian:2015vha}.
@@
 \cite{Kotzinian:1994dv,Mulders:1995dh,Boer:1997nt,Goeke:2005hb,
-Bacchetta:2006tn} which may not be free of doubts
+Bacchetta:2006tn}, which may not be free of doubts
 \cite{Metz:2004je,Gamberg:2006ru}.
@@
 	In App.~C we describe an open-source package implemented
-	in \texttt{mathematica}~\cite{Mathematica} (already available)
+	in \texttt{Mathematica}~\cite{Mathematica} (already available)
 	and \texttt{Python} (to be released in the near future) that is
@@
 where $M_Z$ denotes the mass of the $Z^0$ electroweak gauge boson.
-In addition to $x$, $y$, $z$ the cross section is also differential
-in the azimuthal angle $\phi_h$ of the produced hadron, the square
-of its momentum component $\Phperp$ perpendicular with respect to the
+In addition to $x$, $y$, and $z$, the cross section is also differential
+in the azimuthal angle $\phi_h$ of the produced hadron and in the square
+of the hadron's momentum component $\Phperp$ perpendicular with respect to the
 virtual-photon momentum.  The cross section is also
@@
 to an arbitrary reference axis, which in case of transversely polarized
-targets is chosen to be the direction of $S_T$. In the DIS limit
-$\psi_l \approx \phi_S$, where the latter is the azimuthal angle of
+targets is chosen to be the transverse component $S_T$ of the target-spin direction.
+In the DIS limit, $\psi_l \approx \phi_S$, where the latter is the azimuthal angle of
 the spin-vector defined as in Fig.~\ref{fig-kin-SIDIS}.
-It is convenient to define the unpolarized
+It is convenient to introduce the unpolarized
 lepton--quark scattering subprocess cross section
@@
         + \lambda\,S_T\cos(2\phi_h-\phi_S)\,p_4\,A_{LT}^{\cos(2\phi_h-\phi_S)}
-	\Biggr\}
+	\Biggr\} \, .
    \hspace{1cm} \label{Eq:SIDIS-subleading}
@@
 \ee
-Here the first subscript $X=U(L)$ denotes the unpolarized beam
+Here, the first subscript $X=U(L)$ denotes the unpolarized beam
 (longitudinally polarized beam with helicity $\lambda$). The second
 subscript $Y=U(L\text{ or }T)$ refers to the target, which can be unpolarized
-(longitudinally or transversely polarized with respect to virtual photon).
+(longitudinally or transversely polarized with respect to the virtual photon).
 The superscript ``weight'' indicates the azimuthal dependence with no index
@@
   	+ \lambda\,S_T\cos(\phi_S)\,p_4\,A_{LT}^{\cos(\phi_S)}
-          \Biggr\}
+          \Biggr\} \, ,
      \hspace{1cm} \label{Eq:SIDIS-subleading-integrated}
@@
 	{\cal W}_{(\infty,\,\xi)}\,\psi_i(\xi)|N(P,S)\ra
-    	\with{ }{\xi^+\!=\!0}{$k^+ = xP^+$}
+    	\with{ }{\xi^+\!=\!0}{$k^+ = xP^+$}  \, ,
 	\ee
-where the Wilson-lines  {${\cal W}_{(0,\,\infty)}{\cal W}_{(\infty,\,\xi)}$}
+where the Wilson lines  {${\cal W}_{(0,\,\infty)}{\cal W}_{(\infty,\,\xi)}$}
 refer to the SIDIS process
@@
 The indices $j,k,l$ refer to the plane transverse with respect to the
-light-cone, $\epsilon^{ij}\equiv\epsilon^{-+ij}$ and $\epsilon^{0123}=+1$.
-Dirac-structures not listed in (\ref{Eq:TMD-pdfs-I}--\ref{Eq:TMD-pdfs-VI})
+light cone, $\epsilon^{ij}\equiv\epsilon^{-+ij}$ and $\epsilon^{0123}=+1$.
+Dirac structures not listed in (\ref{Eq:TMD-pdfs-I}--\ref{Eq:TMD-pdfs-VI})
 are twist-4 \cite{Goeke:2005hb}.
@@
 
-{Fragmentation functions are defined through the following correlator %[10]
-\cite{Metz:2016swz}
+{Fragmentation functions are defined through the following correlator~\cite{Metz:2016swz}
 (where $\bfpperp$ denotes the transverse momentum of the produced hadrons
-acquired during the fragmentation process with respect to the quark)}
+acquired during the fragmentation process with respect to the quark)}:
 \be\label{Eq:correlator-FF}
@@
 	 {p^- \!=\! P_h^-/z}
-	 {${\bm p}_\perp \!=\! -\bfpperp/z$.}
+	 {${\bm p}_\perp \!=\! -\bfpperp/z$} \, .
     \ee
@@
 \ee
-where $\omega$ is a weight function which in general depends on
+where $\omega$ is a weight function, which in general depends on
 $\bfkperp$ and $\bfpperp$.
-The 8 leading--twist structure functions are
+The 8 leading-twist structure functions are
 \begin{subequations}
@@
 \ea\end{subequations}
-At subleading--twist we have the structure functions
+At subleading-twist we have the structure functions
 \begin{subequations}
@@
 
-The structure functions surviving $\Phperp$--integration of the SIDIS cross section in
+The structure functions that survive $\Phperp$--integration of the SIDIS cross section in
 (\ref{Eq:SIDIS-leading-integrated},~\ref{Eq:SIDIS-subleading-integrated})
@@
 to connect the twist-2 TMDs $f_{1T}^\perp$, $g_{1T}^\perp$, $h_{1}^\perp$,
-$h_{1L}^\perp$ to certain higher twist collinear matrix elements.
+$h_{1L}^\perp$ to certain higher-twist collinear matrix elements.
 
@@
 derived from the QCD equations of motion and further
-constraint relations, called Lorentz-Invariance Relations (LIRs),
-(see recent review \cite{Kanazawa:2015ajw} and references therein)
+constraint relations, called Lorentz-invariance relations (LIRs),
 into a twist-2 part, and dynamical twist-3 (interactions dependent)
-$\bar{q}gq$-terms and current-quark mass terms.
+$\bar{q}gq$-terms and current-quark mass terms (see recent review \cite{Kanazawa:2015ajw} and references therein).
 
@@
 Sec.~\ref{Sec-3.1:WW-classic}, also certain TMDs and FFs
-can be decomposed in twist-2 contributions and tilde-terms.
+can be decomposed into twist-2 contributions and tilde terms.
 The latter may be assumed, in the spirit of (\ref{Eq:WW-generic}),
@@
 
-In the T-even case one obtains the following approximations \footnote{%
+In the T-even case one obtains the following approximations\footnote{%
 	Notice that Ref.~\cite{Bacchetta:2006tn} uses four-vector notation
@@
 	and analog for other scalar products of {\it transverse} vectors.
-	Notice that in our notation transverse vector
+	Notice that in our notation transverse vectors
 	are never understood as four-vectors such that
@@
 The superscript ``(1)'' denotes the first transverse
-moments of TMDs defined generically as
+moment of TMDs defined generically as
 \ba
@@
 to twist-2 TMDs and are given by the following expressions
-\cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv},
-
-\newpage
-
+\cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv}:
+%
+%\newpage
+%
 \begin{subequations}\ba
@@
 
-Insights on the relative size of hadronic matrix elements, such as
+Insights into the relative size of hadronic matrix elements, such as
 Eq.~(\ref{Eq:WW-generic}), require a non-perturbative approach. It is
-by no means obvious which small parameter in the strong interaction
+by no means obvious which small parameter in the strong-interaction
 regime would allow one to explain such results. An appealing
@@
 
-Applying the instanton vacuum model to studies of $g_T^a(x)$ and $h_L^a(x)$
+Applying the instanton vacuum model to studies of $g_T^a(x)$ and $h_L^a(x)$,
 it was predicted that matrix elements of the $\bar{q}gq$ operators defining
@@
 respective twist-2 parts, which are of order $(\rho/R)^0$.
-For Mellin moments it was found \cite{Balla:1997hf,Dressler:1999hc}
+For Mellin moments it was found that~\cite{Balla:1997hf,Dressler:1999hc}
 \be\label{Eq:WW-instanoton}
@@
 	\biggl(\frac{\rho}{R}\biggr)^{\!4} \log\biggl(\frac{\rho}{R}\biggr)
-	\sim 10^{-2}
+	\sim 10^{-2} \, ,
 \ee
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/g2.pdf}
-\includegraphics[width=0.45\textwidth]{\FigPath/g2-HERMES.pdf}
-\caption{\label{Fig:g2}
-The structure function $xg_2(x)$ in WW-approximation at $Q^2=7.1\,{\rm GeV}^2$,
-Eq.~(\ref{Eq:g2-in-WW-approximation}), for proton (P) and neutron (N) targets.
-Left panel: data from E144 and E155 experiments at
-$\la Q^2\ra=7.1\,{\rm GeV}^2$ \cite{Anthony:2002hy,Abe:1998wq}.
-Right panel: HERMES data for $Q^2>1\,{\rm GeV}^2$ with
-$\la Q^2\ra=2.4\,{\rm GeV}^2$ \cite{Airapetian:2011wu}.
-The estimate of the theoretical uncertainty is described in the text.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 We present calculations of $g_2(x)_{\rm WW}$ in Fig.~\ref{Fig:g2}.
@@
 Ref.~\cite{Accardi:2009au} we proceed as follows: we split the
-$40\,\%$ uncertainty in two parts, $\varepsilon_1=\pm 20\,\%$ and
+$40\,\%$ uncertainty into two parts: $\varepsilon_1=\pm 20\,\%$ and
 $\varepsilon_2(x)=\pm 20\,\%(1-x)^\epsilon$ with a small $\epsilon>0$,
@@
 and in line with theory predictions \cite{Balla:1997hf}.
-Our estimate with the splitted uncertainties
+Our estimate with the split uncertainties
 $\varepsilon_{1,2}$ may overestimate in certain $x$--bins the
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/g2.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/g2-HERMES.pdf}
+\caption{\label{Fig:g2}
+Left panel: The structure function $xg_2(x)$ in WW-approximation at $Q^2=7.1\,{\rm GeV}^2$,
+Eq.~(\ref{Eq:g2-in-WW-approximation}), for proton (P) and neutron (N) targets,
+and data from the SLAC E144 and E155 experiments at
+$\la Q^2\ra=7.1\,{\rm GeV}^2$ \cite{Anthony:2002hy,Abe:1998wq}.
+Right panel: HERMES data for $Q^2>1\,{\rm GeV}^2$ with
+$\la Q^2\ra=2.4\,{\rm GeV}^2$ \cite{Airapetian:2011wu}.
+The estimate of the theoretical uncertainty is described in the text.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Presently $h_L^a(x)$ is unknown.
@@
 and with $N_f = 2$ flavors of light dynamical quarks \cite{Gockeler:2005vw}.
-The obtained results were compatible with a small $\tilde{g}_T^q(x)$.
+The results obtained were compatible with a small $\tilde{g}_T^q(x)$.
 We are not aware of lattice QCD studies related to the PDF $h_L^a(x)$,
@@
 depending on $C$--parity of the involved operators \cite{Mulders:1995dh}.
-The right hand sides of
+The right-hand sides of
 Eqs.~(\ref{Eq:WW-approx-g1T-d},~\ref{Eq:WW-approx-h1L-d}) are $x$--moments
@@
 well-established methods based on operator product expansion.
-The left hand sides are moments of TMDs in $x$ and $\bfkperp$. We have to
+The left-hand sides are moments of TMDs in $x$ and $\bfkperp$. We have to
 keep in mind that TMDs diverge for large $\bfkperp$. Therefore, without
@@
 displacement of quark operators in the correlator evaluated on the lattice.
-In Fourier-space, the aforementioned divergent behavior for large $\bfkperp$
-translates into strong lattice scale and scheme dependencies at short distances
+In Fourier space, the aforementioned divergent behavior for large $\bfkperp$
+translates into strong lattice scale and scheme dependences at short distances
 $\bflperp$ between the quark operators. The $\bfkperp$ integrals needed for
-the left hand sides of Eqs.~(\ref{Eq:WW-approx-g1T-d},~\ref{Eq:WW-approx-h1L-d})
+the left-hand sides of Eqs.~(\ref{Eq:WW-approx-g1T-d},~\ref{Eq:WW-approx-h1L-d})
 correspond to the amplitudes at $\bflperp = 0$, where scheme and
-scale-dependence is greatest.  In Ref.~\cite{Musch:2010ka} Gaussian fits
+scale dependence is greatest.  In Ref.~\cite{Musch:2010ka} Gaussian fits
 have been performed to the amplitudes \emph{excluding} data at short quark
-separations $\bflperp$. The Gaussians describe the long range data quite well
+separations $\bflperp$. The Gaussians describe the long-range data quite well
 and bridge the gap at short distances $\bflperp$.
-Taking the Gaussian fit at $\bflperp = 0$, we get a value which is
-(presumably) largely lattice scheme and scale independent. We have thus
+Taking the Gaussian fit at $\bflperp = 0$, we get a value that is
+(presumably) largely lattice-scheme and scale independent. We have thus
 swept the problem of divergences under the rug. The Gaussian fit acts as
@@
 where the amplitudes $\tilde{A}$ and constants $c$ are those of Ref.~\cite{Musch:2010ka}.
-We have thus expressed the left hand side of
+We have thus expressed the left-hand side of
 Eqs.~(\ref{Eq:WW-approx-g1T-d},~\ref{Eq:WW-approx-h1L-d}) in terms of
@@
 setting the Gaussian integral $c_{2,u-d}$ of the unpolarized TMD $f_1$
-in the isovector channel (u-d) to the nucleon quark content, namely, to 1.
+in the isovector channel (u-d) to the nucleon quark content, namely to 1.
 One then assumes that the normalization of the lattice results for the
@@
 correctly. This assumption holds if renormalization is multiplicative and
-flavor-independent for the non-local lattice operators. This is not true
+flavor independent for the non-local lattice operators. This is not true
 for all lattice actions \cite{Yoon:2017qzo} %PhysRevD.96.094508
@@
 affected, so it may not play a big role for our discussion. Altogether, the
-significance of our numerical ``tests'' of WW-relations should be taken
+significance of our numerical ``tests'' of WW relations should be taken
 with a grain of salt.
 
-For the test of E.~(\ref{Eq:WW-approx-g1T-d}), we use the numbers
+For the test of (\ref{Eq:WW-approx-g1T-d}), we use the numbers
 $\int d x\;g_{1T}^{\perp(1)u}(x)\stackrel{\text{\scriptsize Gaussian}}{=}
@@
 \cite{Gockeler:2005cj} are available for $N=0,\,1,\,2,\,3$ .
-These values have been computed using (quasi-) local operators which
+These values have been computed using (quasi-)local operators that
 have been renormalized to the $\overline{MS}$ scheme at the scale
@@
 Decomposing the results from  \cite{Hagler:2007xi} into
-individual flavors, and inserting them into
-Eq.~(\ref{Eq:WW-approx-g1T-d}) we obtain
+individual flavors and inserting them into (\ref{Eq:WW-approx-g1T-d}), we obtain
 \ba
-        \underbrace{\int d x\;g_{1T}^{\perp(1)u}(x)}
+        \underbrace{\int \! d x\;g_{1T}^{\perp(1)u}(x)}
         _{= 0.1041(85) \;\mbox{\footnotesize Ref.~\cite{Musch:2010ka}}}
         &\stackrel{!}{\approx}
-        \underbrace{\frac{1}{2}\int d x\;x\,g_1^u(x)}
+        \underbrace{\frac{1}{2}\int \! d x\;x\,g_1^u(x)}
         _{= 0.104(9) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
         \hspace{2mm} , \nonumber \\
-        \underbrace{\int d x\;g_{1T}^{\perp(1)d}(x)}
+        \underbrace{\int \! d x\;g_{1T}^{\perp(1)d}(x)}
         _{= -0.0232(42) \;\mbox{\footnotesize Ref.~\cite{Musch:2010ka}}}
         &\stackrel{!}{\approx}
-        \underbrace{\frac{1}{2}\int d x\;x\,g_1^d(x)}
+        \underbrace{\frac{1}{2}\int \!d x\;x\,g_1^d(x)}
         _{= -0.025(9) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
@@
 \ba
-        \underbrace{\int d x\;h_{1L}^{\perp(1)u}(x)}
+        \underbrace{\int \! d x\;h_{1L}^{\perp(1)u}(x)}
         _{= -0.0881(72)\;\mbox{\footnotesize Ref.~\cite{Musch:2010ka}}}
         &\stackrel{!}{\approx}&
-        \underbrace{-\,\frac{1}{3}\int d x\;x\,h_1^u(x)}
+        \underbrace{-\,\frac{1}{3}\int \! d x\;x\,h_1^u(x)}
         _{= -0.093(3) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
         \hspace{2mm} , \hspace{7mm} \nonumber \\
-        \underbrace{\int d x\;h_{1L}^{\perp(1)d}(x)}
+        \underbrace{\int \! d x\;h_{1L}^{\perp(1)d}(x)}
         _{= 0.0137(34) \;\mbox{\footnotesize Ref.~\cite{Musch:2010ka}}}
         &\stackrel{!}{\approx}&
-        \underbrace{-\,\frac{1}{3}\int d x\;x\,h_1^d(x)}
+        \underbrace{-\,\frac{1}{3}\int \! d x\;x\,h_1^d(x)}
         _{= 0.018(1) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
@@
 earlier lattice work \cite{Gockeler:2000ja,Gockeler:2005vw},
-cf.\ Refs.~\cite{Metz:2008ib,Teckentrup:2009tk} and
-Sec.~\ref{Sec-3.6:models}.
+(cf.~Refs.~\cite{Metz:2008ib,Teckentrup:2009tk} and
+Sec.~\ref{Sec-3.6:models}).
 Similarly, the test (\ref{Eq:test-WW-type-lattice-h1L}) of the
 WW-type approximation (\ref{Eq:WW-approx-h1L-d}) actually constitutes
-a test of the WW-approximation (\ref{Eq:WW-original2}). The latter
-however has not been reported previously in literature, and is a
+a test of the WW-approximation (\ref{Eq:WW-original2}). The latter,
+however, has not been reported previously in literature, and constitutes a
 new result.
 
-Third, to be precise:
-Eqs.~(\ref{Eq:test-WW-type-lattice-g1T},~\ref{Eq:test-WW-type-lattice-h1L})
+Third, to be precise,
+(\ref{Eq:test-WW-type-lattice-g1T},~\ref{Eq:test-WW-type-lattice-h1L})
 test the first Mellin moments of the WW approximations
@@
 Burkhardt-Cottingham sum rule for $g_T^a(x)$ and an analogous sum rule for
-$h_L^a(x)$, see \cite{Jaffe:1996zw} and references there in.
+$h_L^a(x)$ (see \cite{Jaffe:1996zw} and references therein).
 In view of the long debate on the validity of those sum rules
@@
 \cite{Hagler:2009mb,Musch:2010ka}, this is already a remarkable and very
-interesting result. Thus, apart from the instanton calculus
+interesting result. Thus, apart from the instanton calculation
 \cite{Dressler:1999hc}, also lattice data provide support for
@@
 When gluons are absent, the correlator consists
-of 12 amplitudes \cite{Tangerman:1994bb,Mulders:1995dh}, i.e., fewer
-amplitudes than TMDs which implies relations: the qLIRs.
-In QCD the correct Lorentz decomposition requires the consideration of
+of twelve amplitudes \cite{Tangerman:1994bb,Mulders:1995dh}, i.e., fewer
+amplitudes than TMDs, which implies relations: the qLIRs.
+In QCD, the correct Lorentz decomposition requires the consideration of
 gauge links, which introduces further amplitudes. As a result one has
@@
 
-The bag, spectator and light-cone constituent quark models support
+The bag, spectator, and light-cone constituent-quark models support
 the approximations (\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L})
@@
 As they are defined in terms of quark bilinear expressions
-(\ref{Eq:correlator}) it is possible to evaluate twist-3 functions
+(\ref{Eq:correlator}), it is possible to evaluate twist-3 functions
 in quark models \cite{Jaffe:1991ra}. The tilde-terms arise due to
@@
 In the covariant parton model with intrinsic 3D-symmetric parton
-orbital motion \cite{Zavada:1996kp}  quarks are free, $\bar{q}gq$
+orbital motion \cite{Zavada:1996kp}, quarks are free, $\bar{q}gq$
 correlations absent, and all WW and WW-type relations exact
@@
 
-Noteworthy is the result from the chiral quark soliton
+Noteworthy is the result from the chiral quark-soliton
 model where the WW-type approximation (\ref{Eq:WW-type-Cahn})
@@
 for quarks and antiquarks \cite{Lorce:2014hxa}. The degrees of freedom
-in this model are quarks, antiquarks and Goldstone bosons which are
+in this model are quarks, antiquarks, and Goldstone bosons, which are
 strongly coupled (the coupling constant is $\sim 4$) and has to be
-solved using nonperturbative techniques (expansion in $1/N_c$ where
+solved using nonperturbative techniques (expansion in $1/N_c$, where
 $N_c$ is the number of colors) with the nucleon described as a
@@
 in terms of the basis functions.\footnote{%
-   Notice that SIDIS alone is not sufficient to determine
-   the 8 basis functions uniquely which appear in 6 SIDIS
-   leading-twist structure functions. It is crucial to take
+   Notice that SIDIS alone is not sufficient to uniquely determine
+   the eight basis functions that appear in six SIDIS
+   leading-twist structure functions. It is thus crucial to take
    advantage of other processes (like Drell-Yan and hadron production in
@@
 
-\subsection{Limitation of WW-type approximation}
+\subsection{Limitation of WW-type approximations}
 \label{Sec-3.8:limitations}
@@
 even if the neglected matrix element  $\la\bar{q}gq\ra$ is very small.
-Notice that this type occurs for all subleading-twist FFs, which enter
+Notice that this type occurs for all subleading-twist FFs that enter
 SIDIS structure functions only in the shape of tilde-FFs, see
@@
 also $H_1^{\perp(1)q}$ would vanish, indicating that the WW-type
-approximation has to be used with care in the chiral-odd FF sector.
+approximation has to be used with care for chiral-odd FFs.
 
@@
 correlator (\ref{Eq:correlator}) with no prefactor of $\kperp$.
-There are three cases: $f_T^a(x,k_\perp)$, $h^a(x,\kperp)$, $e_L^a(x,\kperp)$.
+There are three cases: $f_T^a(x,k_\perp)$, $h^a(x,\kperp)$, and $e_L^a(x,\kperp)$.
 Such TMDs in principle survive integration of the correlator over $\kperp$
@@
 $x\int d^2 k_\perp\,f_T^a(x,k_\perp)\,\stackrel{!?}{=}
--f_{1T}^{\perp(1)a}(x)\neq0$
+-f_{1T}^{\perp(1)a}(x)\neq0$,
 at variance with the sum rule (\ref{Eq:sum-rules-T-odd}). We
@@
 may work at small $k_\perp$ where we use them in our TMD approach.
-This would mean the UV region is essential to realize the sum rules
+This would mean that the UV region is essential to realize the sum rules
 (\ref{Eq:sum-rules-T-odd}). Alternatively, one could also envision
@@
 In the case of the subleading-twist structure functions the WW-type
-approximations in Eqs.~(\ref{Eq:WW-type-1}--\ref{Eq:WW-type-last})
+approximations in (\ref{Eq:WW-type-1}--\ref{Eq:WW-type-last})
 lead to considerable simplifications. We obtain the approximations
@@
 	{h_L^a\to h_{1L}^{\perp a}}
-	{with Eq.~(\ref{Eq:WW-type-6})}
+	{(\ref{Eq:WW-type-6})}
 	\label{Eq:WW-type-FULsinphi}\\
@@
 	{f_T^{\perp a}\to f_{1T}^{\perp a},}
-	{(h_T^a+h_T^{\perp a})\to h_{1T}^{\perp a}}{with
+	{(h_T^a+h_T^{\perp a})\to h_{1T}^{\perp a}}{
 	(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8})} \!
@@
 	{g_T^a\to g_1^a}
-	{Eq.~(\ref{Eq:WW-original1})}  \\
+	{(\ref{Eq:WW-original1})}  \\
 F_{LL}^{\cos \phi_h} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
@@
 	{g_L^{\perp a}\to g_1^a}
-	{Eq.~(\ref{Eq:WW-type-gLperp})}  \\
+	{(\ref{Eq:WW-type-gLperp})}  \\
 F_{LT}^{\cos(2\phi_h - \phi_S)} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
@@
 	{g_T^{\perp a}\to g_1^a}
-	{Eqs.~(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T})}
+	{(\ref{Eq:WW-type-gTperp},~\ref{Eq:WW-approx-g1T})}
 \ea\end{subequations}
@@
 transverse momenta (of hadrons produced in SIDIS, dileptons produced
-in the Drell--Yan process, etc) are small compared to the hard
+in the Drell--Yan process, etc.) are small compared to the hard
 scale in the process, then the Ansatz works quantitatively
@@
 $xg_T^q(x,\kperp^2)\approx\frac{k_\perp^2}{2M_N^2}\,g_{1T}^{q}(x,\kperp^2)$,
-i.e., if $g_{1T}^q(x,\kperp^2)$ was exactly Gaussian then
+e.g., if $g_{1T}^q(x,\kperp^2)$ was exactly Gaussian then
 $g_T^q(x,\kperp^2)$ certainly could not be Gaussian. If one wanted to take
@@
 $g_T^q(x,\kperp^2)$ and $g_{1T}^{q}(x,\kperp^2)$ in our example,
-may each by itself be assumed to be approximately Gaussian in $k_\perp$
+may each by itself be assumed to be approximately Gaussian in $k_\perp$,
 which is supported by quark model calculations \cite{Avakian:2010br}.
@@
 literally and assumed both TMDs to be exactly Gaussian, one would find
-``incompatibilities:'' perhaps most strikingly in the limit $k_\perp\to 0$
+``incompatibilities'', perhaps most strikingly in the limit $k_\perp\to 0$
 where the left-hand side is finite while the right-hand side vanishes.
@@
 Our procedure is as follows. In a first step we assume that all TMDs and
-FFs are (approximately) Gaussian, and solve the convolution integrals.
+FFs are (approximately) Gaussian and solve the convolution integrals.
 In the second step we use the integrated WW-type approximations to
@@
 $Q^2 = 2.4$ GeV$^2$ with $f_1^a(x)$ from \cite{Martin:2009iq},
-$g_1^a(x)$ from \cite{Gluck:1998xa}, $D_1^a(z)$ from
+$g_1^a(x)$ from \cite{Gluck:1998xa}, and $D_1^a(z)$ from
 \cite{deFlorian:2007aj}. The other four TMDs
 have no collinear counterparts.
-For $f_{1T}^{\perp a},\;h_1^{\perp a},\;H_1^{\perp a}$ it is convenient to
-consider their (1)-moments, for $ h_{1T}^{\perp a}$  the (2)-moment,
-see Eq.~(\ref{eq:moments}) for definitions.
+For $f_{1T}^{\perp a}$, $h_1^{\perp a}$, and $H_1^{\perp a}$ it is convenient to
+consider their (1)-moments, for $ h_{1T}^{\perp a}$  the (2)-moment;
+see (\ref{eq:moments}) for definitions.
 This has two important advantages. First, this step simplifies
@@
 the $k_\perp$--moments of these TMDs have in principle simple definitions
-in QCD (whereas, e.g., the function $f_{1T}^{\perp q}(x)$ can be computed in
+in QCD (whereas, e.g., the function $f_{1T}^{\perp a}(x)$ can be computed in
 models but is very cumbersome to define in QCD).
@@
 	\label{Eq:Gauss-g1}\\
-	h_{1}^{q} (x, \kperp^2) &=& h_{1}^{q} (x)\;
+	h_{1}^{a} (x, \kperp^2) &=& h_{1}^{a} (x)\;
   	\frac{1}{\,\pi \avkperp_{h_1}}\;e^{-{\kperp^2}/{\avkperp_{h_1} }} \, ,
@@
 	e^{-\pperp^2/{\avpperp_{H_{1}^\perp}}}\, ,\\
-	f_{1T}^{\perp q}(x,\kperp^2) &=&  f_{1T}^{\perp (1) q}(x)   \;
+	f_{1T}^{\perp a}(x,\kperp^2) &=&  f_{1T}^{\perp (1) a}(x)   \;
 	\frac{2 M^2}{\pi \avkperp_{f_{1T}^\perp}^2} \;
@@
 	\label{Eq:Gauss-f1Tperp}\, ,\\
-	h_{1}^{\perp q}(x,\kperp^2) &=&  h_{1}^{\perp (1) q}(x)\;
+	h_{1}^{\perp a}(x,\kperp^2) &=&  h_{1}^{\perp (1) a}(x)\;
    	\frac{2 M^2}{\pi \avkperp_{h_{1}^\perp}^2}\;
@@
 	\label{Eq:Gauss-h1perp}\, ,\\
-	h_{1T}^{\perp q}(x,\kperp^2) &=&  h_{1T}^{\perp (2) q}(x)\;
+	h_{1T}^{\perp a}(x,\kperp^2) &=&  h_{1T}^{\perp (2) a}(x)\;
    	\frac{2 M^4}{\pi \avkperp_{h_{1T}^\perp}^3} \;
@@
 	% for $\la Q^2\ra=2.37\,{\rm GeV}^2$, $\la x\ra=0.24$, $\la z\ra=0.30$
-	at JLab with 5.75 GeV beam \cite{Osipenko:2008aa}.
+	at JLab with a 5.75 GeV $e^{-}$ beam \cite{Osipenko:2008aa}.
 Middle panel:
@@
 where pions or kaons were measured in the scattering of 27.6 GeV
-positrons from the HERA polarized positron storage ring at DESY
+electrons or positrons of HERA's polarized lepton storage ring
 off proton and deuteron targets in the SIDIS kinematics
@@
 
-To streamline the presentation we refer to the comprehensive Appendix
-on the used parametrizations (App.~\ref{App:basis}), and for
-technical details on the Gaussian Ansatz (App.~\ref{App:factor}).
+To streamline the presentation we refer to the comprehensive App.~\ref{App:basis}
+on the parametrizations used, 
+and for technical details on the Gaussian Ansatz to App.~\ref{App:factor}.
 
@@
 \caption{\label{jlab_ALL}
-	$A_{LL,\la y\ra}$ as function of $P_{hT}$ vs
-	JLab data \cite{Avakian:2010ae}
+	$A_{LL,\la y\ra}$ as function of $P_{hT}$ vs.~JLab
+	data \cite{Avakian:2010ae}
  	for $\pi^+$, $\pi^0$, $\pi^-$. The solid lines are
@@
 	$\langle x \rangle = 0.25$,
-	$\langle z \rangle = 0.5$, $\langle Q^2 \rangle = 1.67$ GeV$^2$.
+	$\langle z \rangle = 0.5$, and $\langle Q^2 \rangle = 1.67$ GeV$^2$.
 }
@@
 
-The definition of the asymmetry in  the JLab experiment \cite{Avakian:2010ae}
-was
+The definition of the asymmetry used by the JLab experiment \cite{Avakian:2010ae} is
 \be\label{Eq:ALLy}
@@
 	= \frac{\la y (2-y) \; F_{LL}(x,z,\Phperp)\ra}
-	{\la(1+(1-y)^2) \; F_{UU}(x,z,\Phperp)\ra}
+	{\la(1+(1-y)^2) \; F_{UU}(x,z,\Phperp)\ra} \, ,
 \ee
@@
 interactions of the struck quark and the rest of the nucleon and could
-not exist without the contribution of the orbital angular momentum of
+not exist without contributions of orbital angular momentum of
 partons to the spin of the nucleon. As such it encodes the correlation
@@
 Only if the relevant weight is $\omega^{\{0\}}$ we obtain 
-``collinear structure functions:''  $F_{UU}(x,z)$, $F_{LL}(x,z)$
-in Secs.~\ref{Sec-5.1:FUU-basis}, \ref{Sec-5.2:FLL-basis}
+``collinear structure functions'':  $F_{UU}(x,z)$, $F_{LL}(x,z)$
+in Secs.~\ref{Sec-5.1:FUU-basis}, \ref{Sec-5.2:FLL-basis},
 and below in Secs.~\ref{Sec-7.2:FLTcosphiS}, \ref{Sec-7.6:FUTsinphiS}.
@@
 We stress this important point by displaying the dependence of
-the structure functions on the mean transverse hadron momenta, for instance
+the structure functions on the mean transverse momentum, e.g.,
 $F_{UT}^{\sin(\phi_h-\phi_S)}(x,z,\la\Phperp\ra) =
@@
 We do not show here the description of the $P_{hT}$--dependence of the
-data but it is well-described by the fit of \cite{Anselmino:2011gs}
+data but it is well described by the fit of \cite{Anselmino:2011gs}
 which confirms that the Gaussian model works also in this case.
@@
 \cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,Bacchetta:2012ty,
-Radici:2015mwa,Radici:2018iag}. The first polarized Drell-Yan data were
+Radici:2015mwa,Radici:2018iag}. The first polarized Drell--Yan data were
 measured by COMPASS~\cite{Aghasyan:2017jop,Parsamyan:2018zju}.
@@
 fundamental correlation between the transverse spin of a fragmenting quark
-and the transverse momentum of the final produced hadron \cite{Collins:1992kk}.
+and the transverse momentum of the final hadron produced~\cite{Collins:1992kk}.
 
@@
 to HERMES \cite{Airapetian:2010ds} and $A_{UT}^{\sin(\phi_h+\phi_S)}= F_{UT}^{\sin(\phi_h+\phi_S)}/F_{UU}$  for COMPASS \cite{Adolph:2014zba}
-data on charged pion production from proton targets.
-We remark that the description of the $P_{hT}$--dependencies of
+data on charged-pion production from proton targets.
+We remark that the description of the $P_{hT}$--dependences of
 this azimuthal spin asymmetry is equally satisfactory by the
@@
 The structure function $F_{UU}^{\cos(2\phi_h)}$ arises from a convolution of
-the Collins fragmention function and the Boer-Mulders TMD $h_{1}^{\perp q}$
+the Collins fragmention function and the Boer-Mulders TMD $h_{1}^{\perp }$,
 which describes
@@
 Boer--Mulders contribution to $A_{UU}^{\cos(2\phi_h)}$, which does not describe
-the data well, especially for COMPASS one can see that calculation and
+the data well. Especially for COMPASS one can see that calculation and
 data are of opposite signs. In fact, it is suspected that this observable
 receives a significant contribution from the Cahn effect \cite{Cahn:1978se},
-a term of higher-twist character of the type $\la\Phperp^2\ra/Q^2$ which
+a term of higher-twist character of the type $\la\Phperp^2\ra/Q^2$, which
 is not negligible in fixed-target experiments as shown in
@@
 In the phenomenological works
-\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa} an attempt was
+\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa}, an attempt was
 made to estimate and correct for this contribution in order
@@
 the current state of art. It is unknown whether other asymmetries
-could be similarly effected by such type of power-corrections.
+could be similarly effected by such type of power corrections.
 This is an important point to be kept in mind as the lesson
@@
 values of $Q$ could be achieved in the fixed target experiments.
-A notable exception is COMPASS where the largest $x$--bins
+A notable exception is COMPASS, where the largest $x$--bins
 (where $Q^2$ is largest) bear the best hints on this TMD,
 see Fig.~\ref{aut_h1tp_jlab}.
-Future high luminosity data from JLab 12 are expected
+Future high-luminosity data from JLab 12 are expected
 to significantly improve our knowledge of this TMD.
@@
 
-Even the well-known collinear functions $f_1^a(x)$, $g_1^a(x)$ have
+Even the well-known collinear functions $f_1^a(x)$ and $g_1^a(x)$ have
 statistical uncertainties and systematic uncertainties (the latter
-introduced by choosing a certain fit Ansatz which however can be
-avoided through neural network techniques \cite{Ball:2014uwa}).
+introduced by choosing a certain fit Ansatz, which however can be
+avoided through neural-network techniques \cite{Ball:2014uwa}).
 These uncertainties as well as those of $D_1^a(z)$ can safely
@@
 making projections based on the WW-type approximation. To avoid
-cumbersome and difficult to interpret figures we will therefore
+cumbersome and difficult-to-interpret figures, we will therefore
 refrain from indicating the uncertainties associated with our
@@
 \label{Sec-6:twist-2-and-WW}
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/g1t.pdf} \quad
-\includegraphics[width=0.45\textwidth]{\FigPath/h1Lperp.pdf}
-	\caption{\label{g1t_h1l_functions}
-	$g^{\perp (1) q}_{1T}(x)$ (left panel) and
-	$h^{\perp (1) q}_{1L}(x)$ distributions (right panel)
-	for $u$-- and $d$--flavor
-	as predicted by the WW-type approximations in
-	Eqs.~(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}).}
-\end{figure}
-
-Two out of the 8 leading--twist structure functions
+
+Two out of the eight leading-twist structure functions
 can be described in the WW-type approximation thanks to
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/g1t.pdf} \quad
+\includegraphics[width=0.45\textwidth]{\FigPath/h1Lperp.pdf}
+	\caption{\label{g1t_h1l_functions}
+	$g^{\perp (1) q}_{1T}(x)$ (left panel) and
+	$h^{\perp (1) q}_{1L}(x)$ distributions (right panel)
+	for up and down flavor
+	as predicted by the WW-type approximations in
+	Eqs.~(\ref{Eq:WW-approx-g1T},~\ref{Eq:WW-approx-h1L}).}
+\end{figure}
+
 \subsection{\boldmath Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$}
@@
 We assume for $g^{\perp}_{1T}$ the Gaussian Ansatz as shown
-in Eq.~(\ref{eq:g1t}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs},
+in (\ref{eq:g1t}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs},
 see also \cite{Kotzinian:2006dw}, and evaluate $g^{\perp (1) q}_{1T}(x)$
-using Eq.~(\ref{Eq:WW-approx-g1T}), which yields the result
+using (\ref{Eq:WW-approx-g1T}), which yields the result
 shown in Fig.~\ref{g1t_h1l_functions}.
-For our numerical estimates we use $\avkperp_{g_{1T}^\perp} = \avkperp_{g_{1}}$
+For our numerical estimates we use $\avkperp_{g_{1T}^\perp} = \avkperp_{g_{1}}$,
 which is supported by lattice results \cite{Hagler:2009mb}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htb]
+\begin{figure}[b]
 \centering
@@
 	\caption{\label{cosphihphis}
-	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$
-	 in comparison to the preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b), and our calculation for COMPASS kinematics (c) .
+	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$:
+	 preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b); and our calculation for COMPASS kinematics (c).
 	}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 In the Gaussian Ansatz the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$
@@
 Parsamyan:2007ju,Parsamyan:2015dfa,Parsamyan:2018evv} and HERMES~\cite{Pappalardo:2011cu,Pappalardo:2012zz} (for the latter two experiments only preliminary results are available so far).
- Fig.~\ref{cosphihphis}
-shows the preliminary results from the 2010 COMPASS data \cite{Parsamyan:2013fia}.
-We approximate the
-charged hadrons ($70-80\,\%$ of which are $\pi^\pm$ at COMPASS) by
+Figure~\ref{cosphihphis} shows the preliminary results from the 2010 COMPASS data \cite{Parsamyan:2013fia}.
+We approximate the charged hadrons ($70-80\,\%$ of which are $\pi^\pm$ at COMPASS) by
 charged pions, see App.~\ref{App:basis-f1-D1}.
@@
 
-%\ps{\ \\
-%PS: HERE IS ENOUGH SPACE TO
-%\begin{itemize}
-%\item 	SHOW PLOTS WITH JLAB DATA \cite{Huang:2011bc} FOR PI$\pm$ FROM NEUTRON,
-%\item	OR WRITE SOME MORE BLA, BLA, BLA.
-%\end{itemize}
-%I HAVE NO INSPIRATION FOR BLA, BLA HERE. \\
-%\red{SHOULD WE ADD THE JLAB HALL-A FIGURES?} \\ }
-
 %\newpage
@@
 We use the Gaussian form for the Kotzinian--Mulders function
-$h_{1L}^{\perp a}$, Eq.~(\ref{eq:h1l_final}) in
+$h_{1L}^{\perp a}$, (\ref{eq:h1l_final}) in
 App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, with
@@
 supported by lattice data \cite{Hagler:2009mb}.
->From (\ref{Eq:WW-approx-h1L}) we obtain the WW-type estimate
+From (\ref{Eq:WW-approx-h1L}) we obtain the WW-type estimate
 for $h_{1L}^{\perp(1) a}(x)$ shown in Fig.~\ref{g1t_h1l_functions}.
@@
 	\caption{\label{aul_jlab}
-	Leading twist $A_{UL}^{\sin(2\phi_h)}$ vs $x$ from the WW-type
-	approximation in comparison to data from
-	HERMES \cite{Airapetian:1999tv}, and $A_{UL}^{\sin(2\phi_h)}$
+	Leading twist $A_{UL}^{\sin(2\phi_h)}$ vs.~$x$ from
+	HERMES \cite{Airapetian:1999tv} and 
 	COMPASS \cite{Parsamyan:2018ovx,Parsamyan:2018evv} (a),
-	and $A_{UL,  \langle y\rangle}^{\sin(2\phi_h)}$
-	JLab \cite{Jawalkar:2017ube} (c),  and our calculation for COMPASS kinematics (b). Results
-	from \cite{Avakian:2007mv} are also shown.}
+	$A_{UL,  \langle y\rangle}^{\sin(2\phi_h)}$ from
+	JLab \cite{Jawalkar:2017ube} (b),  and from our calculation for COMPASS kinematics in the WW-type
+	approximation (c). Results
+	from \cite{Avakian:2007mv} are also shown in comparison to the COMPASS data.}
 \end{figure}
@@
 HERMES experiment measured with the 27.6 GeV positron
-beam from the HERA polarized positron storage ring at DESY for
+beam of HERA for
 $1\,{\rm GeV}^2 < Q^2 < 15 \,{\rm GeV}^2$, $W > 2\,{\rm GeV}$,
-$0.023 < x < 0.4$, $y < 0.85$.
+$0.023 < x < 0.4$, and $y < 0.85$.
 The COMPASS data were taken in 2007 (160 GeV) and 2011 (200 GeV) and show
@@
 (see Sec.~\ref{Sec-2.1:SIDIS+structure-functions}),
-the HERMES data is adequately (``$D(y)$~--'')rescaled.
+the HERMES data are adequately (``$D(y)$~--'')rescaled.
 The CLAS $\pi^0$ data in the right panel were measured using 6$\,$GeV
@@
 longitudinally polarized protons in a cryogenic $^{14}$NH$_3$
-target in the kinematics $1.0\,{\rm GeV}^2 < Q^2 < 3.2\,{\rm GeV}^2$,
+target in the kinematic region of $1.0\,{\rm GeV}^2 < Q^2 < 3.2\,{\rm GeV}^2$,
 $0.12 < x < 0.48$ and $0.4 < z < 0.7$ \cite{Jawalkar:2017ube}.
@@
 bounds \cite{Bacchetta:1999kz}.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/h1lperp_positivity.pdf} \quad
-\includegraphics[width=0.45\textwidth]{\FigPath/g1t_positivity.pdf}
-	\caption{\label{h1l_pos}
-	The normalized inequalities for $g^{\perp(1)q}_{1T}(x)$ and
-	$h^{\perp(1)q}_{1L}(x)$ vs $x$ which are obtained by integrating
-	(\ref{eq:positivity}) and (\ref{eq:positivity1}) over $\kperp$,
-	and normalizing with respect to the sum of the absolute
-	values of the individual terms. The result must be positive and
-	smaller than unity {\it if} the WW-type approximations
-	and the application of the Gaussian model are compatible
-	with positivity, see text. Clearly, our approach respects
-	this test of the positivity conditions.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The Kotzinian--Mulders function $h^{\perp q}_{1L}$ in conjunction with
@@
 and $h^{\perp q}_{1L}$ and Gaussian Ansatz for all TMDs), and (ii) we deal
-with first extractions which have sizable uncertainties including
+with first extractions, which have sizable uncertainties including
 poorly controlled systematic uncertainties.
@@
 
-To conduct a test we use the Gaussian Ansatz
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/h1lperp_positivity.pdf} \quad
+\includegraphics[width=0.45\textwidth]{\FigPath/g1t_positivity.pdf}
+	\caption{\label{h1l_pos}
+	The normalized inequalities for $g^{\perp(1)q}_{1T}(x)$ and
+	$h^{\perp(1)q}_{1L}(x)$ vs.~$x$ which are obtained by integrating
+	(\ref{eq:positivity}) and (\ref{eq:positivity1}) over $\kperp$
+	and normalizing with respect to the sum of the absolute
+	values of the individual terms. The result must be positive and
+	smaller than unity {\it if} the WW-type approximations
+	and the application of the Gaussian model are compatible
+	with positivity, see text. Clearly, our approach respects
+	this test of the positivity conditions.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In order to conduct a test we use the Gaussian Ansatz
 (\ref{Eq:Gauss-f1}, \ref{Eq:Gauss-h1}, \ref{Eq:Gauss-f1Tperp},
@@
 TMDs and integrate over $k_\perp$. The results are shown in
-Fig.~\ref{h1l_pos} where we plot the ``normalized inequalities''
+Fig.~\ref{h1l_pos}, where we plot the ``normalized inequalities''
 defined as follows:
@@
 
-WW-type approximations can be applied to all 8 subleading--twist asymmetries,
+WW-type approximations can be applied to all eight subleading-twist asymmetries,
 see Sec.~\ref{Sec-4.2:WW-twist-3}. In this section we discuss all of them,
@@
 We start our discussion with the structure function $F_{LU}^{\sin\phi_h}$,
-Eq.~(\ref{FLUsinphi}), containing 4 terms:
-2 term are proportional to pure twist-3 fragmentation functions
-$\tilde{G}^{\perp a}$ and $\tilde{E}^a$ and neglected; the other 2
+Eq.~(\ref{FLUsinphi}), containing four terms:
+two terms are proportional to the pure twist-3 fragmentation functions
+$\tilde{G}^{\perp a}$ and $\tilde{E}^a$ and neglected here; the other two
 terms are proportional to the twist-3 TMDs $e^a$ and $g^{\perp a}$, which
 also turn out to be given in terms of pure twist-3 terms upon the
-inspection of Eqs.~(\ref{Eq:WW-type-1},~\ref{Eq:WW-type-gperp}).
+inspection of (\ref{Eq:WW-type-1},~\ref{Eq:WW-type-gperp}).
 Hence, after consequently applying the WW-type approximation, we are left
@@
 
-Indeed, data from JLab, HERMES and COMPASS show a clearly non-zero
+Indeed, data from COMPASS, HERMES, and JLab show a clearly non-zero
 asymmetry $A_{LU}^{\sin\phi_h} = F_{LU}^{\sin\phi_h}/F_{UU}$ of the order of 2\,$\%$
@@
 the experimental result (\ref{Eq:ALU-small})
-contains kinematic prefactors which help to reduce the value.
-Second, the denominator contains $f_1^a$ and $D_1^a$ which are the
+contains kinematic prefactors, which help to reduce the value.
+Second, the denominator contains $f_1^a$ and $D_1^a$, which are the
 largest TMD and FF because of positivity constraints. Third, the
-numerator is a sum of 4 terms, so its overall smallness could result
+numerator is a sum of four terms, so its overall smallness could result
 from cancellation of different terms, rather than indicating that
@@
 
-In  WW-type approximation the structure function
-$F_{LT}^{\cos\phi_S}$ arises from $g_T^a(x,\kperp)$ and $D_1^a(z,\pperp)$
+In the WW-type approximation the structure function
+$F_{LT}^{\cos\phi_S}$ arises from $g_T^a(x,\kperp)$ and $D_1^a(z,\pperp)$,
 whose collinear counterparts are more or less known, see
 Secs.~\ref{Sec-3.4:WW-classic-experiment} and \ref{Sec-5.1:FUU-basis}.
-We assume the Gaussian Ansatz for $g_T^a(x,\kperp)$ shown in
-Eq.~(\ref{eq:gtnew}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}
+We assume the Gaussian Ansatz for $g_T^a(x,\kperp)$, shown in
+(\ref{eq:gtnew}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs},
 with ${\avkperp_{g_T}}={\avkperp_{g_1}}$. We then determine $g^{q}_{T}(x)$
-according to Eq.~(\ref{Eq:WW-original1}), which is a well-tested
+according to (\ref{Eq:WW-original1}), which is a well-tested
 approximation in DIS, see Sec.~\ref{Sec-3.4:WW-classic-experiment}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Notice that we followed here the scheme explained in
@@
 less bulky) expression in (\ref{Eq:FLTcosphiS-Gauss}) automatically
-yields (\ref{Eq:FLTcosphiS-Gauss-b}) which is the correct collinear
-result for this SIDIS function in Eq.~(\ref{Eq:FLT-collinear})
+yields (\ref{Eq:FLTcosphiS-Gauss-b}), which is the correct collinear
+result for this SIDIS function in (\ref{Eq:FLT-collinear})
 in WW-type approximation. This technical remark confirms the
@@
 well the WW-type approximation works in this case. Such data
-could come from JLab12 experiments.
+could come from the JLab12 experiments.
 For further model studies of this asymmetry we refer to
@@
 $g_T^{\perp a}(x,\kperp)$, for which we assume a Gaussian Ansatz according to
-Eq.~(\ref{eq:gtperpnew}) in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs},
+(\ref{eq:gtperpnew}) in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs},
 and use the WW-type approximation (\ref{Eq:WW-type-gTperp}) as
@@
 of $x$ are displayed in Fig.~\ref{altcos2phihphis} in
-comparison to preliminary COMPASS data from Ref.~\cite{Parsamyan:2013fia}.
+addition to preliminary COMPASS data from Ref.~\cite{Parsamyan:2013fia}.
 The asymmetry is very small, so at the current stage one may
@@
 $A_{LT}^{\cos(2\phi_h -\phi_S)}$ is compatible with available data. In view
-of the smallness of the effect, cf.\  Fig.~\ref{altcos2phihphis},
+of the smallness of the effect (cf.~Fig.~\ref{altcos2phihphis}),
 it might be difficult to obtain more quantitative insights
-in near future.
-
-For completeness Fig.~\ref{altcos2phihphis} shows results from a
-quark-diquark model calculation were a more sizable asymmetry was predicted
+in the near future.
+
+For completeness, Fig.~\ref{altcos2phihphis} shows also results from a
+quark-diquark model calculation, where a more sizable asymmetry was predicted
 \cite{Kotzinian:2008fe}. Let us remark that the $A_{LT}^{\cos(2\phi_h -\phi_S)}$
 asymmetry was also studied in a different spectator model in
-Ref.~\cite{Mao:2014fma} which predicts asymmetries of the same
-sign but smaller magnitudes of ${\cal O}(1\,\%)$.
+Ref.~\cite{Mao:2014fma} predicting asymmetries of the same
+sign but of smaller magnitudes of ${\cal O}(1\,\%)$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h]
+\begin{figure}[t]
 \centering
@@
 \caption{\label{altcos2phihphis} $A_{LT}^{\cos(2\phi_h - \phi_S)}$
-	as a function of $ x $ from a proton target in comparison to
+	as a function of $ x $ from a proton target: 
 	preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b), and our calculation for COMPASS kinematics (c). The smallness
@@
 is due to $g_{L}^{\perp q}(x,k_\perp)$, which we assume to have a
-Gaussian $k_\perp$--behavior according to Eq.~(\ref{eq:gLperp})
+Gaussian $k_\perp$--behavior according to (\ref{eq:gLperp})
 in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} with
@@
 WW-type approximation in \cite{Anselmino:2006yc} and more recently
-also in the model study \cite{Mao:2016hdi}. The predictions from
+also in a model study \cite{Mao:2016hdi}. The predictions from
 both works are included in Fig.~\ref{allcosphi_jlab} for
@@
 
-\
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
+\begin{figure}
 \centering
@@
 	\caption{\label{allcosphi_jlab} $A_{LL}^{\cos(\phi_h)}$
-	as a function of $ x $ from the WW-type approximation in
-	comparison to the preliminary COMPASS data
-	\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (a), and our calculation for COMPASS kinematics (b). }
+	as a function of $ x $: preliminary COMPASS data
+	\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (a),  
+	our calculation for COMPASS kinematics using the WW-type approximation (b). }
 \end{figure}
@@
 
-This was historically the first measurement of a single spin
+This was historically the first measurement of a single-spin
 asymmetry in SIDIS, by HERMES \cite{Airapetian:1999tv,Airapetian:2001eg},
@@
 Efremov:2002sd,Ma:2001ie,Ma:2002ns,Schweitzer:2003yr}. A more recent
-smodel study was reported in \cite{Lu:2014fva}.
+model study was reported in \cite{Lu:2014fva}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b]
+\begin{figure}
 \centering
@@
 \caption{\label{aulsinphi_jlab}
-	$A_{UL}^{\sin\phi_h}$ for proton target vs $x$ from WW-type
+	$A_{UL}^{\sin\phi_h}$ for proton target vs.~$x$ from WW-type
 	approximation in comparison to data for the following hadrons.
@@
 
-In this structure function some interesting new features occur.
-The first feature is that after applying the WW-type approximation,
-not one but three terms are left, cf.\
-Eqs.~(\ref{FUTsinphiS},~\ref{Eq:WW-type-FUTsinphiS}):
-two terms proportional to $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$,
-and one term proportional to $f_T^q(x,\kperp)$, which is associated with
-the second interesting feature. This T-odd TMD must satisfy the sum rule
-$\int d^2\kperp \,f_T^q(x,\kperp)=0$, see Eq.~(\ref{Eq:sum-rules-T-odd})
-and Sec.~\ref{Sec-3.8:limitations}.
-
 \begin{figure}[htb]
@@
  	Subleading-twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which
-	is predicted to vanish in the WW-type approximation, in
-	comparison to preliminary COMPASS~\cite{Parsamyan:2013fia} (a,b) 
-	and HERMES data \cite{Schnell:2010zza} (d), and our calculation for COMPASS kinematics (c).}
+	is predicted to vanish in the WW-type approximation: 
+	preliminary COMPASS~\cite{Parsamyan:2013fia} (a,b), 
+	our calculation for COMPASS kinematics (c), and HERMES data \cite{Schnell:2010zza} (d).}
 \end{figure}
 
-This could be implemented in two ways: one could describe it with a
+In this structure function some interesting new features occur.
+The first feature is that after applying the WW-type approximation,
+not one but three terms are left, cf.\
+Eqs.~(\ref{FUTsinphiS},~\ref{Eq:WW-type-FUTsinphiS}):
+two terms proportional to $h_T^{\perp q}(x,\kperp)$ and $h_T^q(x,\kperp)$, respectively, 
+and one term proportional to $f_T^q(x,\kperp)$, which is associated with
+the second interesting feature. This T-odd TMD must satisfy the sum rule
+$\int d^2\kperp \,f_T^q(x,\kperp)=0$, see (\ref{Eq:sum-rules-T-odd})
+and Sec.~\ref{Sec-3.8:limitations}.
+This could be implemented in two ways. One could describe it with a
 superposition of Gaussians, see App.~\ref{App-B:comment-Todd-twist-3}.
@@
 $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_1^{ }}$.
+
 The third interesting feature is the occurrence of a term that drops
 out upon integrating the structure function over $\Phperp$, cf.\
-Eq.~(\ref{Eq:FUTsinphiS-final-PhT}) vs.\ (\ref{Eq:FUTsinphiS-final}).
+(\ref{Eq:FUTsinphiS-final-PhT}) vs.\ (\ref{Eq:FUTsinphiS-final}).
 This is a property of the weight $\omega^{\{2\}}_{\rm B}$, see
-Eq.~(\ref{Eq:wi}) and App.~\ref{App:factor} (which appears also
-in $F_{LT}^{\cos\phi_S}$, Eq.~(\ref{FLTcosphiS}), where it drops
+(\ref{Eq:wi}) and App.~\ref{App:factor} (which appears also
+in $F_{LT}^{\cos\phi_S}$, (\ref{FLTcosphiS}), where it drops
 out in WW-type approximation). This property can help
@@
 
-The final result in Eq.~(\ref{Eq:FUTsinphiS-final}) is the consistent
+The final result in (\ref{Eq:FUTsinphiS-final}) is the consistent
 result for $F_{UT}^{\sin\phi_S}(x,z)$ in WW-type
-approximation, see Eq.~(\ref{Eq:FUT-collinear}). Our prediction is
+approximation, see (\ref{Eq:FUT-collinear}). Our prediction is
 therefore $A_{UT}^{\sin\phi_S}(x)=0$. Preliminary
@@
 thus inconsistent with this WW-type prediction. In order to
-describe the data it is therefore necessary to explicitly model
+describe the data, it is therefore necessary to explicitly model
 the involved tilde-functions. For a recent model study we refer
-to \cite{Mao:2014aoa}.
+to Ref.~\cite{Mao:2014aoa}.
 
@@
 surviving the WW-type approximation. We assume Gaussian Ansatz for
-$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$
-according to Eqs.~(\ref{eq:hTperpnew},~\ref{eq:hTnew},~\ref{eq:ftperpnew})
-in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} with
+$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, and $h_T^q(x,\kperp)$,
+according to (\ref{eq:hTperpnew},~\ref{eq:hTnew},~\ref{eq:ftperpnew})
+in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, with
 $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_{1T}^\perp}$
-and $\la\kperp^2\ra_{f_T^\perp}=\la\kperp^2\ra_{f_{1T}^\perp}$. The obtained
-expressions are given by
+and $\la\kperp^2\ra_{f_T^\perp}=\la\kperp^2\ra_{f_{1T}^\perp}$. The 
+expressions obtained are given by
 \begin{subequations}\begin{alignat}{1}
@@
 	b^{(2)}_{\rm AB}
-	\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\,{\cal G}(\Phperp)&\Biggr]
+	\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\,{\cal G}(\Phperp)&\Biggr] \, ,
 	\label{Eq:FUTsin2phi-phiS-Gauss-PhT}\\
@@
 	c^{(2)}_{\rm AB}
-	\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2} & \Biggr]
+	\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2} & \Biggr] \, ,
 	\label{Eq:FUTsin2phi-phiS-Gauss}
 \end{alignat}\end{subequations}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htb]
-\centering
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (a)}%
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (b)}%
-\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_COMPASS_x} {\tiny (c)}
-\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf} {\tiny (d)}
-\caption{\label{autsin2phihphis}
-	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$  in comparison
-	to preliminary COMPASS data~\cite{Parsamyan:2013fia} (a,b), and 	
-	similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to
-	preliminary HERMES data~\cite{Schnell:2010zza} (d), and our calculation for COMPASS kinematics (c).
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 with respectively
@@
 $\lambda=z^2\la\kperp^2\ra_{h_T^\perp}+\la\pperp^2\ra_{H_1^\perp}$ in the second
-terms in
-Eqs.~(\ref{Eq:FUTsin2phi-phiS-Gauss-PhT},~\ref{Eq:FUTsin2phi-phiS-Gauss}).
+terms in (\ref{Eq:FUTsin2phi-phiS-Gauss-PhT},~\ref{Eq:FUTsin2phi-phiS-Gauss}).
 The coefficients
@@
 with a zero effect within uncertainties.
-For comparison Fig.~\ref{altcos2phihphis} shows also the predictions
+For comparison, Fig.~\ref{altcos2phihphis} shows also the predictions
 from the quark-diquark model calculation of Ref.~\cite{Kotzinian:2008fe}.
@@
 
-\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (a)}%
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (b)}%
+\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_COMPASS_x} {\tiny (c)}
+\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf} {\tiny (d)}
+\caption{\label{autsin2phihphis}
+	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$: 
+	preliminary COMPASS data~\cite{Parsamyan:2013fia} (a,b), our calculation for COMPASS kinematics (c),
+	and similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to
+	preliminary HERMES data~\cite{Schnell:2010zza} (d).
+	}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \subsection{\boldmath Subleading-twist  $A_{UU}^{\cos\phi_h}$ }
@@
 Sec.~\ref{Sec-7.6:FUTsinphiS}.
-Using the Gaussian Ansatz for $f^\perp(x,\kperp)$ in Eq.~(\ref{eq:fperpnew})
-of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} we obtain
+Using the Gaussian Ansatz for $f^\perp(x,\kperp)$ in (\ref{eq:fperpnew})
+of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, we obtain
 \begin{subequations}\begin{alignat}{1}
@@
 	  \biggl(\frac{z \Phperp} {\lambda}\biggr)\, { \cal G}(\Phperp )
-	\Biggr] \label{Eq:XXXa}\\
+	\Biggr] \, ,  \label{Eq:XXXa}\\
 	F_{UU}^{\cos\phi_h}(x,z,\la\Phperp\ra)
@@
 	  \biggl(\frac{z}{\lambda^{1/2}}\biggr)
-	\Biggr] \label{Eq:XXXb}
+	\Biggr] \, , \label{Eq:XXXb}
 \end{alignat}\end{subequations}
@@
 $b^{(1)}_i$ and $c^{(1)}_i$ are defined in App.~\ref{App:convol-details}.
-Note that Eq.~(\ref{Eq:XXXa}) is valid in the ``scheme'' of
-footnote~\ref{Footnote:fT-single-Gauss}, but Eq.~(\ref{Eq:XXXa})
-holds independently how one implements the sum rule (\ref{Eq:sum-rules-T-odd})
+Note that (\ref{Eq:XXXa}) is valid in the ``scheme'' of
+footnote~\ref{Footnote:fT-single-Gauss}, but (\ref{Eq:XXXa})
+holds independent of how one implements the sum rule (\ref{Eq:sum-rules-T-odd})
 (as in footnote~\ref{Footnote:fT-single-Gauss} or
@@
 
-For $f^{\perp(1)}(x)$ we explore Eq.~(\ref{Eq:WW-type-Cahn}) as
+For $f^{\perp(1)}(x)$ we explore (\ref{Eq:WW-type-Cahn}) as
 $xf^{\perp(1)q}(x) = \frac{\la\kperp^2\ra_{f_1}}{2M_N^2}\,f_{1}^q(x)$ and
@@
 of the asymmetry for negative pions or hadrons. More experimental and
-theoretical work is need to clarify whether this could be due to
+theoretical work is needed to clarify whether this could be due to
 power corrections.
@@
 proven, and each structure functions is unambiguously expressed in
-terms of one of 8 twist-2 TMDs convoluted with one of 2 twist-2 FFs.
+terms of one of eight twist-2 TMDs convoluted with one of two twist-2 FFs.
 For subleading-twist SIDIS structure functions the situation
@@
 Second, each of the subleading-twist structure functions
-receives 4 or 6 contributions from various TMDs and FFs one of
+receives four or six contributions from various TMDs and FFs one of
 which is twist-2 and the other twist-3. Clearly, to make
@@
 an approach all twist-2 and twist-3 structure functions can be
-described in terms of 8 basis functions: 6 TMDs and 2 FFs,
+described in terms of eight basis functions: six TMDs and two FFs,
 which are each twist-2. All other TMDs and FFs, assuming this
@@
 
-To make this work self-contained we included a review of the
-available phenomenological information on the basis functions
-which is given in terms of 6 SIDIS structure functions.
-(Of course, one cannot extract 8 basis
-functions from 6 observables: the extraction of 2 basis functions,
+To make this work self-contained, we included a review of the
+available phenomenological information on the basis functions,
+which is given in terms of six SIDIS structure functions.
+(Of course, one cannot extract eight basis
+functions from six observables: the extraction of two basis functions,
 the unpolarized TMD and FF $f_1^q(x,\kperp)$ and $D_1^q(x,\pperp)$,
@@
 useful for experiments prepared in the near term (JLab 12) or proposed
-in the long term (Electron Ion Collider), and provide helpful input for
+in the long term (Electron-Ion Collider), and provide helpful input for
 Monte Carlo event generators \cite{Avakian:2015vha}.
@@
 
-%\bibliography{\BibPath/biblio_ww}
+\bibliography{\BibPath/biblio_ww}
+
+\end{document}
 

### 2019-01-14 arxiv1/test-WW-type.tex
implemented remaining comments and updated bibliography

@@
 
+\newcommand{\Gaussian}{\ensuremath{\stackrel{\text{\scriptsize Gauss}}{=}}}
+
  % PETER'S DEFINITIONS
@@
 	employed in the HERMES, COMPASS and Jefferson Lab (JLab) experiments
-	\cite{Stock:1994vv,Crabb:1997cy,Goertz:2002vv}.
+	\cite{Stock:1994vv,Airapetian:2004yf,Crabb:1997cy,Goertz:2002vv}.
 Complementary information can be obtained
@@
 terms. We denote $\bar{q}gq$--terms and mass terms collectively
-and symbolically by functions with a tilde.
+and symbolically by functions with a tilde.\footnote{In the literature it is 
+customary to reserve the term "tilde terms"
+for matrix elements of $\bar{q}gq$ operators as done, e.g., in
+Ref~\cite{Bacchetta:2006tn}. For convenience in this work "tilde terms"
+refers to both $\bar{q}gq$ terms and current-quark mass terms as
+done, e.g., in \cite{Metz:2008ib}.}  
 Such decompositions are possible because $g_T^a(x)$ and $h_L^a(x)$ are
@@
 Casting this line of thought into mathematics, we get
-\ba
-    	\int_{-1}^1 d x\; g_{1T}^{\perp(1)q}(x)
-	= & \int_{-1}^1 d x\; \int  d^2 \bfkperp
+\begin{align}
+    	\int_{-1}^1 \! d x\; g_{1T}^{\perp(1)q}(x)
+	&=  \int_{-1}^1 \! d x \! \int \! d^2 \bfkperp
 	\frac{\kperp^2}{2M^2} g_{1T}^{\perp q}(x,\kperp)
 	= -2 \tilde{A}_{7,q}( \ell = 0 )
-	\stackrel{\text{\scriptsize Gaussian}}{=} -c_{7,q} \quad \quad \\
-    	\int_{-1}^1 d x\; h_{1L}^{\perp(1)q}(x)
-	= & \int_{-1}^1 d x\; \int  d^2 \bfkperp
+	\Gaussian
+	 -c_{7,q}  \\
+    	\int_{-1}^1 \! d x\; h_{1L}^{\perp(1)q}(x)
+	&=  \int_{-1}^1 \! d x \! \int \!  d^2 \bfkperp
 	\frac{\kperp^2}{2M^2} h_{1T}^{\perp q}(x,\kperp)
 	= -2 \tilde{A}_{10,q}( \ell = 0 )
-	\stackrel{\text{\scriptsize Gaussian}}{=} -c_{10,q} \quad \quad
-\ea
+	\Gaussian
+	-c_{10,q} 
+\end{align}
 where the amplitudes $\tilde{A}$ and constants $c$ are those of Ref.~\cite{Musch:2010ka}.
@@
 For the test of (\ref{Eq:WW-approx-g1T-d}), we use the numbers
-$\int d x\;g_{1T}^{\perp(1)u}(x)\stackrel{\text{\scriptsize Gaussian}}{=}
+$\int d x\;g_{1T}^{\perp(1)u}(x)\Gaussian
 -c_{7,u}= 0.1041(85)$ and
-$\int d x\;g_{1T}^{\perp(1)d}(x)\stackrel{\text{\scriptsize Gaussian}}{=}
+$\int d x\;g_{1T}^{\perp(1)d}(x)\Gaussian
 -c_{7,d}=-0.0232(42)$
@@
 % $\int d x\;h_{1L}^{\perp(1)d}(x) = 0.0130(40)$ from \cite{Hagler:2009mb}
-$\int dx\;h_{1L}^{\perp(1)u}(x)\stackrel{\text{\scriptsize Gaussian}}{=}
--c_{10,u}=-0.0881(72)$
+$\int dx\;h_{1L}^{\perp(1)u}(x)\Gaussian -c_{10,u}=-0.0881(72)$
 and
-$\int dx\;h_{1L}^{\perp(1)d}(x)\stackrel{\text{\scriptsize Gaussian}}{=}
--c_{10,d}=0.0137(34)$
+$\int dx\;h_{1L}^{\perp(1)d}(x)\Gaussian -c_{10,d}=0.0137(34)$
 from \cite{Musch:2010ka} and the lattice data
@@
 The phenomenological success of this approach \cite{Zavada:1996kp} may
-hint at a general smallness of $\bar{q}gq$ terms, although many of the
+hint at a general smallness of $\bar{q}gq$ terms, although some of the
 predictions from this model have yet to be tested \cite{Efremov:2010mt}.
@@
 \begin{subequations}\ba
-F_{UU}^{\cos\phi_h} &\stackrel{\rm WW}{=}&\frac{2M_N}{Q}\,{\cal C}\biggl[\phantom{-}
+F_{UU}^{\cos\phi_h} &\stackrel{\rm WW}{=}&\frac{2M_N}{Q}\,{\cal C}\biggl[
 	 \omega^{\{1\}}_{\rm A}\,x\,h\,H_{1}^{\perp }
@@
 F_{UL}^{\sin\phi_h} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
-   	\phantom{-}\omega^{\{1\}}_{\rm A}\,
+   	\omega^{\{1\}}_{\rm A}\,
     	x\,h_L  H_1^{\perp } \biggr]
@@
 F_{UT}^{\sin \phi_S } &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,
-	{\cal C}\biggl[ \phantom{-}\omega^{\{0\}} \, x\,f_TD_1
+	{\cal C}\biggl[ \omega^{\{0\}} \, x\,f_TD_1
 	-\frac{\omega^{\{2\}}_{\rm B}}{2}\,(xh_T-xh_T^\perp)\,H_{1}^{\perp } \biggr]
@@
 F_{UT}^{\sin(2\phi_h -\phi_S)} &\stackrel{\rm WW}{=}& \frac{2M_N}{Q}\,{\cal C}\biggl[
-   	\;\omega^{\{2\}}_{\rm C}\,
+   	\omega^{\{2\}}_{\rm C}\,
    	{  x\,f_T^\perp}D_1
@@
 	{(h_T^a+h_T^{\perp a})\to h_{1T}^{\perp a}}{
-	(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8})} \!
-	\;\;\;\;\\
-F_{LU}^{\sin\phi_h} &\stackrel{\rm WW}{=}& 0\,, \phantom{\frac11}
+	(\ref{Eq:WW-type-fTperp},~\ref{Eq:WW-type-7},~\ref{Eq:WW-type-8})} 
+	\\
+F_{LU}^{\sin\phi_h} &\stackrel{\rm WW}{=}& 0 \phantom{\frac11}
 	\label{Eq:WW-type-FLUsinphi}\\
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b]
-\centering
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip} {\tiny (a)}
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim} {\tiny (b)}
-\includegraphics[width=0.37\textwidth]{\FigPath/ALT_COMPASS_x.pdf} {\tiny (c)}
-	\caption{\label{cosphihphis}
-	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$:
-	 preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b); and our calculation for COMPASS kinematics (c).
-	}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 In the Gaussian Ansatz the structure function $F_{LT}^{\cos(\phi_h -\phi_S)}$
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip} {\tiny (a)}
+\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim} {\tiny (b)}
+\includegraphics[width=0.37\textwidth]{\FigPath/ALT_COMPASS_x.pdf} {\tiny (c)}
+	\caption{\label{cosphihphis}
+	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$:
+	 preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b); and our calculation for COMPASS kinematics (c).
+	}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 This asymmetry was measured at JLab~\cite{Huang:2011bc}, COMPASS~\cite{
 Parsamyan:2007ju,Parsamyan:2015dfa,Parsamyan:2018evv} and HERMES~\cite{Pappalardo:2011cu,Pappalardo:2012zz} (for the latter two experiments only preliminary results are available so far).
-Figure~\ref{cosphihphis} shows the preliminary results from the 2010 COMPASS data \cite{Parsamyan:2013fia}.
-We approximate the charged hadrons ($70-80\,\%$ of which are $\pi^\pm$ at COMPASS) by
+Figure~\ref{cosphihphis} shows the preliminary results from the 2010 COMPASS data \cite{Parsamyan:2013fia},
+in addition to our calculation, where 
+we approximate the charged hadrons (70--80~\% of which are $\pi^\pm$ at COMPASS) by
 charged pions, see App.~\ref{App:basis-f1-D1}.
-Our results are shown as a shaded area, which indicates a rough estimate
-of the uncertainty of the WW-type approximation.
+%Our results are shown as a shaded area, which indicates a rough estimate
+% of the uncertainty of the WW-type approximation.
 We observe that the WW-type approximation describes the data within
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
+\begin{figure}
 \centering
-\includegraphics[height=3.45cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} {\tiny (a)}
-\hskip -0.2cm\includegraphics[height=3.45cm]{\FigPath/AULsin2phi_COMPASS_x} {\tiny (b)}
-
-\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_JLAB_x.pdf} {\tiny (c)}
+\includegraphics[height=4cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} {\tiny (a)}\\
+\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_JLAB_x.pdf} {\tiny (b)}
+\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_COMPASS_x} {\tiny (c)}
 	\caption{\label{aul_jlab}
@@
 function satisfy even the necessary condition. In this situation we
-do not expect the WW-type approximation to be applicable.
+do not expect the WW-type approximation to work.
 
@@
 \label{Sec-7.6:FUTsinphiS}
-
-\begin{figure}[htb]
-\centering
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pip.pdf}  {\tiny (a)}
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pim.pdf}  {\tiny (b)}
-\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_COMPASS_x}  {\tiny (c)}
-\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_HERMES_x.pdf}  {\tiny (d)}
-\caption{\label{autsinphis}
- 	Subleading-twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which
-	is predicted to vanish in the WW-type approximation: 
-	preliminary COMPASS~\cite{Parsamyan:2013fia} (a,b), 
-	our calculation for COMPASS kinematics (c), and HERMES data \cite{Schnell:2010zza} (d).}
-\end{figure}
 
@@
 $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_1^{ }}$.
+
+\begin{figure}
+\centering
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pip.pdf}  {\tiny (a)}
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pim.pdf}  {\tiny (b)}
+\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_COMPASS_x}  {\tiny (c)}
+\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_HERMES_x.pdf}  {\tiny (d)}
+\caption{\label{autsinphis}
+ 	Subleading-twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which
+	is predicted to vanish in the WW-type approximation: 
+	preliminary COMPASS~\cite{Parsamyan:2013fia} (a,b), 
+	our calculation for COMPASS kinematics (c), and HERMES data \cite{Schnell:2010zza} (d).}
+\end{figure}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_HERMES_x.pdf}
+\caption{\label{auucosphi_jlab}
+	Left panel: asymmetry $A_{UU}^{\cos\phi_h}$ for positive and negative
+	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}. Right
+	panel: the corresponding $A_{UU, \langle y \rangle}^{\cos\phi_h}$ for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The asymmetries $A_{UU}^{\cos\phi_h}$ were measured by
@@
 power corrections.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf}
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_HERMES_x.pdf}
-\caption{\label{auucosphi_jlab}
-	Left panel: asymmetry $A_{UU}^{\cos\phi_h}$ for positive and negative
-	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}. Right
-	panel: the corresponding $A_{UU, \langle y \rangle}^{\cos\phi_h}$ for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 observation that the classical WW-approximation for the twist-3
-SIDIS structure function $g_2(x)$ (or PDF $g_T^q(x)$) works well.
+DIS structure function $g_2(x)$ (or PDF $g_T^q(x)$) works well.
 This was predicted in theoretical studies in the instanton model
@@
 
-\providecommand{\href}[2]{#2}\begingroup\raggedright\begin{thebibliography}{100}
-
-\bibitem{Kotzinian:1994dv}
-A.~Kotzinian, \emph{New quark distributions and semiinclusive electroproduction
-  on the polarized nucleons}, {\emph{Nucl. Phys.} {\bf B441} (1995) 234--248},
-  [\href{https://arxiv.org/abs/hep-ph/9412283}{{\tt hep-ph/9412283}}].
-
-\bibitem{Mulders:1995dh}
-P.~J. Mulders and R.~D. Tangerman, \emph{{The complete tree-level result up to
-  order 1/Q for polarized deep-inelastic leptoproduction}},
-  \href{http://dx.doi.org/10.1016/0550-3213(95)00632-X}{\emph{Nucl. Phys.} {\bf
-  B461} (1996) 197--237}, [\href{https://arxiv.org/abs/hep-ph/9510301}{{\tt
-  hep-ph/9510301}}].
-
-\bibitem{Boer:1997nt}
-D.~Boer and P.~J. Mulders, \emph{{Time-reversal odd distribution functions in
-  leptoproduction}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.57.5780}{\emph{Phys. Rev.} {\bf D57}
-  (1998) 5780--5786}, [\href{https://arxiv.org/abs/hep-ph/9711485}{{\tt
-  hep-ph/9711485}}].
-
-\bibitem{Goeke:2005hb}
-K.~Goeke, A.~Metz and M.~Schlegel, \emph{{Parameterization of the quark-quark
-  correlator of a spin-1/2 hadron}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2005.05.037}{\emph{Phys. Lett.}
-  {\bf B618} (2005) 90--96}, [\href{https://arxiv.org/abs/hep-ph/0504130}{{\tt
-  hep-ph/0504130}}].
-
-\bibitem{Bacchetta:2006tn}
-A.~Bacchetta et~al., \emph{{Semi-inclusive deep inelastic scattering at small
-  transverse momentum}}, {\emph{JHEP} {\bf 02} (2007) 093},
-  [\href{https://arxiv.org/abs/hep-ph/0611265}{{\tt hep-ph/0611265}}].
-
-\bibitem{Stock:1994vv}
-F.~Stock et~al., \emph{{The FILTEX / HERMES polarized hydrogen atomic beam
-  source}}, \href{http://dx.doi.org/10.1016/0168-9002(94)90210-0}{\emph{Nucl.
-  Instrum. Meth.} {\bf A343} (1994) 334--342}.
-
-\bibitem{Crabb:1997cy}
-D.~G. Crabb and W.~Meyer, \emph{{Solid polarized targets for nuclear and
-  particle physics experiments}},
-  \href{http://dx.doi.org/10.1146/annurev.nucl.47.1.67}{\emph{Ann. Rev. Nucl.
-  Part. Sci.} {\bf 47} (1997) 67--109}.
-
-\bibitem{Goertz:2002vv}
-S.~Goertz, W.~Meyer and G.~Reicherz, \emph{{Polarized H, D and He-3 targets for
-  particle physics experiments}},
-  \href{http://dx.doi.org/10.1016/S0146-6410(02)00159-X}{\emph{Prog. Part.
-  Nucl. Phys.} {\bf 49} (2002) 403--489}.
-
-\bibitem{Arnold:2008kf}
-S.~Arnold, A.~Metz and M.~Schlegel, \emph{{Dilepton production from polarized
-  hadron hadron collisions}},  \href{https://arxiv.org/abs/0809.2262}{{\tt
-  0809.2262}}.
-
-\bibitem{Metz:2016swz}
-A.~Metz and A.~Vossen, \emph{{Parton Fragmentation Functions}},
-  \href{http://dx.doi.org/10.1016/j.ppnp.2016.08.003}{\emph{Prog. Part. Nucl.
-  Phys.} {\bf 91} (2016) 136--202},
-  [\href{https://arxiv.org/abs/1607.02521}{{\tt 1607.02521}}].
-
-\bibitem{Miller:2007ae}
-G.~A. Miller, \emph{{Densities, Parton Distributions, and Measuring the
-  Non-Spherical Shape of the Nucleon}},
-  \href{http://dx.doi.org/10.1103/PhysRevC.76.065209}{\emph{Phys. Rev.} {\bf
-  C76} (2007) 065209}, [\href{https://arxiv.org/abs/0708.2297}{{\tt
-  0708.2297}}].
-
-\bibitem{Burkardt:2007rv}
-M.~Burkardt, \emph{{Spin-orbit correlations and single-spin asymmetries}},
-  \href{https://arxiv.org/abs/0709.2966}{{\tt 0709.2966}}.
-
-\bibitem{Burkardt:2009rf}
-M.~Burkardt, \emph{{The g(2) Structure Function}},
-  \href{http://dx.doi.org/10.1063/1.3203298}{\emph{AIP Conf.Proc.} {\bf 1155}
-  (2009) 26--34}, [\href{https://arxiv.org/abs/0905.4079}{{\tt 0905.4079}}].
-
-\bibitem{Bacchetta:1999kz}
-A.~Bacchetta, M.~Boglione, A.~Henneman and P.~J. Mulders, \emph{{Bounds on
-  transverse momentum dependent distribution and fragmentation functions}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.85.712}{\emph{Phys. Rev. Lett.}
-  {\bf 85} (2000) 712--715}, [\href{https://arxiv.org/abs/hep-ph/9912490}{{\tt
-  hep-ph/9912490}}].
-
-\bibitem{Wandzura:1977qf}
-S.~Wandzura and F.~Wilczek, \emph{{Sum Rules for Spin Dependent
-  Electroproduction: Test of Relativistic Constituent Quarks}},
-  \href{http://dx.doi.org/10.1016/0370-2693(77)90700-6}{\emph{Phys. Lett.} {\bf
-  B72} (1977) 195}.
-
-\bibitem{Jaffe:1991ra}
-R.~Jaffe and X.~Ji, \emph{{Chiral odd parton distributions and Drell--Yan
-  processes}},
-  \href{http://dx.doi.org/10.1016/0550-3213(92)90110-W}{\emph{Nucl. Phys.} {\bf
-  B375} (1992) 527--560}.
-
-\bibitem{Jaffe:1989xx}
-R.~Jaffe, \emph{{G(2): The Nucleon's Other Spin Dependent Structure Function}},
-  {\emph{Comments Nucl. Part. Phys.} {\bf 19} (1990) 239}.
-
-\bibitem{Balla:1997hf}
-J.~Balla, M.~V. Polyakov and C.~Weiss, \emph{{Nucleon matrix elements of higher
-  twist operators from the instanton vacuum}},
-  \href{http://dx.doi.org/10.1016/S0550-3213(98)00638-5}{\emph{Nucl. Phys.}
-  {\bf B510} (1998) 327--364},
-  [\href{https://arxiv.org/abs/hep-ph/9707515}{{\tt hep-ph/9707515}}].
-
-\bibitem{Dressler:1999hc}
-B.~Dressler and M.~V. Polyakov, \emph{{On the twist-three contribution to h(L)
-  in the instanton vacuum}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.61.097501}{\emph{Phys. Rev.} {\bf
-  D61} (2000) 097501}, [\href{https://arxiv.org/abs/hep-ph/9912376}{{\tt
-  hep-ph/9912376}}].
-
-\bibitem{Gockeler:2000ja}
-M.~Gockeler, R.~Horsley, W.~Kurzinger, H.~Oelrich, D.~Pleiter et~al., \emph{{A
-  Lattice calculation of the nucleon's spin dependent structure function g(2)
-  revisited}}, \href{http://dx.doi.org/10.1103/PhysRevD.63.074506}{\emph{Phys.
-  Rev.} {\bf D63} (2001) 074506},
-  [\href{https://arxiv.org/abs/hep-lat/0011091}{{\tt hep-lat/0011091}}].
-
-\bibitem{Gockeler:2005vw}
-{Gockeler, M. and Horsley, R. and Pleiter, D. and Rakow, Paul E.L. and
-  Sch\"afer, A. and others}, \emph{{Investigation of the second moment of the
-  nucleon's g(1) and g(2) structure functions in two-flavor lattice QCD}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.72.054507}{\emph{Phys. Rev.} {\bf
-  D72} (2005) 054507}, [\href{https://arxiv.org/abs/hep-lat/0506017}{{\tt
-  hep-lat/0506017}}].
-
-\bibitem{Abe:1998wq}
-{\scshape E143} collaboration, K.~Abe et~al., \emph{{Measurements of the proton
-  and deuteron spin structure functions $g_{1}$ and $g_{2}$}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.58.112003}{\emph{Phys. Rev.} {\bf
-  D58} (1998) 112003}, [\href{https://arxiv.org/abs/hep-ph/9802357}{{\tt
-  hep-ph/9802357}}].
-
-\bibitem{Anthony:2002hy}
-{\scshape E155} collaboration, P.~L. Anthony et~al., \emph{{Precision
-  measurement of the proton and deuteron spin structure functions g2 and
-  asymmetries A(2)}},
-  \href{http://dx.doi.org/10.1016/S0370-2693(02)03015-0}{\emph{Phys. Lett.}
-  {\bf B553} (2003) 18--24}, [\href{https://arxiv.org/abs/hep-ex/0204028}{{\tt
-  hep-ex/0204028}}].
-
-\bibitem{Airapetian:2011wu}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Measurement of
-  the virtual-photon asymmetry $A_2$ and the spin-structure function $g_2$ of
-  the proton}},
-  \href{http://dx.doi.org/10.1140/epjc/s10052-012-1921-5}{\emph{Eur. Phys. J.}
-  {\bf C72} (2012) 1921}, [\href{https://arxiv.org/abs/1112.5584}{{\tt
-  1112.5584}}].
-
-\bibitem{Kotzinian:1995cz}
-A.~M. Kotzinian and P.~J. Mulders, \emph{{Longitudinal quark polarization in
-  transversely polarized nucleons}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.54.1229}{\emph{Phys. Rev.} {\bf D54}
-  (1996) 1229--1232}, [\href{https://arxiv.org/abs/hep-ph/9511420}{{\tt
-  hep-ph/9511420}}].
-
-\bibitem{Kotzinian:1997wt}
-A.~M. Kotzinian and P.~J. Mulders, \emph{{Probing transverse quark polarization
-  via azimuthal asymmetries in leptoproduction}},
-  \href{http://dx.doi.org/10.1016/S0370-2693(97)00708-9}{\emph{Phys. Lett.}
-  {\bf B406} (1997) 373--380},
-  [\href{https://arxiv.org/abs/hep-ph/9701330}{{\tt hep-ph/9701330}}].
-
-\bibitem{Kotzinian:2006dw}
-A.~Kotzinian, B.~Parsamyan and A.~Prokudin, \emph{{Predictions for double spin
-  asymmetry A(LT) in semi inclusive DIS}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.73.114017}{\emph{Phys. Rev.} {\bf
-  D73} (2006) 114017}, [\href{https://arxiv.org/abs/hep-ph/0603194}{{\tt
-  hep-ph/0603194}}].
-
-\bibitem{Avakian:2007mv}
-H.~Avakian et~al., \emph{{Are there approximate relations among transverse
-  momentum dependent distribution functions?}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.77.014023}{\emph{Phys. Rev.} {\bf
-  D77} (2008) 014023}, [\href{https://arxiv.org/abs/0709.3253}{{\tt
-  0709.3253}}].
-
-\bibitem{Metz:2008ib}
-A.~Metz, P.~Schweitzer and T.~Teckentrup, \emph{{Lorentz invariance relations
-  between parton distributions and the Wandzura-Wilczek approximation}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2009.08.052}{\emph{Phys. Lett.}
-  {\bf B680} (2009) 141--147}, [\href{https://arxiv.org/abs/0810.5212}{{\tt
-  0810.5212}}].
-
-\bibitem{Teckentrup:2009tk}
-T.~Teckentrup, A.~Metz and P.~Schweitzer, \emph{{Lorentz invariance relations
-  and Wandzura-Wilczek approximation}},
-  \href{http://dx.doi.org/10.1142/S0217732309001169}{\emph{Mod. Phys. Lett.}
-  {\bf A24} (2009) 2950--2959}, [\href{https://arxiv.org/abs/0910.2567}{{\tt
-  0910.2567}}].
-
-\bibitem{Tangerman:1994bb}
-R.~Tangerman and P.~Mulders, \emph{{Polarized twist-three distributions g(T)
-  and h(L) and the role of intrinsic transverse momentum}},
-  \href{https://arxiv.org/abs/hep-ph/9408305}{{\tt hep-ph/9408305}}.
-
-\bibitem{Avakian:2015vha}
-H.~Avakian, H.~Matevosyan, B.~Pasquini and P.~Schweitzer, \emph{{Studying the
-  information content of TMDs using Monte Carlo generators}},
-  \href{http://dx.doi.org/10.1088/0954-3899/42/3/034015}{\emph{J. Phys.} {\bf
-  G42} (2015) 034015}.
-
-\bibitem{Metz:2004je}
-A.~Metz and M.~Schlegel, \emph{{Twist three single spin asymmetries in
-  semiinclusive deep inelastic scattering}},
-  \href{http://dx.doi.org/10.1140/epja/i2004-10050-8}{\emph{Eur. Phys. J.} {\bf
-  A22} (2004) 489--494}, [\href{https://arxiv.org/abs/hep-ph/0403182}{{\tt
-  hep-ph/0403182}}].
-
-\bibitem{Gamberg:2006ru}
-L.~P. Gamberg, D.~S. Hwang, A.~Metz and M.~Schlegel, \emph{{Light-cone
-  divergence in twist-3 correlation functions}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2006.07.005}{\emph{Phys. Lett.}
-  {\bf B639} (2006) 508--512},
-  [\href{https://arxiv.org/abs/hep-ph/0604022}{{\tt hep-ph/0604022}}].
-
-\bibitem{Mathematica}
-W.~R. Inc., ``Mathematica, {V}ersion 11.3.''
-
-\bibitem{Collins:2002kn}
-J.~C. Collins, \emph{{Leading-twist single-transverse-spin asymmetries:
-  Drell--Yan and deep-inelastic scattering}}, {\emph{Phys. Lett.} {\bf B536}
-  (2002) 43--48}, [\href{https://arxiv.org/abs/hep-ph/0204004}{{\tt
-  hep-ph/0204004}}].
-
-\bibitem{Ralston:1979ys}
-J.~P. Ralston and D.~E. Soper, \emph{{Production of Dimuons from High-Energy
-  Polarized Proton Proton Collisions}},
-  \href{http://dx.doi.org/10.1016/0550-3213(79)90082-8}{\emph{Nucl. Phys.} {\bf
-  B152} (1979) 109}.
-
-\bibitem{Collins:1981uk}
-J.~C. Collins and D.~E. Soper, \emph{{Back-To-Back Jets in QCD}},
-  \href{http://dx.doi.org/10.1016/0550-3213(81)90339-4}{\emph{Nucl. Phys.} {\bf
-  B193} (1981) 381}.
-
-\bibitem{Ji:2004wu}
-X.~Ji, J.-p. Ma and F.~Yuan, \emph{{QCD factorization for semi-inclusive
-  deep-inelastic scattering at low transverse momentum}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.71.034005}{\emph{Phys. Rev.} {\bf
-  D71} (2005) 034005}, [\href{https://arxiv.org/abs/hep-ph/0404183}{{\tt
-  hep-ph/0404183}}].
-
-\bibitem{Ji:2004xq}
-X.~Ji, J.-P. Ma and F.~Yuan, \emph{{QCD factorization for spin-dependent cross
-  sections in DIS and Drell-Yan processes at low transverse momentum}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2004.07.026}{\emph{Phys. Lett.}
-  {\bf B597} (2004) 299--308},
-  [\href{https://arxiv.org/abs/hep-ph/0405085}{{\tt hep-ph/0405085}}].
-
-\bibitem{Collins:2011zzd}
-J.~Collins, \emph{{Foundations of perturbative QCD}}, {\emph{Camb. Monogr.
-  Part. Phys. Nucl. Phys. Cosmol.} {\bf 32} (2011) 1--624}.
-
-\bibitem{Echevarria:2012js}
-M.~G. Echevarr\'ia, A.~Idilbi and I.~Scimemi, \emph{{Soft and Collinear
-  Factorization and Transverse Momentum Dependent Parton Distribution
-  Functions}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2013.09.003}{\emph{Phys. Lett.}
-  {\bf B726} (2013) 795--801}, [\href{https://arxiv.org/abs/1211.1947}{{\tt
-  1211.1947}}].
-
-\bibitem{Aybat:2011zv}
-S.~M. Aybat and T.~C. Rogers, \emph{{TMD Parton Distribution and Fragmentation
-  Functions with QCD Evolution}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.83.114042}{\emph{Phys. Rev.} {\bf
-  D83} (2011) 114042}, [\href{https://arxiv.org/abs/1101.5057}{{\tt
-  1101.5057}}].
-
-\bibitem{Aybat:2011ge}
-S.~M. Aybat, J.~C. Collins, J.-W. Qiu and T.~C. Rogers, \emph{{The QCD
-  Evolution of the Sivers Function}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.85.034043}{\emph{Phys. Rev.} {\bf
-  D85} (2012) 034043}, [\href{https://arxiv.org/abs/1110.6428}{{\tt
-  1110.6428}}].
-
-\bibitem{Echevarria:2014xaa}
-M.~G. Echevarria, A.~Idilbi, Z.-B. Kang and I.~Vitev, \emph{{QCD Evolution of
-  the Sivers Asymmetry}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.89.074013}{\emph{Phys. Rev.} {\bf
-  D89} (2014) 074013}, [\href{https://arxiv.org/abs/1401.5078}{{\tt
-  1401.5078}}].
-
-\bibitem{Collins:2014jpa}
-J.~Collins and T.~Rogers, \emph{{Understanding the large-distance behavior of
-  transverse-momentum-dependent parton densities and the Collins-Soper
-  evolution kernel}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.91.074020}{\emph{Phys. Rev.} {\bf
-  D91} (2015) 074020}, [\href{https://arxiv.org/abs/1412.3820}{{\tt
-  1412.3820}}].
-
-\bibitem{Ma:2013aca}
-J.~P. Ma and G.~P. Zhang, \emph{{QCD Corrections of All Structure Functions in
-  Transverse Momentum Dependent Factorization for Drell-Yan Processes}},
-  \href{http://dx.doi.org/10.1007/JHEP02(2014)100}{\emph{JHEP} {\bf 02} (2014)
-  100}, [\href{https://arxiv.org/abs/1308.2044}{{\tt 1308.2044}}].
-
-\bibitem{Aybat:2011ta}
-S.~M. Aybat, A.~Prokudin and T.~C. Rogers, \emph{{Calculation of TMD Evolution
-  for Transverse Single Spin Asymmetry Measurements}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.108.242003}{\emph{Phys. Rev.
-  Lett.} {\bf 108} (2012) 242003}, [\href{https://arxiv.org/abs/1112.4423}{{\tt
-  1112.4423}}].
-
-\bibitem{Kang:2015msa}
-Z.-B. Kang, A.~Prokudin, P.~Sun and F.~Yuan, \emph{{Extraction of Quark
-  Transversity Distribution and Collins Fragmentation Functions with QCD
-  Evolution}}, \href{http://dx.doi.org/10.1103/PhysRevD.93.014009}{\emph{Phys.
-  Rev.} {\bf D93} (2016) 014009}, [\href{https://arxiv.org/abs/1505.05589}{{\tt
-  1505.05589}}].
-
-\bibitem{Gutierrez-Reyes:2017glx}
-D.~Gutiérrez-Reyes, I.~Scimemi and A.~A. Vladimirov, \emph{{Twist-2 matching of
-  transverse momentum dependent distributions}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2017.03.031}{\emph{Phys. Lett.}
-  {\bf B769} (2017) 84--89}, [\href{https://arxiv.org/abs/1702.06558}{{\tt
-  1702.06558}}].
-
-\bibitem{Gutierrez-Reyes:2018qez}
-D.~Gutierrez-Reyes, I.~Scimemi, W.~J. Waalewijn and L.~Zoppi, \emph{{Transverse
-  momentum dependent distributions with jets}},
-  \href{https://arxiv.org/abs/1807.07573}{{\tt 1807.07573}}.
-
-\bibitem{Scimemi:2018mmi}
-I.~Scimemi and A.~Vladimirov, \emph{{Matching of transverse momentum dependent
-  distributions at twist-3}},  \href{https://arxiv.org/abs/1804.08148}{{\tt
-  1804.08148}}.
-
-\bibitem{Chen:2016hgw}
-A.~P. Chen and J.~P. Ma, \emph{{Light-Cone Singularities and
-  Transverse-Momentum-Dependent Factorization at Twist-3}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2017.03.015}{\emph{Phys. Lett.}
-  {\bf B768} (2017) 380--386}, [\href{https://arxiv.org/abs/1610.08634}{{\tt
-  1610.08634}}].
-
-\bibitem{Efremov:2002qh}
-A.~Efremov and P.~Schweitzer, \emph{{The Chirally odd twist 3 distribution
-  e(a)(x)}}, {\emph{JHEP} {\bf 0308} (2003) 006},
-  [\href{https://arxiv.org/abs/hep-ph/0212044}{{\tt hep-ph/0212044}}].
-
-\bibitem{Jaffe:1996zw}
-R.~L. Jaffe, \emph{{Spin, twist and hadron structure in deep inelastic
-  processes}},  \href{https://arxiv.org/abs/hep-ph/9602236}{{\tt
-  hep-ph/9602236}}.
-
-\bibitem{Kanazawa:2015ajw}
-K.~Kanazawa, Y.~Koike, A.~Metz, D.~Pitonyak and M.~Schlegel, \emph{{Operator
-  Constraints for Twist-3 Functions and Lorentz Invariance Properties of
-  Twist-3 Observables}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.93.054024}{\emph{Phys. Rev.} {\bf
-  D93} (2016) 054024}, [\href{https://arxiv.org/abs/1512.07233}{{\tt
-  1512.07233}}].
-
-\bibitem{Shuryak:1981ff}
-E.~V. Shuryak, \emph{{The Role of Instantons in Quantum Chromodynamics. 1.
-  Physical Vacuum}},
-  \href{http://dx.doi.org/10.1016/0550-3213(82)90478-3}{\emph{Nucl. Phys.} {\bf
-  B203} (1982) 93}.
-
-\bibitem{Diakonov:1983hh}
-D.~Diakonov and V.~Y. Petrov, \emph{{Instanton Based Vacuum from Feynman
-  Variational Principle}},
-  \href{http://dx.doi.org/10.1016/0550-3213(84)90432-2}{\emph{Nucl. Phys.} {\bf
-  B245} (1984) 259}.
-
-\bibitem{Diakonov:1995qy}
-D.~Diakonov, M.~V. Polyakov and C.~Weiss, \emph{{Hadronic matrix elements of
-  gluon operators in the instanton vacuum}},
-  \href{http://dx.doi.org/10.1016/0550-3213(95)00675-3}{\emph{Nucl. Phys.} {\bf
-  B461} (1996) 539--580}, [\href{https://arxiv.org/abs/hep-ph/9510232}{{\tt
-  hep-ph/9510232}}].
-
-\bibitem{Adams:1994id}
-{\scshape Spin Muon (SMC)} collaboration, D.~Adams et~al., \emph{{Spin
-  asymmetry in muon - proton deep inelastic scattering on a transversely
-  polarized target}},
-  \href{http://dx.doi.org/10.1016/0370-2693(94)00968-6}{\emph{Phys. Lett.} {\bf
-  B336} (1994) 125--130}, [\href{https://arxiv.org/abs/hep-ex/9408001}{{\tt
-  hep-ex/9408001}}].
-
-\bibitem{Accardi:2009au}
-A.~Accardi, A.~Bacchetta, W.~Melnitchouk and M.~Schlegel, \emph{{What can break
-  the Wandzura--Wilczek relation?}},
-  \href{http://dx.doi.org/10.1088/1126-6708/2009/11/093}{\emph{JHEP} {\bf 11}
-  (2009) 093}, [\href{https://arxiv.org/abs/0907.2942}{{\tt 0907.2942}}].
-
-\bibitem{Gluck:1998xa}
-M.~Gluck, E.~Reya and A.~Vogt, \emph{{Dynamical parton distributions
-  revisited}}, \href{http://dx.doi.org/10.1007/s100520050289}{\emph{Eur. Phys.
-  J.} {\bf C5} (1998) 461--470},
-  [\href{https://arxiv.org/abs/hep-ph/9806404}{{\tt hep-ph/9806404}}].
-
-\bibitem{Efremov:2006qm}
-A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{Collins effect in
-  semi-inclusive deeply inelastic scattering and in $e^{+} e^{-}$
-  annihilation}, {\emph{Phys. Rev.} {\bf D73} (2006) 094025}.
-
-\bibitem{Anselmino:2007fs}
-M.~Anselmino et~al., \emph{{Transversity and Collins functions from SIDIS and
-  $e^{+} e^{-}$ data}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.75.054032}{\emph{Phys. Rev.} {\bf
-  D75} (2007) 054032}, [\href{https://arxiv.org/abs/hep-ph/0701006}{{\tt
-  hep-ph/0701006}}].
-
-\bibitem{Anselmino:2008jk}
-M.~Anselmino et~al., \emph{{Update on transversity and Collins functions from
-  SIDIS and $e^{+} e^{-}$ data}},
-  \href{http://dx.doi.org/10.1016/j.nuclphysbps.2009.03.117}{\emph{Nucl. Phys.
-  Proc. Suppl.} {\bf 191} (2009) 98--107},
-  [\href{https://arxiv.org/abs/0812.4366}{{\tt 0812.4366}}].
-
-\bibitem{Koike:2008du}
-Y.~Koike, K.~Tanaka and S.~Yoshida, \emph{{Drell-Yan double-spin asymmetry
-  A(LT) in polarized p anti-p collisions: Wandzura-Wilczek contribution}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2008.08.049}{\emph{Phys. Lett.}
-  {\bf B668} (2008) 286--292}, [\href{https://arxiv.org/abs/0805.2289}{{\tt
-  0805.2289}}].
-
-\bibitem{Hagler:2009mb}
-{H\"agler, Ph. and Musch, B. U. and Negele, J. W. and Sch\"afer, A.},
-  \emph{{Intrinsic quark transverse momentum in the nucleon from lattice QCD}},
-  \href{http://dx.doi.org/10.1209/0295-5075/88/61001}{\emph{Europhys. Lett.}
-  {\bf 88} (2009) 61001}, [\href{https://arxiv.org/abs/0908.1283}{{\tt
-  0908.1283}}].
-
-\bibitem{Musch:2010ka}
-{Musch, Bernhard U. and H\"agler, Philipp and Negele, John W. and Sch\"afer,
-  Andreas}, \emph{{Exploring quark transverse momentum distributions with
-  lattice QCD}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.83.094507}{\emph{Phys. Rev.} {\bf
-  D83} (2011) 094507}, [\href{https://arxiv.org/abs/1011.1213}{{\tt
-  1011.1213}}].
-
-\bibitem{Yoon:2017qzo}
-B.~Yoon, M.~Engelhardt, R.~Gupta, T.~Bhattacharya, J.~R. Green, B.~U. Musch
-  et~al., \emph{{Nucleon Transverse Momentum-dependent Parton Distributions in
-  Lattice QCD: Renormalization Patterns and Discretization Effects}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.96.094508}{\emph{Phys. Rev.} {\bf
-  D96} (2017) 094508}, [\href{https://arxiv.org/abs/1706.03406}{{\tt
-  1706.03406}}].
-
-\bibitem{Engelhardt:2015xja}
-{Engelhardt, M. and H\"agler, P. and Musch, B. and Negele, J. and Sch\"afer,
-  A.}, \emph{{Lattice QCD study of the Boer-Mulders effect in a pion}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.93.054501}{\emph{Phys. Rev.} {\bf
-  D93} (2016) 054501}, [\href{https://arxiv.org/abs/1506.07826}{{\tt
-  1506.07826}}].
-
-\bibitem{Ji:2014hxa}
-X.~Ji, P.~Sun, X.~Xiong and F.~Yuan, \emph{{Soft factor subtraction and
-  transverse momentum dependent parton distributions on the lattice}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.91.074009}{\emph{Phys. Rev.} {\bf
-  D91} (2015) 074009}, [\href{https://arxiv.org/abs/1405.7640}{{\tt
-  1405.7640}}].
-
-\bibitem{Musch:2011er}
-{Musch, B. U. and H\"agler, Ph. and Engelhardt, M. and Negele, J. W. and
-  Sch\"afer, A.}, \emph{{Sivers and Boer-Mulders observables from lattice
-  QCD}}, \href{http://dx.doi.org/10.1103/PhysRevD.85.094510}{\emph{Phys. Rev.}
-  {\bf D85} (2012) 094510}, [\href{https://arxiv.org/abs/1111.4249}{{\tt
-  1111.4249}}].
-
-\bibitem{Alexandrou:2017dzj}
-C.~Alexandrou, S.~Bacchio, K.~Cichy, M.~Constantinou, K.~Hadjiyiannakou,
-  K.~Jansen et~al., \emph{{Computation of parton distributions from the
-  quasi-PDF approach at the physical point}},
-  \href{http://dx.doi.org/10.1051/epjconf/201817514008}{\emph{EPJ Web Conf.}
-  {\bf 175} (2018) 14008}, [\href{https://arxiv.org/abs/1710.06408}{{\tt
-  1710.06408}}].
-
-\bibitem{Ishikawa:2017faj}
-T.~Ishikawa, Y.-Q. Ma, J.-W. Qiu and S.~Yoshida, \emph{{Renormalizability of
-  quasiparton distribution functions}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.96.094019}{\emph{Phys. Rev.} {\bf
-  D96} (2017) 094019}, [\href{https://arxiv.org/abs/1707.03107}{{\tt
-  1707.03107}}].
-
-\bibitem{Ji:2017oey}
-X.~Ji, J.-H. Zhang and Y.~Zhao, \emph{{Renormalization in Large Momentum
-  Effective Theory of Parton Physics}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.120.112001}{\emph{Phys. Rev.
-  Lett.} {\bf 120} (2018) 112001},
-  [\href{https://arxiv.org/abs/1706.08962}{{\tt 1706.08962}}].
-
-\bibitem{Green:2017xeu}
-J.~Green, K.~Jansen and F.~Steffens, \emph{{Nonperturbative renormalization of
-  nonlocal quark bilinears for quasi-PDFs on the lattice using an auxiliary
-  field}}, \href{http://dx.doi.org/10.1103/PhysRevLett.121.022004}{\emph{Phys.
-  Rev. Lett.} {\bf 121} (2018) 022004},
-  [\href{https://arxiv.org/abs/1707.07152}{{\tt 1707.07152}}].
-
-\bibitem{Zhang:2017bzy}
-J.-H. Zhang, J.-W. Chen, X.~Ji, L.~Jin and H.-W. Lin, \emph{{Pion Distribution
-  Amplitude from Lattice QCD}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.95.094514}{\emph{Phys. Rev.} {\bf
-  D95} (2017) 094514}, [\href{https://arxiv.org/abs/1702.00008}{{\tt
-  1702.00008}}].
-
-\bibitem{Hagler:2003is}
-{\scshape LHPC} collaboration, LHPC et~al., \emph{{Transverse structure of
-  nucleon parton distributions from lattice QCD}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.93.112001}{\emph{Phys. Rev.
-  Lett.} {\bf 93} (2004) 112001},
-  [\href{https://arxiv.org/abs/hep-lat/0312014}{{\tt hep-lat/0312014}}].
-
-\bibitem{Hagler:2007xi}
-{\scshape LHPC Collaborations} collaboration, {H\"agler, Ph. and others},
-  \emph{{Nucleon Generalized Parton Distributions from Full Lattice QCD}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.77.094502}{\emph{Phys. Rev.} {\bf
-  D77} (2008) 094502}, [\href{https://arxiv.org/abs/0705.4295}{{\tt
-  0705.4295}}].
-
-\bibitem{Gockeler:2005cj}
-{\scshape QCDSF} collaboration, M.~Gockeler et~al., \emph{{Quark helicity flip
-  generalized parton distributions from two-flavor lattice QCD}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2005.09.002}{\emph{Phys. Lett.}
-  {\bf B627} (2005) 113--123},
-  [\href{https://arxiv.org/abs/hep-lat/0507001}{{\tt hep-lat/0507001}}].
-
-\bibitem{Burkardt:2001iy}
-M.~Burkardt and Y.~Koike, \emph{{Violation of sum rules for twist three parton
-  distributions in QCD}},
-  \href{http://dx.doi.org/10.1016/S0550-3213(02)00263-8}{\emph{Nucl. Phys.}
-  {\bf B632} (2002) 311--329},
-  [\href{https://arxiv.org/abs/hep-ph/0111343}{{\tt hep-ph/0111343}}].
-
-\bibitem{Bass:2003vp}
-S.~D. Bass, \emph{{Fixed poles, polarized glue and nucleon spin structure}},
-  {\emph{Acta Phys. Polon.} {\bf B34} (2003) 5893--5926},
-  [\href{https://arxiv.org/abs/hep-ph/0311174}{{\tt hep-ph/0311174}}].
-
-\bibitem{Stratmann:1993aw}
-M.~Stratmann, \emph{{Bag model predictions for polarized structure functions
-  and their Q**2 evolutions}},
-  \href{http://dx.doi.org/10.1007/BF01558408}{\emph{Z. Phys.} {\bf C60} (1993)
-  763--772}.
-
-\bibitem{Signal:1996ct}
-A.~Signal, \emph{{Calculations of higher twist distribution functions in the
-  MIT bag model}},
-  \href{http://dx.doi.org/10.1016/S0550-3213(97)00231-9}{\emph{Nucl. Phys.}
-  {\bf B497} (1997) 415--434},
-  [\href{https://arxiv.org/abs/hep-ph/9610480}{{\tt hep-ph/9610480}}].
-
-\bibitem{Avakian:2010br}
-H.~Avakian, A.~Efremov, P.~Schweitzer and F.~Yuan, \emph{{The transverse
-  momentum dependent distribution functions in the bag model}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.81.074035}{\emph{Phys. Rev.} {\bf
-  D81} (2010) 074035}, [\href{https://arxiv.org/abs/1001.5467}{{\tt
-  1001.5467}}].
-
-\bibitem{Jakob:1997wg}
-R.~Jakob, P.~Mulders and J.~Rodrigues, \emph{{Modeling quark distribution and
-  fragmentation functions}},
-  \href{http://dx.doi.org/10.1016/S0375-9474(97)00588-5}{\emph{Nucl. Phys.}
-  {\bf A626} (1997) 937--965},
-  [\href{https://arxiv.org/abs/hep-ph/9704335}{{\tt hep-ph/9704335}}].
-
-\bibitem{Wakamatsu:2000ex}
-M.~Wakamatsu, \emph{{Polarized structure functions g(2)(x) in the chiral quark
-  soliton model}},
-  \href{http://dx.doi.org/10.1016/S0370-2693(00)00790-5}{\emph{Phys. Lett.}
-  {\bf B487} (2000) 118--124},
-  [\href{https://arxiv.org/abs/hep-ph/0006212}{{\tt hep-ph/0006212}}].
-
-\bibitem{Pasquini:2008ax}
-B.~Pasquini, S.~Cazzaniga and S.~Boffi, \emph{{Transverse momentum dependent
-  parton distributions in a light-cone quark model}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.78.034025}{\emph{Phys. Rev.} {\bf
-  D78} (2008) 034025}, [\href{https://arxiv.org/abs/0806.2298}{{\tt
-  0806.2298}}].
-
-\bibitem{Lorce:2011dv}
-C.~Lorc\'e, B.~Pasquini and M.~Vanderhaeghen, \emph{{Unified framework for
-  generalized and transverse-momentum dependent parton distributions within a
-  3Q light-cone picture of the nucleon}},
-  \href{http://dx.doi.org/10.1007/JHEP05(2011)041}{\emph{JHEP} {\bf 1105}
-  (2011) 041}, [\href{https://arxiv.org/abs/1102.4704}{{\tt 1102.4704}}].
-
-\bibitem{Kundu:2001pk}
-R.~Kundu and A.~Metz, \emph{{Higher twist and transverse momentum dependent
-  parton distributions: A Light front Hamiltonian approach}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.65.014009}{\emph{Phys. Rev.} {\bf
-  D65} (2002) 014009}, [\href{https://arxiv.org/abs/hep-ph/0107073}{{\tt
-  hep-ph/0107073}}].
-
-\bibitem{Schlegel:2004rg}
-M.~Schlegel and A.~Metz, \emph{{On the validity of Lorentz invariance relations
-  between parton distributions}},
-  \href{https://arxiv.org/abs/hep-ph/0406289}{{\tt hep-ph/0406289}}.
-
-\bibitem{Goeke:2003az}
-K.~Goeke, A.~Metz, P.~Pobylitsa and M.~Polyakov, \emph{{Lorentz invariance
-  relations among parton distributions revisited}},
-  \href{http://dx.doi.org/10.1016/S0370-2693(03)00870-0}{\emph{Phys. Lett.}
-  {\bf B567} (2003) 27--30}, [\href{https://arxiv.org/abs/hep-ph/0302028}{{\tt
-  hep-ph/0302028}}].
-
-\bibitem{Lorce:2014hxa}
-C.~Lorc\'e, B.~Pasquini and P.~Schweitzer, \emph{{Unpolarized transverse
-  momentum dependent parton distribution functions beyond leading twist in
-  quark models}}, \href{http://dx.doi.org/10.1007/JHEP01(2015)103}{\emph{JHEP}
-  {\bf 01} (2015) 103}, [\href{https://arxiv.org/abs/1411.2550}{{\tt
-  1411.2550}}].
-
-\bibitem{Lorce:2016ugb}
-C.~Lorc\'e, B.~Pasquini and P.~Schweitzer, \emph{{Transverse pion structure
-  beyond leading twist in constituent models}},
-  \href{http://dx.doi.org/10.1140/epjc/s10052-016-4257-8}{\emph{Eur. Phys. J.}
-  {\bf C76} (2016) 415}, [\href{https://arxiv.org/abs/1605.00815}{{\tt
-  1605.00815}}].
-
-\bibitem{Zavada:1996kp}
-P.~Zavada, \emph{{The Structure functions and parton momenta distribution in
-  the hadron rest system}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.55.4290}{\emph{Phys. Rev.} {\bf D55}
-  (1997) 4290--4299}, [\href{https://arxiv.org/abs/hep-ph/9609372}{{\tt
-  hep-ph/9609372}}].
-
-\bibitem{Efremov:2010mt}
-A.~V. Efremov, P.~Schweitzer, O.~V. Teryaev and P.~Zavada, \emph{{The relation
-  between TMDs and PDFs in the covariant parton model approach}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.83.054025}{\emph{Phys. Rev.} {\bf
-  D83} (2011) 054025}, [\href{https://arxiv.org/abs/1012.5296}{{\tt
-  1012.5296}}].
-
-\bibitem{Efremov:2009ze}
-A.~V. Efremov, P.~Schweitzer, O.~V. Teryaev and P.~Zavada, \emph{{Transverse
-  momentum dependent distribution functions in a covariant parton model
-  approach with quark orbital motion}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.80.014021}{\emph{Phys. Rev.} {\bf
-  D80} (2009) 014021}, [\href{https://arxiv.org/abs/0903.3490}{{\tt
-  0903.3490}}].
-
-\bibitem{Schweitzer:2003uy}
-P.~Schweitzer, \emph{{The Chirally odd twist three distribution function
-  e**alpha(x) in the chiral quark soliton model}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.67.114010}{\emph{Phys. Rev.} {\bf
-  D67} (2003) 114010}, [\href{https://arxiv.org/abs/hep-ph/0303011}{{\tt
-  hep-ph/0303011}}].
-
-\bibitem{Ohnishi:2003mf}
-Y.~Ohnishi and M.~Wakamatsu, \emph{{pi N sigma term and chiral odd twist three
-  distribution function e(x) of the nucleon in the chiral quark soliton
-  model}}, \href{http://dx.doi.org/10.1103/PhysRevD.69.114002}{\emph{Phys.
-  Rev.} {\bf D69} (2004) 114002},
-  [\href{https://arxiv.org/abs/hep-ph/0312044}{{\tt hep-ph/0312044}}].
-
-\bibitem{Cebulla:2007ej}
-C.~Cebulla, J.~Ossmann, P.~Schweitzer and D.~Urbano, \emph{{The Twist-3 parton
-  distribution function e**a(x) in large-N(c) chiral theory}}, {\emph{Acta
-  Phys. Polon.} {\bf B39} (2008) 609--640},
-  [\href{https://arxiv.org/abs/0710.3103}{{\tt 0710.3103}}].
-
-\bibitem{Meissner:2007rx}
-S.~Meissner, A.~Metz and K.~Goeke, \emph{{Relations between generalized and
-  transverse momentum dependent parton distributions}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.76.034002}{\emph{Phys. Rev.} {\bf
-  D76} (2007) 034002}, [\href{https://arxiv.org/abs/hep-ph/0703176}{{\tt
-  hep-ph/0703176}}].
-
-\bibitem{Mukherjee:2009uy}
-A.~Mukherjee, \emph{{Twist Three Distribution e(x): Sum Rules and Equation of
-  Motion Relations}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2010.03.023}{\emph{Phys. Lett.}
-  {\bf B687} (2010) 180--183}, [\href{https://arxiv.org/abs/0912.1446}{{\tt
-  0912.1446}}].
-
-\bibitem{Harindranath:1997qn}
-A.~Harindranath and W.-M. Zhang, \emph{{Examination of Wandzura-Wilczek
-  relation for g2 (x, q**2) in pQCD}},
-  \href{http://dx.doi.org/10.1016/S0370-2693(97)00771-5}{\emph{Phys. Lett.}
-  {\bf B408} (1997) 347--356},
-  [\href{https://arxiv.org/abs/hep-ph/9706419}{{\tt hep-ph/9706419}}].
-
-\bibitem{Boer:2003cm}
-D.~Boer, P.~J. Mulders and F.~Pijlman, \emph{{Universality of T-odd effects in
-  single spin and azimuthal asymmetries}},
-  \href{http://dx.doi.org/10.1016/S0550-3213(03)00527-3}{\emph{Nucl. Phys.}
-  {\bf B667} (2003) 201--241},
-  [\href{https://arxiv.org/abs/hep-ph/0303034}{{\tt hep-ph/0303034}}].
-
-\bibitem{Ji:2006ub}
-X.~Ji, J.-W. Qiu, W.~Vogelsang and F.~Yuan, \emph{{A unified picture for single
-  transverse-spin asymmetries in hard processes}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.97.082002}{\emph{Phys. Rev.
-  Lett.} {\bf 97} (2006) 082002},
-  [\href{https://arxiv.org/abs/hep-ph/0602239}{{\tt hep-ph/0602239}}].
-
-\bibitem{Anselmino:2005nn}
-M.~Anselmino et~al., \emph{{The role of Cahn and Sivers effects in deep
-  inelastic scattering}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.71.074006}{\emph{Phys. Rev.} {\bf
-  D71} (2005) 074006}, [\href{https://arxiv.org/abs/hep-ph/0501196}{{\tt
-  hep-ph/0501196}}].
-
-\bibitem{Collins:2005ie}
-J.~C. Collins et~al., \emph{Sivers effect in semi-inclusive deeply inelastic
-  scattering}, {\emph{Phys. Rev.} {\bf D73} (2006) 014021},
-  [\href{https://arxiv.org/abs/hep-ph/0509076}{{\tt hep-ph/0509076}}].
-
-\bibitem{D'Alesio:2007jt}
-U.~D'Alesio and F.~Murgia, \emph{{Azimuthal and Single Spin Asymmetries in Hard
-  Scattering Processes}},
-  \href{http://dx.doi.org/10.1016/j.ppnp.2008.01.001}{\emph{Prog. Part. Nucl.
-  Phys. 61} {\bf 2008} (2008) 394--454},
-  [\href{https://arxiv.org/abs/0712.4328}{{\tt 0712.4328}}].
-
-\bibitem{Schweitzer:2010tt}
-P.~Schweitzer, T.~Teckentrup and A.~Metz, \emph{{Intrinsic transverse parton
-  momenta in deeply inelastic reactions}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.81.094019}{\emph{Phys. Rev.} {\bf
-  D81} (2010) 094019}, [\href{https://arxiv.org/abs/1003.2190}{{\tt
-  1003.2190}}].
-
-\bibitem{Signori:2013mda}
-A.~Signori, A.~Bacchetta, M.~Radici and G.~Schnell, \emph{{Investigations into
-  the flavor dependence of partonic transverse momentum}},
-  \href{http://dx.doi.org/10.1007/JHEP11(2013)194}{\emph{JHEP} {\bf 11} (2013)
-  194}, [\href{https://arxiv.org/abs/1309.3507}{{\tt 1309.3507}}].
-
-\bibitem{Anselmino:2013lza}
-M.~Anselmino, M.~Boglione, J.~O. Gonzalez~Hernandez, S.~Melis and A.~Prokudin,
-  \emph{{Unpolarised Transverse Momentum Dependent Distribution and
-  Fragmentation Functions from SIDIS Multiplicities}},
-  \href{http://dx.doi.org/10.1007/JHEP04(2014)005}{\emph{JHEP} {\bf 04} (2014)
-  005}, [\href{https://arxiv.org/abs/1312.6261}{{\tt 1312.6261}}].
-
-\bibitem{Bacchetta:2008xw}
-A.~Bacchetta, D.~Boer, M.~Diehl and P.~J. Mulders, \emph{{Matches and
-  mismatches in the descriptions of semi- inclusive processes at low and high
-  transverse momentum}},
-  \href{http://dx.doi.org/10.1088/1126-6708/2008/08/023}{\emph{JHEP} {\bf 08}
-  (2008) 023}, [\href{https://arxiv.org/abs/0803.0227}{{\tt 0803.0227}}].
-
-\bibitem{Landry:2002ix}
-F.~Landry, R.~Brock, P.~M. Nadolsky and C.~Yuan, \emph{{Tevatron Run-1 $Z$
-  boson data and Collins-Soper-Sterman resummation formalism}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.67.073016}{\emph{Phys. Rev.} {\bf
-  D67} (2003) 073016}, [\href{https://arxiv.org/abs/hep-ph/0212159}{{\tt
-  hep-ph/0212159}}].
-
-\bibitem{Martin:2009iq}
-A.~D. Martin, W.~J. Stirling, R.~S. Thorne and G.~Watt, \emph{{Parton
-  distributions for the LHC}},
-  \href{http://dx.doi.org/10.1140/epjc/s10052-009-1072-5}{\emph{Eur. Phys. J.}
-  {\bf C63} (2009) 189--285}, [\href{https://arxiv.org/abs/0901.0002}{{\tt
-  0901.0002}}].
-
-\bibitem{deFlorian:2007aj}
-D.~de~Florian, R.~Sassot and M.~Stratmann, \emph{{Global analysis of
-  fragmentation functions for pions and kaons and their uncertainties}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.75.114010}{\emph{Phys. Rev.} {\bf
-  D75} (2007) 114010}, [\href{https://arxiv.org/abs/hep-ph/0703242}{{\tt
-  hep-ph/0703242}}].
-
-\bibitem{Schweitzer:2012hh}
-P.~Schweitzer, M.~Strikman and C.~Weiss, \emph{{Intrinsic transverse momentum
-  and parton correlations from dynamical chiral symmetry breaking}},
-  \href{http://dx.doi.org/10.1007/JHEP01(2013)163}{\emph{JHEP} {\bf 01} (2013)
-  163}, [\href{https://arxiv.org/abs/1210.1267}{{\tt 1210.1267}}].
-
-\bibitem{Collins:2016hqq}
-J.~Collins, L.~Gamberg, A.~Prokudin, T.~C. Rogers, N.~Sato and B.~Wang,
-  \emph{{Relating Transverse Momentum Dependent and Collinear Factorization
-  Theorems in a Generalized Formalism}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.94.034014}{\emph{Phys. Rev.} {\bf
-  D94} (2016) 034014}, [\href{https://arxiv.org/abs/1605.00671}{{\tt
-  1605.00671}}].
-
-\bibitem{Osipenko:2008aa}
-{\scshape CLAS} collaboration, M.~Osipenko et~al., \emph{{Measurement of
-  unpolarized semi-inclusive pi+ electroproduction off the proton}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.80.032004}{\emph{Phys. Rev.} {\bf
-  D80} (2009) 032004}, [\href{https://arxiv.org/abs/0809.1153}{{\tt
-  0809.1153}}].
-
-\bibitem{Airapetian:2012ki}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Multiplicities of
-  charged pions and kaons from semi-inclusive deep-inelastic scattering by the
-  proton and the deuteron}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.87.074029}{\emph{Phys. Rev.} {\bf
-  D87} (2013) 074029}, [\href{https://arxiv.org/abs/1212.5407}{{\tt
-  1212.5407}}].
-
-\bibitem{Aghasyan:2017ctw}
-{\scshape COMPASS} collaboration, M.~Aghasyan et~al.,
-  \emph{{Transverse-momentum-dependent Multiplicities of Charged Hadrons in
-  Muon-Deuteron Deep Inelastic Scattering}},
-  \href{https://arxiv.org/abs/1709.07374}{{\tt 1709.07374}}.
-
-\bibitem{Bacchetta:2017gcc}
-A.~Bacchetta, F.~Delcarro, C.~Pisano, M.~Radici and A.~Signori,
-  \emph{{Extraction of partonic transverse momentum distributions from
-  semi-inclusive deep-inelastic scattering, Drell-Yan and Z-boson production}},
-  \href{http://dx.doi.org/10.1007/JHEP06(2017)081}{\emph{JHEP} {\bf 06} (2017)
-  081}, [\href{https://arxiv.org/abs/1703.10157}{{\tt 1703.10157}}].
-
-\bibitem{Avakian:2010ae}
-{\scshape CLAS} collaboration, H.~Avakian et~al., \emph{{Measurement of Single
-  and Double Spin Asymmetries in Deep Inelastic Pion Electroproduction with a
-  Longitudinally Polarized Target}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.105.262002}{\emph{Phys. Rev.
-  Lett.} {\bf 105} (2010) 262002}, [\href{https://arxiv.org/abs/1003.4549}{{\tt
-  1003.4549}}].
-
-\bibitem{Anselmino:2011gs}
-M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia and A.~Prokudin,
-  \emph{{Sivers Distribution Functions and the Latest SIDIS Data}},  in
-  \emph{{19th International Workshop on Deep-Inelastic Scattering and Related
-  Subjects (DIS 2011) Newport News, Virginia, April 11-15, 2011}}, 2011.
-\newblock \href{https://arxiv.org/abs/1107.4446}{{\tt 1107.4446}}.
-
-\bibitem{Airapetian:2009ae}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Observation of
-  the Naive-T-odd Sivers Effect in Deep-Inelastic Scattering}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.103.152002}{\emph{Phys. Rev.
-  Lett.} {\bf 103} (2009) 152002}, [\href{https://arxiv.org/abs/0906.3918}{{\tt
-  0906.3918}}].
-
-\bibitem{Adolph:2012sp}
-{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{II Experimental
-  investigation of transverse spin asymmetries in $\mu$-p SIDIS processes:
-  Sivers asymmetries}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2012.09.056}{\emph{Phys. Lett.}
-  {\bf B717} (2012) 383--389}, [\href{https://arxiv.org/abs/1205.5122}{{\tt
-  1205.5122}}].
-
-\bibitem{Sivers:1989cc}
-D.~W. Sivers, \emph{Single spin production asymmetries from the hard scattering
-  of point-like constituents}, {\emph{Phys. Rev.} {\bf D41} (1990) 83}.
-
-\bibitem{Anselmino:2010bs}
-M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia and A.~Prokudin,
-  \emph{{New insight on the Sivers transverse momentum dependent distribution
-  function}}, \href{http://dx.doi.org/10.1088/1742-6596/295/1/012062}{\emph{J.
-  Phys. Conf. Ser.} {\bf 295} (2011) 012062},
-  [\href{https://arxiv.org/abs/1012.3565}{{\tt 1012.3565}}].
-
-\bibitem{Anselmino:2005ea}
-M.~Anselmino et~al., \emph{Extracting the sivers function from polarized sidis
-  data and making predictions}, {\emph{Phys. Rev.} {\bf D72} (2005) 094007},
-  [\href{https://arxiv.org/abs/hep-ph/0507181}{{\tt hep-ph/0507181}}].
-
-\bibitem{Anselmino:2005an}
-M.~Anselmino et~al., \emph{{Comparing extractions of Sivers functions}},
-  \href{https://arxiv.org/abs/hep-ph/0511017}{{\tt hep-ph/0511017}}.
-
-\bibitem{Vogelsang:2005cs}
-W.~Vogelsang and F.~Yuan, \emph{Single-transverse spin asymmetries: From dis to
-  hadronic collisions}, {\emph{Phys. Rev.} {\bf D72} (2005) 054028}.
-
-\bibitem{Anselmino:2008sga}
-M.~Anselmino et~al., \emph{{Sivers Effect for Pion and Kaon Production in Semi-
-  Inclusive Deep Inelastic Scattering}},
-  \href{http://dx.doi.org/10.1140/epja/i2008-10697-y}{\emph{Eur. Phys. J.} {\bf
-  A39} (2009) 89--100}, [\href{https://arxiv.org/abs/0805.2677}{{\tt
-  0805.2677}}].
-
-\bibitem{Bacchetta:2011gx}
-A.~Bacchetta and M.~Radici, \emph{{Constraining quark angular momentum through
-  semi-inclusive measurements}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.107.212001}{\emph{Phys. Rev.
-  Lett.} {\bf 107} (2011) 212001}, [\href{https://arxiv.org/abs/1107.5755}{{\tt
-  1107.5755}}].
-
-\bibitem{Anselmino:2012aa}
-M.~Anselmino, M.~Boglione and S.~Melis, \emph{{A Strategy towards the
-  extraction of the Sivers function with TMD evolution}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.86.014028}{\emph{Phys. Rev.} {\bf
-  D86} (2012) 014028}, [\href{https://arxiv.org/abs/1204.1239}{{\tt
-  1204.1239}}].
-
-\bibitem{Bacchetta:2002ux}
-A.~Bacchetta and M.~Radici, \emph{{Partial wave analysis of two hadron
-  fragmentation functions}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.67.094002}{\emph{Phys. Rev.} {\bf
-  D67} (2003) 094002}, [\href{https://arxiv.org/abs/hep-ph/0212300}{{\tt
-  hep-ph/0212300}}].
-
-\bibitem{Bacchetta:2003vn}
-A.~Bacchetta and M.~Radici, \emph{{Two hadron semiinclusive production
-  including subleading twist}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.69.074026}{\emph{Phys. Rev.} {\bf
-  D69} (2004) 074026}, [\href{https://arxiv.org/abs/hep-ph/0311173}{{\tt
-  hep-ph/0311173}}].
-
-\bibitem{Bacchetta:2011ip}
-A.~Bacchetta, A.~Courtoy and M.~Radici, \emph{{First glances at the
-  transversity parton distribution through dihadron fragmentation functions}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.107.012001}{\emph{Phys. Rev.
-  Lett.} {\bf 107} (2011) 012001}, [\href{https://arxiv.org/abs/1104.3855}{{\tt
-  1104.3855}}].
-
-\bibitem{Bacchetta:2012ty}
-A.~Bacchetta, A.~Courtoy and M.~Radici, \emph{{First extraction of valence
-  transversities in a collinear framework}},
-  \href{http://dx.doi.org/10.1007/JHEP03(2013)119}{\emph{JHEP} {\bf 03} (2013)
-  119}, [\href{https://arxiv.org/abs/1212.3568}{{\tt 1212.3568}}].
-
-\bibitem{Radici:2015mwa}
-M.~Radici, A.~Courtoy, A.~Bacchetta and M.~Guagnelli, \emph{{Improved
-  extraction of valence transversity distributions from inclusive dihadron
-  production}}, \href{http://dx.doi.org/10.1007/JHEP05(2015)123}{\emph{JHEP}
-  {\bf 05} (2015) 123}, [\href{https://arxiv.org/abs/1503.03495}{{\tt
-  1503.03495}}].
-
-\bibitem{Radici:2018iag}
-M.~Radici and A.~Bacchetta, \emph{{First Extraction of Transversity from a
-  Global Analysis of Electron-Proton and Proton-Proton Data}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.120.192001}{\emph{Phys. Rev.
-  Lett.} {\bf 120} (2018) 192001},
-  [\href{https://arxiv.org/abs/1802.05212}{{\tt 1802.05212}}].
-
-\bibitem{Aghasyan:2017jop}
-{\scshape COMPASS} collaboration, M.~Aghasyan et~al., \emph{{First measurement
-  of transverse-spin-dependent azimuthal asymmetries in the Drell-Yan
-  process}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.119.112002}{\emph{Phys. Rev.
-  Lett.} {\bf 119} (2017) 112002},
-  [\href{https://arxiv.org/abs/1704.00488}{{\tt 1704.00488}}].
-
-\bibitem{Parsamyan:2018zju}
-{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{First measurement of
-  transverse-spin-dependent azimuthal asymmetries in the Drell-Yan process}},
-  \href{http://dx.doi.org/10.22323/1.297.0243}{\emph{PoS} {\bf DIS2017} (2018)
-  243}, [\href{https://arxiv.org/abs/1801.01487}{{\tt 1801.01487}}].
-
-\bibitem{Collins:1992kk}
-J.~C. Collins, \emph{Fragmentation of transversely polarized quarks probed in
-  transverse momentum distributions}, {\emph{Nucl. Phys.} {\bf B396} (1993)
-  161--182}.
-
-\bibitem{Anselmino:2013vqa}
-M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia and A.~Prokudin,
-  \emph{{Simultaneous extraction of transversity and Collins functions from new
-  SIDIS and $e^{+}e^{-}$ data}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.87.094019}{\emph{Phys. Rev.} {\bf
-  D87} (2013) 094019}, [\href{https://arxiv.org/abs/1303.3822}{{\tt
-  1303.3822}}].
-
-\bibitem{Kang:2014zza}
-Z.-B. Kang, A.~Prokudin, P.~Sun and F.~Yuan, \emph{{Nucleon tensor charge from
-  Collins azimuthal asymmetry measurements}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.91.071501}{\emph{Phys. Rev.} {\bf
-  D91} (2015) 071501}, [\href{https://arxiv.org/abs/1410.4877}{{\tt
-  1410.4877}}].
-
-\bibitem{Anselmino:2015sxa}
-M.~Anselmino, M.~Boglione, U.~D'Alesio, J.~O. Gonzalez~Hernandez, S.~Melis,
-  F.~Murgia et~al., \emph{{Collins functions for pions from SIDIS and new
-  $e^+e^-$ data: a first glance at their transverse momentum dependence}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.92.114023}{\emph{Phys. Rev.} {\bf
-  D92} (2015) 114023}, [\href{https://arxiv.org/abs/1510.05389}{{\tt
-  1510.05389}}].
-
-\bibitem{Airapetian:2010ds}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Effects of
-  transversity in deep-inelastic scattering by polarized protons}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2010.08.012}{\emph{Phys. Lett.}
-  {\bf B693} (2010) 11--16}, [\href{https://arxiv.org/abs/1006.4221}{{\tt
-  1006.4221}}].
-
-\bibitem{Adolph:2014zba}
-{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{Collins and Sivers
-  asymmetries in muonproduction of pions and kaons off transversely polarised
-  protons}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2015.03.056}{\emph{Phys. Lett.}
-  {\bf B744} (2015) 250--259}, [\href{https://arxiv.org/abs/1408.4405}{{\tt
-  1408.4405}}].
-
-\bibitem{Barone:2009hw}
-V.~Barone, S.~Melis and A.~Prokudin, \emph{{The Boer-Mulders effect in
-  unpolarized SIDIS: An Analysis of the COMPASS and HERMES data on the cos2phi
-  asymmetry}}, \href{http://dx.doi.org/10.1103/PhysRevD.81.114026}{\emph{Phys.
-  Rev.} {\bf D81} (2010) 114026}, [\href{https://arxiv.org/abs/0912.5194}{{\tt
-  0912.5194}}].
-
-\bibitem{Airapetian:2012yg}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Azimuthal
-  distributions of charged hadrons, pions, and kaons produced in deep-inelastic
-  scattering off unpolarized protons and deuterons}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.87.012010}{\emph{Phys. Rev.} {\bf
-  D87} (2013) 012010}, [\href{https://arxiv.org/abs/1204.4161}{{\tt
-  1204.4161}}].
-
-\bibitem{Adolph:2014pwc}
-{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{Measurement of
-  azimuthal hadron asymmetries in semi-inclusive deep inelastic scattering off
-  unpolarised nucleons}},
-  \href{http://dx.doi.org/10.1016/j.nuclphysb.2014.07.019}{\emph{Nucl. Phys.}
-  {\bf B886} (2014) 1046--1077}, [\href{https://arxiv.org/abs/1401.6284}{{\tt
-  1401.6284}}].
-
-\bibitem{Cahn:1978se}
-R.~N. Cahn, \emph{{Azimuthal Dependence in Leptoproduction: A Simple Parton
-  Model Calculation}},
-  \href{http://dx.doi.org/10.1016/0370-2693(78)90020-5}{\emph{Phys. Lett.} {\bf
-  B78} (1978) 269}.
-
-\bibitem{Cao:2018qqf}
-X.~Cao, \emph{{Parton distributions and $\cos 2\phi_h$ asymmetry induced by
-  anomalous photon-quark coupling}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.97.114010}{\emph{Phys. Rev.} {\bf
-  D97} (2018) 114010}, [\href{https://arxiv.org/abs/1802.02417}{{\tt
-  1802.02417}}].
-
-\bibitem{Barone:2010gk}
-V.~Barone, S.~Melis and A.~Prokudin, \emph{{Azimuthal asymmetries in
-  unpolarized Drell-Yan processes and the Boer-Mulders distributions of
-  antiquarks}}, \href{http://dx.doi.org/10.1103/PhysRevD.82.114025}{\emph{Phys.
-  Rev.} {\bf D82} (2010) 114025}, [\href{https://arxiv.org/abs/1009.3423}{{\tt
-  1009.3423}}].
-
-\bibitem{Barone:2015ksa}
-V.~Barone, M.~Boglione, J.~O. Gonzalez~Hernandez and S.~Melis,
-  \emph{{Phenomenological analysis of azimuthal asymmetries in unpolarized
-  semi-inclusive deep inelastic scattering}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.91.074019}{\emph{Phys. Rev.} {\bf
-  D91} (2015) 074019}, [\href{https://arxiv.org/abs/1502.04214}{{\tt
-  1502.04214}}].
-
-\bibitem{Avakian:2008dz}
-H.~Avakian, A.~V. Efremov, P.~Schweitzer and F.~Yuan, \emph{{Transverse
-  momentum dependent distribution function $h_{1T}^\perp$ and the single spin
-  asymmetry $A_{UT}^{\sin(3\phi-\phi_S)}$}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.78.114024}{\emph{Phys. Rev.} {\bf
-  D78} (2008) 114024}, [\href{https://arxiv.org/abs/0805.3355}{{\tt
-  0805.3355}}].
-
-\bibitem{She:2009jq}
-J.~She, J.~Zhu and B.-Q. Ma, \emph{{Pretzelosity h(1T)**perpendicular and quark
-  orbital angular momentum}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.79.054008}{\emph{Phys. Rev.} {\bf
-  D79} (2009) 054008}, [\href{https://arxiv.org/abs/0902.3718}{{\tt
-  0902.3718}}].
-
-\bibitem{Lorce:2011kn}
-C.~Lorce and B.~Pasquini, \emph{{Pretzelosity TMD and Quark Orbital Angular
-  Momentum}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2012.03.025}{\emph{Phys. Lett.}
-  {\bf B710} (2012) 486--488}, [\href{https://arxiv.org/abs/1111.6069}{{\tt
-  1111.6069}}].
-
-\bibitem{Parsamyan:2013fia}
-{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Transverse spin
-  asymmetries at COMPASS: beyond Collins and Sivers effects}}, {\emph{PoS} {\bf
-  DIS2013} (2013) 231}, [\href{https://arxiv.org/abs/1307.0183}{{\tt
-  1307.0183}}].
-
-\bibitem{Schnell:2010zza}
-{\scshape HERMES} collaboration, G.~Schnell, \emph{{The Sivers and other
-  semi-inclusive single-spin asymmetries at HERMES}}, {\emph{PoS} {\bf DIS2010}
-  (2010) 247}.
-
-\bibitem{Lefky:2014eia}
-C.~Lefky and A.~Prokudin, \emph{{Extraction of the distribution function
-  $h^{\perp}_{1T}$ from experimental data}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.91.034010}{\emph{Phys. Rev.} {\bf
-  D91} (2015) 034010}, [\href{https://arxiv.org/abs/1411.0580}{{\tt
-  1411.0580}}].
-
-\bibitem{Kotzinian:2008fe}
-A.~Kotzinian, \emph{{SIDIS Asymmetries in Quark-Diquark Model}},  in
-  \emph{{Transversity 2008: 2nd International Workshop on Transverse
-  Polarization Phenomena in Hard Processes Ferrara, Italy, May 28-31, 2008}},
-  2008.
-\newblock \href{https://arxiv.org/abs/0806.3804}{{\tt 0806.3804}}.
-\newblock \href{http://dx.doi.org/10.1142/9789814277785_0029}{DOI}.
-
-\bibitem{Boffi:2009sh}
-S.~Boffi, A.~V. Efremov, B.~Pasquini and P.~Schweitzer, \emph{{Azimuthal spin
-  asymmetries in light-cone constituent quark models}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.79.094012}{\emph{Phys. Rev.} {\bf
-  D79} (2009) 094012}, [\href{https://arxiv.org/abs/0903.1271}{{\tt
-  0903.1271}}].
-
-\bibitem{Ball:2014uwa}
-{\scshape NNPDF} collaboration, R.~D. Ball et~al., \emph{{Parton distributions
-  for the LHC Run II}},
-  \href{http://dx.doi.org/10.1007/JHEP04(2015)040}{\emph{JHEP} {\bf 04} (2015)
-  040}, [\href{https://arxiv.org/abs/1410.8849}{{\tt 1410.8849}}].
-
-\bibitem{Huang:2011bc}
-{\scshape Jefferson Lab Hall A} collaboration, J.~Huang et~al.,
-  \emph{{Beam-Target Double Spin Asymmetry $A_{LT}$ in Charged Pion Production
-  from Deep Inelastic Scattering on a Transversely Polarized He-3 Target at
-  $1.4 < Q^2 < 2.7 GeV^2$}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.108.052001}{\emph{Phys. Rev.
-  Lett.} {\bf 108} (2012) 052001}, [\href{https://arxiv.org/abs/1108.0489}{{\tt
-  1108.0489}}].
-
-\bibitem{Parsamyan:2007ju}
-{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{New target transverse
-  spin dependent azimuthal asymmetries from COMPASS experiment}},
-  \href{http://dx.doi.org/10.1140/epjst/e2008-00780-1}{\emph{Eur. Phys. J. ST}
-  {\bf 162} (2008) 89--96}, [\href{https://arxiv.org/abs/0709.3440}{{\tt
-  0709.3440}}].
-
-\bibitem{Parsamyan:2015dfa}
-{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Transverse spin
-  azimuthal asymmetries in SIDIS at COMPASS: Multidimensional analysis}},
-  \href{http://dx.doi.org/10.1142/S2010194516600296}{\emph{Int. J. Mod. Phys.
-  Conf. Ser.} {\bf 40} (2016) 1660029},
-  [\href{https://arxiv.org/abs/1504.01599}{{\tt 1504.01599}}].
-
-\bibitem{Parsamyan:2018evv}
-{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Measurement of
-  target-polarization dependent azimuthal asymmetries in SIDIS and Drell-Yan
-  processes at COMPASS experiment}}, {\emph{PoS} {\bf QCDEV2017} (2018) 042}.
-
-\bibitem{Pappalardo:2011cu}
-{\scshape HERMES} collaboration, L.~L. Pappalardo and M.~Diefenthaler,
-  \emph{{Measurements of Double-Spin Asymmetries in SIDIS of Longitudinally
-  Polarized Leptons off Transversely Polarized Protons}},
-  \href{https://arxiv.org/abs/1107.4227}{{\tt 1107.4227}}.
-
-\bibitem{Pappalardo:2012zz}
-{\scshape HERMES} collaboration, L.~L. Pappalardo, \emph{{Accessing TMDs at
-  HERMES}}, \href{http://dx.doi.org/10.1063/1.3700519}{\emph{AIP Conf. Proc.}
-  {\bf 1441} (2012) 229--232}.
-
-\bibitem{Airapetian:1999tv}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Observation of a
-  single spin azimuthal asymmetry in semiinclusive pion electro production}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.84.4047}{\emph{Phys. Rev. Lett.}
-  {\bf 84} (2000) 4047--4051},
-  [\href{https://arxiv.org/abs/hep-ex/9910062}{{\tt hep-ex/9910062}}].
-
-\bibitem{Parsamyan:2018ovx}
-{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Measurement of
-  longitudinal-target-polarization dependent azimuthal asymmetries in SIDIS at
-  COMPASS experiment}}, {\emph{PoS} {\bf DIS2017} (2018) 259},
-  [\href{https://arxiv.org/abs/1801.01488}{{\tt 1801.01488}}].
-
-\bibitem{Jawalkar:2017ube}
-S.~Jawalkar et~al., \emph{{Semi-Inclusive $\pi_0$ target and beam-target
-  asymmetries from 6 GeV electron scattering with CLAS}},
-  \href{https://arxiv.org/abs/1709.10054}{{\tt 1709.10054}}.
-
-\bibitem{Airapetian:2002mf}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Measurement of
-  single spin azimuthal asymmetries in semiinclusive electroproduction of pions
-  and kaons on a longitudinally polarized deuterium target}},
-  \href{http://dx.doi.org/10.1016/S0370-2693(03)00566-5}{\emph{Phys. Lett.}
-  {\bf B562} (2003) 182--192},
-  [\href{https://arxiv.org/abs/hep-ex/0212039}{{\tt hep-ex/0212039}}].
-
-\bibitem{Avakian:2003pk}
-{\scshape CLAS} collaboration, H.~Avakian et~al., \emph{{Measurement of
-  beam-spin asymmetries for pi + electroproduction above the baryon resonance
-  region}}, \href{http://dx.doi.org/10.1103/PhysRevD.69.112004}{\emph{Phys.
-  Rev.} {\bf D69} (2004) 112004},
-  [\href{https://arxiv.org/abs/hep-ex/0301005}{{\tt hep-ex/0301005}}].
-
-\bibitem{Airapetian:2006rx}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Beam-Spin
-  Asymmetries in the Azimuthal Distribution of Pion Electroproduction}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2007.03.015}{\emph{Phys. Lett.}
-  {\bf B648} (2007) 164--170},
-  [\href{https://arxiv.org/abs/hep-ex/0612059}{{\tt hep-ex/0612059}}].
-
-\bibitem{Gohn:2009zz}
-W.~Gohn, H.~Avakian, K.~Joo and M.~Ungaro, \emph{{Beam spin asymmetries from
-  semi-inclusive pion electroproduction in deep inelastic scattering}},
-  \href{http://dx.doi.org/10.1063/1.3215689}{\emph{AIP Conf. Proc.} {\bf 1149}
-  (2009) 461--464}.
-
-\bibitem{Aghasyan:2011ha}
-M.~Aghasyan, H.~Avakian, P.~Rossi, E.~De~Sanctis, D.~Hasch et~al.,
-  \emph{{Precise Measurements of Beam Spin Asymmetries in Semi-Inclusive
-  $\pi^0$ production}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2011.09.044}{\emph{Phys. Lett.}
-  {\bf B704} (2011) 397--402}, [\href{https://arxiv.org/abs/1106.2293}{{\tt
-  1106.2293}}].
-
-\bibitem{Gohn:2014zbz}
-{\scshape CLAS} collaboration, W.~Gohn et~al., \emph{{Beam-spin asymmetries
-  from semi-inclusive pion electroproduction}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.89.072011}{\emph{Phys. Rev.} {\bf
-  D89} (2014) 072011}, [\href{https://arxiv.org/abs/1402.4097}{{\tt
-  1402.4097}}].
-
-\bibitem{Efremov:2002ut}
-A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Azimuthal asymmetries at
-  CLAS: extraction of e**a(x) and prediction of A(UL)}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.67.114014}{\emph{Phys. Rev.} {\bf
-  D67} (2003) 114014}, [\href{https://arxiv.org/abs/hep-ph/0208124}{{\tt
-  hep-ph/0208124}}].
-
-\bibitem{Afanasev:2003ze}
-A.~Afanasev and C.~E. Carlson, \emph{{Single spin beam asymmetry in
-  semiexclusive deep inelastic electroproduction}},  in \emph{{Intersections of
-  particle and nuclear physics. Proceedings, 8th Conference, CIPANP 2003, New
-  York, USA, May 19-24, 2003}}, 2003.
-\newblock \href{https://arxiv.org/abs/hep-ph/0308163}{{\tt hep-ph/0308163}}.
-
-\bibitem{Yuan:2003gu}
-F.~Yuan, \emph{{The Beam single spin asymmetry in semiinclusive deep inelastic
-  scattering}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2004.03.040}{\emph{Phys. Lett.}
-  {\bf B589} (2004) 28--34}, [\href{https://arxiv.org/abs/hep-ph/0310279}{{\tt
-  hep-ph/0310279}}].
-
-\bibitem{Gamberg:2003pz}
-L.~P. Gamberg, D.~S. Hwang and K.~A. Oganessyan, \emph{{Chiral odd
-  fragmentation functions in single pion inclusive electroproduction}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2004.01.054}{\emph{Phys. Lett.}
-  {\bf B584} (2004) 276--284},
-  [\href{https://arxiv.org/abs/hep-ph/0311221}{{\tt hep-ph/0311221}}].
-
-\bibitem{Afanasev:2006gw}
-A.~V. Afanasev and C.~E. Carlson, \emph{{Beam Single-Spin Asymmetry in
-  Semi-Inclusive Deep Inelastic Scattering}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.74.114027}{\emph{Phys. Rev.} {\bf
-  D74} (2006) 114027}, [\href{https://arxiv.org/abs/hep-ph/0603269}{{\tt
-  hep-ph/0603269}}].
-
-\bibitem{Mao:2012dk}
-W.~Mao and Z.~Lu, \emph{{Beam single spin asymmetry of neutral pion production
-  in semi-inclusive deep inelastic scattering}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.87.014012}{\emph{Phys. Rev.} {\bf
-  D87} (2013) 014012}, [\href{https://arxiv.org/abs/1210.4790}{{\tt
-  1210.4790}}].
-
-\bibitem{Mao:2013waa}
-W.~Mao and Z.~Lu, \emph{{Beam spin asymmetries of charged and neutral pion
-  production in semi-inclusive DIS}},
-  \href{http://dx.doi.org/10.1140/epjc/s10052-013-2557-9}{\emph{Eur. Phys. J.}
-  {\bf C73} (2013) 2557}, [\href{https://arxiv.org/abs/1306.1004}{{\tt
-  1306.1004}}].
-
-\bibitem{Mao:2014dva}
-W.~Mao and Z.~Lu, \emph{{On the beam spin asymmetries of electroproduction of
-  charged hadrons off the nucleon targets}},
-  \href{http://dx.doi.org/10.1140/epjc/s10052-014-2910-7}{\emph{Eur. Phys. J.}
-  {\bf C74} (2014) 2910}, [\href{https://arxiv.org/abs/1401.4653}{{\tt
-  1401.4653}}].
-
-\bibitem{Courtoy:2014ixa}
-A.~Courtoy, \emph{{Insights into the higher-twist distribution $e(x)$ at
-  CLAS}},  \href{https://arxiv.org/abs/1405.7659}{{\tt 1405.7659}}.
-
-\bibitem{Yang:2016mxl}
-Y.~Yang, Z.~Lu and I.~Schmidt, \emph{{Twist-3 T-odd fragmentation functions
-  $G^\perp$ and $\tilde{G}^\perp$ in a spectator model}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2016.08.053}{\emph{Phys. Lett.}
-  {\bf B761} (2016) 333--339}, [\href{https://arxiv.org/abs/1607.01638}{{\tt
-  1607.01638}}].
-
-\bibitem{Mao:2014fma}
-W.~Mao, Z.~Lu, B.-Q. Ma and I.~Schmidt, \emph{{Double spin asymmetries
-  $A_{LT}^{\cos\phi_S}$ and $A_{LT}^{\cos(2\phi_h -\phi_S)}$ in semi-inclusive
-  DIS}}, \href{http://dx.doi.org/10.1103/PhysRevD.91.034029}{\emph{Phys. Rev.}
-  {\bf D91} (2015) 034029}, [\href{https://arxiv.org/abs/1412.7390}{{\tt
-  1412.7390}}].
-
-\bibitem{Wang:2016dti}
-X.~Wang, W.~Mao and Z.~Lu, \emph{{Double-spin asymmetry $A^{\cos\phi_S}_{LT}$
-  in semi-inclusive DIS at CLAS12 and EIC within the collinear framework}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.94.074014}{\emph{Phys. Rev.} {\bf
-  D94} (2016) 074014}, [\href{https://arxiv.org/abs/1606.01649}{{\tt
-  1606.01649}}].
-
-\bibitem{Airapetian:2018rlq}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Longitudinal
-  double-spin asymmetries in semi-inclusive deep-inelastic scattering of
-  electrons and positrons by protons and deuterons}},
-  \href{https://arxiv.org/abs/1810.07054}{{\tt 1810.07054}}.
-
-\bibitem{Anselmino:2006yc}
-M.~Anselmino, A.~Efremov, A.~Kotzinian and B.~Parsamyan, \emph{{Transverse
-  momentum dependence of the quark helicity distributions and the Cahn effect
-  in double-spin asymmetry A(LL) in semi inclusive DIS}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.74.074015}{\emph{Phys. Rev.} {\bf
-  D74} (2006) 074015}, [\href{https://arxiv.org/abs/hep-ph/0608048}{{\tt
-  hep-ph/0608048}}].
-
-\bibitem{Mao:2016hdi}
-W.~Mao, X.~Wang, X.~Du, Z.~Lu and B.-Q. Ma, \emph{{On the cos $\phi_h$
-  asymmetry in electroproduction of pions in double longitudinally polarized
-  process}},
-  \href{http://dx.doi.org/10.1016/j.nuclphysa.2015.10.004}{\emph{Nucl. Phys.}
-  {\bf A945} (2016) 153--167}.
-
-\bibitem{Airapetian:2001eg}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Single spin
-  azimuthal asymmetries in electroproduction of neutral pions in semiinclusive
-  deep inelastic scattering}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.64.097101}{\emph{Phys. Rev.} {\bf
-  D64} (2001) 097101}, [\href{https://arxiv.org/abs/hep-ex/0104005}{{\tt
-  hep-ex/0104005}}].
-
-\bibitem{DeSanctis:2000fh}
-E.~De~Sanctis, W.~D. Nowak and K.~A. Oganesian, \emph{{Single spin azimuthal
-  asymmetries in the `Reduced twist - three approximation'}},
-  \href{http://dx.doi.org/10.1016/S0370-2693(00)00596-7}{\emph{Phys. Lett.}
-  {\bf B483} (2000) 69--73}, [\href{https://arxiv.org/abs/hep-ph/0002091}{{\tt
-  hep-ph/0002091}}].
-
-\bibitem{Oganessian:2000um}
-K.~A. Oganessian, N.~Bianchi, E.~De~Sanctis and W.~D. Nowak,
-  \emph{{Investigation of single spin asymmetries in pi+ electroproduction}},
-  \href{http://dx.doi.org/10.1016/S0375-9474(00)00609-6}{\emph{Nucl. Phys.}
-  {\bf A689} (2001) 784--792},
-  [\href{https://arxiv.org/abs/hep-ph/0010261}{{\tt hep-ph/0010261}}].
-
-\bibitem{Efremov:2001ia}
-A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Predictions for azimuthal
-  asymmetries in pion and kaon production in SIDIS off a longitudinally
-  polarized deuterium target at HERMES}},
-  \href{http://dx.doi.org/10.1007/s100520200918}{\emph{Eur. Phys. J.} {\bf C24}
-  (2002) 407--412}, [\href{https://arxiv.org/abs/hep-ph/0112166}{{\tt
-  hep-ph/0112166}}].
-
-\bibitem{Efremov:2002td}
-A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Azimuthal asymmetry in
-  electroproduction of neutral pions in semiinclusive DIS}},
-  \href{http://dx.doi.org/10.1016/S0370-2693(01)01258-8,
-  10.1016/S0370-2693(02)02518-2}{\emph{Phys. Lett.} {\bf B522} (2001) 37--48},
-  [\href{https://arxiv.org/abs/hep-ph/0108213}{{\tt hep-ph/0108213}}].
-
-\bibitem{Efremov:2002sd}
-A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Azimuthal asymmetries and
-  Collins analyzing power}},
-  \href{http://dx.doi.org/10.1016/S0375-9474(02)01199-5}{\emph{Nucl. Phys.}
-  {\bf A711} (2002) 84--88}, [\href{https://arxiv.org/abs/hep-ph/0206267}{{\tt
-  hep-ph/0206267}}].
-
-\bibitem{Ma:2001ie}
-B.-Q. Ma, I.~Schmidt and J.-J. Yang, \emph{{Azimuthal spin asymmetries of pion
-  electroproduction}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.65.034010}{\emph{Phys. Rev.} {\bf
-  D65} (2002) 034010}, [\href{https://arxiv.org/abs/hep-ph/0110324}{{\tt
-  hep-ph/0110324}}].
-
-\bibitem{Ma:2002ns}
-B.-Q. Ma, I.~Schmidt and J.-J. Yang, \emph{{Reanalysis of azimuthal spin
-  asymmetries of meson electroproduction}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.66.094001}{\emph{Phys. Rev.} {\bf
-  D66} (2002) 094001}, [\href{https://arxiv.org/abs/hep-ph/0209114}{{\tt
-  hep-ph/0209114}}].
-
-\bibitem{Schweitzer:2003yr}
-P.~Schweitzer and A.~Bacchetta, \emph{{Azimuthal single spin asymmetries in
-  SIDIS in the light of chiral symmetry breaking}},
-  \href{http://dx.doi.org/10.1016/j.nuclphysa.2003.12.010}{\emph{Nucl. Phys.}
-  {\bf A732} (2004) 106--124},
-  [\href{https://arxiv.org/abs/hep-ph/0310318}{{\tt hep-ph/0310318}}].
-
-\bibitem{Lu:2014fva}
-Z.~Lu, \emph{{Single-spin asymmetries in electroproduction of pions on the
-  longitudinally polarized nucleon targets}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.90.014037}{\emph{Phys. Rev.} {\bf
-  D90} (2014) 014037}, [\href{https://arxiv.org/abs/1404.4229}{{\tt
-  1404.4229}}].
-
-\bibitem{Airapetian:2005jc}
-{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Subleading-twist
-  effects in single-spin asymmetries in semi-inclusive deep-inelastic
-  scattering on a longitudinally polarized hydrogen target}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2005.06.067}{\emph{Phys. Lett.}
-  {\bf B622} (2005) 14--22}, [\href{https://arxiv.org/abs/hep-ex/0505042}{{\tt
-  hep-ex/0505042}}].
-
-\bibitem{Mao:2014aoa}
-W.~Mao, Z.~Lu and B.-Q. Ma, \emph{{Transverse single-spin asymmetries of pion
-  production in semi-inclusive DIS at subleading twist}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.90.014048}{\emph{Phys. Rev.} {\bf
-  D90} (2014) 014048}, [\href{https://arxiv.org/abs/1405.3876}{{\tt
-  1405.3876}}].
-
-\bibitem{Cheng:1972sy}
-T.~P. Cheng and A.~Zee, \emph{{Coincidence electroproduction and scaling in the
-  regge region}}, \href{http://dx.doi.org/10.1103/PhysRevD.6.885}{\emph{Phys.
-  Rev.} {\bf D6} (1972) 885--893}.
-
-\bibitem{Aubert:1983cz}
-{\scshape European Muon} collaboration, J.~J. Aubert et~al., \emph{{Measurement
-  of Hadronic Azimuthal Distributions in Deep Inelastic Muon Proton
-  Scattering}},
-  \href{http://dx.doi.org/10.1016/0370-2693(83)91076-6}{\emph{Phys. Lett.} {\bf
-  130B} (1983) 118--122}.
-
-\bibitem{Dakin:1972db}
-J.~T. Dakin, G.~J. Feldman, W.~L. Lakin, F.~Martin, M.~L. Perl, E.~W. Petraske
-  et~al., \emph{Preliminary results on the inclusive electroproduction of
-  hadrons},  1972.
-
-\bibitem{Mkrtchyan:2007sr}
-H.~Mkrtchyan, P.~Bosted, G.~Adams, A.~Ahmidouch, T.~Angelescu et~al.,
-  \emph{{Transverse momentum dependence of semi-inclusive pion production}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2008.05.047}{\emph{Phys. Lett.}
-  {\bf B665} (2008) 20--25}, [\href{https://arxiv.org/abs/0709.3020}{{\tt
-  0709.3020}}].
-
-\bibitem{Anselmino:2011ch}
-M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia et~al.,
-  \emph{{General Helicity Formalism for Polarized Semi-Inclusive Deep Inelastic
-  Scattering}}, \href{http://dx.doi.org/10.1103/PhysRevD.83.114019}{\emph{Phys.
-  Rev.} {\bf D83} (2011) 114019}, [\href{https://arxiv.org/abs/1101.1011}{{\tt
-  1101.1011}}].
-
-\bibitem{Efremov:2004tp}
-A.~V. Efremov, K.~Goeke, S.~Menzel, A.~Metz and P.~Schweitzer, \emph{{Sivers
-  effect in semi-inclusive DIS and in the Drell-Yan process}},
-  \href{http://dx.doi.org/10.1016/j.physletb.2005.03.010}{\emph{Phys. Lett.}
-  {\bf B612} (2005) 233--244},
-  [\href{https://arxiv.org/abs/hep-ph/0412353}{{\tt hep-ph/0412353}}].
-
-\bibitem{Gamberg:2013kla}
-L.~Gamberg, Z.-B. Kang and A.~Prokudin, \emph{{Indication on the
-  process-dependence of the Sivers effect}},
-  \href{http://dx.doi.org/10.1103/PhysRevLett.110.232301}{\emph{Phys. Rev.
-  Lett.} {\bf 110} (2013) 232301}, [\href{https://arxiv.org/abs/1302.3218}{{\tt
-  1302.3218}}].
-
-\bibitem{Sun:2013dya}
-P.~Sun and F.~Yuan, \emph{{Energy Evolution for the Sivers Asymmetries in Hard
-  Processes}}, \href{http://dx.doi.org/10.1103/PhysRevD.88.034016}{\emph{Phys.
-  Rev.} {\bf D88} (2013) 034016}, [\href{https://arxiv.org/abs/1304.5037}{{\tt
-  1304.5037}}].
-
-\bibitem{Gluck:2000dy}
-M.~Gluck, E.~Reya, M.~Stratmann and W.~Vogelsang, \emph{{Models for the
-  polarized parton distributions of the nucleon}},
-  \href{http://dx.doi.org/10.1103/PhysRevD.63.094005}{\emph{Phys. Rev.} {\bf
-  D63} (2001) 094005}, [\href{https://arxiv.org/abs/hep-ph/0011215}{{\tt
-  hep-ph/0011215}}].
-
-\bibitem{Buckley:2014ana}
-A.~Buckley, J.~Ferrando, S.~Lloyd, K.~Nordström, B.~Page, M.~Rüfenacht et~al.,
-  \emph{{LHAPDF6: parton density access in the LHC precision era}},
-  \href{http://dx.doi.org/10.1140/epjc/s10052-015-3318-8}{\emph{Eur. Phys. J.}
-  {\bf C75} (2015) 132}, [\href{https://arxiv.org/abs/1412.7420}{{\tt
-  1412.7420}}].
-
-\bibitem{Berthou:2015oaw}
-B.~Berthou et~al., \emph{{PARTONS: PARtonic Tomography Of Nucleon Software}},
-  \href{http://dx.doi.org/10.1140/epjc/s10052-018-5948-0}{\emph{Eur. Phys. J.}
-  {\bf C78} (2018) 478}, [\href{https://arxiv.org/abs/1512.06174}{{\tt
-  1512.06174}}].
-
-\bibitem{Hautmann:2014kza}
-F.~Hautmann, H.~Jung, M.~Krämer, P.~J. Mulders, E.~R. Nocera, T.~C. Rogers
-  et~al., \emph{{TMDlib and TMDplotter: library and plotting tools for
-  transverse-momentum-dependent parton distributions}},
-  \href{http://dx.doi.org/10.1140/epjc/s10052-014-3220-9}{\emph{Eur. Phys. J.}
-  {\bf C74} (2014) 3220}, [\href{https://arxiv.org/abs/1408.3015}{{\tt
-  1408.3015}}].
-
-\end{thebibliography}\endgroup
-
-\end{document}
+%%%%%%%%%
+
+%
+%\providecommand{\href}[2]{#2}\begingroup\raggedright\begin{thebibliography}{100}
+%
+%
+%
+%\end{thebibliography}\endgroup
+%
+%\end{document}

### 2019-03-13 arxiv2/reply-to-referee-v2E.tex
AP

\documentclass[a4paper,11pt]{article}
\bibliographystyle{JHEP}
\usepackage{jheppub} 
\begin{document}

\section*{REPLY TO THE EDITOR}

Dear Editor,

\ \\
We would like to thank the Referee for careful reading, 
constructive criticism, and helpful recommendations. We 
revised the manuscript closely following the Referee's
suggestions in all points.

\ \\
Sincerely,

\ \\
Prokudin's Eleven \\

\section*{REPLY TO THE REFEREE}

We would like to thank the Referee for careful reading, 
constructive criticism, and the many helpful recommendations. 
We revised the manuscript closely following the Referee's
suggestions  as detailed out in the attached ``Summary of Changes.''
Below we respond to several specific points in the report.

\begin{itemize}

\item	We agree that the $Q^2$ evolution is an important 
	limiting factor, and added a brief comment in the
	Introduction as well as a more detailed paragraph
	in Sec.~3.8.

\item	The preliminary COMPASS data shown in Fig.~12 and
	several subsequent figures have been released and
	can be shown in our work under the condition that
	we show these Figures exactly as provided to us
	by the COMPASS Collaboration. This means that at
	this point we are not allowed to include the 
	results of our calculations in these plots, and
	must show them separately. These data will 
	presumably be unconditionally released at some later 
	time in the summer of this year. We added explanatory
	remarks in Fig.~12 and other figures where this applies.
	On the one hand, this makes the presentation of the
	results and the formatting of the figures cumbersome
	in many cases. On the other hand, we are grateful
	to the COMPASS Collaboration for giving us this
	possibility to show their preliminary data.
	We are also grateful to the HERMES Collaboration
	for making their preliminary data available and
	allowing us to include our curves in those plots.
	We added a remark in the acknowledgments.

\item	We understand the concerns of the Referee regarding the 
	subpercent results shown e.g.\ in Fig.~15. We had similar
	concerns but decided to show these results, even though
	subpercent asymmetries are not realistic predictions for 
	COMPASS. But the smallness of the effect shown in Fig.~15 is 
	not only due to the (in our approximation) small involved 
	TMDs but also due to the kinematical suppression in the
	COMPASS kinematics. The figure still gives insights e.g.\ 
	on the relative flavor dependence for the production of 
	positive vs negative pions in the WW-type approximation.

\item	Finally, we followed the recommendations of the Referee
	and removed App.~C on the mathematica package, unified 
	the notation for the masses of produced hadrons $m_h$, 
	specified the Mellin moments before Eq.~(3.8), fixed 
	the literal repetition on pages 16/17, improved
	non-optimal wording and fixed typos. It is inexplicable
	how some of these things could have escaped our attention 
	during proof-reading, and we are grateful for these corrections.

\end{itemize}

\section*{SUMMARY OF CHANGES}

\begin{itemize}

\item
Sec.1, page 3, the following paragraph and the new references
\cite{Ali:1991em,Koike:1994st,Balitsky:1996uh,Belitsky:1997zw} are added:

"The WW-type approximation is not preserved under $Q^2$ evolution.
 Some intuition can be obtained from the collinear case
 \cite{Ali:1991em,Koike:1994st,Balitsky:1996uh,Belitsky:1997zw}. 
 However, much less is known about the $k_\perp$-evolution especially at 
 subleading twist. More theoretical work is required here."

\item
Sec.1, page 3, we replaced:

"study of all SIDIS structure functions up to twist-3 in a unique approach."
$\to$\\
"study of all SIDIS structure functions up to twist-3 evaluated within one
common systematic theoretical guideline."

\item
Sec.1, page 3, we replaced the paragraph:

	In App.~C we describe an open-source package implemented
	in \texttt{Mathematica}~\cite{Mathematica} (already available)
	and \texttt{Python} (to be released in the near future) that is
	made publicly available on \texttt{github.com}: {\href{
	https://github.com/prokudin/WW-SIDIS}{
	https://github.com/prokudin/WW-SIDIS}}

by:

	An open-source package is available which allows one to visualize 
	and reproduce the results presented in this work, and may easily 
	be adapted by interested colleagues for their purposes
	\cite{Mathematica}.

and we removed App.~C.

\item
Sec.~3.3, page 14: The sentence before Eq.~(3.8) is modified as:

	For the $n = 3$ Mellin moments (i.e.\ the lowest non-trivial ones 
	for these tilde-functions) it was found $\dots$

\item
Sec.~3.5, page 17: The first instance of the repetitive sentence 
starting with ``This assumption holds $\dots$'' is removed.

\item
Sec.~3.8, page 20: The paragraph is added:

As it was mentioned in the Introduction one important limitation concerns 
the fact that the WW-type approximations are not preserved under $Q^2$ 
evolution. Still some intuition can be 
obtained from the collinear case: the evolution equations for $g_T^a(x)$ 
and $h_L^a(x)$ exhibit complicated mixing patterns typical for higher 
twist functions which simplify to DGLAP-type evolutions in the limit 
of a large number of colors $N_c$ and in the limit of large-$x$ 
\cite{Ali:1991em,Koike:1994st,Balitsky:1996uh,Belitsky:1997zw}. 
These evolution equations differ from those of the leading-twist
functions $g_1^a(x)$ and and $h_1^a(x)$. This point is of not much
practical relevance here, because the $Q^2$ varies only moderately
between JLab, HERMES, and COMPASS (except for the largest $x$-bins).
However, if for some reason the $\bar{q}gq$-terms were found to be
very small at one renormalization scale, it is not guaranteed the
WW-type approximation will work equally well also at other scales. 
 More theoretical work is required, especially also in order to 
understand $k_\perp$-evolution effects at subleading twist.

\item 
Caption of Fig.7, page 31, is modified as follows:

"(where $(-1)A_{UT}^{\sin(\phi_h+\phi_S)}$ is shown since COMPASS
 uses an opposite sign in its Collins asymmetry convention)."

\item
Sec.~5.6, page 32 (our correction): we added $\langle\dots\rangle$
in the following in-line formula  
$A_{UT, \langle y \rangle}^{\sin(3 \phi_h - \phi_S)}=\langle
(1-y)F_{UT}^{\sin(3 \phi_h - \phi_S)}\rangle/\langle(1-y + y^2/2)F_{UU}\rangle$
to indicate that the kinematic variable $y$ is averaged over.

\item
Captions of Figs.~9, 11, 12, 14, 15, 16, 19:
we added explanations why our curves cannot be added
on the plots provided by the COMPASS Collaboration.

\item
Fig.~18 (our correction):
the previous Fig.~18c was showing an estimate of the asymmetry
from an earlier (less consistent and superseded) way of using
the Gaussian model and applying the WW-type approximation, and 
we removed this plot. In the presently adopted scheme this
asymmetry vanishes as described in the caption of Fig.~18
and in Sec.~7.6.

\item
Sec.~5.6, page 33, the text is removed:

 "A notable exception is COMPASS, where the largest $x$--bins
 (where $Q^2$ is largest) bear the best hints on this TMD,
 see Fig.~9."

\item
Conclusions, page 47, the text is removed:

 "The classic WW approximation for $g_2(x)$ works with a relative
 accuracy of $\pm\,40\,\%$ or better. This is remarkable."

 The following phrase is modified:

 "on the positive site we also observe no alarming hints" $\to$\\
 "on the positive side we also observe no hints"

\item 
The misprints are fixed, the consistent notation $m_h$ is used,
and several figures are rearranged and placed more accurately 
within the sections where they are discussed. We did minor
editing in several places (purely stylistic improvements).

\item   Acknowledgments, we added the remark:

We thank the COMPASS and HERMES Collaborations for the 
permissions to show their preliminary data on several figures.

\item	{\bf Harut:} Do we show something preliminary from JLab?\\
	If so, we should acknowledge JLab too!  ;-)

\item	{\bf Alexei:} please eloborate on Ref.~\cite{Mathematica}
	as needed.

\end{itemize}

% REMARK: 
%
% "When submitting the document source (.tex) file to external parties, 
% it is strongly recommended that the BIBTEX .bbl file be manually copied 
% into the document (within the traditional LATEX bibliography environment) 
% so as not to depend on external files to generate the bibliography and to
% prevent the possibility of changes occurring therein"
%
% This means: 
% STEP 1: compile with \bibliography{biblio_ww} as usual, 
% STEP 2: uncomment \bibliography{biblio_ww}
% STEP 3: paste the contents of the file reply-to-referee-v2C.bbl
%
%
% STEP 1: done
%
% STEP 2: uncommenting
% \bibliography{biblio_ww}
%
% STEP 3: pasting (yeah, it works ;-)
%

\providecommand{\href}[2]{#2}\begingroup\raggedright\begin{thebibliography}{1}

\bibitem{Ali:1991em}
A.~Ali, V.~M. Braun and G.~Hiller, \emph{{Asymptotic solutions of the evolution
  equation for the polarized nucleon structure function $g_2 (x, Q^2)$}},
  \href{http://dx.doi.org/10.1016/0370-2693(91)90753-D}{\emph{Phys. Lett.} {\bf
  B266} (1991) 117--125}.

\bibitem{Koike:1994st}
Y.~Koike and K.~Tanaka, \emph{{$Q^2 $evolution of nucleon's chiral odd
  twist-three structure function: $h_L (x, Q^2)$}},
  \href{http://dx.doi.org/10.1103/PhysRevD.51.6125}{\emph{Phys. Rev.} {\bf D51}
  (1995) 6125--6138}, [\href{https://arxiv.org/abs/hep-ph/9412310}{{\tt
  hep-ph/9412310}}].

\bibitem{Balitsky:1996uh}
I.~I. Balitsky, V.~M. Braun, Y.~Koike and K.~Tanaka, \emph{{$Q^2$ evolution of
  chiral odd twist-three distributions $h_L(x,Q^2)$ and $e(x,Q^2)$ in the large
  $N_c$ limit}},
  \href{http://dx.doi.org/10.1103/PhysRevLett.77.3078}{\emph{Phys. Rev. Lett.}
  {\bf 77} (1996) 3078--3081},
  [\href{https://arxiv.org/abs/hep-ph/9605439}{{\tt hep-ph/9605439}}].

\bibitem{Belitsky:1997zw}
A.~V. Belitsky and D.~{M\"u}ller, \emph{{Scale dependence of the chiral odd
  twist-three distributions $h_L(x)$ and $e(x)$}},
  \href{http://dx.doi.org/10.1016/S0550-3213(97)00432-X}{\emph{Nucl. Phys.}
  {\bf B503} (1997) 279--308},
  [\href{https://arxiv.org/abs/hep-ph/9702354}{{\tt hep-ph/9702354}}].

\bibitem{Mathematica}
A.~Prokudin and K.~Tezgin, ``{Open-source packages with implementations of
  SIDIS structure functions in the WW-type approximation are publicly available
  on \texttt{github.com}: \\ in \texttt{Mathematica, {V}ersion 11.3} on {\href{
  https://github.com/prokudin/WW-SIDIS}{
  https://github.com/prokudin/WW-SIDIS}},\\ in \texttt{Python} on {\href{
  https://jeffersonlab.github.io/jam3d/_build/html/index.html}{
  https://jeffersonlab.github.io/jam3d/\_build/html/index.html}}}.''

\end{thebibliography}\endgroup

\end{document}

### 2019-03-13 arxiv2/test-WW-type-v2E.tex
AP

--- 2019-01-14 arxiv1/test-WW-type.tex
@@
 \newcommand{\di}{ {\rm d} }
+\newcommand{\mh}{ m_h }
 \newcommand{\with}[3]{{\Biggl|{\renewcommand*{\arraystretch}{0.8}
@@
 
-\newcommand{\AP}[1]{\red{#1}}
-%\newcommand{\ak}[1]{\orange{#1}}
+%\newcommand{\AP}[1]{\red{#1}}
+\newcommand{\ak}[1]{\orange{#1}}
+\newcommand{\Bernie}[1]{{\color[rgb]{0,0.5,0.75}#1}}
 \newcommand{\ps}[1]{\blue{#1}}
-%\newcommand{\gs}[1]{{\color[rgb]{0.65,0,0.65}#1}}
+\newcommand{\gs}[1]{{\color[rgb]{0.65,0,0.65}#1}}
 %\newcommand{\bp}[1]{{\color[rgb]{0,0.65,0.35}#1}}
@@
 
-\title{	Semi-Inclusive Deep-Inelastic Scattering
+\title{	Semi-inclusive deep-inelastic scattering
 	in Wandzura--Wilczek-type approximation}
@@
 
-The present work is the first study of all SIDIS structure functions up to
-twist-3 in a unique approach. Our results are of importance for measurements
+\ps{The WW-type approximation is not preserved under $Q^2$ evolution.
+Some intuition can be obtained from the collinear case. However,
+much less is known about the $k_\perp$-evolution especially at 
+subleading twist. More theoretical work is required here.}
+
+The present work is the first 
+% study of all SIDIS structure functions up to twist-3 in a unique approach. 
+\ps{study of all SIDIS structure functions up to twist-3 evaluated within one
+common systematic theoretical guideline.}
+Our results are of importance for measurements
 performed or in preparation at COMPASS, HERMES, and JLab with
@@
 technical details.
-	In App.~C we describe an open-source package implemented
-	in \texttt{Mathematica}~\cite{Mathematica} (already available)
-	and \texttt{Python} (to be released in the near future) that is
-	made publicly available on \texttt{github.com}: {\href{
-	https://github.com/prokudin/WW-SIDIS}{
-	https://github.com/prokudin/WW-SIDIS}}
+\ps{	An open-source package is available which allows one to visualize 
+	and reproduce the results presented in this work, and may easily 
+	be adapted by \ak{interested colleagues for their purposes}
+	\cite{Mathematica}.
+}
 
@@
 	\frac{1}{2}{\rm Tr}\big[i\sigma^{j-}\gamma_5\Delta(z,\bfpperp)\big]
-	&=& \epsilon^{jk}\,\frac{\pperp^k}{zm_h}\red{H_1^\perp}\;,
+	&=& \epsilon^{jk}\,\frac{\pperp^k}{z\mh}\red{H_1^\perp}\;,
 	\label{eq:DeltaTr-twist-2b}
@@
     \frac12\;{\rm Tr}\biggl[\,1\;\Delta(z,\bfpperp)\biggr]         &=&
-    \phantom{-}\frac{M_h}{P^-_h}\;\blue{E}\;,  \label{eq:DeltaTr-twist-3a}\\
+    \phantom{-}\frac{\mh}{P^-_h}\;\blue{E}\;,  \label{eq:DeltaTr-twist-3a}\\
     \frac12\;{\rm Tr}\biggl[\;\,\gamma^j\;\Delta(z,\bfpperp)\biggr]  &=&
@@
 	\biggr] &=&
-    -\varepsilon^{jk}\,\frac{M_h}{P_h^-}\;\red{H}\;.  \label{eq:DeltaTr-twist-3d}
+    -\varepsilon^{jk}\,\frac{\mh}{P_h^-}\;\red{H}\;.  \label{eq:DeltaTr-twist-3d}
 \ea\end{subequations}
@@
 \ea\end{subequations}
-where $r_h = m_h/M_N$ and
+where $r_h = \mh/M_N$ and
 $F_{XY}^{\rm weight}\equiv F_{XY}^{\rm weight}(x,z,\Phperp)$. The
@@
 && \omega^{\{0\}}  	= 1 \, , \nonumber\\
-&& \omega^{\{1\}}_{\rm A} 	= \frac{\bfhp\cdot\bfpperp^{ }}{z m_h}  \, , \;\;\;
+&& \omega^{\{1\}}_{\rm A} 	= \frac{\bfhp\cdot\bfpperp^{ }}{z \mh}  \, , \;\;\;
    \omega^{\{1\}}_{\rm B} 	= \frac{\bfhp\cdot\bfkperp^{ }}{M_N}\,,\nonumber\\
 && \omega^{\{2\}}_{\rm A} 	=  \frac{2\, \bigl(\bfhp\cdot\bfpperp^{ }\bigr)\,
-			\bigl(\bfhp\cdot\bfkperp^{ }\bigr)}{zM_Nm_h}\,,\;\;\;
-   \omega^{\{2\}}_{\rm B}	= -\frac{\bfpperp^{ }\cdot\bfkperp^{ }}{zM_Nm_h}\,,\;\;\;
+			\bigl(\bfhp\cdot\bfkperp^{ }\bigr)}{zM_N\mh}\,,\;\;\;
+   \omega^{\{2\}}_{\rm B}	= -\frac{\bfpperp^{ }\cdot\bfkperp^{ }}{zM_N\mh}\,,\;\;\;
    \omega^{\{2\}}_{\rm C}	= \frac{2\,(\bfhp\cdot\bfkperp^{ })^2-\bfkperp^2}{2M_N^2}
@@
    			-\bigl(\bfhp\cdot\bfpperp^{ }\bigr)\,\bfkperp^2\
-   			}{2 z M_N^2 m_h}\,,
+   			}{2 z M_N^2 \mh}\,,
 			\label{Eq:wi} \ea
@@
 	\label{Eq:FLT-collinear}\\
-	 F_{UT}^{\sin\phi_S}(x,z) &=& -\,\frac{2\,m_h}{Q}\; x\sum_a e_a^2\,
+	 F_{UT}^{\sin\phi_S}(x,z) &=& -\,\frac{2\,\mh}{Q}\; x\sum_a e_a^2\,
 	h_1^a(x)\frac{\tilde{H}^a(z)}{z} \, .
@@
 techniques \cite{Wandzura:1977qf,Jaffe:1991ra}. Notice that the
-operators defining $g_T^a$ and and $h_L^a$ can also be decomposed
+operators defining $g_T^a$ and $h_L^a$ can also be decomposed
 within the TMD framework by means of a combination of relations
@@
 	and analog for other scalar products of {\it transverse} vectors.
-	Notice that in our notation transverse vectors
+	In our notation transverse vectors
 	are never understood as four-vectors such that
@@
 The resulting relations are the only WW-type relations applicable
-to twist-2 TMDs and are given by the following expressions
+to twist-2 TMDs and are given by % the following expressions
 \cite{Tangerman:1994bb,Mulders:1995dh,Avakian:2007mv}:
@@
 	H(z,\pperp^2) &\WWtype&
-	-\frac{\pperp^2}{zM_h^2}\;H_1^\perp(z,\pperp^2)\,. \label{Eq:WW-type-FF-4}
+	-\frac{\pperp^2}{z\mh^2}\;H_1^\perp(z,\pperp^2)\,. \label{Eq:WW-type-FF-4}
 \ea\end{subequations}
@@
 respective twist-2 parts, which are of order $(\rho/R)^0$.
-For Mellin moments it was found that~\cite{Balla:1997hf,Dressler:1999hc}
+\gs{For the $n = 3$ Mellin moments (i.e.\ the lowest non-trivial ones for 
+these tilde-functions) it was found} \cite{Balla:1997hf,Dressler:1999hc}
 \be\label{Eq:WW-instanoton}
@@
 with an accuracy of about $40\,\%$ or better \cite{Accardi:2009au}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
+\centering
+\includegraphics[width=0.45\textwidth]{\FigPath/g2.pdf}
+\includegraphics[width=0.45\textwidth]{\FigPath/g2-HERMES.pdf}
+\caption{\label{Fig:g2}
+Left panel: The structure function $xg_2(x)$ in WW-approximation at $Q^2=7.1\,{\rm GeV}^2$,
+Eq.~(\ref{Eq:g2-in-WW-approximation}), for proton (P) and neutron (N) targets,
+and data from the SLAC E144 and E155 experiments at
+$\la Q^2\ra=7.1\,{\rm GeV}^2$ \cite{Anthony:2002hy,Abe:1998wq}.
+Right panel: HERMES data for $Q^2>1\,{\rm GeV}^2$ with
+$\la Q^2\ra=2.4\,{\rm GeV}^2$ \cite{Airapetian:2011wu}.
+The estimate of the theoretical uncertainty is described in the text.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/g2.pdf}
-\includegraphics[width=0.45\textwidth]{\FigPath/g2-HERMES.pdf}
-\caption{\label{Fig:g2}
-Left panel: The structure function $xg_2(x)$ in WW-approximation at $Q^2=7.1\,{\rm GeV}^2$,
-Eq.~(\ref{Eq:g2-in-WW-approximation}), for proton (P) and neutron (N) targets,
-and data from the SLAC E144 and E155 experiments at
-$\la Q^2\ra=7.1\,{\rm GeV}^2$ \cite{Anthony:2002hy,Abe:1998wq}.
-Right panel: HERMES data for $Q^2>1\,{\rm GeV}^2$ with
-$\la Q^2\ra=2.4\,{\rm GeV}^2$ \cite{Airapetian:2011wu}.
-The estimate of the theoretical uncertainty is described in the text.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 Presently $h_L^a(x)$ is unknown.
@@
 \cite{Hagler:2009mb,Musch:2010ka}, recent years have witnessed considerable
-progress and improvements with regard to rigor, realism and methodology
-\cite{Yoon:2017qzo, %PhysRevD.96.094508
-Engelhardt:2015xja,%Phys.Rev. D93 (2016) no.5, 054501,
-Ji:2014hxa,%Phys.Rev. D91 (2015) 074009,
-Musch:2011er%Phys.Rev. D85 (2012) 094510
-}.
-However, numerical results from recent calculations are only available
-for a subset of observables, and the quantities calculated are not in a
-form that lends itself to straightforward tests of the WW-type relations
-as presented in this paper.
-   {This assumption holds if renormalization is multiplicative and
-   flavor-independent for the non-local lattice operators. This is
-   not true for all lattice actions \cite{Musch:2010ka}. % PS: [66]? CHECK!!
-   But presumably it is true
-   if the lattice action preserves chiral symmetry, as it does in
-   the present case. For the latest developments we refer the
+progress and improvements with regard to rigor, realism and methodology.
+\Bernie{For the latest developments we refer the
 	interested reader to Refs.~\cite{Alexandrou:2017dzj,Ishikawa:2017faj,
@@
    Ji:2017oey,Yoon:2017qzo,Green:2017xeu,Zhang:2017bzy}.}
+However, numerical results from recent calculations are only available
+for a subset of observables, and the quantities calculated are not in a
+form that lends itself to straightforward tests of the WW-type relations
+as presented in this paper.
 
@@
 In Fourier space, the aforementioned divergent behavior for large $\bfkperp$
-translates into strong lattice scale and scheme dependences at short distances
+translates into strong lattice scale and scheme dependencies at short distances
 $\bflperp$ between the quark operators. The $\bfkperp$ integrals needed for
@@
 unpolarized TMD $f_1$ also fixes the normalization for polarized quantities
-correctly. This assumption holds if renormalization is multiplicative and
-flavor independent for the non-local lattice operators. This is not true
-for all lattice actions \cite{Yoon:2017qzo} %PhysRevD.96.094508
-but presumably it is true if the lattice action preserves chiral symmetry,
-as it does in the present case.
+correctly. 
+\Bernie{This assumption holds if renormalization is multiplicative and
+   flavor-independent for the non-local lattice operators. This is
+   not true for all lattice actions \cite{Yoon:2017qzo}. %PhysRevD.96.094508
+   % NOT \cite{Musch:2010ka}.
+   But presumably it is true
+   if the lattice action preserves chiral symmetry, as it does in
+   the present case.} 
 The Gaussian fits along with the normalization prescription serve as
@@
         \underbrace{-\,\frac{1}{3}\int \! d x\;x\,h_1^u(x)}
-        _{= -0.093(3) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
+        _{= -0.093(3) \;\mbox{\footnotesize Ref.~\cite{Gockeler:2005cj}}}
         \hspace{2mm} , \hspace{7mm} \nonumber \\
@@
         \underbrace{-\,\frac{1}{3}\int \! d x\;x\,h_1^d(x)}
-        _{= 0.018(1) \;\mbox{\footnotesize Ref.~\cite{Hagler:2007xi}}}
+        _{= 0.018(1) \;\mbox{\footnotesize Ref.~\cite{Gockeler:2005cj}}}
         \hspace{2mm},
@@
 
-The approximation may work in the case when the TMD or FF
+The approximation may work in the case when a TMD or FF
 $=\la\bar{q}q\ra + \la\bar{q}gq\ra \approx \la\bar{q}q\ra \neq 0$ with
@@
 even if the neglected matrix element  $\la\bar{q}gq\ra$ is very small.
-Notice that this type occurs for all subleading-twist FFs that enter
+Notice that this occurs for all subleading-twist FFs that enter
 SIDIS structure functions only in the shape of tilde-FFs, see
@@
 correlator (\ref{Eq:correlator}) with no prefactor of $\kperp$.
-There are three cases: $f_T^a(x,k_\perp)$, $h^a(x,\kperp)$, and $e_L^a(x,\kperp)$.
+There are three cases: $f_T^a(x,k_\perp^{2})$, $h^a(x,\kperp^{2})$, and $e_L^a(x,\kperp^{2})$.
 Such TMDs in principle survive integration of the correlator over $\kperp$
@@
 
-Let us first discuss the case of $f_T^a(x,k_\perp)$. Taking the
+Let us first discuss the case of $f_T^a(x,k_\perp^{2})$. Taking the
 WW-type approximation (\ref{Eq:WW-type-fT}) literally means
-$x\int d^2 k_\perp\,f_T^a(x,k_\perp)\,\stackrel{!?}{=}
+$x\int d^2 k_\perp\,f_T^a(x,k_\perp^{2})\,\stackrel{!?}{=}
 -f_{1T}^{\perp(1)a}(x)\neq0$,
 at variance with the sum rule (\ref{Eq:sum-rules-T-odd}). We
-have $xf_T^a(x,k_\perp)=x\tilde{f}_T^a(x,k_\perp)-f_{1T}^{\perp(1)a}(x,k_\perp)$
+have $xf_T^a(x,k_\perp)=x\tilde{f}_T^a(x,k_\perp^{2})-f_{1T}^{\perp(1)a}(x,k_\perp^{2})$
 from QCD equations of motion \cite{Bacchetta:2006tn}, which yields
@@
 The situation for the chirally and T-odd twist-3
-TMD $h^a(x,k_\perp)$ is analogous. The third
+TMD $h^a(x,k_\perp^{2})$ is analogous. The third
 function in (\ref{Eq:sum-rules-T-odd}) causes no issues since
-$e_L^a(x,k_\perp)=\tilde{e}_L^a(x,k_\perp)\approx0$ in WW-type approximation.
-
-Does it mean WW-type approximations fail for $f_T^a(x,k_\perp)$
-and $h^a(x,k_\perp)$? Not necessarily! The approximations may
+$e_L^a(x,k_\perp^{2})=\tilde{e}_L^a(x,k_\perp^{2})\approx0$ in WW-type approximation.
+
+Does it mean WW-type approximations fail for $f_T^a(x,k_\perp^{2})$
+and $h^a(x,k_\perp^{2})$? Not necessarily! The approximations may
 work in some but not all regions of $\kperp$, but the sum rules
@@
 (\ref{Eq:sum-rules-T-odd}) do not need to exclude the
-possibility that the WW-type approximations for $f_T^a(x,k_\perp)$ and
-$h^a(x,k_\perp)$ in (\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-last})
+possibility that the WW-type approximations for $f_T^a(x,k_\perp^{2})$ and
+$h^a(x,k_\perp^{2})$ in (\ref{Eq:WW-type-fT},~\ref{Eq:WW-type-last})
 may work at small $k_\perp$ where we use them in our TMD approach.
@@
 in tilde-terms.
-
 Presently too little is known in the theory of subleading-twist TMDs.
-Below in Sec.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi} we
-will present a pragmatic solution for how to deal with the TMDs
-$f_T^a(x,k_\perp)$ and $h^a(x,k_\perp)$ phenomenologically.
+In Secs.~\ref{Sec-7.6:FUTsinphiS} and \ref{Sec-7.7:FUUcosphi} we
+will present pragmatic solutions for how to deal with the TMDs
+$f_T^a(x,k_\perp^{2})$ and $h^a(x,k_\perp)$ phenomenologically.
 For now let us keep in mind that
 one has to keep a vigilant eye on all WW-type approximations, and
-especially on those for $f_T^a(x,k_\perp)$ and $h^a(x,k_\perp)$.
+especially on those for $f_T^a(x,k_\perp^{2})$ and $h^a(x,k_\perp^{2})$.
+
+\ak{As it was mentioned in the Introduction}
+\ps{one important limitation concerns the fact that the WW-type approximations
+are not preserved under $Q^2$ evolution. \ak{Still} some intuition can be 
+obtained from the collinear case: the evolution equations for $g_T^a(x)$ 
+and $h_L^a(x)$ exhibit complicated mixing patterns typical for higher 
+twist functions, which simplify to DGLAP-type evolutions in the limit 
+of a large number of colors $N_c$ and in the limit of large-$x$ 
+\cite{Ali:1991em,Koike:1994st,Balitsky:1996uh,Belitsky:1997zw}. 
+These evolution equations differ from those of the leading-twist
+functions $g_1^a(x)$ and $h_1^a(x)$. This point is of not much
+practical relevance here, because the $Q^2$ varies only moderately
+between JLab, HERMES, and COMPASS (except for the largest $x$-bins).
+However, if for some reason the $\bar{q}gq$-terms were found to be
+very small at one renormalization scale, it is not guaranteed the
+WW-type approximation will work equally well also at other scales. 
+ More theoretical work is required, especially also in order to 
+understand $k_\perp$-evolution effects at subleading twist.}
 
@@
 	H_{1}^{\perp}(z,\pperp^2) &=&  H_{1}^{\perp (1)}(z) \;
-	\frac{2 z^2 m_h^2}{\pi \avpperp_{H_{1}^\perp}^2} \;
+	\frac{2 z^2 \mh^2}{\pi \avpperp_{H_{1}^\perp}^2} \;
 	e^{-\pperp^2/{\avpperp_{H_{1}^\perp}}}\, ,\\
@@
 where $\lambda=z^2 \avkperp_{h_1} + \avpperp_{H_1^\perp}$ and
-$b^{(1)}_{\rm A}=2m_h$ and $c^{(1)}_{\rm A} = \sqrt{\pi}\,m_h$,
+$b^{(1)}_{\rm A}=2\mh$ and $c^{(1)}_{\rm A} = \sqrt{\pi}\,\mh$,
 see App.~\ref{App:convol-details} for details.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
+\begin{figure}[t!]
 \centering
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_x.pdf}
+{\tiny(a)}
 \includegraphics[width=0.45\textwidth]{\FigPath/AUTCollins_COMPASS_x.pdf}
+{\tiny(b)}
 \caption{\label{aut_h1_jlab}  Collins asymmetry
-	$A_{UT,  \langle y\rangle}^{\sin(\phi_h+\phi_S)}$ for a proton target as function of $ x $
+	$A_{UT,  \langle y\rangle}^{\sin(\phi_h+\phi_S)}$ for a proton target 
+	as function of $ x $
 	based on the fit \cite{Anselmino:2013vqa} in comparison to
-	(left panel) HERMES \cite{Airapetian:2010ds} and
-	(right panel) COMPASS data \cite{Adolph:2014zba} (where
-	$(-1)A_{UT}^{\sin(\phi_h+\phi_S)}$ is shown since for historical
-	reasons the COMPASS collaboration likes to analyze their data
-	with an opposite sign convention.)}
+	\ps{(a)} HERMES \cite{Airapetian:2010ds} and
+	\ps{(b)} COMPASS \cite{Adolph:2014zba} data [where
+	$(-1)A_{UT}^{\sin(\phi_h+\phi_S)}$ is shown since COMPASS 
+	\gs{uses an opposite sign in its Collins asymmetry convention}].}
 \end{figure}
@@
 The structure function $F_{UU}^{\cos(2\phi_h)}$ arises from a convolution of
-the Collins fragmention function and the Boer-Mulders TMD $h_{1}^{\perp }$,
+the Collins fragmention function and the Boer--Mulders TMD $h_{1}^{\perp }$,
 which describes
@@
 where $\lambda=z^2 \avkperp_{h_1^\perp} + \avpperp_{H_1^\perp}$ and
-$b^{(2)}_{\rm AB}=4M_Nm_h$ and $c^{(2)}_{\rm AB} = 4M_Nm_h$,
+$b^{(2)}_{\rm AB}=4M_N\mh$ and $c^{(2)}_{\rm AB} = 4M_N\mh$,
 see App.~\ref{App:convol-details}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
+\begin{figure}[t!]
 \centering
@@
 \caption{\label{auu_cos2phi_jlab} The asymmetry
-	$A_{UU, \langle y\rangle}^{\cos(2\phi_h)}$ for a proton target as function of $ x $
-	based on the fit \cite{Barone:2009hw} in comparison to
+	$A_{UU, \langle y\rangle}^{\cos(2\phi_h)}$ for a proton target as function 
+	of $ x $ based on the fit \cite{Barone:2009hw} in comparison to
 	(left panel) HERMES \cite{Airapetian:2012yg} and $A_{UU}^{\cos(2\phi_h)}$
@@
 where $\lambda=z^2 \avkperp_{h_{1T}^\perp} + \avpperp_{H_1^\perp}$ and
-$b^{(3)}=2M_N^2m_h$ and $c^{(3)}_{\rm  } = 3/2\sqrt{\pi} \,M_N^2m_h$,
+$b^{(3)}=2M_N^2\mh$ and $c^{(3)}_{\rm  } = 3/2\sqrt{\pi} \,M_N^2\mh$,
 see App.~\ref{App:convol-details}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
+\begin{figure}[t!]
 \centering
-\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf} {\tiny (a)}%
-\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf} {\tiny (b)}%
-\includegraphics[height=3.2cm]{\FigPath/AUTPretzelosity_x.pdf}{\tiny (c)}%
-
-\includegraphics[height=3.3cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}{\tiny (d)}%
+\begin{tabular}{cc}
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_pretzelosity_pip.pdf}{\tiny(a)}&
+\includegraphics[height=3.4cm]{\FigPath/AUTPretzelosity_HERMES_x.pdf}{\tiny(c)}
+\\
+\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_pretzelosity_pim.pdf}{\tiny(b)}&
+\includegraphics[height=3.4cm]{\FigPath/AUTPretzelosity_x.pdf}{\tiny(d)}
+\end{tabular}
 \caption{\label{aut_h1tp_jlab} $A_{UT}^{\sin(3 \phi_h - \phi_S)}$
-	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2013fia} (a,b)
-	and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES
-	\cite{Schnell:2010zza}(d) in comparison to the best fit from \cite{Lefky:2014eia}
-	(whose 1-$\sigma$ uncertainty band is compatible with zero), and our calculation for COMPASS kinematics (c). For comparison the COMPASS plots
-	show the model results \cite{Kotzinian:2008fe,Boffi:2009sh}.
-	}
+	as a function of $x$ from preliminary COMPASS \cite{Parsamyan:2013fia} 
+	(a,b) and $A_{UT,\langle y\rangle}^{\sin(3 \phi_h - \phi_S)}$ for HERMES
+	\cite{Schnell:2010zza} (c) in comparison to the best fit from 
+	\cite{Lefky:2014eia}
+	(whose 1-$\sigma$ uncertainty band is compatible with zero), and 
+	our calculation for COMPASS kinematics (d). For comparison the 
+	COMPASS plots show the model results 
+	\cite{Kotzinian:2008fe,Boffi:2009sh}.
+        \ps{[We remark that in this and several subsequent figures we have 
+        the permission to show the preliminary data \cite{Parsamyan:2013fia} 
+	%only in the figures exactly as provided by COMPASS collaboration in 
+	\gs{only in the official figures provided by the COMPASS collaboration}
+ 	in (a,b), and have to display our results separately in (d).]}}
 \end{figure}
@@
 
-The preliminary COMPASS data \cite{Parsamyan:2013fia} for $A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ and the preliminary HERMES data \cite{Schnell:2010zza} for
-$A_{UT, \langle y \rangle}^{\sin(3 \phi_h - \phi_S)}=(1-y)F_{UT}^{\sin(3 \phi_h - \phi_S)}/((1-y + y^2/2)F_{UU})$
+Preliminary COMPASS data \cite{Parsamyan:2013fia} for 
+$A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ and 
+preliminary HERMES data \cite{Schnell:2010zza} for
+$A_{UT, \langle y \rangle}^{\sin(3 \phi_h - \phi_S)}=\ps{\la
+(1-y)F_{UT}^{\sin(3 \phi_h - \phi_S)}\ra/\la(1-y + y^2/2)F_{UU}\ra}$
 are plotted in Fig.~\ref{aut_h1tp_jlab}. 
@@
 values of $Q$ could be achieved in the fixed target experiments.
-A notable exception is COMPASS, where the largest $x$--bins
-(where $Q^2$ is largest) bear the best hints on this TMD,
-see Fig.~\ref{aut_h1tp_jlab}.
+% \ps{A notable exception is COMPASS, where the largest $x$--bins
+% (where $Q^2$ is largest) bear the best hints on this TMD,
+% see Fig.~\ref{aut_h1tp_jlab}.}
 Future high-luminosity data from JLab 12 are expected
@@
 For TMDs the situation is different. Already the transverse
-momentum descriptions of $f_1^a(x,\kperp)$ and $D_1^a(z,\pperp)$
+momentum descriptions of $f_1^a(x,\kperp^{2})$ and $D_1^a(z,\pperp^{2})$
 are associated with non-negligible statistical uncertainties,
@@
 
-\begin{figure}
+\begin{figure}[b!]
 \centering
@@
 \centering
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip} {\tiny (a)}
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim} {\tiny (b)}
-\includegraphics[width=0.37\textwidth]{\FigPath/ALT_COMPASS_x.pdf} {\tiny (c)}
+\begin{tabular}{ccc}\ \hspace{-8mm}
+\includegraphics[width=0.31\textwidth]{\FigPath/LT_Pr10_cosphihphis_pip}&
+\ \hspace{-3mm}
+\includegraphics[width=0.31\textwidth]{\FigPath/LT_Pr10_cosphihphis_pim}&
+\ \hspace{-3mm}
+\includegraphics[width=0.36\textwidth]{\FigPath/ALT_COMPASS_x.pdf} \\
+ {\tiny (a)}&{\tiny (b)}&{\tiny (c)}
+\end{tabular}
 	\caption{\label{cosphihphis}
 	Leading-twist $A_{LT}^{\cos(\phi_h-\phi_S)}$:
-	 preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b); and our calculation for COMPASS kinematics (c).
-	}
+	preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b); 
+	and our calculation for COMPASS kinematics (c)
+	\ps{shown separately for reasons explained in 
+	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.}}
 \end{figure}
@@
 where $\lambda= z^2 \avkperp_{h_{1L}^\perp} + \avpperp_{H_1^\perp}$ and
-$b^{(2)}_{\rm AB}=c^{(2)}_{\rm AB}=4M_Nm_h$,
+$b^{(2)}_{\rm AB}=c^{(2)}_{\rm AB}=4M_N\mh$,
 see App.~\ref{App:convol-details} for details.
@@
 \begin{figure}
-\centering
-\includegraphics[height=4cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} {\tiny (a)}\\
-\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_JLAB_x.pdf} {\tiny (b)}
-\includegraphics[height=3.5cm]{\FigPath/AULsin2phi_COMPASS_x} {\tiny (c)}
+\centering \ \hspace{-6mm}
+\includegraphics[height=5.5cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \\
+
+\vspace{-0.5cm}
+
+\ \hspace{1cm} {\tiny (a)} \hspace{6cm} {\tiny (b)}
+
+\vspace{1cm}
+
+\includegraphics[height=4cm]{\FigPath/AULsin2phi_JLAB_x.pdf} \
+\includegraphics[height=4cm]{\FigPath/AULsin2phi_COMPASS_x} \\
+\ \hspace{1cm} {\tiny (c)} \hspace{6cm} {\tiny (d)}
 	\caption{\label{aul_jlab}
@@
 	HERMES \cite{Airapetian:1999tv} and 
-	COMPASS \cite{Parsamyan:2018ovx,Parsamyan:2018evv} (a),
+	COMPASS \cite{Parsamyan:2018ovx,Parsamyan:2018evv} (a, b),
 	$A_{UL,  \langle y\rangle}^{\sin(2\phi_h)}$ from
-	JLab \cite{Jawalkar:2017ube} (b),  and from our calculation for COMPASS kinematics in the WW-type
-	approximation (c). Results
-	from \cite{Avakian:2007mv} are also shown in comparison to the COMPASS data.}
+	JLab \cite{Jawalkar:2017ube} (c),  and from our calculation 
+	for COMPASS kinematics in the WW-type approximation (d)
+	\ps{shown separately for reasons explained in the
+	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.} Results
+	from \cite{Avakian:2007mv} are also shown in comparison to the 
+	COMPASS data.}
 \end{figure}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+\begin{figure}[b!]
 \centering
@@
 
-WW-type approximations can be applied to all eight subleading-twist asymmetries,
+WW-type approximations can be applied to all eight twist-3 asymmetries,
 see Sec.~\ref{Sec-4.2:WW-twist-3}. In this section we discuss all of them,
@@
 Eq.~(\ref{FLUsinphi}), containing four terms:
-two terms are proportional to the pure twist-3 fragmentation functions
-$\tilde{G}^{\perp a}$ and $\tilde{E}^a$ and neglected here; the other two
+two are proportional to the pure twist-3 fragmentation functions
+$\tilde{G}^{\perp a}$ and $\tilde{E}^a$; % and neglected here; 
+the other two
 terms are proportional to the twist-3 TMDs $e^a$ and $g^{\perp a}$, which
@@
 each single $\bar{q}gq$--term is small. Fourth, some asymmetries
-predicted to be non-zero in WW-approximation are not much larger and
+predicted to be non-zero in WW-approximation are not larger and
 in some cases even smaller than the result in (\ref{Eq:ALU-small}).
@@
 In the WW-type approximation the structure function
-$F_{LT}^{\cos\phi_S}$ arises from $g_T^a(x,\kperp)$ and $D_1^a(z,\pperp)$,
+$F_{LT}^{\cos\phi_S}$ arises from $g_T^a(x,\kperp^{2})$ and $D_1^a(z,\pperp^{2})$,
 whose collinear counterparts are more or less known, see
 Secs.~\ref{Sec-3.4:WW-classic-experiment} and \ref{Sec-5.1:FUU-basis}.
-We assume the Gaussian Ansatz for $g_T^a(x,\kperp)$, shown in
+We assume the Gaussian Ansatz for $g_T^a(x,\kperp^{2})$, shown in
 (\ref{eq:gtnew}) of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs},
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[htb!]
+\begin{figure}[b!]
 \centering
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pip.pdf} {\tiny (a)}
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cosphis_pim.pdf} {\tiny (b)}
-\includegraphics[width=0.35\textwidth]{\FigPath/ALTcosPhi_COMPASS_x} {\tiny (c)}
+\begin{tabular}{ccc} \ \hspace{-8mm}
+\includegraphics[height=3.3cm]{\FigPath/LT_Pr10_cosphis_pip.pdf}&
+\includegraphics[height=3.3cm]{\FigPath/LT_Pr10_cosphis_pim.pdf}&
+\includegraphics[height=3.1cm]{\FigPath/ALTcosPhi_COMPASS_x}\\
+{\tiny(a)}& {\tiny(b)}& {\tiny(c)}
+\end{tabular}
 \caption{\label{altcosphis} Subleading-twist asymmetry $A_{LT}^{\cos\phi_S}$
@@
 	longitudinally polarized muons off a transversely polarized
-	proton target \cite{Parsamyan:2013fia} (a,b),  and our calculation for COMPASS kinematics (c).
-	}
+	proton target \cite{Parsamyan:2013fia} (a,b),  and our 
+	calculation for COMPASS kinematics (c) \ps{where a different 
+	scale is chosen to better visualize the theory curves.}}
 \end{figure}
@@
 yields (\ref{Eq:FLTcosphiS-Gauss-b}), which is the correct collinear
-result for this SIDIS function in (\ref{Eq:FLT-collinear})
+result for this SIDIS structure function in (\ref{Eq:FLT-collinear})
 in WW-type approximation. This technical remark confirms the
@@
 In the WW-type approximation this asymmetry is expressed in terms of
-$g_T^{\perp a}(x,\kperp)$, for which we assume a Gaussian Ansatz according to
+$g_T^{\perp a}(x,\kperp^{2})$, for which we assume a Gaussian Ansatz according to
 (\ref{eq:gtperpnew}) in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs},
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[b!]
+\centering
+\begin{tabular}{ccc} \ \hspace{-8mm}
+\includegraphics[width=0.30\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pip}&
+\includegraphics[width=0.30\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pim}&
+\includegraphics[width=0.36\textwidth]{\FigPath/ALTcos2PhiminusPhiS_COMPASS_x}\\
+{\tiny(a)}& {\tiny(b)}& {\tiny(c)}
+\end{tabular}
+\caption{\label{altcos2phihphis} $A_{LT}^{\cos(2\phi_h - \phi_S)}$
+	as a function of $ x $ from a proton target: 
+	preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b), 
+	and our calculation for COMPASS kinematics (c)
+	\ps{shown separately for reasons explained in the
+	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.} The smallness
+	of this asymmetry has two natural reasons: first, being twist-3
+	it is $M_N/Q$ suppressed; and second, it is proportional to
+	$P_{hT}^2$  in TMD approach.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Our predictions for the asymmetry
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pip} {\tiny (a)}
-\includegraphics[width=0.35\textwidth]{\FigPath/LT_Pr10_cos2phihphis_pim} {\tiny (b)}
-\includegraphics[width=0.35\textwidth]{\FigPath/ALTcos2PhiminusPhiS_COMPASS_x} {\tiny (c)}
-\caption{\label{altcos2phihphis} $A_{LT}^{\cos(2\phi_h - \phi_S)}$
-	as a function of $ x $ from a proton target: 
-	preliminary COMPASS data \cite{Parsamyan:2013fia} (a,b), and our calculation for COMPASS kinematics (c). The smallness
-	of this asymmetry has two natural reasons: first, being twist-3
-	it is $M_N/Q$ suppressed; and second, it is proportional to
-	$P_{hT}^2$  in TMD approach.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\newpage
-
 \subsection{\boldmath   Subleading-twist  $A_{LL}^{\cos\phi_h}$}
@@
 In WW-type approximation the only contribution to $F_{LL}^{\cos\phi_h}$
-is due to $g_{L}^{\perp q}(x,k_\perp)$, which we assume to have a
+is due to $g_{L}^{\perp q}(x,k_\perp^{2})$, which we assume to have a
 Gaussian $k_\perp$--behavior according to (\ref{eq:gLperp})
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+\begin{figure}[t!]
 \centering
-\vspace{5mm}
-\includegraphics[width=0.7\textwidth]{\FigPath/A_LL_Pr0711_Zgt02.pdf} {\tiny (a)}
-\includegraphics[width=0.35\textwidth]{\FigPath/ALLcosphi_COMPASS_x} {\tiny (b)}
+\begin{tabular}{cc} \ \hspace{-8mm}
+\includegraphics[width=0.6\textwidth]{\FigPath/A_LL_Pr0711_Zgt02.pdf}&
+\includegraphics[width=0.38\textwidth]{\FigPath/ALLcosphi_COMPASS_x}\\
+{\tiny (a) \hspace{3cm} (b)}&{\tiny (c)}
+\end{tabular}
 	\caption{\label{allcosphi_jlab} $A_{LL}^{\cos(\phi_h)}$
 	as a function of $ x $: preliminary COMPASS data
-	\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (a),  
-	our calculation for COMPASS kinematics using the WW-type approximation (b). }
+	\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (a,b),  
+	and our calculation for COMPASS kinematics in 
+	WW-type approximation (c)
+	\ps{shown separately for reasons explained in the
+	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.}}
 \end{figure}
@@
 
-%\newpage
+\
+
+\
+
 \subsection{\boldmath Subleading-twist $A_{UL}^{\sin\phi_h}$ }
@@
 In WW-type approximation $A_{UL}^{\sin\phi_h}$ is described by
-$h_L^q(x,\kperp)$, for which we assume the Gaussian Ansatz
+$h_L^q(x,\kperp^{2})$, for which we assume the Gaussian Ansatz
 (\ref{eq:hLnew}) in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}
@@
 where $\lambda=z^2 \avkperp_{h_L} + \avpperp_{H_1^\perp}$ and
-$b^{(1)}_{\rm A}=2m_h$ and $c^{(1)}_{\rm A} = \sqrt{\pi}\,m_h$,
+$b^{(1)}_{\rm A}=2\mh$ and $c^{(1)}_{\rm A} = \sqrt{\pi}\,\mh$,
 see App.~\ref{App:convol-details} for details.
@@
 \begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
-\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
+\centering \ 
+\includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
+\includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
 \includegraphics[width=0.8\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}
 \caption{\label{aulsinphi_jlab}
-	$A_{UL}^{\sin\phi_h}$ for proton target vs.~$x$ from WW-type
+	$A_{UL}^{\sin\phi_h}$ for proton vs.~$x$ from WW-type
 	approximation in comparison to data for the following hadrons.
@@
 The WW-type approximation seems not incompatible with data for negative
-pions and hadrons, but understimates the magnitude of the asymmetry for
+pions and hadrons, but underestimates the magnitude of the asymmetry for
 positive pions and hadrons at HERMES and COMPASS. For neutral pions the
@@
 Eqs.~(\ref{FUTsinphiS},~\ref{Eq:WW-type-FUTsinphiS}):
-two terms proportional to $h_T^{\perp q}(x,\kperp)$ and $h_T^q(x,\kperp)$, respectively, 
-and one term proportional to $f_T^q(x,\kperp)$, which is associated with
+two terms proportional to $h_T^{\perp q}(x,\kperp^{2})$ and $h_T^q(x,\kperp^{2})$, respectively, 
+and one term proportional to $f_T^q(x,\kperp^{2})$, which is associated with
 the second interesting feature. This T-odd TMD must satisfy the sum rule
-$\int d^2\kperp \,f_T^q(x,\kperp)=0$, see (\ref{Eq:sum-rules-T-odd})
+$\int d^2\kperp \,f_T^q(x,\kperp^{2})=0$, see (\ref{Eq:sum-rules-T-odd})
 and Sec.~\ref{Sec-3.8:limitations}.
@@
 and pragmatic solution, namely to neglect the contribution of
-$f_T^q(x,\kperp)$.\footnote{\label{Footnote:fT-single-Gauss} This
+$f_T^q(x,\kperp^{2})$.\footnote{\label{Footnote:fT-single-Gauss} This
 	corresponds to using a ``single Gaussian'' as
-	$f_T^q(x,\kperp) = f_T^q(x)\;
-	\frac{\exp(-\kperp^2/\la\kperp^2\ra_{f_T}^{ })}
+	$f_T^q(x,\kperp^{2}) = f_T^q(x)\;
+	\frac{\exp\left(-\kperp^2/\la\kperp^2\ra_{f_T}^{ }\right)}
 	{\pi\la\kperp^2\ra_{f_T}^{ }}$
@@
 Assuming Gaussian Ansatz (\ref{eq:hTperpnew},~\ref{eq:hTnew})
-for $h_T^{\perp q}(x,\kperp)$, $h_T^q(x,\kperp)$ in
+for $h_T^{\perp q}(x,\kperp^{2})$, $h_T^q(x,\kperp^{2})$ in
 App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs} and relating
@@
 	&= \,\frac{2M_N}{Q}\;x\sum_q e_q^2\,
-	h_1^{(1)q}(x)\,H_1^{\perp(1)q}(z)\; \frac{4z^2 m_h\,M_N}{\lambda}
+	h_1^{(1)q}(x)\,H_1^{\perp(1)q}(z)\; \frac{4z^2 \mh\,M_N}{\lambda}
 	\left(1-\frac{\Phperp^2}{\lambda}\right) {\cal G}(\Phperp)
@@
 $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_1^{ }}$.
-
-\begin{figure}
-\centering
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pip.pdf}  {\tiny (a)}
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sinphis_pim.pdf}  {\tiny (b)}
-\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_COMPASS_x}  {\tiny (c)}
-\includegraphics[height=3.5cm]{\FigPath/AUTsinphiS_HERMES_x.pdf}  {\tiny (d)}
-\caption{\label{autsinphis}
- 	Subleading-twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which
-	is predicted to vanish in the WW-type approximation: 
-	preliminary COMPASS~\cite{Parsamyan:2013fia} (a,b), 
-	our calculation for COMPASS kinematics (c), and HERMES data \cite{Schnell:2010zza} (d).}
-\end{figure}
-
 The third interesting feature is the occurrence of a term that drops
@@
 to discriminate experimentally the terms associated with this weight.
+
+\begin{figure}
+\centering
+\begin{tabular}{ccc} \ \hspace{-8mm}
+\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_sinphis_pip.pdf}&
+\includegraphics[height=3.3cm]{\FigPath/UT_Pr10_sinphis_pim.pdf}&
+%\includegraphics[height=2.7cm]{\FigPath/AUTsinphiS_COMPASS_x}  
+\includegraphics[height=3.3cm]{\FigPath/AUTsinphiS_HERMES_x.pdf}\\
+{\tiny (a)}&{\tiny (b)}&{\tiny (c)}
+\end{tabular}
+\caption{\label{autsinphis}
+ 	Subleading-twist asymmetry $A_{UT}^{\sin\phi_S}(x)$, which
+	is predicted to vanish in the WW-type approximation: 
+	preliminary COMPASS~\cite{Parsamyan:2013fia} (a,b), 
+	% \ps{our calculation for COMPASS kinematics (c),}
+	and HERMES data \cite{Schnell:2010zza} (c).}
+\end{figure}
 
@@
 
-%\newpage
+\newpage
 \subsection{\boldmath Subleading-twist  $A_{UT}^{\sin(2\phi_h-\phi_S)}$ }
@@
 
-Also in this asymmetry we end up with more than one contribution
-surviving the WW-type approximation. We assume Gaussian Ansatz for
-$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, and $h_T^q(x,\kperp)$,
+%Also in this asymmetry we end up with more than one contribution
+%surviving the WW-type approximation. We assume Gaussian Ansatz for
+%$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, and $h_T^q(x,\kperp)$,
+%according to (\ref{eq:hTperpnew},~\ref{eq:hTnew},~\ref{eq:ftperpnew})
+%in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, with
+%$\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_{1T}^\perp}$
+%and $\la\kperp^2\ra_{f_T^\perp}=\la\kperp^2\ra_{f_{1T}^\perp}$. The 
+%expressions obtained are given by
+
+\ps{In this asymmetry, two terms survive the WW-type approximation.
+Using the} Gaussian Ansatz for
+$f_T^{\perp q}(x,\kperp^{2})$, $h_T^{\perp q}(x,\kperp^{2})$, $h_T^q(x,\kperp^{2})$,
 according to (\ref{eq:hTperpnew},~\ref{eq:hTnew},~\ref{eq:ftperpnew})
@@
 $\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_{1T}^\perp}$
-and $\la\kperp^2\ra_{f_T^\perp}=\la\kperp^2\ra_{f_{1T}^\perp}$. The 
-expressions obtained are given by
+and $\la\kperp^2\ra_{f_T^\perp}=\la\kperp^2\ra_{f_{1T}^\perp}$
+\ps{yields} the expressions 
 \begin{subequations}\begin{alignat}{1}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t!]
+\centering
+\includegraphics[height=3.1cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (a)}%
+\includegraphics[height=3.1cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (b)}
+
+\includegraphics[height=2.4cm]{\FigPath/AUTsin2PhiminusPhiS_COMPASS_x} {\tiny (c)}
+\includegraphics[height=2.4cm]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf} {\tiny (d)}
+
+\vspace{-2mm}
+
+\caption{\label{autsin2phihphis}
+	$A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$: 
+	preliminary COMPASS data~\cite{Parsamyan:2013fia} (a,b)
+ %\ps{and our calculation for this kinematics (c) shown separately}.
+  \gs{and our calculation for COMPASS kinematics in WW-type 
+      approximation (c) shown separately for reasons explained 
+      in the caption of Fig.~\ref{aut_h1tp_jlab}.}
+	Similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ vs
+	preliminary HERMES data~\cite{Schnell:2010zza} (d).
+	}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The asymmetries $A_{UT}^{\sin (2 \phi_h-\phi_S)}=F_{UT}^{\sin (2 \phi_h-\phi_S)}/F_{UU}$
@@
 For comparison, Fig.~\ref{altcos2phihphis} shows also the predictions
-from the quark-diquark model calculation of Ref.~\cite{Kotzinian:2008fe}.
+from the quark-diquark model of Ref.~\cite{Kotzinian:2008fe}.
 More recently the $A_{UT}^{\sin(2\phi_h -\phi_S)}$ was also studied in the
@@
 
+\subsection{\boldmath Subleading-twist  $A_{UU}^{\cos\phi_h}$ }
+\label{Sec-7.7:FUUcosphi}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+\begin{figure}[t!]
 \centering
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (a)}%
-\includegraphics[height=3.5cm]{\FigPath/UT_Pr10_sin2phihphis_pip} {\tiny (b)}%
-\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_COMPASS_x} {\tiny (c)}
-\includegraphics[height=3.5cm]{\FigPath/AUTsin2PhiminusPhiS_HERMES_x.pdf} {\tiny (d)}
-\caption{\label{autsin2phihphis}
-	Subleading-twist $A_{UT}^{\sin(2 \phi_h - \phi_S)}(x)$: 
-	preliminary COMPASS data~\cite{Parsamyan:2013fia} (a,b), our calculation for COMPASS kinematics (c),
-	and similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ in comparison to
-	preliminary HERMES data~\cite{Schnell:2010zza} (d).
-	}
+\includegraphics[width=0.38\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf}
+\includegraphics[width=0.38\textwidth]{\FigPath/AUUcosphi_HERMES_x.pdf}
+\caption{\label{auucosphi_jlab}
+	Left panel: asymmetry $A_{UU}^{\cos\phi_h}$ for positive and negative
+	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}. Right
+	panel: the corresponding $A_{UU, \langle y \rangle}^{\cos\phi_h}$ for 
+	$\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{\boldmath Subleading-twist  $A_{UU}^{\cos\phi_h}$ }
-\label{Sec-7.7:FUUcosphi}
 
@@
 This structure function contains after the WW-type approximation initially
-two contributions, proportional to $f^\perp(x,\pperp)$ and $h^{q}(x,\kperp)$.
+two contributions, proportional to $f^\perp(x,\kperp^{2})$ and $h^{q}(x,\kperp^{2})$.
 The latter is T-odd and obeys the sum rule (\ref{Eq:sum-rules-T-odd}).
-We treat $h^{q}(x,\kperp)$ exactly as $f_T^q(x,\kperp)$ in
+We treat $h^{q}(x,\kperp^{2})$ exactly as $f_T^q(x,\kperp^{2})$ in
 Sec.~\ref{Sec-7.6:FUTsinphiS}.
-Using the Gaussian Ansatz for $f^\perp(x,\kperp)$ in (\ref{eq:fperpnew})
+Using the Gaussian Ansatz for $f^\perp(x,\kperp^{2})$ in (\ref{eq:fperpnew})
 of App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, we obtain
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_COMPASS_x.pdf}
-\includegraphics[width=0.45\textwidth]{\FigPath/AUUcosphi_HERMES_x.pdf}
-\caption{\label{auucosphi_jlab}
-	Left panel: asymmetry $A_{UU}^{\cos\phi_h}$ for positive and negative
-	hadrons at COMPASS for a proton target \cite{Adolph:2014pwc}. Right
-	panel: the corresponding $A_{UU, \langle y \rangle}^{\cos\phi_h}$ for $\pi^\pm$ from HERMES \cite{Airapetian:2012yg}.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 The asymmetries $A_{UU}^{\cos\phi_h}$ were measured by
@@
 COMPASS data.
-The WW-type approximation tends to overstimate the data at
+The WW-type approximation tends to overestimate the data at
 COMPASS especially in the small-$x$ region. It is also not
@@
 functions from six observables: the extraction of two basis functions,
-the unpolarized TMD and FF $f_1^q(x,\kperp)$ and $D_1^q(x,\pperp)$,
+the unpolarized TMD and FF $f_1^q(x,\kperp^{2})$ and $D_1^q(x,\pperp^{2})$,
 makes also use of other experiments, most notably Drell--Yan
@@
 of the QCD vacuum, and confirmed by data and lattice QCD studies.
-The classic WW approximation for $g_2(x)$ works with a relative
-accuracy of $\pm\,40\,\%$ or better. This is remarkable.
+% The classic WW approximation for $g_2(x)$ works with a relative
+% accuracy of $\pm\,40\,\%$ or better. This is remarkable.
 The instanton vacuum model predicts an analogous WW approximation
@@
 data are consistent with zero within their statistical
-accuracies. This cannot be considered a thorough evidence
+accuracy. This cannot be considered a thorough evidence
 for the applicability of the WW-type approximations, but
-on the positive site we also observe no alarming hints
+on the \ps{positive side we also observe no hints}
 that the WW-type approximations fail in these cases.
 
-In the case of the three subleading-twist structure functions
+In the case of the subleading-twist structure functions
 	$F_{UU}^{\cos\phi_h}$,
@@
 the very first non-zero target single-spin asymmetry measured in SIDIS
-($F_{UL}^{\sin\phi_h}$), and {and the beam-spin asymmetry} ($F_{LU}^{\sin\phi_h}$).
+($F_{UL}^{\sin\phi_h}$), and the beam-spin asymmetry ($F_{LU}^{\sin\phi_h}$).
 The WW-type prediction for $F_{UU}^{\cos(\phi_h)}$ tends to overshoot
 the data. In the case of $F_{UL}^{\sin\phi_h}$ the WW-type approximation
-undershoots data by a factor of 2 or so.
+undershoots data by a factor of two or so.
 Most interestingly, in the case of $F_{LU}^{\sin\phi_h}$ the WW-type
@@
 
-The non-applicability of the WW--type approximation in these three
+The non-applicability of the WW--type approximation in these 
 cases should not be too surprising. After all it is a crude method
@@
 in $F_{UL}^{\sin\phi_h}$ or $F_{LU}^{\sin\phi_h}$ a single $\bar{q}gq$--term
-is anomalously large, or whether it is a accumulative effect of
+is anomalously large, or whether it is an accumulative effect of
 several small terms $\bar{q}gq$--terms adding up to the observed asymmetry.
@@
 To the best of our knowledge, it is the first complete study of all SIDIS
-structure functions up to twist-3 in a unique approach. The results are
+structure functions up to twist-3 % in a unique approach. 
+\ps{using systematically a common theoretical guideline.}
+The results are
 useful for experiments prepared in the near term (JLab 12) or proposed
@@
 Contract No.\ PHY-1406298 (P.S.), and the Wilhelm Schuler Stiftung (P.S.).
+\ps{We thank the COMPASS and HERMES Collaborations for the 
+permissions to show their preliminary data on several figures.}
 
@@
 \caption{\label{Table:Gauss-paramaters}
-  	Gaussian model parameters for $f_1^a(x,k_\perp)$, $D_1^a(z,P_\perp)$,
- 	$g_{1}^a(x,k_\perp)$ from phenomenological and lattice QCD studies.
+  	Gaussian model parameters for $f_1^a(x,k_\perp^{2})$, $D_1^a(z,P_\perp^{2})$,
+ 	$g_{1}^a(x,k_\perp^{2})$ from phenomenological and lattice QCD studies.
   	The kinematics to which the phenomenological results and the
@@
 
-\subsection{\boldmath Sivers function $f_{1T}^{\perp q}(x,k_\perp)$}
+\subsection{\boldmath Sivers function $f_{1T}^{\perp q}(x,k_\perp^{2})$}
 \label{App:basis-f1Tperp}
 
-Sivers distribution function was studied in Refs.~\cite{Efremov:2004tp,Anselmino:2008sga,Anselmino:2011gs,Anselmino:2011ch, Aybat:2011ge,Gamberg:2013kla,Bacchetta:2011gx,Anselmino:2012aa,Sun:2013dya,Echevarria:2014xaa}.
+The Sivers distribution function was studied in Refs.~\cite{Efremov:2004tp,Anselmino:2008sga,Anselmino:2011gs,Anselmino:2011ch, Aybat:2011ge,Gamberg:2013kla,Bacchetta:2011gx,Anselmino:2012aa,Sun:2013dya,Echevarria:2014xaa}.
 We will use parametrizations from  Refs.~\cite{Anselmino:2008sga,Anselmino:2011gs,Anselmino:2011ch}:
 \ba
- \avkperp_{f_{1T}^\perp} &\equiv& \frac{\avkperp M_1^2}{\avkperp + M_1^2} \\
+ \avkperp_{f_{1T}^\perp} &\equiv& \frac{\avkperp M_1^2}{\avkperp + M_1^2} \, ,\\
 f_{1T}^{\perp}(x, \kperp^2)& =& - \frac {M}{M_1} \sqrt{2e} \;
@@
 \frac{(\alpha + \beta)^{(\alpha +\beta)}}
-{\alpha^{\alpha} \beta^{\beta}}
+{\alpha^{\alpha} \beta^{\beta}} \, .
  \ea
-The first moment of Sivers function is:
+The first moment of the Sivers function is:
 \ba
-f_{1T}^{\perp (1) q}(x)  = -\frac{\sqrt{\frac{e}{2}} \ \avkperp M_1^3}{M (\avkperp + M_1^2)^2}  \ {\cal N}_q(x)  f_q(x, Q) = -\sqrt{\frac{e}{2}} \frac{1}{M M_1}  \frac{\avkperp_{f_{1T}^\perp}^2}{\avkperp}    \ {\cal N}_q(x)  f_q(x, Q)
+f_{1T}^{\perp (1) q}(x)  &=& -\frac{\sqrt{\frac{e}{2}} \ \avkperp M_1^3}{M (\avkperp + M_1^2)^2}  \ {\cal N}_q(x)  f_q(x, Q) \nonumber \\ 
+&=&  -\sqrt{\frac{e}{2}} \frac{1}{M M_1}  \frac{\avkperp_{f_{1T}^\perp}^2}{\avkperp}    \ {\cal N}_q(x)  f_q(x, Q)
 \label{siversm} \ .
 \ea
-
-We can rewrite parametrizations of Sivers functions as
-
+%
+We can rewrite the parametrizations of the Sivers functions as
+%
 \ba
@@
 including only Sivers functions for $u$ and $d$ quarks was done in Ref.~\cite{Anselmino:2011gs},
-corresponding to seven free parameters, and parameters are shown in Table~\ref{tab:a}.
+corresponding to seven free parameters, which are shown in Table~\ref{tab:a}.
 
@@
 \hline
-$N_u=0.40$ & $\alpha_u=0.35$ & $\beta_u=2.6$ & \\
+$N_u=\phantom{-}0.40$ & $\alpha_u=0.35$ & $\beta_u=2.6\phantom{0}$ & \\
 $N_d=-0.97$ & $\alpha_d=0.44$ & $\beta_d=0.90$ & $M_1^2=0.19\;\textrm{(GeV}^2$)\\
@@
 
-\subsection{\boldmath Transversity $h_{1}^{q}(x,k_\perp)$ and
-Collins function $H_{1}^{\perp q}(x,P_\perp)$}
+\subsection{\boldmath Transversity $h_{1}^{q}(x,k_\perp^{2})$ and
+Collins function $H_{1}^{\perp q}(x,P_\perp^{2})$}
 \label{App:basis-h1-H1perp}
@@
 [f_{1}(x)+g_1(x)]\; ,\\
-H_{1 h/q}^{\perp}(z, \pperp^2) = \frac{z m_h}{2 \pperp} \Delta^N \!
-D_{h/q^\uparrow}(z,\pperp^2) &=&  \frac{z m_h}{M_C} e^{-p_{\perp}^2/M_C^2} \sqrt{2 e} H_{1 h/q}^{\perp}(z) \,\frac{e^{-\pperp^2/{\avpperp}}}{\pi \avpperp}\,,
+H_{1 h/q}^{\perp}(z, \pperp^2) = \frac{z \mh}{2 \pperp} \Delta^N \!
+D_{h/q^\uparrow}(z,\pperp^2) &=&  \frac{z \mh}{M_C} e^{-p_{\perp}^2/M_C^2} \sqrt{2 e} H_{1 h/q}^{\perp}(z) \,\frac{e^{-\pperp^2/{\avpperp}}}{\pi \avpperp}\,,
 \label{coll-funct}
  \ea
- with $m_h$ the mass of the produced hadron and
+ with $\mh$ the mass of the produced hadron and
  \ba
- {\cal N}^{\T}_q(x)= N^{\T}_q
+ {\cal N}^{\T}_q(x) &=& N^{\T}_q
 \,x^{\alpha} (1-x)^{\beta} \, \frac{(\alpha + \beta)^{(\alpha
@@
 \\
-H_{1 h/q}^{\perp}(z) =  {\cal N}^{\C}_q(z) D_{h/q}(z)\, , \\
-{\cal N}^{\C}_q(z)= N^{\C}_q \, z^{\gamma} (1-z)^{\delta} \,
+H_{1 h/q}^{\perp}(z) &=&  {\cal N}^{\C}_q(z) D_{h/q}(z)\, , \\
+{\cal N}^{\C}_q(z) &=& N^{\C}_q \, z^{\gamma} (1-z)^{\delta} \,
 \frac{(\gamma + \delta)^{(\gamma +\delta)}}
@@
 
-\begin{table}[h]
+\begin{table}[t]
 \centering
@@
 \ba
-H_{1 h/q}^{\perp (1)}(z) = \frac{H_{1 h/q}^{\perp}(z) \sqrt{e/2}  \avpperp M_C^3}{z m_h  (M_C^2+\avpperp)^2}\; .
+H_{1 h/q}^{\perp (1)}(z) = \frac{H_{1 h/q}^{\perp}(z) \sqrt{e/2}  \avpperp M_C^3}{z \mh  (M_C^2+\avpperp)^2}\; .
 \ea
@@
 \ba
-H_{1}^{\perp}(z,\pperp^2) =  H_{1}^{\perp (1)}(z)   \frac{2 z^2 m_h^2}{\pi \avpperp_{H_{1}^\perp}^2} e^{-\pperp^2/{\avpperp_{H_{1}^\perp}}}
+H_{1}^{\perp}(z,\pperp^2) =  H_{1}^{\perp (1)}(z)   \frac{2 z^2 \mh^2}{\pi \avpperp_{H_{1}^\perp}^2} e^{-\pperp^2/{\avpperp_{H_{1}^\perp}}}
 \label{coll-funct_new} \, .
@@
 
-\subsection{\boldmath Boer-Mulders function $h_{1}^{\perp q}(x,k_\perp)$}
+\subsection{\boldmath Boer--Mulders function $h_{1}^{\perp q}(x,k_\perp^{2})$}
 \label{App:basis-h1perp}
 
-The Boer-Mulders function $h_{1}^{\perp}$~\cite{Boer:1997nt} measures
+The Boer--Mulders function $h_{1}^{\perp}$~\cite{Boer:1997nt} measures
 the transverse polarization asymmetry of quarks inside an unpolarized
-nucleon. The Boer-Mulders functions were studied phenomenologically in
+nucleon. The Boer--Mulders functions were studied phenomenologically in
 Refs.~\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa}
 
-Ref.~\cite{Barone:2010gk} used the parametrization in which Boer-Mulders function is proportional to the Sivers functions, such that:
+Ref.~\cite{Barone:2010gk} used the parametrization in which the Boer--Mulders function is proportional to the Sivers functions, such that
 \ba
@@
 
-The first moment of Boer-Mulders function is:
+The first moment of the Boer--Mulders function is
 \ba
-h_{1}^{\perp (1) q}(x)  = -\frac{\sqrt{\frac{e}{2}} \ \avkperp M_{BM}^3}{M (\avkperp + M_{BM}^2)^2}  \ {N}_q f_q(x, Q) = -\sqrt{\frac{e}{2}} \frac{1}{M M_{BM}}  \frac{\avkperp_{h_1^\perp}^2}{\avkperp}    \ {N}_q  f_q(x, Q)
+h_{1}^{\perp (1) q}(x)  &=& -\frac{\sqrt{\frac{e}{2}} \ \avkperp M_{BM}^3}{M (\avkperp + M_{BM}^2)^2}  \ {N}_q f_q(x, Q)  \nonumber \\
+&=& -\sqrt{\frac{e}{2}} \frac{1}{M M_{BM}}  \frac{\avkperp_{h_1^\perp}^2}{\avkperp}    \ {N}_q  f_q(x, Q)
 \label{bm} \ .
@@
 
-We can rewrite parametrizations of Boer-Mulders functions as
+We can rewrite the parametrizations of Boer--Mulders functions as
 \ba
@@
 and fixed parameters (those without error bars)
-of the Boer-Mulders quark distributions from Ref.~\cite{Barone:2009hw}.}
+of the Boer--Mulders quark distributions from Ref.~\cite{Barone:2009hw}.}
 \label{fitparbm}
@@
 %\end{tabular}
-%\caption{Fitted parameters of Boer-Mulders quark distributions. Values are from Ref.~\cite{Barone:2015ksa}}
+%\caption{Fitted parameters of Boer--Mulders quark distributions. Values are from Ref.~\cite{Barone:2015ksa}}
 %\label{fitparbm}
@@
 
-\subsection{\boldmath Pretzelosity distribution $h_{1T}^{\perp q}(x,k_\perp)$}
+\subsection{\boldmath Pretzelosity distribution $h_{1T}^{\perp q}(x,k_\perp^{2})$}
 \label{App:basis-h1Tperp}
@@
 \ba
-h^{\perp a}_{1T}(x) = e  \ {\cal N}^a(x) (f_{1}^{a}(x, Q) - g_{1}^{a}(x, Q)), \label{eq:hx_par}\\
-{\cal N}^a(x) = N^{a} x^{\alpha} (1-x)^{\beta} \frac{(\alpha + \beta)^{\alpha + \beta}}{\alpha^{\alpha} \beta^{\beta}}\, ,  \\
-\avkperp_{h_{1T}^\perp}  = \frac{\avkperp M_{TT}^2}{\avkperp + M_{TT}^2}\, ,
+h^{\perp a}_{1T}(x) &=& e  \ {\cal N}^a(x) (f_{1}^{a}(x, Q) - g_{1}^{a}(x, Q)), \label{eq:hx_par}\\
+{\cal N}^a(x) &=& N^{a} x^{\alpha} (1-x)^{\beta} \frac{(\alpha + \beta)^{\alpha + \beta}}{\alpha^{\alpha} \beta^{\beta}}\, ,  \\
+\avkperp_{h_{1T}^\perp}  &=& \frac{\avkperp M_{TT}^2}{\avkperp + M_{TT}^2}\, ,
 \ea
-where ${N}^a$, $\alpha$, $\beta$, and $M_T$ are parameters fitted to data that can be found in Table~\ref{fitparI}.
+and where ${N}^a$, $\alpha$, $\beta$, and $M_T$ are parameters fitted to data and can be found in Table~\ref{fitparI}.
 
 %
-\begin{table}[b]
+\begin{table}[t]
 \centering
@@
 	D^{(n)}(z) &=& \int d^2\bfpperp
-	\left(\frac{\pperp^2}{2 z^2 m_h^2}\right)^{\!\!n}\; D(z, \pperp^2)
+	\left(\frac{\pperp^2}{2 z^2 \mh^2}\right)^{\!\!n}\; D(z, \pperp^2)
 	\;&\stackrel{\rm Gauss}{=}&\;
@@
 In this section we comment on the twist-3 TMDs
-$f_T^q(x,\kperp)$,  $h^q(x,\kperp)$, $e_L^q(x,\kperp)$,
+$f_T^q(x,\kperp^{2})$,  $h^q(x,\kperp^{2})$, $e_L^q(x,\kperp^{2})$,
 which are T-odd, appear in the decompositions of the correlator with no
@@
 	exhibit nodes for the $u$-- and $d$--flavor \cite{Efremov:2010mt}.
-	We will have to revise our description of $g_1^q(x,\kperp)$
+	We will have to revise our description of $g_1^q(x,\kperp^{2})$
 	in Eq.~(\ref{Eq:Gauss-g1}) and App.~\ref{App:basis-g1} to something
@@
 \begin{alignat}{1}
-	x \, f_T^q(x,\kperp) =  - \, f_{1T}^{\perp (1)q}(x)\;
+	x \, f_T^q(x,\kperp^{2}) =  - \, f_{1T}^{\perp (1)q}(x)\;
 	&\sum\limits_{i=1}^{n} a_i\;
@@
 \end{alignat}
-Notice that in (\ref{Eq:multiple-Gauss}) we cannot write ``$f_T^q(x)$''
-which would be zero according to (\ref{Eq:sum-rules-T-odd}) and we
+Notice that in (\ref{Eq:multiple-Gauss}) we cannot write ``$f_T^q(x)$'',
+which would be zero according to (\ref{Eq:sum-rules-T-odd}), and we
 explore here the WW-type approximation (\ref{Eq:WW-type-fT}).
@@
 very large $\la\kperp^2\ra_2^{ } \gg \la\kperp^2\ra_{f_1^\perp}$ to
-model the Gaussian description of $f_T^{q}(x,\kperp)$ similar to
+model the Gaussian description of $f_T^{q}(x,\kperp^{2})$ similar to
 that of $f_{1T}^{\perp(1)q}(x,\kperp^2)$ at intermediate $\kperp$.
@@
 the present stage, but in principle this could be a
-pragmatic way of modeling the TMD $f_T^q(x,\kperp)$
-and analogously $h^q(x,\kperp)$, $e_L^q(x,\kperp)$.
+pragmatic way of modeling the TMD $f_T^q(x,\kperp^{2})$
+and analogously $h^q(x,\kperp^{2})$, $e_L^q(x,\kperp^{2})$.
 
@@
     &=&	\phantom{-}\,u \;{\cal G}(\Phperp)\;
-	\biggl(\frac{z\Phperp}{m_h}\biggr)\;\frac{\la\pperp^2\ra}{z^2\lambda}\\
+	\biggl(\frac{z\Phperp}{\mh}\biggr)\;\frac{\la\pperp^2\ra}{z^2\lambda}\\
   {\cal C}\bigl[\omega^{\{1\}}_{\rm B} \, f \, D \bigr]
@@
     &=&	\phantom{-}\,u \; {\cal G}(\Phperp)\;
-	\frac{\la\kperp^2\ra\la\pperp^2\ra}{\lambda M_N m_h}
+	\frac{\la\kperp^2\ra\la\pperp^2\ra}{\lambda M_N \mh}
 	\left(-1+\frac{2\Phperp^2}{\lambda}\right)\\
@@
     &=&	\phantom{-}\,u \; {\cal G}(\Phperp)\;
-	\frac{\la\kperp^2\ra\la\pperp^2\ra}{\lambda M_N m_h}
+	\frac{\la\kperp^2\ra\la\pperp^2\ra}{\lambda M_N \mh}
 	\left(1-\frac{\Phperp^2}{\lambda}\right)\\
@@
 	\biggl(\frac{z\Phperp}{M_N}\biggr)
-	\biggl(\frac{z\Phperp}{M_h}\biggr)
+	\biggl(\frac{z\Phperp}{\mh}\biggr)
 	\;\frac{\la\kperp^2\ra}{\lambda}
@@
 	\biggl(\frac{z\Phperp}{M_N}\biggr)
-	\biggl(\frac{z\Phperp}{m_h}\biggr)
+	\biggl(\frac{z\Phperp}{\mh}\biggr)
 	\;\frac{\la\kperp^2\ra}{\lambda}
@@
 The ``non-compact'' notation in Eqs.~(\ref{Eq:Gaussian-integrals-RAW})
-was chosen to display the pattern. The masses $M_N$ or $m_h$ in the
+was chosen to display the pattern. The masses $M_N$ or $\mh$ in the
 denominators of the $\Phperp$ indicate the ``origins'' of the
@@
     &=&	\phantom{-}\,u^{(1)}_{\rm A} \;{\cal G}(\Phperp)\;
-	\biggl(\frac{z\Phperp}{m_h}\biggr)\;\frac{2m_h^2}{\lambda}\\
+	\biggl(\frac{z\Phperp}{\mh}\biggr)\;\frac{2\mh^2}{\lambda}\\
   {\cal C}\bigl[ \omega^{\{1\}}_{\rm B} \, f \, D \bigr]
@@
     &=&	\phantom{-}\, u^{(2)}_{\rm B}\; {\cal G}(\Phperp)\;
-	\frac{4z^2 m_h\,M_N}{\lambda}
+	\frac{4z^2 \mh\,M_N}{\lambda}
 	\left(1-\frac{\Phperp^2}{\lambda}\right)\\
@@
 	\biggl(\frac{z\Phperp}{M_N}\biggr)
-	\biggl(\frac{z\Phperp}{M_h}\biggr)
+	\biggl(\frac{z\Phperp}{\mh}\biggr)
 	\;\frac{2M_N^2}{\lambda}
-	\;\frac{2m_h^2}{\lambda}\\
+	\;\frac{2\mh^2}{\lambda}\\
   {\cal C}\bigl[ \, \omega^{\{2\}}_{\rm C} \: f \, D \bigr]
@@
 	\biggl(\frac{z\Phperp}{M_N}\biggr)
-	\biggl(\frac{z\Phperp}{m_h}\biggr)
+	\biggl(\frac{z\Phperp}{\mh}\biggr)
 	\;\frac{2M_N^2}{\lambda}
 	\;\frac{2M_N^2}{\lambda}
-	\;\frac{2m_h^2}{\lambda}
+	\;\frac{2\mh^2}{\lambda}
 \ea\end{subequations}
@@
 	b^{(0)}_{\rm  } 	&= 1 \, , \\
-	b^{(1)}_{\rm A} 	&= 2m_h	\, , &
+	b^{(1)}_{\rm A} 	&= 2\mh	\, , &
 	b^{(1)}_{\rm B} 	&= 2M_N	\, , \\
-	a^{(2)}_{\rm B}	&= 4M_Nm_h\lambda^{-1}\,z^2  \, , \;\;\;\;\;\; &
+	a^{(2)}_{\rm B}	&= 4M_N\mh\lambda^{-1}\,z^2  \, , \;\;\;\;\;\; &
 	b^{(2)}_{\rm AB} 	&= -\,b^{(2)}_{\rm B}
-			 = 4M_Nm_h 	\, , \;\;\;\;\;\; &
+			 = 4M_N\mh 	\, , \;\;\;\;\;\; &
 	b^{(2)}_{\rm C} 	&= M_N^2  \, ,\\
-	b^{(3)}_{\rm  } 	&= 2M_N^2m_h \, .
+	b^{(3)}_{\rm  } 	&= 2M_N^2\mh \, .
 	\label{Eq:Gaussian-integrals-working-III}
@@
 	c^{(0)}_{\rm  } 	&= 1 \, , \\
-	c^{(1)}_{\rm A} 	&= \sqrt{\pi}\,m_h	\, , &
+	c^{(1)}_{\rm A} 	&= \sqrt{\pi}\,\mh	\, , &
 	c^{(1)}_{\rm B} 	&= \sqrt{\pi}\,M_N	\, , \\
-	c^{(2)}_{\rm AB} 	&= 4M_Nm_h		\, , \;\;\;\;\;\; &
+	c^{(2)}_{\rm AB} 	&= 4M_N\mh		\, , \;\;\;\;\;\; &
 	c^{(2)}_{\rm C} 	&= M_N^2 		\, , \;\;\;\;\;\;\;\;\;\; &
 	c^{(2)}_{\rm B}	&= 0 			\, ,\\
-	c^{(3)}_{\rm  } 	&= {\textstyle\frac32}\sqrt{\pi} \,M_N^2m_h
+	c^{(3)}_{\rm  } 	&= {\textstyle\frac32}\sqrt{\pi} \,M_N^2\mh
 	\, . \;\;\;     &
@@
 \end{alignat}
-
-\section{Mathematica package}
-\label{app:package}
-
-A package available to a wide physics community is needed for several
-reasons. First of all it is intended to facilitate visualization,
-reproduction, and verification of our results presented in this paper.
-Second, the package may prove useful for experimentalists in need of
-estimates of measured quantities for certain kinematics of a particular
-experiment. Third, the phenomenological workers in the community
-will have an easy access to our results for comparison and/or use in
-phenomenological or theoretical papers. The authors believe that the
-open source access to the codes used in a project is the right way of
-handling scientific information in the 21$^{st}$ century. For example,
-collinear parton distribution functions are well tabulated in
-the \texttt{LHAPDF} project \cite{Buckley:2014ana}, but collinear
-fragmentation function still need a dedicated repository. There exist
-already several databases which are being developed for extensions
-of collinear one-dimensional picture of the nucleon structure.
-Generalized Parton Distributions are present in the framework
-called \texttt{PARTONS} \cite{Berthou:2015oaw}, several extractions
-of Transverse Momentum Dependent distributions are tabulated in
-\texttt{TMDlib} project \cite{Hautmann:2014kza}.
-
-If you use this package, please, cite this paper and the link to
-the repository. Please, acknowledge using any of the extracted TMDs
-presented in this package. The corresponding \texttt{bibitem}
-codes are included in the description of each TMD function.
-
-The source code of the project can be downloaded or cloned from the
-open source repository: \texttt{https://github.com/prokudin/WW-SIDIS}.
-Using \texttt{Mathematica}  run the  file named \texttt{example.nb},
-you will see an example of usage of the code, code description and
-several visualizations of functions, asymmetries, and SIDIS cross-sections.
-Please note that, for now, the package can compute the aforementioned
-observables for a proton target, detected charged pions and beam
-helicities $\pm1$ or $0$ (with the latter denoting an unpolarized beam).
-Make sure that you do not move \texttt{example.nb} to another directory
-as it uses grids for TMDs, PDFs, and FFs. SIDIS cross section examples are presented in Fig.~\ref{fig:package}.
-
-\begin{figure}[t]
-\centering
-%\vspace{5mm}
-\includegraphics[width=0.45\textwidth]{\FigPath/cross_section_phih.pdf}
-\includegraphics[width=0.45\textwidth]{\FigPath/cross_section_phiS.pdf}
-\caption{\label{fig:package}
-	Left panel:
-	$\phi_h$ dependence of the SIDIS cross section at $\phi_S = \pi/2$.
-	Right panel:
-	$\phi_S$ dependence of the SIDIS cross section at $\phi_h = 0$.
-	Also $x = 0.3$, $z=0.2$, $\Phperp = 0.5$ GeV,
-	$Q^2$ = 2.4 GeV$^2$, and the beam energy $E_{beam}$ = 5.7 GeV,
-	averaged over beam helicities,  transverse proton target polarization.}
-\end{figure}
 

### 2019-04-01 arxiv2/test-WW-type-v2F.tex
AP

--- 2019-03-13 arxiv2/test-WW-type-v2E.tex
@@
 \newcommand{\gs}[1]{{\color[rgb]{0.65,0,0.65}#1}}
-%\newcommand{\bp}[1]{{\color[rgb]{0,0.65,0.35}#1}}
+\newcommand{\bp}[1]{{\color[rgb]{0,0.65,0.35}#1}}
 %\newcommand{\ms}[1]{\darkgreen{#1}}
@@
 The superscript ``weight'' indicates the azimuthal dependence with no index
-indicating an isotropic angular distribution of the produced hadrons.
+indicating \bp{a $\phi$-independent} distribution of the produced hadrons.
 
@@
 These evolution equations differ from those of the leading-twist
-functions $g_1^a(x)$ and $h_1^a(x)$. This point is of not much
-practical relevance here, because the $Q^2$ varies only moderately
-between JLab, HERMES, and COMPASS (except for the largest $x$-bins).
-However, if for some reason the $\bar{q}gq$-terms were found to be
-very small at one renormalization scale, it is not guaranteed the
-WW-type approximation will work equally well also at other scales. 
- More theoretical work is required, especially also in order to 
-understand $k_\perp$-evolution effects at subleading twist.}
+functions $g_1^a(x)$ and $h_1^a(x)$. 
+% This point is of not much
+% practical relevance here, because the $Q^2$ varies only moderately
+% between JLab, HERMES, and COMPASS (except for the largest $x$-bins).
+% However, if for some reason the $\bar{q}gq$-terms were found to be
+% very small at one renormalization scale, it is not guaranteed the
+% WW-type approximation will work equally well also at other scales. 
+% More theoretical work is required, especially also in order to 
+% understand $k_\perp$-evolution effects at subleading twist.
+\bp{However, since $Q^2$ varies moderately in the considered experiments 
+(e.g.\ for common values of $x$ the $Q^2$ at COMPASS is only about factor 2 
+larger than at HERMES), this point is not a major uncertainty in our study.
+More theoretical work will be required to understand $k_\perp$-evolution 
+effects of subleading twist TMDs in future experiments (EIC) 
+covering larger $Q^2$ ranges.}}
 
@@
 which confirms that the Gaussian model works also in this case.
+\bp{The Sivers function is predicted to enter the description of hadron-hadron 
+collisions (with transversely polarized protons) with an opposite sign 
+compared to SIDIS \cite{Collins:2002kn,Brodsky:2002cx,Brodsky:2002rv}.
+Recent results on single-spin asymmetries in weak boson production 
+from RHIC \cite{Adamczyk:2015gyk} and Drell--Yan from COMPASS 
+\cite{Aghasyan:2017jop,Parsamyan:2018zju} are consistent 
+with this prediction.}
 
@@
 due to the convolution of the transversity distribution $h_1$ and the Collins
-FF $H_1^\perp$. Transversity can in principle be accessed also as a PDF in
-Drell--Yan or in dihadron production
-\cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,Bacchetta:2012ty,
-Radici:2015mwa,Radici:2018iag}. The first polarized Drell--Yan data were
-measured by COMPASS~\cite{Aghasyan:2017jop,Parsamyan:2018zju}.
+FF $H_1^\perp$. 
 It describes the distribution of transversely polarized quarks 
 in a transversely polarized nucleon, and is the only source of information
-on the tensor charge of the nucleon. The Collins FF $H_1^\perp$ decodes the
+on the tensor charge of the nucleon. 
+\bp{Transversity can also be accessed as a PDF in Drell--Yan or dihadron 
+production \cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,
+Bacchetta:2012ty,Radici:2015mwa,Radici:2018iag}.} 
+% The first polarized Drell--Yan data were measured by 
+% COMPASS~\cite{Aghasyan:2017jop,Parsamyan:2018zju}.
+The Collins FF $H_1^\perp$ decodes the
 fundamental correlation between the transverse spin of a fragmenting quark
-and the transverse momentum of the final hadron produced~\cite{Collins:1992kk}.
-
-There are many extractions of $h_1$ and $H_1^\perp$ from a
-combined fit of SIDIS and $e^+e^-$ data, for instance those of
+and the transverse momentum of the produced final hadron~\cite{Collins:1992kk}.
+%
+There are many extractions of $h_1$ and $H_1^\perp$ from 
+combined fits of SIDIS and $e^+e^-$ data, for instance those of
 Refs.~\cite{Anselmino:2013vqa,Kang:2014zza,Anselmino:2015sxa}.
@@
 	\ps{(a)} HERMES \cite{Airapetian:2010ds} and
-	\ps{(b)} COMPASS \cite{Adolph:2014zba} data [where
-	$(-1)A_{UT}^{\sin(\phi_h+\phi_S)}$ is shown since COMPASS 
-	\gs{uses an opposite sign in its Collins asymmetry convention}].}
+	\ps{(b)} COMPASS \cite{Adolph:2014zba} data. Notice that we multiplied COMPASS data by a factor $-1$ in order to match our convention of the Collins angle.}
 \end{figure}
@@
 WW-type approximation in this case is compatible with preliminary COMPASS
-\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (see Fig.~\ref{allcosphi_jlab}) and HERMES \cite{Airapetian:2018rlq} data.
+\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (see Fig.~\ref{allcosphi_jlab}) 
+and HERMES \cite{Airapetian:2018rlq} data.
 We remark that previously this asymmetry was studied in basically

### 2019-04-11 arxiv2/test-WW-type-v2F.tex
AP

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering \ 
-\includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf}
+\begin{figure}[t!]
+\centering
+\begin{tabular}{cc} \ \hspace{-8mm}
+\includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf} &
 \includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
-\includegraphics[width=0.8\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}
+{\tiny (a) }&{\tiny (b)} \\
+\includegraphics[width=0.6\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}&
+\includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf}\\
+{\tiny (c) \hspace{3cm} (d)}&{\tiny (e)}
+\end{tabular}
 	\caption{\label{aulsinphi_jlab} 
 	$A_{UL}^{\sin\phi_h}$ for proton vs.~$x$ from WW-type
-	approximation in comparison to data for the following hadrons.
-	Upper panel left: $\pi^\pm$ from HERMES \cite{Airapetian:2005jc}.
-	Upper panel right: $\pi^0$ from HERMES (blue) \cite{Airapetian:2001eg}
-	and JLab (red) \cite{Jawalkar:2017ube}.
-	Lower panel: preliminary $h^\pm$ COMPASS data \cite{Parsamyan:2018ovx,Parsamyan:2018evv}.}
+	approximation and comparison to the data.
+	$\pi^\pm$ from HERMES \cite{Airapetian:2005jc} (a), $\pi^0$ from HERMES (blue) \cite{Airapetian:2001eg} and JLab (red) \cite{Jawalkar:2017ube} (b), 
+	preliminary COMPASS data
+	\cite{Parsamyan:2018ovx,Parsamyan:2018evv} (c,d),  
+	and our calculation for COMPASS kinematics in 
+	WW-type approximation (e)
+	\ps{shown separately for reasons explained in the
+	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.}}
 \end{figure}

### 2019-04-16 arxiv2/test-WW-type-v2G.tex
AP

--- 2019-04-11 arxiv2/test-WW-type-v2F.tex
@@
 the spin-vector defined as in Fig.~\ref{fig-kin-SIDIS}.
-It is convenient to introduce the unpolarized
-lepton--quark scattering subprocess cross section
-\ba\label{Eq:sigma0-FUU}
-	\frac{d \hat{\sigma}}{dy}
-	=
-	\frac{4 \pi \alpha_{em}^2}{x\,y\,Q^2}
-	\biggl(1-y+\frac12y^2\biggr)\;.
-\ea
+% It is convenient to introduce the unpolarized
+% lepton--quark scattering subprocess cross section
+% \ba\label{Eq:sigma0-FUU}
+%	\frac{d \hat{\sigma}}{dy}
+%	=
+%	\frac{4 \pi \alpha_{em}^2}{x\,y\,Q^2}
+%	\biggl(1-y+\frac12y^2\biggr)\;.
+% \ea
 
@@
 \begin{subequations}\ba\hspace{-1cm}
-   &&  \frac{d^6\sigma_{\rm leading}}{dx\,dy\,dz\,d\psi_l\,d\phi_h\,d \Phperp^2}
-   =	 \frac{1}{4\pi}\;\frac{d \hat{\sigma}}{dy}\;F_{UU}(x,z,\Phperp^2)
-        \Biggl\{\;1
-        + \cos(2\phi_h)\,   p_1\,A_{UU}^{\cos(2\phi_h)} \nonumber\\
+   &&  \hspace{-5mm}
+	\frac{d^6\sigma_{\rm leading}}{dx\,dy\,dz\,d\psi_l\,d\phi_h\,d \Phperp^2}
+   =	% \frac{1}{4\pi}\;\frac{d \hat{\sigma}}{dy}
+	\bp{\frac{\alpha_{em}^2}{x\,y\,Q^2}\biggl(1-y+\frac12y^2\biggr)}
+	\;F_{UU}(x,z,\Phperp^2) 
+	\nonumber\\
+   && \times     \Biggl\{\;1
+        + \cos(2\phi_h)\,   p_1\,A_{UU}^{\cos(2\phi_h)} 
+  %\nonumber\\
+  % && \hspace{1cm}
+  	+ S_L\sin(2\phi_h)\,p_1\,A_{UL}^{\sin(2\phi_h)}
+	+ \lambda\,S_L\,    p_2\,A_{LL}  \nonumber\\
    && \hspace{1cm}
-  	+ S_L\sin(2\phi_h)\,p_1\,A_{UL}^{\sin(2\phi_h)}
-	+ \lambda\,S_L\,    p_2\,A_{LL}  \phantom{\frac11}\nonumber\\
-   && \hspace{1cm}
-       	+ S_T\sin( \phi_h-\phi_S)\, A_{UT}^{\sin( \phi_h-\phi_S)}
-	+ S_T\sin( \phi_h+\phi_S)\,p_1\,A_{UT}^{\sin( \phi_h+\phi_S)}
+       	+ \; 	S_T\sin( \phi_h-\phi_S)\, A_{UT}^{\sin( \phi_h-\phi_S)}
+	\; + \;	S_T\sin( \phi_h+\phi_S)\,p_1\,A_{UT}^{\sin( \phi_h+\phi_S)}
 	 \phantom{\frac11}
@@
    && \hspace{1cm}
-        + S_T\sin(3\phi_h-\phi_S)\,p_1\,A_{UT}^{\sin(3\phi_h-\phi_S)}
+        + \;	   S_T\sin(3\phi_h-\phi_S)\,p_1\,A_{UT}^{\sin(3\phi_h-\phi_S)}
 	+ \lambda\,S_T\cos(\phi_h-\phi_S)\,p_2\,A_{LT}^{\cos( \phi_h-\phi_S)}\Biggr\}
@@
    &&   \frac{d^6\sigma_{\rm subleading}}{dx\,dy\,dz\,d\psi_l\,d\phi_h\,d \Phperp^2}
-   =	\frac{1}{4\pi} \; \frac{d \hat{\sigma}}{dy} \; F_{UU}(x,z,\Phperp^2)
+   =	%\frac{1}{4\pi} \; \frac{d \hat{\sigma}}{dy} 
+	\bp{\frac{\alpha_{em}^2}{x\,y\,Q^2}\biggl(1-y+\frac12y^2\biggr)}
+	\; F_{UU}(x,z,\Phperp^2)
         \Biggl\{
@@
 The superscript ``weight'' indicates the azimuthal dependence with no index
-indicating \bp{a $\phi$-independent} distribution of the produced hadrons.
+indicating \bp{a $\phi_h$-independent asymmetry or structure function.}
 
@@
 (\ref{Eqs:structure-functions-twist-3}) is based on the
-{\it assumption} that that SIDIS cross section factorizes.
+{\it assumption} that the SIDIS cross section factorizes.
 
@@
 with the Gaussian Ansatz within uncertainties. Second, the lattice
-results---in the way we use them in App.~\ref{App:basis-g1}---give an appropriate
-description of the data.
+results---in the way we use them in App.~\ref{App:basis-g1}---give an 
+appropriate description of the data.
 	(Another important test was already presented in
@@
 	approximation, indeed already probing DIS \cite{Avakian:2010ae}.)
+\bp{We remark that HERMES and COMPASS data also show flat 
+$P_{hT}$-distributions \cite{Adolph:2016vou,Airapetian:2018rlq}.}
 
@@
 \label{Sec-5.3:Sivers-basis}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[b!]
-\centering
-\includegraphics[width=0.35\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
-\includegraphics[width=0.35\textwidth]{\FigPath/AUTSivers_COMPASS_x.pdf}
-\caption{\label{aut_f1t_jlab} Sivers asymmetry
-	$A_{UT}^{\sin(\phi_h-\phi_S)}$ for a proton target as function of $ x $
-	based on the fit \cite{Anselmino:2011gs} in comparison to
-	(left panel) HERMES \cite{Airapetian:2009ae}
-	and (right panel) COMPASS  \cite{Adolph:2012sp} data.}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 The $F_{UT}^{\sin(\phi_h-\phi_S)}$ structure function is related to the
@@
 in (\ref{FUTsiv-Gauss}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t!]
+\centering
+\includegraphics[width=0.35\textwidth]{\FigPath/AUTSivers_x.pdf}  \hspace{5mm}
+\includegraphics[width=0.35\textwidth]{\FigPath/AUTSivers_COMPASS_x.pdf}
+\caption{\label{aut_f1t_jlab} Sivers asymmetry
+	$A_{UT}^{\sin(\phi_h-\phi_S)}$ for a proton target as function of $ x $
+	based on the fit \cite{Anselmino:2011gs} in comparison to
+	(left panel) HERMES \cite{Airapetian:2009ae}
+	and (right panel) COMPASS  \cite{Adolph:2012sp} data.}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 {\tiny(b)}
-\caption{\label{aut_h1_jlab}  Collins asymmetry
-	$A_{UT,  \langle y\rangle}^{\sin(\phi_h+\phi_S)}$ for a proton target 
-	as function of $ x $
-	based on the fit \cite{Anselmino:2013vqa} in comparison to
-	\ps{(a)} HERMES \cite{Airapetian:2010ds} and
-	\ps{(b)} COMPASS \cite{Adolph:2014zba} data. Notice that we multiplied COMPASS data by a factor $-1$ in order to match our convention of the Collins angle.}
+\caption{\label{aut_h1_jlab}  Collins asymmetry for a proton target 
+	vs $x$ based on the fit \cite{Anselmino:2013vqa}.
+	(a) \bp{$A_{UT,  \langle y\rangle}^{\sin(\phi_h+\phi_S)}$ in comparison} 
+	to HERMES \cite{Airapetian:2010ds} data.
+	(b) \bp{$A_{UT}^{\sin(\phi_h+\phi_S)}$ in comparison} 
+	to COMPASS \cite{Adolph:2014zba} data.}
 \end{figure}
@@
         the permission to show the preliminary data \cite{Parsamyan:2013fia} 
-	%only in the figures exactly as provided by COMPASS collaboration in 
 	\gs{only in the official figures provided by the COMPASS collaboration}
- 	in (a,b), and have to display our results separately in (d).]}}
+ 	in (a,b), and have to display our results separately in (d).
+	Notice also the different scale on the y-axis in panel (d) 
+	as compared to (a,b).]}}
 \end{figure}
@@
 $A_{UT}^{\sin(3 \phi_h - \phi_S)}=F_{UT}^{\sin(3 \phi_h - \phi_S)}/F_{UU}$ and 
-preliminary HERMES data \cite{Schnell:2010zza} for
-$A_{UT, \langle y \rangle}^{\sin(3 \phi_h - \phi_S)}=\ps{\la
+preliminary HERMES data \cite{Schnell:2010zza} for$
+A_{UT, \langle y \rangle}^{\sin(3 \phi_h - \phi_S)}=\ps{\la
 (1-y)F_{UT}^{\sin(3 \phi_h - \phi_S)}\ra/\la(1-y + y^2/2)F_{UU}\ra}$
@@
 \centering \ \hspace{-6mm}
-\includegraphics[height=5.5cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \\
+\includegraphics[height=5cm]{\FigPath/A_UL2_Pr0711_Zgt02.pdf} \\
 
@@
 
-\includegraphics[height=4cm]{\FigPath/AULsin2phi_JLAB_x.pdf} \
-\includegraphics[height=4cm]{\FigPath/AULsin2phi_COMPASS_x} \\
+\includegraphics[height=3.6cm]{\FigPath/AULsin2phi_JLAB_x.pdf} \
+\includegraphics[height=3.6cm]{\FigPath/AULsin2phi_COMPASS_x} \\
 \ \hspace{1cm} {\tiny (c)} \hspace{6cm} {\tiny (d)}
@@
 	\ps{shown separately for reasons explained in the
-	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.} The smallness
-	of this asymmetry has two natural reasons: first, being twist-3
-	it is $M_N/Q$ suppressed; and second, it is proportional to
-	$P_{hT}^2$  in TMD approach.}
+	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.}}
+	% The smallness of this asymmetry has two natural reasons: first, 
+    	% being twist-3 it is $M_N/Q$ suppressed; and second, it is 
+	% proportional to $P_{hT}^2$  in TMD approach.
 \end{figure}
@@
 the Gaussian width $\avkperp_{g_{L}^\perp}=\avkperp_{g_1}$.
-The structure function $F_{UL}^{\cos\phi_h}$ reads
+The structure function \bp{$F_{LL}^{\cos\phi_h}$} reads
 \begin{subequations}\ba
@@
 \includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} \\
-{\tiny (a) }&{\tiny (b)} \\
+{\tiny (a) }&{\tiny (b)} \vspace{5mm}\\
+\ \hspace{-8mm}
 \includegraphics[width=0.6\textwidth]{\FigPath/A_UL1_Pr0711_Zgt02.pdf}&
 \includegraphics[width=0.38\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf}\\
-{\tiny (c) \hspace{3cm} (d)}&{\tiny (e)}
+{\tiny (c) \hspace{3cm} (d)}&{\tiny (e)} \vspace{5mm}
 \end{tabular}
@@
 	preliminary COMPASS data~\cite{Parsamyan:2013fia} (a,b)
- %\ps{and our calculation for this kinematics (c) shown separately}.
   \gs{and our calculation for COMPASS kinematics in WW-type 

### 2019-04-29 arxiv2/test-WW-type-v2H.tex
Gunars edits as described in email 2019-04-29

--- 2019-04-16 arxiv2/test-WW-type-v2G.tex
@@
 \bp{However, since $Q^2$ varies moderately in the considered experiments 
-(e.g.\ for common values of $x$ the $Q^2$ at COMPASS is only about factor 2 
+(e.g.\ for common values of $x$ the $Q^2$ at COMPASS is only about \gs{a factor 2-3} 
 larger than at HERMES), this point is not a major uncertainty in our study.
@@
 effects of subleading twist TMDs in future experiments (EIC) 
-covering larger $Q^2$ ranges.}}
+\gs{covering kinematic regions that vary by orders of magnitude in $Q^2$.}}}
 
@@
 \bp{We remark that HERMES and COMPASS data also show flat 
-$P_{hT}$-distributions \cite{Adolph:2016vou,Airapetian:2018rlq}.}
+$P_{hT}$-distributions \cite{Airapetian:2018rlq,Adolph:2016vou}.}
 
@@
 compared to SIDIS \cite{Collins:2002kn,Brodsky:2002cx,Brodsky:2002rv}.
-Recent results on single-spin asymmetries in weak boson production 
+Recent results on single-spin asymmetries in weak-boson production 
 from RHIC \cite{Adamczyk:2015gyk} and Drell--Yan from COMPASS 
@@
 \ \hspace{-3mm}
-\includegraphics[width=0.36\textwidth]{\FigPath/ALT_COMPASS_x.pdf} \\
- {\tiny (a)}&{\tiny (b)}&{\tiny (c)}
+\includegraphics[width=0.36\textwidth]{\FigPath/ALT_COMPASS_x.pdf} \\[-3mm]
+ {\tiny (a)}&~~~~{\tiny (b)}&~~~~~~{\tiny (c)}
 \end{tabular}
@@
 	and our calculation for COMPASS kinematics (c)
-	\ps{shown separately for reasons explained in 
+	\ps{shown separately for reasons explained in the
 	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.}}

### 2019-04-30 arxiv2/reply-to-referee-v2H.tex
AP

\documentclass[a4paper,11pt]{article}
\bibliographystyle{JHEP}
\usepackage{jheppub} 
\begin{document}

\section*{REPLY TO THE EDITOR}

Dear Editor,

\ \\
We would like to thank the Referee for careful reading, 
constructive criticism, and helpful recommendations. We 
revised the manuscript closely following the Referee's
suggestions in all points.

\ \\
Sincerely,

\ \\
Authors \\

\section*{REPLY TO THE REFEREE}

We would like to thank the Referee for careful reading, 
constructive criticism, and the many helpful recommendations. 
We revised the manuscript closely following the Referee's
suggestions  as detailed out in the attached ``Summary of Changes.''
Below we respond to several specific points in the report.

\begin{itemize}

\item	We agree that the $Q^2$ evolution is an important 
	limiting factor, and added a brief comment in the
	Introduction as well as a more detailed paragraph
	in Sec.~3.8.

\item	The preliminary COMPASS data shown in Fig.~12 and
	several subsequent figures have been released and
	can be shown in our work under the condition that
	we show these Figures exactly as provided to us
	by the COMPASS Collaboration. This means that at
	this point we are not allowed to include the 
	results of our calculations in these plots, and
	must show them separately. These data will 
	presumably be unconditionally released at some later 
	time in the summer of this year. We added explanatory
	remarks in Fig.~12 and other figures where this applies.
	On the one hand, this makes the presentation of the
	results and the formatting of the figures cumbersome
	in many cases. On the other hand, we are grateful
	to the COMPASS Collaboration for giving us this
	possibility to show their preliminary data.
	We are also grateful to the HERMES Collaboration
	for making their preliminary data available and
	allowing us to include our curves in those plots.
	We added a remark in the Acknowledgments.

\item	We understand the concerns of the Referee regarding the 
	subpercent results shown e.g.\ in Fig.~15. We had similar
	concerns but decided to show these results, even though
	subpercent asymmetries are not realistic predictions for 
	COMPASS. But the smallness of the effect shown in Fig.~15 is 
	not only due to the (in our approximation) small involved 
	TMDs but also due to the kinematical suppression in the
	COMPASS kinematics. The figure still gives insights e.g.\ 
	on the relative flavor dependence for the production of 
	positive vs negative pions in the WW-type approximation.

\item	Finally, we followed the recommendations of the Referee
	and removed App.~C on the mathematica package, unified 
	the notation for the masses of produced hadrons $m_h$, 
	specified the Mellin moments before Eq.~(3.8), fixed 
	the literal repetition on pages 16/17, improved
	non-optimal wording and fixed typos. It is inexplicable
	how some of these things could have escaped our attention 
	during proof-reading, and we are grateful for these corrections.

\end{itemize}

\section*{SUMMARY OF CHANGES}

\begin{itemize}

\item
Sec.1, page 3, the following paragraph and the new references
\cite{Ali:1991em,Koike:1994st,Balitsky:1996uh,Belitsky:1997zw} are added:

``The WW-type approximation is not preserved under $Q^2$ evolution.
 Some intuition can be obtained from the collinear case
 \cite{Ali:1991em,Koike:1994st,Balitsky:1996uh,Belitsky:1997zw}. 
 However, much less is known about the $k_\perp$-evolution especially at 
 subleading twist. More theoretical work is required here.''

\item
Sec.1, page 3, we replaced:

``study of all SIDIS structure functions up to twist-3 in a unique approach.''
$\to$\\
``study of all SIDIS structure functions up to twist-3 evaluated within one
common systematic theoretical guideline''

\item
Sec.1, page 3, we replaced the paragraph:

	``In App.~C we describe an open-source package implemented
	in \texttt{Mathematica}~\cite{Mathematica} (already available)
	and \texttt{Python} (to be released in the near future) that is
	made publicly available on \texttt{github.com}: {\href{
	https://github.com/prokudin/WW-SIDIS}{
	https://github.com/prokudin/WW-SIDIS}}''

by:

	``An open-source package is available which allows one to visualize 
	and reproduce the results presented in this work, and may easily 
	be adapted by interested colleagues for their purposes
	\cite{Mathematica}.''

and we removed App.~C.

\item
Sec.~2.1, Eq. 2.2: we absorbed the definition of the unpolarized lepton-quark 
subprocess cross section in the overall cross section formulas.

\item
Sec.~3.3, page 14: The sentence before Eq.~(3.8) is modified as:

	``For the $n = 3$ Mellin moments (i.e.\ the lowest non-trivial ones 
	for these tilde-functions) it was found $\dots$''

\item
Sec.~3.5, page 16: In the second paragraph we added a sentence refering 
to the latest developments concerning lattice:

``For the latest developments we refer the interested reader to Refs. [70Ð78]''

\item
Sec.~3.5, page 17: The first instance of the repetitive sentence 
starting with ``This assumption holds $\dots$'' is removed.

\item
Sec.~3.8, page 22: The paragraph is added:

``As it was mentioned in the Introduction
one important limitation concerns the fact that the WW-type approximations
are not preserved under $Q^2$ evolution. Still some intuition can be 
obtained from the collinear case: the evolution equations for $g_T^a(x)$ 
and $h_L^a(x)$ exhibit complicated mixing patterns typical for higher 
twist functions, which simplify to DGLAP-type evolutions in the limit 
of a large number of colors $N_c$ and in the limit of large-$x$ 
\cite{Ali:1991em,Koike:1994st,Balitsky:1996uh,Belitsky:1997zw}. 
These evolution equations differ from those of the leading-twist
functions $g_1^a(x)$ and $h_1^a(x)$. 
However, since $Q^2$ varies moderately in the considered experiments 
(e.g.\ for common values of $x$ the $Q^2$ at COMPASS is only about a factor 2-3
larger than at HERMES), this point is not a major uncertainty in our study.
More theoretical work will be required to understand $k_\perp$-evolution 
effects of subleading twist TMDs in future experiments (EIC) 
covering kinematic regions that vary by orders of magnitude in $Q^2$.''

\item
Sec. 5.2, page 29:
``We remark that HERMES and COMPASS data also show flat 
$P_{hT}$-distributions \cite{Airapetian:2018rlq,Adolph:2016vou}.''

\item
Sec. 5.3, page 30: the sign change of the Sivers asymmetry in hadron-hadron collisions 
is pointed out, including references to recent experimental results by STAR and COMPASS:

``The Sivers function is predicted to enter the description of hadron-hadron 
collisions (with transversely polarized protons) with an opposite sign 
compared to SIDIS \cite{Collins:2002kn,Brodsky:2002cx,Brodsky:2002rv}.
Recent results on single-spin asymmetries in weak-boson production 
from RHIC \cite{Adamczyk:2015gyk} and Drell--Yan from COMPASS 
\cite{Aghasyan:2017jop,Parsamyan:2018zju} are consistent 
with this prediction.''

\item
Sec. 5.4, page 30:
``Transversity can also be accessed as a PDF in Drell--Yan or dihadron 
production \cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,
Bacchetta:2012ty,Radici:2015mwa,Radici:2018iag}."

\item 
(Caption of) Fig.~7, page 31, removed the debated statement about the different sign 
conventions and plotted the COMPASS data using the conventions used here:

``Collins asymmetry for a proton target 
	vs $x$ based on the fit \cite{Anselmino:2013vqa}.
	(a) $A_{UT,  \langle y\rangle}^{\sin(\phi_h+\phi_S)}$ in comparison
	to HERMES \cite{Airapetian:2010ds} data.
	(b) $A_{UT}^{\sin(\phi_h+\phi_S)}$ in comparison
	to COMPASS \cite{Adolph:2014zba} data''

\item
Sec.~5.6, page 33 (our correction): we added $\langle\dots\rangle$
in the following in-line formula  
$A_{UT, \langle y \rangle}^{\sin(3 \phi_h - \phi_S)}=\langle
(1-y)F_{UT}^{\sin(3 \phi_h - \phi_S)}\rangle/\langle(1-y + y^2/2)F_{UU}\rangle$
to indicate that the kinematic variable $y$ is averaged over.

\item
Sec.~5.6, page 33, the text is removed:

 "A notable exception is COMPASS, where the largest $x$--bins
 (where $Q^2$ is largest) bear the best hints on this TMD,
 see Fig.~9."

\item
Captions of Figs.~9, 11, 12, 15, 16, 17, 19:
we added explanations why our curves cannot be added
on the plots provided by the COMPASS Collaboration.

``
[We remark that in this and several subsequent figures we have 
        the permission to show the preliminary data \cite{Parsamyan:2013fia} 
	only in the official figures provided by the COMPASS collaboration
 	in (a,b), and have to display our results separately in (d).
	Notice also the different scale on the y-axis in panel (d) 
	as compared to (a,b).]
"
\item
Sect.~7.2, caption of Fig.~14: added  ``where a different scale is chosen to better visualize the theory curves.''

\item
Sect.~7.4, third line (our correction): $F_{UL}^{\cos\phi_h}$ changed to $F_{LL}^{\cos\phi_h}$

\item
Fig.~18 (our correction):
the previous Fig.~18c was showing an estimate of the asymmetry
from an earlier (less consistent and superseded) way of using
the Gaussian model and applying the WW-type approximation, and 
we removed this plot. In the presently adopted scheme this
asymmetry vanishes as described in the caption of Fig.~18
and in Sec.~7.6.

\item
Fig.~20 (our correction): HEPDATA were used for the COMPASS results, which we realized have a bug. The plot got replaced using the original data tables from the COMPASS paper.

\item
Conclusions, page 47, the text is removed:

 ``The classic WW approximation for $g_2(x)$ works with a relative
 accuracy of $\pm\,40\,\%$ or better. This is remarkable."

 The following phrase is modified:

 ``on the positive site we also observe no alarming hints" $\to$\\
 ``on the positive side we also observe no hints"

\item 
The misprints are fixed, the consistent notation $m_h$ is used,
and several figures are rearranged and placed more accurately 
within the sections where they are discussed. We did minor
editing in several places (purely stylistic improvements), 
and used a $\log x$ scale also for the HERMES data at several places for consistency with COMPASS plots shown in the same figure.

\item   Acknowledgments, we added the remark:

We thank the COMPASS and HERMES Collaborations for the 
permissions to show their preliminary data on several figures.

\end{itemize}

% REMARK: 
%
% "When submitting the document source (.tex) file to external parties, 
% it is strongly recommended that the BIBTEX .bbl file be manually copied 
% into the document (within the traditional LATEX bibliography environment) 
% so as not to depend on external files to generate the bibliography and to
% prevent the possibility of changes occurring therein"
%
% This means: 
% STEP 1: compile with \bibliography{biblio_ww} as usual, 
% STEP 2: uncomment \bibliography{biblio_ww}
% STEP 3: paste the contents of the file reply-to-referee-v2C.bbl
%
%
% STEP 1: done
%
% STEP 2: uncommenting
% \bibliography{biblio_ww}
%
% STEP 3: pasting (yeah, it works ;-)
%

\providecommand{\href}[2]{#2}\begingroup\raggedright\begin{thebibliography}{1}

\bibitem{Ali:1991em}
A.~Ali, V.~M. Braun and G.~Hiller, \emph{{Asymptotic solutions of the evolution
  equation for the polarized nucleon structure function $g_2 (x, Q^2)$}},
  \href{http://dx.doi.org/10.1016/0370-2693(91)90753-D}{\emph{Phys. Lett.} {\bf
  B266} (1991) 117--125}.

\bibitem{Koike:1994st}
Y.~Koike and K.~Tanaka, \emph{{$Q^2 $evolution of nucleon's chiral odd
  twist-three structure function: $h_L (x, Q^2)$}},
  \href{http://dx.doi.org/10.1103/PhysRevD.51.6125}{\emph{Phys. Rev.} {\bf D51}
  (1995) 6125--6138}, [\href{https://arxiv.org/abs/hep-ph/9412310}{{\tt
  hep-ph/9412310}}].

\bibitem{Balitsky:1996uh}
I.~I. Balitsky, V.~M. Braun, Y.~Koike and K.~Tanaka, \emph{{$Q^2$ evolution of
  chiral odd twist-three distributions $h_L(x,Q^2)$ and $e(x,Q^2)$ in the large
  $N_c$ limit}},
  \href{http://dx.doi.org/10.1103/PhysRevLett.77.3078}{\emph{Phys. Rev. Lett.}
  {\bf 77} (1996) 3078--3081},
  [\href{https://arxiv.org/abs/hep-ph/9605439}{{\tt hep-ph/9605439}}].

\bibitem{Belitsky:1997zw}
A.~V. Belitsky and D.~{M\"u}ller, \emph{{Scale dependence of the chiral odd
  twist-three distributions $h_L(x)$ and $e(x)$}},
  \href{http://dx.doi.org/10.1016/S0550-3213(97)00432-X}{\emph{Nucl. Phys.}
  {\bf B503} (1997) 279--308},
  [\href{https://arxiv.org/abs/hep-ph/9702354}{{\tt hep-ph/9702354}}].

\bibitem{Bacchetta:2002ux}
A.~Bacchetta and M.~Radici, \emph{{Partial-wave analysis of two-hadron
  fragmentation functions}},
  \href{http://dx.doi.org/10.1103/PhysRevD.67.094002}{\emph{Phys. Rev.} {\bf
  D67} (2003) 094002}, [\href{https://arxiv.org/abs/hep-ph/0212300}{{\tt
  hep-ph/0212300}}].

\bibitem{Bacchetta:2003vn}
A.~Bacchetta and M.~Radici, \emph{{Two-hadron semi-inclusive production
  including subleading twist contributions}},
  \href{http://dx.doi.org/10.1103/PhysRevD.69.074026}{\emph{Phys. Rev.} {\bf
  D69} (2004) 074026}, [\href{https://arxiv.org/abs/hep-ph/0311173}{{\tt
  hep-ph/0311173}}].

\bibitem{Bacchetta:2011ip}
A.~Bacchetta, A.~Courtoy and M.~Radici, \emph{{First Glances at the
  Transversity Parton Distribution through Dihadron Fragmentation Functions}},
  \href{http://dx.doi.org/10.1103/PhysRevLett.107.012001}{\emph{Phys. Rev.
  Lett.} {\bf 107} (2011) 012001}, [\href{https://arxiv.org/abs/1104.3855}{{\tt
  1104.3855}}].

\bibitem{Bacchetta:2012ty}
A.~Bacchetta, A.~Courtoy and M.~Radici, \emph{{First extraction of valence
  transversities in a collinear framework}},
  \href{http://dx.doi.org/10.1007/JHEP03(2013)119}{\emph{JHEP} {\bf 03} (2013)
  119}, [\href{https://arxiv.org/abs/1212.3568}{{\tt 1212.3568}}].

\bibitem{Radici:2015mwa}
M.~Radici, A.~Courtoy, A.~Bacchetta and M.~Guagnelli, \emph{{Improved
  extraction of valence transversity distributions from inclusive dihadron
  production}}, \href{http://dx.doi.org/10.1007/JHEP05(2015)123}{\emph{JHEP}
  {\bf 05} (2015) 123}, [\href{https://arxiv.org/abs/1503.03495}{{\tt
  1503.03495}}].

\bibitem{Radici:2018iag}
M.~Radici and A.~Bacchetta, \emph{{First Extraction of Transversity from a
  Global Analysis of Electron-Proton and Proton-Proton Data}},
  \href{http://dx.doi.org/10.1103/PhysRevLett.120.192001}{\emph{Phys. Rev.
  Lett.} {\bf 120} (2018) 192001},
  [\href{https://arxiv.org/abs/1802.05212}{{\tt 1802.05212}}].
\bibitem{Airapetian:2018rlq}
{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Longitudinal
  double-spin asymmetries in semi-inclusive deep-inelastic scattering of
  electrons and positrons by protons and deuterons}},
  \href{https://arxiv.org/abs/1810.07054}{{\tt 1810.07054}}.

\bibitem{Adolph:2016vou}
{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{Azimuthal
  asymmetries of charged hadrons produced in high-energy muon scattering off
  longitudinally polarised deuterons}},
  \href{http://dx.doi.org/10.1140/epjc/s10052-018-6379-7}{\emph{Eur. Phys. J.}
  {\bf C78} (2018) 952}, [\href{https://arxiv.org/abs/1609.06062}{{\tt
  1609.06062}}].

\bibitem{Parsamyan:2013fia}
{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Transverse spin
  asymmetries at COMPASS: beyond Collins and Sivers effects}}, {\emph{PoS} {\bf
  DIS2013} (2013) 231}, [\href{https://arxiv.org/abs/1307.0183}{{\tt
  1307.0183}}].

\bibitem{Mathematica}
A.~Prokudin and K.~Tezgin, ``{Open-source packages with implementations of
  SIDIS structure functions in the WW-type approximation are publicly available
  on \texttt{github.com}: \\ in \texttt{Mathematica, {V}ersion 11.3} on {\href{
  https://github.com/prokudin/WW-SIDIS}{
  https://github.com/prokudin/WW-SIDIS}},\\ in \texttt{Python} on {\href{
  https://jeffersonlab.github.io/jam3d/_build/html/index.html}{
  https://jeffersonlab.github.io/jam3d/\_build/html/index.html}}}.''

\bibitem{Collins:2002kn}
J.~C. Collins, \emph{{Leading-twist single-transverse-spin asymmetries:
  Drell--Yan and deep-inelastic scattering}}, {\emph{Phys. Lett.} {\bf B536}
  (2002) 43--48}, [\href{https://arxiv.org/abs/hep-ph/0204004}{{\tt
  hep-ph/0204004}}].

\bibitem{Brodsky:2002cx}
S.~J. Brodsky, D.~S. Hwang and I.~Schmidt, \emph{{Final-state interactions and
  single-spin asymmetries in semi-inclusive deep inelastic scattering}},
  {\emph{Phys. Lett.} {\bf B530} (2002) 99--107},
  [\href{https://arxiv.org/abs/hep-ph/0201296}{{\tt hep-ph/0201296}}].

\bibitem{Brodsky:2002rv}
S.~J. Brodsky, D.~S. Hwang and I.~Schmidt, \emph{{Initial-state interactions
  and single-spin asymmetries in Drell-Yan processes}},
  \href{http://dx.doi.org/10.1016/S0550-3213(02)00617-X}{\emph{Nucl. Phys.}
  {\bf B642} (2002) 344--356},
  [\href{https://arxiv.org/abs/hep-ph/0206259}{{\tt hep-ph/0206259}}].

\bibitem{Adamczyk:2015gyk}
{\scshape STAR} collaboration, L.~Adamczyk et~al., \emph{{Measurement of the
  transverse single-spin asymmetry in $p^\uparrow+p \to W^{\pm}/Z^0$ at RHIC}},
  \href{http://dx.doi.org/10.1103/PhysRevLett.116.132301}{\emph{Phys. Rev.
  Lett.} {\bf 116} (2016) 132301},
  [\href{https://arxiv.org/abs/1511.06003}{{\tt 1511.06003}}].

\bibitem{Aghasyan:2017jop}
{\scshape COMPASS} collaboration, M.~Aghasyan et~al., \emph{{First Measurement
  of Transverse-Spin-Dependent Azimuthal Asymmetries in the Drell--Yan
  Process}},
  \href{http://dx.doi.org/10.1103/PhysRevLett.119.112002}{\emph{Phys. Rev.
  Lett.} {\bf 119} (2017) 112002},
  [\href{https://arxiv.org/abs/1704.00488}{{\tt 1704.00488}}].

\bibitem{Parsamyan:2018zju}
{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{First measurement of
  transverse-spin-dependent azimuthal asymmetries in the Drell-Yan process}},
  \href{http://dx.doi.org/10.22323/1.297.0243}{\emph{PoS} {\bf DIS2017} (2018)
  243}, [\href{https://arxiv.org/abs/1801.01487}{{\tt 1801.01487}}].

\bibitem{Anselmino:2013vqa}
M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia and A.~Prokudin,
  \emph{{Simultaneous extraction of transversity and Collins functions from new
  SIDIS and $e^{+}e^{-}$ data}},
  \href{http://dx.doi.org/10.1103/PhysRevD.87.094019}{\emph{Phys. Rev.} {\bf
  D87} (2013) 094019}, [\href{https://arxiv.org/abs/1303.3822}{{\tt
  1303.3822}}].

\bibitem{Airapetian:2010ds}
{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Effects of
  transversity in deep-inelastic scattering by polarized protons}},
  \href{http://dx.doi.org/10.1016/j.physletb.2010.08.012}{\emph{Phys. Lett.}
  {\bf B693} (2010) 11--16}, [\href{https://arxiv.org/abs/1006.4221}{{\tt
  1006.4221}}].

\bibitem{Adolph:2014zba}
{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{Collins and Sivers
  asymmetries in muonproduction of pions and kaons off transversely polarised
  protons}},
  \href{http://dx.doi.org/10.1016/j.physletb.2015.03.056}{\emph{Phys. Lett.}
  {\bf B744} (2015) 250--259}, [\href{https://arxiv.org/abs/1408.4405}{{\tt
  1408.4405}}].

\end{thebibliography}\endgroup

\end{document}

### 2019-04-30 arxiv2/test-WW-type-v2H.tex
AP

@@
 
-\ps{The WW-type approximation is not preserved under $Q^2$ evolution.
+The WW-type approximation is not preserved under $Q^2$ evolution.
 Some intuition can be obtained from the collinear case. However,
 much less is known about the $k_\perp$-evolution especially at 
-subleading twist. More theoretical work is required here.}
+subleading twist. More theoretical work is required here.
 
 The present work is the first 
-% study of all SIDIS structure functions up to twist-3 in a unique approach. 
-\ps{study of all SIDIS structure functions up to twist-3 evaluated within one
-common systematic theoretical guideline.}
+study of all SIDIS structure functions up to twist-3 evaluated within one
+common systematic theoretical guideline.
 Our results are of importance for measurements
@@
 technical details.
-\ps{	An open-source package is available which allows one to visualize 
+An open-source package is available which allows one to visualize 
 	and reproduce the results presented in this work, and may easily 
-	be adapted by \ak{interested colleagues for their purposes}
+	be adapted by interested colleagues for their purposes
 	\cite{Mathematica}.
-}
 
@@
    =	% \frac{1}{4\pi}\;\frac{d \hat{\sigma}}{dy}
-	\bp{\frac{\alpha_{em}^2}{x\,y\,Q^2}\biggl(1-y+\frac12y^2\biggr)}
+	\frac{\alpha_{em}^2}{x\,y\,Q^2}\biggl(1-y+\frac12y^2\biggr)
 	\;F_{UU}(x,z,\Phperp^2) 
@@
    =	%\frac{1}{4\pi} \; \frac{d \hat{\sigma}}{dy} 
-	\bp{\frac{\alpha_{em}^2}{x\,y\,Q^2}\biggl(1-y+\frac12y^2\biggr)}
+	\frac{\alpha_{em}^2}{x\,y\,Q^2}\biggl(1-y+\frac12y^2\biggr)
 	\; F_{UU}(x,z,\Phperp^2)
@@
 Neglecting $1/Q^2$ corrections, the kinematic prefactors $p_i$ are given by
-% \ba\label{Eq:y-prefactors}
-% &&	p_1 = \varepsilon \equiv
-%        \frac{1-y -\frac{1}{4}\slim \gamma^2 y^2}{1-y
-%        + \frac{1}{2}\slim y^2 +\frac{1}{4}\slim \gamma^2 y^2}
-%        \approx \frac{1-y}{1-y+\frac12\,y^2} 		\;,\nonumber\\
-% &&	p_2 = \sqrt{1-\epsilon^2} \approx
-%        \frac{y(1-\frac12\,y)}{1-y+\frac12\,y^2} 	\;,\nonumber\\
-% &&	p_3 =  \sqrt{2\varepsilon(1+\varepsilon)}
-%        \approx \frac{(2-y)\sqrt{1-y}}{1-y+\frac12\,y^2}\;,\nonumber\\
-% &&	p_4 =  \sqrt{2\varepsilon(1-\varepsilon)}
-%        \approx \frac{y\sqrt{1-y}}{1-y+\frac12\,y^2} 	\;,\;\;\;
-% \ea
 \be\label{Eq:y-prefactors}
@@
 The superscript ``weight'' indicates the azimuthal dependence with no index
-indicating \bp{a $\phi_h$-independent asymmetry or structure function.}
+indicating a $\phi_h$-independent asymmetry or structure function.
 
@@
 respective twist-2 parts, which are of order $(\rho/R)^0$.
-\gs{For the $n = 3$ Mellin moments (i.e.\ the lowest non-trivial ones for 
-these tilde-functions) it was found} \cite{Balla:1997hf,Dressler:1999hc}
+For the $n = 3$ Mellin moments (i.e.\ the lowest non-trivial ones for 
+these tilde-functions) it was found \cite{Balla:1997hf,Dressler:1999hc}
 \be\label{Eq:WW-instanoton}
@@
 progress and improvements with regard to rigor, realism and methodology.
-\Bernie{For the latest developments we refer the
+For the latest developments we refer the
 	interested reader to Refs.~\cite{Alexandrou:2017dzj,Ishikawa:2017faj,
@@
 	Musch:2011er,%Phys.Rev. D85 (2012) 094510
-   Ji:2017oey,Yoon:2017qzo,Green:2017xeu,Zhang:2017bzy}.}
+   Ji:2017oey,Yoon:2017qzo,Green:2017xeu,Zhang:2017bzy}.
 However, numerical results from recent calculations are only available
@@
 correctly. 
-\Bernie{This assumption holds if renormalization is multiplicative and
+This assumption holds if renormalization is multiplicative and
    flavor-independent for the non-local lattice operators. This is
-   not true for all lattice actions \cite{Yoon:2017qzo}. %PhysRevD.96.094508
-   % NOT \cite{Musch:2010ka}.
-   But presumably it is true
+   not true for all lattice actions \cite{Yoon:2017qzo}.    But presumably it is true
    if the lattice action preserves chiral symmetry, as it does in
-   the present case.} 
+   the present case.
 The Gaussian fits along with the normalization prescription serve as
@@
 
-\ak{As it was mentioned in the Introduction}
-\ps{one important limitation concerns the fact that the WW-type approximations
-are not preserved under $Q^2$ evolution. \ak{Still} some intuition can be 
+As it was mentioned in the Introduction
+one important limitation concerns the fact that the WW-type approximations
+are not preserved under $Q^2$ evolution. Still some intuition can be 
 obtained from the collinear case: the evolution equations for $g_T^a(x)$ 
@@
 functions $g_1^a(x)$ and $h_1^a(x)$. 
-% This point is of not much
-% practical relevance here, because the $Q^2$ varies only moderately
-% between JLab, HERMES, and COMPASS (except for the largest $x$-bins).
-% However, if for some reason the $\bar{q}gq$-terms were found to be
-% very small at one renormalization scale, it is not guaranteed the
-% WW-type approximation will work equally well also at other scales. 
-% More theoretical work is required, especially also in order to 
-% understand $k_\perp$-evolution effects at subleading twist.
-\bp{However, since $Q^2$ varies moderately in the considered experiments 
-(e.g.\ for common values of $x$ the $Q^2$ at COMPASS is only about \gs{a factor 2-3} 
+However, since $Q^2$ varies moderately in the considered experiments 
+(e.g.\ for common values of $x$ the $Q^2$ at COMPASS is only about a factor 2-3
 larger than at HERMES), this point is not a major uncertainty in our study.
@@
 effects of subleading twist TMDs in future experiments (EIC) 
-\gs{covering kinematic regions that vary by orders of magnitude in $Q^2$.}}}
+covering kinematic regions that vary by orders of magnitude in $Q^2$.
 
@@
 which confirms that the Gaussian model works also in this case.
-\bp{The Sivers function is predicted to enter the description of hadron-hadron 
+The Sivers function is predicted to enter the description of hadron-hadron 
 collisions (with transversely polarized protons) with an opposite sign 
@@
 \cite{Aghasyan:2017jop,Parsamyan:2018zju} are consistent 
-with this prediction.}
+with this prediction.
 
@@
 on the tensor charge of the nucleon. 
-\bp{Transversity can also be accessed as a PDF in Drell--Yan or dihadron 
+Transversity can also be accessed as a PDF in Drell--Yan or dihadron 
 production \cite{Bacchetta:2002ux,Bacchetta:2003vn,Bacchetta:2011ip,
-Bacchetta:2012ty,Radici:2015mwa,Radici:2018iag}.} 
-% The first polarized Drell--Yan data were measured by 
-% COMPASS~\cite{Aghasyan:2017jop,Parsamyan:2018zju}.
+Bacchetta:2012ty,Radici:2015mwa,Radici:2018iag}. 
 The Collins FF $H_1^\perp$ decodes the
@@
 	vs $x$ based on the fit \cite{Anselmino:2013vqa}.
-	(a) \bp{$A_{UT,  \langle y\rangle}^{\sin(\phi_h+\phi_S)}$ in comparison} 
+	(a) $A_{UT,  \langle y\rangle}^{\sin(\phi_h+\phi_S)}$ in comparison
 	to HERMES \cite{Airapetian:2010ds} data.
-	(b) \bp{$A_{UT}^{\sin(\phi_h+\phi_S)}$ in comparison} 
+	(b) $A_{UT}^{\sin(\phi_h+\phi_S)}$ in comparison 
 	to COMPASS \cite{Adolph:2014zba} data.}
@@
 	\cite{Kotzinian:2008fe,Boffi:2009sh}.
-        \ps{[We remark that in this and several subsequent figures we have 
+        [We remark that in this and several subsequent figures we have 
         the permission to show the preliminary data \cite{Parsamyan:2013fia} 
-	\gs{only in the official figures provided by the COMPASS collaboration}
+	only in the official figures provided by the COMPASS collaboration
  	in (a,b), and have to display our results separately in (d).
 	Notice also the different scale on the y-axis in panel (d) 
-	as compared to (a,b).]}}
+	as compared to (a,b).]}
 \end{figure}
@@
 preliminary HERMES data \cite{Schnell:2010zza} for$
-A_{UT, \langle y \rangle}^{\sin(3 \phi_h - \phi_S)}=\ps{\la
-(1-y)F_{UT}^{\sin(3 \phi_h - \phi_S)}\ra/\la(1-y + y^2/2)F_{UU}\ra}$
+A_{UT, \langle y \rangle}^{\sin(3 \phi_h - \phi_S)}=\la
+(1-y)F_{UT}^{\sin(3 \phi_h - \phi_S)}\ra/\la(1-y + y^2/2)F_{UU}\ra$
 are plotted in Fig.~\ref{aut_h1tp_jlab}. 
@@
 	and our calculation for COMPASS kinematics (c)
-	\ps{shown separately for reasons explained in the
-	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.}}
+	shown separately for reasons explained in the
+	caption of Fig.~\ref{aut_h1tp_jlab}.}
 \end{figure}
@@
 	for COMPASS kinematics in the WW-type approximation (d)
-	\ps{shown separately for reasons explained in the
-	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.} Results
+	shown separately for reasons explained in the
+	caption of Fig.~\ref{aut_h1tp_jlab}. Results
 	from \cite{Avakian:2007mv} are also shown in comparison to the 
@@
 	proton target \cite{Parsamyan:2013fia} (a,b),  and our 
-	calculation for COMPASS kinematics (c) \ps{where a different 
-	scale is chosen to better visualize the theory curves.}}
+	calculation for COMPASS kinematics (c) where a different 
+	scale is chosen to better visualize the theory curves.}
 \end{figure}
@@
 	and our calculation for COMPASS kinematics (c)
-	\ps{shown separately for reasons explained in the
-	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.}}
-	% The smallness of this asymmetry has two natural reasons: first, 
-    	% being twist-3 it is $M_N/Q$ suppressed; and second, it is 
-	% proportional to $P_{hT}^2$  in TMD approach.
+	shown separately for reasons explained in the
+	caption of Fig.~\ref{aut_h1tp_jlab}.}
 \end{figure}
@@
 the Gaussian width $\avkperp_{g_{L}^\perp}=\avkperp_{g_1}$.
-The structure function \bp{$F_{LL}^{\cos\phi_h}$} reads
+The structure function $F_{LL}^{\cos\phi_h}$ reads
 \begin{subequations}\ba
@@
 	WW-type approximation (c)
-	\ps{shown separately for reasons explained in the
-	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.}}
+	shown separately for reasons explained in the
+	caption of Fig.~\ref{aut_h1tp_jlab}.}
 \end{figure}
@@
 	WW-type approximation (e)
-	\ps{shown separately for reasons explained in the
-	caption \gs{of} Fig.~\ref{aut_h1tp_jlab}.}}
+	shown separately for reasons explained in the
+	caption of Fig.~\ref{aut_h1tp_jlab}.}
 \end{figure}
@@
 
-%Also in this asymmetry we end up with more than one contribution
-%surviving the WW-type approximation. We assume Gaussian Ansatz for
-%$f_T^{\perp q}(x,\kperp)$, $h_T^{\perp q}(x,\kperp)$, and $h_T^q(x,\kperp)$,
-%according to (\ref{eq:hTperpnew},~\ref{eq:hTnew},~\ref{eq:ftperpnew})
-%in App.~\ref{App-B:Gauss-Ansatz-non-basis-TMDs}, with
-%$\la\kperp^2\ra_{h_T^\perp}=\la\kperp^2\ra_{h_T^{ }}=\la\kperp^2\ra_{h_{1T}^\perp}$
-%and $\la\kperp^2\ra_{f_T^\perp}=\la\kperp^2\ra_{f_{1T}^\perp}$. The 
-%expressions obtained are given by
-
-\ps{In this asymmetry, two terms survive the WW-type approximation.
-Using the} Gaussian Ansatz for
+In this asymmetry, two terms survive the WW-type approximation.
+Using the Gaussian Ansatz for
 $f_T^{\perp q}(x,\kperp^{2})$, $h_T^{\perp q}(x,\kperp^{2})$, $h_T^q(x,\kperp^{2})$,
@@
 and $\la\kperp^2\ra_{f_T^\perp}=\la\kperp^2\ra_{f_{1T}^\perp}$
-\ps{yields} the expressions 
+yields the expressions 
 \begin{subequations}\begin{alignat}{1}
@@
 	preliminary COMPASS data~\cite{Parsamyan:2013fia} (a,b)
-  \gs{and our calculation for COMPASS kinematics in WW-type 
+  and our calculation for COMPASS kinematics in WW-type 
       approximation (c) shown separately for reasons explained 
-      in the caption of Fig.~\ref{aut_h1tp_jlab}.}
+      in the caption of Fig.~\ref{aut_h1tp_jlab}.
 	Similarly $A_{UT, \langle y \rangle}^{\sin(2\phi_h-\phi_S)}(x)$ vs
@@
 for the applicability of the WW-type approximations, but
-on the \ps{positive side we also observe no hints}
+on the positive side we also observe no hints
 that the WW-type approximations fail in these cases.
@@
 To the best of our knowledge, it is the first complete study of all SIDIS
-structure functions up to twist-3 % in a unique approach. 
-\ps{using systematically a common theoretical guideline.}
+structure functions up to twist-3 
+using systematically a common theoretical guideline.
 The results are
@@
 Contract No.\ PHY-1406298 (P.S.), and the Wilhelm Schuler Stiftung (P.S.).
-\ps{We thank the COMPASS and HERMES Collaborations for the 
-permissions to show their preliminary data on several figures.}
+We thank the COMPASS and HERMES Collaborations for the 
+permissions to show their preliminary data on several figures.
 

### 2019-05-02 arxiv2/test-WW-type-v2H.tex
AP

@@
 	approximation, indeed already probing DIS \cite{Avakian:2010ae}.)
-\bp{We remark that HERMES and COMPASS data also show flat 
-$P_{hT}$-distributions \cite{Airapetian:2018rlq,Adolph:2016vou}.}
+We remark that HERMES and COMPASS data also show flat 
+$P_{hT}$-distributions \cite{Airapetian:2018rlq,Adolph:2016vou}.
 
@@
 
-\bibliography{\BibPath/biblio_ww}
+\providecommand{\href}[2]{#2}\begingroup\raggedright\begin{thebibliography}{100}
+
+\bibitem{Kotzinian:1994dv}
+A.~Kotzinian, \emph{{New quark distributions and semiinclusive
+  electroproduction on the polarized nucleons}},
+  \href{http://dx.doi.org/10.1016/0550-3213(95)00098-D}{\emph{Nucl. Phys.} {\bf
+  B441} (1995) 234--248}, [\href{https://arxiv.org/abs/hep-ph/9412283}{{\tt
+  hep-ph/9412283}}].
+
+\bibitem{Mulders:1995dh}
+P.~J. Mulders and R.~D. Tangerman, \emph{{The complete tree-level result up to
+  order 1/Q for polarized deep-inelastic leptoproduction}},
+  \href{http://dx.doi.org/10.1016/0550-3213(95)00632-X}{\emph{Nucl. Phys.} {\bf
+  B461} (1996) 197--237}, [\href{https://arxiv.org/abs/hep-ph/9510301}{{\tt
+  hep-ph/9510301}}].
+
+\bibitem{Boer:1997nt}
+D.~Boer and P.~J. Mulders, \emph{{Time-reversal odd distribution functions in
+  leptoproduction}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.57.5780}{\emph{Phys. Rev.} {\bf D57}
+  (1998) 5780--5786}, [\href{https://arxiv.org/abs/hep-ph/9711485}{{\tt
+  hep-ph/9711485}}].
+
+\bibitem{Goeke:2005hb}
+K.~Goeke, A.~Metz and M.~Schlegel, \emph{{Parameterization of the quark--quark
+  correlator of a spin-1/2 hadron}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2005.05.037}{\emph{Phys. Lett.}
+  {\bf B618} (2005) 90--96}, [\href{https://arxiv.org/abs/hep-ph/0504130}{{\tt
+  hep-ph/0504130}}].
+
+\bibitem{Bacchetta:2006tn}
+A.~Bacchetta, M.~Diehl, K.~Goeke, A.~Metz, P.~J. Mulders and M.~Schlegel,
+  \emph{{Semi-inclusive deep inelastic scattering at small transverse
+  momentum}},
+  \href{http://dx.doi.org/10.1088/1126-6708/2007/02/093}{\emph{JHEP} {\bf 02}
+  (2007) 093}, [\href{https://arxiv.org/abs/hep-ph/0611265}{{\tt
+  hep-ph/0611265}}].
+
+\bibitem{Stock:1994vv}
+F.~Stock et~al., \emph{{The FILTEX / HERMES polarized hydrogen atomic beam
+  source}}, \href{http://dx.doi.org/10.1016/0168-9002(94)90210-0}{\emph{Nucl.
+  Instrum. Meth.} {\bf A343} (1994) 334--342}.
+
+\bibitem{Airapetian:2004yf}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{The HERMES
+  polarized hydrogen and deuterium gas target in the HERA electron storage
+  ring}}, \href{http://dx.doi.org/10.1016/j.nima.2004.11.020}{\emph{Nucl.
+  Instrum. Meth.} {\bf A540} (2005) 68--101},
+  [\href{https://arxiv.org/abs/physics/0408137}{{\tt physics/0408137}}].
+
+\bibitem{Crabb:1997cy}
+D.~G. Crabb and W.~Meyer, \emph{{Solid polarized targets for nuclear and
+  particle physics experiments}},
+  \href{http://dx.doi.org/10.1146/annurev.nucl.47.1.67}{\emph{Ann. Rev. Nucl.
+  Part. Sci.} {\bf 47} (1997) 67--109}.
+
+\bibitem{Goertz:2002vv}
+S.~Goertz, W.~Meyer and G.~Reicherz, \emph{{Polarized H, D and $^{3}$He targets
+  for particle physics experiments}},
+  \href{http://dx.doi.org/10.1016/S0146-6410(02)00159-X}{\emph{Prog. Part.
+  Nucl. Phys.} {\bf 49} (2002) 403--489}.
+
+\bibitem{Arnold:2008kf}
+S.~Arnold, A.~Metz and M.~Schlegel, \emph{{Dilepton production from polarized
+  hadron hadron collisions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.79.034005}{\emph{Phys. Rev.} {\bf
+  D79} (2009) 034005}, [\href{https://arxiv.org/abs/0809.2262}{{\tt
+  0809.2262}}].
+
+\bibitem{Metz:2016swz}
+A.~Metz and A.~Vossen, \emph{{Parton fragmentation functions}},
+  \href{http://dx.doi.org/10.1016/j.ppnp.2016.08.003}{\emph{Prog. Part. Nucl.
+  Phys.} {\bf 91} (2016) 136--202},
+  [\href{https://arxiv.org/abs/1607.02521}{{\tt 1607.02521}}].
+
+\bibitem{Miller:2007ae}
+G.~A. Miller, \emph{{Densities, parton distributions, and measuring the
+  nonspherical shape of the nucleon}},
+  \href{http://dx.doi.org/10.1103/PhysRevC.76.065209}{\emph{Phys. Rev.} {\bf
+  C76} (2007) 065209}, [\href{https://arxiv.org/abs/0708.2297}{{\tt
+  0708.2297}}].
+
+\bibitem{Burkardt:2007rv}
+M.~Burkardt, \emph{{Spin-orbit correlations and single-spin asymmetries}},  in
+  \emph{{Workshop on Exclusive Reactions at High Momentum Transfer Newport
+  News, Virginia, May 21-24, 2007}}, 2007.
+\newblock \href{https://arxiv.org/abs/0709.2966}{{\tt 0709.2966}}.
+
+\bibitem{Burkardt:2009rf}
+M.~Burkardt, \emph{{The $g_{2}$ Structure Function}},
+  \href{http://dx.doi.org/10.1063/1.3203298}{\emph{AIP Conf.Proc.} {\bf 1155}
+  (2009) 26--34}, [\href{https://arxiv.org/abs/0905.4079}{{\tt 0905.4079}}].
+
+\bibitem{Bacchetta:1999kz}
+A.~Bacchetta, M.~Boglione, A.~Henneman and P.~J. Mulders, \emph{{Bounds on
+  Transverse Momentum Dependent Distribution and Fragmentation Functions}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.85.712}{\emph{Phys. Rev. Lett.}
+  {\bf 85} (2000) 712--715}, [\href{https://arxiv.org/abs/hep-ph/9912490}{{\tt
+  hep-ph/9912490}}].
+
+\bibitem{Wandzura:1977qf}
+S.~Wandzura and F.~Wilczek, \emph{{Sum rules for spin-dependent
+  electroproduction: Test of relativistic constituent quarks}},
+  \href{http://dx.doi.org/10.1016/0370-2693(77)90700-6}{\emph{Phys. Lett.} {\bf
+  B72} (1977) 195}.
+
+\bibitem{Jaffe:1991ra}
+R.~Jaffe and X.~Ji, \emph{{Chiral-odd parton distributions and Drell--Yan
+  processes}},
+  \href{http://dx.doi.org/10.1016/0550-3213(92)90110-W}{\emph{Nucl. Phys.} {\bf
+  B375} (1992) 527--560}.
+
+\bibitem{Jaffe:1989xx}
+R.~L. Jaffe, \emph{{$g_{2}$-The Nucleon's Other Spin-Dependent Structure
+  Function}}, {\emph{Comments Nucl. Part. Phys.} {\bf 19} (1990) 239--257}.
+
+\bibitem{Balla:1997hf}
+J.~Balla, M.~V. Polyakov and C.~Weiss, \emph{{Nucleon matrix elements of
+  higher-twist operators from the instanton vacuum}},
+  \href{http://dx.doi.org/10.1016/S0550-3213(98)00638-5}{\emph{Nucl. Phys.}
+  {\bf B510} (1998) 327--364},
+  [\href{https://arxiv.org/abs/hep-ph/9707515}{{\tt hep-ph/9707515}}].
+
+\bibitem{Dressler:1999hc}
+B.~Dressler and M.~V. Polyakov, \emph{{Twist-three contribution to $h_{L}$ in
+  the instanton vacuum}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.61.097501}{\emph{Phys. Rev.} {\bf
+  D61} (2000) 097501}, [\href{https://arxiv.org/abs/hep-ph/9912376}{{\tt
+  hep-ph/9912376}}].
+
+\bibitem{Gockeler:2000ja}
+M.~G{\"o}ckeler, R.~Horsley, W.~K{\"u}rzinger, H.~Oelrich, D.~Pleiter et~al.,
+  \emph{{Lattice calculation of the nucleon's spin-dependent structure function
+  $g_{2}$ reexamined}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.63.074506}{\emph{Phys. Rev.} {\bf
+  D63} (2001) 074506}, [\href{https://arxiv.org/abs/hep-lat/0011091}{{\tt
+  hep-lat/0011091}}].
+
+\bibitem{Gockeler:2005vw}
+M.~G{\"o}ckeler, R.~Horsley, D.~Pleiter, P.~E. Rakow, A.~Sch{\"a}fer et~al.,
+  \emph{{Investigation of the second moment of the nucleon's $g_{1}$ and
+  $g_{2}$ structure functions in two-flavor lattice QCD}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.72.054507}{\emph{Phys. Rev.} {\bf
+  D72} (2005) 054507}, [\href{https://arxiv.org/abs/hep-lat/0506017}{{\tt
+  hep-lat/0506017}}].
+
+\bibitem{Abe:1998wq}
+{\scshape E143} collaboration, K.~Abe et~al., \emph{{Measurements of the proton
+  and deuteron spin structure functions $g_{1}$ and $g_{2}$}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.58.112003}{\emph{Phys. Rev.} {\bf
+  D58} (1998) 112003}, [\href{https://arxiv.org/abs/hep-ph/9802357}{{\tt
+  hep-ph/9802357}}].
+
+\bibitem{Anthony:2002hy}
+{\scshape E155} collaboration, P.~L. Anthony et~al., \emph{{Precision
+  measurement of the proton and deuteron spin structure functions $g_{2}$ and
+  asymmetries $A_{2}$}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(02)03015-0}{\emph{Phys. Lett.}
+  {\bf B553} (2003) 18--24}, [\href{https://arxiv.org/abs/hep-ex/0204028}{{\tt
+  hep-ex/0204028}}].
+
+\bibitem{Airapetian:2011wu}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Measurement of
+  the virtual-photon asymmetry $A_2$ and the spin-structure function $g_2$ of
+  the proton}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-012-1921-5}{\emph{Eur. Phys. J.}
+  {\bf C72} (2012) 1921}, [\href{https://arxiv.org/abs/1112.5584}{{\tt
+  1112.5584}}].
+
+\bibitem{Kotzinian:1995cz}
+A.~M. Kotzinian and P.~J. Mulders, \emph{{Longitudinal quark polarization in
+  transversely polarized nucleons}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.54.1229}{\emph{Phys. Rev.} {\bf D54}
+  (1996) 1229--1232}, [\href{https://arxiv.org/abs/hep-ph/9511420}{{\tt
+  hep-ph/9511420}}].
+
+\bibitem{Kotzinian:1997wt}
+A.~M. Kotzinian and P.~J. Mulders, \emph{{Probing transverse quark polarization
+  via azimuthal asymmetries in leptoproduction}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(97)00708-9}{\emph{Phys. Lett.}
+  {\bf B406} (1997) 373--380},
+  [\href{https://arxiv.org/abs/hep-ph/9701330}{{\tt hep-ph/9701330}}].
+
+\bibitem{Kotzinian:2006dw}
+A.~Kotzinian, B.~Parsamyan and A.~Prokudin, \emph{{Predictions for double spin
+  asymmetry $A_{LT}$ in semiinclusive DIS}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.73.114017}{\emph{Phys. Rev.} {\bf
+  D73} (2006) 114017}, [\href{https://arxiv.org/abs/hep-ph/0603194}{{\tt
+  hep-ph/0603194}}].
+
+\bibitem{Avakian:2007mv}
+H.~Avakian et~al., \emph{{Are there approximate relations among transverse
+  momentum dependent distribution functions?}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.77.014023}{\emph{Phys. Rev.} {\bf
+  D77} (2008) 014023}, [\href{https://arxiv.org/abs/0709.3253}{{\tt
+  0709.3253}}].
+
+\bibitem{Metz:2008ib}
+A.~Metz, P.~Schweitzer and T.~Teckentrup, \emph{{Lorentz invariance relations
+  between parton distributions and the Wandzura--Wilczek approximation}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2009.08.052}{\emph{Phys. Lett.}
+  {\bf B680} (2009) 141--147}, [\href{https://arxiv.org/abs/0810.5212}{{\tt
+  0810.5212}}].
+
+\bibitem{Teckentrup:2009tk}
+T.~Teckentrup, A.~Metz and P.~Schweitzer, \emph{{Lorentz invariance relations
+  and Wandzura--Wilczek approximation}},
+  \href{http://dx.doi.org/10.1142/S0217732309001169}{\emph{Mod. Phys. Lett.}
+  {\bf A24} (2009) 2950--2959}, [\href{https://arxiv.org/abs/0910.2567}{{\tt
+  0910.2567}}].
+
+\bibitem{Tangerman:1994bb}
+R.~Tangerman and P.~Mulders, \emph{{Polarized twist-three distributions $g_{T}$
+  and $h_{L}$ and the role of intrinsic transverse momentum}},
+  \href{https://arxiv.org/abs/hep-ph/9408305}{{\tt hep-ph/9408305}}.
+
+\bibitem{Avakian:2015vha}
+H.~Avakian, H.~Matevosyan, B.~Pasquini and P.~Schweitzer, \emph{{Studying the
+  information content of TMDs using Monte Carlo generators}},
+  \href{http://dx.doi.org/10.1088/0954-3899/42/3/034015}{\emph{J. Phys.} {\bf
+  G42} (2015) 034015}.
+
+\bibitem{Metz:2004je}
+A.~Metz and M.~Schlegel, \emph{{Twist-3 single-spin asymmetries in
+  semi-inclusive deep-inelastic scattering}},
+  \href{http://dx.doi.org/10.1140/epja/i2004-10050-8}{\emph{Eur. Phys. J.} {\bf
+  A22} (2004) 489--494}, [\href{https://arxiv.org/abs/hep-ph/0403182}{{\tt
+  hep-ph/0403182}}].
+
+\bibitem{Gamberg:2006ru}
+L.~P. Gamberg, D.~S. Hwang, A.~Metz and M.~Schlegel, \emph{{Light-cone
+  divergence in twist-3 correlation functions}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2006.07.005}{\emph{Phys. Lett.}
+  {\bf B639} (2006) 508--512},
+  [\href{https://arxiv.org/abs/hep-ph/0604022}{{\tt hep-ph/0604022}}].
+
+\bibitem{Mathematica}
+A.~Prokudin and K.~Tezgin, ``{Open-source packages with implementations of
+  SIDIS structure functions in the WW-type approximation are publicly available
+  on \texttt{github.com}: \\ in \texttt{Mathematica, {V}ersion 11.3} on {\href{
+  https://github.com/prokudin/WW-SIDIS}{
+  https://github.com/prokudin/WW-SIDIS}},\\ in \texttt{Python} on {\href{
+  https://jeffersonlab.github.io/jam3d/_build/html/index.html}{
+  https://jeffersonlab.github.io/jam3d/\_build/html/index.html}}}.''
+
+\bibitem{Collins:2002kn}
+J.~C. Collins, \emph{{Leading-twist single-transverse-spin asymmetries:
+  Drell--Yan and deep-inelastic scattering}}, {\emph{Phys. Lett.} {\bf B536}
+  (2002) 43--48}, [\href{https://arxiv.org/abs/hep-ph/0204004}{{\tt
+  hep-ph/0204004}}].
+
+\bibitem{Ralston:1979ys}
+J.~P. Ralston and D.~E. Soper, \emph{{Production of Dimuons from High-Energy
+  Polarized Proton Proton Collisions}},
+  \href{http://dx.doi.org/10.1016/0550-3213(79)90082-8}{\emph{Nucl. Phys.} {\bf
+  B152} (1979) 109}.
+
+\bibitem{Collins:1981uk}
+J.~C. Collins and D.~E. Soper, \emph{{Back-To-Back Jets in QCD}},
+  \href{http://dx.doi.org/10.1016/0550-3213(81)90339-4}{\emph{Nucl. Phys.} {\bf
+  B193} (1981) 381}.
+
+\bibitem{Ji:2004wu}
+X.~Ji, J.-P. Ma and F.~Yuan, \emph{{QCD factorization for semi-inclusive
+  deep-inelastic scattering at low transverse momentum}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.71.034005}{\emph{Phys. Rev.} {\bf
+  D71} (2005) 034005}, [\href{https://arxiv.org/abs/hep-ph/0404183}{{\tt
+  hep-ph/0404183}}].
+
+\bibitem{Ji:2004xq}
+X.~Ji, J.-P. Ma and F.~Yuan, \emph{{QCD factorization for spin-dependent cross
+  sections in DIS and Drell-Yan processes at low transverse momentum}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2004.07.026}{\emph{Phys. Lett.}
+  {\bf B597} (2004) 299--308},
+  [\href{https://arxiv.org/abs/hep-ph/0405085}{{\tt hep-ph/0405085}}].
+
+\bibitem{Collins:2011zzd}
+J.~Collins, \emph{{Foundations of perturbative QCD}}, {\emph{Camb. Monogr.
+  Part. Phys. Nucl. Phys. Cosmol.} {\bf 32} (2011) 1--624}.
+
+\bibitem{Echevarria:2012js}
+M.~G. Echevarr\'ia, A.~Idilbi and I.~Scimemi, \emph{{Soft and collinear
+  factorization and transverse momentum dependent parton distribution
+  functions}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2013.09.003}{\emph{Phys. Lett.}
+  {\bf B726} (2013) 795--801}, [\href{https://arxiv.org/abs/1211.1947}{{\tt
+  1211.1947}}].
+
+\bibitem{Aybat:2011zv}
+S.~M. Aybat and T.~C. Rogers, \emph{{TMD Parton Distribution and Fragmentation
+  Functions with QCD Evolution}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.83.114042}{\emph{Phys. Rev.} {\bf
+  D83} (2011) 114042}, [\href{https://arxiv.org/abs/1101.5057}{{\tt
+  1101.5057}}].
+
+\bibitem{Aybat:2011ge}
+S.~M. Aybat, J.~C. Collins, J.-W. Qiu and T.~C. Rogers, \emph{{The QCD
+  Evolution of the Sivers Function}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.85.034043}{\emph{Phys. Rev.} {\bf
+  D85} (2012) 034043}, [\href{https://arxiv.org/abs/1110.6428}{{\tt
+  1110.6428}}].
+
+\bibitem{Echevarria:2014xaa}
+M.~G. Echevarria, A.~Idilbi, Z.-B. Kang and I.~Vitev, \emph{{QCD Evolution of
+  the Sivers Asymmetry}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.89.074013}{\emph{Phys. Rev.} {\bf
+  D89} (2014) 074013}, [\href{https://arxiv.org/abs/1401.5078}{{\tt
+  1401.5078}}].
+
+\bibitem{Collins:2014jpa}
+J.~Collins and T.~Rogers, \emph{{Understanding the large-distance behavior of
+  transverse-momentum-dependent parton densities and the Collins-Soper
+  evolution kernel}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.91.074020}{\emph{Phys. Rev.} {\bf
+  D91} (2015) 074020}, [\href{https://arxiv.org/abs/1412.3820}{{\tt
+  1412.3820}}].
+
+\bibitem{Ma:2013aca}
+J.~P. Ma and G.~P. Zhang, \emph{{QCD corrections of all structure functions in
+  transverse momentum dependent factorization for Drell--Yan processes}},
+  \href{http://dx.doi.org/10.1007/JHEP02(2014)100}{\emph{JHEP} {\bf 02} (2014)
+  100}, [\href{https://arxiv.org/abs/1308.2044}{{\tt 1308.2044}}].
+
+\bibitem{Aybat:2011ta}
+S.~M. Aybat, A.~Prokudin and T.~C. Rogers, \emph{{Calculation of TMD Evolution
+  for Transverse Single Spin Asymmetry Measurements}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.108.242003}{\emph{Phys. Rev.
+  Lett.} {\bf 108} (2012) 242003}, [\href{https://arxiv.org/abs/1112.4423}{{\tt
+  1112.4423}}].
+
+\bibitem{Kang:2015msa}
+Z.-B. Kang, A.~Prokudin, P.~Sun and F.~Yuan, \emph{{Extraction of quark
+  transversity distribution and Collins fragmentation functions with QCD
+  evolution}}, \href{http://dx.doi.org/10.1103/PhysRevD.93.014009}{\emph{Phys.
+  Rev.} {\bf D93} (2016) 014009}, [\href{https://arxiv.org/abs/1505.05589}{{\tt
+  1505.05589}}].
+
+\bibitem{Gutierrez-Reyes:2017glx}
+D.~Gutiérrez-Reyes, I.~Scimemi and A.~A. Vladimirov, \emph{{Twist-2 matching of
+  transverse momentum dependent distributions}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2017.03.031}{\emph{Phys. Lett.}
+  {\bf B769} (2017) 84--89}, [\href{https://arxiv.org/abs/1702.06558}{{\tt
+  1702.06558}}].
+
+\bibitem{Gutierrez-Reyes:2018qez}
+D.~Gutierrez-Reyes, I.~Scimemi, W.~J. Waalewijn and L.~Zoppi,
+  \emph{{Transverse-Momentum-Dependent Distributions with Jets}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.121.162001}{\emph{Phys. Rev.
+  Lett.} {\bf 121} (2018) 162001},
+  [\href{https://arxiv.org/abs/1807.07573}{{\tt 1807.07573}}].
+
+\bibitem{Scimemi:2018mmi}
+I.~Scimemi and A.~Vladimirov, \emph{{Matching of transverse momentum dependent
+  distributions at twist-3}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-018-6263-5}{\emph{Eur. Phys. J.}
+  {\bf C78} (2018) 802}, [\href{https://arxiv.org/abs/1804.08148}{{\tt
+  1804.08148}}].
+
+\bibitem{Chen:2016hgw}
+A.~P. Chen and J.~P. Ma, \emph{{Light-cone singularities and
+  transverse-momentum-dependent factorization at twist-3}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2017.03.015}{\emph{Phys. Lett.}
+  {\bf B768} (2017) 380--386}, [\href{https://arxiv.org/abs/1610.08634}{{\tt
+  1610.08634}}].
+
+\bibitem{Efremov:2002qh}
+A.~V. Efremov and P.~Schweitzer, \emph{{The chirally-odd twist-3 distribution
+  $e^{a}(x)$}},
+  \href{http://dx.doi.org/10.1088/1126-6708/2003/08/006}{\emph{JHEP} {\bf 08}
+  (2003) 006}, [\href{https://arxiv.org/abs/hep-ph/0212044}{{\tt
+  hep-ph/0212044}}].
+
+\bibitem{Jaffe:1996zw}
+R.~L. Jaffe, \emph{{Spin, twist and hadron structure in deep inelastic
+  processes}},  in \emph{{The spin structure of the nucleon. Proceedings,
+  International School of Nucleon Structure, 1st Course, Erice, Italy, August
+  3-10, 1995}}, pp.~42--129, 1996.
+\newblock \href{https://arxiv.org/abs/hep-ph/9602236}{{\tt hep-ph/9602236}}.
+
+\bibitem{Kanazawa:2015ajw}
+K.~Kanazawa, Y.~Koike, A.~Metz, D.~Pitonyak and M.~Schlegel, \emph{{Operator
+  constraints for twist-3 functions and Lorentz invariance properties of
+  twist-3 observables}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.93.054024}{\emph{Phys. Rev.} {\bf
+  D93} (2016) 054024}, [\href{https://arxiv.org/abs/1512.07233}{{\tt
+  1512.07233}}].
+
+\bibitem{Shuryak:1981ff}
+E.~V. Shuryak, \emph{{The role of instantons in quantum chromodynamics: (I).
+  Physical vacuum}},
+  \href{http://dx.doi.org/10.1016/0550-3213(82)90478-3}{\emph{Nucl. Phys.} {\bf
+  B203} (1982) 93}.
+
+\bibitem{Diakonov:1983hh}
+D.~Diakonov and V.~Y. Petrov, \emph{{Instanton-based vacuum from Feynman
+  variational principle}},
+  \href{http://dx.doi.org/10.1016/0550-3213(84)90432-2}{\emph{Nucl. Phys.} {\bf
+  B245} (1984) 259}.
+
+\bibitem{Diakonov:1995qy}
+D.~Diakonov, M.~V. Polyakov and C.~Weiss, \emph{{Hadronic matrix elements of
+  gluon operators in the instanton vacuum}},
+  \href{http://dx.doi.org/10.1016/0550-3213(95)00675-3}{\emph{Nucl. Phys.} {\bf
+  B461} (1996) 539--580}, [\href{https://arxiv.org/abs/hep-ph/9510232}{{\tt
+  hep-ph/9510232}}].
+
+\bibitem{Adams:1994id}
+{\scshape Spin Muon} collaboration, D.~Adams et~al., \emph{{Spin asymmetry in
+  muon-proton deep inelastic scattering on a transversely polarized target}},
+  \href{http://dx.doi.org/10.1016/0370-2693(94)00968-6}{\emph{Phys. Lett.} {\bf
+  B336} (1994) 125--130}, [\href{https://arxiv.org/abs/hep-ex/9408001}{{\tt
+  hep-ex/9408001}}].
+
+\bibitem{Accardi:2009au}
+A.~Accardi, A.~Bacchetta, W.~Melnitchouk and M.~Schlegel, \emph{{What can break
+  the Wandzura--Wilczek relation?}},
+  \href{http://dx.doi.org/10.1088/1126-6708/2009/11/093}{\emph{JHEP} {\bf 11}
+  (2009) 093}, [\href{https://arxiv.org/abs/0907.2942}{{\tt 0907.2942}}].
+
+\bibitem{Gluck:1998xa}
+M.~Gl{\"u}ck, E.~Reya and A.~Vogt, \emph{{Dynamical parton distributions
+  revisited}}, \href{http://dx.doi.org/10.1007/s100520050289}{\emph{Eur. Phys.
+  J.} {\bf C5} (1998) 461--470},
+  [\href{https://arxiv.org/abs/hep-ph/9806404}{{\tt hep-ph/9806404}}].
+
+\bibitem{Efremov:2006qm}
+A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Collins effect in
+  semiinclusive deeply inelastic scattering and in
+  electron-positron-annihilation}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.73.094025}{\emph{Phys. Rev.} {\bf
+  D73} (2006) 094025}, [\href{https://arxiv.org/abs/hep-ph/0603054}{{\tt
+  hep-ph/0603054}}].
+
+\bibitem{Anselmino:2007fs}
+M.~Anselmino et~al., \emph{{Transversity and Collins functions from SIDIS and
+  $e^{+} e^{-}$ data}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.75.054032}{\emph{Phys. Rev.} {\bf
+  D75} (2007) 054032}, [\href{https://arxiv.org/abs/hep-ph/0701006}{{\tt
+  hep-ph/0701006}}].
+
+\bibitem{Anselmino:2008jk}
+M.~Anselmino et~al., \emph{{Update on transversity and Collins functions from
+  SIDIS and $e^{+} e^{-}$ data}},
+  \href{http://dx.doi.org/10.1016/j.nuclphysbps.2009.03.117}{\emph{Nucl. Phys.
+  Proc. Suppl.} {\bf 191} (2009) 98--107},
+  [\href{https://arxiv.org/abs/0812.4366}{{\tt 0812.4366}}].
+
+\bibitem{Koike:2008du}
+Y.~Koike, K.~Tanaka and S.~Yoshida, \emph{{Drell--Yan double-spin asymmetry
+  $A_{LT}$ in polarized $p\bar{p}$ collisions: Wandzura--Wilczek
+  contribution}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2008.08.049}{\emph{Phys. Lett.}
+  {\bf B668} (2008) 286--292}, [\href{https://arxiv.org/abs/0805.2289}{{\tt
+  0805.2289}}].
+
+\bibitem{Hagler:2009mb}
+P.~H{\"a}gler, B.~U. Musch, J.~W. Negele and A.~Sch{\"a}fer, \emph{{Intrinsic
+  quark transverse momentum in the nucleon from lattice QCD}},
+  \href{http://dx.doi.org/10.1209/0295-5075/88/61001}{\emph{Europhys. Lett.}
+  {\bf 88} (2009) 61001}, [\href{https://arxiv.org/abs/0908.1283}{{\tt
+  0908.1283}}].
+
+\bibitem{Musch:2010ka}
+B.~U. Musch, P.~H{\"a}gler, J.~W. Negele and A.~Sch{\"a}fer, \emph{{Exploring
+  quark transverse momentum distributions with lattice QCD}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.83.094507}{\emph{Phys. Rev.} {\bf
+  D83} (2011) 094507}, [\href{https://arxiv.org/abs/1011.1213}{{\tt
+  1011.1213}}].
+
+\bibitem{Alexandrou:2017dzj}
+C.~Alexandrou, S.~Bacchio, K.~Cichy, M.~Constantinou, K.~Hadjiyiannakou,
+  K.~Jansen et~al., \emph{{Computation of parton distributions from the
+  quasi-PDF approach at the physical point}},
+  \href{http://dx.doi.org/10.1051/epjconf/201817514008}{\emph{EPJ Web Conf.}
+  {\bf 175} (2018) 14008}, [\href{https://arxiv.org/abs/1710.06408}{{\tt
+  1710.06408}}].
+
+\bibitem{Ishikawa:2017faj}
+T.~Ishikawa, Y.-Q. Ma, J.-W. Qiu and S.~Yoshida, \emph{{Renormalizability of
+  quasiparton distribution functions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.96.094019}{\emph{Phys. Rev.} {\bf
+  D96} (2017) 094019}, [\href{https://arxiv.org/abs/1707.03107}{{\tt
+  1707.03107}}].
+
+\bibitem{Engelhardt:2015xja}
+M.~Engelhardt, P.~H{\"a}gler, B.~Musch, J.~Negele and A.~Sch{\"a}fer,
+  \emph{{Lattice QCD study of the Boer-Mulders effect in a pion}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.93.054501}{\emph{Phys. Rev.} {\bf
+  D93} (2016) 054501}, [\href{https://arxiv.org/abs/1506.07826}{{\tt
+  1506.07826}}].
+
+\bibitem{Ji:2014hxa}
+X.~Ji, P.~Sun, X.~Xiong and F.~Yuan, \emph{{Soft factor subtraction and
+  transverse momentum dependent parton distributions on the lattice}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.91.074009}{\emph{Phys. Rev.} {\bf
+  D91} (2015) 074009}, [\href{https://arxiv.org/abs/1405.7640}{{\tt
+  1405.7640}}].
+
+\bibitem{Musch:2011er}
+B.~U. Musch, P.~H{\"a}gler, M.~Engelhardt, J.~W. Negele and A.~Sch{\"a}fer,
+  \emph{{Sivers and Boer-Mulders observables from lattice QCD}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.85.094510}{\emph{Phys. Rev.} {\bf
+  D85} (2012) 094510}, [\href{https://arxiv.org/abs/1111.4249}{{\tt
+  1111.4249}}].
+
+\bibitem{Ji:2017oey}
+X.~Ji, J.-H. Zhang and Y.~Zhao, \emph{{Renormalization in Large Momentum
+  Effective Theory of Parton Physics}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.120.112001}{\emph{Phys. Rev.
+  Lett.} {\bf 120} (2018) 112001},
+  [\href{https://arxiv.org/abs/1706.08962}{{\tt 1706.08962}}].
+
+\bibitem{Yoon:2017qzo}
+B.~Yoon, M.~Engelhardt, R.~Gupta, T.~Bhattacharya, J.~R. Green, B.~U. Musch
+  et~al., \emph{{Nucleon transverse-momentum-dependent parton distributions in
+  lattice QCD: Renormalization patterns and discretization effects}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.96.094508}{\emph{Phys. Rev.} {\bf
+  D96} (2017) 094508}, [\href{https://arxiv.org/abs/1706.03406}{{\tt
+  1706.03406}}].
+
+\bibitem{Green:2017xeu}
+J.~Green, K.~Jansen and F.~Steffens, \emph{{Nonperturbative Renormalization of
+  Nonlocal Quark Bilinears for Parton Quasidistribution Functions on the
+  Lattice Using an Auxiliary Field}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.121.022004}{\emph{Phys. Rev.
+  Lett.} {\bf 121} (2018) 022004},
+  [\href{https://arxiv.org/abs/1707.07152}{{\tt 1707.07152}}].
+
+\bibitem{Zhang:2017bzy}
+J.-H. Zhang, J.-W. Chen, X.~Ji, L.~Jin and H.-W. Lin, \emph{{Pion distribution
+  amplitude from lattice QCD}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.95.094514}{\emph{Phys. Rev.} {\bf
+  D95} (2017) 094514}, [\href{https://arxiv.org/abs/1702.00008}{{\tt
+  1702.00008}}].
+
+\bibitem{Hagler:2003is}
+{\scshape LHPC and SESAM} collaboration, LHPC, P.~H{\"a}gler, J.~W. Negele,
+  D.~B. Renner, W.~Schroers, T.~Lippert et~al., \emph{{Transverse structure of
+  nucleon parton distributions from lattice QCD}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.93.112001}{\emph{Phys. Rev.
+  Lett.} {\bf 93} (2004) 112001},
+  [\href{https://arxiv.org/abs/hep-lat/0312014}{{\tt hep-lat/0312014}}].
+
+\bibitem{Hagler:2007xi}
+{\scshape LHPC} collaboration, P.~H{\"a}gler, W.~Schroers, J.~Bratt, J.~W.
+  Negele, A.~V. Pochinsky, R.~G. Edwards et~al., \emph{{Nucleon generalized
+  parton distributions from full lattice QCD}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.77.094502}{\emph{Phys. Rev.} {\bf
+  D77} (2008) 094502}, [\href{https://arxiv.org/abs/0705.4295}{{\tt
+  0705.4295}}].
+
+\bibitem{Gockeler:2005cj}
+{\scshape QCDSF and UKQCD} collaboration, M.~G{\"o}ckeler, P.~H{\"a}gler,
+  R.~Horsley, D.~Pleiter, P.~E.~L. Rakow, A.~Sch{\"a}fer et~al., \emph{{Quark
+  helicity flip generalized parton distributions from two-flavor lattice QCD}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2005.09.002}{\emph{Phys. Lett.}
+  {\bf B627} (2005) 113--123},
+  [\href{https://arxiv.org/abs/hep-lat/0507001}{{\tt hep-lat/0507001}}].
+
+\bibitem{Burkardt:2001iy}
+M.~Burkardt and Y.~Koike, \emph{{Violation of sum rules for twist-3 parton
+  distributions in QCD}},
+  \href{http://dx.doi.org/10.1016/S0550-3213(02)00263-8}{\emph{Nucl. Phys.}
+  {\bf B632} (2002) 311--329},
+  [\href{https://arxiv.org/abs/hep-ph/0111343}{{\tt hep-ph/0111343}}].
+
+\bibitem{Bass:2003vp}
+S.~D. Bass, \emph{{Fixed poles, polarized glue and nucleon spin structure}},
+  {\emph{Acta Phys. Polon.} {\bf B34} (2003) 5893--5926},
+  [\href{https://arxiv.org/abs/hep-ph/0311174}{{\tt hep-ph/0311174}}].
+
+\bibitem{Stratmann:1993aw}
+M.~Stratmann, \emph{{Bag model predictions for polarized structure functions
+  and their $Q^{2}$-evolutions}},
+  \href{http://dx.doi.org/10.1007/BF01558408}{\emph{Z. Phys.} {\bf C60} (1993)
+  763--772}.
+
+\bibitem{Signal:1996ct}
+A.~Signal, \emph{{Calculations of higher twist distribution functions in the
+  MIT bag model}},
+  \href{http://dx.doi.org/10.1016/S0550-3213(97)00231-9}{\emph{Nucl. Phys.}
+  {\bf B497} (1997) 415--434},
+  [\href{https://arxiv.org/abs/hep-ph/9610480}{{\tt hep-ph/9610480}}].
+
+\bibitem{Avakian:2010br}
+H.~Avakian, A.~Efremov, P.~Schweitzer and F.~Yuan, \emph{{The transverse
+  momentum dependent distribution functions in the bag model}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.81.074035}{\emph{Phys. Rev.} {\bf
+  D81} (2010) 074035}, [\href{https://arxiv.org/abs/1001.5467}{{\tt
+  1001.5467}}].
+
+\bibitem{Jakob:1997wg}
+R.~Jakob, P.~Mulders and J.~Rodrigues, \emph{{Modeling quark distribution and
+  fragmentation functions}},
+  \href{http://dx.doi.org/10.1016/S0375-9474(97)00588-5}{\emph{Nucl. Phys.}
+  {\bf A626} (1997) 937--965},
+  [\href{https://arxiv.org/abs/hep-ph/9704335}{{\tt hep-ph/9704335}}].
+
+\bibitem{Wakamatsu:2000ex}
+M.~Wakamatsu, \emph{{Polarized structure functions $g_{2}(x)$ in the chiral
+  quark soliton model}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(00)00790-5}{\emph{Phys. Lett.}
+  {\bf B487} (2000) 118--124},
+  [\href{https://arxiv.org/abs/hep-ph/0006212}{{\tt hep-ph/0006212}}].
+
+\bibitem{Pasquini:2008ax}
+B.~Pasquini, S.~Cazzaniga and S.~Boffi, \emph{{Transverse momentum dependent
+  parton distributions in a light-cone quark model}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.78.034025}{\emph{Phys. Rev.} {\bf
+  D78} (2008) 034025}, [\href{https://arxiv.org/abs/0806.2298}{{\tt
+  0806.2298}}].
+
+\bibitem{Lorce:2011dv}
+C.~Lorc\'e, B.~Pasquini and M.~Vanderhaeghen, \emph{{Unified framework for
+  generalized and transverse-momentum dependent parton distributions within a
+  3Q light-cone picture of the nucleon}},
+  \href{http://dx.doi.org/10.1007/JHEP05(2011)041}{\emph{JHEP} {\bf 1105}
+  (2011) 041}, [\href{https://arxiv.org/abs/1102.4704}{{\tt 1102.4704}}].
+
+\bibitem{Kundu:2001pk}
+R.~Kundu and A.~Metz, \emph{{Higher twist and transverse momentum dependent
+  parton distributions: A Light front Hamiltonian approach}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.65.014009}{\emph{Phys. Rev.} {\bf
+  D65} (2002) 014009}, [\href{https://arxiv.org/abs/hep-ph/0107073}{{\tt
+  hep-ph/0107073}}].
+
+\bibitem{Schlegel:2004rg}
+M.~Schlegel and A.~Metz, \emph{{On the validity of Lorentz invariance relations
+  between parton distributions}},  in \emph{{Proceedings, 10th Advanced
+  Research Workshop on High-Energy Spin Physics, Dubna, Russia, September
+  16-20, 2003}}, pp.~169--173, 2004.
+\newblock \href{https://arxiv.org/abs/hep-ph/0406289}{{\tt hep-ph/0406289}}.
+
+\bibitem{Goeke:2003az}
+K.~Goeke, A.~Metz, P.~Pobylitsa and M.~Polyakov, \emph{{Lorentz invariance
+  relations among parton distributions revisited}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(03)00870-0}{\emph{Phys. Lett.}
+  {\bf B567} (2003) 27--30}, [\href{https://arxiv.org/abs/hep-ph/0302028}{{\tt
+  hep-ph/0302028}}].
+
+\bibitem{Lorce:2014hxa}
+C.~Lorc\'e, B.~Pasquini and P.~Schweitzer, \emph{{Unpolarized transverse
+  momentum dependent parton distribution functions beyond leading twist in
+  quark models}}, \href{http://dx.doi.org/10.1007/JHEP01(2015)103}{\emph{JHEP}
+  {\bf 01} (2015) 103}, [\href{https://arxiv.org/abs/1411.2550}{{\tt
+  1411.2550}}].
+
+\bibitem{Lorce:2016ugb}
+C.~Lorc\'e, B.~Pasquini and P.~Schweitzer, \emph{{Transverse pion structure
+  beyond leading twist in constituent models}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-016-4257-8}{\emph{Eur. Phys. J.}
+  {\bf C76} (2016) 415}, [\href{https://arxiv.org/abs/1605.00815}{{\tt
+  1605.00815}}].
+
+\bibitem{Zavada:1996kp}
+P.~Zavada, \emph{{The Structure functions and parton momenta distribution in
+  the hadron rest system}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.55.4290}{\emph{Phys. Rev.} {\bf D55}
+  (1997) 4290--4299}, [\href{https://arxiv.org/abs/hep-ph/9609372}{{\tt
+  hep-ph/9609372}}].
+
+\bibitem{Efremov:2010mt}
+A.~V. Efremov, P.~Schweitzer, O.~V. Teryaev and P.~Zavada, \emph{{The relation
+  between TMDs and PDFs in the covariant parton model approach}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.83.054025}{\emph{Phys. Rev.} {\bf
+  D83} (2011) 054025}, [\href{https://arxiv.org/abs/1012.5296}{{\tt
+  1012.5296}}].
+
+\bibitem{Efremov:2009ze}
+A.~V. Efremov, P.~Schweitzer, O.~V. Teryaev and P.~Zavada, \emph{{Transverse
+  momentum dependent distribution functions in a covariant parton model
+  approach with quark orbital motion}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.80.014021}{\emph{Phys. Rev.} {\bf
+  D80} (2009) 014021}, [\href{https://arxiv.org/abs/0903.3490}{{\tt
+  0903.3490}}].
+
+\bibitem{Schweitzer:2003uy}
+P.~Schweitzer, \emph{{Chirally-odd twist-3 distribution function $e^{a}(x)$ in
+  the chiral quark-soliton model}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.67.114010}{\emph{Phys. Rev.} {\bf
+  D67} (2003) 114010}, [\href{https://arxiv.org/abs/hep-ph/0303011}{{\tt
+  hep-ph/0303011}}].
+
+\bibitem{Ohnishi:2003mf}
+Y.~Ohnishi and M.~Wakamatsu, \emph{{$\pi N$ sigma term and chira-odd twist-3
+  distribution function $e(x)$ of the nucleon in the chiral quark soliton
+  model}}, \href{http://dx.doi.org/10.1103/PhysRevD.69.114002}{\emph{Phys.
+  Rev.} {\bf D69} (2004) 114002},
+  [\href{https://arxiv.org/abs/hep-ph/0312044}{{\tt hep-ph/0312044}}].
+
+\bibitem{Cebulla:2007ej}
+C.~Cebulla, J.~Ossmann, P.~Schweitzer and D.~Urbano, \emph{{The Twist-3 Parton
+  Distribution Function $e^{a}(x)$ in Large-N$_{c}$ Chiral Theory}},
+  {\emph{Acta Phys. Polon.} {\bf B39} (2008) 609--640},
+  [\href{https://arxiv.org/abs/0710.3103}{{\tt 0710.3103}}].
+
+\bibitem{Meissner:2007rx}
+S.~Meissner, A.~Metz and K.~Goeke, \emph{{Relations between generalized and
+  transverse momentum dependent parton distributions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.76.034002}{\emph{Phys. Rev.} {\bf
+  D76} (2007) 034002}, [\href{https://arxiv.org/abs/hep-ph/0703176}{{\tt
+  hep-ph/0703176}}].
+
+\bibitem{Mukherjee:2009uy}
+A.~Mukherjee, \emph{{Twist-three Distribution $e(x)$: Sum Rules and Equation of
+  Motion Relations}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2010.03.023}{\emph{Phys. Lett.}
+  {\bf B687} (2010) 180--183}, [\href{https://arxiv.org/abs/0912.1446}{{\tt
+  0912.1446}}].
+
+\bibitem{Harindranath:1997qn}
+A.~Harindranath and W.-M. Zhang, \emph{{Examination of Wandzura--Wilczek
+  relation for $g_{2} (x,Q^{2})$ in pQCD}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(97)00771-5}{\emph{Phys. Lett.}
+  {\bf B408} (1997) 347--356},
+  [\href{https://arxiv.org/abs/hep-ph/9706419}{{\tt hep-ph/9706419}}].
+
+\bibitem{Boer:2003cm}
+D.~Boer, P.~J. Mulders and F.~Pijlman, \emph{{Universality of T-odd effects in
+  single spin and azimuthal asymmetries}},
+  \href{http://dx.doi.org/10.1016/S0550-3213(03)00527-3}{\emph{Nucl. Phys.}
+  {\bf B667} (2003) 201--241},
+  [\href{https://arxiv.org/abs/hep-ph/0303034}{{\tt hep-ph/0303034}}].
+
+\bibitem{Ji:2006ub}
+X.~Ji, J.-W. Qiu, W.~Vogelsang and F.~Yuan, \emph{{Unified Picture for Single
+  Transverse-Spin Asymmetries in Hard-Scattering Processes}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.97.082002}{\emph{Phys. Rev.
+  Lett.} {\bf 97} (2006) 082002},
+  [\href{https://arxiv.org/abs/hep-ph/0602239}{{\tt hep-ph/0602239}}].
+
+\bibitem{Ali:1991em}
+A.~Ali, V.~M. Braun and G.~Hiller, \emph{{Asymptotic solutions of the evolution
+  equation for the polarized nucleon structure function $g_2 (x, Q^2)$}},
+  \href{http://dx.doi.org/10.1016/0370-2693(91)90753-D}{\emph{Phys. Lett.} {\bf
+  B266} (1991) 117--125}.
+
+\bibitem{Koike:1994st}
+Y.~Koike and K.~Tanaka, \emph{{$Q^2 $evolution of nucleon's chiral odd
+  twist-three structure function: $h_L (x, Q^2)$}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.51.6125}{\emph{Phys. Rev.} {\bf D51}
+  (1995) 6125--6138}, [\href{https://arxiv.org/abs/hep-ph/9412310}{{\tt
+  hep-ph/9412310}}].
+
+\bibitem{Balitsky:1996uh}
+I.~I. Balitsky, V.~M. Braun, Y.~Koike and K.~Tanaka, \emph{{$Q^2$ evolution of
+  chiral odd twist-three distributions $h_L(x,Q^2)$ and $e(x,Q^2)$ in the large
+  $N_c$ limit}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.77.3078}{\emph{Phys. Rev. Lett.}
+  {\bf 77} (1996) 3078--3081},
+  [\href{https://arxiv.org/abs/hep-ph/9605439}{{\tt hep-ph/9605439}}].
+
+\bibitem{Belitsky:1997zw}
+A.~V. Belitsky and D.~{M\"u}ller, \emph{{Scale dependence of the chiral odd
+  twist-three distributions $h_L(x)$ and $e(x)$}},
+  \href{http://dx.doi.org/10.1016/S0550-3213(97)00432-X}{\emph{Nucl. Phys.}
+  {\bf B503} (1997) 279--308},
+  [\href{https://arxiv.org/abs/hep-ph/9702354}{{\tt hep-ph/9702354}}].
+
+\bibitem{Anselmino:2005nn}
+M.~Anselmino et~al., \emph{{The role of Cahn and Sivers effects in deep
+  inelastic scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.71.074006}{\emph{Phys. Rev.} {\bf
+  D71} (2005) 074006}, [\href{https://arxiv.org/abs/hep-ph/0501196}{{\tt
+  hep-ph/0501196}}].
+
+\bibitem{Collins:2005ie}
+J.~C. Collins, A.~V. Efremov, K.~Goeke, S.~Menzel, A.~Metz and P.~Schweitzer,
+  \emph{{Sivers effect in semiinclusive deeply inelastic scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.73.014021}{\emph{Phys. Rev.} {\bf
+  D73} (2006) 014021}, [\href{https://arxiv.org/abs/hep-ph/0509076}{{\tt
+  hep-ph/0509076}}].
+
+\bibitem{D'Alesio:2007jt}
+U.~D'Alesio and F.~Murgia, \emph{{Azimuthal and single spin asymmetries in hard
+  scattering processes}},
+  \href{http://dx.doi.org/10.1016/j.ppnp.2008.01.001}{\emph{Prog. Part. Nucl.
+  Phys. 61} {\bf 2008} (2008) 394--454},
+  [\href{https://arxiv.org/abs/0712.4328}{{\tt 0712.4328}}].
+
+\bibitem{Schweitzer:2010tt}
+P.~Schweitzer, T.~Teckentrup and A.~Metz, \emph{{Intrinsic transverse parton
+  momenta in deeply inelastic reactions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.81.094019}{\emph{Phys. Rev.} {\bf
+  D81} (2010) 094019}, [\href{https://arxiv.org/abs/1003.2190}{{\tt
+  1003.2190}}].
+
+\bibitem{Signori:2013mda}
+A.~Signori, A.~Bacchetta, M.~Radici and G.~Schnell, \emph{{Investigations into
+  the flavor dependence of partonic transverse momentum}},
+  \href{http://dx.doi.org/10.1007/JHEP11(2013)194}{\emph{JHEP} {\bf 11} (2013)
+  194}, [\href{https://arxiv.org/abs/1309.3507}{{\tt 1309.3507}}].
+
+\bibitem{Anselmino:2013lza}
+M.~Anselmino, M.~Boglione, J.~O. Gonzalez~Hernandez, S.~Melis and A.~Prokudin,
+  \emph{{Unpolarised transverse momentum dependent distribution and
+  fragmentation functions from SIDIS multiplicities}},
+  \href{http://dx.doi.org/10.1007/JHEP04(2014)005}{\emph{JHEP} {\bf 04} (2014)
+  005}, [\href{https://arxiv.org/abs/1312.6261}{{\tt 1312.6261}}].
+
+\bibitem{Bacchetta:2008xw}
+A.~Bacchetta, D.~Boer, M.~Diehl and P.~J. Mulders, \emph{{Matches and
+  mismatches in the descriptions of semi-inclusive processes at low and high
+  transverse momentum}},
+  \href{http://dx.doi.org/10.1088/1126-6708/2008/08/023}{\emph{JHEP} {\bf 08}
+  (2008) 023}, [\href{https://arxiv.org/abs/0803.0227}{{\tt 0803.0227}}].
+
+\bibitem{Landry:2002ix}
+F.~Landry, R.~Brock, P.~M. Nadolsky and C.~Yuan, \emph{{Tevatron run-1 $Z$
+  boson data and Collins-Soper-Sterman resummation formalism}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.67.073016}{\emph{Phys. Rev.} {\bf
+  D67} (2003) 073016}, [\href{https://arxiv.org/abs/hep-ph/0212159}{{\tt
+  hep-ph/0212159}}].
+
+\bibitem{Martin:2009iq}
+A.~D. Martin, W.~J. Stirling, R.~S. Thorne and G.~Watt, \emph{{Parton
+  distributions for the LHC}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-009-1072-5}{\emph{Eur. Phys. J.}
+  {\bf C63} (2009) 189--285}, [\href{https://arxiv.org/abs/0901.0002}{{\tt
+  0901.0002}}].
+
+\bibitem{deFlorian:2007aj}
+D.~de~Florian, R.~Sassot and M.~Stratmann, \emph{{Global analysis of
+  fragmentation functions for pions and kaons and their uncertainties}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.75.114010}{\emph{Phys. Rev.} {\bf
+  D75} (2007) 114010}, [\href{https://arxiv.org/abs/hep-ph/0703242}{{\tt
+  hep-ph/0703242}}].
+
+\bibitem{Schweitzer:2012hh}
+P.~Schweitzer, M.~Strikman and C.~Weiss, \emph{{Intrinsic transverse momentum
+  and parton correlations from dynamical chiral symmetry breaking}},
+  \href{http://dx.doi.org/10.1007/JHEP01(2013)163}{\emph{JHEP} {\bf 01} (2013)
+  163}, [\href{https://arxiv.org/abs/1210.1267}{{\tt 1210.1267}}].
+
+\bibitem{Collins:2016hqq}
+J.~Collins, L.~Gamberg, A.~Prokudin, T.~C. Rogers, N.~Sato and B.~Wang,
+  \emph{{Relating transverse-momentum-dependent and collinear factorization
+  theorems in a generalized formalism}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.94.034014}{\emph{Phys. Rev.} {\bf
+  D94} (2016) 034014}, [\href{https://arxiv.org/abs/1605.00671}{{\tt
+  1605.00671}}].
+
+\bibitem{Osipenko:2008aa}
+{\scshape CLAS} collaboration, M.~Osipenko et~al., \emph{{Measurement of
+  unpolarized semi-inclusive $\pi^{+}$ electroproduction off the proton}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.80.032004}{\emph{Phys. Rev.} {\bf
+  D80} (2009) 032004}, [\href{https://arxiv.org/abs/0809.1153}{{\tt
+  0809.1153}}].
+
+\bibitem{Airapetian:2012ki}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Multiplicities of
+  charged pions and kaons from semi-inclusive deep-inelastic scattering by the
+  proton and the deuteron}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.87.074029}{\emph{Phys. Rev.} {\bf
+  D87} (2013) 074029}, [\href{https://arxiv.org/abs/1212.5407}{{\tt
+  1212.5407}}].
+
+\bibitem{Aghasyan:2017ctw}
+{\scshape COMPASS} collaboration, M.~Aghasyan et~al.,
+  \emph{{Transverse-momentum-dependent multiplicities of charged hadrons in
+  muon-deuteron deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.97.032006}{\emph{Phys. Rev.} {\bf
+  D97} (2018) 032006}, [\href{https://arxiv.org/abs/1709.07374}{{\tt
+  1709.07374}}].
+
+\bibitem{Bacchetta:2017gcc}
+A.~Bacchetta, F.~Delcarro, C.~Pisano, M.~Radici and A.~Signori,
+  \emph{{Extraction of partonic transverse momentum distributions from
+  semi-inclusive deep-inelastic scattering, Drell--Yan and Z-boson
+  production}}, \href{http://dx.doi.org/10.1007/JHEP06(2017)081}{\emph{JHEP}
+  {\bf 06} (2017) 081}, [\href{https://arxiv.org/abs/1703.10157}{{\tt
+  1703.10157}}].
+
+\bibitem{Avakian:2010ae}
+{\scshape CLAS} collaboration, H.~Avakian et~al., \emph{{Measurement of Single-
+  and Double-Spin Asymmetries in Deep Inelastic Pion Electroproduction with a
+  Longitudinally Polarized Target}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.105.262002}{\emph{Phys. Rev.
+  Lett.} {\bf 105} (2010) 262002}, [\href{https://arxiv.org/abs/1003.4549}{{\tt
+  1003.4549}}].
+
+\bibitem{Airapetian:2018rlq}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Longitudinal
+  double-spin asymmetries in semi-inclusive deep-inelastic scattering of
+  electrons and positrons by protons and deuterons}},
+  \href{https://arxiv.org/abs/1810.07054}{{\tt 1810.07054}}.
+
+\bibitem{Adolph:2016vou}
+{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{Azimuthal
+  asymmetries of charged hadrons produced in high-energy muon scattering off
+  longitudinally polarised deuterons}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-018-6379-7}{\emph{Eur. Phys. J.}
+  {\bf C78} (2018) 952}, [\href{https://arxiv.org/abs/1609.06062}{{\tt
+  1609.06062}}].
+
+\bibitem{Sivers:1989cc}
+D.~W. Sivers, \emph{{Single-spin production asymmetries from the hard
+  scattering of pointlike constituents}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.41.83}{\emph{Phys. Rev.} {\bf D41}
+  (1990) 83}.
+
+\bibitem{Anselmino:2010bs}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia and A.~Prokudin,
+  \emph{{New insight on the Sivers transverse momentum dependent distribution
+  function}}, \href{http://dx.doi.org/10.1088/1742-6596/295/1/012062}{\emph{J.
+  Phys. Conf. Ser.} {\bf 295} (2011) 012062},
+  [\href{https://arxiv.org/abs/1012.3565}{{\tt 1012.3565}}].
+
+\bibitem{Anselmino:2005ea}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, A.~Kotzinian, F.~Murgia and
+  A.~Prokudin, \emph{{Extracting the Sivers function from polarized
+  semi-inclusive deep inelastic scattering data and making predictions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.72.094007,
+  10.1103/PhysRevD.72.099903}{\emph{Phys. Rev.} {\bf D72} (2005) 094007},
+  [\href{https://arxiv.org/abs/hep-ph/0507181}{{\tt hep-ph/0507181}}].
+
+\bibitem{Anselmino:2005an}
+M.~Anselmino et~al., \emph{{Comparing extractions of Sivers functions}},  in
+  \emph{{Transversity. Proceedings, Workshop, Como, Italy, September 7-10,
+  2005}}, pp.~236--243, 2005.
+\newblock \href{https://arxiv.org/abs/hep-ph/0511017}{{\tt hep-ph/0511017}}.
+
+\bibitem{Vogelsang:2005cs}
+W.~Vogelsang and F.~Yuan, \emph{{Single-transverse-spin asymmetries: From deep
+  inelastic scattering to hadronic collisions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.72.054028}{\emph{Phys. Rev.} {\bf
+  D72} (2005) 054028}, [\href{https://arxiv.org/abs/hep-ph/0507266}{{\tt
+  hep-ph/0507266}}].
+
+\bibitem{Anselmino:2008sga}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, A.~Kotzinian, S.~Melis, F.~Murgia
+  et~al., \emph{{Sivers effect for pion and kaon production in semi-inclusive
+  deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1140/epja/i2008-10697-y}{\emph{Eur. Phys. J.} {\bf
+  A39} (2009) 89--100}, [\href{https://arxiv.org/abs/0805.2677}{{\tt
+  0805.2677}}].
+
+\bibitem{Bacchetta:2011gx}
+A.~Bacchetta and M.~Radici, \emph{{Constraining Quark Angular Momentum through
+  Semi-Inclusive Measurements}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.107.212001}{\emph{Phys. Rev.
+  Lett.} {\bf 107} (2011) 212001}, [\href{https://arxiv.org/abs/1107.5755}{{\tt
+  1107.5755}}].
+
+\bibitem{Anselmino:2011gs}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia and A.~Prokudin,
+  \emph{{Sivers Distribution Functions and the Latest SIDIS Data}},  in
+  \emph{{19th International Workshop on Deep-Inelastic Scattering and Related
+  Subjects (DIS 2011) Newport News, Virginia, April 11-15, 2011}}, 2011.
+\newblock \href{https://arxiv.org/abs/1107.4446}{{\tt 1107.4446}}.
+
+\bibitem{Airapetian:2009ae}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Observation of
+  the Naive-T-odd Sivers Effect in Deep-Inelastic Scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.103.152002}{\emph{Phys. Rev.
+  Lett.} {\bf 103} (2009) 152002}, [\href{https://arxiv.org/abs/0906.3918}{{\tt
+  0906.3918}}].
+
+\bibitem{Adolph:2012sp}
+{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{II Experimental
+  investigation of transverse spin asymmetries in $\mu$-p SIDIS processes:
+  Sivers asymmetries}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2012.09.056}{\emph{Phys. Lett.}
+  {\bf B717} (2012) 383--389}, [\href{https://arxiv.org/abs/1205.5122}{{\tt
+  1205.5122}}].
+
+\bibitem{Anselmino:2012aa}
+M.~Anselmino, M.~Boglione and S.~Melis, \emph{{Strategy towards the extraction
+  of the Sivers function with transverse momentum dependent evolution}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.86.014028}{\emph{Phys. Rev.} {\bf
+  D86} (2012) 014028}, [\href{https://arxiv.org/abs/1204.1239}{{\tt
+  1204.1239}}].
+
+\bibitem{Brodsky:2002cx}
+S.~J. Brodsky, D.~S. Hwang and I.~Schmidt, \emph{{Final-state interactions and
+  single-spin asymmetries in semi-inclusive deep inelastic scattering}},
+  {\emph{Phys. Lett.} {\bf B530} (2002) 99--107},
+  [\href{https://arxiv.org/abs/hep-ph/0201296}{{\tt hep-ph/0201296}}].
+
+\bibitem{Brodsky:2002rv}
+S.~J. Brodsky, D.~S. Hwang and I.~Schmidt, \emph{{Initial-state interactions
+  and single-spin asymmetries in Drell-Yan processes}},
+  \href{http://dx.doi.org/10.1016/S0550-3213(02)00617-X}{\emph{Nucl. Phys.}
+  {\bf B642} (2002) 344--356},
+  [\href{https://arxiv.org/abs/hep-ph/0206259}{{\tt hep-ph/0206259}}].
+
+\bibitem{Adamczyk:2015gyk}
+{\scshape STAR} collaboration, L.~Adamczyk et~al., \emph{{Measurement of the
+  transverse single-spin asymmetry in $p^\uparrow+p \to W^{\pm}/Z^0$ at RHIC}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.116.132301}{\emph{Phys. Rev.
+  Lett.} {\bf 116} (2016) 132301},
+  [\href{https://arxiv.org/abs/1511.06003}{{\tt 1511.06003}}].
+
+\bibitem{Aghasyan:2017jop}
+{\scshape COMPASS} collaboration, M.~Aghasyan et~al., \emph{{First Measurement
+  of Transverse-Spin-Dependent Azimuthal Asymmetries in the Drell--Yan
+  Process}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.119.112002}{\emph{Phys. Rev.
+  Lett.} {\bf 119} (2017) 112002},
+  [\href{https://arxiv.org/abs/1704.00488}{{\tt 1704.00488}}].
+
+\bibitem{Parsamyan:2018zju}
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{First measurement of
+  transverse-spin-dependent azimuthal asymmetries in the Drell-Yan process}},
+  \href{http://dx.doi.org/10.22323/1.297.0243}{\emph{PoS} {\bf DIS2017} (2018)
+  243}, [\href{https://arxiv.org/abs/1801.01487}{{\tt 1801.01487}}].
+
+\bibitem{Bacchetta:2002ux}
+A.~Bacchetta and M.~Radici, \emph{{Partial-wave analysis of two-hadron
+  fragmentation functions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.67.094002}{\emph{Phys. Rev.} {\bf
+  D67} (2003) 094002}, [\href{https://arxiv.org/abs/hep-ph/0212300}{{\tt
+  hep-ph/0212300}}].
+
+\bibitem{Bacchetta:2003vn}
+A.~Bacchetta and M.~Radici, \emph{{Two-hadron semi-inclusive production
+  including subleading twist contributions}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.69.074026}{\emph{Phys. Rev.} {\bf
+  D69} (2004) 074026}, [\href{https://arxiv.org/abs/hep-ph/0311173}{{\tt
+  hep-ph/0311173}}].
+
+\bibitem{Bacchetta:2011ip}
+A.~Bacchetta, A.~Courtoy and M.~Radici, \emph{{First Glances at the
+  Transversity Parton Distribution through Dihadron Fragmentation Functions}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.107.012001}{\emph{Phys. Rev.
+  Lett.} {\bf 107} (2011) 012001}, [\href{https://arxiv.org/abs/1104.3855}{{\tt
+  1104.3855}}].
+
+\bibitem{Bacchetta:2012ty}
+A.~Bacchetta, A.~Courtoy and M.~Radici, \emph{{First extraction of valence
+  transversities in a collinear framework}},
+  \href{http://dx.doi.org/10.1007/JHEP03(2013)119}{\emph{JHEP} {\bf 03} (2013)
+  119}, [\href{https://arxiv.org/abs/1212.3568}{{\tt 1212.3568}}].
+
+\bibitem{Radici:2015mwa}
+M.~Radici, A.~Courtoy, A.~Bacchetta and M.~Guagnelli, \emph{{Improved
+  extraction of valence transversity distributions from inclusive dihadron
+  production}}, \href{http://dx.doi.org/10.1007/JHEP05(2015)123}{\emph{JHEP}
+  {\bf 05} (2015) 123}, [\href{https://arxiv.org/abs/1503.03495}{{\tt
+  1503.03495}}].
+
+\bibitem{Radici:2018iag}
+M.~Radici and A.~Bacchetta, \emph{{First Extraction of Transversity from a
+  Global Analysis of Electron-Proton and Proton-Proton Data}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.120.192001}{\emph{Phys. Rev.
+  Lett.} {\bf 120} (2018) 192001},
+  [\href{https://arxiv.org/abs/1802.05212}{{\tt 1802.05212}}].
+
+\bibitem{Collins:1992kk}
+J.~C. Collins, \emph{Fragmentation of transversely polarized quarks probed in
+  transverse momentum distributions}, {\emph{Nucl. Phys.} {\bf B396} (1993)
+  161--182}.
+
+\bibitem{Anselmino:2013vqa}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia and A.~Prokudin,
+  \emph{{Simultaneous extraction of transversity and Collins functions from new
+  SIDIS and $e^{+}e^{-}$ data}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.87.094019}{\emph{Phys. Rev.} {\bf
+  D87} (2013) 094019}, [\href{https://arxiv.org/abs/1303.3822}{{\tt
+  1303.3822}}].
+
+\bibitem{Kang:2014zza}
+Z.-B. Kang, A.~Prokudin, P.~Sun and F.~Yuan, \emph{{Nucleon tensor charge from
+  Collins azimuthal asymmetry measurements}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.91.071501}{\emph{Phys. Rev.} {\bf
+  D91} (2015) 071501}, [\href{https://arxiv.org/abs/1410.4877}{{\tt
+  1410.4877}}].
+
+\bibitem{Anselmino:2015sxa}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, J.~O. Gonzalez~Hernandez, S.~Melis,
+  F.~Murgia et~al., \emph{{Collins functions for pions from SIDIS and new
+  $e^+e^-$ data: a first glance at their transverse momentum dependence}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.92.114023}{\emph{Phys. Rev.} {\bf
+  D92} (2015) 114023}, [\href{https://arxiv.org/abs/1510.05389}{{\tt
+  1510.05389}}].
+
+\bibitem{Airapetian:2010ds}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Effects of
+  transversity in deep-inelastic scattering by polarized protons}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2010.08.012}{\emph{Phys. Lett.}
+  {\bf B693} (2010) 11--16}, [\href{https://arxiv.org/abs/1006.4221}{{\tt
+  1006.4221}}].
+
+\bibitem{Adolph:2014zba}
+{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{Collins and Sivers
+  asymmetries in muonproduction of pions and kaons off transversely polarised
+  protons}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2015.03.056}{\emph{Phys. Lett.}
+  {\bf B744} (2015) 250--259}, [\href{https://arxiv.org/abs/1408.4405}{{\tt
+  1408.4405}}].
+
+\bibitem{Barone:2009hw}
+V.~Barone, S.~Melis and A.~Prokudin, \emph{{The Boer-Mulders effect in
+  unpolarized SIDIS: An Analysis of the COMPASS and HERMES data on the cos2phi
+  asymmetry}}, \href{http://dx.doi.org/10.1103/PhysRevD.81.114026}{\emph{Phys.
+  Rev.} {\bf D81} (2010) 114026}, [\href{https://arxiv.org/abs/0912.5194}{{\tt
+  0912.5194}}].
+
+\bibitem{Airapetian:2012yg}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Azimuthal
+  distributions of charged hadrons, pions, and kaons produced in deep-inelastic
+  scattering off unpolarized protons and deuterons}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.87.012010}{\emph{Phys. Rev.} {\bf
+  D87} (2013) 012010}, [\href{https://arxiv.org/abs/1204.4161}{{\tt
+  1204.4161}}].
+
+\bibitem{Adolph:2014pwc}
+{\scshape COMPASS} collaboration, C.~Adolph et~al., \emph{{Measurement of
+  azimuthal hadron asymmetries in semi-inclusive deep inelastic scattering off
+  unpolarised nucleons}},
+  \href{http://dx.doi.org/10.1016/j.nuclphysb.2014.07.019}{\emph{Nucl. Phys.}
+  {\bf B886} (2014) 1046--1077}, [\href{https://arxiv.org/abs/1401.6284}{{\tt
+  1401.6284}}].
+
+\bibitem{Cahn:1978se}
+R.~N. Cahn, \emph{{Azimuthal dependence in leptoproduction: A simple parton
+  model calculation}},
+  \href{http://dx.doi.org/10.1016/0370-2693(78)90020-5}{\emph{Phys. Lett.} {\bf
+  B78} (1978) 269}.
+
+\bibitem{Cao:2018qqf}
+X.~Cao, \emph{{Parton distributions and $\cos 2\phi_h$ asymmetry induced by
+  anomalous photon-quark coupling}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.97.114010}{\emph{Phys. Rev.} {\bf
+  D97} (2018) 114010}, [\href{https://arxiv.org/abs/1802.02417}{{\tt
+  1802.02417}}].
+
+\bibitem{Barone:2010gk}
+V.~Barone, S.~Melis and A.~Prokudin, \emph{{Azimuthal asymmetries in
+  unpolarized Drell--Yan processes and the Boer--Mulders distributions of
+  antiquarks}}, \href{http://dx.doi.org/10.1103/PhysRevD.82.114025}{\emph{Phys.
+  Rev.} {\bf D82} (2010) 114025}, [\href{https://arxiv.org/abs/1009.3423}{{\tt
+  1009.3423}}].
+
+\bibitem{Barone:2015ksa}
+V.~Barone, M.~Boglione, J.~O. Gonzalez~Hernandez and S.~Melis,
+  \emph{{Phenomenological analysis of azimuthal asymmetries in unpolarized
+  semi-inclusive deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.91.074019}{\emph{Phys. Rev.} {\bf
+  D91} (2015) 074019}, [\href{https://arxiv.org/abs/1502.04214}{{\tt
+  1502.04214}}].
+
+\bibitem{Avakian:2008dz}
+H.~Avakian, A.~V. Efremov, P.~Schweitzer and F.~Yuan, \emph{{Transverse
+  momentum dependent distribution function $h_{1T}^\perp$ and the single spin
+  asymmetry $A_{UT}^{\sin(3\phi-\phi_S)}$}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.78.114024}{\emph{Phys. Rev.} {\bf
+  D78} (2008) 114024}, [\href{https://arxiv.org/abs/0805.3355}{{\tt
+  0805.3355}}].
+
+\bibitem{She:2009jq}
+J.~She, J.~Zhu and B.-Q. Ma, \emph{{$h_{1T}^{\perp}$ and quark orbital angular
+  momentum}}, \href{http://dx.doi.org/10.1103/PhysRevD.79.054008}{\emph{Phys.
+  Rev.} {\bf D79} (2009) 054008}, [\href{https://arxiv.org/abs/0902.3718}{{\tt
+  0902.3718}}].
+
+\bibitem{Lorce:2011kn}
+C.~Lorce and B.~Pasquini, \emph{{The pretzelosity TMD and quark orbital angular
+  momentum}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2012.03.025}{\emph{Phys. Lett.}
+  {\bf B710} (2012) 486--488}, [\href{https://arxiv.org/abs/1111.6069}{{\tt
+  1111.6069}}].
+
+\bibitem{Parsamyan:2013fia}
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Transverse spin
+  asymmetries at COMPASS: beyond Collins and Sivers effects}}, {\emph{PoS} {\bf
+  DIS2013} (2013) 231}, [\href{https://arxiv.org/abs/1307.0183}{{\tt
+  1307.0183}}].
+
+\bibitem{Schnell:2010zza}
+{\scshape HERMES} collaboration, G.~Schnell, \emph{{The Sivers and other
+  semi-inclusive single-spin asymmetries at HERMES}},
+  \href{http://dx.doi.org/10.22323/1.106.0247}{\emph{PoS} {\bf DIS2010} (2010)
+  247}.
+
+\bibitem{Lefky:2014eia}
+C.~Lefky and A.~Prokudin, \emph{{Extraction of the distribution function
+  $h^{\perp}_{1T}$ from experimental data}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.91.034010}{\emph{Phys. Rev.} {\bf
+  D91} (2015) 034010}, [\href{https://arxiv.org/abs/1411.0580}{{\tt
+  1411.0580}}].
+
+\bibitem{Kotzinian:2008fe}
+A.~Kotzinian, \emph{{SIDIS Asymmetries in Quark-Diquark Model}},  in
+  \emph{{Transversity 2008: 2nd International Workshop on Transverse
+  Polarization Phenomena in Hard Processes Ferrara, Italy, May 28-31, 2008}},
+  2008.
+\newblock \href{https://arxiv.org/abs/0806.3804}{{\tt 0806.3804}}.
+
+\bibitem{Boffi:2009sh}
+S.~Boffi, A.~V. Efremov, B.~Pasquini and P.~Schweitzer, \emph{{Azimuthal spin
+  asymmetries in light-cone constituent quark models}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.79.094012}{\emph{Phys. Rev.} {\bf
+  D79} (2009) 094012}, [\href{https://arxiv.org/abs/0903.1271}{{\tt
+  0903.1271}}].
+
+\bibitem{Ball:2014uwa}
+{\scshape NNPDF} collaboration, R.~D. Ball et~al., \emph{{Parton distributions
+  for the LHC Run II}},
+  \href{http://dx.doi.org/10.1007/JHEP04(2015)040}{\emph{JHEP} {\bf 04} (2015)
+  040}, [\href{https://arxiv.org/abs/1410.8849}{{\tt 1410.8849}}].
+
+\bibitem{Huang:2011bc}
+{\scshape Jefferson Lab Hall A} collaboration, J.~Huang et~al.,
+  \emph{{Beam-Target Double Spin Asymmetry $A_{LT}$ in Charged Pion Production
+  from Deep Inelastic Scattering on a Transversely Polarized $^{3}$He Target at
+  $1.4 < Q^2 < 2.7 GeV^2$}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.108.052001}{\emph{Phys. Rev.
+  Lett.} {\bf 108} (2012) 052001}, [\href{https://arxiv.org/abs/1108.0489}{{\tt
+  1108.0489}}].
+
+\bibitem{Parsamyan:2007ju}
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{New target transverse
+  spin dependent azimuthal asymmetries from COMPASS experiment}},
+  \href{http://dx.doi.org/10.1140/epjst/e2008-00780-1}{\emph{Eur. Phys. J. ST}
+  {\bf 162} (2008) 89--96}, [\href{https://arxiv.org/abs/0709.3440}{{\tt
+  0709.3440}}].
+
+\bibitem{Parsamyan:2015dfa}
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Transverse spin
+  azimuthal asymmetries in SIDIS at COMPASS: Multidimensional analysis}},
+  \href{http://dx.doi.org/10.1142/S2010194516600296}{\emph{Int. J. Mod. Phys.
+  Conf. Ser.} {\bf 40} (2016) 1660029},
+  [\href{https://arxiv.org/abs/1504.01599}{{\tt 1504.01599}}].
+
+\bibitem{Parsamyan:2018evv}
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Measurement of
+  target-polarization dependent azimuthal asymmetries in SIDIS and Drell-Yan
+  processes at COMPASS experiment}}, {\emph{PoS} {\bf QCDEV2017} (2018) 042}.
+
+\bibitem{Pappalardo:2011cu}
+{\scshape HERMES} collaboration, L.~L. Pappalardo and M.~Diefenthaler,
+  \emph{{Measurements of Double-Spin Asymmetries in SIDIS of Longitudinally
+  Polarized Leptons off Transversely Polarized Protons}},
+  \href{https://arxiv.org/abs/1107.4227}{{\tt 1107.4227}}.
+
+\bibitem{Pappalardo:2012zz}
+{\scshape HERMES} collaboration, L.~L. Pappalardo, \emph{{Accessing TMDs at
+  HERMES}}, \href{http://dx.doi.org/10.1063/1.3700519}{\emph{AIP Conf. Proc.}
+  {\bf 1441} (2012) 229--232}.
+
+\bibitem{Airapetian:1999tv}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Evidence for a
+  Single-Spin Azimuthal Asymmetry in Semi-inclusive Pion Electroproduction}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.84.4047}{\emph{Phys. Rev. Lett.}
+  {\bf 84} (2000) 4047--4051},
+  [\href{https://arxiv.org/abs/hep-ex/9910062}{{\tt hep-ex/9910062}}].
+
+\bibitem{Parsamyan:2018ovx}
+{\scshape COMPASS} collaboration, B.~Parsamyan, \emph{{Measurement of
+  longitudinal-target-polarization dependent azimuthal asymmetries in SIDIS at
+  COMPASS experiment}}, {\emph{PoS} {\bf DIS2017} (2018) 259},
+  [\href{https://arxiv.org/abs/1801.01488}{{\tt 1801.01488}}].
+
+\bibitem{Jawalkar:2017ube}
+{\scshape CLAS} collaboration, S.~Jawalkar et~al., \emph{{Semi-Inclusive
+  $\pi^0$ target and beam-target asymmetries from 6 GeV electron scattering
+  with CLAS}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2018.06.014}{\emph{Phys. Lett.}
+  {\bf B782} (2018) 662--667}, [\href{https://arxiv.org/abs/1709.10054}{{\tt
+  1709.10054}}].
+
+\bibitem{Airapetian:2002mf}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Measurement of
+  single-spin azimuthal asymmetries in semi-inclusive electroproduction of
+  pions and kaons on a longitudinally polarised deuterium target}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(03)00566-5}{\emph{Phys. Lett.}
+  {\bf B562} (2003) 182--192},
+  [\href{https://arxiv.org/abs/hep-ex/0212039}{{\tt hep-ex/0212039}}].
+
+\bibitem{Avakian:2003pk}
+{\scshape CLAS} collaboration, H.~Avakian et~al., \emph{{Measurement of
+  beam-spin asymmetries for $\pi^{+}$ electroproduction above the baryon
+  resonance region}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.69.112004}{\emph{Phys. Rev.} {\bf
+  D69} (2004) 112004}, [\href{https://arxiv.org/abs/hep-ex/0301005}{{\tt
+  hep-ex/0301005}}].
+
+\bibitem{Airapetian:2006rx}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{Beam-spin
+  asymmetries in the azimuthal distribution of pion electroproduction},
+  \href{http://dx.doi.org/10.1016/j.physletb.2007.03.015}{\emph{Phys. Lett.}
+  {\bf B648} (2007) 164--170},
+  [\href{https://arxiv.org/abs/hep-ex/0612059}{{\tt hep-ex/0612059}}].
+
+\bibitem{Gohn:2009zz}
+W.~Gohn, H.~Avakian, K.~Joo and M.~Ungaro, \emph{{Beam spin asymmetries from
+  semi-inclusive pion electroproduction in deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1063/1.3215689}{\emph{AIP Conf. Proc.} {\bf 1149}
+  (2009) 461--464}.
+
+\bibitem{Aghasyan:2011ha}
+M.~Aghasyan, H.~Avakian, P.~Rossi, E.~De~Sanctis, D.~Hasch et~al.,
+  \emph{Precise measurements of beam spin asymmetries in semi-inclusive $\pi^0$
+  production},
+  \href{http://dx.doi.org/10.1016/j.physletb.2011.09.044}{\emph{Phys. Lett.}
+  {\bf B704} (2011) 397--402}, [\href{https://arxiv.org/abs/1106.2293}{{\tt
+  1106.2293}}].
+
+\bibitem{Gohn:2014zbz}
+{\scshape CLAS} collaboration, W.~Gohn et~al., \emph{{Beam-spin asymmetries
+  from semi-inclusive pion electroproduction}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.89.072011}{\emph{Phys. Rev.} {\bf
+  D89} (2014) 072011}, [\href{https://arxiv.org/abs/1402.4097}{{\tt
+  1402.4097}}].
+
+\bibitem{Efremov:2002ut}
+A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Azimuthal asymmetries at
+  CLAS: Extraction of $e^{a}(x)$ and prediction of $A_{UL}$}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.67.114014}{\emph{Phys. Rev.} {\bf
+  D67} (2003) 114014}, [\href{https://arxiv.org/abs/hep-ph/0208124}{{\tt
+  hep-ph/0208124}}].
+
+\bibitem{Afanasev:2003ze}
+A.~Afanasev and C.~E. Carlson, \emph{{Single spin beam asymmetry in
+  semiexclusive deep inelastic electroproduction}},  in \emph{{Intersections of
+  particle and nuclear physics. Proceedings, 8th Conference, CIPANP 2003, New
+  York, USA, May 19-24, 2003}}, 2003.
+\newblock \href{https://arxiv.org/abs/hep-ph/0308163}{{\tt hep-ph/0308163}}.
+
+\bibitem{Yuan:2003gu}
+F.~Yuan, \emph{{The Beam single spin asymmetry in semi-inclusive deep inelastic
+  scattering}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2004.03.040}{\emph{Phys. Lett.}
+  {\bf B589} (2004) 28--34}, [\href{https://arxiv.org/abs/hep-ph/0310279}{{\tt
+  hep-ph/0310279}}].
+
+\bibitem{Gamberg:2003pz}
+L.~P. Gamberg, D.~S. Hwang and K.~A. Oganessyan, \emph{{Chiral-odd
+  fragmentation functions in single pion inclusive electroproduction}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2004.01.054}{\emph{Phys. Lett.}
+  {\bf B584} (2004) 276--284},
+  [\href{https://arxiv.org/abs/hep-ph/0311221}{{\tt hep-ph/0311221}}].
+
+\bibitem{Afanasev:2006gw}
+A.~V. Afanasev and C.~E. Carlson, \emph{Beam single-spin asymmetry in
+  semiinclusive deep inelastic scattering},
+  \href{http://dx.doi.org/10.1103/PhysRevD.74.114027}{\emph{Phys. Rev.} {\bf
+  D74} (2006) 114027}, [\href{https://arxiv.org/abs/hep-ph/0603269}{{\tt
+  hep-ph/0603269}}].
+
+\bibitem{Mao:2012dk}
+W.~Mao and Z.~Lu, \emph{{Beam single spin asymmetry of neutral pion production
+  in semi-inclusive deep inelastic scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.87.014012}{\emph{Phys. Rev.} {\bf
+  D87} (2013) 014012}, [\href{https://arxiv.org/abs/1210.4790}{{\tt
+  1210.4790}}].
+
+\bibitem{Mao:2013waa}
+W.~Mao and Z.~Lu, \emph{{Beam spin asymmetries of charged and neutral pion
+  production in semi-inclusive DIS}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-013-2557-9}{\emph{Eur. Phys. J.}
+  {\bf C73} (2013) 2557}, [\href{https://arxiv.org/abs/1306.1004}{{\tt
+  1306.1004}}].
+
+\bibitem{Mao:2014dva}
+W.~Mao and Z.~Lu, \emph{{On the beam spin asymmetries of electroproduction of
+  charged hadrons off the nucleon targets}},
+  \href{http://dx.doi.org/10.1140/epjc/s10052-014-2910-7}{\emph{Eur. Phys. J.}
+  {\bf C74} (2014) 2910}, [\href{https://arxiv.org/abs/1401.4653}{{\tt
+  1401.4653}}].
+
+\bibitem{Courtoy:2014ixa}
+A.~Courtoy, \emph{{Insights into the higher-twist distribution $e(x)$ at
+  CLAS}},  \href{https://arxiv.org/abs/1405.7659}{{\tt 1405.7659}}.
+
+\bibitem{Yang:2016mxl}
+Y.~Yang, Z.~Lu and I.~Schmidt, \emph{{Twist-3 T-odd fragmentation functions
+  $G^\perp$ and $\tilde{G}^\perp$ in a spectator model}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2016.08.053}{\emph{Phys. Lett.}
+  {\bf B761} (2016) 333--339}, [\href{https://arxiv.org/abs/1607.01638}{{\tt
+  1607.01638}}].
+
+\bibitem{Mao:2014fma}
+W.~Mao, Z.~Lu, B.-Q. Ma and I.~Schmidt, \emph{{Double spin asymmetries
+  $A_{LT}^{\cos\phi_S}$ and $A_{LT}^{\cos(2\phi_h -\phi_S)}$ in semi-inclusive
+  DIS}}, \href{http://dx.doi.org/10.1103/PhysRevD.91.034029}{\emph{Phys. Rev.}
+  {\bf D91} (2015) 034029}, [\href{https://arxiv.org/abs/1412.7390}{{\tt
+  1412.7390}}].
+
+\bibitem{Wang:2016dti}
+X.~Wang, W.~Mao and Z.~Lu, \emph{{Double-spin asymmetry $A^{\cos\phi_S}_{LT}$
+  in semi-inclusive DIS at CLAS12 and EIC within the collinear framework}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.94.074014}{\emph{Phys. Rev.} {\bf
+  D94} (2016) 074014}, [\href{https://arxiv.org/abs/1606.01649}{{\tt
+  1606.01649}}].
+
+\bibitem{Anselmino:2006yc}
+M.~Anselmino, A.~Efremov, A.~Kotzinian and B.~Parsamyan, \emph{{Transverse
+  momentum dependence of the quark helicity distributions and the Cahn effect
+  in double-spin asymmetry $A_{LL}$ in semi inclusive DIS}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.74.074015}{\emph{Phys. Rev.} {\bf
+  D74} (2006) 074015}, [\href{https://arxiv.org/abs/hep-ph/0608048}{{\tt
+  hep-ph/0608048}}].
+
+\bibitem{Mao:2016hdi}
+W.~Mao, X.~Wang, X.~Du, Z.~Lu and B.-Q. Ma, \emph{{On the cos $\phi_h$
+  asymmetry in electroproduction of pions in double longitudinally polarized
+  process}},
+  \href{http://dx.doi.org/10.1016/j.nuclphysa.2015.10.004}{\emph{Nucl. Phys.}
+  {\bf A945} (2016) 153--167}.
+
+\bibitem{Airapetian:2001eg}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Single-spin
+  azimuthal asymmetries in electroproduction of neutral pions in semi-inclusive
+  deep-inelastic scattering}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.64.097101}{\emph{Phys. Rev.} {\bf
+  D64} (2001) 097101}, [\href{https://arxiv.org/abs/hep-ex/0104005}{{\tt
+  hep-ex/0104005}}].
+
+\bibitem{DeSanctis:2000fh}
+E.~De~Sanctis, W.~D. Nowak and K.~A. Oganesian, \emph{{Single-spin azimuthal
+  asymmetries in the ``Reduced twist-3 approximation''}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(00)00596-7}{\emph{Phys. Lett.}
+  {\bf B483} (2000) 69--73}, [\href{https://arxiv.org/abs/hep-ph/0002091}{{\tt
+  hep-ph/0002091}}].
+
+\bibitem{Oganessian:2000um}
+K.~A. Oganessian, N.~Bianchi, E.~De~Sanctis and W.~D. Nowak,
+  \emph{{Investigation of single spin asymmetries in $\pi^{+}$
+  electroproduction}},
+  \href{http://dx.doi.org/10.1016/S0375-9474(00)00609-6}{\emph{Nucl. Phys.}
+  {\bf A689} (2001) 784--792},
+  [\href{https://arxiv.org/abs/hep-ph/0010261}{{\tt hep-ph/0010261}}].
+
+\bibitem{Efremov:2001ia}
+A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Predictions for azimuthal
+  asymmetries in pion and kaon production in SIDIS off a longitudinally
+  polarized deuterium target at HERMES}},
+  \href{http://dx.doi.org/10.1007/s100520200918}{\emph{Eur. Phys. J.} {\bf C24}
+  (2002) 407--412}, [\href{https://arxiv.org/abs/hep-ph/0112166}{{\tt
+  hep-ph/0112166}}].
+
+\bibitem{Efremov:2002td}
+A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Azimuthal asymmetry in
+  electroproduction of neutral pions in semiinclusive DIS}},
+  \href{http://dx.doi.org/10.1016/S0370-2693(01)01258-8,
+  10.1016/S0370-2693(02)02518-2}{\emph{Phys. Lett.} {\bf B522} (2001) 37--48},
+  [\href{https://arxiv.org/abs/hep-ph/0108213}{{\tt hep-ph/0108213}}].
+
+\bibitem{Efremov:2002sd}
+A.~V. Efremov, K.~Goeke and P.~Schweitzer, \emph{{Azimuthal asymmetries and
+  Collins analyzing power}},
+  \href{http://dx.doi.org/10.1016/S0375-9474(02)01199-5}{\emph{Nucl. Phys.}
+  {\bf A711} (2002) 84--88}, [\href{https://arxiv.org/abs/hep-ph/0206267}{{\tt
+  hep-ph/0206267}}].
+
+\bibitem{Ma:2001ie}
+B.-Q. Ma, I.~Schmidt and J.-J. Yang, \emph{{Azimuthal spin asymmetries of pion
+  electroproduction}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.65.034010}{\emph{Phys. Rev.} {\bf
+  D65} (2002) 034010}, [\href{https://arxiv.org/abs/hep-ph/0110324}{{\tt
+  hep-ph/0110324}}].
+
+\bibitem{Ma:2002ns}
+B.-Q. Ma, I.~Schmidt and J.-J. Yang, \emph{{Reanalysis of azimuthal spin
+  asymmetries of meson electroproduction}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.66.094001}{\emph{Phys. Rev.} {\bf
+  D66} (2002) 094001}, [\href{https://arxiv.org/abs/hep-ph/0209114}{{\tt
+  hep-ph/0209114}}].
+
+\bibitem{Schweitzer:2003yr}
+P.~Schweitzer and A.~Bacchetta, \emph{{Azimuthal single spin asymmetries in
+  SIDIS in the light of chiral symmetry breaking}},
+  \href{http://dx.doi.org/10.1016/j.nuclphysa.2003.12.010}{\emph{Nucl. Phys.}
+  {\bf A732} (2004) 106--124},
+  [\href{https://arxiv.org/abs/hep-ph/0310318}{{\tt hep-ph/0310318}}].
+
+\bibitem{Lu:2014fva}
+Z.~Lu, \emph{{Single-spin asymmetries in electroproduction of pions on the
+  longitudinally polarized nucleon targets}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.90.014037}{\emph{Phys. Rev.} {\bf
+  D90} (2014) 014037}, [\href{https://arxiv.org/abs/1404.4229}{{\tt
+  1404.4229}}].
+
+\bibitem{Airapetian:2005jc}
+{\scshape HERMES} collaboration, A.~Airapetian et~al., \emph{{Subleading-twist
+  effects in single-spin asymmetries in semi-inclusive deep-inelastic
+  scattering on a longitudinally polarized hydrogen target}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2005.06.067}{\emph{Phys. Lett.}
+  {\bf B622} (2005) 14--22}, [\href{https://arxiv.org/abs/hep-ex/0505042}{{\tt
+  hep-ex/0505042}}].
+
+\bibitem{Mao:2014aoa}
+W.~Mao, Z.~Lu and B.-Q. Ma, \emph{{Transverse single-spin asymmetries of pion
+  production in semi-inclusive DIS at subleading twist}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.90.014048}{\emph{Phys. Rev.} {\bf
+  D90} (2014) 014048}, [\href{https://arxiv.org/abs/1405.3876}{{\tt
+  1405.3876}}].
+
+\bibitem{Cheng:1972sy}
+T.~P. Cheng and A.~Zee, \emph{{Coincidence Electroproduction and Scaling in the
+  Regge Region}}, \href{http://dx.doi.org/10.1103/PhysRevD.6.885}{\emph{Phys.
+  Rev.} {\bf D6} (1972) 885--893}.
+
+\bibitem{Aubert:1983cz}
+{\scshape European Muon} collaboration, J.~J. Aubert et~al., \emph{Measurement
+  of hadronic azimuthal distributions in deep inelastic muon proton
+  scattering},
+  \href{http://dx.doi.org/10.1016/0370-2693(83)91076-6}{\emph{Phys. Lett.} {\bf
+  130B} (1983) 118--122}.
+
+\bibitem{Dakin:1972db}
+J.~T. Dakin, G.~J. Feldman, W.~L. Lakin, F.~Martin, M.~L. Perl, E.~W. Petraske
+  et~al., \emph{Preliminary results on the inclusive electroproduction of
+  hadrons},  1972.
+
+\bibitem{Mkrtchyan:2007sr}
+H.~Mkrtchyan, P.~Bosted, G.~Adams, A.~Ahmidouch, T.~Angelescu et~al.,
+  \emph{{Transverse momentum dependence of semi-inclusive pion production}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2008.05.047}{\emph{Phys. Lett.}
+  {\bf B665} (2008) 20--25}, [\href{https://arxiv.org/abs/0709.3020}{{\tt
+  0709.3020}}].
+
+\bibitem{Anselmino:2011ch}
+M.~Anselmino, M.~Boglione, U.~D'Alesio, S.~Melis, F.~Murgia et~al.,
+  \emph{General helicity formalism for polarized semi-inclusive deep inelastic
+  scattering}, \href{http://dx.doi.org/10.1103/PhysRevD.83.114019}{\emph{Phys.
+  Rev.} {\bf D83} (2011) 114019}, [\href{https://arxiv.org/abs/1101.1011}{{\tt
+  1101.1011}}].
+
+\bibitem{Efremov:2004tp}
+A.~V. Efremov, K.~Goeke, S.~Menzel, A.~Metz and P.~Schweitzer, \emph{{Sivers
+  effect in semi-inclusive DIS and in the Drell--Yan process}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2005.03.010}{\emph{Phys. Lett.}
+  {\bf B612} (2005) 233--244},
+  [\href{https://arxiv.org/abs/hep-ph/0412353}{{\tt hep-ph/0412353}}].
+
+\bibitem{Gamberg:2013kla}
+L.~Gamberg, Z.-B. Kang and A.~Prokudin, \emph{{Indication on the Process
+  Dependence of the Sivers Effect}},
+  \href{http://dx.doi.org/10.1103/PhysRevLett.110.232301}{\emph{Phys. Rev.
+  Lett.} {\bf 110} (2013) 232301}, [\href{https://arxiv.org/abs/1302.3218}{{\tt
+  1302.3218}}].
+
+\bibitem{Sun:2013dya}
+P.~Sun and F.~Yuan, \emph{{Energy evolution for the Sivers asymmetries in hard
+  processes}}, \href{http://dx.doi.org/10.1103/PhysRevD.88.034016}{\emph{Phys.
+  Rev.} {\bf D88} (2013) 034016}, [\href{https://arxiv.org/abs/1304.5037}{{\tt
+  1304.5037}}].
+
+\bibitem{Gluck:2000dy}
+M.~Gl{\"u}ck, E.~Reya, M.~Stratmann and W.~Vogelsang, \emph{{Models for the
+  polarized parton distributions of the nucleon}},
+  \href{http://dx.doi.org/10.1103/PhysRevD.63.094005}{\emph{Phys. Rev.} {\bf
+  D63} (2001) 094005}, [\href{https://arxiv.org/abs/hep-ph/0011215}{{\tt
+  hep-ph/0011215}}].
+
+\end{thebibliography}\endgroup
+
+%\bibliography{\BibPath/biblio_ww}
 

### 2019-05-29 arxiv2/test-WW-type-v2H.tex
AP

--- 2019-04-30 arxiv2/test-WW-type-v2H.tex
@@
 	and reproduce the results presented in this work, and may easily 
-	be adapted by interested colleagues for their purposes
-	\cite{Mathematica}.
-
-\newpage
+	be adapted by interested colleagues for their purposes~\footnote{Open-source packages with implementations of SIDIS structure functions
+in the WW-type approximation are publicly available on github.com: in
+Mathematica, Version 11.3 on https://github.com/prokudin/WW-SIDIS, in Python on https://jeffersonlab.github.io/jam3d.}.
+
+%\newpage
 %======= SECTION 2: SIDIS & TMDs & FFs ===============================
@@
 \be
-	N(x,\dots,\phi) = \frac{N_0(x,\dots)}{2\pi} \biggl(1
-		+ \cos\phi\;\asympre{UU}{\cos\phi_h}(x,\dots)
-		+ \cos2\phi\;\asympre{UU}{\cos2\phi_h}(x,\dots)\Biggr)
+	N(x,\dots,\phi_h) = \frac{N_0(x,\dots)}{2\pi} \biggl(1
+		+ \cos\phi_h\;\asympre{UU}{\cos\phi_h}(x,\dots)
+		+ \cos2\phi_h\;\asympre{UU}{\cos2\phi_h}(x,\dots)\Biggr)
 \ee
@@
      	\frac{d^4\sigma_{\rm leading}}{dx\,dy\,dz\,d\psi_l}
-   &=&	 \frac{1}{2\pi}\;\frac{d \hat{\sigma}}{dy} \; F_{UU}(x,z)
+   &=&	 \frac{1}{2\pi}\; \frac{4\pi \alpha_{em}^2}{xyQ^2}\biggl(1-y+\frac12y^2\biggr) \; F_{UU}(x,z)
         \Biggl\{\;1 + \lambda\,S_L\,    p_2\,A_{LL} \Biggr\}
@@
 	\frac{d^4\sigma_{\rm subleading}}{dx\,dy\,dz\,d\psi_l}
-   &=&	 \frac{1}{2\pi}\;\frac{d \hat{\sigma}}{dy} \; F_{UU}(x,z)
-        \Biggl\{ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)}
-  	+ \lambda\,S_T\cos(\phi_S)\,p_4\,A_{LT}^{\cos(\phi_S)}
+   &=&	 \frac{1}{2\pi}\; \frac{4\pi \alpha_{em}^2}{xyQ^2}\biggl(1-y+\frac12y^2\biggr) \; F_{UU}(x,z)
+        \Biggl\{ S_T\sin(\phi_S)\,p_3\,A_{UT}^{\sin(\phi_S)} +
+  \nonumber \\
+  & &	 \lambda\,S_T\cos(\phi_S)\,p_4\,A_{LT}^{\cos(\phi_S)}
           \Biggr\} \, ,
@@
 
-\newpage
+%\newpage
 \begin{subequations}\ba
@@
 xh_T^q(x,\kperp^2)      &\WWtype&
-                       	- h_1^q(x,\kperp^2) - h_{1T}^{\perp(1)}(x,\kperp^2),
+                       	- h_1^q(x,\kperp^2) - h_{1T}^{\perp(1)q}(x,\kperp^2),
                        	\label{Eq:WW-type-7}\\
 xh_T^{\perp q}(x,\kperp^2)&\WWtype&
-                       	\phantom{-}h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)}(x,\kperp^2).
+                       	\phantom{-}h_1^q(x,\kperp^2)-h_{1T}^{\perp(1)q}(x,\kperp^2).
                        	\phantom{\frac11} \label{Eq:WW-type-8}
@@
 xh^q(x,\kperp^2)           	&\WWtype&
-                       	- 2\,{h_1^{\perp(1)}(x,\kperp^2)}.\phantom{\frac11 XXXXx}
+                       	- 2\,{h_1^{\perp(1)q}(x,\kperp^2)}.\phantom{\frac11 XXXXx}
                        	\label{Eq:WW-type-last}
@@
 will present pragmatic solutions for how to deal with the TMDs
-$f_T^a(x,k_\perp^{2})$ and $h^a(x,k_\perp)$ phenomenologically.
+$f_T^a(x,k_\perp^{2})$ and $h^a(x,k_\perp^2)$ phenomenologically.
 For now let us keep in mind that
@@
 \cite{Efremov:2002qh,Schweitzer:2003uy,Ohnishi:2003mf,Cebulla:2007ej,
-Efremov:2002ut,Afanasev:2003ze,Yuan:2003gu,Gamberg:2003pz,Metz:2004je,Afanasev:2006gw,Mao:2012dk,Mao:2013waa,Mao:2014dva,Lorce:2014hxa,Courtoy:2014ixa,Yang:2016mxl}.
+Efremov:2002ut,Afanasev:2003ze,Yuan:2003gu,Gamberg:2003pz,Metz:2004je,Afanasev:2006gw,Mao:2012dk,Mao:2013waa,Mao:2014dva,Lorce:2014hxa,Courtoy:2014ixa,Yang:2016mxl, Pasquini:2018oyz}.
 But more phenomenological work and dedicated studies on the basis of models
@@
 Science Foundation under Contract No.\ PHY-1623454 (A.P.) and
-Contract No.\ PHY-1406298 (P.S.), and the Wilhelm Schuler Stiftung (P.S.).
+Contract No.\ PHY-1812423 (P.S.), and the Wilhelm Schuler Stiftung (P.S.). The work was supported by DOE grant no. DE-FG02-04ER41309.
 We thank the COMPASS and HERMES Collaborations for the 
@@
 nucleon. The Boer--Mulders functions were studied phenomenologically in
-Refs.~\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa}
+Refs.~\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa},  we present the parameters of extractions of 
+the Boer-Mulders frunction from Ref.~\cite{Barone:2010gk} in Tablel~\ref{fitparbm}.
 
@@
 		\frac{2 M_N^2}{\pi{\avkperp_{h_{1L}^\perp}^2}}\,
-		e^{-\kperp^2/{\avkperp_{h_{1L}^\perp}^2}}
+		e^{-\kperp^2/{\avkperp_{h_{1L}^\perp}}}
 	  && 	\mbox{cf.\ Sec.~\ref{Sec-6.2:FULsin2phi},}	

### 2019-05-30 arxiv2/test-WW-type-v2H.tex
AP

@@
 Notice also that, e.g., $f_{1T}^{\perp (1),q}(x)$ is related to the
-soft-gluon-pole matrix element $F_{FT}(x,x)$ \cite{Boer:2003cm,Ji:2006ub},
+soft-gluon-pole matrix element $T_{F}(x,x)$ \cite{Boer:2003cm,Ji:2006ub},
 which is a $\bar{q}gq$-term that one would naturally neglect
@@
 	\label{Eq:Gauss-h1}\\
-	H_{1}^{\perp}(z,\pperp^2) &=&  H_{1}^{\perp (1)}(z) \;
+	H_{1}^{\perp a}(z,\pperp^2) &=&  H_{1}^{\perp (1) a}(z) \;
 	\frac{2 z^2 \mh^2}{\pi \avpperp_{H_{1}^\perp}^2} \;
@@
 
-The asymmetries $A_{UT, \langle y \rangle}^{\sin(\phi_h+\phi_S)}= (1-y)F_{UT}^{\sin(\phi_h+\phi_S)}/((1-y + y^2/2)F_{UU})$
+The asymmetries $A_{UT, \langle y \rangle}^{\sin(\phi_h+\phi_S)}= \langle(1-y)F_{UT}^{\sin(\phi_h+\phi_S)}\rangle/\langle(1-y + y^2/2)F_{UU}\rangle$
 are plotted in Fig.~\ref{aut_h1_jlab} as functions of $x$ in comparison
@@
 
-The asymmetries  $A_{UU, \langle y\rangle}^{\cos(2\phi_h)}=(1-y)F_{UU}^{\cos(2\phi_h)}/((1-y + y^2/2)F_{UU})$
+The asymmetries  $A_{UU, \langle y\rangle}^{\cos(2\phi_h)}=\langle(1-y)F_{UU}^{\cos(2\phi_h)}\rangle/\langle(1-y + y^2/2)F_{UU}\rangle$
 for HERMES \cite{Airapetian:2012yg} and $A_{UU}^{\cos(2\phi_h)}=F_{UU}^{\cos(2\phi_h)}/F_{UU}$ for COMPASS \cite{Adolph:2014pwc}
@@
 	\frac{2M_N}{Q}\;x\sum_q e_q^2\,\Biggl[
-	x \, f_T^{\perp(2)q}(x) \; D_1(z) \;b^{(2)}_{\rm C}\;
+	x \, f_T^{\perp(2)q}(x) \; D_1^q(z) \;b^{(2)}_{\rm C}\;
 	\left(\frac{z\Phperp}{\lambda}\right)^{\!\!2}\,{ \cal G}(\Phperp)&
@@
 	\frac{2M_N}{Q}\;x\sum_q e_q^2\,\Biggl[
-	x \; f_T^{\perp(2)q}(x) \; D_1(z) \; c^{(2)}_{\rm C} \;
+	x \; f_T^{\perp(2)q}(x) \; D_1^q(z) \; c^{(2)}_{\rm C} \;
 	\biggl(\frac{z}{\lambda^{1/2}}\biggr)^{\!\!2} &
@@
 To describe the transverse momentum dependence of $f_1^a(x,k_\perp^2)$
-and $D_1(z,P_\perp^2)$ we use the Gaussian Ansatz in
+and $D_1^a(z,P_\perp^2)$ we use the Gaussian Ansatz in
 Eqs.~(\ref{Eq:Gauss-f1},~\ref{Eq:Gauss-D1}). All early
@@
 Refs.~\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa},  we present the parameters of extractions of 
-the Boer-Mulders frunction from Ref.~\cite{Barone:2010gk} in Tablel~\ref{fitparbm}.
+the Boer-Mulders function from Ref.~\cite{Barone:2010gk} in Tablel~\ref{fitparbm}.
 

### 2019-06-09 arxiv2/test-WW-type-v2H.tex
AP

--- 2019-05-02 arxiv2/test-WW-type-v2H.tex
@@
 \author[f]{B.~U.~Musch}
-\author[k]{B.~Parsamyan}
+\author[k,e]{B.~Parsamyan}
 \author[g,b]{A.~Prokudin}
@@
 nucleon. The Boer--Mulders functions were studied phenomenologically in
-Refs.~\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa}
+Refs.~\cite{Barone:2009hw,Barone:2010gk,Barone:2015ksa},  we present the parameters of extractions of 
+the Boer-Mulders function from Ref.~\cite{Barone:2010gk} in Tablel~\ref{fitparbm}.
 
@@
   [\href{https://arxiv.org/abs/hep-ph/0604022}{{\tt hep-ph/0604022}}].
-
-\bibitem{Mathematica}
-A.~Prokudin and K.~Tezgin, ``{Open-source packages with implementations of
-  SIDIS structure functions in the WW-type approximation are publicly available
-  on \texttt{github.com}: \\ in \texttt{Mathematica, {V}ersion 11.3} on {\href{
-  https://github.com/prokudin/WW-SIDIS}{
-  https://github.com/prokudin/WW-SIDIS}},\\ in \texttt{Python} on {\href{
-  https://jeffersonlab.github.io/jam3d/_build/html/index.html}{
-  https://jeffersonlab.github.io/jam3d/\_build/html/index.html}}}.''
 
@@
 
+\bibitem{Pasquini:2018oyz}
+B.~Pasquini and S.~Rodini, \emph{{The twist-three distribution $e^q(x,k_\perp)$
+  in a light-front model}},
+  \href{http://dx.doi.org/10.1016/j.physletb.2018.11.033}{\emph{Phys. Lett.}
+  {\bf B788} (2019) 414--424}, [\href{https://arxiv.org/abs/1806.10932}{{\tt
+  1806.10932}}].
+
 \bibitem{Mao:2014fma}
@@
 \end{thebibliography}\endgroup
-
-%\bibliography{\BibPath/biblio_ww}
 
